### 2018-11-02 2ECFDT.tex
Initial commit

\section{FDT for 2EC}\label{2EC}

In Section \ref{binaryfdt} our focus was on binary MIPs. In this section, in an attempt to extend FDT to 0,1,2 problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem. Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2. In the 2EC problem, we are given non-negative costs on the edge of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$. Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take an edge at most 2 times. The natural linear programming relaxation is $\EC(G) = \{x\in [0,2]^E: x(\delta(U))\geq 2 \mbox{ for } \emptyset \subset U \subset V\}$. Notice that $\dom(\EC(G))\cap [0,2]^{E} = \EC(G)$, since 2EC is a covering problem. We want to prove the following theorem.

\FDTEC*

We do not know the exact value for $g_{\EC}$, but we know $\frac{6}{5} \leq g_{\EC} \leq \frac{3}{2}$ \cite{carr-ravi,Wolsey1980}. Also, we need to remark that polyhedral version of Christofides' algorithm provides a $\frac{3}{2}$-approximation for 2EC, i.e. we already have an algorithm with $C\leq \frac{3}{2}$. However, we show later in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$.

The FDT algorithm for 2EC is very similar to the one for binary MIPs, but there are some differences as well. First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for 0,1,2 problems expect for one additional clause.

\begin{restatable}{lemma}{2ECLPC}
	\label{LPC2EC}
		Given $x\in \EC(G)$, and $e\in E$ we can find in polynomial time vectors $x^0,x^1$ and $x^2$ and scalars $\gamma_0,\gamma_1$, and $\gamma_2$ such that
	\begin{itemize}
		\item[(i)] $\gamma_0 + \gamma_1 +\gamma_2 \geq \frac{ 1}{g_{\EC}}$,
		\item[(ii)] $x^0,x^1,$ and $x^2$ are in  $ \EC(G)$, 
		\item[(iii)] $x^0_e=0$, $x^1_e=1$, and $x^2_e=2$,
		\item[(iv)] $\gamma_0 x^0 + \gamma_1{x}^1  + \gamma_2x^2\leq {x}$,
		\item[(v)] for $f\in E$ with ${x}_f\geq 1$, we have $x^j_f\geq 1$ for $j=0,1,2$. 
	\end{itemize}
\end{restatable}

\begin{proof}
	Consider the following linear programing with variables $\lambda_j$ and $x^j$ for $j=0,1,2$. 
	\begin{align}
	\quad\quad& \max\quad \;\sum_{j=0,1,2}\lambda_j\\
	&\;\text{s.t.} \quad x^j(\delta(U))\geq 2\lambda_j \;& \mbox{ for $\emptyset \subset U \subset V$, and $j=0,1,2$} \label{feasibility2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq 2\lambda_j\; &\mbox{ for $j=0,1,2$}\label{bound2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^j_e = j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1+x^2 \leq x\label{packing2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1,\lambda_2 \geq 0
	\end{align}

	Let $x^j$, $\gamma_j$ for $j=0,1,2$ be an optimal solution solution to the LP above. Let $\hat{x}^{j}=\frac{x^j}{\gamma_j}$ for $j=0,1,2$ where $\gamma_j>0$. If $\gamma_j=0$, let $\hat{x}^{j}=0$. Observe that  (ii), (iii), (iv), and (v) are satisfied with this choice. In order to show that (i) is also satisfied we prove the following claim.

	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1+\gamma_2\geq \frac{1}{g_{\EC}}$.
	\end{claim}
	\begin{proof}
		Suppose for contradiction $\sum_{j=0,1,2}\gamma_j = \frac{1}{g_{\EC}} - \epsilon$ for some $\epsilon >0$.

		Construct graph $G'$ by removing edge $f$ with $x_f\geq 1$ and replacing it with a path $P_f$ of length $\ceil{\frac{2}{\epsilon}}$. Define $x'_h = x_h$ for each edge $h$ such that $x_h<1$. For each $h\in P_f$ let $x'_h= x_f$ for all $f$ with $x_f\geq 1$. It is easy to check that $x'\in \EC(G')$. By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and 2-edge-connected multigraphs $F'_i$ of $G'$ for $i=1,\ldots,k$ such that 
		$\sum_{i=1}^{k}\theta_i \chi^{F'_i}\leq g_{\EC}x'$.

		Note that each $F'_i$ contains at least one copy of every edge in any path $P_f$, except for at most one edge in the path. We will obtain 2-edge-connected multigraphs $F_1,\ldots,F_k$ of $G$ using $F'_1,\ldots,F'_k$, respectively. To obtain $F_i$ first remove all $P_f$ paths from $F'_i$. Suppose there is an edge $h$ in $P_f$ such that $\chi^{F'_i}_h=0$, this means that for any edge $p\in P_f$ such that $p\neq h$, $\chi^{F'_i}_p=2$. In this case, let $\chi^{F_i}_f=2$, i.e. add two copies of $f$ to $F_i$. If there is an edge $h\in P_f$ with $\chi^{F'_i}_h = 1$, let $\chi^{F_i}_f=1$, i.e. add one copy of $f$ to $F_i$. If for all edge $h\in P_f$, we have $\chi^{F'_i}_h=2$, then let $\chi^{F_i}_f=2$. For $f\in E$ with $x_f<1$ we have
		\begin{equation}
		\sum_{i=1}^{k}\theta_i \chi^{F_i}_f=\sum_{i=1}^{k}\theta_i \chi^{F'_i}_f\leq g_{\EC}x'_f= g_{\EC}x_f.
		\end{equation}
		In addition for $f\in E$ with $x_f\geq 1$ we have $\chi^{F_i}_f \leq \frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}$ by construction.
		\begin{align*}
		\sum_{i=1}^{k}\theta_i \chi^{F_i}_f&\leq \sum_{i=1}^{k}\theta_i\frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
		&= \frac{\sum_{h\in P_f} \sum_{i=1}^{k}\theta_i\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
		&\leq \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
		&= \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
		&= \frac{\ceil{\frac{2}{\epsilon}}}{\ceil{\frac{2}{\epsilon}}-1}g_{\EC}x_f
		\end{align*}
		Therefore, we have 
		\begin{equation}
		x' \geq \sum_{i\in [k]: \chi^{F_i}_e=1}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}+\sum_{i\in [k]: \chi^{F_i}_e=2}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}.
		\end{equation}
		Let $x^j = \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}$ and $\theta_j =  \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$ for $j=0,1,2$. It is easy to check that $x^j$ , $\theta_j$ for $j=0,1,2$ is a feasible solution to the LP above. Notice that $\sum_{j=0,1,2}\theta_j = \frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$. By assumption, we have $\frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\leq  \frac{1}{g_{\EC}}-\epsilon$. However, this means $2\leq 1$ which is a contradiction.
	\end{proof}
	This concludes the proof.
\end{proof}

In contrast to FDT for binary MIPs where we round up the fractional variables that are already branched on at each level, in FDT for 2EC we keep all coordinates as they are and preform a rounding procedure at the end. Formally, let $L_i$ for $i=1,\ldots,|\sup(x^*)|$ be collections of pairs of feasible points in $\EC(G)$ together with their multipliers. Let $t=|\sup(x^*)|$ and assume without loss of generality that $\sup(x^*)=\{e_1,\ldots,e_t\}$.

\begin{lemma}\label{2ecpruning}
	The FDT algorithm for 2EC in  polynomial time produces sets $L_0,\ldots,L_t$ of pairs $x\in \EC(G)$ together with multipliers $\lambda$ with the following properties.
	\begin{enumerate}
			\item[a.] If $x\in L_i$, then $x_{e_j}=0$ or $x_{e_j}\geq 1$ for $j=1,\ldots,i$,
		\item [b.] $\sum_{(x,\lambda)\in L_i }\lambda \geq \frac{1}{g_{\EC}^i}$,
		\item[c.]  $\sum_{(x,\lambda)\in L_i }\lambda x \leq x^*$,
		\item[d.] $|L_i|\leq t$.
		\end{enumerate}
\end{lemma}
\begin{proof}
	We proceed by induction on the $i$. Define $L_0=\{(x^*,1)\}$. It is easy to check all the properties are satisfied. Now, suppose by induction we have $L_{i-1}$ for some $i=1,\ldots,t$ that satisfies all the properties. For each solution $x^\ell$ in $L_{i-1}$ apply Lemma \ref{LPC2EC} on $x^\ell$ and $e_{i}$ to obtain $x^{\ell j}$ and $\lambda_{\ell j}$ for $j=0,1,2$. Let $L'$ be the collection that contains $(x^{\ell j},\lambda_\ell \cdot \lambda_{\ell j})$ for $j=0,1,2$, when applied to all $(x^\ell,\lambda_\ell)$ in $L_{i-1}$. Similar to the proof in Lemma \ref{prune} one can check that $L_i$ satisfies properties (b), (c). We now verify property (a). Consider a solution $x^\ell$ in $L_{i-1}$. For $e\in \{e_1,\ldots,e_{i-1}\}$ if $x^\ell_e =0$, then by property (iv) in Lemma \ref{LPC2EC} we have $x^{\ell j}=0$ for $j=0,1,2$. Otherwise by induction we have $x^{\ell}_{e}\geq 1$ in which case property (v) in Lemma \ref{LPC2EC} ensures that $x^{\ell j}_e\geq 1$ for $j=0,1,2$. Also, $x^{\ell j}_{e_i}= j$, so $x^{\ell j}_{e_i}=0$ or $x^{\ell j}_{e_i}\geq 1$ for $j=0,1,2$.

	If $|L'|\geq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
\end{proof}

Consider the solutions $x$ in $L_t$. For each variable $e$ we have $x_e=0$ or $x_e\geq 1$. 
\begin{lemma}\label{rounddown}
	Let $x$ be a solution in $L_t$. Then $\floor{x} \in \EC(G)$. 
\end{lemma}
\begin{proof}
	Suppose not. Then there is a set of vertices $\emptyset \subset U \subset V$ such that $\sum_{e\in \delta(U)}\floor{x_e}<2$. Since $x\in \EC(G)$ we have $\sum_{e\in \delta(U)}x_e \geq 2$. Therefore, there is an edge $f\in \delta(U)$ such that $x_f$ is fractional. By property (a) in Lemma \ref{2ecpruning}, we have $1<  x_f < 2$. Therefore, there is another edge $h$ in $\delta(U)$ such that $x_h>0$, which implies that $x_h\geq 1$. But in this case $\sum_{e\in \delta(U)}\floor{x_e}\geq  \floor{x_f}+\floor{x_h}  \geq 2$. This is a contradiction.
\end{proof}

The FDT algorithm for 2EC iteratively applies Lemmas \ref{LPC2EC} and \ref{2ecpruning} to variables $x_1,\ldots,x_t$ to obtain leaf point solutions $L_t$. Then, we just need to apply Lemma \ref{rounddown} to obtain the 2-edge-connected multigraphs from every solution in $L_t$. Notice that $t\leq 2|V|-3$ \cite{}. By Lemma \ref{2ecpruning} we have
\begin{align*}
\sum_{(x,\lambda)\in L_t} \frac{\lambda}{\sum_{(x,\lambda)\in L_t}\lambda} \floor{x} \leq \frac{1}{\sum_{(x,\lambda)\in L_t}\lambda} \sum_{(x,\lambda)\in L_t} \lambda {x} \leq g^t_{\EC} x^*.
\end{align*}

### 2018-11-02 algorithmbinary.tex
Initial commit

\section{FDT on binary MIPs}
\label{binaryfdt}

In this section we present the fractional decomposition tree (FDT) algorithm and prove its correctness.

Consider a formulation instance $I=(A,G,b)$, set 
\begin{equation}
S(I)= \{(x,y)\in \mathbb{R}^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
\end{equation}
and its linear relaxation
\begin{equation}
P(I) = \{(x,y)\in \mathbb{R}^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
\end{equation}
Also assume we are given a point $(x^*,y^*)\in P(I)$. For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$. In this section, we prove the following theorem.

\binaryFDT*

One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{DomToIP} that we will also prove in this section.

Although the theoretical worst-case upper bound on $C$ in the statement of Theorem \ref{binaryFDT} can be very large, we will show that in practice $C$ can be really small and hence FDT can provide good LP-based approximation algorithms in many cases. We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.  In the remainder of this section we explain the FDT algorithm and prove Theorem \ref{binaryFDT}. For simplicity in the notations we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively. Let $t=|\sup(x^*,y^*)|$. We assume without loss of generality that $\sup(x^*,y^*)= \{1,\ldots,t\}$.

We begin with the following lemmas that show how the FDT algorithm branches on a variable.
\begin{lemma}\label{LPClemma}
	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vector $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that
	\begin{itemize}
		\item[(i)] $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$,
		\item[(ii)] $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$, 
		\item[(iii)] $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$,
		\item[(iv)] $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
	\end{itemize}
\end{lemma}

\begin{proof}[Proof of Lemma \ref{LPClemma}]

	Consider the following linear programing which we denote by $\LPC(\ell,x',y')$. The variables of $\LPC(\ell,x',y')$ are $\gamma_0,\gamma_1$ and $(x^0,y^0)$ and $(x^1,y^1)$. 
	\begin{align}
	\LPC(\ell,x',y')\quad\quad& \max\quad \;\lambda_0+\lambda_1\\
	&\;\text{s.t.} \quad Ax^j + Gy^j\geq b\lambda_j & \mbox{ for $j=0,1$} \label{feasibility}\\
	&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq \lambda_j &\mbox{ for $j=0,1$}\label{bound}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0_\ell = 0,\; x^1_\ell =\lambda_1\label{branchcoordinate}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1 \leq x'\label{packing}\\
	&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1 \geq 0
	\end{align}

	Let $(x^0,y^0),(x^1,y^1)$, and $\gamma_0,\gamma_1$ be an optimal solution solution to the LP above. Let $(\hat{x}^0,\hat{y}^0) = (\frac{x^0}{\gamma_0},\frac{y^0}{\gamma_0})$, $(\hat{x}^1,\hat{y}^1) = (\frac{x^1}{\gamma_1},\frac{y^1}{\gamma_1})$. Observe that  (ii), (iii), (iv) are satisfied with this choice. In order to show that (i) is also satisfied we prove the following claim.

	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1\geq \frac{1}{g}$.
	\end{claim}
\begin{proof}
We show that there is a feasible solution that achieves the objective value of $\frac{1}{g}$. By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $(\tilde{x}^i,\tilde{y}^i)\in S$ for $i=1,\ldots,k$ such that 
 $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$.

\begin{equation}\label{splitting}
 x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
  ={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}
\end{equation}
For $j=0,1$, let $(x^j,y^j) = \sum_{i\in [k]:\tilde{x}^i_\ell=j} \frac{\theta_i}{g}(\tilde{x}^i,\tilde{y}^i)$. Also let $\lambda_0=\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g}$ and $\lambda_1 = \sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g}$. Note that $\lambda_0+\lambda_1 = \frac{1}{g}$. Constraint \ref{packing} is satisfied by Inequality \ref{splitting}. Also, for $j=0,1$ we have
\begin{equation}
 Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \leq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
\end{equation}
Hence, Constraints \ref{feasibility} holds. Constraint \ref{branchcoordinate} also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$. The rest of the constraints trivially hold. 
\end{proof}
This concludes the proof.	
\end{proof}

We now show if $x'$ in the statement of of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.

\begin{lemma}\label{round-up}
	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vector $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that
	\begin{itemize}
		\item[(i)] $\gamma_0 + \gamma_1  \geq\frac{ 1}{g}$,
		\item[(ii)] $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, 
		\item[(iii)] $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$,
		\item[(iv)] $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
		 x'$,
		 \item[(v)] $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
	 	\end{itemize}
\end{lemma} 
\begin{proof}
	By Lemma \ref{LPClemma} we can find $(\bar{x}^0,\bar{y}^0)$, $(\bar{x}^1,\bar{y}^1)$, $\gamma_0$ and $\gamma_1$ that satisfy (i), (ii), (iii), and (iv). We define $\hat{x}^0$ and $\hat{x}^1$ as follows. For $i=0,1$, for $j=1,\ldots,\ell-1$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,n$ let $\hat{x}^i_j = \bar{x}^i_j$. We now show that $(\hat{x}^0,\bar{y}^0)$, $(\hat{x}^1,\bar{y}^1)$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions. Note that conditions (i), (ii), (iii), and (v) are trivially satisfied. Thus we only need to show (iv) holds. We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$. If $j=\ell,\ldots,n$, then this clearly holds. Hence, assume $j\leq \ell-1$. By the property of $x'$ we have $x'_j\in \{0,1\}$. If $x'_j= 0$, then by Constraint \ref{packing} we have $\bar{x}^0_j = \bar{x}^1_j=0$. Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds. Otherwise if $x'_j = 1$, then we have
	\begin{equation*}\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.\end{equation*}
Therefore (v) holds.
\end{proof}

The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs. Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$. The solutions contained in the nodes of the tree become progressively more integral at each level. Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$. We will later see how we can turn these into points in $S$.

Let us define the FDT algorithm more formally. The algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm. The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree. The points in the leaves of the FDT tree, or $L_t$, are points in $\dom(P)$ and are integral for all integer variables.

\begin{lemma}\label{prune}
	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $(x,y)\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$. 
	\begin{enumerate}
			\item[a.] If $(x,y)\in L_i$, then $x_j \in \{0,1\}$ for $j=1,\ldots,i$, i.e. the first $i$ coordinates of a solution in level $i$ are integral. 
		\item[b.] $\sum_{[(x,y),\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$.
		\item[c.] $\sum_{[(x,y),\lambda]\in L_i}\lambda x \leq x^*$.
		\item[d.] $|L_i|\leq t$.
	\end{enumerate}
\end{lemma}
\begin{proof}
	We prove this lemma using induction but one can clearly see how to turn this proof into a polynomial time algorithm. Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $(x^*,y^*)$ and multiplier 1. It is easy to check all the requirements in the lemma are satisfied for this choice.

	Suppose by induction that we have constructed sets $L_0,\ldots,L_i$. Let the solutions in $L_i$ be $(x^j,y^j)$ for $j=1,\ldots,k$ and $\lambda_j$ be their multipliers, respectively. For each $j\in 1,\ldots,k$ by Lemma \ref{round-up} (setting $(x',y')= (x^j,y^j)$ and $\ell = i$) we can find $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and $\lambda^0_j$, $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}. Define $L'$ to be the set of node with solutions $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and multipliers  $\lambda_j\lambda^0_j$, $\lambda_j\lambda^1_j$, respectively, for $j=1,\ldots,k$.

	Notice that for each $j\in \{1,\ldots,k\}$ by property (v) in Lemma \ref{round-up} we have $x_\ell^{j0}, x_\ell^{j1}\in \{0,1\}$ for $\ell = 0,\ldots,i+1$. We also have
	\begin{align*}
	\sum_{[(x,y),\lambda]\in L'} \lambda & =  \sum_{j=1}^{k} \lambda_j\lambda^0_j+\lambda_j\lambda^1_j&\\
	& \geq \sum_{j=1}^{k} \frac{\lambda_j}{ g} & (\text{By property (i) in Lemma \ref{round-up}})\\
	& \geq \frac{1}{g} \sum_{[(x,y),\lambda]\in L_i}\lambda&\\
	 & \geq \frac{1}{g^{i+1}}.&(\text{By induction hypothesis})	 
	\end{align*} 
	Also 
	\begin{align*}
\sum_{[(x,y),\lambda]\in L'}\lambda x & =  \sum_{j=1}^{k} \lambda_j\big(\lambda^0_jx^{j0}+\lambda^1_jx^{j1}\big)&\\ 
& \leq \sum_{j=1}^{k} \lambda_j x^j  & (\text{By property (iv) in Lemma \ref{round-up}})\\
& \leq \sum_{[(x,y),\lambda]\in L_i}\lambda x&\\
& \leq x^*.&(\text{By induction hypothesis})	 
\end{align*} 
Set $L'$ seems like a suitable candidate for $L_{i+1}$, however we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$. We call the following linear programming $\prun(L')$. Let $L' = \{[(x^1,y^1),\lambda_1],\ldots,[(x^k,y^k),\lambda_k]\}$. The variables of $\prun(L')$ is a scalar variable $\theta_j$ for each node $j$ in $L'$.

\begin{align}
\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{k} \theta_j\\
&\;\text{s.t.} \quad \;\;\sum_{j=1}^{k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
&\;{\color{white}{\text{s.t.}} }\quad  \;\quad\quad\theta \geq 0\label{nonneg}
\end{align}

Notice that $\theta = \lambda$ is in fact a feasible solution to $\prun(L')$. Let $\theta^*$ be the optimal vertex point solution to this LP. Since the problem is in $\mathbb{R}^k$,  $\theta^*$ has to satisfy $k$ linearly independent constraints at equality. However, there are only $t$ constraints of type \ref{packs}. Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero. We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma. Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$. Also, since $\theta^*$ is optimal and $\lambda$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{k}\lambda_j \geq \frac{1}{g^{i+1}}$. 
\end{proof}

The leaves of the FDT tree, or $L_t$ have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$. Our goal to now replace these leaves solutions in $\dom(P)$ with solutions in $S$. To this end, we need to reduce some variables with value of 1 into variables of value 0 and obtain feasibility in the meantime. We introduce a procedure that given a  point $(x,y)\in \dom(P)$ with $x\in \{0,1\}^n$ outputs a point $z\leq x$ with $z\in \{0,1\}^n$ such that $(z,w)$ is in $S$ for some vector $w\in \mathbb{R}^p$.

The algorithm ``fixes" the variables iteratively, from $x_1$ to $x_t$. Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$. Now consider the following linear programming. The variables of this LP are the $z\in \mathbb{R}^n$ variables and $w\in \mathbb{R}^p$.
\begin{align}
\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
\end{align}

If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$. Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$. Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$. This procedure is summarized in Algorithm \ref{domtoIP}.

\begin{algorithm}[H]\label{domtoIP}
	\KwIn{$(x,y)\in \dom(S)$}
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
	$x^{(0)}\leftarrow x$\\
		\For{$\ell = 0$ \textbf{to} $t-1$}{
			$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
			$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
			$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
				\eIf{$\eta = 0$}{
				$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
			}{
				$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
			}
		}
	\caption{The DomToIP algorithm}
\end{algorithm}

The following lemma proves Theorem \ref{domtoIP}.
\begin{lemma}
	Given $(x,y)\in \dom(P)$ Algorithm \ref{domtoIP} correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
\end{lemma}
\begin{proof}
	First, we need to show that in any iteration $\ell\in \{0,\ldots,n-1\}$ of Algorithm \ref{domtoIP} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
	\begin{align*}
	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
	\end{align*}
	Notice that if $\LP^{(\ell)}$ is an non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$. First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$. By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$. Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^0$. So if $x^0_j$ is zero, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$. Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$. Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.

  Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$. Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.

  We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ . We have
  \begin{equation}
   \sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
  \end{equation}
  So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of Algorithm \ref{domtoIP}. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.

  Now for the second case, assume $z^*_{\ell+1} > 0$. We have $x^{(\ell+1)}_{\ell+1}=1$. Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e. $z_{\ell+1}=1$. This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.

  Now consider $(x^{(t)},y^{(t)})$. Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$. If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$. If $x^{(t)} =1$, it must be the case that $z_t > 0$. By the argument above there is a point $(z',w')\in \IP^{(t-1)}$. We show that $x^{(t)} = z'$. Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$. We just need to show that $z'_j = 1$. Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.
  \end{proof}

This completes the FDT algorithm.

\begin{algorithm}[H]\label{FDTFull}
	\KwIn{$P= \{(x,y)\in \mathbb{R}^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \mathbb{R}^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
	\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
	$L^0\leftarrow [(x^*,y^*),1]$\\
	\For{$i=1$ \textbf{to} $t$}{
		$L'\leftarrow \emptyset$\\
		\For{$[(x,y),\lambda] \in L^i$}{
			Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
			$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
		}
		Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
	}
	\For{$[(x,y),\lambda] \in L^t$}{
		Apply Algorithm \ref{domtoIP} to $(x,y)$ to obtain $(z,w)\in S$\\
		$F \leftarrow F \cup \{[(z,w),\lambda]\}$
	}
	\textbf{return} $F$
	\caption{Fractional Decomposition Tree Algorithm}
\end{algorithm}

### 2018-11-02 gap.tex
Initial commit

\section{Stronger version of Carr-Vempala for covering problems} \label{gap}

Theorem \ref{CV} characterizes the integrality gap as the smallest number such that for any point $x\in \dom(P)$, $gx$ dominates a convex combination of points in $S$, i.e. there exists convex combination $\sum_{i=1}^{k}\lambda_ix^i \leq gx$.  In a covering problem, we assume that matrix $A$ in the description of $P$ is a non-negative matrix, hence if $y\geq x$ and $x\in P$ we have $y\in P$. We also assume the right hand side vector in (\ref{P}) is of the form $b\textbf{1}$, i.e. it is a uniform vector. Finally we assume we have bound constraints $x\leq b\textbf{1}$. This class of problems include a broad class of problems. Notice that for a covering problem $\dom(P)=P$.  We show that for these problems, we can make Theorem \ref{CV} stronger in the following sense.

\tightcuts*

In other words, the integrality gap is the smallest number such that for any $x\in P$, there exists a convex combination $y=\sum_{i=1}^{k}\lambda_ix^i$, such that $A_jy\leq g(A_jx)$ for all $j$ such that $A_jx=b$.

Notice that the proof of this theorem, same as Theorem \ref{CV}, does not imply a polynomial time algorithm.

Observe that if $C\geq g$, by Theorem \ref{CV}, there is a convex combination of points in $S$ that is dominated by $Cx$, i.e. there exists $\theta\in [0,1]^{k}$, where $\sum_{i=1}^{k}\theta_i=1$, and $x^i\in S$, such that $\sum_{i=1}^{k}\theta_ix^i\leq gx$. The same convex combination also trivially satisfies both requirements in Theorem \ref{tightcuts}. The more interesting direction is the converse. We begin with the following theorem. Suppose $v^1,\ldots,v^r$ are the extreme points of $P$. Assume for each $i=1,\ldots,r$, there exists a convex combination of points in $S$, namely $\sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell$ such that $A_j \sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell \leq CA_jv^i$ for $j$ such that $A_jv^i = b$. Let $z^i = \sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell$.
\begin{lemma}\label{epsilon}
	For any  $i\in\{1,\ldots,r\}$, there exists $\epsilon_i >0$ and ${x^i}\in P$ where ${x^i}\leq \frac{Cv^i-\epsilon_i z^i}{C(1-\epsilon_i)}$.
\end{lemma}
\begin{proof}

	Let $u^i(\epsilon) = \frac{Cv^i-\epsilon z^i}{C(1-\epsilon)}$. For $j\in \{1,\ldots,m\}$, let $t_j = A_jz^i-Cb$ and $s_j=A_jv^i-b$. 
	Assume $\epsilon <1$. For $j\in \{1,\ldots,m\}$ such that $A_jz^i\leq Cb$, i.e. $t_j\leq 0$ (this includes $j$ such that $A_jv^i=b$, i.e. $s_j=0$) we have
	\begin{equation}
	A_j u^i(\epsilon) = \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}\geq \frac{Cb-\epsilon Cb}{C(1-\epsilon)}=b
	\end{equation}
	Assume $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$. Notice that $\max_{j: t_j >0} \frac{s_j}{t_j}>0$ since for $j$ such that $t_j>0$, we have $A_jz_i > Cb$ which implies that $A_jv^i>b$, so $s_j>0$. For $j$ such that $t_j>0$ we have
	\begin{align*}
	A_ju^i(\epsilon) &= \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}& \\
	&= \frac{C(b+s_j)-\epsilon (Cb+t_j)}{C(1-\epsilon)}&\\
	&= b+ \frac{Cs_j-\epsilon t_j}{C(1-\epsilon)}&\\
	&\geq b & (\epsilon  \leq C\cdot  \frac{s_j}{t_j}, \mbox{ and } \epsilon <1, \mbox{ so } \frac{Cs_j-\epsilon t_j}{C(1-\epsilon)}\geq 0 )
	\end{align*} 
	Therefore if $\epsilon \leq 1$ and $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$ we have $Au^i(\epsilon)\geq \textbf{1}b$. Next, we show that we can choose $\epsilon$ so that $ u^i(\epsilon)\geq 0$.

	For $\ell\in \{1,\ldots,n\}$, if $z^i_\ell=0$, then we have $u_\ell^i(\epsilon) = \frac{Cv_\ell^i}{C(1-\epsilon)}\geq 0$, since $v^i_\ell\geq 0$ and $\epsilon <1$. Otherwise we have $z^i_\ell>0$. Assume $\epsilon \leq C\cdot \min_{ \ell:z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}$. Notice that for $\ell$ such that $z^i_\ell>0$, we have $v^i_\ell>0$ since $z^i$ lies in the support of $v^i$ by assumption. This means that $\min_{\ell:z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}>0$. Now, for $\ell$ such that $z^i_\ell>0$, we have $u^i_\ell(\epsilon) = \frac{Cv_\ell^i-\epsilon z_\ell^i}{C(1-\epsilon)}\geq 0$ by choice of $\epsilon$.

	Define $\epsilon_i =\min\{1, C\cdot \min_{j: t_j >0}\frac{s_j}{t_j},C\cdot\min_{\ell: z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}\}$. By the arguments above $Au^i(\epsilon_i)\geq \textbf{1}b$ and $u^i(\epsilon_i)\geq 0$. Define $x^i$ as follows: For each $j\in \{1,\ldots,m\}$, if $u^i_j(\epsilon_i)\leq b$, then let $x^i_j=u^i_j(\epsilon_i)$, otherwise let $x^i_j=b$. We need to show that $x^i\in P$. Note that clearly $x^i\geq 0$, hence we only need to show that $Ax^i\geq \textbf{1}b$. Suppose for contradiction there is $j\in \{1,\ldots,m\}$ such that $A_jx^i <b$. Since $u^i(\epsilon)\in P$, there must be $\ell^*\in\{1,\ldots,n\}$ such that $u^i_{\ell^*}(\epsilon)>b$, and $A_{j,\ell^*}>0$. But this means that $A_{j,\ell^*}\geq 1$ and $x^i_{\ell^*}=b$. Therefore $A_jx^i \geq  A_{j,\ell^*}x^i_{\ell^*}= A_{j,\ell^*}b\geq b$. \end{proof}
\begin{lemma}\label{tightcutcomb}
	There exists a convex combination of point in $S$ that is dominated by $Cv^i$ for $i=1,\ldots,r$.
\end{lemma}
\begin{proof}

	We prove something slightly stronger. We show that for $i\in\{1,\ldots,r\}$, and for $j=1,\ldots,i$, the vector $Cv^j$ dominates  a convex combination of $z^1,\ldots,z^i$ and $Cv^{i+1},\ldots,Cv^r$. Note that this is enough to prove our statement since for $i=r$, the statement implies that $Cv^j$ dominates a convex combination of $z^1,\ldots,z^r$ for $j=1,\ldots,r$.

	We proceed by induction on $i$. If $i=1$, we just need to show that $Cv^1$ is dominated by a convex combination of $z^1$ and $Cv^2,\ldots,Cv^r$. By Lemma \ref{epsilon}, there exists $x^1\leq  \frac{Cv^1-\epsilon_1z^1}{C(1-\epsilon_1)}$. We have $x^1\in P$, so we can write $x^1$ as convex combination of $v^1,\ldots, v^r$. We have
	\begin{equation}
	Cv^1 \geq  \epsilon_1z^1 + C(1-\epsilon_1)x^1 \geq \epsilon_1z^1 + C(1-\epsilon_1) \sum_{\ell=1}^{r}\lambda^1_\ell v^\ell.
	\end{equation}
	Hence,
	\begin{equation}
	Cv^1 \geq \frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}\cdot z^1 + (1-\epsilon_i)\sum_{\ell=2}^{r} \frac{\lambda^1_\ell}{1-(1-\epsilon_1)\lambda_1^1}\cdot Cv^\ell.
	\end{equation}
	Observe that $\frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}$ and $(1-\epsilon_1)\frac{\lambda^1_\ell}{1-(1-\epsilon_1)\lambda_1^1}$ for $\ell=2,\ldots,r$ form convex multipliers, so the base case holds.

	Now consider $i\in \{1,\ldots,r-1\}$. By induction, for $j=1,\ldots,i$ we have
	\begin{equation}\label{IHs}
	Cv^j \geq  \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell + \sum_{\ell=i+1}^{r}\theta^{j}_{\ell}Cv^\ell.
	\end{equation}
	Suppose we are able to show 
	 \begin{equation}\label{claim} 
	 Cv^{i+1} \geq \sum_{\ell=1}^{i+1} \mu_\ell z^\ell + \sum_{\ell=i+2}^{r}\mu_{\ell}Cv^\ell,\end{equation} 
	where $\mu\geq 0$, and $\sum_{\ell=1}^{r}\mu_{\ell}=1$. Then for $j=1,\ldots,i$ we have
	\begin{align*}
	Cv^j& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\theta^{j}_{i+1}Cv^{i+1}+  \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell.& (\mbox{By } \ref{IHs})\\
		& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\sum_{\ell=1}^{i+1}\theta^{j}_{i+1}\mu_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_{i+1}\mu_{\ell}Cv^\ell +   \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell.& (\mbox{By } \ref{claim})\\
		&= \sum_{\ell=1}^{i} (\theta^j_\ell+\mu_{\ell}\theta^j_{i+1}) z^\ell + \mu_{j+1}\theta^j_{i+1}z^{i+1} + \sum_{\ell=i+2}^{r} (\theta^j_\ell+\mu_\ell\theta^j_{i+1})Cv^\ell.&
 			\end{align*} 
		It is easy to see that the multipliers above are convex. Thus, we only need to show the convex combination in (\ref{claim}) exists. This will be similar to what we did in the base case. By Lemma \ref{epsilon}, there exists $\epsilon_{i+1}$ and $x^{i+1}$ such that
		\begin{align*}
		Cv^{i+1}&\geq \epsilon_{i+1}z^{i+1}+ C(1-\epsilon_{i+1})x^{i+1}\\
		&\geq \epsilon_{i+1}z^{i+1}+ (1-\epsilon_{i+1})\sum_{\ell=1}^{k}\lambda_{\ell}Cv^\ell
			\end{align*}
			Applying induction we can replace $Cv^j$ by $ \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell + \sum_{\ell=i+1}^{r}\theta^{j}_{\ell}Cv^\ell$ for $j=1,\ldots,i$. 
			This means
			\begin{align*}
			(1-(1-\epsilon_{i+1})(\lambda_{i+1}+\sum_{j=1}^{i}\lambda_j\theta^j_{i+1}))Cv^{i+1}&\geq \epsilon_{i+1}z^{i+1}+(1-\epsilon_{i+1})\sum_{j=1}^{i}\lambda_j (\sum_{\ell=1}^{i}\theta^j_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_\ell Cv^\ell)\\
			&+(1-\epsilon_{i+1})(\sum_{j=1}^{i}\lambda_j \lambda^j_{i+1}+\lambda^i_{i+1})C+ (1-\epsilon_{i+1})\sum_{j=i+2}^{r}\lambda_jCv^{j} 
			\end{align*}
			It is easy to show that  multipliers above are convex.
\end{proof}

### 2018-11-02 integralitygap.tex
Initial commit

\section{Introduction}

In \textbf{Multicommodity flow problem in
	trees} (\textbf{MFT}) we are given (i) a tree $T=(V,E)$, (ii) positive integer $c_e$ for each $e\in E$, i.e. \textit{capacity of edge $e$}, (iii) a collection of pairs of (distinct) vertices of $T$ denoted by $D$, called \textit{demands}, and (iv) a profit function $p:D\rightarrow \mathbb{Z}^+$. A set $L\subseteq D$ is  \textit{routable } in $(T,c)$ if the set of demands in $L$ can be routed through $T$ in the following sense.
\begin{equation}
|\{(u,v)\in L: \mbox{$e$ is in the unique $uv$-path in $T$}\}|\leq c_e \quad \mbox{for all $e\in E$}.\end{equation}

For any $L\subseteq D$, we let $L_e=\{(u,v)\in L: \mbox{$e$ is in the unique $uv$-path in $T$}\}$, the set of demands in $L$ that pass through $e$. Hence, $D_e$ is the set of all demands  that ``load" edge $e$. In MFT the goal is to find the maximum profit set of demands $L$ that is routable in $(T,c)$. For the maximum profit routable subset of demands $L$ we have $\opt(T,D,c,p)= \sum_{d \in L}p(d)$. When $c_e=1$ for all $e\in T$, we have the \textbf{Unit-capacity MFT} (UMFT).

The natural linear programing relaxation, \textit{cut-LP}, for the problem is as follows.
\begin{align}
\lp_{cut}(T,D,c,p)=&\max \sum_{d\in D} p(d) x_d&\\
&\sum_{d\in D_e}x_d \leq c_e &\quad\text{for } e\in E\\
&0\leq x_d \leq 1 &\quad\text{for } d\in D.
\end{align}

We denote by $\cut(T,D,c)$ the feasible region of the above LP. The integrality gap of this cut-LP, which is denoted by $\alpha_{cut}$, 
is $\max_{T,D,c,p} \frac{\lp_{cut} (T,D,c,p)}{\opt (T,D,c,p)}$. Since this is a maximization problem we clearly have $\alpha_{cut}\geq 1$. A $\beta$-approximation algorithm is a polynomial time algorithm that produces a solution $L\subseteq D$, such that $\opt(T,D,c,p)\leq \beta \sum_{d \in L} p(d)$.

Many special cases of MFT are well studied. For example if $T$ is a path, then the problem can be reduced to a minimum cost circulation problem and the cut-LP is totally unimodular. Furthermore, if $T$ is a star, then the problem can be reduced to a capacitated $b$-matching problem. Therefore, demand flow problem can be solved in polynomial time for both special cases. For general trees the best known result is the $4$-approximation of Chekuri et al. \cite{Chekuri}, which also obtain the upper bound of $4$ on $\alpha_{cut}$. Cheriyan et. al \cite{Cheriyan1999} conjectured that $\alpha_{cut}\leq \frac{3}{2}$. They also provide evidence for their conjecture by proving this upper bound in the case that the optimal solution to cut-LP is half-integral.

There are several results for special demand sets as well. When all the profits are 1 \cite{Garg1997} gave a 2-approximation primal-dual algorithm. Moreover, they gave an exact polynomial-time algorithm for UMFT. However, their result does not prove an upper bound on $\alpha_{cut}$. In fact, the best known lower  bound on  $\alpha_{cut}$ is from an instance of UMFT and has a gap of $\frac{3}{2}$.  We will present this instance later in the paper.

Another interesting special case where we can improve the $4$-approximation algorithm is when $c_e\geq 2$ for all $e\in T$ as shown in \cite{ojas1}. In fact, in this case they provide an LP-based $3$-approximation for the problem which is via iterative rounding (hence $\alpha_{cut}\leq 3$ in this case.).

When restricting general structure for demands, we also have improved results. Suppose that $r$ is the root of tree $T$. If every demand $d=(u,v)$ in $D$ is such that one of $u$ or $v$ is an ancestor of the other (i.e. every demand is a \textit{radial} demand) then the matrix in the cut-LP is totally unimodular, and hence in this case $\alpha_{cut} =1$ \cite{IPbook}. More generally, \cite{ojas1} proved that if for some vertex $r$ of $T$ (as the root of the tree) every demand $d=(u,v)$ in $D$ has the property that $d$ is a radial demand, or the unique $uv$-path in $T$ contains $r$ (\textit{root} demand), then the problem can be solved exactly in polynomial time. Note that, their algorithm does not prove an upper bound on $\alpha_{cut}$. In fact, we use this fact later in the paper to prove one of our results.

In this paper, besides studying MFT we will also study a generalization of MFT which we call the \textbf{multi-state multi-commodity flow in trees (MMFT)}. 
 In this problem we are given: (i) A set of \textit{states} $S$, (ii) a tree network $T=(V,E)$, (iii) a positive integer $c^s_e$ for  $e\in S$ and $e\in E$, i.e. \textit{the capacity of edge $e$ on state $s$}, (iv) a positive integer $c_e$ for $e\in E$, i.e. \textit{total capacity of edge $e$}, (v) a collection of pairs of (distinct) vertices  $D$, called \textit{demands}, (vi) a profit function $p:D\rightarrow \mathbb{Z}^+$, and finally (vii) state function $q:D\rightarrow S$, which determines the state of each demand.

For a subset $L$ of $D$, and state $s\in S$ let $L^s=\{d\in L: q(d)=s\}$. A set $L\subseteq D$ is called \textit{ state-wise routable} on $(T,c,c^s:s\in S)$ if

\begin{equation}
|L_e|\leq c_e \quad \mbox{for all $e\in E$}\end{equation}
and 
\begin{equation}
|L^s_e|\leq c^s_e \quad \mbox{for all $e\in E$, $s\in S$}.\end{equation}

If $|S|=1$, then MMFT is the same as MFT. For the maximum profit state-wise routable subset of demands $L$ we denote $$\opt(T,D,S,c,p,q)= \sum_{d\in L}p(d).$$ We also have the following linear programming relaxation for MMFT, namely \textit{state-cut-LP}. First let us present the natural linear programming relaxation of the multi-state demand flow problem.

\begin{align}
LP_{state-cut}(T,D,S,c,p,q)=\max&\sum_{d\in D} p(d) x_d\label{obj}\\
&\sum_{d\in D_e}x_d \leq c_e \quad\text{for } e\in E \label{overall}\\
&\sum_{d\in D^s_e}x_d \leq c^s_e \quad\text{for } e\in E, s\in S\label{state}\\
&0\leq x_d \leq 1 \quad\;\;\;\text{for } d\in D \label{nonneg}.
\end{align}

Let $\statecut(T,D,S,c,q)$ be the feasible region of the LP above, and $\alpha^{m}_{cut}$ the integrality gap of this the above LP for MMFT for instances with $|S|=m$. In other words $$\alpha^m_{cut} =\max_{T,D,c,p,q } \frac{\lp_{state-cut}(T,D,\{1,\ldots,m\},c,p,q)}{\opt(T,D,\{1,\ldots,m\},c,p,q)}$$

If we restrict $T$ to be a path the state-cut-LP becomes integral since the matrix in the formulation will be totally unimodular (consecutive 1s matrix). When $T$ is a star, the problem reduces to a problem we call the \textbf{Multi-state $b$-matching} problem which we discuss later.

\subsection{Motivation}
Multi-commodity flow problems are intensely studied and have various and important applications \cite{}. The applications arise when the underlying graph network has specific properties such as when the graph is planar, or a simple cycle or a tree \cite{}.

Our main problem of study, MMFT, like most multi-commodity flow problems have various and important applications. Particularly, MMFT is a model for layered networks, such as the Internet. In detail, each level of the tree represents a layer of agents in the network. For example, leaves correspond to users and clients while lower level inner vertices of the tree correspond to local ISPs, and the domain of the network gets larger as we go up the tree. In this model, a demand is a request sent from a client is this network to another. This request can be accepted and routed through this layered network. Each request has a type: video streaming, online gaming, etc (the state of the demand). Also, each ISP and router in the network will have some predefined capacity for each type of request from its clients and also an overall capacity.

Apart from real word applications, MFT and MMFT have very interesting application in other combinatorial optimization problems. For example, MFT is a generalization of $b$-matchings (when the tree is a star) \cite{Chekuri}. In the same way, MMFT is a generalization of a multi-state version of $b$-matching. This generalized $b$-matching problem, which in this paper is called the multi-state $b$-matching problem, has interesting similarities to the recently studied bounded color matching and $b$-matching problem \cite{color-matching0,color-matching1, color-matching2, color-matching3}.
\subsection{Our results}

In this paper we show that the integrality gap of the cut-LP is exactly $\frac{3}{2}$ in the case of UMFT. We provide a $\frac{3}{2}$-approximation algorithms for this case of MFT based on the cut-LP upper bound. Note that the dynamic programming algorithm in \cite{Garg1997} is not LP based. Also the integrality gap for the cut-LP is known to be at least $\frac{3}{2}$.

Next, we prove that MMFT when $T$ is a star can be solved in polynomial time with a reduction to an easy instance of MFT. This result is independently interesting as this case of the problem can be couched as a ``state-wise" $b$-matching problem.

We will also present a $2(|S|+1)$-approximation algorithm for MMFT where $|S|$ is the number of states in the MMFT instance. The approximation algorithm is LP-based and proves that $\alpha^m_{cut}\leq 2(m+1)$, e.g. the integrality gap is at most  $6$ when $|S|=2$. Finally, we show when $|S|=2$, the integrality gap of the same formulation is at least $2$, hence $2\leq \alpha^2_{cut} \leq 6$.

\subsection{Notation and Preliminaries}

In this paper, we sometimes treat subsets of demands or edges as vectors, in which case are referring to the characteristics vector of those subsets. When the instance is clear from the context, instead of saying a subset of demands is routable in $(T,c)$ (or state-wise routable in $(T,c,c^s:s\in S)$), we may say a (state-wise) routable subset of demands in $T$, or a (state-wise) routable subset of demands.

### 2018-11-02 introduction.tex
Initial commit

\section{Introduction}

Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, is a classic NP-hard problem \cite{GJ79}. In fact it is NP-hard in general to determine if there is a feasible solution to an MILP problem \cite{GJ79}. However, intelligent branch-and-bound strategies allow commercial and open-source MIP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems. Modeling combinatorial optimization problems with MILPs also started the very popular area of LP-based approximation algorithms.

Consider the set of point described by a set 
\begin{equation}
S(A,G,b)= \{(x,y)\in \mathbb{Z}^{n}\times \mathbb{R}^p\;:\; Ax+Gy\geq b\}  \label{S}
\end{equation}
and the  linear relaxation of set $S(A,G,b)$,
\begin{equation}
P(A,G,b) = \{(x,y)\in \mathbb{R}^{n+ p}\;:\; Ax+Gy\geq b\}. \label{P}
\end{equation}

To make the notation simpler we use $I=(A,G,b)$, i.e. an instance of the formulation. Then we use $S(I)$ and $P(I)$ to denote $S(A,G,b)$ and $P(A,G,b)$, respectively. Notice that $\min \;\{cx:\; (x,y) \in S(I)\}$ is in fact an MILP problem and $\min \;\{cx:\;(x,y)\in P(I) \}$ is lower bound provided from the LP relaxation. Let $z_{IP}(I,c)$ and $z_{LP}(I,c)$ be the optimal solution to these problems, respectively.

Many researchers (see \cite{sw, vazirani}) have developed polynomial time algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$ for some $C$ which can be a constant number or dependent on some parameter of the MILP, e.g. $O(\log(n))$. However, for many combinatorial optimization problems there is a limit to such techniques. Let $g_I= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$. Parameter $g_I$ depends on set $S(I)$ and the linear constraints in (\ref{S}) and is known as the \textit{integrality gap} of the formulation for instance $I$. It is easy to see, that we cannot hope to find solutions for the MILP with objective values better than $g_I\cdot z_{LP}(I,c)$. More generally we can define the integrality gap for a class of instances $\mathcal{I}$. In this case, the integrality gap for problem $\mathcal{I}$ is
\begin{equation}
g_\mathcal{I} = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}
\end{equation}

For example, in the problem of finding a minimum weight 2-edge-connected multigraph, the gap of the the natural formulation, constraining every cut to be crossed at least twice, is at most $\frac{3}{2}$ \cite{Wolsey1980} and at least $\frac{6}{5}$ \cite{carr-ravi}. Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation. If we have $g_I=1$, $P(I)=\conv(S(I))$ and $P(I)$ is an \textit{integral} polyhedron. There are many interesting examples of such formulations such as spanning tree polytope and the perfect matching polytope \cite{schrijver}. For such problems we know how to write a vector $x\in P(I)$ as convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.

\begin{fact}\label{cara}
	If $g_I=1$, then for $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$. Moreover, we can find such a convex combination in polynomial time.
\end{fact}

	Now assume $1<g<\infty$. Denote by $\dom(P(I))$ be the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$.

	A analogous result to Fact \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}.

\begin{theorem}[Carr, Vempala \cite{CV}] \label{CV}
	Let $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(S(I))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ if and only if $g_I \leq C$.
\end{theorem}

In contrast to Fact \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time. This points to an interesting open question.

\begin{question}\label{question1}
	Assume reasonable complexity assumptions (such as $\UGC$ or $\Pp\neq \NP$). Given instance $I$ with $1<g_I<\infty$ and $(x,y)\in P(I)$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(\conv(S(I)))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_Ix$ in polynomial time?
\end{question}

This seems to be a very hard question. A more specific question is of more interest.

\begin{question}\label{question2}
	Assume reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g_{\mathcal{I}}<\infty$, and $(x,y)\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_{\mathcal{I}}x$ in polynomial time?
\end{question}
Although Question \ref{question2} is wide open, for some problems $\mathcal{I}$ there are polynomial time algorithms. For example, for generalized Steiner forest problem \cite{jain} gave an LP-based 2-approximation algorithm. The gap for this problem is also lower bounded by 2. Same holds for the set covering problem \cite{randomizedrounding}. In fact, for set cover the approximation algorithm achieving the same factor as the integrality gap lower bound, is a \textit{randomized rounding} algorithm. Rhagavan and Thompson \cite{randomizedrounding} showed that this technique acheives provably good approximation for many combinatorial optimization problems.

One key step, in answering Question \ref{question1} and \ref{question2} is being able to find a solution in $S(I)$. In fact, for general $I$ it is NP-hard to even decide if $S(I)$ is empty or not. There are a number of heuristics for this purpose, such as the feasibility pump heuristic \cite{fp1,fp2}. These heuristics are often very effective and fast in practice, however, they can sometimes fail in finding a feasible solution. In addition these algorithms do not provide any bounds on the quality of the solution they find.

\subsection{Our results}

In this paper we study Theorem \ref{CV} and the natural questions that follow from it (Questions \ref{question1} and \ref{question2}).

 We give a general approximation framework for solving $\{0,1\}$-MILPs.  Consider the set of point described by a set 
\begin{equation}
S(I)= \{(x,y)\in \mathbb{R}^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
\end{equation}
and a linear relaxation of set $S$
\begin{equation}
P(I) = \{(x,y)\in \mathbb{R}^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
\end{equation}
For a point $(x,y)\in P(I)$, let $\sup(x,y)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.

\begin{restatable}{theorem}{binaryFDT}
	\label{binaryFDT}
	Assume $1\leq g_I<\infty$. 	
The FDT algorithm (Algorithm \ref{FDTFull}), given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\sup(x^*,y^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$. Moreover, $C\leq g_I^{|\sup(x^*,y^*)|}$.
\end{restatable}

Notice, that the FDT algorithm needs to find feasible solutions to any MILP with finite gap. This can be of independent interest.
\begin{restatable}{theorem}{DomToIP}
	\label{DomToIP}
		Assume $1\leq g_I \leq \infty$. The DomToIP algorithm (Algorithm \ref{domtoIP}) finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
\end{restatable}

In attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem. In this problem we want to find the minimum weight 2-edge-connected multigraph in a graph $G=(V,E)$ with respect to weights $c\in \mathbb{R}^E_{\geq 0}$. For this problem the natural linear programming relaxation is
 \begin{equation}\label{2ECpol}
 \EC(G)= \{x\in \mathbb{R}_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
 We prove the following theorem.

 \begin{restatable}{theorem}{FDTEC}
 	\label{FDT2EC}
 	Let $G=(V,E)$ and $x$ be an extreme point of  $\EC(G)$. The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq O(|V|)$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$. Moreover, $C\leq g_{\EC}^{O(|V|)}$, where $g_{\EC}$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol}) 
 \end{restatable}

Although the bound guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are very large for large problems, we show that in practice, the algorithm works very well providing approximation ratios that are far better than the theoretical bound in the theorem statements. We examine FDT for binary MILPs for problems such as the tree augmentation problem (TAP) and we apply FDT for 2EC on some interesting and ``hard to decompose" points in the linear relaxation.

Finally we give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems. For this purpose assume $P= \{x\in \mathbb{R}^n_{\geq 0}: Ax\geq b\textbf{1}, x \leq b\textbf{1}\}$, $S= P\cap \mathbb{Z}^n$, and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$. Examples of such problems include the 2-edge-connected multigraph problem, the tree augmentation problem, and many others.

\begin{restatable}{theorem}{tightcuts}
	\label{tightcuts}
	 Let $x\in P$, there exists $\theta\in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i = 1$ and $\tilde{x}^i \in S$ for $i=1,\ldots,k$ such that \begin{itemize}
		\item for $\ell\in \{1,\ldots,n\}$, if $x_\ell =0$, then $\tilde{x}^i_\ell=0$ for $i =1,\ldots,k$, i.e. $\tilde{x}^i$ is in the support of $x$,
		\item we have $Cb = C\cdot A_j x \geq A_j (\sum_{i=1}^{k}\theta_i\tilde{x}^i)$, for $j$ such that $A_j x =b$,  
	\end{itemize}
	if and only if $C\geq g$.
\end{restatable}

This means in order to prove an upper bound on the integrality gap of a covering problem, we need to show there is a convex combination of integer feasible points that is ``cheap'' on all tight cuts. Notice that Theorem \ref{CV} requires the certificate convex combination to be ``cheap" on every single variable.

\subsection{Notation and Preliminaries}

### 2018-11-02 old version/old bib.tex
new

% TODO: deal with the issue of no credit after branching up for packing:
% y_0 + y_1 \le x becomes y_0 + lambda_1 \le x
\documentclass[11pt]{article}
\date {}
\textwidth=6.5in
\textheight=9.0in
\oddsidemargin=0.0in
\topmargin=0.0in
\headheight=0.0in
\headsep=0.0in

\usepackage{ifthen}
\usepackage{boxedminipage}
\usepackage{alltt}
%\usepackage{latexsym}
%\usepackage{epsfig}
%\usepackage{graphicx}
\usepackage{color}
\usepackage{url}

% LP environments
% NEEDS \usepackage{ifthen} in the document preamble

\newenvironment{lpconstraintsraw}{%
\displaystyle\begin{array}{ll}
}{%
\end{array}%
}
\newenvironment{lpconstraints}{\begin{center}$\begin{lpconstraintsraw}%
}{\end{lpconstraintsraw}$\end{center}}
\newenvironment{lp}[3]{%
\begin{center}
\begin{tabular}{lrlr}
\ifthenelse{\equal{#1}{}}{}{({#1})} & {#2} & $\displaystyle{#3}$ &\\
                                    & where & $\left\{\begin{lpconstraintsraw}
}{%
\end{lpconstraintsraw}\right.$ &\\
\end{tabular}
\end{center}%
}
\newenvironment{minlp}[2]{\begin{lp}{#1}{minimize}{#2}}{\end{lp}}
\newenvironment{maxlp}[2]{\begin{lp}{#1}{maximize}{#2}}{\end{lp}}

\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}

\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}

\title{Fractional Decomposition Trees: Finding Feasible Solutions to Integer Programs with Bounded Integrality Gap}

\author{
\parbox[t]{6cm}{\centering
Robert Carr\\
\small{{Sandia National Laboratories\\{\tt rdcarr@sandia.gov}}}\\
%\footnotesize{rdcarr@sandia.gov}
}
\parbox[t]{6cm}{\centering
Cynthia Phillips\thanks{
Discrete Algorithms and Math Department, Sandia National Laboratories, Albuquerque, NM, USA.
\texttt{caphill@sandia.gov}.
Sandia is a multipurpose laboratory
operated by Sandia Corporation, a Lockheed-Martin Company, for the
United States Department of Energy under contract DE-AC04-94AL85000.
}\\
\small{{Sandia National Laboratories\\{\tt caphill@sandia.gov}}}\\
%\footnotesize{caphill@sandia.gov}
}
}% end author

\begin{document}
\special{papersize=8.5in,11in}

\maketitle

\thispagestyle{empty}
\setcounter{page}{0}

\begin{abstract}
We present a new algorithm for finding a feasible solution for a
integer program. The algorithm runs in polynomial time and is
guaranteed to find a feasible integer solution provided the
integrality gap is bounded.  The algorithm is based on convex
decomposition of scaled linear-programming relaxations, so in general
it provides a suite of integer solutions.  Because of the relationship
between convex decomposition and integrality gaps, this algorithm
could also be a tool for experimentally evaluating integrality gaps of
integer programming formulations.  We apply the decomposition
procedure to a set of hard-to-decompose instances of the traveling
salesman problem.  Our preliminary computational results offer some
support for the $4/3$ conjecture and show that the FDT algorithm can
decompose fractional solutions close to optimally in practice, at
least for this class of problems.
\end{abstract}

{\bf Keywords:} integer programming, incumbent heuristics, traveling salesman, integrality gaps, approximation algorithms, branch and bound algorithms, polyhedral combinatorics

\newpage

\section{Introduction}

Mixed-integer programming (MIP), the optimization of a linear
objective function subject to linear and integrality constraints, is a
classic NP-hard problem~\cite{GJ79}.  In fact it is NP-hard in general
to determine if there is a feasible solution to a MIP
instance\cite{GJ79}.  However, intelligent branch-and-bound-based
strategies allow commericial and open-source MIP solvers to give exact
solutions (or near-optimal with provable bounds) to many specific
instances of NP-hard combinatorial optimization problems.  Unlike many
NP-hard problems, whose proof of equivalence to SAT involves a
sequence of complicated reductions, expressing an combinatorial
optimization problem as a MIP is usually natural and direct.  In
particular, it is easy to capture (linear) side constraints that
frequently arise in practical applications.  Because of the quality of
modern MIP solvers, the expressive power of MIP, and the availability
of mathematical modeling languages and tools such as AMPL\cite{ampl},
a first choice strategy for finding an optimal solution to a
particular instance of an NP-complete problem is to formulate the
instance as a MIP and try a general-purpose MIP solver.

Though commercial and free solvers are constantly improving, there are
still real-world instances of MIPs for which these solvers do not find
any feasible solution even after days of computation.  Finding a
feasible solution early in the computation can speed branch-and-bound
search by providing a value for pruning search regions and they
provide at least some solutions if applications have a time limit or
if the users must terminate the search early.

In this paper we give a polynomial-time algorithm that is guaranteed
to find a feasible solution for a broad class of integer programming
problems.  Although we cannot provide a meaningful bound on the
approximation quality of this feasible solution, there is considerable
practical benefit for finding any feasible solution for some problems.
Our algorithm is highly parallelizable, so it can make use of excess
processors early in a run.

We consider a binary MIP, which has the following form:
\begin{minlp}{MIP} {c^Tx}
Ax\ge b&\\
x_j \in \{0,1\} & \forall j \in D \subseteq \{1, \ldots, n\}\\
\ell_j \le x_j \le u_j & \forall j \not\in D
\end{minlp}
where $A$ is an arbitrary $m \times n$ matrix, $x$ is an $n$-vector of
variables, and $D$ represents the indices of the variables that must
be binary, taking on only the value $0$ or $1$.  If $D$ is the entire
set of variables, then this is an {\em integer program}
(IP). Expressing all constraints as ``greater than'' inequalities is a
convenience; We can also handle any mix of equalities or inequalities
in the other direction.  We require that the objective function $c$ is
non-negative, that is has at least one strictly positive component,
and that $c_j = 0$ for all $j \not \in D$.  That is, the continuous
variables are helper variables that do not participate in the
objective function.

If we remove the integrality constraints and allow $0 \le x_j \le 1$
for all $j \in D$, the resulting problem is the {\em
linear-programming (LP)} relaxation of the MIP.  Linear programming
problems can be solved in polynomial time~\cite{Khachian79}.  The
feasible region, the set of vectors $x$ that satisfy all the
constraints, forms an $n$-dimensional polytope $F$.  A polytope
specifies a family of MIP problems based on the objective.  Let
MIP$(F, c)$, be the optimal value of a MIP instance for a
specific objective function $c$, and let LP$(F, c)$ be the
optimal value of its LP relaxation.  The {\em integrality gap}
$g_F$ of a family of MIP instances is the largest ratio between
the optimal integer solution and the optimal value of its LP
relaxation.  Specifically:
$$ g_F = \max_c \frac{\mbox{MIP}(F, c)}{\mbox{LP}(F, c)}.$$ We will
denote the integrality gap of a MIP family by $g$ when the polytope is
understood from context. The integrality gap $g$ is {\em bounded} if
this ratio is finite.  Specifically, the optimal LP value is never
zero unless the optimal MIP value is also zero, and whenever the LP
relaxation is feasible, the MIP problem is feasible too.

We present a polynomial-time algorithm that is guaranteed to find a
feasible solution for a MIP instance provided the integrality gap of
its family is bounded and the problem obeys the structural assumptions
on the objective function given above.  For this class of MIPs, the
feasibility question is in ${\cal P}$: just solve the LP relaxation.
So we are not claiming to solve an NP-hard problem.  However, there
are problems in this class, for example scheduling problems that
always have feasible solutions, for which the best commericial solvers
still cannot find feasible solutions.  Given only a matrix
representation, it is difficult to infer underlying combinatorial
structure (such as a variant on a scheduling problem or a routing
problem).  We give the first polynomial-time algorithm that finds
solutions to these problems given only the matrix representation.

Rhagavan and Thompson\cite{RT87} show how to use randomized rounding
to find provably good approximations for covering problems.  Covering
problems fit into the class of instances for which our algorithm is
guaranteed to work (though we do not provide the quality guarantee of
randomized rounding for this case).  There are a number of heuristics
for finding feasible, preferably high-quality, solutions to MIPs such
as the feasibility pump\cite{FGL05}.  Although these can work well in
practice, they can fail to find a feasible solution and also provide
no quality guarantee.

A number of researchers (see
~\cite{BarNoyGNS01,Naor+Schieber:shallow-trees,PhillipsUW2000,Srinivasan+Teo:STOC97},
for example) have developed provably-good approximations to
combinatorial optimization problems expressed as integer programs
using {\em convex decomposition}.  Others have used the decomposition
method to develop bicriteria (pseudo)approximation
algorithms~\cite{BurchCKMPS03} or to prove structural results about
the set of feasible solutions for a combinatorial optimization
problem~\cite{BoydCarr}.

The general decomposition method works as follows. Given an integer
program (IP), let $x^*$ be an optimal solution to the
linear-programming (LP) relaxation.  Find a set of integer solutions
$S_1, S_2, \ldots, S_k$, each feasible for the MIP.  For each $S_i$ for
$i = 1, \ldots, k$, also find a $0 \le \lambda_i \le 1$ such that
$\sum_{i=1}^k \lambda_i = 1$.  These solutions form a convex
decomposition if $\sum_{i=1}^k \lambda_i S_i \le \rho x^*$, for an
appropriate scaling factor $\rho \ge 1.$ In this case, at least one of
the solutions $S_i$ is a $\rho$-approximation to the optimal MIP value.
In fact, it is no more than a factor of $\rho$ greater than the value
of the LP relaxation.  Thus $\rho$ must be at least as large as the
integrality gap of the specific instance.  Carr and
Vempala~\cite{CarrVempala} proved that $\rho$ equal to the integrality
gap is sufficient: the integrality gap is at most $\rho$ if and only
if there exists a convex combination of integer feasible solutions
dominated by $\rho x^*$ where $x^*$ is any feasible solution to the
LP.  In fact, it is sufficient to consider only extreme points for the above
decomposition.

To date, all approximation algorithms based on convex decompositions
have been problem specific, usually involving clever exploitation of
problem structure.  In this paper, we present the {\em fractional
decomposition tree (FDT)} algorithm, which works for integer programs
with bounded integrality gap.  The FDT algorithm grows a tree similar
to the classic branch-and-bound search tree for integer programs.
Each node represents a partial solution with solutions becoming
progressively more integral at each level.  Leaves contain solutions
with integer values for all binary variables that dominate an
integer-feasible solution for the MIP.  We then transform this vector
into a feasible solution.  Unlike a branch-and-bound tree, however,
the fractional decomposition tree has only a polynomial number of
nodes at each level.  The computation requires $O(n_b^2)$
linear-programming solves where $n_b$ is the number of integer
variables that have non-zero values in the LP relaxation.

The FDT algorithm produces a convex decomposition of the fractional
input point.  The scale factor $\rho$ is not guaranteed to be equal to
the integrality gap.  However, it provides an upper bound in the
integrality gap for that instance.  So consistent positive results
that give decompositions with small values of $\rho$ provide good
experimental support for small integrality gaps for specific
formulations.

We applied the FDT algorithm to fundamental extreme points of the
traveling salesman polytope with subtour-elimination constraints.
Our preliminary computation study provides some support for the $4/3$
conjecture and shows that the FDT can decompose with scaling factors
quite close to optimal.

The remainder of the paper is organized as follows.  In
Section~\ref{sec:FDT}, we present the fractional decomposition tree
(FDT) algorithm and argue its correctness.  In section~\ref{sec:tsp},
we discuss the $4/3$ conjecture for the traveling salesman problem
(TSP) and describe a preliminary experiment applying the FDT algorithm
to difficult-to-decompose instances of TSP.  In
section~\ref{sec:future}, we discuss objective function issues in more
detail, consider faster heuristics based on FDT, and describe future
research directions.

\section{The FDT Algorithm}
\label{sec:FDT}
In this section we present the fractional decomposition tree (FDT) algorithm
and argue its correctness.  We also discuss some implementation issues.

We begin by considering the Carr/Vempala result a little more
carefully.  A vector $y$ {\em dominates} a vector $x$ if each
component of $y$ is at least as large as the corresponding component
of $x$.  We require the following definition from~\cite{CarrVempala}: the
{\em dominant} ${\cal D}(Z)$ of an $n$-dimensional polyhedron $Z$ is
the set of points $y \in {\cal R}^n$ that dominate some point $x \in
Z$.  That is
$$ {\cal D} = \{y \in {\cal R}^n | \exists x \in Z: \forall i \in \{1,
\ldots, n\} y_i \ge x_i\}.$$ Consider a problem with LP feasible
region $F$.  The convex hull of the integer points within $F$ is
another convex polytope $Z$ (the integer polytope) with integer
extreme points.  Carr and Vempala proved the following theorem:
\begin{theorem}[\cite{CarrVempala}]
The integrality gap of an LP relaxation $F$ of an integral polyhedron $Z$ in the
positive orthant is the smallest real number g such that for any
extreme point $f \in F$, $gf \in {\cal D}(Z)$.
\label{thm:CV}
\end{theorem}
In other words, if we scale the LP solution by a factor $g$ at least
as large as the integrality gap, this scaled vector will be in the
dominant of the integer polytope $Z$.  Speaking practically, that
means that point $gf$ now dominates a point $z \in Z$.  Any point in
the integer polytope is a convex combination of integer feasible
(extreme-point) solutions, so $gf$ dominates a convex combination of
feasible solutions.

Classical branch and bound for integer programming grows a tree.  The
root of the tree is the original MIP problem.  We begin by solving the
LP relaxation of the MIP to get a lower bound on the optimal MIP
value.  If optimal solution to the LP relaxation is integral where
required, we are done.  That is an optimal solution to the MIP.
Otherwise, we select a binary variable $x_i$ that should be integral,
but is strictly fractional in the LP solution.  We create two
children: one where $x_i$ is forced to be $0$ and one where $x_i$ is
forced to be $1$.  The original LP solution is not feasible in either
child, so we can apply the same procedure to the children.  We prune a
node if the LP relaxation is integral or infeasible or if the lower
bound is worse than a feasible solution we've already found (hence the
value of feasible solutions found early in the search).  The procedure
terminates when there are no more open (unpruned) nodes.  This search
requires exponential time in the worst case.

In the FDT, we grow a tree in a similar way, but the tree represents
the decomposition of a feasible solution for the MIP's LP relaxation.
Each node at level $\ell$ contains a vector $x$ with integer values
for the first $\ell$ variables.  There exists, by construction, a
solution to the LP relaxation that $x$ dominates in the first $\ell$
variables and matches on the remaining variables.  Each leaf contains
a vector $x_l$ that is integral on all integer variables and dominates
an LP solution.  We prove that if the integrality gap is bounded, each
$x_l$ also dominates a feasible solution for the MIP.  We show how to
find this integer feasible solution for each leaf.

\paragraph{Growing the FDT tree}
We grow the FDT tree as follows.  The root of the FDT contains $x^*$,
a feasible fractional solution for the LP relaxation of the MIP,
usually an optimal LP solution.  If $\rho x^*$ dominates a convex
combination of integer-feasible solutions $S^1, \ldots, S^{q}$, for
some scalar $\rho$, then for all $1 \le j \le q$, we have $S^j_i= 0$
if $x^*_i = 0$.  This follows from the definition of the
decomposition: $\rho x^* \ge \sum_j \lambda_j S^j$ where $\lambda_j
\ge 0$ and $\sum_j \lambda_j = 1$. However, it's possible $S^j_i = 0$
for all $j$ even when $x^*_i = 1$, since we only require that the
scaled $x^*$ dominate the combination.  So we will not treat
coincidental non-zero integral values ($1$) as fixed.  We branch only
on variables that are fractional in a partial solution.  The zeros
will remain fixed, but the $1$'s might become fractional and require
branching later.

Consider the set of integer variables that have non-zero values in
$x^*$: $\{x_1, x_2, \ldots, x_{n_b}\}$, ordered arbitrarily. The root
has two children.  The down child contains an LP-feasible solution
$y^{0}$ with variable $x_1 = 0$ and the up child contains an
LP-feasible solution $y^{1}$ with variable $x_1= 1$. The two solutions
are chosen such that a convex combination of $y^{0}$ and $y^{1}$ packs
into a scaled version of $x^*$ with the smallest possible scaling
factor $\rho.$ That is, we have $\lambda_{0} y^{0} + \lambda_{1} y^{1}
\le \rho_{1} x^*.$ where $0 \le \lambda_{0}, \lambda_{1} \le 1$,
$\lambda_{0} + \lambda_{1} = 1$, and $\rho_1$ is as small as possible.

We solve the following linear program to compute the $y^i$.  This LP
accepts a level parameter $\ell$ which specifies which variable to
branch on and a parent vector $x$.  At the root we use LPC$(1,x^*)$

% Someday make a labeled version of the LP macros and use labels!
\begin{maxlp}{LPC($\ell, x$)} {\lambda_0 + \lambda_1}
Az^0\ge b\lambda_0&(1)\\
Az^1\ge b\lambda_1&(2)\\
0 \le z^0 \le \lambda_0&(3)\\
0 \le z^1 \le \lambda_1&(4)\\
z^0_{\ell} = 0; z^1_{\ell} = \lambda_1&(5)\\
z^0 + z^1 \le x&(6)\\
\lambda_0, \lambda_1 \ge 0
\end{maxlp}

We set $y^0 = z^0/\lambda_0$ and $y^1 = z^1/\lambda_1$.  We prove
below that the $y^i$ have the required properties with convex
multipliers $\lambda'_0 = \frac{\lambda_0}{\lambda_0 + \lambda_1}$,
$\lambda'_1 = \frac{\lambda_1}{\lambda_0 + \lambda_1}$, and $\rho =
\frac{1}{\lambda_0 + \lambda_1}$.  A more intuitive mathematical
program to compute the scale factors directly would be nonlinear.

If $\lambda_0 = 0$, then the root has only one child $y^1$, and
similarly if $\lambda_1 = 1$, the root has only the $y^0$ child.  If
the MIP instance has only one feasible solution and the integrality gap
is bounded, the ``tree'' will be a chain leading to the single
feasible solution at the leaf.

If either of the $y_i$ are integral, it is a feasible solution for the
MIP.  If this heuristic is part of a classical branch-and-bound
search, we could report this feasible solution.  If we wish to
continue the decomposition (e.g. to study integrality gaps), then this
node never requires further decomposition; it travels to the next level
of the tree unchanged.

We now decompose the children of the root.  Any descendant of the
$y^0$ (down) child must have $x_1 = 0$ by the argument above
concerning decompositions of $0$-valued components.  However
descendants of the $1$ (up) child are {\em allowed} to have $x_1 = 1$,
but not forced to.  We consider the variable $x_2$ for each of the
level-1 nodes.  If variable $x_2$ is already integer in $y^0$, then
that node passes down to level 2 unchanged.  We use linear program
LPC$(2,y^i)$.  That is, we branch on variable 2 and pack into vector $y^i$.

There is one issue with the $y^1$ (branch up) child. The LPC linear
program does {\em not} fix variable $x_1$ (from the first branching)
to $1$ when further decomposing the $y^1$ (up) child into its children
$y^{10}$ and $y^{11}$.  This produces smaller convex multipliers,
leading to better decompositions and better approximations.  It may
also be required for correctness because, as we mentioned above, the
integer points that $y^1$ dominates in variable $x_1$ may, in fact,
have $x_1 = 0$.  LPC$(2,y^i)$ might return a fractional solution for variable
$x_1$ in one or both of these children.  If so, we reset $x_1 = 1$ for
future decompositions.  Specifically, the value $w^{10}$ and $w^{11}$
stored in the level-2 descendants of the level-1 up child have
$w^{1i}_1 = 1$ (respect the branch) and otherwise have $w^{1i}_j =
y^i_j$.

We continue decomposing the solutions, building the tree breadth first
until all nodes are integral.  For each level of the FDT, the y values
(from the LPC invocations) form a convex decomposition of the root
$x^*$, with convex multipliers equal the the product of the
multipliers on the node-to-leaf path.  Each $w$ value on level $\ell$
is integral for the first $\ell$ values, reflecting the branching
decisions to that point.  Vector $w$ dominates an LP solution that
respects the $0$ branches.

To control the size of the tree, we prune a level if it has more than
$\alpha n_b$ nodes for some constant $\alpha > 1$.  Suppose there are
$k > \alpha n_b$ nodes on some level with partial solutions $y_1, y_2, \ldots
y_k$.  We use the following linear program to prune the level:

\begin{maxlp}{LPP} {\sum_{i=1}^k\lambda_i}
\sum \lambda_i y_i \le x^*&\\
0 \le \lambda_i \le 0 & \forall i=1\ldots k
\end{maxlp}

\noindent where $x^*$ is the original LP relaxation, the solution at the root of
the FDT.  This linear program ``repacks'' all the partial solution and
recomputes a new $\rho = 1/\sum_i \lambda_i.$ We only need to enforce
the packing on the nonzero variables, since binary variables that were
zero in $x^*$ will be zero in all decompositions.  So there are $n_b$
constraints.  Therefore, there can be at most $n_b$ values of
$\lambda_i$ that are basic.  All others will be $0$.  We keep the
solutions corresponding to the nonzero values of $\lambda_i$.  Thus no
level of the FDT has more than $n_b$ nodes.  After expanding all nodes
to leaves, we can run the pruning LP a final time to compute a final
packing with minimum $\rho.$

\paragraph{Finding feasible solutions from the FDT}
Each leaf in the FDT contains a vector $x_l$ that has integer values
for all binary variables.  It dominates an LP solution, but it may not
be LP feasible.  We reduce some of the $1$-valued variables in $x_l$
to produce an integer-feasible solution.  Since the objective function
is non-negative, this also improves the cost of the solution.

Suppose we have a vector $x \in {\cal D}(Z)$ for some integer polytope
$Z$ ($x$ is in the dominant of $Z$), and suppose that $Z$ has an
integer point.  We fix each variable iteratively, starting with $x_1$.
Suppose we have fixed $k \ge 0$ variables so far, yielding a partial
solution $x^{(k)}$.  We run the following linear program
(dominant-to-feasible), parameterized by $k$, to determine the value for $x_{k+1}$:
\begin{minlp}{LPD2F(k)} {y_{k+1}}
Ay\ge b&\\
y_j = x^{(k)}_j & \forall j \le k\\
y_j \le x^{(k)}_j & \forall j \ge k+1\\
y \ge 0
\end{minlp}

This LP finds the minimum value of the $k+1$st component for a solution that
is LP feasible, dominated by $x$, and respects the component decisions we have
made so far.

The procedure DOM2IP, shown in figure~\ref{fig:D2I} uses this LP to
compute a feasible integer solution from a point in the dominant.

\begin{figure}[tbh]
{\footnotesize
\begin{center}
\begin{boxedminipage}{3.2in}
\begin{alltt}
Input: \( x\sb{l} \) from FDT leaf
    \( x\sp{(0)} = x\sb{l} \)
    \( \mbox{for} k := 0 \mbox{to} n\sb{f}-1\)
       let \( x\sp{(k+1)} = x\sp{(k)} \)
       let a = solution to LPD2F(k)
       if a = 0 then \( x\sp{(k+1)}\sb{k+1} = 0 \)
       else \( x\sp{(k+1)}\sb{k+1} = 1 \)
\end{alltt}
\end{boxedminipage}
\end{center}
\caption{The algorithm to convert a vector in the dominant of the integer polytope
into an integer feasible solution.  LPD2F(k) is a linear program that computes the minimum
possible value for the (k+1)st component. \label{fig:D2I}.}
}
\end{figure}

\paragraph{Correctness}
We now show that the FDT algorithm is correct.  First we show that
using the linear program LPC, we correctly decompose the vector $x$ in
a level-$\ell$ FDT node into two child problems $y^0$ and $y^1$ that
respect the $0$ values in vector $x$, enforce the branching on the $\ell$th variable, and pack
into $x$.  Recall we set $y^0 = z^0/\lambda_0$ and $y^1 =
z^1/\lambda_1$, where the $z^i$ are the vectors computed by
LPC$(\ell,x)$.  We require $\lambda_{0} y^{0} + \lambda_{1} y^{1} \le
\rho_{1} x.$ We now show that the vectors $y^i$ have the required
properties with convex multipliers $\lambda'_0 =
\frac{\lambda_0}{\lambda_0 + \lambda_1}$, $\lambda'_1 =
\frac{\lambda_1}{\lambda_0 + \lambda_1}$, and $\rho =
\frac{1}{\lambda_0 + \lambda_1}$.

Because $z^0 = \lambda_0y^0$, Constraints (1) imply that $A(\lambda_0y^0) \ge \lambda_0b$,
or that $Ay^0 \ge b$.  Thus $y^0$ is LP feasible.  Similarly from constraints (2) and the
definition of $y^1$ imply that $y^1$ is LP feasible.  Constraints (3) and (4) imply that
the elements of vectors $y^0$ and $y^1$ are bounded between $0$ and $1$.  Constraints
(5) enforce the branching by setting the value of the $\ell$th variable to appropriate integer
values.  Constraint (6) enforces the decomposition:
\begin{eqnarray*}
z^0 + z^1 & \le & x^*\\
\lambda_0\left(\frac{z^0}{\lambda_0}\right) + \lambda_1\left(\frac{z^1}{\lambda_1}\right) & \le & x^*\\
\lambda_0y^0 + \lambda_1y^1 & \le & x^*\\
\left(\frac{\lambda_0}{\lambda_0 + \lambda_1}\right)y^0 + \left(\frac{\lambda_1}{\lambda_0 + \lambda_1}\right)y^1 & \le & 
       \left(\frac{1}{\lambda_0 + \lambda_1}\right)x^*\\
\lambda'_0 y^0 + \lambda'_1 y^1 & \le & \rho x^*.
\end{eqnarray*}
We have $\lambda'_0 + \lambda'_1 = \frac{\lambda_0}{\lambda_0 + \lambda_1} + \frac{\lambda_1}{\lambda_0 + \lambda_1} = 1$,
and both are nonnegative.

Because LPC is correct, by construction each leaf $l$ contains a
vector $x_l$ that is integral and dominates an LP solution.  We now
prove the correctness of algorithm DOM2IP that converts a vector in
the dominant into a feasible solution for the MIP.  Specifically, we
need to prove that $x_l$ dominates an {\em integer} feasible solution
and that DOM2IP correctly finds such a solution.

We require the following notation.  Let $F$ be the feasible region for the
LP relaxation of the MIP.  Let $K$ be the depth of the FDT tree.  And let
$x^{(k)}$ be the solution after $k$ iterations of the inner loop of algorithm
DOM2IP in figure~\ref{fig:D2I}. For $k=0,1,\ldots, K$, we define:
\begin{displaymath}
\begin{array}{llllll}
LP^{(k)} &:=& \{y \in F & | & y\leq x^{(k)}\mbox{ and 1st $k$ positions 
fixed by DOM2IP}\} \\
IP^{(k)} &:=& \{y\in LP^{(k)} & | & y\in \{0,1\}\mbox{ on binary variables}\}.
\end{array}
\end{displaymath}

The following theorem proves that the DOM2IP procedure preserve integer feasibility
through each iteration:

\begin{theorem}
Let MIP be a binary MIP with integrality gap $g$ and costs only on the
binary variables. Let $x^*$ be a point that is 0-1 on the binary
variables MIP and dominates a solution of an LP relaxation of MIP.
Without loss of generality, let the first $K>0$ values of $x^*$ be
integer variables that are at $1$ and the rest integer variables at
$0$ or continuous variables.  Let $x^{(0)},x^{(1)},\ldots,x^{(K)}$ be
the sequence of increasingly-integral solutions from algorithm DOM2IP
and $IP^{(0)},IP^{(1)},\ldots, IP^{(K)}$ be the MIP problem constrained
to respect these decisions.  Then,
$$\forall k\in \{0,\ldots,K\}\quad IP^{(k)}\neq \emptyset.$$
\end{theorem}
{\bf Proof: } In this proof, when we make statements about dominance
or state inequalities between vectors, we ignore continuous variables.
We prove this by induction on $k$.  We start with $x^{(0)}:=x_l$ which
dominates a solution of the LP relaxation when $x_l$ is a leaf
obtained from the FDT algorithm or otherwise satisfies the conditions
of this theorem.

For $k=0$, we have $LP^{0}\neq \emptyset$ and a finite integrality gap
$g$ for the LP relaxation.  Thus, by Theorem~\ref{thm:CV}, $IP^{0}\neq
\emptyset$.

Assume the theorem holds for all values up to an arbitrary $k<K$.
The problem LPD2F(k) can be interpreted as the following LP:
\begin{displaymath}
\begin{array}{llllll}
\mbox{minimize}& y_{k+1} \\
\mbox{subject to}& y\in LP^{(k)}.
\end{array}
\end{displaymath}
This LP has a feasible solution because $IP^{(k)} \neq 0$, by the induction
hypothesis and any solution to $IP^{(k)}$ satisfies the constraints of the LP.

Suppose first that the minimizer $y^*$ achieves $y^*_{k+1}=0$.  Then 
DOM2IP fixes $x^{(k+1)}_{k+1}$ to $0$ and we have $y^*\in LP^{(k+1)}$.  
Since $y^*\leq x^{(k+1)}$, $y^*\in F$, and the integrality gap of the MIP is finite, 
by Theorem~\ref{thm:CV},  we have
$$S_{k+1}:=\{y\in IPfeas\, |\, y\leq x^{(k+1)}\}\neq \emptyset,$$ 
where $IPfeas$ is the set of integer feasible solutions.  
Let $\hat{y}\in S_{k+1}$.  We show by contradiction that $\hat{y}\in 
IP^{(k+1)}$.  Suppose  $\hat{y}\not \in IP^{(k+1)}$.  Then there is a 
smallest $1\leq l\leq k$ such that $\hat{y}_l=0$ but $x^{(k+1)}_l=1$.  
But then $\hat{y}\leq x^{(k+1)}\leq x^{(l-1)}$.  The latter inequality
follows from the nature of DOM2IP.  Because it only sets $1$ values to $0$,
the vector produced at each iteration is dominated by the vector from the
previous iteration.  Furthermore, we have $\hat{y}\in F$, and 
$\hat{y}$ respects how variables $1,\ldots,l-1$ are fixed by DOM2IP.  
Thus, $\hat{y}\in LP^{(l-1)}$.  But, $\hat{y}_l=0$ contradicting the 
fact that the minimum to the linear program that fixed variable $l$ was 
greater than $0$.  Thus, $IP^{(k+1)}\neq \emptyset$ in this case.

Now suppose that the minimizer $y^*$ has $y^*_{k+1}>0$.  Then $x^{(k+1)}_
{k+1}$ is fixed to $1$.  Now, $\forall z\in IP^{(k)}\quad z\in LP^{(k)}$ 
and hence $z_{k+1}>0$, and therefore $z_{k+1}=1$.  So, $z \in LP^{(k+1)}$ 
and $z$ is integer.  Thus, $z\in IP^{(k+1)}$, showing  
$IP^{(k+1)}\neq \emptyset$ in this case too.  \hfill \framebox

\begin{corollary}
Running the DOM2IP algorithm starting from a leaf of the FDT tree will produce
a feasible solution for any MIP with finite integrality gap.
\end{corollary}

By straight averaging, one of the solutions we compute will have an
approximation ratio of at most $\rho$, where $\rho$ is the value
returned after the final packing.  The final $\rho$ value (expansion
factor) will not generally be equal to the integrality gap $\rho_g$ of
the instance.  Each individual LCP instance will have $\rho \le
\rho_g$.  This is because each LCP instance is decomposing a solution
that dominates an LP-feasible solution by construction.  Therefore a
decomposition exists with expansion factor at most $\rho_g$.  At level
$i$, the appropriate convex combination of integer feasible solutions
with appropriate values for the first $i-1$ levels and with $i$th
variable equal to $0$ is a feasible value of $y^0$. Similarly the
convex combination of integer feasible solutions with $i$ variable
equal to $1$ is feasible for $y^1$.  However, the error can compound
at each level.  In the worst case, one could imagine a final scaling
value of $\rho_g^{n_b}$.  The pruning LPs (LPP) reduce the value of
$\rho$ and in practice do not expect this worst-case growth in $\rho$.
If $\rho_g$ is bounded, then even this worst case bound is finite and
the FDT will find an integer feasible solution.

\section{Preliminary Computational Experience with the TSP}
\label{sec:tsp}

The traveling salesman problem (TSP) is one of the most studied
combinatorial optimization problems, both in terms of approximation
algorithms and heuristics and its polyhedral structure.  Given a
complete undirected graph with edge weights satisfying the triangle
inequality, we wish to find a tour of minimum total edge length that
visits each node in the graph.

If an IP formulation for TSP only enforces that each node have degree
at least 2, the integer solutions might have multiple disjoint
subtours that together cover all the nodes.  The {\em
subtour-elimination constraints} require that for each subset $S$ of
the nodes, there are at least two edges between $S$ and $\bar{S}$.
There are an exponential number of such constraints, but one can
enforce them via separation using a minimum cut algorithm.  For our
example, we enforce the subtour elimination constraints using Carr
et.\ al.'s compact representation\cite{CarrKLNP07}.

Shmoys and Williamson~\cite{ShmoysWilliamson} has used the
Christofides upper bound~\cite{Christofides76} to prove that the
integrality gap of a TSP formulation with the subtour-elimination
constraints is at most $3/2$.  There is an example showing the
integrality gap is at least $4/3$. Wolsey and later Goemans
conjectured that the actual gap is $4/3$.  This is {\em $4/3$
conjecture}.  Boyd and Labont\'{e}~\cite{BoydLabonte} experimentally
proved this conjecture for problems with up to $10$ vertices.  Boyd
and Carr~\cite{BoydCarr} conjectured that for all extreme points $x^*$
of an IP formulation with the subtour constraints $\frac{4}{3}x^* \ge
\sum_i \lambda_i x^i,$ where the $\lambda_i$ form a convex
decomposition and the $x^i$ are {\em Eulerian} graphs.  That means the
$x^i$ are subgraphs of the complete graph with edge weights in
$\{0,1,2\}$ such that the sum of the weights of the edges adjacent to
any node is even.  Boyd and Carr~\cite{BoydCarr} together with Carr
and Vempala~\cite{CarrVempala} proved this statement is equivalent to
the $4/3$ conjecture.

Boyd, Carr, and Ravi~\cite{BoydCarr,CarrRavi} proved that if the $4/3$
conjecture holds for {\em fundamental extreme points}, then it holds
for all extreme points.  A fundamental extreme point $x^*$ has
non-zero values on edge variables with the following structure,
illustrated in Figure~\ref{fig:fundExtreme}.  There are an even number
of nodes.  All nodes on a single cycle.  Values in $x^*$ for edges on
the cycle alternate between $0 \le \sigma \le 1$ and $0 \le 1 - \sigma
\le 1$.  Each node also has precisely one chord across the cycle with
$x^*$ value equal to $1$.  Technically there are arbitrarily-many
degree-$2$ vertices on each chord.  This is necessary to force
worst-case behavior.  We need not explicitly model these vertices.  We
simply note that in any decomposition, the values for variables that
represent chord edges must be either $1$ or $2$.

\begin{figure}
\begin{center}
\input{fundExtreme.latex}
\end{center}
\caption{A fundamental extreme point with 8 nodes along the cycle.}
\label{fig:fundExtreme}
\end{figure}

We customized the FDT algorithm for this TSP problem.  Specifically,
we considered the class of general integer variables with only the
values $1$ and $2$.  The tree is still binary, but we must branch on
all of these general integer variables even if they are exactly equal
to $1$ in the fractional solution $x^*$.  We implemented this in the
ampl running on a linux workstation with 2 3.2Ghz Pentium 4 processors
and 512Kb of cache.  We used the PICO solver as the back end to ampl,
calling the CLP linear programming solver from PICO.

We generated 3600 instances of fundamental extreme points with 20
vertices on the cycle.  This is a small instance, but is still
relevant for the study of the $4/3$ conjecture because it represents
significantly larger TSP graphs.  We generated chords greedily at
random, throwing out instances that did not have the appropriate chord
structure (e.g. when the last edge was an edge on the cycle).  This
does not uniformly sample from among all fundamental extreme points.
One can use a minimum cut algorithm to compute the optimal value for
$\sigma$, and to throw out instances that are infeasible because the
global (fractional) minimum cut is less than 2.  However, for this
preliminary study, we simply set $\sigma = 0.5$.  This adds a degree
of freedom compared to using true extreme points and therefore may
make the decomposition somewhat easier.  With no optimization, other
than using the strong compact formulation, the instances solved in
about 11 seconds.

Of the 3600 instances, 56 were invalid TSP relaxations.  Of the
remaining 3544 instances, 2032 or 57\% had a final $\rho \le 4/3$.  Of
these $929$ were exactly $4/3$ and remaining 1103 were superoptimal
packings with respect to the true integrality gap for the problem
family.  For example, this will happen if the FDT algorithm finds an
optimal solution to the TSP problem.  Of the 3544 valid instances, 178
or 5\% had $4/3 < \rho \le 3/2$.  Finally, 1334 or 38\% had $\rho >
3/2$.  In this case, the final packing scaling factor was larger than
an upper bound on the true integrality gap.  However, the worst-case
instance had $\rho = 2$.  Thus although the theoretical bound on FDT's
performance for this case was approximately $(4/3)^{30}$, it actually
performed at or near optimal in all cases.

\section{Discussion}
\label{sec:future}

TODO: We can get a feasible solution for a problem with bounded integrality gap by
just applying the DOM2IP algorithm.  But starting with solutions from the FDT leaves
will be better in general.

In this section we consider variations on the algorithm, heuristic versions that
may be faster (but may fail to find a feasible solution), implementation issues,
and future directions.

Though it is easier conceptually to have each level of the FDT correspond to a
single variable, the algorithm also works if at each level, nodes branch on
any fractional variable.  Because unfixed $1$-valued variables can become fractional,
one must generally make multiple passes over the variables before the decomposed solutions
become integral.  All nodes at each level have the same number of branches, and therefore
we make progress at each level.

We can extend the method to general integer variables, provided the number
of values for each general integer variable is finite.  Instead of creating
two children, we create $c$ children when branching on an integer variable
with $c$ possible values.  For most reasonable IP models, $c$ will be a small
constant for all general integer variables.

This algorithm works for MIPs that have continuous variables contributing to the
objective function when these variables are always binary at extreme points of the
integer polytope.  For example, for the p-median integer program~\cite{MF90}, there are binary
decision variables representing the location of facilities and continuous (implied
binary) variables representing facility assignments to customers.  Only the
continuous (effectively binary) variables contribute to the objective function.

If one considers families of MIPs, such as the p-median problem, where some binary
variables never contribute to the objective function, then the quality of the LPC
decompositions depends only upon the integrality gap $g$ that comes from considering
only objective functions that are always $0$ on these non-contributing variables.
We require that the complementary gap $g'$, where the objective function is non-zero
only on non-contributing variables is finite.  Regardless of how large $g'$ is, it
has no effect on the performance of LPC.

If we force the upward branches in the LPC linear program, then we can use the
results of that LP directly in the FDT nodes.  These vectors are always LP feasible
and we need not go through the DOM2IP computation to move a leaf to the LP feasible
region.  This worked quite well for the TSP example we describe here.  However, we
cannot yet prove that this variant will always give a feasible solution.  It's possible
we may prune away all integer solutions.

If one would like a single feasible solution as quickly as possible,
one can dive on a single path in the FDT.  Heuristically, one can
initially travel down the child with highest value of $\lambda _i$, or
one can chose randomly based on the values of $\lambda _i$.  This dive is
not guaranteed to find a feasible solution.  However, particularly in
a parallel computing environment, this might find a feasible solution
much faster ($O(n_b)$ LP solves) than the time required to run the whole FDT algorithm.

We need not actually grow a tree, maintaing parent/child links,
though there may be some value to that if we are doing multiple dives.
When computing a full decomposition, we can keep the tree nodes in a
queue, stored with their level.  We take the first node in the queue,
expand it, and put the children back at the end of the queue if
appropriate.  We can detect a change in levels when the node leaving
the queue has a higher level.  At that point, we can alter the working
LPC, putting in the new bounds for constraints (5).  Otherwise, we
need only alter the righthand side of constraints (6).  We report any
integer solutions as possible incumbents, but keep them for the
pruning phase.

\iffalse
The PICO integer programming solver computes gradients (LP bound
movement per unit variable up or down change) for all integer
variables with fractional values in $x^*$.  In practice, it may be
good to order the fractional variables by gradient.
\fi

Given the speed of unoptimized versions of this problem run in ampl,
we expect more carefully crafted C++ versions run from within PICO
will allow us to investigate significantly larger TSP instances.
Computing the optimal $\sigma$ values is also an obvious way to make
the TSP results more compelling.  We are investigating ways to generate
fundamental extreme points uniformly at random.  We can also consider
ultra fundamental extreme points~\cite{CarrVempala}, which are even
harder to decompose than fundamental extreme points.

Given the computational cost of running FDT, we expect general MIP
solvers will use it only on classes of problems for which faster
heuristics consistently fail.  However, for applications that require
a feasible solution, the FDT algorithm guarantees a polynomial-time
solution for the broadest class of MIPs to date.

\paragraph{Acknowledgements}  The authors are grateful to Jonathan Eckstein and Jeff
Linderoth for helpful discussions.  We thank David Gay for his help with ampl runs.
\bibliographystyle{plain}
\bibliography{FDT}

\end{document}

### 2018-11-02 introduction.tex
color-code commenting enabled

@@
 \section{Introduction}
-
 Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, is a classic NP-hard problem \cite{GJ79}.

### 2018-11-12 IPCO format/FDT.tex
ipco format added

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%

\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{FDT\thanks{Supported by organization x.}}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Robert Carr\inst{1}\orcidID{} \and
Arash Haddadan\inst{2}\orcidID{} \and
Cynthia Phillips\inst{3}\orcidID{}}
%
\authorrunning{Carr et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of New Mexico, Albuquerque NM 87131, USA\\
\email{bobcarr@unm.}\\   \and
Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
\email{ahaddada@cmu.edu}\and
Sandia National Laboratories, Albuquerque, NM 87185, USA\\
\email{caphill@sandia.gov}}
%
\maketitle              % typeset the header of the con	tribution
%
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{First keyword  \and Second keyword \and Another keyword.}
\end{abstract}
%
%
%

\section{Introduction}
Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, is a classic NP-hard problem \cite{GJ79}. In fact it is NP-hard in general to determine if there is a feasible solution to an MILP problem \cite{GJ79}. However, intelligent branch-and-bound strategies allow commercial and open-source MIP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems. Modeling combinatorial optimization problems with MILPs also started the very popular area of LP-based approximation algorithms.

Consider the set of point described by a set 
\begin{equation}
S(A,G,b)= \{(x,y)\in \bbbz^{n}\times \bbbr^p\;:\; Ax+Gy\geq b\}  \label{S}
\end{equation}
and the  linear relaxation of set $S(A,G,b)$,
\begin{equation}
P(A,G,b) = \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b\}. \label{P}
\end{equation}

To make the notation simpler we use $I=(A,G,b)$, i.e. an instance of the formulation. Then we use $S(I)$ and $P(I)$ to denote $S(A,G,b)$ and $P(A,G,b)$, respectively. Notice that $\min \;\{cx:\; (x,y) \in S(I)\}$ is in fact an MILP problem and $\min \;\{cx:\;(x,y)\in P(I) \}$ is lower bound provided from the LP relaxation. Let $z_{IP}(I,c)$ and $z_{LP}(I,c)$ be the optimal solution to these problems, respectively.

Many researchers (see \cite{sw, vazirani}) have developed polynomial time algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$ for some $C$ which can be a constant number or dependent on some parameter of the MILP, e.g. $O(\log(n))$. However, for many combinatorial optimization problems there is a limit to such techniques. Let $g_I= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$. Parameter $g_I$ depends on set $S(I)$ and the linear constraints in (\ref{S}) and is known as the \textit{integrality gap} of the formulation for instance $I$. It is easy to see, that we cannot hope to find solutions for the MILP with objective values better than $g_I\cdot z_{LP}(I,c)$. More generally we can define the integrality gap for a class of instances $\mathcal{I}$. In this case, the integrality gap for problem $\mathcal{I}$ is
\begin{equation}
g_\mathcal{I} = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}
\end{equation}

For example, in the problem of finding a minimum weight 2-edge-connected multigraph, the gap of the the natural formulation, constraining every cut to be crossed at least twice, is at most $\frac{3}{2}$ \cite{Wolsey1980} and at least $\frac{6}{5}$ \cite{carr-ravi}. Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation. If we have $g_I=1$, $P(I)=\conv(S(I))$ and $P(I)$ is an \textit{integral} polyhedron. There are many interesting examples of such formulations such as spanning tree polytope and the perfect matching polytope \cite{schrijver}. For such problems we know how to write a vector $x\in P(I)$ as convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.

\begin{proposition}\label{cara}
	If $g_I=1$, then for $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$. Moreover, we can find such a convex combination in polynomial time.
\end{proposition}

Now assume $1<g<\infty$. Denote by $\dom(P(I))$ be the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$.

A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}.

\begin{theorem}[Carr, Vempala \cite{CV}] \label{CV}
	Let $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(S(I))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ if and only if $g_I \leq C$.
\end{theorem}

In contrast to Fact \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time. This points to an interesting open question.

\begin{question}\label{question1}
	Assume reasonable complexity assumptions (such as UGC or $\textrm{P}\neq \textrm{NP}$). Given instance $I$ with $1<g_I<\infty$ and $(x,y)\in P(I)$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(\conv(S(I)))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_Ix$ in polynomial time?
\end{question}

This seems to be a very hard question. A more specific question is of more interest.

\begin{question}\label{question2}
	Assume reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g_{\mathcal{I}}<\infty$, and $(x,y)\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_{\mathcal{I}}x$ in polynomial time?
\end{question}
Although Question \ref{question2} is wide open, for some problems $\mathcal{I}$ there are polynomial time algorithms. For example, for generalized Steiner forest problem \cite{jain} gave an LP-based 2-approximation algorithm. The gap for this problem is also lower bounded by 2. Same holds for the set covering problem \cite{randomizedrounding}. In fact, for set cover the approximation algorithm achieving the same factor as the integrality gap lower bound, is a \textit{randomized rounding} algorithm. Rhagavan and Thompson \cite{randomizedrounding} showed that this technique acheives provably good approximation for many combinatorial optimization problems.

One key step, in answering Question \ref{question1} and \ref{question2} is being able to find a solution in $S(I)$. In fact, for general $I$ it is NP-hard to even decide if $S(I)$ is empty or not. There are a number of heuristics for this purpose, such as the feasibility pump heuristic \cite{fp1,fp2}. These heuristics are often very effective and fast in practice, however, they can sometimes fail in finding a feasible solution. In addition these algorithms do not provide any bounds on the quality of the solution they find.

\subsection{Our results}

In this paper we study Theorem \ref{CV} and the natural questions that follow from it (Questions \ref{question1} and \ref{question2}).

We give a general approximation framework for solving $\{0,1\}$-MILPs.  Consider the set of point described by a set 
\begin{equation}
S(I)= \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
\end{equation}
and a linear relaxation of set $S$
\begin{equation}
P(I) = \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
\end{equation}
For a point $(x,y)\in P(I)$, let $\sup(x,y)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.

\begin{restatable}{theorem}{binaryFDT}
	\label{binaryFDT}
	Assume $1\leq g_I<\infty$. 	
	The FDT algorithm (Algorithm \ref{FDTFull}), given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\sup(x^*,y^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$. Moreover, $C\leq g_I^{|\sup(x^*,y^*)|}$.
\end{restatable}

Notice, that the FDT algorithm needs to find feasible solutions to any MILP with finite gap. This can be of independent interest.
\begin{restatable}{theorem}{DomToIP}
	\label{DomToIP}
	Assume $1\leq g_I \leq \infty$. The DomToIP algorithm (Algorithm \ref{domtoIP}) finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
\end{restatable}

In attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem. In this problem we want to find the minimum weight 2-edge-connected multigraph in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$. For this problem the natural linear programming relaxation is
\begin{equation}\label{2ECpol}
\EC(G)= \{x\in \bbbr_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
We prove the following theorem.

\begin{restatable}{theorem}{FDTEC}
	\label{FDT2EC}
	Let $G=(V,E)$ and $x$ be an extreme point of  $\EC(G)$. The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq O(|V|)$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$. Moreover, $C\leq g_{\EC}^{O(|V|)}$, where $g_{\EC}$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol}) 
\end{restatable}

Although the bound guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are very large for large problems, we show that in practice, the algorithm works very well providing approximation ratios that are far better than the theoretical bound in the theorem statements. We examine FDT for binary MILPs for problems such as the tree augmentation problem (TAP) and we apply FDT for 2EC on some interesting and ``hard to decompose" points in the linear relaxation.

Finally we give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems. For this purpose assume $P= \{x\in \bbbr^n_{\geq 0}: Ax\geq b\textbf{1}, x \leq b\textbf{1}\}$, $S= P\cap \bbbz^n$, and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$. Examples of such problems include the 2-edge-connected multigraph problem, the tree augmentation problem, and many others.

\begin{restatable}{theorem}{tightcuts}
	\label{tightcuts}
	Let $x\in P$, there exists $\theta\in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i = 1$ and $\tilde{x}^i \in S$ for $i=1,\ldots,k$ such that \begin{itemize}
		\item for $\ell\in \{1,\ldots,n\}$, if $x_\ell =0$, then $\tilde{x}^i_\ell=0$ for $i =1,\ldots,k$, i.e. $\tilde{x}^i$ is in the support of $x$,
		\item we have $Cb = C\cdot A_j x \geq A_j (\sum_{i=1}^{k}\theta_i\tilde{x}^i)$, for $j$ such that $A_j x =b$,  
	\end{itemize}
	if and only if $C\geq g$.
\end{restatable}

This means in order to prove an upper bound on the integrality gap of a covering problem, we need to show there is a convex combination of integer feasible points that is ``cheap'' on all tight cuts. Notice that Theorem \ref{CV} requires the certificate convex combination to be ``cheap" on every single variable.

\subsection{Notation and Preliminaries}

\section{FDT on binary MIPs}
\label{binaryfdt}

In this section we present the fractional decomposition tree (FDT) algorithm and prove its correctness.

Consider a formulation instance $I=(A,G,b)$, set 
\begin{equation}
S(I)= \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
\end{equation}
and its linear relaxation
\begin{equation}
P(I) = \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
\end{equation}
Also assume we are given a point $(x^*,y^*)\in P(I)$. For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$. In this section, we prove the following theorem.

\binaryFDT*

One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{DomToIP} that we will also prove in this section.

Although the theoretical worst-case upper bound on $C$ in the statement of Theorem \ref{binaryFDT} can be very large, we will show that in practice $C$ can be really small and hence FDT can provide good LP-based approximation algorithms in many cases. We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.  In the remainder of this section we explain the FDT algorithm and prove Theorem \ref{binaryFDT}. For simplicity in the notations we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively. Let $t=|\sup(x^*,y^*)|$. We assume without loss of generality that $\sup(x^*,y^*)= \{1,\ldots,t\}$.

We begin with the following lemmas that show how the FDT algorithm branches on a variable.
\begin{lemma}\label{LPClemma}
	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vector $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that
	\begin{itemize}
		\item[(i)] $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$,
		\item[(ii)] $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$, 
		\item[(iii)] $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$,
		\item[(iv)] $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
	\end{itemize}
\end{lemma}

\begin{proof}[Proof of Lemma \ref{LPClemma}]

	Consider the following linear programing which we denote by $\LPC(\ell,x',y')$. The variables of $\LPC(\ell,x',y')$ are $\gamma_0,\gamma_1$ and $(x^0,y^0)$ and $(x^1,y^1)$. 
	\begin{align}
		\LPC(\ell,x',y')\quad\quad& \max\quad \;\lambda_0+\lambda_1\\
		&\;\text{s.t.} \quad Ax^j + Gy^j\geq b\lambda_j & \mbox{ for $j=0,1$} \label{feasibility}\\
		&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq \lambda_j &\mbox{ for $j=0,1$}\label{bound}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^0_\ell = 0,\; x^1_\ell =\lambda_1\label{branchcoordinate}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1 \leq x'\label{packing}\\
		&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1 \geq 0
	\end{align}

	Let $(x^0,y^0),(x^1,y^1)$, and $\gamma_0,\gamma_1$ be an optimal solution solution to the LP above. Let $(\hat{x}^0,\hat{y}^0) = (\frac{x^0}{\gamma_0},\frac{y^0}{\gamma_0})$, $(\hat{x}^1,\hat{y}^1) = (\frac{x^1}{\gamma_1},\frac{y^1}{\gamma_1})$. Observe that  (ii), (iii), (iv) are satisfied with this choice. In order to show that (i) is also satisfied we prove the following claim.

	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1\geq \frac{1}{g}$.
	\end{claim}
	\begin{proof}
		We show that there is a feasible solution that achieves the objective value of $\frac{1}{g}$. By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $(\tilde{x}^i,\tilde{y}^i)\in S$ for $i=1,\ldots,k$ such that 
		$\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$.

		\begin{equation}\label{splitting}
		x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}
		\end{equation}
		For $j=0,1$, let $(x^j,y^j) = \sum_{i\in [k]:\tilde{x}^i_\ell=j} \frac{\theta_i}{g}(\tilde{x}^i,\tilde{y}^i)$. Also let $\lambda_0=\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g}$ and $\lambda_1 = \sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g}$. Note that $\lambda_0+\lambda_1 = \frac{1}{g}$. Constraint \ref{packing} is satisfied by Inequality \ref{splitting}. Also, for $j=0,1$ we have
		\begin{equation}
		Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \leq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
		\end{equation}
		Hence, Constraints \ref{feasibility} holds. Constraint \ref{branchcoordinate} also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$. The rest of the constraints trivially hold. 
	\end{proof}
	This concludes the proof.	
\end{proof}

We now show if $x'$ in the statement of of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
\begin{lemma}\label{round-up}
	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vector $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that
	\begin{itemize}
		\item[(i)] $\gamma_0 + \gamma_1  \geq\frac{ 1}{g}$,
		\item[(ii)] $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, 
		\item[(iii)] $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$,
		\item[(iv)] $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
		x'$,
		\item[(v)] $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
	\end{itemize}
\end{lemma} 
\begin{proof}
	By Lemma \ref{LPClemma} we can find $(\bar{x}^0,\bar{y}^0)$, $(\bar{x}^1,\bar{y}^1)$, $\gamma_0$ and $\gamma_1$ that satisfy (i), (ii), (iii), and (iv). We define $\hat{x}^0$ and $\hat{x}^1$ as follows. For $i=0,1$, for $j=1,\ldots,\ell-1$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,n$ let $\hat{x}^i_j = \bar{x}^i_j$. We now show that $(\hat{x}^0,\bar{y}^0)$, $(\hat{x}^1,\bar{y}^1)$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions. Note that conditions (i), (ii), (iii), and (v) are trivially satisfied. Thus we only need to show (iv) holds. We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$. If $j=\ell,\ldots,n$, then this clearly holds. Hence, assume $j\leq \ell-1$. By the property of $x'$ we have $x'_j\in \{0,1\}$. If $x'_j= 0$, then by Constraint \ref{packing} we have $\bar{x}^0_j = \bar{x}^1_j=0$. Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds. Otherwise if $x'_j = 1$, then we have
	\begin{equation*}\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.\end{equation*}
	Therefore (v) holds.
\end{proof}
The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs. Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$. The solutions contained in the nodes of the tree become progressively more integral at each level. Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$. We will later see how we can turn these into points in $S$.

Let us define the FDT algorithm more formally. The algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm. The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree. The points in the leaves of the FDT tree, or $L_t$, are points in $\dom(P)$ and are integral for all integer variables.

\begin{lemma}\label{prune}
	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $(x,y)\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$. 
	\begin{itemize}
		\item[a.] If $(x,y)\in L_i$, then $x_j \in \{0,1\}$ for $j=1,\ldots,i$, i.e. the first $i$ coordinates of a solution in level $i$ are integral. 
		\item[b.] $\sum_{[(x,y),\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$.
		\item[c.] $\sum_{[(x,y),\lambda]\in L_i}\lambda x \leq x^*$.
		\item[d.] $|L_i|\leq t$.
	\end{itemize}
\end{lemma}
\begin{proof}
	We prove this lemma using induction but one can clearly see how to turn this proof into a polynomial time algorithm. Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $(x^*,y^*)$ and multiplier 1. It is easy to check all the requirements in the lemma are satisfied for this choice.

	Suppose by induction that we have constructed sets $L_0,\ldots,L_i$. Let the solutions in $L_i$ be $(x^j,y^j)$ for $j=1,\ldots,k$ and $\lambda_j$ be their multipliers, respectively. For each $j\in 1,\ldots,k$ by Lemma \ref{round-up} (setting $(x',y')= (x^j,y^j)$ and $\ell = i$) we can find $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and $\lambda^0_j$, $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}. Define $L'$ to be the set of node with solutions $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and multipliers  $\lambda_j\lambda^0_j$, $\lambda_j\lambda^1_j$, respectively, for $j=1,\ldots,k$.

	Notice that for each $j\in \{1,\ldots,k\}$ by property (v) in Lemma \ref{round-up} we have $x_\ell^{j0}, x_\ell^{j1}\in \{0,1\}$ for $\ell = 0,\ldots,i+1$. We also have
	\begin{align*}
		\sum_{[(x,y),\lambda]\in L'} \lambda & =  \sum_{j=1}^{k} \lambda_j\lambda^0_j+\lambda_j\lambda^1_j&\\
		& \geq \sum_{j=1}^{k} \frac{\lambda_j}{ g} & (\text{By property (i) in Lemma \ref{round-up}})\\
		& \geq \frac{1}{g} \sum_{[(x,y),\lambda]\in L_i}\lambda&\\
		& \geq \frac{1}{g^{i+1}}.&(\text{By induction hypothesis})	 
	\end{align*} 
	Also 
	\begin{align*}
		\sum_{[(x,y),\lambda]\in L'}\lambda x & =  \sum_{j=1}^{k} \lambda_j\big(\lambda^0_jx^{j0}+\lambda^1_jx^{j1}\big)&\\ 
		& \leq \sum_{j=1}^{k} \lambda_j x^j  & (\text{By property (iv) in Lemma \ref{round-up}})\\
		& \leq \sum_{[(x,y),\lambda]\in L_i}\lambda x&\\
		& \leq x^*.&(\text{By induction hypothesis})	 
	\end{align*} 
	Set $L'$ seems like a suitable candidate for $L_{i+1}$, however we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$. We call the following linear programming $\prun(L')$. Let $L' = \{[(x^1,y^1),\lambda_1],\ldots,[(x^k,y^k),\lambda_k]\}$. The variables of $\prun(L')$ is a scalar variable $\theta_j$ for each node $j$ in $L'$.

	\begin{align}
		\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{k} \theta_j\\
		&\;\text{s.t.} \quad \;\;\sum_{j=1}^{k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
		&\;{\color{white}{\text{s.t.}} }\quad  \;\quad\quad\theta \geq 0\label{nonneg}
	\end{align}

	Notice that $\theta = \lambda$ is in fact a feasible solution to $\prun(L')$. Let $\theta^*$ be the optimal vertex point solution to this LP. Since the problem is in $\bbbr^k$,  $\theta^*$ has to satisfy $k$ linearly independent constraints at equality. However, there are only $t$ constraints of type \ref{packs}. Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero. We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma. Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$. Also, since $\theta^*$ is optimal and $\lambda$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{k}\lambda_j \geq \frac{1}{g^{i+1}}$. 
\end{proof}

The leaves of the FDT tree, or $L_t$ have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$. Our goal to now replace these leaves solutions in $\dom(P)$ with solutions in $S$. To this end, we need to reduce some variables with value of 1 into variables of value 0 and obtain feasibility in the meantime. We introduce a procedure that given a  point $(x,y)\in \dom(P)$ with $x\in \{0,1\}^n$ outputs a point $z\leq x$ with $z\in \{0,1\}^n$ such that $(z,w)$ is in $S$ for some vector $w\in \bbbr^p$.

The algorithm ``fixes" the variables iteratively, from $x_1$ to $x_t$. Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$. Now consider the following linear programming. The variables of this LP are the $z\in \bbbr^n$ variables and $w\in \bbbr^p$.
\begin{align}
	\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
	&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
	&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
\end{align}

If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$. Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$. Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$. This procedure is summarized in Algorithm \ref{domtoIP}.

\begin{algorithm}[H]\label{domtoIP}
	\KwIn{$(x,y)\in \dom(S)$}
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
	$x^{(0)}\leftarrow x$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\caption{The DomToIP algorithm}
\end{algorithm}

The following lemma proves Theorem \ref{domtoIP}.
\begin{lemma}
	Given $(x,y)\in \dom(P)$ Algorithm \ref{domtoIP} correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
\end{lemma}
\begin{proof}
	First, we need to show that in any iteration $\ell\in \{0,\ldots,n-1\}$ of Algorithm \ref{domtoIP} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
	\begin{align*}
		\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
		\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
	\end{align*}
	Notice that if $\LP^{(\ell)}$ is an non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$. First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$. By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$. Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^0$. So if $x^0_j$ is zero, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$. Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$. Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.

	Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$. Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.

	We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ . We have
	\begin{equation}
	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
	\end{equation}
	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of Algorithm \ref{domtoIP}. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.

	Now for the second case, assume $z^*_{\ell+1} > 0$. We have $x^{(\ell+1)}_{\ell+1}=1$. Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e. $z_{\ell+1}=1$. This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.

	Now consider $(x^{(t)},y^{(t)})$. Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$. If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$. If $x^{(t)} =1$, it must be the case that $z_t > 0$. By the argument above there is a point $(z',w')\in \IP^{(t-1)}$. We show that $x^{(t)} = z'$. Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$. We just need to show that $z'_j = 1$. Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.
\end{proof}

This completes the FDT algorithm.

\begin{algorithm}[H]\label{FDTFull}
	\KwIn{$P= \{(x,y)\in \bbbr^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \bbbr^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
	\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
	$L^0\leftarrow [(x^*,y^*),1]$\\
	\For{$i=1$ \textbf{to} $t$}{
		$L'\leftarrow \emptyset$\\
		\For{$[(x,y),\lambda] \in L^i$}{
			Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
			$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
		}
		Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
	}
	\For{$[(x,y),\lambda] \in L^t$}{
		Apply Algorithm \ref{domtoIP} to $(x,y)$ to obtain $(z,w)\in S$\\
		$F \leftarrow F \cup \{[(z,w),\lambda]\}$
	}
	\textbf{return} $F$
	\caption{Fractional Decomposition Tree Algorithm}
\end{algorithm}
\section{FDT for 2EC}\label{2EC}

In Section \ref{binaryfdt} our focus was on binary MIPs. In this section, in an attempt to extend FDT to 0,1,2 problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem. Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2. In the 2EC problem, we are given non-negative costs on the edge of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$. Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take an edge at most 2 times. The natural linear programming relaxation is $\EC(G) = \{x\in [0,2]^E: x(\delta(U))\geq 2 \mbox{ for } \emptyset \subset U \subset V\}$. Notice that $\dom(\EC(G))\cap [0,2]^{E} = \EC(G)$, since 2EC is a covering problem. We want to prove the following theorem.

\FDTEC*

We do not know the exact value for $g_{\EC}$, but we know $\frac{6}{5} \leq g_{\EC} \leq \frac{3}{2}$ \cite{carr-ravi,Wolsey1980}. Also, we need to remark that polyhedral version of Christofides' algorithm provides a $\frac{3}{2}$-approximation for 2EC, i.e. we already have an algorithm with $C\leq \frac{3}{2}$. However, we show later in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$.

The FDT algorithm for 2EC is very similar to the one for binary MIPs, but there are some differences as well. First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for 0,1,2 problems expect for one additional clause.

\begin{restatable}{lemma}{2ECLPC}
	\label{LPC2EC}
	Given $x\in \EC(G)$, and $e\in E$ we can find in polynomial time vectors $x^0,x^1$ and $x^2$ and scalars $\gamma_0,\gamma_1$, and $\gamma_2$ such that
	\begin{itemize}
		\item[(i)] $\gamma_0 + \gamma_1 +\gamma_2 \geq \frac{ 1}{g_{\EC}}$,
		\item[(ii)] $x^0,x^1,$ and $x^2$ are in  $ \EC(G)$, 
		\item[(iii)] $x^0_e=0$, $x^1_e=1$, and $x^2_e=2$,
		\item[(iv)] $\gamma_0 x^0 + \gamma_1{x}^1  + \gamma_2x^2\leq {x}$,
		\item[(v)] for $f\in E$ with ${x}_f\geq 1$, we have $x^j_f\geq 1$ for $j=0,1,2$. 
	\end{itemize}
\end{restatable}

\begin{proof}
	Consider the following linear programing with variables $\lambda_j$ and $x^j$ for $j=0,1,2$. 
	\begin{align}
		\quad\quad& \max\quad \;\sum_{j=0,1,2}\lambda_j\\
		&\;\text{s.t.} \quad x^j(\delta(U))\geq 2\lambda_j \;& \mbox{ for $\emptyset \subset U \subset V$, and $j=0,1,2$} \label{feasibility2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq 2\lambda_j\; &\mbox{ for $j=0,1,2$}\label{bound2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^j_e = j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1+x^2 \leq x\label{packing2ec}\\
		&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1,\lambda_2 \geq 0
	\end{align}

	Let $x^j$, $\gamma_j$ for $j=0,1,2$ be an optimal solution solution to the LP above. Let $\hat{x}^{j}=\frac{x^j}{\gamma_j}$ for $j=0,1,2$ where $\gamma_j>0$. If $\gamma_j=0$, let $\hat{x}^{j}=0$. Observe that  (ii), (iii), (iv), and (v) are satisfied with this choice. In order to show that (i) is also satisfied we prove the following claim.

	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1+\gamma_2\geq \frac{1}{g_{\EC}}$.
	\end{claim}
	\begin{proof}
		Suppose for contradiction $\sum_{j=0,1,2}\gamma_j = \frac{1}{g_{\EC}} - \epsilon$ for some $\epsilon >0$.

		Construct graph $G'$ by removing edge $f$ with $x_f\geq 1$ and replacing it with a path $P_f$ of length $\ceil{\frac{2}{\epsilon}}$. Define $x'_h = x_h$ for each edge $h$ such that $x_h<1$. For each $h\in P_f$ let $x'_h= x_f$ for all $f$ with $x_f\geq 1$. It is easy to check that $x'\in \EC(G')$. By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and 2-edge-connected multigraphs $F'_i$ of $G'$ for $i=1,\ldots,k$ such that 
		$\sum_{i=1}^{k}\theta_i \chi^{F'_i}\leq g_{\EC}x'$.

		Note that each $F'_i$ contains at least one copy of every edge in any path $P_f$, except for at most one edge in the path. We will obtain 2-edge-connected multigraphs $F_1,\ldots,F_k$ of $G$ using $F'_1,\ldots,F'_k$, respectively. To obtain $F_i$ first remove all $P_f$ paths from $F'_i$. Suppose there is an edge $h$ in $P_f$ such that $\chi^{F'_i}_h=0$, this means that for any edge $p\in P_f$ such that $p\neq h$, $\chi^{F'_i}_p=2$. In this case, let $\chi^{F_i}_f=2$, i.e. add two copies of $f$ to $F_i$. If there is an edge $h\in P_f$ with $\chi^{F'_i}_h = 1$, let $\chi^{F_i}_f=1$, i.e. add one copy of $f$ to $F_i$. If for all edge $h\in P_f$, we have $\chi^{F'_i}_h=2$, then let $\chi^{F_i}_f=2$. For $f\in E$ with $x_f<1$ we have
		\begin{equation}
		\sum_{i=1}^{k}\theta_i \chi^{F_i}_f=\sum_{i=1}^{k}\theta_i \chi^{F'_i}_f\leq g_{\EC}x'_f= g_{\EC}x_f.
		\end{equation}
		In addition for $f\in E$ with $x_f\geq 1$ we have $\chi^{F_i}_f \leq \frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}$ by construction.
		\begin{align*}
			\sum_{i=1}^{k}\theta_i \chi^{F_i}_f&\leq \sum_{i=1}^{k}\theta_i\frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&= \frac{\sum_{h\in P_f} \sum_{i=1}^{k}\theta_i\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&\leq \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&= \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
			&= \frac{\ceil{\frac{2}{\epsilon}}}{\ceil{\frac{2}{\epsilon}}-1}g_{\EC}x_f
		\end{align*}
		Therefore, we have 
		\begin{equation}
		x' \geq \sum_{i\in [k]: \chi^{F_i}_e=1}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}+\sum_{i\in [k]: \chi^{F_i}_e=2}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}.
		\end{equation}
		Let $x^j = \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}$ and $\theta_j =  \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$ for $j=0,1,2$. It is easy to check that $x^j$ , $\theta_j$ for $j=0,1,2$ is a feasible solution to the LP above. Notice that $\sum_{j=0,1,2}\theta_j = \frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$. By assumption, we have $\frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\leq  \frac{1}{g_{\EC}}-\epsilon$. However, this means $2\leq 1$ which is a contradiction.
	\end{proof}
	This concludes the proof.
\end{proof}

In contrast to FDT for binary MIPs where we round up the fractional variables that are already branched on at each level, in FDT for 2EC we keep all coordinates as they are and preform a rounding procedure at the end. Formally, let $L_i$ for $i=1,\ldots,|\sup(x^*)|$ be collections of pairs of feasible points in $\EC(G)$ together with their multipliers. Let $t=|\sup(x^*)|$ and assume without loss of generality that $\sup(x^*)=\{e_1,\ldots,e_t\}$.

\begin{lemma}\label{2ecpruning}
	The FDT algorithm for 2EC in  polynomial time produces sets $L_0,\ldots,L_t$ of pairs $x\in \EC(G)$ together with multipliers $\lambda$ with the following properties.
	\begin{enumerate}
		\item[a.] If $x\in L_i$, then $x_{e_j}=0$ or $x_{e_j}\geq 1$ for $j=1,\ldots,i$,
		\item [b.] $\sum_{(x,\lambda)\in L_i }\lambda \geq \frac{1}{g_{\EC}^i}$,
		\item[c.]  $\sum_{(x,\lambda)\in L_i }\lambda x \leq x^*$,
		\item[d.] $|L_i|\leq t$.
	\end{enumerate}
\end{lemma}
\begin{proof}
	We proceed by induction on the $i$. Define $L_0=\{(x^*,1)\}$. It is easy to check all the properties are satisfied. Now, suppose by induction we have $L_{i-1}$ for some $i=1,\ldots,t$ that satisfies all the properties. For each solution $x^\ell$ in $L_{i-1}$ apply Lemma \ref{LPC2EC} on $x^\ell$ and $e_{i}$ to obtain $x^{\ell j}$ and $\lambda_{\ell j}$ for $j=0,1,2$. Let $L'$ be the collection that contains $(x^{\ell j},\lambda_\ell \cdot \lambda_{\ell j})$ for $j=0,1,2$, when applied to all $(x^\ell,\lambda_\ell)$ in $L_{i-1}$. Similar to the proof in Lemma \ref{prune} one can check that $L_i$ satisfies properties (b), (c). We now verify property (a). Consider a solution $x^\ell$ in $L_{i-1}$. For $e\in \{e_1,\ldots,e_{i-1}\}$ if $x^\ell_e =0$, then by property (iv) in Lemma \ref{LPC2EC} we have $x^{\ell j}=0$ for $j=0,1,2$. Otherwise by induction we have $x^{\ell}_{e}\geq 1$ in which case property (v) in Lemma \ref{LPC2EC} ensures that $x^{\ell j}_e\geq 1$ for $j=0,1,2$. Also, $x^{\ell j}_{e_i}= j$, so $x^{\ell j}_{e_i}=0$ or $x^{\ell j}_{e_i}\geq 1$ for $j=0,1,2$.

	If $|L'|\geq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
\end{proof}

Consider the solutions $x$ in $L_t$. For each variable $e$ we have $x_e=0$ or $x_e\geq 1$. 
\begin{lemma}\label{rounddown}
	Let $x$ be a solution in $L_t$. Then $\floor{x} \in \EC(G)$. 
\end{lemma}
\begin{proof}
	Suppose not. Then there is a set of vertices $\emptyset \subset U \subset V$ such that $\sum_{e\in \delta(U)}\floor{x_e}<2$. Since $x\in \EC(G)$ we have $\sum_{e\in \delta(U)}x_e \geq 2$. Therefore, there is an edge $f\in \delta(U)$ such that $x_f$ is fractional. By property (a) in Lemma \ref{2ecpruning}, we have $1<  x_f < 2$. Therefore, there is another edge $h$ in $\delta(U)$ such that $x_h>0$, which implies that $x_h\geq 1$. But in this case $\sum_{e\in \delta(U)}\floor{x_e}\geq  \floor{x_f}+\floor{x_h}  \geq 2$. This is a contradiction.
\end{proof}

The FDT algorithm for 2EC iteratively applies Lemmas \ref{LPC2EC} and \ref{2ecpruning} to variables $x_1,\ldots,x_t$ to obtain leaf point solutions $L_t$. Then, we just need to apply Lemma \ref{rounddown} to obtain the 2-edge-connected multigraphs from every solution in $L_t$. Notice that $t\leq 2|V|-3$ \cite{}. By Lemma \ref{2ecpruning} we have
\begin{align*}
	\sum_{(x,\lambda)\in L_t} \frac{\lambda}{\sum_{(x,\lambda)\in L_t}\lambda} \floor{x} \leq \frac{1}{\sum_{(x,\lambda)\in L_t}\lambda} \sum_{(x,\lambda)\in L_t} \lambda {x} \leq g^t_{\EC} x^*.
\end{align*}

\section{Stronger version of Carr-Vempala for covering problems} \label{gap}

Theorem \ref{CV} characterizes the integrality gap as the smallest number such that for any point $x\in \dom(P)$, $gx$ dominates a convex combination of points in $S$, i.e. there exists convex combination $\sum_{i=1}^{k}\lambda_ix^i \leq gx$.  In a covering problem, we assume that matrix $A$ in the description of $P$ is a non-negative matrix, hence if $y\geq x$ and $x\in P$ we have $y\in P$. We also assume the right hand side vector in (\ref{P}) is of the form $b\textbf{1}$, i.e. it is a uniform vector. Finally we assume we have bound constraints $x\leq b\textbf{1}$. This class of problems include a broad class of problems. Notice that for a covering problem $\dom(P)=P$.  We show that for these problems, we can make Theorem \ref{CV} stronger in the following sense.

\tightcuts*

In other words, the integrality gap is the smallest number such that for any $x\in P$, there exists a convex combination $y=\sum_{i=1}^{k}\lambda_ix^i$, such that $A_jy\leq g(A_jx)$ for all $j$ such that $A_jx=b$.

Notice that the proof of this theorem, same as Theorem \ref{CV}, does not imply a polynomial time algorithm.

Observe that if $C\geq g$, by Theorem \ref{CV}, there is a convex combination of points in $S$ that is dominated by $Cx$, i.e. there exists $\theta\in [0,1]^{k}$, where $\sum_{i=1}^{k}\theta_i=1$, and $x^i\in S$, such that $\sum_{i=1}^{k}\theta_ix^i\leq gx$. The same convex combination also trivially satisfies both requirements in Theorem \ref{tightcuts}. The more interesting direction is the converse. We begin with the following theorem. Suppose $v^1,\ldots,v^r$ are the extreme points of $P$. Assume for each $i=1,\ldots,r$, there exists a convex combination of points in $S$, namely $\sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell$ such that $A_j \sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell \leq CA_jv^i$ for $j$ such that $A_jv^i = b$. Let $z^i = \sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell$.
\begin{lemma}\label{epsilon}
	For any  $i\in\{1,\ldots,r\}$, there exists $\epsilon_i >0$ and ${x^i}\in P$ where ${x^i}\leq \frac{Cv^i-\epsilon_i z^i}{C(1-\epsilon_i)}$.
\end{lemma}
\begin{proof}

	Let $u^i(\epsilon) = \frac{Cv^i-\epsilon z^i}{C(1-\epsilon)}$. For $j\in \{1,\ldots,m\}$, let $t_j = A_jz^i-Cb$ and $s_j=A_jv^i-b$. 
	Assume $\epsilon <1$. For $j\in \{1,\ldots,m\}$ such that $A_jz^i\leq Cb$, i.e. $t_j\leq 0$ (this includes $j$ such that $A_jv^i=b$, i.e. $s_j=0$) we have
	\begin{equation}
	A_j u^i(\epsilon) = \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}\geq \frac{Cb-\epsilon Cb}{C(1-\epsilon)}=b
	\end{equation}
	Assume $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$. Notice that $\max_{j: t_j >0} \frac{s_j}{t_j}>0$ since for $j$ such that $t_j>0$, we have $A_jz_i > Cb$ which implies that $A_jv^i>b$, so $s_j>0$. For $j$ such that $t_j>0$ we have
	\begin{align*}
		A_ju^i(\epsilon) &= \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}& \\
		&= \frac{C(b+s_j)-\epsilon (Cb+t_j)}{C(1-\epsilon)}&\\
		&= b+ \frac{Cs_j-\epsilon t_j}{C(1-\epsilon)}&\\
		&\geq b & (\epsilon  \leq C\cdot  \frac{s_j}{t_j}, \mbox{ and } \epsilon <1, \mbox{ so } \frac{Cs_j-\epsilon t_j}{C(1-\epsilon)}\geq 0 )
	\end{align*} 
	Therefore if $\epsilon \leq 1$ and $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$ we have $Au^i(\epsilon)\geq \textbf{1}b$. Next, we show that we can choose $\epsilon$ so that $ u^i(\epsilon)\geq 0$.

	For $\ell\in \{1,\ldots,n\}$, if $z^i_\ell=0$, then we have $u_\ell^i(\epsilon) = \frac{Cv_\ell^i}{C(1-\epsilon)}\geq 0$, since $v^i_\ell\geq 0$ and $\epsilon <1$. Otherwise we have $z^i_\ell>0$. Assume $\epsilon \leq C\cdot \min_{ \ell:z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}$. Notice that for $\ell$ such that $z^i_\ell>0$, we have $v^i_\ell>0$ since $z^i$ lies in the support of $v^i$ by assumption. This means that $\min_{\ell:z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}>0$. Now, for $\ell$ such that $z^i_\ell>0$, we have $u^i_\ell(\epsilon) = \frac{Cv_\ell^i-\epsilon z_\ell^i}{C(1-\epsilon)}\geq 0$ by choice of $\epsilon$.

	Define $\epsilon_i =\min\{1, C\cdot \min_{j: t_j >0}\frac{s_j}{t_j},C\cdot\min_{\ell: z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}\}$. By the arguments above $Au^i(\epsilon_i)\geq \textbf{1}b$ and $u^i(\epsilon_i)\geq 0$. Define $x^i$ as follows: For each $j\in \{1,\ldots,m\}$, if $u^i_j(\epsilon_i)\leq b$, then let $x^i_j=u^i_j(\epsilon_i)$, otherwise let $x^i_j=b$. We need to show that $x^i\in P$. Note that clearly $x^i\geq 0$, hence we only need to show that $Ax^i\geq \textbf{1}b$. Suppose for contradiction there is $j\in \{1,\ldots,m\}$ such that $A_jx^i <b$. Since $u^i(\epsilon)\in P$, there must be $\ell^*\in\{1,\ldots,n\}$ such that $u^i_{\ell^*}(\epsilon)>b$, and $A_{j,\ell^*}>0$. But this means that $A_{j,\ell^*}\geq 1$ and $x^i_{\ell^*}=b$. Therefore $A_jx^i \geq  A_{j,\ell^*}x^i_{\ell^*}= A_{j,\ell^*}b\geq b$. \end{proof}
\begin{lemma}\label{tightcutcomb}
	There exists a convex combination of point in $S$ that is dominated by $Cv^i$ for $i=1,\ldots,r$.
\end{lemma}
\begin{proof}

	We prove something slightly stronger. We show that for $i\in\{1,\ldots,r\}$, and for $j=1,\ldots,i$, the vector $Cv^j$ dominates  a convex combination of $z^1,\ldots,z^i$ and $Cv^{i+1},\ldots,Cv^r$. Note that this is enough to prove our statement since for $i=r$, the statement implies that $Cv^j$ dominates a convex combination of $z^1,\ldots,z^r$ for $j=1,\ldots,r$.

	We proceed by induction on $i$. If $i=1$, we just need to show that $Cv^1$ is dominated by a convex combination of $z^1$ and $Cv^2,\ldots,Cv^r$. By Lemma \ref{epsilon}, there exists $x^1\leq  \frac{Cv^1-\epsilon_1z^1}{C(1-\epsilon_1)}$. We have $x^1\in P$, so we can write $x^1$ as convex combination of $v^1,\ldots, v^r$. We have
	\begin{equation}
	Cv^1 \geq  \epsilon_1z^1 + C(1-\epsilon_1)x^1 \geq \epsilon_1z^1 + C(1-\epsilon_1) \sum_{\ell=1}^{r}\lambda^1_\ell v^\ell.
	\end{equation}
	Hence,
	\begin{equation}
	Cv^1 \geq \frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}\cdot z^1 + (1-\epsilon_i)\sum_{\ell=2}^{r} \frac{\lambda^1_\ell}{1-(1-\epsilon_1)\lambda_1^1}\cdot Cv^\ell.
	\end{equation}
	Observe that $\frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}$ and $(1-\epsilon_1)\frac{\lambda^1_\ell}{1-(1-\epsilon_1)\lambda_1^1}$ for $\ell=2,\ldots,r$ form convex multipliers, so the base case holds.

	Now consider $i\in \{1,\ldots,r-1\}$. By induction, for $j=1,\ldots,i$ we have
	\begin{equation}\label{IHs}
	Cv^j \geq  \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell + \sum_{\ell=i+1}^{r}\theta^{j}_{\ell}Cv^\ell.
	\end{equation}
	Suppose we are able to show 
	\begin{equation}\label{claim} 
	Cv^{i+1} \geq \sum_{\ell=1}^{i+1} \mu_\ell z^\ell + \sum_{\ell=i+2}^{r}\mu_{\ell}Cv^\ell,\end{equation} 
	where $\mu\geq 0$, and $\sum_{\ell=1}^{r}\mu_{\ell}=1$. Then for $j=1,\ldots,i$ we have
	\begin{align*}
		Cv^j& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\theta^{j}_{i+1}Cv^{i+1}+  \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell.& (\mbox{By } \ref{IHs})\\
		& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\sum_{\ell=1}^{i+1}\theta^{j}_{i+1}\mu_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_{i+1}\mu_{\ell}Cv^\ell +   \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell.& (\mbox{By } \ref{claim})\\
		&= \sum_{\ell=1}^{i} (\theta^j_\ell+\mu_{\ell}\theta^j_{i+1}) z^\ell + \mu_{j+1}\theta^j_{i+1}z^{i+1} + \sum_{\ell=i+2}^{r} (\theta^j_\ell+\mu_\ell\theta^j_{i+1})Cv^\ell.&
	\end{align*} 
	It is easy to see that the multipliers above are convex. Thus, we only need to show the convex combination in (\ref{claim}) exists. This will be similar to what we did in the base case. By Lemma \ref{epsilon}, there exists $\epsilon_{i+1}$ and $x^{i+1}$ such that
	\begin{align*}
		Cv^{i+1}&\geq \epsilon_{i+1}z^{i+1}+ C(1-\epsilon_{i+1})x^{i+1}\\
		&\geq \epsilon_{i+1}z^{i+1}+ (1-\epsilon_{i+1})\sum_{\ell=1}^{k}\lambda_{\ell}Cv^\ell
	\end{align*}
	Applying induction we can replace $Cv^j$ by $ \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell + \sum_{\ell=i+1}^{r}\theta^{j}_{\ell}Cv^\ell$ for $j=1,\ldots,i$. 
	This means
	\begin{align*}
		(1-(1-\epsilon_{i+1})(\lambda_{i+1}+\sum_{j=1}^{i}\lambda_j\theta^j_{i+1}))Cv^{i+1}&\geq \epsilon_{i+1}z^{i+1}+(1-\epsilon_{i+1})\sum_{j=1}^{i}\lambda_j (\sum_{\ell=1}^{i}\theta^j_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_\ell Cv^\ell)\\
		&+(1-\epsilon_{i+1})(\sum_{j=1}^{i}\lambda_j \lambda^j_{i+1}+\lambda^i_{i+1})C+ (1-\epsilon_{i+1})\sum_{j=i+2}^{r}\lambda_jCv^{j} 
	\end{align*}
	It is easy to show that  multipliers above are convex.
\end{proof}

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
% \bibliographystyle{splncs04}
% \bibliography{mybibliography}
%
\begin{thebibliography}{8}

	\bibitem[CR98]{carr-ravi}
	Robert Carr and R.~Ravi.
	\newblock A new bound for the 2-edge connected subgraph problem.
	\newblock In {\em Proceedings of the 6th International IPCO Conference on
		Integer Programming and Combinatorial Optimization}, pages 112--125, London,
	UK, UK, 1998. Springer-Verlag.

	\bibitem[CV04]{CV}
	Robert Carr and Santosh Vempala.
	\newblock On the held-karp relaxation for the asymmetric and symmetric
	traveling salesman problems.
	\newblock {\em Mathematical Programming}, 100(3):569--587, Jul 2004.

	\bibitem[FGL05]{fp1}
	Matteo Fischetti, Fred Glover, and Andrea Lodi.
	\newblock The feasibility pump.
	\newblock {\em Mathematical Programming}, 104(1):91--104, Sep 2005.

	\bibitem[FS09]{fp2}
	Matteo Fischetti and Domenico Salvagnin.
	\newblock Feasibility pump 2.0.
	\newblock {\em Mathematical Programming Computation}, 1(2):201--222, Oct 2009.

	\bibitem[GJ79]{GJ79}
	M.R. Garey and D.S. Johnson.
	\newblock {\em Computers and Intractability -- A Guide to the Theory of
		{NP}-Completeness}.
	\newblock Freeman, San Francisco, CA, 1979.

	\bibitem[GLS93]{cons-cara}
	Martin Gr{\"o}tschel, L{\'a}szl{\'o} Lov{\'a}sz, and Alexander Schrijver.
	\newblock {\em Geometric Algorithms and Combinatorial Optimization}, volume~2.
	\newblock Second corrected edition edition, 1993.

	\bibitem[Jai98]{jain}
	Kamal Jain.
	\newblock A factor 2 approximation algorithm for the generalized steiner
	network problem.
	\newblock In {\em Proceedings of the 39th Annual Symposium on Foundations of
		Computer Science}, FOCS '98, pages 448--, Washington, DC, USA, 1998. IEEE
	Computer Society.

	\bibitem[RT87]{randomizedrounding}
	Prabhakar Raghavan and Clark~D. Tompson.
	\newblock Randomized rounding: A technique for provably good algorithms and
	algorithmic proofs.
	\newblock {\em Combinatorica}, 7(4):365--374, Dec 1987.

	\bibitem[Sch03]{schrijver}
	A.~Schrijver.
	\newblock {\em Combinatorial Optimization - Polyhedra and Efficiency}.
	\newblock Springer, 2003.

	\bibitem[Vaz01]{vazirani}
	Vijay~V. Vazirani.
	\newblock {\em Approximation Algorithms}.
	\newblock Springer-Verlag, Berlin, Heidelberg, 2001.

	\bibitem[Wol80]{Wolsey1980}
	Laurence~A. Wolsey.
	\newblock {\em Heuristic analysis, linear programming and branch and bound},
	pages 121--134.
	\newblock Springer Berlin Heidelberg, Berlin, Heidelberg, 1980.

	\bibitem[WS11]{sw}
	David~P. Williamson and David~B. Shmoys.
	\newblock {\em The Design of Approximation Algorithms}.
	\newblock Cambridge University Press, New York, NY, USA, 1st edition, 2011.

\end{thebibliography}
\end{document}

### 2018-11-13 IPCO format/FDT.tex
bib fixed

@@
 %
-\authorrunning{Carr et al.}
+\authorrunning{R. Carr, A. Haddadan, C. Phillips}
 % First names are abbreviated in the running head.
@@
 
-Many researchers (see \cite{sw, vazirani}) have developed polynomial time algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$ for some $C$ which can be a constant number or dependent on some parameter of the MILP, e.g.
+Many researchers (see \cite{vazirani,sw}) have developed polynomial time algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$ for some $C$ which can be a constant number or dependent on some parameter of the MILP, e.g.
 $O(\log(n))$.
@@
 
-In contrast to Fact \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
+In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
 This points to an interesting open question.
@@
 
-\subsection{Notation and Preliminaries}
+\subsection{Notation}
+For vectors $x,y\in \bbbr_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$.
+For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$.
+Let $\textbf{1}$ be the vector of all ones of a suitable dimension.
+For a set $S$ of vectors in $\bbbr_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.
 
@@
 Then, we just need to apply Lemma \ref{rounddown} to obtain the 2-edge-connected multigraphs from every solution in $L_t$.
-Notice that $t\leq 2|V|-3$ \cite{}.
+Notice that since $x$ is an extreme point we have $t\leq 2|V|-3$ \cite{}.
 By Lemma \ref{2ecpruning} we have
@@
 %
-\begin{thebibliography}{8}
+\begin{thebibliography}{10}
 
-	\bibitem[CR98]{carr-ravi}
+		\bibitem{carr-ravi}
 		Robert Carr and R.~Ravi.
@@
 
-	\bibitem[CV04]{CV}
+		\bibitem{CV}
 		Robert Carr and Santosh Vempala.
@@
 
-	\bibitem[FGL05]{fp1}
+		\bibitem{gerard}
+		G{\'e}rard Cornu{\'e}jols, Jean Fonlupt, and Denis Naddef.
+		\newblock The traveling salesman problem on a graph and some related integer
+		polyhedra.
+		\newblock {\em Mathematical Programming}, 33(1):1--27, Sep 1985.
+
+		\bibitem{fp1}
 		Matteo Fischetti, Fred Glover, and Andrea Lodi.
@@
 
-	\bibitem[FS09]{fp2}
+		\bibitem{fp2}
 		Matteo Fischetti and Domenico Salvagnin.
@@
 
-	\bibitem[GJ79]{GJ79}
+		\bibitem{GJ79}
 		M.R. Garey and D.S. Johnson.
@@
 
-	\bibitem[GLS93]{cons-cara}
+		\bibitem{cons-cara}
 		Martin Gr{\"o}tschel, L{\'a}szl{\'o} Lov{\'a}sz, and Alexander Schrijver.
@@
 
-	\bibitem[Jai98]{jain}
+		\bibitem{jain}
 		Kamal Jain.
@@
 
-	\bibitem[RT87]{randomizedrounding}
+		\bibitem{randomizedrounding}
 		Prabhakar Raghavan and Clark~D. Tompson.
@@
 
-	\bibitem[Sch03]{schrijver}
+		\bibitem{schrijver}
 		A.~Schrijver.
@@
 
-	\bibitem[Vaz01]{vazirani}
+		\bibitem{vazirani}
 		Vijay~V. Vazirani.
@@
 
-	\bibitem[Wol80]{Wolsey1980}
+		\bibitem{sw}
+		David~P. Williamson and David~B. Shmoys.
+		\newblock {\em The Design of Approximation Algorithms}.
+		\newblock Cambridge University Press, New York, NY, USA, 1st edition, 2011.
+
+		\bibitem{Wolsey1980}
 		Laurence~A. Wolsey.
@@
 
-	\bibitem[WS11]{sw}
-	David~P. Williamson and David~B. Shmoys.
-	\newblock {\em The Design of Approximation Algorithms}.
-	\newblock Cambridge University Press, New York, NY, USA, 1st edition, 2011.
-
 \end{thebibliography}

### 2018-11-18 IPCO format/FDT.tex
shorter version

@@
 
-A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}.
+A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}, which is a generalization of Goemans proof for blocking polyhedra \cite{goemans}.
 
@@
 \end{question}
-Although Question \ref{question2} is wide open, for some problems $\mathcal{I}$ there are polynomial time algorithms.
+Although Question \ref{question2} is wide open, for some problems $\mathcal{I}$ there are polynomial time algorithms closing the gap.
 For example, for generalized Steiner forest problem \cite{jain} gave an LP-based 2-approximation algorithm.
@@
 In addition these algorithms do not provide any bounds on the quality of the solution they find.
-
 \subsection{Our results}
-
 In this paper we study Theorem \ref{CV} and the natural questions that follow from it (Questions \ref{question1} and \ref{question2}).
@@
 \end{equation}
-For a point $(x,y)\in P(I)$, let $\sup(x,y)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.
+For a vector $x\in \bbbr^n$ such that $(x,y)\in P(I)$ for some $y\in \bbbr^p$, let $\spp(x)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.
 
@@
 	\label{binaryFDT}
-	Assume $1\leq g_I<\infty$. 	
-	The FDT algorithm (Algorithm \ref{FDTFull}), given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\sup(x^*,y^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g_I^{|\sup(x^*,y^*)|}$.
+	Assume $1\leq g_I 	<\infty$. 	
+	The FDT algorithm, given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\spp(x^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
+Moreover, $C\leq g_I^{|\spp(x^*)|}$.
 \end{restatable}
@@
 \begin{restatable}{theorem}{DomToIP}
-	\label{DomToIP}
-	Assume $1\leq g_I \leq \infty$. The DomToIP algorithm (Algorithm \ref{domtoIP}) finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
+	\label{domtoIP}
+	Assume $1\leq g_I < \infty$. The DomToIP algorithm finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
 \end{restatable}
@@
 In attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem.
-In this problem we want to find the minimum weight 2-edge-connected multigraph in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
+In this problem we want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
 For this problem the natural linear programming relaxation is
@@
 
-\subsection{Notation}
+\subsection{Notations}
 For vectors $x,y\in \bbbr_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$.
@@
 \begin{equation}
-S(I)= \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
+S(I)= \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
 \end{equation}
@@
 \begin{equation}
-P(I) = \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
+P(I) = \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
 \end{equation}
@@
 For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
-In this section, we prove the following theorem.
-
-\binaryFDT*
-
-One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{DomToIP} that we will also prove in this section.
+In this section, we prove Theorem \ref{binaryFDT}.
+One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{domtoIP} that we will also prove in this section.
 
@@
 In the remainder of this section we explain the FDT algorithm and prove Theorem \ref{binaryFDT}.
-For simplicity in the notations we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively.
-Let $t=|\sup(x^*,y^*)|$.
-We assume without loss of generality that $\sup(x^*,y^*)= \{1,\ldots,t\}$.
+For simplicity in the notation we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively.
+Let $t=|\spp(x^*)|$.
+We assume without loss of generality that $\spp(x^*)= \{1,\ldots,t\}$.
 
@@
 \begin{lemma}\label{LPClemma}
-	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vector $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that
-	\begin{itemize}
-		\item[(i)] $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$,
-		\item[(ii)] $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$, 
-		\item[(iii)] $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$,
-		\item[(iv)] $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
-	\end{itemize}
+	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$,
+		,(iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
 \end{lemma}
 
-\begin{proof}[Proof of Lemma \ref{LPClemma}]
-
-	Consider the following linear programing which we denote by $\LPC(\ell,x',y')$. The variables of $\LPC(\ell,x',y')$ are $\gamma_0,\gamma_1$ and $(x^0,y^0)$ and $(x^1,y^1)$. 
+\begin{proof} 
+	Consider the following linear program which we denote by $\LPC(\ell,x',y')$. The variables of $\LPC(\ell,x',y')$ are $\gamma_0,\gamma_1$ and $(x^0,y^0)$ and $(x^1,y^1)$. 
 	\begin{align}
@@
 Note that $\lambda_0+\lambda_1 = \frac{1}{g}$.
-Constraint \ref{packing} is satisfied by Inequality \ref{splitting}.
+Constraint (\ref{packing}) is satisfied by Inequality (\ref{splitting}).
 Also, for $j=0,1$ we have
 		\begin{equation}
-		Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \leq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
+		Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \geq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
 		\end{equation}
-		Hence, Constraints \ref{feasibility} holds.
-Constraint \ref{branchcoordinate} also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$.
+		Hence, Constraints (\ref{feasibility}) holds.
+Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$.
 The rest of the constraints trivially hold.
@@
 
-We now show if $x'$ in the statement of of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
+We now show if $x'$ in the statement of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
 \begin{lemma}\label{round-up}
-	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vector $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that
-	\begin{itemize}
-		\item[(i)] $\gamma_0 + \gamma_1  \geq\frac{ 1}{g}$,
-		\item[(ii)] $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, 
-		\item[(iii)] $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$,
-		\item[(iv)] $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
-		x'$,
-		\item[(v)] $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
-	\end{itemize}
+	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\frac{ 1}{g}\leq \gamma_0 + \gamma_1  \leq 1$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
+		x'$,(v) $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
 \end{lemma} 
@@
 We define $\hat{x}^0$ and $\hat{x}^1$ as follows.
-For $i=0,1$, for $j=1,\ldots,\ell-1$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,n$ let $\hat{x}^i_j = \bar{x}^i_j$.
+For $i=0,1$, for $j=1,\ldots,\ell-1$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,t$ let $\hat{x}^i_j = \bar{x}^i_j$.
 We now show that $(\hat{x}^0,\bar{y}^0)$, $(\hat{x}^1,\bar{y}^1)$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions.
@@
 We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$.
-If $j=\ell,\ldots,n$, then this clearly holds.
+If $j=\ell,\ldots,t$, then this clearly holds.
 Hence, assume $j\leq \ell-1$.
 By the property of $x'$ we have $x'_j\in \{0,1\}$.
-If $x'_j= 0$, then by Constraint \ref{packing} we have $\bar{x}^0_j = \bar{x}^1_j=0$.
+If $x'_j= 0$, then by Constraint (\ref{packing}) we have $\bar{x}^0_j = \bar{x}^1_j=0$.
 Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds.
 Otherwise if $x'_j = 1$, then we have
-	\begin{equation*}\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.\end{equation*}
+	$\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.$ 
 	Therefore (v) holds.
@@
 The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree.
-The points in the leaves of the FDT tree, or $L_t$, are points in $\dom(P)$ and are integral for all integer variables.
+The points in the leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.
 
 \begin{lemma}\label{prune}
-	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $(x,y)\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$. 
-	\begin{itemize}
-		\item[a.] If $(x,y)\in L_i$, then $x_j \in \{0,1\}$ for $j=1,\ldots,i$, i.e. the first $i$ coordinates of a solution in level $i$ are integral. 
-		\item[b.] $\sum_{[(x,y),\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$.
-		\item[c.] $\sum_{[(x,y),\lambda]\in L_i}\lambda x \leq x^*$.
-		\item[d.] $|L_i|\leq t$.
-	\end{itemize}
+	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $(x,y)\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$:
+		(a) If $(x,y)\in L_i$, then $x_j \in \{0,1\}$ for $j=1,\ldots,i$, i.e.
+the first $i$ coordinates of a solution in level $i$ are integral, (b) $\sum_{[(x,y),\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$, (c) $\sum_{[(x,y),\lambda]\in L_i}\lambda x \leq x^*$, (d) $|L_i|\leq t$.
 \end{lemma}
@@
 Let the solutions in $L_i$ be $(x^j,y^j)$ for $j=1,\ldots,k$ and $\lambda_j$ be their multipliers, respectively.
-For each $j\in 1,\ldots,k$ by Lemma \ref{round-up} (setting $(x',y')= (x^j,y^j)$ and $\ell = i$) we can find $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and $\lambda^0_j$, $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}.
-Define $L'$ to be the set of node with solutions $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and multipliers  $\lambda_j\lambda^0_j$, $\lambda_j\lambda^1_j$, respectively, for $j=1,\ldots,k$.
-
-	Notice that for each $j\in \{1,\ldots,k\}$ by property (v) in Lemma \ref{round-up} we have $x_\ell^{j0}, x_\ell^{j1}\in \{0,1\}$ for $\ell = 0,\ldots,i+1$. We also have
+For each $j= 1,\ldots,k$ by Lemma \ref{round-up} (setting $(x',y')= (x^j,y^j)$ and $\ell = i+1$) we can find $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and $\lambda^0_j$, $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}.
+Define $L'$ to be the set of nodes with solutions $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and multipliers  $\lambda_j\lambda^0_j$, $\lambda_j\lambda^1_j$, respectively, for $j=1,\ldots,k$.
+It is easy to check that \iffalse{
+	Notice that for each $j= 1,\ldots,k$ by property (v) in Lemma \ref{round-up} we have $x_h^{j0}, x_h^{j1}\in \{0,1\}$ for $h = 0,\ldots,i+1$. We also have
 	\begin{align*}
@@
 		& \leq x^*.&(\text{By induction hypothesis})	 
-	\end{align*} 
-	Set $L'$ seems like a suitable candidate for $L_{i+1}$, however we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$.
-We call the following linear programming $\prun(L')$.
-Let $L' = \{[(x^1,y^1),\lambda_1],\ldots,[(x^k,y^k),\lambda_k]\}$.
+	\end{align*} \fi set $L'$ is a suitable candidate for $L_{i+1}$, i.e.
+set $L'$ satisfies (a), (b) and (c).
+However we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$.
+We call the following linear program $\prun(L')$.
+Let $L' = \{[(x^1,y^1),\gamma_1],\ldots,[(x^{2k},y^{2k}),\gamma_{2k}]\}$.
 The variables of $\prun(L')$ is a scalar variable $\theta_j$ for each node $j$ in $L'$.
-
 	\begin{align}
-		\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{k} \theta_j\\
-		&\;\text{s.t.} \quad \;\;\sum_{j=1}^{k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
+		\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{2k} \theta_j\\
+		&\;\text{s.t.} \quad \;\;\sum_{j=1}^{2k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
 		&\;{\color{white}{\text{s.t.}} }\quad  \;\quad\quad\theta \geq 0\label{nonneg}
@@
 
-	Notice that $\theta = \lambda$ is in fact a feasible solution to $\prun(L')$.
+	Notice that $\theta = \gamma$ is in fact a feasible solution to $\prun(L')$.
 Let $\theta^*$ be the optimal vertex point solution to this LP.
-Since the problem is in $\bbbr^k$,  $\theta^*$ has to satisfy $k$ linearly independent constraints at equality.
-However, there are only $t$ constraints of type \ref{packs}.
+Since the problem is in $\bbbr^{2k}$,  $\theta^*$ has to satisfy $2k$ linearly independent constraints at equality.
+However, there are only $t$ constraints of type (\ref{packs}).
 Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero.
-We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma.
+We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,2k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma.
 Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$.
-Also, since $\theta^*$ is optimal and $\lambda$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{k}\lambda_j \geq \frac{1}{g^{i+1}}$.
+Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$.
 \end{proof}
-
-The leaves of the FDT tree, or $L_t$ have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$.
+The leaves of the FDT tree,  $L_t$, have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$.
 Our goal to now replace these leaves solutions in $\dom(P)$ with solutions in $S$.
@@
 The algorithm ``fixes" the variables iteratively, from $x_1$ to $x_t$.
-Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
-Now consider the following linear programming.
+Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$.
+Now consider the following linear program.
 The variables of this LP are the $z\in \bbbr^n$ variables and $w\in \bbbr^p$.
@@
 Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$.
-This procedure is summarized in Algorithm \ref{domtoIP}.
-
-\begin{algorithm}[H]\label{domtoIP}
+This procedure is the DomToIP algorithm.
+\iffalse{
+\begin{algorithm}[H]
 	\KwIn{$(x,y)\in \dom(S)$}
@@
 	}
+	\label{domtoIPalg}
 	\caption{The DomToIP algorithm}
 \end{algorithm}
-
+}\fi
 The following lemma proves Theorem \ref{domtoIP}.
 \begin{lemma}
-	Given $(x,y)\in \dom(P)$ Algorithm \ref{domtoIP} correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
+	Given $(x,y)\in \dom(P)$, DomToIP algorithm correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
 \end{lemma}
-\begin{proof}
-	First, we need to show that in any iteration $\ell\in \{0,\ldots,n-1\}$ of Algorithm \ref{domtoIP} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
-	\begin{align*}
-		\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
-		\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
-	\end{align*}
-	Notice that if $\LP^{(\ell)}$ is an non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible.
-We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
-First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$.
-By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
-Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^0$.
-So if $x^0_j$ is zero, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$.
-Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$.
-Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.
+The proof is in Appendix \ref{lemma4}.
 
-	Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$.
-Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.
-
-	We consider two cases.
-In the first case, we have $z^*_{\ell+1}=0$.
-In this case we have $x^{(\ell+1)}_{\ell+1}=0$.
-Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$.
-Also, $(z^*,w^*)\in P$.
-By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ .
-We have
-	\begin{equation}
-	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
-	\end{equation}
-	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$.
-Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$.
-Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$.
-We claim that $(z,w)\in \IP^{(\ell+1)}$.
-If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$.
-Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
-Consider iteration $j$ of Algorithm \ref{domtoIP}.
-Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.
-We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero.
-However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0.
-This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.
-
-	Now for the second case, assume $z^*_{\ell+1} > 0$.
-We have $x^{(\ell+1)}_{\ell+1}=1$.
-Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e.
-$z_{\ell+1}=1$.
-This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.
-
-	Now consider $(x^{(t)},y^{(t)})$.
-Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$.
-If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$.
-If $x^{(t)} =1$, it must be the case that $z_t > 0$.
-By the argument above there is a point $(z',w')\in \IP^{(t-1)}$.
-We show that $x^{(t)} = z'$.
-Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
-We just need to show that $z'_j = 1$.
-Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.
-\end{proof}
-
-This completes the FDT algorithm.
-
+\iffalse{
 \begin{algorithm}[H]\label{FDTFull}
@@
 	\caption{Fractional Decomposition Tree Algorithm}
-\end{algorithm}
+\end{algorithm}}\fi
 \section{FDT for 2EC}\label{2EC}
@@
 	\label{LPC2EC}
-	Given $x\in \EC(G)$, and $e\in E$ we can find in polynomial time vectors $x^0,x^1$ and $x^2$ and scalars $\gamma_0,\gamma_1$, and $\gamma_2$ such that
-	\begin{itemize}
-		\item[(i)] $\gamma_0 + \gamma_1 +\gamma_2 \geq \frac{ 1}{g_{\EC}}$,
-		\item[(ii)] $x^0,x^1,$ and $x^2$ are in  $ \EC(G)$, 
-		\item[(iii)] $x^0_e=0$, $x^1_e=1$, and $x^2_e=2$,
-		\item[(iv)] $\gamma_0 x^0 + \gamma_1{x}^1  + \gamma_2x^2\leq {x}$,
-		\item[(v)] for $f\in E$ with ${x}_f\geq 1$, we have $x^j_f\geq 1$ for $j=0,1,2$. 
-	\end{itemize}
+	Given $x\in \EC(G)$, and $e\in E$ we can find in polynomial time vectors $x^0,x^1$ and $x^2$ and scalars $\gamma_0,\gamma_1$, and $\gamma_2$ such that: (i) $\gamma_0 + \gamma_1 +\gamma_2 \geq \frac{ 1}{g_{\EC}}$, (ii) $x^0,x^1,$ and $x^2$ are in  $ \EC(G)$, (iii) $x^0_e=0$, $x^1_e=1$, and $x^2_e=2$, (iv) $\gamma_0 x^0 + \gamma_1{x}^1  + \gamma_2x^2\leq {x}$, (v) for $f\in E$ with ${x}_f\geq 1$, we have $x^j_f\geq 1$ for $j=0,1,2$.
 \end{restatable}
@@
 \begin{proof}
-	Consider the following linear programing with variables $\lambda_j$ and $x^j$ for $j=0,1,2$. 
+	Consider the following LP with variables $\lambda_j$ and $x^j$ for $j=0,1,2$. 
 	\begin{align}
@@
 		&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1,\lambda_2 \geq 0
-	\end{align}
-
-	Let $x^j$, $\gamma_j$ for $j=0,1,2$ be an optimal solution solution to the LP above.
+	\end{align}	Let $x^j$, $\gamma_j$ for $j=0,1,2$ be an optimal solution solution to the LP above.
 Let $\hat{x}^{j}=\frac{x^j}{\gamma_j}$ for $j=0,1,2$ where $\gamma_j>0$.
@@
 Observe that  (ii), (iii), (iv), and (v) are satisfied with this choice.
-In order to show that (i) is also satisfied we prove the following claim.
-
+We can also show that $\gamma_0+\gamma_1+\gamma_2\geq \frac{1}{g_{\EC}}$, which means that (i) is also satisfied.
+The proof is similar to the proof of the claim in Lemma \ref{LPClemma}, but we need to replace each $f\in E$ with $x_f\geq 0$ with a suitably long path to ensure that Constraint (\ref{1edges2ec}) is also satisfied.	We skip the details.\iffalse{
 	\begin{claim}\label{CVexists}
@@
 	\end{proof}
-	This concludes the proof.
-\end{proof}
+	This concludes the proof.}\fi \end{proof}
 
 In contrast to FDT for binary MIPs where we round up the fractional variables that are already branched on at each level, in FDT for 2EC we keep all coordinates as they are and preform a rounding procedure at the end.
-Formally, let $L_i$ for $i=1,\ldots,|\sup(x^*)|$ be collections of pairs of feasible points in $\EC(G)$ together with their multipliers.
-Let $t=|\sup(x^*)|$ and assume without loss of generality that $\sup(x^*)=\{e_1,\ldots,e_t\}$.
+Formally, let $L_i$ for $i=1,\ldots,|\spp(x^*)|$ be collections of pairs of feasible points in $\EC(G)$ together with their multipliers.
+Let $t=|\spp(x^*)|$ and assume without loss of generality that $\spp(x^*)=\{e_1,\ldots,e_t\}$.
 
@@
 	The FDT algorithm for 2EC in  polynomial time produces sets $L_0,\ldots,L_t$ of pairs $x\in \EC(G)$ together with multipliers $\lambda$ with the following properties.
-	\begin{enumerate}
-		\item[a.] If $x\in L_i$, then $x_{e_j}=0$ or $x_{e_j}\geq 1$ for $j=1,\ldots,i$,
-		\item [b.] $\sum_{(x,\lambda)\in L_i }\lambda \geq \frac{1}{g_{\EC}^i}$,
-		\item[c.]  $\sum_{(x,\lambda)\in L_i }\lambda x \leq x^*$,
-		\item[d.] $|L_i|\leq t$.
-	\end{enumerate}
+		(a) If $x\in L_i$, then $x_{e_j}=0$ or $x_{e_j}\geq 1$ for $j=1,\ldots,i$, (b) $\sum_{(x,\lambda)\in L_i }\lambda \geq \frac{1}{g_{\EC}^i}$, (c) $\sum_{(x,\lambda)\in L_i }\lambda x \leq x^*$, (d) $|L_i|\leq t$.
 \end{lemma}
+The proof is similar to Lemma \ref{prune}, but we need to use property (i) in Lemma \ref{LPC2EC} to prove that (a) also holds.
+\iffalse{
 \begin{proof}
@@
 	If $|L'|\geq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
-\end{proof}
+\end{proof}	}\fi
 
@@
 Then, we just need to apply Lemma \ref{rounddown} to obtain the 2-edge-connected multigraphs from every solution in $L_t$.
-Notice that since $x$ is an extreme point we have $t\leq 2|V|-3$ \cite{}.
+Notice that since $x$ is an extreme point we have $t\leq 2|V|-1$ \cite{gerard}.
 By Lemma \ref{2ecpruning} we have
@@
 
-\section{Stronger version of Carr-Vempala for covering problems} \label{gap}
+\section{Stronger version of Theorem \ref{CV} for covering problems} \label{gap}
 
@@
 Notice that for a covering problem $\dom(P)=P$.
-We show that for these problems, we can make Theorem \ref{CV} stronger in the following sense.
-
-\tightcuts*
+We show that for these problems, we can make Theorem \ref{CV} stronger in the sense of Theorem\ref{tightcuts}.
 
@@
 \end{lemma}
+\begin{proof}[Proof Sketch]
+
+	\end{proof}
+
+\iffalse{
 \begin{proof}
@@
 Therefore $A_jx^i \geq  A_{j,\ell^*}x^i_{\ell^*}= A_{j,\ell^*}b\geq b$.
-\end{proof}
+\end{proof}}\fi
 \begin{lemma}\label{tightcutcomb}
@@
 
+	We can prove this statement by induction on $i$ and applying Lemma \ref{epsilon} to prove the induction step.
+	\iffalse{
 	We proceed by induction on $i$.
@@
 	\end{align*}
-	It is easy to show that  multipliers above are convex.
+	It is easy to show that  multipliers above are convex.}\fi
 \end{proof}
@@
 
+	\bibitem{goemans}
+	Michel~X. Goemans.
+	\newblock Worst-case comparison of valid inequalities for the {TSP}.
+	\newblock {\em Math. Program.}, 69(2):335--349, August 1995.
+
 	\bibitem{cons-cara}
@@
 \end{thebibliography}
+
+\appendix
+\section{Proof of Lemma 4}\label{lemma4}
+	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of Algorithm \ref{domtoIPalg} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
+	\begin{align*}
+	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
+	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
+	\end{align*}
+	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible.
+We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
+First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$.
+By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
+Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
+So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$.
+Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$.
+Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.
+
+	Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$.
+Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.
+
+	We consider two cases.
+In the first case, we have $z^*_{\ell+1}=0$.
+In this case we have $x^{(\ell+1)}_{\ell+1}=0$.
+Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$.
+Also, $(z^*,w^*)\in P$.
+By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ .
+We have
+	\begin{equation}
+	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
+	\end{equation}
+	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$.
+Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$.
+Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$.
+We claim that $(z,w)\in \IP^{(\ell+1)}$.
+If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$.
+Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
+Consider iteration $j$ of Algorithm \ref{domtoIPalg}.
+Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.
+We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero.
+However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0.
+This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.
+
+	Now for the second case, assume $z^*_{\ell+1} > 0$.
+We have $x^{(\ell+1)}_{\ell+1}=1$.
+Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e.
+$z_{\ell+1}=1$.
+This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.
+
+	Now consider $(x^{(t)},y^{(t)})$.
+Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$.
+If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$.
+If $x^{(t)} =1$, it must be the case that $z_t > 0$.
+By the argument above there is a point $(z',w')\in \IP^{(t-1)}$.
+We show that $x^{(t)} = z'$.
+Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
+We just need to show that $z'_j = 1$.
+Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.
 \end{document}

### 2018-11-19 IPCO format/2ECFDT.tex
broked main body into pieces

--- 2018-11-18 IPCO format/FDT.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-
-\documentclass[runningheads]{llncs}
-%
-\usepackage{graphicx}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
-
-\begin{document}
-%
-\title{FDT\thanks{Supported by organization x.}}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{Robert Carr\inst{1}\orcidID{} \and
-Arash Haddadan\inst{2}\orcidID{} \and
-Cynthia Phillips\inst{3}\orcidID{}}
-%
-\authorrunning{R. Carr, A. Haddadan, C. Phillips}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-\institute{University of New Mexico, Albuquerque NM 87131, USA\\
-\email{bobcarr@unm.}\\   \and
-Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
-\email{ahaddada@cmu.edu}\and
-Sandia National Laboratories, Albuquerque, NM 87185, USA\\
-\email{caphill@sandia.gov}}
-%
-\maketitle              % typeset the header of the con	tribution
-%
-\begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
-
-\keywords{First keyword  \and Second keyword \and Another keyword.}
-\end{abstract}
-%
-%
-%
-
-\section{Introduction}
-Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, is a classic NP-hard problem \cite{GJ79}.
-In fact it is NP-hard in general to determine if there is a feasible solution to an MILP problem \cite{GJ79}.
-However, intelligent branch-and-bound strategies allow commercial and open-source MIP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.
-Modeling combinatorial optimization problems with MILPs also started the very popular area of LP-based approximation algorithms.
-
-Consider the set of point described by a set 
-\begin{equation}
-S(A,G,b)= \{(x,y)\in \bbbz^{n}\times \bbbr^p\;:\; Ax+Gy\geq b\}  \label{S}
-\end{equation}
-and the  linear relaxation of set $S(A,G,b)$,
-\begin{equation}
-P(A,G,b) = \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b\}. \label{P}
-\end{equation}
-
-To make the notation simpler we use $I=(A,G,b)$, i.e.
-an instance of the formulation.
-Then we use $S(I)$ and $P(I)$ to denote $S(A,G,b)$ and $P(A,G,b)$, respectively.
-Notice that $\min \;\{cx:\; (x,y) \in S(I)\}$ is in fact an MILP problem and $\min \;\{cx:\;(x,y)\in P(I) \}$ is lower bound provided from the LP relaxation.
-Let $z_{IP}(I,c)$ and $z_{LP}(I,c)$ be the optimal solution to these problems, respectively.
-
-Many researchers (see \cite{vazirani,sw}) have developed polynomial time algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$ for some $C$ which can be a constant number or dependent on some parameter of the MILP, e.g.
-$O(\log(n))$.
-However, for many combinatorial optimization problems there is a limit to such techniques.
-Let $g_I= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$.
-Parameter $g_I$ depends on set $S(I)$ and the linear constraints in (\ref{S}) and is known as the \textit{integrality gap} of the formulation for instance $I$.
-It is easy to see, that we cannot hope to find solutions for the MILP with objective values better than $g_I\cdot z_{LP}(I,c)$.
-More generally we can define the integrality gap for a class of instances $\mathcal{I}$.
-In this case, the integrality gap for problem $\mathcal{I}$ is
-\begin{equation}
-g_\mathcal{I} = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}
-\end{equation}
-
-For example, in the problem of finding a minimum weight 2-edge-connected multigraph, the gap of the the natural formulation, constraining every cut to be crossed at least twice, is at most $\frac{3}{2}$ \cite{Wolsey1980} and at least $\frac{6}{5}$ \cite{carr-ravi}.
-Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation.
-If we have $g_I=1$, $P(I)=\conv(S(I))$ and $P(I)$ is an \textit{integral} polyhedron.
-There are many interesting examples of such formulations such as spanning tree polytope and the perfect matching polytope \cite{schrijver}.
-For such problems we know how to write a vector $x\in P(I)$ as convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.
-
-\begin{proposition}\label{cara}
-	If $g_I=1$, then for $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$.
-Moreover, we can find such a convex combination in polynomial time.
-\end{proposition}
-
-Now assume $1<g<\infty$. Denote by $\dom(P(I))$ be the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$.
-
-A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}, which is a generalization of Goemans proof for blocking polyhedra \cite{goemans}.
-
-\begin{theorem}[Carr, Vempala \cite{CV}] \label{CV}
-	Let $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(S(I))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ if and only if $g_I \leq C$.
-\end{theorem}
-
-In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
-This points to an interesting open question.
-
-\begin{question}\label{question1}
-	Assume reasonable complexity assumptions (such as UGC or $\textrm{P}\neq \textrm{NP}$).
-Given instance $I$ with $1<g_I<\infty$ and $(x,y)\in P(I)$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(\conv(S(I)))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_Ix$ in polynomial time?
-\end{question}
-
-This seems to be a very hard question. A more specific question is of more interest.
-
-\begin{question}\label{question2}
-	Assume reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g_{\mathcal{I}}<\infty$, and $(x,y)\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_{\mathcal{I}}x$ in polynomial time?
-\end{question}
-Although Question \ref{question2} is wide open, for some problems $\mathcal{I}$ there are polynomial time algorithms closing the gap.
-For example, for generalized Steiner forest problem \cite{jain} gave an LP-based 2-approximation algorithm.
-The gap for this problem is also lower bounded by 2.
-Same holds for the set covering problem \cite{randomizedrounding}.
-In fact, for set cover the approximation algorithm achieving the same factor as the integrality gap lower bound, is a \textit{randomized rounding} algorithm.
-Rhagavan and Thompson \cite{randomizedrounding} showed that this technique acheives provably good approximation for many combinatorial optimization problems.
-
-One key step, in answering Question \ref{question1} and \ref{question2} is being able to find a solution in $S(I)$.
-In fact, for general $I$ it is NP-hard to even decide if $S(I)$ is empty or not.
-There are a number of heuristics for this purpose, such as the feasibility pump heuristic \cite{fp1,fp2}.
-These heuristics are often very effective and fast in practice, however, they can sometimes fail in finding a feasible solution.
-In addition these algorithms do not provide any bounds on the quality of the solution they find.
-\subsection{Our results}
-In this paper we study Theorem \ref{CV} and the natural questions that follow from it (Questions \ref{question1} and \ref{question2}).
-
-We give a general approximation framework for solving $\{0,1\}$-MILPs.  Consider the set of point described by a set 
-\begin{equation}
-S(I)= \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
-\end{equation}
-and a linear relaxation of set $S$
-\begin{equation}
-P(I) = \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
-\end{equation}
-For a vector $x\in \bbbr^n$ such that $(x,y)\in P(I)$ for some $y\in \bbbr^p$, let $\spp(x)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.
-
-\begin{restatable}{theorem}{binaryFDT}
-	\label{binaryFDT}
-	Assume $1\leq g_I 	<\infty$. 	
-	The FDT algorithm, given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\spp(x^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g_I^{|\spp(x^*)|}$.
-\end{restatable}
-
-Notice, that the FDT algorithm needs to find feasible solutions to any MILP with finite gap. This can be of independent interest.
-\begin{restatable}{theorem}{DomToIP}
-	\label{domtoIP}
-	Assume $1\leq g_I < \infty$. The DomToIP algorithm finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
-\end{restatable}
-
-In attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem.
-In this problem we want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
-For this problem the natural linear programming relaxation is
-\begin{equation}\label{2ECpol}
-\EC(G)= \{x\in \bbbr_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
-We prove the following theorem.
-
-\begin{restatable}{theorem}{FDTEC}
-	\label{FDT2EC}
-	Let $G=(V,E)$ and $x$ be an extreme point of  $\EC(G)$.
-The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq O(|V|)$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g_{\EC}^{O(|V|)}$, where $g_{\EC}$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol})
-\end{restatable}
-
-Although the bound guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are very large for large problems, we show that in practice, the algorithm works very well providing approximation ratios that are far better than the theoretical bound in the theorem statements.
-We examine FDT for binary MILPs for problems such as the tree augmentation problem (TAP) and we apply FDT for 2EC on some interesting and ``hard to decompose" points in the linear relaxation.
-
-Finally we give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems.
-For this purpose assume $P= \{x\in \bbbr^n_{\geq 0}: Ax\geq b\textbf{1}, x \leq b\textbf{1}\}$, $S= P\cap \bbbz^n$, and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$.
-Examples of such problems include the 2-edge-connected multigraph problem, the tree augmentation problem, and many others.
-
-\begin{restatable}{theorem}{tightcuts}
-	\label{tightcuts}
-	Let $x\in P$, there exists $\theta\in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i = 1$ and $\tilde{x}^i \in S$ for $i=1,\ldots,k$ such that \begin{itemize}
-		\item for $\ell\in \{1,\ldots,n\}$, if $x_\ell =0$, then $\tilde{x}^i_\ell=0$ for $i =1,\ldots,k$, i.e. $\tilde{x}^i$ is in the support of $x$,
-		\item we have $Cb = C\cdot A_j x \geq A_j (\sum_{i=1}^{k}\theta_i\tilde{x}^i)$, for $j$ such that $A_j x =b$,  
-	\end{itemize}
-	if and only if $C\geq g$.
-\end{restatable}
-
-This means in order to prove an upper bound on the integrality gap of a covering problem, we need to show there is a convex combination of integer feasible points that is ``cheap'' on all tight cuts.
-Notice that Theorem \ref{CV} requires the certificate convex combination to be ``cheap" on every single variable.
-
-\subsection{Notations}
-For vectors $x,y\in \bbbr_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$.
-For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$.
-Let $\textbf{1}$ be the vector of all ones of a suitable dimension.
-For a set $S$ of vectors in $\bbbr_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.
-
-\section{FDT on binary MIPs}
-\label{binaryfdt}
-
-In this section we present the fractional decomposition tree (FDT) algorithm and prove its correctness.
-
-Consider a formulation instance $I=(A,G,b)$, set 
-\begin{equation}
-S(I)= \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
-\end{equation}
-and its linear relaxation
-\begin{equation}
-P(I) = \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
-\end{equation}
-Also assume we are given a point $(x^*,y^*)\in P(I)$.
-For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
-In this section, we prove Theorem \ref{binaryFDT}.
-One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{domtoIP} that we will also prove in this section.
-
-Although the theoretical worst-case upper bound on $C$ in the statement of Theorem \ref{binaryFDT} can be very large, we will show that in practice $C$ can be really small and hence FDT can provide good LP-based approximation algorithms in many cases.
-We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.
-In the remainder of this section we explain the FDT algorithm and prove Theorem \ref{binaryFDT}.
-For simplicity in the notation we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively.
-Let $t=|\spp(x^*)|$.
-We assume without loss of generality that $\spp(x^*)= \{1,\ldots,t\}$.
-
-We begin with the following lemmas that show how the FDT algorithm branches on a variable.
-\begin{lemma}\label{LPClemma}
-	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$,
-		,(iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
-\end{lemma}
-
-\begin{proof} 
-	Consider the following linear program which we denote by $\LPC(\ell,x',y')$. The variables of $\LPC(\ell,x',y')$ are $\gamma_0,\gamma_1$ and $(x^0,y^0)$ and $(x^1,y^1)$. 
-	\begin{align}
-		\LPC(\ell,x',y')\quad\quad& \max\quad \;\lambda_0+\lambda_1\\
-		&\;\text{s.t.} \quad Ax^j + Gy^j\geq b\lambda_j & \mbox{ for $j=0,1$} \label{feasibility}\\
-		&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq \lambda_j &\mbox{ for $j=0,1$}\label{bound}\\
-		&\;{\color{white}{\text{s.t.}} }\quad x^0_\ell = 0,\; x^1_\ell =\lambda_1\label{branchcoordinate}\\
-		&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1 \leq x'\label{packing}\\
-		&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1 \geq 0
-	\end{align}
-
-	Let $(x^0,y^0),(x^1,y^1)$, and $\gamma_0,\gamma_1$ be an optimal solution solution to the LP above.
-Let $(\hat{x}^0,\hat{y}^0) = (\frac{x^0}{\gamma_0},\frac{y^0}{\gamma_0})$, $(\hat{x}^1,\hat{y}^1) = (\frac{x^1}{\gamma_1},\frac{y^1}{\gamma_1})$.
-Observe that  (ii), (iii), (iv) are satisfied with this choice.
-In order to show that (i) is also satisfied we prove the following claim.
-
-	\begin{claim}\label{CVexists}
-		We have $\gamma_0 + \gamma_1\geq \frac{1}{g}$.
-	\end{claim}
-	\begin{proof}
-		We show that there is a feasible solution that achieves the objective value of $\frac{1}{g}$.
-By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $(\tilde{x}^i,\tilde{y}^i)\in S$ for $i=1,\ldots,k$ such that
-		$\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$.
-
-		\begin{equation}\label{splitting}
-		x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
-		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}
-		\end{equation}
-		For $j=0,1$, let $(x^j,y^j) = \sum_{i\in [k]:\tilde{x}^i_\ell=j} \frac{\theta_i}{g}(\tilde{x}^i,\tilde{y}^i)$.
-Also let $\lambda_0=\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g}$ and $\lambda_1 = \sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g}$.
-Note that $\lambda_0+\lambda_1 = \frac{1}{g}$.
-Constraint (\ref{packing}) is satisfied by Inequality (\ref{splitting}).
-Also, for $j=0,1$ we have
-		\begin{equation}
-		Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \geq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
-		\end{equation}
-		Hence, Constraints (\ref{feasibility}) holds.
-Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$.
-The rest of the constraints trivially hold.
-	\end{proof}
-	This concludes the proof.	
-\end{proof}
-
-We now show if $x'$ in the statement of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
-\begin{lemma}\label{round-up}
-	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\frac{ 1}{g}\leq \gamma_0 + \gamma_1  \leq 1$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
-		x'$,(v) $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
-\end{lemma} 
-\begin{proof}
-	By Lemma \ref{LPClemma} we can find $(\bar{x}^0,\bar{y}^0)$, $(\bar{x}^1,\bar{y}^1)$, $\gamma_0$ and $\gamma_1$ that satisfy (i), (ii), (iii), and (iv).
-We define $\hat{x}^0$ and $\hat{x}^1$ as follows.
-For $i=0,1$, for $j=1,\ldots,\ell-1$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,t$ let $\hat{x}^i_j = \bar{x}^i_j$.
-We now show that $(\hat{x}^0,\bar{y}^0)$, $(\hat{x}^1,\bar{y}^1)$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions.
-Note that conditions (i), (ii), (iii), and (v) are trivially satisfied.
-Thus we only need to show (iv) holds.
-We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$.
-If $j=\ell,\ldots,t$, then this clearly holds.
-Hence, assume $j\leq \ell-1$.
-By the property of $x'$ we have $x'_j\in \{0,1\}$.
-If $x'_j= 0$, then by Constraint (\ref{packing}) we have $\bar{x}^0_j = \bar{x}^1_j=0$.
-Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds.
-Otherwise if $x'_j = 1$, then we have
-	$\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.$ 
-	Therefore (v) holds.
-\end{proof}
-The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs.
-Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$.
-The solutions contained in the nodes of the tree become progressively more integral at each level.
-Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$.
-We will later see how we can turn these into points in $S$.
-
-Let us define the FDT algorithm more formally.
-The algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm.
-The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree.
-The points in the leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.
-
-\begin{lemma}\label{prune}
-	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $(x,y)\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$:
-		(a) If $(x,y)\in L_i$, then $x_j \in \{0,1\}$ for $j=1,\ldots,i$, i.e.
-the first $i$ coordinates of a solution in level $i$ are integral, (b) $\sum_{[(x,y),\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$, (c) $\sum_{[(x,y),\lambda]\in L_i}\lambda x \leq x^*$, (d) $|L_i|\leq t$.
-\end{lemma}
-\begin{proof}
-	We prove this lemma using induction but one can clearly see how to turn this proof into a polynomial time algorithm.
-Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $(x^*,y^*)$ and multiplier 1.
-It is easy to check all the requirements in the lemma are satisfied for this choice.
-
-	Suppose by induction that we have constructed sets $L_0,\ldots,L_i$.
-Let the solutions in $L_i$ be $(x^j,y^j)$ for $j=1,\ldots,k$ and $\lambda_j$ be their multipliers, respectively.
-For each $j= 1,\ldots,k$ by Lemma \ref{round-up} (setting $(x',y')= (x^j,y^j)$ and $\ell = i+1$) we can find $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and $\lambda^0_j$, $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}.
-Define $L'$ to be the set of nodes with solutions $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and multipliers  $\lambda_j\lambda^0_j$, $\lambda_j\lambda^1_j$, respectively, for $j=1,\ldots,k$.
-It is easy to check that \iffalse{
-	Notice that for each $j= 1,\ldots,k$ by property (v) in Lemma \ref{round-up} we have $x_h^{j0}, x_h^{j1}\in \{0,1\}$ for $h = 0,\ldots,i+1$. We also have
-	\begin{align*}
-		\sum_{[(x,y),\lambda]\in L'} \lambda & =  \sum_{j=1}^{k} \lambda_j\lambda^0_j+\lambda_j\lambda^1_j&\\
-		& \geq \sum_{j=1}^{k} \frac{\lambda_j}{ g} & (\text{By property (i) in Lemma \ref{round-up}})\\
-		& \geq \frac{1}{g} \sum_{[(x,y),\lambda]\in L_i}\lambda&\\
-		& \geq \frac{1}{g^{i+1}}.&(\text{By induction hypothesis})	 
-	\end{align*} 
-	Also 
-	\begin{align*}
-		\sum_{[(x,y),\lambda]\in L'}\lambda x & =  \sum_{j=1}^{k} \lambda_j\big(\lambda^0_jx^{j0}+\lambda^1_jx^{j1}\big)&\\ 
-		& \leq \sum_{j=1}^{k} \lambda_j x^j  & (\text{By property (iv) in Lemma \ref{round-up}})\\
-		& \leq \sum_{[(x,y),\lambda]\in L_i}\lambda x&\\
-		& \leq x^*.&(\text{By induction hypothesis})	 
-	\end{align*} \fi set $L'$ is a suitable candidate for $L_{i+1}$, i.e.
-set $L'$ satisfies (a), (b) and (c).
-However we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$.
-We call the following linear program $\prun(L')$.
-Let $L' = \{[(x^1,y^1),\gamma_1],\ldots,[(x^{2k},y^{2k}),\gamma_{2k}]\}$.
-The variables of $\prun(L')$ is a scalar variable $\theta_j$ for each node $j$ in $L'$.
-	\begin{align}
-		\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{2k} \theta_j\\
-		&\;\text{s.t.} \quad \;\;\sum_{j=1}^{2k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
-		&\;{\color{white}{\text{s.t.}} }\quad  \;\quad\quad\theta \geq 0\label{nonneg}
-	\end{align}
-
-	Notice that $\theta = \gamma$ is in fact a feasible solution to $\prun(L')$.
-Let $\theta^*$ be the optimal vertex point solution to this LP.
-Since the problem is in $\bbbr^{2k}$,  $\theta^*$ has to satisfy $2k$ linearly independent constraints at equality.
-However, there are only $t$ constraints of type (\ref{packs}).
-Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero.
-We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,2k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma.
-Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$.
-Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$.
-\end{proof}
-The leaves of the FDT tree,  $L_t$, have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$.
-Our goal to now replace these leaves solutions in $\dom(P)$ with solutions in $S$.
-To this end, we need to reduce some variables with value of 1 into variables of value 0 and obtain feasibility in the meantime.
-We introduce a procedure that given a  point $(x,y)\in \dom(P)$ with $x\in \{0,1\}^n$ outputs a point $z\leq x$ with $z\in \{0,1\}^n$ such that $(z,w)$ is in $S$ for some vector $w\in \bbbr^p$.
-
-The algorithm ``fixes" the variables iteratively, from $x_1$ to $x_t$.
-Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$.
-Now consider the following linear program.
-The variables of this LP are the $z\in \bbbr^n$ variables and $w\in \bbbr^p$.
-\begin{align}
-	\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
-	&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
-	&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
-	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
-	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
-\end{align}
-
-If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$.
-Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$.
-Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$.
-This procedure is the DomToIP algorithm.
-\iffalse{
-\begin{algorithm}[H]
-	\KwIn{$(x,y)\in \dom(S)$}
-	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
-	$x^{(0)}\leftarrow x$\\
-	\For{$\ell = 0$ \textbf{to} $t-1$}{
-		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
-		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
-		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
-		\eIf{$\eta = 0$}{
-			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
-		}{
-			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
-		}
-	}
-	\label{domtoIPalg}
-	\caption{The DomToIP algorithm}
-\end{algorithm}
-}\fi
-The following lemma proves Theorem \ref{domtoIP}.
-\begin{lemma}
-	Given $(x,y)\in \dom(P)$, DomToIP algorithm correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
-\end{lemma}
-The proof is in Appendix \ref{lemma4}.
-
-\iffalse{
-\begin{algorithm}[H]\label{FDTFull}
-	\KwIn{$P= \{(x,y)\in \bbbr^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \bbbr^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
-	\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
-	$L^0\leftarrow [(x^*,y^*),1]$\\
-	\For{$i=1$ \textbf{to} $t$}{
-		$L'\leftarrow \emptyset$\\
-		\For{$[(x,y),\lambda] \in L^i$}{
-			Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
-			$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
-		}
-		Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
-	}
-	\For{$[(x,y),\lambda] \in L^t$}{
-		Apply Algorithm \ref{domtoIP} to $(x,y)$ to obtain $(z,w)\in S$\\
-		$F \leftarrow F \cup \{[(z,w),\lambda]\}$
-	}
-	\textbf{return} $F$
-	\caption{Fractional Decomposition Tree Algorithm}
-\end{algorithm}}\fi
 \section{FDT for 2EC}\label{2EC}
@@
 \end{align*}
-
-\section{Stronger version of Theorem \ref{CV} for covering problems} \label{gap}
-
-Theorem \ref{CV} characterizes the integrality gap as the smallest number such that for any point $x\in \dom(P)$, $gx$ dominates a convex combination of points in $S$, i.e.
-there exists convex combination $\sum_{i=1}^{k}\lambda_ix^i \leq gx$.
-In a covering problem, we assume that matrix $A$ in the description of $P$ is a non-negative matrix, hence if $y\geq x$ and $x\in P$ we have $y\in P$.
-We also assume the right hand side vector in (\ref{P}) is of the form $b\textbf{1}$, i.e.
-it is a uniform vector.
-Finally we assume we have bound constraints $x\leq b\textbf{1}$.
-This class of problems include a broad class of problems.
-Notice that for a covering problem $\dom(P)=P$.
-We show that for these problems, we can make Theorem \ref{CV} stronger in the sense of Theorem\ref{tightcuts}.
-
-In other words, the integrality gap is the smallest number such that for any $x\in P$, there exists a convex combination $y=\sum_{i=1}^{k}\lambda_ix^i$, such that $A_jy\leq g(A_jx)$ for all $j$ such that $A_jx=b$.
-
-Notice that the proof of this theorem, same as Theorem \ref{CV}, does not imply a polynomial time algorithm.
-
-Observe that if $C\geq g$, by Theorem \ref{CV}, there is a convex combination of points in $S$ that is dominated by $Cx$, i.e.
-there exists $\theta\in [0,1]^{k}$, where $\sum_{i=1}^{k}\theta_i=1$, and $x^i\in S$, such that $\sum_{i=1}^{k}\theta_ix^i\leq gx$.
-The same convex combination also trivially satisfies both requirements in Theorem \ref{tightcuts}.
-The more interesting direction is the converse.
-We begin with the following theorem.
-Suppose $v^1,\ldots,v^r$ are the extreme points of $P$.
-Assume for each $i=1,\ldots,r$, there exists a convex combination of points in $S$, namely $\sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell$ such that $A_j \sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell \leq CA_jv^i$ for $j$ such that $A_jv^i = b$.
-Let $z^i = \sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell$.
-\begin{lemma}\label{epsilon}
-	For any  $i\in\{1,\ldots,r\}$, there exists $\epsilon_i >0$ and ${x^i}\in P$ where ${x^i}\leq \frac{Cv^i-\epsilon_i z^i}{C(1-\epsilon_i)}$.
-\end{lemma}
-\begin{proof}[Proof Sketch]
-
-	\end{proof}
-
-\iffalse{
-\begin{proof}
-
-	Let $u^i(\epsilon) = \frac{Cv^i-\epsilon z^i}{C(1-\epsilon)}$. For $j\in \{1,\ldots,m\}$, let $t_j = A_jz^i-Cb$ and $s_j=A_jv^i-b$. 
-	Assume $\epsilon <1$. For $j\in \{1,\ldots,m\}$ such that $A_jz^i\leq Cb$, i.e. $t_j\leq 0$ (this includes $j$ such that $A_jv^i=b$, i.e. $s_j=0$) we have
-	\begin{equation}
-	A_j u^i(\epsilon) = \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}\geq \frac{Cb-\epsilon Cb}{C(1-\epsilon)}=b
-	\end{equation}
-	Assume $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$.
-Notice that $\max_{j: t_j >0} \frac{s_j}{t_j}>0$ since for $j$ such that $t_j>0$, we have $A_jz_i > Cb$ which implies that $A_jv^i>b$, so $s_j>0$.
-For $j$ such that $t_j>0$ we have
-	\begin{align*}
-		A_ju^i(\epsilon) &= \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}& \\
-		&= \frac{C(b+s_j)-\epsilon (Cb+t_j)}{C(1-\epsilon)}&\\
-		&= b+ \frac{Cs_j-\epsilon t_j}{C(1-\epsilon)}&\\
-		&\geq b & (\epsilon  \leq C\cdot  \frac{s_j}{t_j}, \mbox{ and } \epsilon <1, \mbox{ so } \frac{Cs_j-\epsilon t_j}{C(1-\epsilon)}\geq 0 )
-	\end{align*} 
-	Therefore if $\epsilon \leq 1$ and $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$ we have $Au^i(\epsilon)\geq \textbf{1}b$.
-Next, we show that we can choose $\epsilon$ so that $ u^i(\epsilon)\geq 0$.
-
-	For $\ell\in \{1,\ldots,n\}$, if $z^i_\ell=0$, then we have $u_\ell^i(\epsilon) = \frac{Cv_\ell^i}{C(1-\epsilon)}\geq 0$, since $v^i_\ell\geq 0$ and $\epsilon <1$.
-Otherwise we have $z^i_\ell>0$.
-Assume $\epsilon \leq C\cdot \min_{ \ell:z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}$.
-Notice that for $\ell$ such that $z^i_\ell>0$, we have $v^i_\ell>0$ since $z^i$ lies in the support of $v^i$ by assumption.
-This means that $\min_{\ell:z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}>0$.
-Now, for $\ell$ such that $z^i_\ell>0$, we have $u^i_\ell(\epsilon) = \frac{Cv_\ell^i-\epsilon z_\ell^i}{C(1-\epsilon)}\geq 0$ by choice of $\epsilon$.
-
-	Define $\epsilon_i =\min\{1, C\cdot \min_{j: t_j >0}\frac{s_j}{t_j},C\cdot\min_{\ell: z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}\}$.
-By the arguments above $Au^i(\epsilon_i)\geq \textbf{1}b$ and $u^i(\epsilon_i)\geq 0$.
-Define $x^i$ as follows: For each $j\in \{1,\ldots,m\}$, if $u^i_j(\epsilon_i)\leq b$, then let $x^i_j=u^i_j(\epsilon_i)$, otherwise let $x^i_j=b$.
-We need to show that $x^i\in P$.
-Note that clearly $x^i\geq 0$, hence we only need to show that $Ax^i\geq \textbf{1}b$.
-Suppose for contradiction there is $j\in \{1,\ldots,m\}$ such that $A_jx^i <b$.
-Since $u^i(\epsilon)\in P$, there must be $\ell^*\in\{1,\ldots,n\}$ such that $u^i_{\ell^*}(\epsilon)>b$, and $A_{j,\ell^*}>0$.
-But this means that $A_{j,\ell^*}\geq 1$ and $x^i_{\ell^*}=b$.
-Therefore $A_jx^i \geq  A_{j,\ell^*}x^i_{\ell^*}= A_{j,\ell^*}b\geq b$.
-\end{proof}}\fi
-\begin{lemma}\label{tightcutcomb}
-	There exists a convex combination of point in $S$ that is dominated by $Cv^i$ for $i=1,\ldots,r$.
-\end{lemma}
-\begin{proof}
-
-	We prove something slightly stronger.
-We show that for $i\in\{1,\ldots,r\}$, and for $j=1,\ldots,i$, the vector $Cv^j$ dominates  a convex combination of $z^1,\ldots,z^i$ and $Cv^{i+1},\ldots,Cv^r$.
-Note that this is enough to prove our statement since for $i=r$, the statement implies that $Cv^j$ dominates a convex combination of $z^1,\ldots,z^r$ for $j=1,\ldots,r$.
-
-	We can prove this statement by induction on $i$ and applying Lemma \ref{epsilon} to prove the induction step.
-	\iffalse{
-	We proceed by induction on $i$.
-If $i=1$, we just need to show that $Cv^1$ is dominated by a convex combination of $z^1$ and $Cv^2,\ldots,Cv^r$.
-By Lemma \ref{epsilon}, there exists $x^1\leq  \frac{Cv^1-\epsilon_1z^1}{C(1-\epsilon_1)}$.
-We have $x^1\in P$, so we can write $x^1$ as convex combination of $v^1,\ldots, v^r$.
-We have
-	\begin{equation}
-	Cv^1 \geq  \epsilon_1z^1 + C(1-\epsilon_1)x^1 \geq \epsilon_1z^1 + C(1-\epsilon_1) \sum_{\ell=1}^{r}\lambda^1_\ell v^\ell.
-	\end{equation}
-	Hence,
-	\begin{equation}
-	Cv^1 \geq \frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}\cdot z^1 + (1-\epsilon_i)\sum_{\ell=2}^{r} \frac{\lambda^1_\ell}{1-(1-\epsilon_1)\lambda_1^1}\cdot Cv^\ell.
-	\end{equation}
-	Observe that $\frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}$ and $(1-\epsilon_1)\frac{\lambda^1_\ell}{1-(1-\epsilon_1)\lambda_1^1}$ for $\ell=2,\ldots,r$ form convex multipliers, so the base case holds.
-
-	Now consider $i\in \{1,\ldots,r-1\}$. By induction, for $j=1,\ldots,i$ we have
-	\begin{equation}\label{IHs}
-	Cv^j \geq  \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell + \sum_{\ell=i+1}^{r}\theta^{j}_{\ell}Cv^\ell.
-	\end{equation}
-	Suppose we are able to show 
-	\begin{equation}\label{claim} 
-	Cv^{i+1} \geq \sum_{\ell=1}^{i+1} \mu_\ell z^\ell + \sum_{\ell=i+2}^{r}\mu_{\ell}Cv^\ell,\end{equation} 
-	where $\mu\geq 0$, and $\sum_{\ell=1}^{r}\mu_{\ell}=1$. Then for $j=1,\ldots,i$ we have
-	\begin{align*}
-		Cv^j& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\theta^{j}_{i+1}Cv^{i+1}+  \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell.& (\mbox{By } \ref{IHs})\\
-		& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\sum_{\ell=1}^{i+1}\theta^{j}_{i+1}\mu_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_{i+1}\mu_{\ell}Cv^\ell +   \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell.& (\mbox{By } \ref{claim})\\
-		&= \sum_{\ell=1}^{i} (\theta^j_\ell+\mu_{\ell}\theta^j_{i+1}) z^\ell + \mu_{j+1}\theta^j_{i+1}z^{i+1} + \sum_{\ell=i+2}^{r} (\theta^j_\ell+\mu_\ell\theta^j_{i+1})Cv^\ell.&
-	\end{align*} 
-	It is easy to see that the multipliers above are convex.
-Thus, we only need to show the convex combination in (\ref{claim}) exists.
-This will be similar to what we did in the base case.
-By Lemma \ref{epsilon}, there exists $\epsilon_{i+1}$ and $x^{i+1}$ such that
-	\begin{align*}
-		Cv^{i+1}&\geq \epsilon_{i+1}z^{i+1}+ C(1-\epsilon_{i+1})x^{i+1}\\
-		&\geq \epsilon_{i+1}z^{i+1}+ (1-\epsilon_{i+1})\sum_{\ell=1}^{k}\lambda_{\ell}Cv^\ell
-	\end{align*}
-	Applying induction we can replace $Cv^j$ by $ \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell + \sum_{\ell=i+1}^{r}\theta^{j}_{\ell}Cv^\ell$ for $j=1,\ldots,i$. 
-	This means
-	\begin{align*}
-		(1-(1-\epsilon_{i+1})(\lambda_{i+1}+\sum_{j=1}^{i}\lambda_j\theta^j_{i+1}))Cv^{i+1}&\geq \epsilon_{i+1}z^{i+1}+(1-\epsilon_{i+1})\sum_{j=1}^{i}\lambda_j (\sum_{\ell=1}^{i}\theta^j_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_\ell Cv^\ell)\\
-		&+(1-\epsilon_{i+1})(\sum_{j=1}^{i}\lambda_j \lambda^j_{i+1}+\lambda^i_{i+1})C+ (1-\epsilon_{i+1})\sum_{j=i+2}^{r}\lambda_jCv^{j} 
-	\end{align*}
-	It is easy to show that  multipliers above are convex.}\fi
-\end{proof}
-
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
-%
-\begin{thebibliography}{10}
-
-	\bibitem{carr-ravi}
-	Robert Carr and R.~Ravi.
-	\newblock A new bound for the 2-edge connected subgraph problem.
-	\newblock In {\em Proceedings of the 6th International IPCO Conference on
-		Integer Programming and Combinatorial Optimization}, pages 112--125, London,
-	UK, UK, 1998. Springer-Verlag.
-
-	\bibitem{CV}
-	Robert Carr and Santosh Vempala.
-	\newblock On the held-karp relaxation for the asymmetric and symmetric
-	traveling salesman problems.
-	\newblock {\em Mathematical Programming}, 100(3):569--587, Jul 2004.
-
-	\bibitem{gerard}
-	G{\'e}rard Cornu{\'e}jols, Jean Fonlupt, and Denis Naddef.
-	\newblock The traveling salesman problem on a graph and some related integer
-	polyhedra.
-	\newblock {\em Mathematical Programming}, 33(1):1--27, Sep 1985.
-
-	\bibitem{fp1}
-	Matteo Fischetti, Fred Glover, and Andrea Lodi.
-	\newblock The feasibility pump.
-	\newblock {\em Mathematical Programming}, 104(1):91--104, Sep 2005.
-
-	\bibitem{fp2}
-	Matteo Fischetti and Domenico Salvagnin.
-	\newblock Feasibility pump 2.0.
-	\newblock {\em Mathematical Programming Computation}, 1(2):201--222, Oct 2009.
-
-	\bibitem{GJ79}
-	M.R. Garey and D.S. Johnson.
-	\newblock {\em Computers and Intractability -- A Guide to the Theory of
-		{NP}-Completeness}.
-	\newblock Freeman, San Francisco, CA, 1979.
-
-	\bibitem{goemans}
-	Michel~X. Goemans.
-	\newblock Worst-case comparison of valid inequalities for the {TSP}.
-	\newblock {\em Math. Program.}, 69(2):335--349, August 1995.
-
-	\bibitem{cons-cara}
-	Martin Gr{\"o}tschel, L{\'a}szl{\'o} Lov{\'a}sz, and Alexander Schrijver.
-	\newblock {\em Geometric Algorithms and Combinatorial Optimization}, volume~2.
-	\newblock Second corrected edition edition, 1993.
-
-	\bibitem{jain}
-	Kamal Jain.
-	\newblock A factor 2 approximation algorithm for the generalized steiner
-	network problem.
-	\newblock In {\em Proceedings of the 39th Annual Symposium on Foundations of
-		Computer Science}, FOCS '98, pages 448--, Washington, DC, USA, 1998. IEEE
-	Computer Society.
-
-	\bibitem{randomizedrounding}
-	Prabhakar Raghavan and Clark~D. Tompson.
-	\newblock Randomized rounding: A technique for provably good algorithms and
-	algorithmic proofs.
-	\newblock {\em Combinatorica}, 7(4):365--374, Dec 1987.
-
-	\bibitem{schrijver}
-	A.~Schrijver.
-	\newblock {\em Combinatorial Optimization - Polyhedra and Efficiency}.
-	\newblock Springer, 2003.
-
-	\bibitem{vazirani}
-	Vijay~V. Vazirani.
-	\newblock {\em Approximation Algorithms}.
-	\newblock Springer-Verlag, Berlin, Heidelberg, 2001.
-
-	\bibitem{sw}
-	David~P. Williamson and David~B. Shmoys.
-	\newblock {\em The Design of Approximation Algorithms}.
-	\newblock Cambridge University Press, New York, NY, USA, 1st edition, 2011.
-
-	\bibitem{Wolsey1980}
-	Laurence~A. Wolsey.
-	\newblock {\em Heuristic analysis, linear programming and branch and bound},
-	pages 121--134.
-	\newblock Springer Berlin Heidelberg, Berlin, Heidelberg, 1980.
-
-\end{thebibliography}
-
-\appendix
-\section{Proof of Lemma 4}\label{lemma4}
-	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of Algorithm \ref{domtoIPalg} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
-	\begin{align*}
-	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
-	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
-	\end{align*}
-	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible.
-We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
-First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$.
-By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
-Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
-So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$.
-Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$.
-Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.
-
-	Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$.
-Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.
-
-	We consider two cases.
-In the first case, we have $z^*_{\ell+1}=0$.
-In this case we have $x^{(\ell+1)}_{\ell+1}=0$.
-Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$.
-Also, $(z^*,w^*)\in P$.
-By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ .
-We have
-	\begin{equation}
-	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
-	\end{equation}
-	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$.
-Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$.
-Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$.
-We claim that $(z,w)\in \IP^{(\ell+1)}$.
-If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$.
-Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
-Consider iteration $j$ of Algorithm \ref{domtoIPalg}.
-Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.
-We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero.
-However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0.
-This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.
-
-	Now for the second case, assume $z^*_{\ell+1} > 0$.
-We have $x^{(\ell+1)}_{\ell+1}=1$.
-Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e.
-$z_{\ell+1}=1$.
-This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.
-
-	Now consider $(x^{(t)},y^{(t)})$.
-Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$.
-If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$.
-If $x^{(t)} =1$, it must be the case that $z_t > 0$.
-By the argument above there is a point $(z',w')\in \IP^{(t-1)}$.
-We show that $x^{(t)} = z'$.
-Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
-We just need to show that $z'_j = 1$.
-Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.
-\end{document}

### 2018-11-19 IPCO format/FDT.tex
broked main body into pieces

@@
 \begin{abstract}
-The abstract should briefly summarize the contents of the paper in
-150--250 words.
+We present a new algorithm for finding a feasible solution for a mixed-integer linear program. The algorithm runs in polynomial time and is guaranteed to find a feasible integer solution provided the
+integrality gap is bounded. The algorithm is based on convex decomposition of scaled linear-
+programming relaxations, so in general it provides a suite of integer solutions. Because of the
+relationship between convex decomposition and integrality gaps, this algorithm can be seen as an approximation algorithm. We apply our algorithm our algorithm to a class of 
+fractional extreme points for two known problems in combinatorial optimization: the 2-edge-connected spanning subgraph problem and the tree augmentaion problem.
+These computational experiments show that our algorithm can be used as a tool to evaluate the integrality gap of integer programs with their linear relaxation.
+Finally we provide a stronger characterization of integrality gap for a class of covering problems than that of \cite{goemans}.
 
-\keywords{First keyword  \and Second keyword \and Another keyword.}
+\keywords{Mixed-integer linear programming  \and  Integrality gap \and convex combiniations.}
 \end{abstract}
@@
 %
-
-\section{Introduction}
-Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, is a classic NP-hard problem \cite{GJ79}.
-In fact it is NP-hard in general to determine if there is a feasible solution to an MILP problem \cite{GJ79}.
-However, intelligent branch-and-bound strategies allow commercial and open-source MIP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.
-Modeling combinatorial optimization problems with MILPs also started the very popular area of LP-based approximation algorithms.
-
-Consider the set of point described by a set 
-\begin{equation}
-S(A,G,b)= \{(x,y)\in \bbbz^{n}\times \bbbr^p\;:\; Ax+Gy\geq b\}  \label{S}
-\end{equation}
-and the  linear relaxation of set $S(A,G,b)$,
-\begin{equation}
-P(A,G,b) = \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b\}. \label{P}
-\end{equation}
-
-To make the notation simpler we use $I=(A,G,b)$, i.e.
-an instance of the formulation.
-Then we use $S(I)$ and $P(I)$ to denote $S(A,G,b)$ and $P(A,G,b)$, respectively.
-Notice that $\min \;\{cx:\; (x,y) \in S(I)\}$ is in fact an MILP problem and $\min \;\{cx:\;(x,y)\in P(I) \}$ is lower bound provided from the LP relaxation.
-Let $z_{IP}(I,c)$ and $z_{LP}(I,c)$ be the optimal solution to these problems, respectively.
-
-Many researchers (see \cite{vazirani,sw}) have developed polynomial time algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$ for some $C$ which can be a constant number or dependent on some parameter of the MILP, e.g.
-$O(\log(n))$.
-However, for many combinatorial optimization problems there is a limit to such techniques.
-Let $g_I= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$.
-Parameter $g_I$ depends on set $S(I)$ and the linear constraints in (\ref{S}) and is known as the \textit{integrality gap} of the formulation for instance $I$.
-It is easy to see, that we cannot hope to find solutions for the MILP with objective values better than $g_I\cdot z_{LP}(I,c)$.
-More generally we can define the integrality gap for a class of instances $\mathcal{I}$.
-In this case, the integrality gap for problem $\mathcal{I}$ is
-\begin{equation}
-g_\mathcal{I} = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}
-\end{equation}
-
-For example, in the problem of finding a minimum weight 2-edge-connected multigraph, the gap of the the natural formulation, constraining every cut to be crossed at least twice, is at most $\frac{3}{2}$ \cite{Wolsey1980} and at least $\frac{6}{5}$ \cite{carr-ravi}.
-Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation.
-If we have $g_I=1$, $P(I)=\conv(S(I))$ and $P(I)$ is an \textit{integral} polyhedron.
-There are many interesting examples of such formulations such as spanning tree polytope and the perfect matching polytope \cite{schrijver}.
-For such problems we know how to write a vector $x\in P(I)$ as convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.
-
-\begin{proposition}\label{cara}
-	If $g_I=1$, then for $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$.
-Moreover, we can find such a convex combination in polynomial time.
-\end{proposition}
-
-Now assume $1<g<\infty$. Denote by $\dom(P(I))$ be the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$.
-
-A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}, which is a generalization of Goemans proof for blocking polyhedra \cite{goemans}.
-
-\begin{theorem}[Carr, Vempala \cite{CV}] \label{CV}
-	Let $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(S(I))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ if and only if $g_I \leq C$.
-\end{theorem}
-
-In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
-This points to an interesting open question.
-
-\begin{question}\label{question1}
-	Assume reasonable complexity assumptions (such as UGC or $\textrm{P}\neq \textrm{NP}$).
-Given instance $I$ with $1<g_I<\infty$ and $(x,y)\in P(I)$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(\conv(S(I)))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_Ix$ in polynomial time?
-\end{question}
-
-This seems to be a very hard question. A more specific question is of more interest.
-
-\begin{question}\label{question2}
-	Assume reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g_{\mathcal{I}}<\infty$, and $(x,y)\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_{\mathcal{I}}x$ in polynomial time?
-\end{question}
-Although Question \ref{question2} is wide open, for some problems $\mathcal{I}$ there are polynomial time algorithms closing the gap.
-For example, for generalized Steiner forest problem \cite{jain} gave an LP-based 2-approximation algorithm.
-The gap for this problem is also lower bounded by 2.
-Same holds for the set covering problem \cite{randomizedrounding}.
-In fact, for set cover the approximation algorithm achieving the same factor as the integrality gap lower bound, is a \textit{randomized rounding} algorithm.
-Rhagavan and Thompson \cite{randomizedrounding} showed that this technique acheives provably good approximation for many combinatorial optimization problems.
-
-One key step, in answering Question \ref{question1} and \ref{question2} is being able to find a solution in $S(I)$.
-In fact, for general $I$ it is NP-hard to even decide if $S(I)$ is empty or not.
-There are a number of heuristics for this purpose, such as the feasibility pump heuristic \cite{fp1,fp2}.
-These heuristics are often very effective and fast in practice, however, they can sometimes fail in finding a feasible solution.
-In addition these algorithms do not provide any bounds on the quality of the solution they find.
-\subsection{Our results}
-In this paper we study Theorem \ref{CV} and the natural questions that follow from it (Questions \ref{question1} and \ref{question2}).
-
-We give a general approximation framework for solving $\{0,1\}$-MILPs.  Consider the set of point described by a set 
-\begin{equation}
-S(I)= \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
-\end{equation}
-and a linear relaxation of set $S$
-\begin{equation}
-P(I) = \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
-\end{equation}
-For a vector $x\in \bbbr^n$ such that $(x,y)\in P(I)$ for some $y\in \bbbr^p$, let $\spp(x)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.
-
-\begin{restatable}{theorem}{binaryFDT}
-	\label{binaryFDT}
-	Assume $1\leq g_I 	<\infty$. 	
-	The FDT algorithm, given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\spp(x^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g_I^{|\spp(x^*)|}$.
-\end{restatable}
-
-Notice, that the FDT algorithm needs to find feasible solutions to any MILP with finite gap. This can be of independent interest.
-\begin{restatable}{theorem}{DomToIP}
-	\label{domtoIP}
-	Assume $1\leq g_I < \infty$. The DomToIP algorithm finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
-\end{restatable}
-
-In attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem.
-In this problem we want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
-For this problem the natural linear programming relaxation is
-\begin{equation}\label{2ECpol}
-\EC(G)= \{x\in \bbbr_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
-We prove the following theorem.
-
-\begin{restatable}{theorem}{FDTEC}
-	\label{FDT2EC}
-	Let $G=(V,E)$ and $x$ be an extreme point of  $\EC(G)$.
-The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq O(|V|)$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g_{\EC}^{O(|V|)}$, where $g_{\EC}$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol})
-\end{restatable}
-
-Although the bound guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are very large for large problems, we show that in practice, the algorithm works very well providing approximation ratios that are far better than the theoretical bound in the theorem statements.
-We examine FDT for binary MILPs for problems such as the tree augmentation problem (TAP) and we apply FDT for 2EC on some interesting and ``hard to decompose" points in the linear relaxation.
-
-Finally we give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems.
-For this purpose assume $P= \{x\in \bbbr^n_{\geq 0}: Ax\geq b\textbf{1}, x \leq b\textbf{1}\}$, $S= P\cap \bbbz^n$, and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$.
-Examples of such problems include the 2-edge-connected multigraph problem, the tree augmentation problem, and many others.
-
-\begin{restatable}{theorem}{tightcuts}
-	\label{tightcuts}
-	Let $x\in P$, there exists $\theta\in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i = 1$ and $\tilde{x}^i \in S$ for $i=1,\ldots,k$ such that \begin{itemize}
-		\item for $\ell\in \{1,\ldots,n\}$, if $x_\ell =0$, then $\tilde{x}^i_\ell=0$ for $i =1,\ldots,k$, i.e. $\tilde{x}^i$ is in the support of $x$,
-		\item we have $Cb = C\cdot A_j x \geq A_j (\sum_{i=1}^{k}\theta_i\tilde{x}^i)$, for $j$ such that $A_j x =b$,  
-	\end{itemize}
-	if and only if $C\geq g$.
-\end{restatable}
-
-This means in order to prove an upper bound on the integrality gap of a covering problem, we need to show there is a convex combination of integer feasible points that is ``cheap'' on all tight cuts.
-Notice that Theorem \ref{CV} requires the certificate convex combination to be ``cheap" on every single variable.
-
-\subsection{Notations}
-For vectors $x,y\in \bbbr_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$.
-For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$.
-Let $\textbf{1}$ be the vector of all ones of a suitable dimension.
-For a set $S$ of vectors in $\bbbr_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.
-
-\section{FDT on binary MIPs}
-\label{binaryfdt}
-
-In this section we present the fractional decomposition tree (FDT) algorithm and prove its correctness.
-
-Consider a formulation instance $I=(A,G,b)$, set 
-\begin{equation}
-S(I)= \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
-\end{equation}
-and its linear relaxation
-\begin{equation}
-P(I) = \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
-\end{equation}
-Also assume we are given a point $(x^*,y^*)\in P(I)$.
-For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
-In this section, we prove Theorem \ref{binaryFDT}.
-One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{domtoIP} that we will also prove in this section.
-
-Although the theoretical worst-case upper bound on $C$ in the statement of Theorem \ref{binaryFDT} can be very large, we will show that in practice $C$ can be really small and hence FDT can provide good LP-based approximation algorithms in many cases.
-We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.
-In the remainder of this section we explain the FDT algorithm and prove Theorem \ref{binaryFDT}.
-For simplicity in the notation we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively.
-Let $t=|\spp(x^*)|$.
-We assume without loss of generality that $\spp(x^*)= \{1,\ldots,t\}$.
-
-We begin with the following lemmas that show how the FDT algorithm branches on a variable.
-\begin{lemma}\label{LPClemma}
-	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$,
-		,(iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
-\end{lemma}
-
-\begin{proof} 
-	Consider the following linear program which we denote by $\LPC(\ell,x',y')$. The variables of $\LPC(\ell,x',y')$ are $\gamma_0,\gamma_1$ and $(x^0,y^0)$ and $(x^1,y^1)$. 
-	\begin{align}
-		\LPC(\ell,x',y')\quad\quad& \max\quad \;\lambda_0+\lambda_1\\
-		&\;\text{s.t.} \quad Ax^j + Gy^j\geq b\lambda_j & \mbox{ for $j=0,1$} \label{feasibility}\\
-		&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq \lambda_j &\mbox{ for $j=0,1$}\label{bound}\\
-		&\;{\color{white}{\text{s.t.}} }\quad x^0_\ell = 0,\; x^1_\ell =\lambda_1\label{branchcoordinate}\\
-		&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1 \leq x'\label{packing}\\
-		&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1 \geq 0
-	\end{align}
-
-	Let $(x^0,y^0),(x^1,y^1)$, and $\gamma_0,\gamma_1$ be an optimal solution solution to the LP above.
-Let $(\hat{x}^0,\hat{y}^0) = (\frac{x^0}{\gamma_0},\frac{y^0}{\gamma_0})$, $(\hat{x}^1,\hat{y}^1) = (\frac{x^1}{\gamma_1},\frac{y^1}{\gamma_1})$.
-Observe that  (ii), (iii), (iv) are satisfied with this choice.
-In order to show that (i) is also satisfied we prove the following claim.
-
-	\begin{claim}\label{CVexists}
-		We have $\gamma_0 + \gamma_1\geq \frac{1}{g}$.
-	\end{claim}
-	\begin{proof}
-		We show that there is a feasible solution that achieves the objective value of $\frac{1}{g}$.
-By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $(\tilde{x}^i,\tilde{y}^i)\in S$ for $i=1,\ldots,k$ such that
-		$\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$.
-
-		\begin{equation}\label{splitting}
-		x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
-		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}
-		\end{equation}
-		For $j=0,1$, let $(x^j,y^j) = \sum_{i\in [k]:\tilde{x}^i_\ell=j} \frac{\theta_i}{g}(\tilde{x}^i,\tilde{y}^i)$.
-Also let $\lambda_0=\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g}$ and $\lambda_1 = \sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g}$.
-Note that $\lambda_0+\lambda_1 = \frac{1}{g}$.
-Constraint (\ref{packing}) is satisfied by Inequality (\ref{splitting}).
-Also, for $j=0,1$ we have
-		\begin{equation}
-		Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \geq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
-		\end{equation}
-		Hence, Constraints (\ref{feasibility}) holds.
-Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$.
-The rest of the constraints trivially hold.
-	\end{proof}
-	This concludes the proof.	
-\end{proof}
-
-We now show if $x'$ in the statement of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
-\begin{lemma}\label{round-up}
-	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\frac{ 1}{g}\leq \gamma_0 + \gamma_1  \leq 1$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
-		x'$,(v) $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
-\end{lemma} 
-\begin{proof}
-	By Lemma \ref{LPClemma} we can find $(\bar{x}^0,\bar{y}^0)$, $(\bar{x}^1,\bar{y}^1)$, $\gamma_0$ and $\gamma_1$ that satisfy (i), (ii), (iii), and (iv).
-We define $\hat{x}^0$ and $\hat{x}^1$ as follows.
-For $i=0,1$, for $j=1,\ldots,\ell-1$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,t$ let $\hat{x}^i_j = \bar{x}^i_j$.
-We now show that $(\hat{x}^0,\bar{y}^0)$, $(\hat{x}^1,\bar{y}^1)$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions.
-Note that conditions (i), (ii), (iii), and (v) are trivially satisfied.
-Thus we only need to show (iv) holds.
-We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$.
-If $j=\ell,\ldots,t$, then this clearly holds.
-Hence, assume $j\leq \ell-1$.
-By the property of $x'$ we have $x'_j\in \{0,1\}$.
-If $x'_j= 0$, then by Constraint (\ref{packing}) we have $\bar{x}^0_j = \bar{x}^1_j=0$.
-Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds.
-Otherwise if $x'_j = 1$, then we have
-	$\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.$ 
-	Therefore (v) holds.
-\end{proof}
-The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs.
-Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$.
-The solutions contained in the nodes of the tree become progressively more integral at each level.
-Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$.
-We will later see how we can turn these into points in $S$.
-
-Let us define the FDT algorithm more formally.
-The algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm.
-The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree.
-The points in the leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.
-
-\begin{lemma}\label{prune}
-	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $(x,y)\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$:
-		(a) If $(x,y)\in L_i$, then $x_j \in \{0,1\}$ for $j=1,\ldots,i$, i.e.
-the first $i$ coordinates of a solution in level $i$ are integral, (b) $\sum_{[(x,y),\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$, (c) $\sum_{[(x,y),\lambda]\in L_i}\lambda x \leq x^*$, (d) $|L_i|\leq t$.
-\end{lemma}
-\begin{proof}
-	We prove this lemma using induction but one can clearly see how to turn this proof into a polynomial time algorithm.
-Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $(x^*,y^*)$ and multiplier 1.
-It is easy to check all the requirements in the lemma are satisfied for this choice.
-
-	Suppose by induction that we have constructed sets $L_0,\ldots,L_i$.
-Let the solutions in $L_i$ be $(x^j,y^j)$ for $j=1,\ldots,k$ and $\lambda_j$ be their multipliers, respectively.
-For each $j= 1,\ldots,k$ by Lemma \ref{round-up} (setting $(x',y')= (x^j,y^j)$ and $\ell = i+1$) we can find $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and $\lambda^0_j$, $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}.
-Define $L'$ to be the set of nodes with solutions $(x^{j0},y^{j0}), (x^{j1},y^{j1})$ and multipliers  $\lambda_j\lambda^0_j$, $\lambda_j\lambda^1_j$, respectively, for $j=1,\ldots,k$.
-It is easy to check that \iffalse{
-	Notice that for each $j= 1,\ldots,k$ by property (v) in Lemma \ref{round-up} we have $x_h^{j0}, x_h^{j1}\in \{0,1\}$ for $h = 0,\ldots,i+1$. We also have
-	\begin{align*}
-		\sum_{[(x,y),\lambda]\in L'} \lambda & =  \sum_{j=1}^{k} \lambda_j\lambda^0_j+\lambda_j\lambda^1_j&\\
-		& \geq \sum_{j=1}^{k} \frac{\lambda_j}{ g} & (\text{By property (i) in Lemma \ref{round-up}})\\
-		& \geq \frac{1}{g} \sum_{[(x,y),\lambda]\in L_i}\lambda&\\
-		& \geq \frac{1}{g^{i+1}}.&(\text{By induction hypothesis})	 
-	\end{align*} 
-	Also 
-	\begin{align*}
-		\sum_{[(x,y),\lambda]\in L'}\lambda x & =  \sum_{j=1}^{k} \lambda_j\big(\lambda^0_jx^{j0}+\lambda^1_jx^{j1}\big)&\\ 
-		& \leq \sum_{j=1}^{k} \lambda_j x^j  & (\text{By property (iv) in Lemma \ref{round-up}})\\
-		& \leq \sum_{[(x,y),\lambda]\in L_i}\lambda x&\\
-		& \leq x^*.&(\text{By induction hypothesis})	 
-	\end{align*} \fi set $L'$ is a suitable candidate for $L_{i+1}$, i.e.
-set $L'$ satisfies (a), (b) and (c).
-However we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$.
-We call the following linear program $\prun(L')$.
-Let $L' = \{[(x^1,y^1),\gamma_1],\ldots,[(x^{2k},y^{2k}),\gamma_{2k}]\}$.
-The variables of $\prun(L')$ is a scalar variable $\theta_j$ for each node $j$ in $L'$.
-	\begin{align}
-		\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{2k} \theta_j\\
-		&\;\text{s.t.} \quad \;\;\sum_{j=1}^{2k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
-		&\;{\color{white}{\text{s.t.}} }\quad  \;\quad\quad\theta \geq 0\label{nonneg}
-	\end{align}
-
-	Notice that $\theta = \gamma$ is in fact a feasible solution to $\prun(L')$.
-Let $\theta^*$ be the optimal vertex point solution to this LP.
-Since the problem is in $\bbbr^{2k}$,  $\theta^*$ has to satisfy $2k$ linearly independent constraints at equality.
-However, there are only $t$ constraints of type (\ref{packs}).
-Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero.
-We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,2k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma.
-Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$.
-Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$.
-\end{proof}
-The leaves of the FDT tree,  $L_t$, have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$.
-Our goal to now replace these leaves solutions in $\dom(P)$ with solutions in $S$.
-To this end, we need to reduce some variables with value of 1 into variables of value 0 and obtain feasibility in the meantime.
-We introduce a procedure that given a  point $(x,y)\in \dom(P)$ with $x\in \{0,1\}^n$ outputs a point $z\leq x$ with $z\in \{0,1\}^n$ such that $(z,w)$ is in $S$ for some vector $w\in \bbbr^p$.
-
-The algorithm ``fixes" the variables iteratively, from $x_1$ to $x_t$.
-Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$.
-Now consider the following linear program.
-The variables of this LP are the $z\in \bbbr^n$ variables and $w\in \bbbr^p$.
-\begin{align}
-	\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
-	&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
-	&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
-	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
-	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
-\end{align}
-
-If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$.
-Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$.
-Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$.
-This procedure is the DomToIP algorithm.
+\input{introduction.tex}
+\input{binaryFDT.tex}
+\input{2ECFDT.tex}
+\input{computational}
 \iffalse{
-\begin{algorithm}[H]
-	\KwIn{$(x,y)\in \dom(S)$}
-	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
-	$x^{(0)}\leftarrow x$\\
-	\For{$\ell = 0$ \textbf{to} $t-1$}{
-		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
-		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
-		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
-		\eIf{$\eta = 0$}{
-			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
-		}{
-			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
-		}
-	}
-	\label{domtoIPalg}
-	\caption{The DomToIP algorithm}
-\end{algorithm}
+\input{strongerCV}
 }\fi
-The following lemma proves Theorem \ref{domtoIP}.
-\begin{lemma}
-	Given $(x,y)\in \dom(P)$, DomToIP algorithm correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
-\end{lemma}
-The proof is in Appendix \ref{lemma4}.
-
-\iffalse{
-\begin{algorithm}[H]\label{FDTFull}
-	\KwIn{$P= \{(x,y)\in \bbbr^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \bbbr^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
-	\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
-	$L^0\leftarrow [(x^*,y^*),1]$\\
-	\For{$i=1$ \textbf{to} $t$}{
-		$L'\leftarrow \emptyset$\\
-		\For{$[(x,y),\lambda] \in L^i$}{
-			Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
-			$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
-		}
-		Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
-	}
-	\For{$[(x,y),\lambda] \in L^t$}{
-		Apply Algorithm \ref{domtoIP} to $(x,y)$ to obtain $(z,w)\in S$\\
-		$F \leftarrow F \cup \{[(z,w),\lambda]\}$
-	}
-	\textbf{return} $F$
-	\caption{Fractional Decomposition Tree Algorithm}
-\end{algorithm}}\fi
-\section{FDT for 2EC}\label{2EC}
-
-In Section \ref{binaryfdt} our focus was on binary MIPs.
-In this section, in an attempt to extend FDT to 0,1,2 problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem.
-Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2.
-In the 2EC problem, we are given non-negative costs on the edge of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$.
-Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take an edge at most 2 times.
-The natural linear programming relaxation is $\EC(G) = \{x\in [0,2]^E: x(\delta(U))\geq 2 \mbox{ for } \emptyset \subset U \subset V\}$.
-Notice that $\dom(\EC(G))\cap [0,2]^{E} = \EC(G)$, since 2EC is a covering problem.
-We want to prove the following theorem.
-
-\FDTEC*
-
-We do not know the exact value for $g_{\EC}$, but we know $\frac{6}{5} \leq g_{\EC} \leq \frac{3}{2}$ \cite{carr-ravi,Wolsey1980}.
-Also, we need to remark that polyhedral version of Christofides' algorithm provides a $\frac{3}{2}$-approximation for 2EC, i.e.
-we already have an algorithm with $C\leq \frac{3}{2}$.
-However, we show later in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$.
-
-The FDT algorithm for 2EC is very similar to the one for binary MIPs, but there are some differences as well.
-First, we need a branching lemma.
-Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for 0,1,2 problems expect for one additional clause.
-
-\begin{restatable}{lemma}{2ECLPC}
-	\label{LPC2EC}
-	Given $x\in \EC(G)$, and $e\in E$ we can find in polynomial time vectors $x^0,x^1$ and $x^2$ and scalars $\gamma_0,\gamma_1$, and $\gamma_2$ such that: (i) $\gamma_0 + \gamma_1 +\gamma_2 \geq \frac{ 1}{g_{\EC}}$, (ii) $x^0,x^1,$ and $x^2$ are in  $ \EC(G)$, (iii) $x^0_e=0$, $x^1_e=1$, and $x^2_e=2$, (iv) $\gamma_0 x^0 + \gamma_1{x}^1  + \gamma_2x^2\leq {x}$, (v) for $f\in E$ with ${x}_f\geq 1$, we have $x^j_f\geq 1$ for $j=0,1,2$.
-\end{restatable}
-
-\begin{proof}
-	Consider the following LP with variables $\lambda_j$ and $x^j$ for $j=0,1,2$. 
-	\begin{align}
-		\quad\quad& \max\quad \;\sum_{j=0,1,2}\lambda_j\\
-		&\;\text{s.t.} \quad x^j(\delta(U))\geq 2\lambda_j \;& \mbox{ for $\emptyset \subset U \subset V$, and $j=0,1,2$} \label{feasibility2ec}\\
-		&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq 2\lambda_j\; &\mbox{ for $j=0,1,2$}\label{bound2ec}\\
-		&\;{\color{white}{\text{s.t.}} }\quad x^j_e = j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
-		&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
-		&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1+x^2 \leq x\label{packing2ec}\\
-		&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1,\lambda_2 \geq 0
-	\end{align}	Let $x^j$, $\gamma_j$ for $j=0,1,2$ be an optimal solution solution to the LP above.
-Let $\hat{x}^{j}=\frac{x^j}{\gamma_j}$ for $j=0,1,2$ where $\gamma_j>0$.
-If $\gamma_j=0$, let $\hat{x}^{j}=0$.
-Observe that  (ii), (iii), (iv), and (v) are satisfied with this choice.
-We can also show that $\gamma_0+\gamma_1+\gamma_2\geq \frac{1}{g_{\EC}}$, which means that (i) is also satisfied.
-The proof is similar to the proof of the claim in Lemma \ref{LPClemma}, but we need to replace each $f\in E$ with $x_f\geq 0$ with a suitably long path to ensure that Constraint (\ref{1edges2ec}) is also satisfied.	We skip the details.\iffalse{
-	\begin{claim}\label{CVexists}
-		We have $\gamma_0 + \gamma_1+\gamma_2\geq \frac{1}{g_{\EC}}$.
-	\end{claim}
-	\begin{proof}
-		Suppose for contradiction $\sum_{j=0,1,2}\gamma_j = \frac{1}{g_{\EC}} - \epsilon$ for some $\epsilon >0$.
-
-		Construct graph $G'$ by removing edge $f$ with $x_f\geq 1$ and replacing it with a path $P_f$ of length $\ceil{\frac{2}{\epsilon}}$.
-Define $x'_h = x_h$ for each edge $h$ such that $x_h<1$.
-For each $h\in P_f$ let $x'_h= x_f$ for all $f$ with $x_f\geq 1$.
-It is easy to check that $x'\in \EC(G')$.
-By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and 2-edge-connected multigraphs $F'_i$ of $G'$ for $i=1,\ldots,k$ such that
-		$\sum_{i=1}^{k}\theta_i \chi^{F'_i}\leq g_{\EC}x'$.
-
-		Note that each $F'_i$ contains at least one copy of every edge in any path $P_f$, except for at most one edge in the path.
-We will obtain 2-edge-connected multigraphs $F_1,\ldots,F_k$ of $G$ using $F'_1,\ldots,F'_k$, respectively.
-To obtain $F_i$ first remove all $P_f$ paths from $F'_i$.
-Suppose there is an edge $h$ in $P_f$ such that $\chi^{F'_i}_h=0$, this means that for any edge $p\in P_f$ such that $p\neq h$, $\chi^{F'_i}_p=2$.
-In this case, let $\chi^{F_i}_f=2$, i.e.
-add two copies of $f$ to $F_i$.
-If there is an edge $h\in P_f$ with $\chi^{F'_i}_h = 1$, let $\chi^{F_i}_f=1$, i.e.
-add one copy of $f$ to $F_i$.
-If for all edge $h\in P_f$, we have $\chi^{F'_i}_h=2$, then let $\chi^{F_i}_f=2$.
-For $f\in E$ with $x_f<1$ we have
-		\begin{equation}
-		\sum_{i=1}^{k}\theta_i \chi^{F_i}_f=\sum_{i=1}^{k}\theta_i \chi^{F'_i}_f\leq g_{\EC}x'_f= g_{\EC}x_f.
-		\end{equation}
-		In addition for $f\in E$ with $x_f\geq 1$ we have $\chi^{F_i}_f \leq \frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}$ by construction.
-		\begin{align*}
-			\sum_{i=1}^{k}\theta_i \chi^{F_i}_f&\leq \sum_{i=1}^{k}\theta_i\frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
-			&= \frac{\sum_{h\in P_f} \sum_{i=1}^{k}\theta_i\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
-			&\leq \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
-			&= \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
-			&= \frac{\ceil{\frac{2}{\epsilon}}}{\ceil{\frac{2}{\epsilon}}-1}g_{\EC}x_f
-		\end{align*}
-		Therefore, we have 
-		\begin{equation}
-		x' \geq \sum_{i\in [k]: \chi^{F_i}_e=1}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}+\sum_{i\in [k]: \chi^{F_i}_e=2}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}.
-		\end{equation}
-		Let $x^j = \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}$ and $\theta_j =  \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$ for $j=0,1,2$.
-It is easy to check that $x^j$ , $\theta_j$ for $j=0,1,2$ is a feasible solution to the LP above.
-Notice that $\sum_{j=0,1,2}\theta_j = \frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$.
-By assumption, we have $\frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\leq  \frac{1}{g_{\EC}}-\epsilon$.
-However, this means $2\leq 1$ which is a contradiction.
-	\end{proof}
-	This concludes the proof.}\fi \end{proof}
-
-In contrast to FDT for binary MIPs where we round up the fractional variables that are already branched on at each level, in FDT for 2EC we keep all coordinates as they are and preform a rounding procedure at the end.
-Formally, let $L_i$ for $i=1,\ldots,|\spp(x^*)|$ be collections of pairs of feasible points in $\EC(G)$ together with their multipliers.
-Let $t=|\spp(x^*)|$ and assume without loss of generality that $\spp(x^*)=\{e_1,\ldots,e_t\}$.
-
-\begin{lemma}\label{2ecpruning}
-	The FDT algorithm for 2EC in  polynomial time produces sets $L_0,\ldots,L_t$ of pairs $x\in \EC(G)$ together with multipliers $\lambda$ with the following properties.
-		(a) If $x\in L_i$, then $x_{e_j}=0$ or $x_{e_j}\geq 1$ for $j=1,\ldots,i$, (b) $\sum_{(x,\lambda)\in L_i }\lambda \geq \frac{1}{g_{\EC}^i}$, (c) $\sum_{(x,\lambda)\in L_i }\lambda x \leq x^*$, (d) $|L_i|\leq t$.
-\end{lemma}
-The proof is similar to Lemma \ref{prune}, but we need to use property (i) in Lemma \ref{LPC2EC} to prove that (a) also holds.
-\iffalse{
-\begin{proof}
-	We proceed by induction on the $i$.
-Define $L_0=\{(x^*,1)\}$.
-It is easy to check all the properties are satisfied.
-Now, suppose by induction we have $L_{i-1}$ for some $i=1,\ldots,t$ that satisfies all the properties.
-For each solution $x^\ell$ in $L_{i-1}$ apply Lemma \ref{LPC2EC} on $x^\ell$ and $e_{i}$ to obtain $x^{\ell j}$ and $\lambda_{\ell j}$ for $j=0,1,2$.
-Let $L'$ be the collection that contains $(x^{\ell j},\lambda_\ell \cdot \lambda_{\ell j})$ for $j=0,1,2$, when applied to all $(x^\ell,\lambda_\ell)$ in $L_{i-1}$.
-Similar to the proof in Lemma \ref{prune} one can check that $L_i$ satisfies properties (b), (c).
-We now verify property (a).
-Consider a solution $x^\ell$ in $L_{i-1}$.
-For $e\in \{e_1,\ldots,e_{i-1}\}$ if $x^\ell_e =0$, then by property (iv) in Lemma \ref{LPC2EC} we have $x^{\ell j}=0$ for $j=0,1,2$.
-Otherwise by induction we have $x^{\ell}_{e}\geq 1$ in which case property (v) in Lemma \ref{LPC2EC} ensures that $x^{\ell j}_e\geq 1$ for $j=0,1,2$.
-Also, $x^{\ell j}_{e_i}= j$, so $x^{\ell j}_{e_i}=0$ or $x^{\ell j}_{e_i}\geq 1$ for $j=0,1,2$.
-
-	If $|L'|\geq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
-\end{proof}	}\fi
-
-Consider the solutions $x$ in $L_t$. For each variable $e$ we have $x_e=0$ or $x_e\geq 1$. 
-\begin{lemma}\label{rounddown}
-	Let $x$ be a solution in $L_t$. Then $\floor{x} \in \EC(G)$. 
-\end{lemma}
-\begin{proof}
-	Suppose not.
-Then there is a set of vertices $\emptyset \subset U \subset V$ such that $\sum_{e\in \delta(U)}\floor{x_e}<2$.
-Since $x\in \EC(G)$ we have $\sum_{e\in \delta(U)}x_e \geq 2$.
-Therefore, there is an edge $f\in \delta(U)$ such that $x_f$ is fractional.
-By property (a) in Lemma \ref{2ecpruning}, we have $1<  x_f < 2$.
-Therefore, there is another edge $h$ in $\delta(U)$ such that $x_h>0$, which implies that $x_h\geq 1$.
-But in this case $\sum_{e\in \delta(U)}\floor{x_e}\geq  \floor{x_f}+\floor{x_h}  \geq 2$.
-This is a contradiction.
-\end{proof}
-
-The FDT algorithm for 2EC iteratively applies Lemmas \ref{LPC2EC} and \ref{2ecpruning} to variables $x_1,\ldots,x_t$ to obtain leaf point solutions $L_t$.
-Then, we just need to apply Lemma \ref{rounddown} to obtain the 2-edge-connected multigraphs from every solution in $L_t$.
-Notice that since $x$ is an extreme point we have $t\leq 2|V|-1$ \cite{gerard}.
-By Lemma \ref{2ecpruning} we have
-\begin{align*}
-	\sum_{(x,\lambda)\in L_t} \frac{\lambda}{\sum_{(x,\lambda)\in L_t}\lambda} \floor{x} \leq \frac{1}{\sum_{(x,\lambda)\in L_t}\lambda} \sum_{(x,\lambda)\in L_t} \lambda {x} \leq g^t_{\EC} x^*.
-\end{align*}
-
-\section{Stronger version of Theorem \ref{CV} for covering problems} \label{gap}
-
-Theorem \ref{CV} characterizes the integrality gap as the smallest number such that for any point $x\in \dom(P)$, $gx$ dominates a convex combination of points in $S$, i.e.
-there exists convex combination $\sum_{i=1}^{k}\lambda_ix^i \leq gx$.
-In a covering problem, we assume that matrix $A$ in the description of $P$ is a non-negative matrix, hence if $y\geq x$ and $x\in P$ we have $y\in P$.
-We also assume the right hand side vector in (\ref{P}) is of the form $b\textbf{1}$, i.e.
-it is a uniform vector.
-Finally we assume we have bound constraints $x\leq b\textbf{1}$.
-This class of problems include a broad class of problems.
-Notice that for a covering problem $\dom(P)=P$.
-We show that for these problems, we can make Theorem \ref{CV} stronger in the sense of Theorem\ref{tightcuts}.
-
-In other words, the integrality gap is the smallest number such that for any $x\in P$, there exists a convex combination $y=\sum_{i=1}^{k}\lambda_ix^i$, such that $A_jy\leq g(A_jx)$ for all $j$ such that $A_jx=b$.
-
-Notice that the proof of this theorem, same as Theorem \ref{CV}, does not imply a polynomial time algorithm.
-
-Observe that if $C\geq g$, by Theorem \ref{CV}, there is a convex combination of points in $S$ that is dominated by $Cx$, i.e.
-there exists $\theta\in [0,1]^{k}$, where $\sum_{i=1}^{k}\theta_i=1$, and $x^i\in S$, such that $\sum_{i=1}^{k}\theta_ix^i\leq gx$.
-The same convex combination also trivially satisfies both requirements in Theorem \ref{tightcuts}.
-The more interesting direction is the converse.
-We begin with the following theorem.
-Suppose $v^1,\ldots,v^r$ are the extreme points of $P$.
-Assume for each $i=1,\ldots,r$, there exists a convex combination of points in $S$, namely $\sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell$ such that $A_j \sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell \leq CA_jv^i$ for $j$ such that $A_jv^i = b$.
-Let $z^i = \sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell$.
-\begin{lemma}\label{epsilon}
-	For any  $i\in\{1,\ldots,r\}$, there exists $\epsilon_i >0$ and ${x^i}\in P$ where ${x^i}\leq \frac{Cv^i-\epsilon_i z^i}{C(1-\epsilon_i)}$.
-\end{lemma}
-\begin{proof}[Proof Sketch]
-
-	\end{proof}
-
-\iffalse{
-\begin{proof}
-
-	Let $u^i(\epsilon) = \frac{Cv^i-\epsilon z^i}{C(1-\epsilon)}$. For $j\in \{1,\ldots,m\}$, let $t_j = A_jz^i-Cb$ and $s_j=A_jv^i-b$. 
-	Assume $\epsilon <1$. For $j\in \{1,\ldots,m\}$ such that $A_jz^i\leq Cb$, i.e. $t_j\leq 0$ (this includes $j$ such that $A_jv^i=b$, i.e. $s_j=0$) we have
-	\begin{equation}
-	A_j u^i(\epsilon) = \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}\geq \frac{Cb-\epsilon Cb}{C(1-\epsilon)}=b
-	\end{equation}
-	Assume $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$.
-Notice that $\max_{j: t_j >0} \frac{s_j}{t_j}>0$ since for $j$ such that $t_j>0$, we have $A_jz_i > Cb$ which implies that $A_jv^i>b$, so $s_j>0$.
-For $j$ such that $t_j>0$ we have
-	\begin{align*}
-		A_ju^i(\epsilon) &= \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}& \\
-		&= \frac{C(b+s_j)-\epsilon (Cb+t_j)}{C(1-\epsilon)}&\\
-		&= b+ \frac{Cs_j-\epsilon t_j}{C(1-\epsilon)}&\\
-		&\geq b & (\epsilon  \leq C\cdot  \frac{s_j}{t_j}, \mbox{ and } \epsilon <1, \mbox{ so } \frac{Cs_j-\epsilon t_j}{C(1-\epsilon)}\geq 0 )
-	\end{align*} 
-	Therefore if $\epsilon \leq 1$ and $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$ we have $Au^i(\epsilon)\geq \textbf{1}b$.
-Next, we show that we can choose $\epsilon$ so that $ u^i(\epsilon)\geq 0$.
-
-	For $\ell\in \{1,\ldots,n\}$, if $z^i_\ell=0$, then we have $u_\ell^i(\epsilon) = \frac{Cv_\ell^i}{C(1-\epsilon)}\geq 0$, since $v^i_\ell\geq 0$ and $\epsilon <1$.
-Otherwise we have $z^i_\ell>0$.
-Assume $\epsilon \leq C\cdot \min_{ \ell:z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}$.
-Notice that for $\ell$ such that $z^i_\ell>0$, we have $v^i_\ell>0$ since $z^i$ lies in the support of $v^i$ by assumption.
-This means that $\min_{\ell:z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}>0$.
-Now, for $\ell$ such that $z^i_\ell>0$, we have $u^i_\ell(\epsilon) = \frac{Cv_\ell^i-\epsilon z_\ell^i}{C(1-\epsilon)}\geq 0$ by choice of $\epsilon$.
-
-	Define $\epsilon_i =\min\{1, C\cdot \min_{j: t_j >0}\frac{s_j}{t_j},C\cdot\min_{\ell: z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}\}$.
-By the arguments above $Au^i(\epsilon_i)\geq \textbf{1}b$ and $u^i(\epsilon_i)\geq 0$.
-Define $x^i$ as follows: For each $j\in \{1,\ldots,m\}$, if $u^i_j(\epsilon_i)\leq b$, then let $x^i_j=u^i_j(\epsilon_i)$, otherwise let $x^i_j=b$.
-We need to show that $x^i\in P$.
-Note that clearly $x^i\geq 0$, hence we only need to show that $Ax^i\geq \textbf{1}b$.
-Suppose for contradiction there is $j\in \{1,\ldots,m\}$ such that $A_jx^i <b$.
-Since $u^i(\epsilon)\in P$, there must be $\ell^*\in\{1,\ldots,n\}$ such that $u^i_{\ell^*}(\epsilon)>b$, and $A_{j,\ell^*}>0$.
-But this means that $A_{j,\ell^*}\geq 1$ and $x^i_{\ell^*}=b$.
-Therefore $A_jx^i \geq  A_{j,\ell^*}x^i_{\ell^*}= A_{j,\ell^*}b\geq b$.
-\end{proof}}\fi
-\begin{lemma}\label{tightcutcomb}
-	There exists a convex combination of point in $S$ that is dominated by $Cv^i$ for $i=1,\ldots,r$.
-\end{lemma}
-\begin{proof}
-
-	We prove something slightly stronger.
-We show that for $i\in\{1,\ldots,r\}$, and for $j=1,\ldots,i$, the vector $Cv^j$ dominates  a convex combination of $z^1,\ldots,z^i$ and $Cv^{i+1},\ldots,Cv^r$.
-Note that this is enough to prove our statement since for $i=r$, the statement implies that $Cv^j$ dominates a convex combination of $z^1,\ldots,z^r$ for $j=1,\ldots,r$.
-
-	We can prove this statement by induction on $i$ and applying Lemma \ref{epsilon} to prove the induction step.
-	\iffalse{
-	We proceed by induction on $i$.
-If $i=1$, we just need to show that $Cv^1$ is dominated by a convex combination of $z^1$ and $Cv^2,\ldots,Cv^r$.
-By Lemma \ref{epsilon}, there exists $x^1\leq  \frac{Cv^1-\epsilon_1z^1}{C(1-\epsilon_1)}$.
-We have $x^1\in P$, so we can write $x^1$ as convex combination of $v^1,\ldots, v^r$.
-We have
-	\begin{equation}
-	Cv^1 \geq  \epsilon_1z^1 + C(1-\epsilon_1)x^1 \geq \epsilon_1z^1 + C(1-\epsilon_1) \sum_{\ell=1}^{r}\lambda^1_\ell v^\ell.
-	\end{equation}
-	Hence,
-	\begin{equation}
-	Cv^1 \geq \frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}\cdot z^1 + (1-\epsilon_i)\sum_{\ell=2}^{r} \frac{\lambda^1_\ell}{1-(1-\epsilon_1)\lambda_1^1}\cdot Cv^\ell.
-	\end{equation}
-	Observe that $\frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}$ and $(1-\epsilon_1)\frac{\lambda^1_\ell}{1-(1-\epsilon_1)\lambda_1^1}$ for $\ell=2,\ldots,r$ form convex multipliers, so the base case holds.
-
-	Now consider $i\in \{1,\ldots,r-1\}$. By induction, for $j=1,\ldots,i$ we have
-	\begin{equation}\label{IHs}
-	Cv^j \geq  \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell + \sum_{\ell=i+1}^{r}\theta^{j}_{\ell}Cv^\ell.
-	\end{equation}
-	Suppose we are able to show 
-	\begin{equation}\label{claim} 
-	Cv^{i+1} \geq \sum_{\ell=1}^{i+1} \mu_\ell z^\ell + \sum_{\ell=i+2}^{r}\mu_{\ell}Cv^\ell,\end{equation} 
-	where $\mu\geq 0$, and $\sum_{\ell=1}^{r}\mu_{\ell}=1$. Then for $j=1,\ldots,i$ we have
-	\begin{align*}
-		Cv^j& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\theta^{j}_{i+1}Cv^{i+1}+  \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell.& (\mbox{By } \ref{IHs})\\
-		& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\sum_{\ell=1}^{i+1}\theta^{j}_{i+1}\mu_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_{i+1}\mu_{\ell}Cv^\ell +   \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell.& (\mbox{By } \ref{claim})\\
-		&= \sum_{\ell=1}^{i} (\theta^j_\ell+\mu_{\ell}\theta^j_{i+1}) z^\ell + \mu_{j+1}\theta^j_{i+1}z^{i+1} + \sum_{\ell=i+2}^{r} (\theta^j_\ell+\mu_\ell\theta^j_{i+1})Cv^\ell.&
-	\end{align*} 
-	It is easy to see that the multipliers above are convex.
-Thus, we only need to show the convex combination in (\ref{claim}) exists.
-This will be similar to what we did in the base case.
-By Lemma \ref{epsilon}, there exists $\epsilon_{i+1}$ and $x^{i+1}$ such that
-	\begin{align*}
-		Cv^{i+1}&\geq \epsilon_{i+1}z^{i+1}+ C(1-\epsilon_{i+1})x^{i+1}\\
-		&\geq \epsilon_{i+1}z^{i+1}+ (1-\epsilon_{i+1})\sum_{\ell=1}^{k}\lambda_{\ell}Cv^\ell
-	\end{align*}
-	Applying induction we can replace $Cv^j$ by $ \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell + \sum_{\ell=i+1}^{r}\theta^{j}_{\ell}Cv^\ell$ for $j=1,\ldots,i$. 
-	This means
-	\begin{align*}
-		(1-(1-\epsilon_{i+1})(\lambda_{i+1}+\sum_{j=1}^{i}\lambda_j\theta^j_{i+1}))Cv^{i+1}&\geq \epsilon_{i+1}z^{i+1}+(1-\epsilon_{i+1})\sum_{j=1}^{i}\lambda_j (\sum_{\ell=1}^{i}\theta^j_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_\ell Cv^\ell)\\
-		&+(1-\epsilon_{i+1})(\sum_{j=1}^{i}\lambda_j \lambda^j_{i+1}+\lambda^i_{i+1})C+ (1-\epsilon_{i+1})\sum_{j=i+2}^{r}\lambda_jCv^{j} 
-	\end{align*}
-	It is easy to show that  multipliers above are convex.}\fi
-\end{proof}
 
@@
 	\newblock {\em Mathematical Programming}, 100(3):569--587, Jul 2004.
+
+		\bibitem{fj}
+	Greg N. Frederickson and Joseph Ja'Ja'.
+	\newblock Approximation algorithms for several graph
+	augmentation problems.
+	\newblock {\em SIAM Journal on Computing}, 10(2):270--283, 1981.
+
+		\bibitem{32gap}
+	Cheriyan, Joseph and Karloff, Howard and Khandekar, Rohit and K{\"o}nemann, Jochen.
+	\newblock On the integrality ratio for tree augmentation.
+	\newblock {\em Operations Research Letters}, 36(4):399--401, 2008.
 

### 2018-11-19 IPCO format/binaryFDT.tex
broked main body into pieces

--- 2018-11-02 algorithmbinary.tex
@@
 
-Consider a formulation instance $I=(A,G,b)$, set 
-\begin{equation}
-S(I)= \{(x,y)\in \mathbb{R}^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
-\end{equation}
-and its linear relaxation
-\begin{equation}
-P(I) = \{(x,y)\in \mathbb{R}^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
-\end{equation}
+Consider a formulation instance $I=(A,G,b)$.
+Define sets $S(I)$ and $P(I)$ as in (\ref{S'}) and (\ref{P'}), respectively.
 Also assume we are given a point $(x^*,y^*)\in P(I)$.
 For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
-In this section, we prove the following theorem.
-
-\binaryFDT*
-
-One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{DomToIP} that we will also prove in this section.
+In this section, we prove Theorem \ref{binaryFDT}.
+One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{domtoIP} that we will also prove in this section.
 
@@
 In the remainder of this section we explain the FDT algorithm and prove Theorem \ref{binaryFDT}.
-For simplicity in the notations we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively.
-Let $t=|\sup(x^*,y^*)|$.
-We assume without loss of generality that $\sup(x^*,y^*)= \{1,\ldots,t\}$.
+For simplicity in the notation we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively.
+Let $t=|\spp(x^*)|$.
+We assume without loss of generality that $\spp(x^*)= \{1,\ldots,t\}$.
 
+The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs.
+Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$.
+The solutions contained in the nodes of the tree become progressively more integral at each level.
+In each level of the tree, the algorithm maintain a conic combination of points with the properties mentioned above.
+Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$.
+We will later see how we can turn these into points in $S$.
 We begin with the following lemmas that show how the FDT algorithm branches on a variable.
 \begin{lemma}\label{LPClemma}
-	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vector $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that
-	\begin{itemize}
-		\item[(i)] $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$,
-		\item[(ii)] $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$, 
-		\item[(iii)] $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$,
-		\item[(iv)] $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
-	\end{itemize}
+	Given $(x',y')\in \dom(P)$ and $\ell\in \{1,\ldots,n\}$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\gamma_0 + \gamma_1  \geq \frac{ 1}{g}$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $ P$
+		,(iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
 \end{lemma}
 
-\begin{proof}[Proof of Lemma \ref{LPClemma}]
-
-	Consider the following linear programing which we denote by $\LPC(\ell,x',y')$. The variables of $\LPC(\ell,x',y')$ are $\gamma_0,\gamma_1$ and $(x^0,y^0)$ and $(x^1,y^1)$. 
+\begin{proof} 
+	Consider the following linear program which we denote by $\LPC(\ell,x',y')$. The variables of $\LPC(\ell,x',y')$ are $\gamma_0,\gamma_1$ and $(x^0,y^0)$ and $(x^1,y^1)$. 
 	\begin{align}
@@
 Note that $\lambda_0+\lambda_1 = \frac{1}{g}$.
-Constraint \ref{packing} is satisfied by Inequality \ref{splitting}.
+Constraint (\ref{packing}) is satisfied by Inequality (\ref{splitting}).
 Also, for $j=0,1$ we have
 		\begin{equation}
- Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \leq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
+		Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \geq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
 		\end{equation}
-Hence, Constraints \ref{feasibility} holds.
-Constraint \ref{branchcoordinate} also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$.
+		Hence, Constraints (\ref{feasibility}) holds.
+Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$.
 The rest of the constraints trivially hold.
@@
 
-We now show if $x'$ in the statement of of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
-
+We now show if $x'$ in the statement of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
 \begin{lemma}\label{round-up}
-	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vector $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that
-	\begin{itemize}
-		\item[(i)] $\gamma_0 + \gamma_1  \geq\frac{ 1}{g}$,
-		\item[(ii)] $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, 
-		\item[(iii)] $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$,
-		\item[(iv)] $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
-		 x'$,
-		 \item[(v)] $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
-	 	\end{itemize}
+	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\frac{ 1}{g}\leq \gamma_0 + \gamma_1  \leq 1$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
+		x'$,(v) $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
 \end{lemma} 
@@
 We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$.
-If $j=\ell,\ldots,n$, then this clearly holds.
+If $j=\ell,\ldots,t$, then this clearly holds.
 Hence, assume $j\leq \ell-1$.
 By the property of $x'$ we have $x'_j\in \{0,1\}$.
-If $x'_j= 0$, then by Constraint \ref{packing} we have $\bar{x}^0_j = \bar{x}^1_j=0$.
+If $x'_j= 0$, then by Constraint (\ref{packing}) we have $\bar{x}^0_j = \bar{x}^1_j=0$.
 Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds.
 Otherwise if $x'_j = 1$, then we have
-	\begin{equation*}\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.\end{equation*}
+	$\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.$ 
 	Therefore (v) holds.
 \end{proof}
-
-The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs.
-Each node represents a partially integral vector $(\bar{x},\bar{y})$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$.
-The solutions contained in the nodes of the tree become progressively more integral at each level.
-Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$.
-We will later see how we can turn these into points in $S$.
 
@@
 The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree.
-The points in the leaves of the FDT tree, or $L_t$, are points in $\dom(P)$ and are integral for all integer variables.
+The points in the leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.
 
 \begin{lemma}\label{prune}
-	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $(x,y)\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$. 
-	\begin{enumerate}
-			\item[a.] If $(x,y)\in L_i$, then $x_j \in \{0,1\}$ for $j=1,\ldots,i$, i.e. the first $i$ coordinates of a solution in level $i$ are integral. 
-		\item[b.] $\sum_{[(x,y),\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$.
-		\item[c.] $\sum_{[(x,y),\lambda]\in L_i}\lambda x \leq x^*$.
-		\item[d.] $|L_i|\leq t$.
-	\end{enumerate}
+	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $(x,y)\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$:
+		(a) If $(x,y)\in L_i$, then $x_j \in \{0,1\}$ for $j=1,\ldots,i$, i.e.
+the first $i$ coordinates of a solution in level $i$ are integral, (b) $\sum_{[(x,y),\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$, (c) $\sum_{[(x,y),\lambda]\in L_i}\lambda x \leq x^*$, (d) $|L_i|\leq t$.
 \end{lemma}
@@
 		& \leq x^*.&(\text{By induction hypothesis})	 
-\end{align*} 
-Set $L'$ seems like a suitable candidate for $L_{i+1}$, however we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$.
-We call the following linear programming $\prun(L')$.
-Let $L' = \{[(x^1,y^1),\lambda_1],\ldots,[(x^k,y^k),\lambda_k]\}$.
+	\end{align*} \fi set $L'$ is a suitable candidate for $L_{i+1}$, i.e.
+set $L'$ satisfies (a), (b) and (c).
+However we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$.
+We call the following linear program $\prun(L')$.
+Let $L' = \{[(x^1,y^1),\gamma_1],\ldots,[(x^{2k},y^{2k}),\gamma_{2k}]\}$.
 The variables of $\prun(L')$ is a scalar variable $\theta_j$ for each node $j$ in $L'$.
-
 	\begin{align}
-\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{k} \theta_j\\
-&\;\text{s.t.} \quad \;\;\sum_{j=1}^{k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
+		\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{2k} \theta_j\\
+		&\;\text{s.t.} \quad \;\;\sum_{j=1}^{2k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
 		&\;{\color{white}{\text{s.t.}} }\quad  \;\quad\quad\theta \geq 0\label{nonneg}
@@
 
-Notice that $\theta = \lambda$ is in fact a feasible solution to $\prun(L')$.
+	Notice that $\theta = \gamma$ is in fact a feasible solution to $\prun(L')$.
 Let $\theta^*$ be the optimal vertex point solution to this LP.
-Since the problem is in $\mathbb{R}^k$,  $\theta^*$ has to satisfy $k$ linearly independent constraints at equality.
-However, there are only $t$ constraints of type \ref{packs}.
+Since the problem is in $\bbbr^{2k}$,  $\theta^*$ has to satisfy $2k$ linearly independent constraints at equality.
+However, there are only $t$ constraints of type (\ref{packs}).
 Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero.
-We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma.
+We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,2k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma.
 Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$.
-Also, since $\theta^*$ is optimal and $\lambda$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{k}\lambda_j \geq \frac{1}{g^{i+1}}$.
+Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$.
 \end{proof}
-
-The leaves of the FDT tree, or $L_t$ have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$.
+The leaves of the FDT tree,  $L_t$, have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$.
 Our goal to now replace these leaves solutions in $\dom(P)$ with solutions in $S$.
 To this end, we need to reduce some variables with value of 1 into variables of value 0 and obtain feasibility in the meantime.
-We introduce a procedure that given a  point $(x,y)\in \dom(P)$ with $x\in \{0,1\}^n$ outputs a point $z\leq x$ with $z\in \{0,1\}^n$ such that $(z,w)$ is in $S$ for some vector $w\in \mathbb{R}^p$.
+We introduce a procedure that given a  point $(x,y)\in \dom(P)$ with $x\in \{0,1\}^n$ outputs a point $z\leq x$ with $z\in \{0,1\}^n$ such that $(z,w)$ is in $S$ for some vector $w\in \bbbr^p$.
 
 The algorithm ``fixes" the variables iteratively, from $x_1$ to $x_t$.
-Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
-Now consider the following linear programming.
-The variables of this LP are the $z\in \mathbb{R}^n$ variables and $w\in \mathbb{R}^p$.
+Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$.
+Now consider the following linear program.
+The variables of this LP are the $z\in \bbbr^n$ variables and $w\in \bbbr^p$.
 \begin{align}
@@
 	}
+	\label{domtoIPalg}
 	\caption{The DomToIP algorithm}
 \end{algorithm}
-
+}\fi
 The following lemma proves Theorem \ref{domtoIP}.
 \begin{lemma}
-	Given $(x,y)\in \dom(P)$ Algorithm \ref{domtoIP} correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
+	Given $(x,y)\in \dom(P)$, DomToIP algorithm correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
 \end{lemma}
-\begin{proof}
-	First, we need to show that in any iteration $\ell\in \{0,\ldots,n-1\}$ of Algorithm \ref{domtoIP} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
-	\begin{align*}
-	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
-	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
-	\end{align*}
-	Notice that if $\LP^{(\ell)}$ is an non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible.
-We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
-First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$.
-By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
-Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^0$.
-So if $x^0_j$ is zero, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$.
-Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$.
-Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.
+The proof is in Appendix \ref{lemma4}.
 
-  Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$.
-Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.
-
-  We consider two cases.
-In the first case, we have $z^*_{\ell+1}=0$.
-In this case we have $x^{(\ell+1)}_{\ell+1}=0$.
-Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$.
-Also, $(z^*,w^*)\in P$.
-By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ .
-We have
-  \begin{equation}
-   \sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
-  \end{equation}
-  So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$.
-Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$.
-Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$.
-We claim that $(z,w)\in \IP^{(\ell+1)}$.
-If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$.
-Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
-Consider iteration $j$ of Algorithm \ref{domtoIP}.
-Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.
-We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero.
-However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0.
-This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.
-
-  Now for the second case, assume $z^*_{\ell+1} > 0$.
-We have $x^{(\ell+1)}_{\ell+1}=1$.
-Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e.
-$z_{\ell+1}=1$.
-This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.
-
-  Now consider $(x^{(t)},y^{(t)})$.
-Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$.
-If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$.
-If $x^{(t)} =1$, it must be the case that $z_t > 0$.
-By the argument above there is a point $(z',w')\in \IP^{(t-1)}$.
-We show that $x^{(t)} = z'$.
-Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
-We just need to show that $z'_j = 1$.
-Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.
-  \end{proof}
-
-This completes the FDT algorithm.
-
+\iffalse{
 \begin{algorithm}[H]\label{FDTFull}
-	\KwIn{$P= \{(x,y)\in \mathbb{R}^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \mathbb{R}^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
+	\KwIn{$P= \{(x,y)\in \bbbr^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \bbbr^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
 	\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
@@
 	\caption{Fractional Decomposition Tree Algorithm}
-\end{algorithm}
+\end{algorithm}}\fi

### 2018-11-19 IPCO format/computational.tex
broked main body into pieces

\section{Computational experiments with FDT}\label{experiment}
We implement FDT to two covering problem. First, the tree argumentation problem (TAP) where given a tree $T=(V,E)$, and a set of link $L$ between the vertices in $V$ and costs $c\in \bbbr^{L}_{\geq 0}$ we with to find minimum cost subset $L'$ of $L$ such that $T+L'$ is 2-edge-connected. For $\ell\in L$, let $P_\ell$ be the set of edges in the unique path between the endpoints of $\ell$ in $T$. For TAP, $S(\mbox{TAP})=\{x\in \bbbz^{L}_{\geq 0}: \sum_{\ell: e\in P_\ell}x_\ell \geq 1, \mbox{ for $e\in E$}\}$. Relaxing the integrality constraint we get $P(\mbox{TAP})$. It is been shown that $\frac{3}{2}\leq g({\mbox{TAP}})\leq 2$ \cite{fj,32gap}. We applied the binary FDT algorithm on a set of 264 fractional extreme points of $P(\mbox{TAP})$. The result are summarized in Figure \ref{plotTAP}.

Next we implemented the FDT for 2EC on a 900 fractional extreme points of $\EC(G)$. These points are obtained by considering all fundamental vertices with $12$ vertices (See \cite{CV} for the definition of fundamental vertices). The results are summarized in Figure \ref{plot2EC}. We also, implemented polyhedral version of Christofides' algorithm \cite{Wolsey1980} and compared its performance on fundamental extreme points with 10 vertices. The result are in Figure \ref{}.

### 2018-11-19 IPCO format/introduction.tex
broked main body into pieces

--- 2018-11-02 introduction.tex
@@
 
-Consider the set of point described by a set 
+Consider the set of points described by a set 
 \begin{equation}
-S(A,G,b)= \{(x,y)\in \mathbb{Z}^{n}\times \mathbb{R}^p\;:\; Ax+Gy\geq b\}  \label{S}
+S(A,G,b)= \{(x,y)\in \bbbz^{n}\times \bbbr^p\;:\; Ax+Gy\geq b\}  \label{S}
 \end{equation}
@@
 \begin{equation}
-P(A,G,b) = \{(x,y)\in \mathbb{R}^{n+ p}\;:\; Ax+Gy\geq b\}. \label{P}
+P(A,G,b) = \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b\}. \label{P}
 \end{equation}
@@
 
-\begin{fact}\label{cara}
+\begin{proposition}\label{cara}
 	If $g_I=1$, then for $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$.
 Moreover, we can find such a convex combination in polynomial time.
-\end{fact}
+\end{proposition}
 
-	Now assume $1<g<\infty$. Denote by $\dom(P(I))$ be the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$.
+Now assume $1<g(I)<\infty$.
+Denote by $\dom(P(I))$ be the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$, also known as the dominant of $P(I)$.
+Notice that for covering problems the dominant of a polyhedron is essentially the same as its dominant, but for problems that are not covering, the two might be different.
+We show later, for $I$ with $g(I)<\infty$, the notation of dominant is in fact useful.
 
-	A analogous result to Fact \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}.
+A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}, which is a generalization of Goemans proof for blocking polyhedra \cite{goemans}.
 
@@
 \begin{question}\label{question1}
-	Assume reasonable complexity assumptions (such as $\UGC$ or $\Pp\neq \NP$).
+	Assume reasonable complexity assumptions (such as UGC or $\textrm{P}\neq \textrm{NP}$).
 Given instance $I$ with $1<g_I<\infty$ and $(x,y)\in P(I)$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(\conv(S(I)))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_Ix$ in polynomial time?
@@
 \end{question}
-Although Question \ref{question2} is wide open, for some problems $\mathcal{I}$ there are polynomial time algorithms.
+Although Question \ref{question2} is wide open, for some problems there are polynomial time algorithms closing the gap.
 For example, for generalized Steiner forest problem \cite{jain} gave an LP-based 2-approximation algorithm.
@@
 In fact, for set cover the approximation algorithm achieving the same factor as the integrality gap lower bound, is a \textit{randomized rounding} algorithm.
-Rhagavan and Thompson \cite{randomizedrounding} showed that this technique acheives provably good approximation for many combinatorial optimization problems.
+Raghavan and Thompson \cite{randomizedrounding} showed that this technique achieves provably good approximation for many combinatorial optimization problems.
 
@@
 \begin{equation}
-S(I)= \{(x,y)\in \mathbb{R}^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
+S(I)= \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'} 
 \end{equation}
@@
 \begin{equation}
-P(I) = \{(x,y)\in \mathbb{R}^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
+P(I) = \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
 \end{equation}
-For a point $(x,y)\in P(I)$, let $\sup(x,y)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.
+For a vector $x\in \bbbr^n$ such that $(x,y)\in P(I)$ for some $y\in \bbbr^p$, let $\spp(x)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.
 
@@
 	\label{binaryFDT}
-	Assume $1\leq g_I<\infty$. 	
-The FDT algorithm (Algorithm \ref{FDTFull}), given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\sup(x^*,y^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g_I^{|\sup(x^*,y^*)|}$.
+	Assume $1\leq g_I 	<\infty$. 	
+	The Fractional Decomposition Tree (FDT) algorithm , given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\spp(x^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
+Moreover, $C\leq g_I^{|\spp(x^*)|}$.
 \end{restatable}
@@
 \begin{restatable}{theorem}{DomToIP}
-	\label{DomToIP}
-		Assume $1\leq g_I \leq \infty$. The DomToIP algorithm (Algorithm \ref{domtoIP}) finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
+	\label{domtoIP}
+	Assume $1\leq g_I < \infty$. The DomToIP algorithm finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
 \end{restatable}
@@
 In attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem.
-In this problem we want to find the minimum weight 2-edge-connected multigraph in a graph $G=(V,E)$ with respect to weights $c\in \mathbb{R}^E_{\geq 0}$.
+In this problem we want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
 For this problem the natural linear programming relaxation is
 \begin{equation}\label{2ECpol}
- \EC(G)= \{x\in \mathbb{R}_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
+\EC(G)= \{x\in \bbbr_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
 We prove the following theorem.
@@
 Finally we give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems.
-For this purpose assume $P= \{x\in \mathbb{R}^n_{\geq 0}: Ax\geq b\textbf{1}, x \leq b\textbf{1}\}$, $S= P\cap \mathbb{Z}^n$, and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$.
+For this purpose assume $P= \{x\in \bbbr^n_{\geq 0}: Ax\geq b\textbf{1}, x \leq b\textbf{1}\}$, $S= P\cap \bbbz^n$, and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$.
 Examples of such problems include the 2-edge-connected multigraph problem, the tree augmentation problem, and many others.
@@
 
-\subsection{Notation and Preliminaries}
+\subsection{Notations}
+For vectors $x,y\in \bbbr_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$.
+For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$.
+Let $\textbf{1}$ be the vector of all ones of a suitable dimension.
+For a set $S$ of vectors in $\bbbr_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.

### 2018-11-20 IPCO format/computational.tex
computational experminets

@@
 We applied the binary FDT algorithm on a set of 264 fractional extreme points of $P(\mbox{TAP})$.
-The result are summarized in Figure \ref{plotTAP}.
-
-Next we implemented the FDT for 2EC on a 900 fractional extreme points of $\EC(G)$.
-These points are obtained by considering all fundamental vertices with $12$ vertices (See \cite{CV} for the definition of fundamental vertices).
-The results are summarized in Figure \ref{plot2EC}.
-We also, implemented polyhedral version of Christofides' algorithm \cite{Wolsey1980} and compared its performance on fundamental extreme points with 10 vertices.
-The result are in Figure \ref{}.
+The result are summarized in Table \ref{tableTAP}.
+\begin{table}[h]
+	\centering
+	  \begin{tabular}{c c c c c}
+	  \toprule
+	  	& $C\in [1.1,1.2]\;$ & $\;C\in (1.2,1.3]\;$ &
+               $\;C\in (1.3,1.4]$ &\; $C\in (1.4,1.5]\;$ \\ \midrule
+	  	TAP & $36$ & $66$ & $170$ & $10$\\  \bottomrule \\
+	  \end{tabular}\caption{FDT impletemented applied to 264 randomly generated TAP instances with fractional extreme points: 138 of the 264 have $74$ variables, so the theoretical guarantee of Theorem \ref{binaryFDT} is at least $(1.5)^{74}$.
+For the rest, the number of variables in $250$.}
+	  \label{tableTAP}
+\end{table}
+Next we implemented the FDT for 2EC on a 963 fractional extreme points of $\EC(G)$.
+These points are obtained by considering all fundamental vertices with $10$ and $12$ vertices (See \cite{CV} for the definition of fundamental vertices).
+The results are summarized in Table \ref{table2EC}.
+\begin{table}[h]
+	\centering
+	  \begin{tabular}{c c c c c}
+	  	\toprule
+	  	& $C\in [1.08,1.11]\;$ & $\;C\in (1.11,1.14]\;$ &
+               $\;C\in (1.14,1.17]$ &\; $C\in (1.17,1.2]\;$ \\ \midrule
+	  	2EC & $79$ & $201$ & $605$ & $78$ \\ \bottomrule\\
+	  \end{tabular}\caption{FDT for $\EC$ implemented applied to all fundamental extreme points with 10 and 12 vertices.
+The number of variables for a fundamental extreme point with $k$ vertices is $\frac{3k}{2}$ and the lower bound on $g_\EC$ is $\frac{6}{5}$.}
+	  \label{table2EC}
+\end{table}
+We also implemented polyhedral version of Christofides' algorithm \cite{Wolsey1980} and compared its performance on fundamental extreme points with 10 vertices.
+The result are in Figure \ref{fdtvschris}.
+\begin{figure*}%
+\centering
+\includegraphics[width=8cm]{"fdt vs christofides".png}}
+\caption{Christofides' algorithm vs FDT on all fundamental extreme points with 10 vertices.}
+\label{fdtvschris}
+\end{figure*}

### 2018-11-20 IPCO format/introduction.tex
computational experminets

@@
 
-In attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem.
+In an attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem.
 In this problem we want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
@@
 
+\iffalse{
 Finally we give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems.
@@
 Notice that Theorem \ref{CV} requires the certificate convex combination to be ``cheap" on every single variable.
-
 \subsection{Notations}
@@
 For a set $S$ of vectors in $\bbbr_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.
+}\fi

### 2018-11-20 IPCO format/FDT.tex
computational experminets
intro modified

@@
 
-\keywords{Mixed-integer linear programming  \and  Integrality gap \and convex combiniations.}
+\keywords{Mixed-integer linear programming  \and  Integrality gap \and convex combinations.}
 \end{abstract}
@@
 	Robert Carr and Santosh Vempala.
-	\newblock On the held-karp relaxation for the asymmetric and symmetric
+	\newblock On the {H}eld-{K}arp relaxation for the asymmetric and symmetric
 	traveling salesman problems.
@@
 	\newblock {\em Operations Research Letters}, 36(4):399--401, 2008.
+
+	\bibitem{abe}
+    Anthony Alexander, Sylvia Boyd, and Paul Elliott-Magwood.
+    \newblock {On the Integrality Gap of the 2-Edge Connected Subgraph Problem}.
+    \newblock Technical report, University of Ottawa, Ottawa, Canada, 04 2006.
+
+    \bibitem{TSPcompute}
+    Geneviève Benoit and Sylvia Boyd.
+    \newblock Finding the exact integrality gap for small traveling salesman
+      problems.
+    \newblock {\em Mathematics of Operations Research}, 33(4):921--931, 2008.
 

### 2018-11-20 IPCO format/introduction.tex
intro modified

@@
 
-One key step, in answering Question \ref{question1} and \ref{question2} is being able to find a solution in $S(I)$.
-In fact, for general $I$ it is NP-hard to even decide if $S(I)$ is empty or not.
-There are a number of heuristics for this purpose, such as the feasibility pump heuristic \cite{fp1,fp2}.
-These heuristics are often very effective and fast in practice, however, they can sometimes fail in finding a feasible solution.
-In addition these algorithms do not provide any bounds on the quality of the solution they find.
-\subsection{Our results}
-In this paper we study Theorem \ref{CV} and the natural questions that follow from it (Questions \ref{question1} and \ref{question2}).
+If we relax Question \ref{question1} (resp.
+Question \ref{question2}), but multiplying $g(I)$ (resp.
+$g(\mathcal{I})$) by a factor $C$, they are still very interesting, since they will provide upper bounds on the integraltiy gap the instance (resp.
+the problem).
+The results in this paper serve this purpose.
 
@@
 \end{equation}
-For a vector $x\in \bbbr^n$ such that $(x,y)\in P(I)$ for some $y\in \bbbr^p$, let $\spp(x)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.
+For a vector $x\in \bbbr^n$ such that $(x,y)\in P(I)$ for some $y\in \bbbr^p$, let $\spp(x)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.
+
+The \textit{Fractional Decomposition Tree} algorithm (henceforth FDT) is a polynomial time algorithm that given a point $x\in P(I)$ produces a convex combination of feasible point in $S(I)$ that are dominates by a ``factor" of $x$.
+If this factor is $g_I$, it would settle Question \ref{question2}, however we can only guarantee a factor of $g_I^|\spp(x)|$.
+FDT relies on iteratively solving linear programs that are about the same size as the description of $P(I)$.
 
@@
 
-In an attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem.
+Note that for general $I$ it is NP-hard to even decide if $S(I)$ is empty or not.
+There are a number of heuristics for this purpose, such as the feasibility pump heuristic \cite{fp1,fp2}.
+These heuristics are often very effective and fast in practice, however, they can sometimes fail in finding a feasible solution.
+In addition these algorithms do not provide any bounds on the quality of the solution they find.
+
+One can trivially extend the FDT algorithm for binary MILPs into covering $\{0,1,2\}$-MILPs by losing a factor $2^{|\spp(x)|}$.
+In order to eradicate this factor, we need to treat the coordinate $i$ with $x_i=1$ differently.
+For  the 2-edge-connected subgraph problem we show how this can be done.
 In this problem we want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
@@
 We examine FDT for binary MILPs for problems such as the tree augmentation problem (TAP) and we apply FDT for 2EC on some interesting and ``hard to decompose" points in the linear relaxation.
+Our computational results show that the FDT algorithm is a good tool to evaluate the integrality gap of integer programming formulations.
+
+Evaluating the integrality gap for instances of interesting problems such as TSP or $\EC$ have been done by others as well.
+For instance, Benoit and Boyd \cite{TSPcompute} used a quadratic programming model to show that the integrality gap for TSP is at most $\frac{20}{17}$ for instances with at most 10 vertices.
+Also,  Alexander et.
+al \cite{abe} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $\EC$ on instances with at most 10 vertices.
+For $\EC$ we can show that the integrality gap of $\EC$ is at most $\frac{6}{5}$ for fundamental vertices with 12 vertices.
+In fact, since FDT can be applied to different problem, we can use it to evaluate the integrality gap of other well-known problem.
+For example, for TAP, we create random fractional extreme points and round them using FDT.
+For the instances that we create the blow-up factor is always below $\frac{3}{2}$ providing an upper bound for such instances.
 

### 2018-11-20 IPCO format/2ECFDT.tex
minor organization changes

@@
 Notice that $\dom(\EC(G))\cap [0,2]^{E} = \EC(G)$, since 2EC is a covering problem.
-We want to prove the following theorem.
-
-\FDTEC*
-
+We want to prove Theorem \ref{FDT2EC}.
 We do not know the exact value for $g_{\EC}$, but we know $\frac{6}{5} \leq g_{\EC} \leq \frac{3}{2}$ \cite{carr-ravi,Wolsey1980}.
@@
 we already have an algorithm with $C\leq \frac{3}{2}$.
-However, we show later in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$.
+However, we showed in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$ for fundamental extreme points with 10 vertices.
 
-The FDT algorithm for 2EC is very similar to the one for binary MIPs, but there are some differences as well.
-First, we need a branching lemma.
-Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for 0,1,2 problems expect for one additional clause.
+The FDT algorithm for 2EC is very similar to the one for binary MILPs, but there are some differences as well.
+A natural thing to do is to have three branches for each node of the FDT tree, however, the branches that are equivalent to setting a variable to $1$, might need further decomposition.
+That is the main difficulty when dealing with $\{0,1,2\}$-MILPs.
+
+First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for 0,1,2 problems expect for one additional clause.
 

### 2018-11-20 IPCO format/FDT.tex
minor organization changes

@@
 relationship between convex decomposition and integrality gaps, this algorithm can be seen as an approximation algorithm. We apply our algorithm our algorithm to a class of 
-fractional extreme points for two known problems in combinatorial optimization: the 2-edge-connected spanning subgraph problem and the tree augmentaion problem.
+fractional extreme points for two known problems in combinatorial optimization: the 2-edge-connected spanning subgraph problem and the tree augmentation problem.
 These computational experiments show that our algorithm can be used as a tool to evaluate the integrality gap of integer programs with their linear relaxation.
@@
 \input{binaryFDT.tex}
-\input{2ECFDT.tex}
 \input{computational}
@@
 \end{thebibliography}
+\newpage
+\appendix
 
-\appendix
-\section{Proof of Lemma 4}\label{lemma4}
-	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of Algorithm \ref{domtoIPalg} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
-	\begin{align*}
-	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
-	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
-	\end{align*}
-	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible.
-We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
-First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$.
-By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
-Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
-So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$.
-Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$.
-Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.
+\input{2ECFDT.tex}
 
-	Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$.
-Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.
-
-	We consider two cases.
-In the first case, we have $z^*_{\ell+1}=0$.
-In this case we have $x^{(\ell+1)}_{\ell+1}=0$.
-Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$.
-Also, $(z^*,w^*)\in P$.
-By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ .
-We have
-	\begin{equation}
-	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
-	\end{equation}
-	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$.
-Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$.
-Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$.
-We claim that $(z,w)\in \IP^{(\ell+1)}$.
-If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$.
-Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
-Consider iteration $j$ of Algorithm \ref{domtoIPalg}.
-Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.
-We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero.
-However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0.
-This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.
-
-	Now for the second case, assume $z^*_{\ell+1} > 0$.
-We have $x^{(\ell+1)}_{\ell+1}=1$.
-Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e.
-$z_{\ell+1}=1$.
-This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.
-
-	Now consider $(x^{(t)},y^{(t)})$.
-Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$.
-If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$.
-If $x^{(t)} =1$, it must be the case that $z_t > 0$.
-By the argument above there is a point $(z',w')\in \IP^{(t-1)}$.
-We show that $x^{(t)} = z'$.
-Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
-We just need to show that $z'_j = 1$.
-Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.
 \end{document}

### 2018-11-20 IPCO format/binaryFDT.tex
minor organization changes

@@
 \end{lemma}
-The proof is in Appendix \ref{lemma4}.
+
+\begin{proof}
+	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of Algorithm \ref{domtoIPalg} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
+	\begin{align*}
+	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
+	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
+	\end{align*}
+	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible.
+We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
+First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$.
+By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
+Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
+So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$.
+Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$.
+Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.
+
+	Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$.
+Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.
+
+	We consider two cases.
+In the first case, we have $z^*_{\ell+1}=0$.
+In this case we have $x^{(\ell+1)}_{\ell+1}=0$.
+Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$.
+Also, $(z^*,w^*)\in P$.
+By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ .
+We have
+	\begin{equation}
+	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
+	\end{equation}
+	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$.
+Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$.
+Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$.
+We claim that $(z,w)\in \IP^{(\ell+1)}$.
+If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$.
+Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
+Consider iteration $j$ of Algorithm \ref{domtoIPalg}.
+Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.
+We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero.
+However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0.
+This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.
+
+	Now for the second case, assume $z^*_{\ell+1} > 0$.
+We have $x^{(\ell+1)}_{\ell+1}=1$.
+Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e.
+$z_{\ell+1}=1$.
+This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.
+
+	Now consider $(x^{(t)},y^{(t)})$.
+Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$.
+If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$.
+If $x^{(t)} =1$, it must be the case that $z_t > 0$.
+By the argument above there is a point $(z',w')\in \IP^{(t-1)}$.
+We show that $x^{(t)} = z'$.
+Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
+We just need to show that $z'_j = 1$.
+Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.\end{proof}
 

### 2018-11-20 IPCO format/computational.tex
minor organization changes

@@
 \section{Computational experiments with FDT}\label{experiment}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=5.5cm]{"fdt vs christofides".png}
+\caption{Christofides' algorithm vs FDT on all fundamental extreme points with 10 vertices.}
+\label{fdtvschris}
+\end{figure}
 We implement FDT to two covering problem.
@@
 	  	TAP & $36$ & $66$ & $170$ & $10$\\  \bottomrule \\
-	  \end{tabular}\caption{FDT impletemented applied to 264 randomly generated TAP instances with fractional extreme points: 138 of the 264 have $74$ variables, so the theoretical guarantee of Theorem \ref{binaryFDT} is at least $(1.5)^{74}$.
+	  \end{tabular}\caption{FDT implemented applied to 264 randomly generated TAP instances with fractional extreme points: 138 of the 264 have $74$ variables, so the theoretical guarantee of Theorem \ref{binaryFDT} is at least $(1.5)^{74}$.
 For the rest, the number of variables in $250$.}
@@
 \end{table}
+\vspace*{-30pt}
 Next we implemented the FDT for 2EC on a 963 fractional extreme points of $\EC(G)$.
@@
 	  	2EC & $79$ & $201$ & $605$ & $78$ \\ \bottomrule\\
-	  \end{tabular}\caption{FDT for $\EC$ implemented applied to all fundamental extreme points with 10 and 12 vertices.
-The number of variables for a fundamental extreme point with $k$ vertices is $\frac{3k}{2}$ and the lower bound on $g_\EC$ is $\frac{6}{5}$.}
+	  \end{tabular}	\caption{FDT for $\EC$ implemented applied to all fundamental extreme points with 10 and 12 vertices.
+The number of variables for a fundamental extreme point with $k$ vertices is $\frac{3k}{2}$ and the lower bound on $g(\EC)$ is $\frac{6}{5}$}.
 	  \label{table2EC}
 \end{table}
+\vspace*{-30pt}
 We also implemented polyhedral version of Christofides' algorithm \cite{Wolsey1980} and compared its performance on fundamental extreme points with 10 vertices.
 The result are in Figure \ref{fdtvschris}.
-\begin{figure*}%
-\centering
-\includegraphics[width=8cm]{"fdt vs christofides".png}}
-\caption{Christofides' algorithm vs FDT on all fundamental extreme points with 10 vertices.}
-\label{fdtvschris}
-\end{figure*}

### 2018-11-20 IPCO format/introduction.tex
minor organization changes

@@
 The \textit{Fractional Decomposition Tree} algorithm (henceforth FDT) is a polynomial time algorithm that given a point $x\in P(I)$ produces a convex combination of feasible point in $S(I)$ that are dominates by a ``factor" of $x$.
-If this factor is $g_I$, it would settle Question \ref{question2}, however we can only guarantee a factor of $g_I^|\spp(x)|$.
+If this factor is $g_I$, it would settle Question \ref{question2}, however we can only guarantee a factor of $g_I^{|\spp(x)|}$.
 FDT relies on iteratively solving linear programs that are about the same size as the description of $P(I)$.
@@
 	Let $G=(V,E)$ and $x$ be an extreme point of  $\EC(G)$.
-The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq O(|V|)$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g_{\EC}^{O(|V|)}$, where $g_{\EC}$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol})
+The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq 2|V|-1$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
+Moreover, $C\leq g({\EC})^{k}$, where $g({\EC})$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol})
 \end{restatable}

### 2018-11-20 IPCO format/FDT.tex
lengend added
refrence added
Adding title, removing orchid and shortening affiliations (no addresses required)

@@
 \usepackage{graphicx}
+\usepackage{amsthm}
 % Used for displaying a sample figure. If possible, figure files should
@@
 %
-\title{FDT\thanks{Supported by organization x.}}
+\title{Fractional Decomposition Trees: A tool for studying mixed-integer-program integrality gaps}
+% \thanks{Supported by organization x.}}
 %
@@
 %
-\author{Robert Carr\inst{1}\orcidID{} \and
-Arash Haddadan\inst{2}\orcidID{} \and
-Cynthia Phillips\inst{3}\orcidID{}}
+\author{Robert D. Carr\inst{1} \and
+Arash Haddadan\inst{2} \and
+Cynthia A. Phillips\inst{3}}
+
+%\author{Robert Carr\inst{1}\orcidID{} \and
+%Arash Haddadan\inst{2}\orcidID{} \and
+%Cynthia Phillips\inst{3}\orcidID{}}
+
 %
@@
 %
-\institute{University of New Mexico, Albuquerque NM 87131, USA\\
-\email{bobcarr@unm.}\\   \and
-Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
-\email{ahaddada@cmu.edu}\and
-Sandia National Laboratories, Albuquerque, NM 87185, USA\\
-\email{caphill@sandia.gov}}
+% Shorter institutions
+\institute{University of New Mexico, \email{bobcarr@unm.}\\   \and
+Carnegie Mellon University, \email{ahaddada@cmu.edu}\and
+Sandia National Laboratories, \email{caphill@sandia.gov}}
+% Longer version
+%\institute{University of New Mexico, Albuquerque NM 87131, USA\\
+%\email{bobcarr@unm.}\\   \and
+%Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
+%\email{ahaddada@cmu.edu}\and
+%Sandia National Laboratories, Albuquerque, NM 87185, USA\\
+%\email{caphill@sandia.gov}}
 %
@@
 \begin{thebibliography}{10}
+
+	\bibitem[BC11]{Boyd-Carr-2011}
+	Sylvia Boyd and Robert Carr.
+	\newblock Finding low cost tsp and 2-matching solutions using certain
+	half-integer subtour vertices.
+	\newblock {\em Discrete Optimization}, 8(4):525--539, 2011.
 

### 2018-11-21 IPCO format/binaryFDT.tex
binaryFDT updated

@@
+\section{Finding a feasible solution}\label{domTOIP}
+Consider a formulation instance $I=(A,G,b)$.
+Define sets $S(I)$ and $P(I)$ as in (\ref{S'}) and (\ref{P'}), respectively.
+For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section.
+Also, for both sections we assume $t=|\spp(x)|$.
+Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$.
+
+In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
+\begin{lemma}\label{domlemma}
+	Given $(x,y)\in \dom(P)$, there is an algorithm (the DomToIP algorithm) that finds $(x^{(t)},y^{(t)})\in S$ in polynomial time, such that $x^{t}\leq x$, where $t=|\spp(x)|$\end{lemma}
+
+We prove Lemma \ref{domlemma} by introducing an algorithm that ``fixes" the variables iteratively, starting from $x_1$ and ending at $x_t$.
+Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$.
+Now consider the following linear program.
+The variables of this linear program are the $z\in \bbbr^n$ variables and $w\in \bbbr^p$.
+\begin{align}
+	\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
+	&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
+	&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
+	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
+	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
+\end{align}
+
+If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$.
+Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$.
+Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$.
+
+The above procedure suggests how to find $(x^{(\ell+1)},y^{(\ell+1)})$ from $(x^{(\ell)},y^{(\ell)})$.
+The DomToIP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$.
+\iffalse{
+\begin{algorithm}[H]
+	\KwIn{$(x,y)\in \dom(S)$}
+	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
+	$x^{(0)}\leftarrow x$\\
+	\For{$\ell = 0$ \textbf{to} $t-1$}{
+		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
+		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
+		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
+		\eIf{$\eta = 0$}{
+			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
+		}{
+			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
+		}
+	}
+	\label{domtoIPalg}
+	\caption{The DomToIP algorithm}
+\end{algorithm}
+}\fi
+We prove that indeed $(x^{(t)},y^{(t)})\in S$.
+
+	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomtoIP the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
+	\begin{align*}
+	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
+	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
+	\end{align*}
+	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible.
+We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
+First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$.
+By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
+Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
+So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$.
+Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$.
+Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.
+
+	Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$.
+Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.
+
+	We consider two cases.
+In the first case, we have $z^*_{\ell+1}=0$.
+In this case we have $x^{(\ell+1)}_{\ell+1}=0$.
+Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$.
+Also, $(z^*,w^*)\in P$.
+By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ .
+We have
+	\begin{equation}
+	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
+	\end{equation}
+	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$.
+Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$.
+Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$.
+We claim that $(z,w)\in \IP^{(\ell+1)}$.
+If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$.
+Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
+Consider iteration $j$ of the DomToIP algorithm.
+Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.
+We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero.
+However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0.
+This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.
+
+	Now for the second case, assume $z^*_{\ell+1} > 0$.
+We have $x^{(\ell+1)}_{\ell+1}=1$.
+Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e.
+$z_{\ell+1}=1$.
+This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.
+
+	Now consider $(x^{(t)},y^{(t)})$.
+Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$.
+If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$.
+If $x^{(t)} =1$, it must be the case that $z_t > 0$.
+By the argument above there is a point $(z',w')\in \IP^{(t-1)}$.
+We show that $x^{(t)} = z'$.
+Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
+We just need to show that $z'_j = 1$.
+Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.
+This concludes the proof of Lemma \ref{domlemma}.
+
+	Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: rounding up any fractional point in $P$ gives us a point in $\dom(P)$.
+
+\iffalse{
+\begin{algorithm}[H]\label{FDTFull}
+	\KwIn{$P= \{(x,y)\in \bbbr^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \bbbr^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
+	\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
+	$L^0\leftarrow [(x^*,y^*),1]$\\
+	\For{$i=1$ \textbf{to} $t$}{
+		$L'\leftarrow \emptyset$\\
+		\For{$[(x,y),\lambda] \in L^i$}{
+			Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
+			$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
+		}
+		Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
+	}
+	\For{$[(x,y),\lambda] \in L^t$}{
+		Apply Algorithm \ref{domtoIP} to $(x,y)$ to obtain $(z,w)\in S$\\
+		$F \leftarrow F \cup \{[(z,w),\lambda]\}$
+	}
+	\textbf{return} $F$
+	\caption{Fractional Decomposition Tree Algorithm}
+\end{algorithm}}\fi
+
 \section{FDT on binary MIPs}
@@
 
-In this section we present the fractional decomposition tree (FDT) algorithm and prove its correctness.
-
-Consider a formulation instance $I=(A,G,b)$.
-Define sets $S(I)$ and $P(I)$ as in (\ref{S'}) and (\ref{P'}), respectively.
-Also assume we are given a point $(x^*,y^*)\in P(I)$.
+Assume we are given a point $(x^*,y^*)\in P$.
 For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
-In this section, we prove Theorem \ref{binaryFDT}.
-One key ingredient in proving Theorem \ref{binaryFDT} is Theorem \ref{domtoIP} that we will also prove in this section.
-
-Although the theoretical worst-case upper bound on $C$ in the statement of Theorem \ref{binaryFDT} can be very large, we will show that in practice $C$ can be really small and hence FDT can provide good LP-based approximation algorithms in many cases.
-We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.
-In the remainder of this section we explain the FDT algorithm and prove Theorem \ref{binaryFDT}.
-For simplicity in the notation we denote $P(I),S(I),$ and $g_I$ with $P,S,$ and $g$, respectively.
-Let $t=|\spp(x^*)|$.
-We assume without loss of generality that $\spp(x^*)= \{1,\ldots,t\}$.
+In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm.
+\iffalse{We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution. }\fi
 
@@
 We will later see how we can turn these into points in $S$.
+
+\paragraph{Branching on a node}
 We begin with the following lemmas that show how the FDT algorithm branches on a variable.
@@
 
-Let us define the FDT algorithm more formally.
-The algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm.
+\paragraph{Growing and Pruning FDT tree} The FDT algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm.
 The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree.
@@
 \end{proof}
+\paragraph{From leaves of FDT to feasible solutions}
 The leaves of the FDT tree,  $L_t$, have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$.
-Our goal to now replace these leaves solutions in $\dom(P)$ with solutions in $S$.
-To this end, we need to reduce some variables with value of 1 into variables of value 0 and obtain feasibility in the meantime.
-We introduce a procedure that given a  point $(x,y)\in \dom(P)$ with $x\in \{0,1\}^n$ outputs a point $z\leq x$ with $z\in \{0,1\}^n$ such that $(z,w)$ is in $S$ for some vector $w\in \bbbr^p$.
-
-The algorithm ``fixes" the variables iteratively, from $x_1$ to $x_t$.
-Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$.
-Now consider the following linear program.
-The variables of this LP are the $z\in \bbbr^n$ variables and $w\in \bbbr^p$.
-\begin{align}
-	\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
-	&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
-	&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
-	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
-	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
-\end{align}
-
-If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$.
-Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$.
-Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$.
-This procedure is the DomToIP algorithm.
-\iffalse{
-\begin{algorithm}[H]
-	\KwIn{$(x,y)\in \dom(S)$}
-	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
-	$x^{(0)}\leftarrow x$\\
-	\For{$\ell = 0$ \textbf{to} $t-1$}{
-		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
-		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
-		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
-		\eIf{$\eta = 0$}{
-			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
-		}{
-			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
-		}
-	}
-	\label{domtoIPalg}
-	\caption{The DomToIP algorithm}
-\end{algorithm}
-}\fi
-The following lemma proves Theorem \ref{domtoIP}.
-\begin{lemma}
-	Given $(x,y)\in \dom(P)$, DomToIP algorithm correctly finds $(x^{(t)},y^{(t)})\in S$ in polynomial time.
-\end{lemma}
-
-\begin{proof}
-	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of Algorithm \ref{domtoIPalg} the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
-	\begin{align*}
-	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
-	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
-	\end{align*}
-	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible.
-We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
-First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$.
-By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
-Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
-So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$.
-Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$.
-Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.
-
-	Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in \{0,\ldots,t-2\}$.
-Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $(z^*,w^*)$.
-
-	We consider two cases.
-In the first case, we have $z^*_{\ell+1}=0$.
-In this case we have $x^{(\ell+1)}_{\ell+1}=0$.
-Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$.
-Also, $(z^*,w^*)\in P$.
-By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ .
-We have
-	\begin{equation}
-	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
-	\end{equation}
-	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$.
-Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$.
-Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$.
-We claim that $(z,w)\in \IP^{(\ell+1)}$.
-If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$.
-Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
-Consider iteration $j$ of Algorithm \ref{domtoIPalg}.
-Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.
-We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero.
-However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0.
-This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.
-
-	Now for the second case, assume $z^*_{\ell+1} > 0$.
-We have $x^{(\ell+1)}_{\ell+1}=1$.
-Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e.
-$z_{\ell+1}=1$.
-This means that $(z,w)\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.
-
-	Now consider $(x^{(t)},y^{(t)})$.
-Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$.
-If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$.
-If $x^{(t)} =1$, it must be the case that $z_t > 0$.
-By the argument above there is a point $(z',w')\in \IP^{(t-1)}$.
-We show that $x^{(t)} = z'$.
-Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
-We just need to show that $z'_j = 1$.
-Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.\end{proof}
-
-\iffalse{
-\begin{algorithm}[H]\label{FDTFull}
-	\KwIn{$P= \{(x,y)\in \bbbr^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \bbbr^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
-	\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
-	$L^0\leftarrow [(x^*,y^*),1]$\\
-	\For{$i=1$ \textbf{to} $t$}{
-		$L'\leftarrow \emptyset$\\
-		\For{$[(x,y),\lambda] \in L^i$}{
-			Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
-			$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
-		}
-		Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
-	}
-	\For{$[(x,y),\lambda] \in L^t$}{
-		Apply Algorithm \ref{domtoIP} to $(x,y)$ to obtain $(z,w)\in S$\\
-		$F \leftarrow F \cup \{[(z,w),\lambda]\}$
-	}
-	\textbf{return} $F$
-	\caption{Fractional Decomposition Tree Algorithm}
-\end{algorithm}}\fi
+By applying Lemma \ref{domlemma} we can obtain a point $(x',y')\in S$ such that $x'\leq x$.
+This conclude the description of the FDT algorithm and proves Theorem \ref{binaryFDT}.

### 2018-11-21 IPCO format/introduction.tex
First pass at intro changes

@@
 \section{Introduction}
-Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, is a classic NP-hard problem \cite{GJ79}.
-In fact it is NP-hard in general to determine if there is a feasible solution to an MILP problem \cite{GJ79}.
-However, intelligent branch-and-bound strategies allow commercial and open-source MIP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.
-Modeling combinatorial optimization problems with MILPs also started the very popular area of LP-based approximation algorithms.
 
-Consider the set of points described by a set 
+Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, models many practical optimization problems including scheduling, logistics and resource allocation.
+The set of feasible points for a MILP is the set
 \begin{equation}
-S(A,G,b)= \{(x,y)\in \bbbz^{n}\times \bbbr^p\;:\; Ax+Gy\geq b\}  \label{S}
+S(A,G,b)= \{(x,y)\in \bbbz^{n}\times \bbbr^p\;:\; Ax+Gy\geq b\}  \label{S}.
 \end{equation}
-and the  linear relaxation of set $S(A,G,b)$,
+If we drop the integrality constraints, we have the linear relaxation of set $S(A,G,b)$,
 \begin{equation}
@@
 
-To make the notation simpler we use $I=(A,G,b)$, i.e.
-an instance of the formulation.
-Then we use $S(I)$ and $P(I)$ to denote $S(A,G,b)$ and $P(A,G,b)$, respectively.
-Notice that $\min \;\{cx:\; (x,y) \in S(I)\}$ is in fact an MILP problem and $\min \;\{cx:\;(x,y)\in P(I) \}$ is lower bound provided from the LP relaxation.
-Let $z_{IP}(I,c)$ and $z_{LP}(I,c)$ be the optimal solution to these problems, respectively.
+Let $I=(A,G,b)$ be the feasible set of a specific instance.
+Then $S(I)$ and $P(I)$ denote $S(A,G,b)$ and $P(A,G,b)$, respectively.
+Given a linear objective function $c$, a MILP problem is $\min \;\{cx:\; (x,y) \in S(I)\}$.
+It is  NP-hard even to determine if a MILP instance has a feasible solution~\cite{GJ79}.
+However, intelligent branch-and-bound strategies allow commercial and open-source MIP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.
 
-Many researchers (see \cite{vazirani,sw}) have developed polynomial time algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$ for some $C$ which can be a constant number or dependent on some parameter of the MILP, e.g.
+Relaxing the integrality constraints gives the polynomial-time-solvable linear-programming relaxation: $\min \;\{cx:\;(x,y)\in P(I) \}$.
+The optimal value of this linear program (LP), denoted $z_{LP}(I,c)$, is a lower bound on the optimal value for the MILP, denoted $z_{IP}(I,c)$.
+The solution can also provide some useful global structure, even though the fractional values are not directly meaningful.
+{\em LP-based approximation algorithms} for combinatorial problems involve modeling the problem as a MILP, solving the LP relaxation, finding a (problem-specific) integer-feasible solution from the LP solution, and proving an approximation bound by comparing the solution value to the LP lower bound.
+
+Many researchers (see \cite{vazirani,sw}) have developed polynomial-time LP-based algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$.
+The approximation factor $C$ can be a constant or depend a MILP parameter, e.g.
 $O(\log(n))$.
 However, for many combinatorial optimization problems there is a limit to such techniques.
-Let $g_I= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$.
-Parameter $g_I$ depends on set $S(I)$ and the linear constraints in (\ref{S}) and is known as the \textit{integrality gap} of the formulation for instance $I$.
-It is easy to see, that we cannot hope to find solutions for the MILP with objective values better than $g_I\cdot z_{LP}(I,c)$.
-More generally we can define the integrality gap for a class of instances $\mathcal{I}$.
-In this case, the integrality gap for problem $\mathcal{I}$ is
+Define the \textit{integrality gap} of the MILP formulation for instance $I$ to be $g_I= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$.
+This value depends on the constraints in (\ref{S}).
+We cannot hope to find solutions for the MILP with objective values better than $g_I\cdot z_{LP}(I,c)$.
+
+More generally we can define the integrality gap for a class of instances $\mathcal{I}$:% In this case, the integrality gap for problem $\mathcal{I}$ is
 \begin{equation}
@@
 \end{equation}
+For example, finding a  minimum-weight 2-edge-connected multigraph has a natural formulation: constraining every cut to be crossed at least twice.
+The gap for this formulation is at most $\frac{3}{2}$ \cite{Wolsey1980} and at least $\frac{6}{5}$ \cite{carr-ravi}.
+Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation.
 
-For example, in the problem of finding a minimum weight 2-edge-connected multigraph, the gap of the the natural formulation, constraining every cut to be crossed at least twice, is at most $\frac{3}{2}$ \cite{Wolsey1980} and at least $\frac{6}{5}$ \cite{carr-ravi}.
-Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation.
-If we have $g_I=1$, $P(I)=\conv(S(I))$ and $P(I)$ is an \textit{integral} polyhedron.
-There are many interesting examples of such formulations such as spanning tree polytope and the perfect matching polytope \cite{schrijver}.
-For such problems we know how to write a vector $x\in P(I)$ as convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.
+\paragraph{The value of good MILP formulations:} There can be multiple correct MILP formulations for a problem with different integrality gaps.
+Finding MILP formulations with small integrality gap, e.g.
+by adding extra contraints, enables better provable approximation algorithms.
+Such formulations are also likely to work better in practice when using exact solvers because branch-and-bound algorithms for MILP use LP bounds to prove whole regions of the search space can be pruned.
+In this paper, we provide tools to help modelers develop MILP formulations with integrality gaps closer to the optimal.
 
+\paragraph{Decomposition} Our methods will take advantage of theory connecting integrality gaps to sets of feasible solutions.
+Instances $I$ with  $g_I=1$ has $P(I)=\conv(S(I))$ where $\conv(S(I))$ is the convex hull of the lattice of feasible points.
+In this case, $P(I)$ is an \textit{integral} polyhedron.
+The spanning-tree polytope and the perfect-matching polytope \cite{schrijver} have this property.
+For such problems there is an algorithm to express vector $x\in P(I)$ as a convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.
 \begin{proposition}\label{cara}
@@
 
-Now assume $1<g(I)<\infty$.
-Denote by $\dom(P(I))$ be the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$, also known as the dominant of $P(I)$.
-Notice that for covering problems the dominant of a polyhedron is essentially the same as its dominant, but for problems that are not covering, the two might be different.
-We show later, for $I$ with $g(I)<\infty$, the notation of dominant is in fact useful.
-
-A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}, which is a generalization of Goemans proof for blocking polyhedra \cite{goemans}.
+Carr and Vempala~\cite{CV} have a similar decomposition result for finite integrality gap $1<g(I)<\infty$.
+%A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}, which
+This is a generalization of Goemans' proof for blocking polyhedra \cite{goemans}.
 
@@
 \end{theorem}
+In this theorem $\dom(P(I))$ is the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$, also known as the dominant of $P(I)$.
+For covering problems the polyhedron is essentially the same as its dominant, but this is not true in general.
+In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
+%This points to an interesting open question. 
+% We show later, for $I$ with $g(I)<\infty$, the notation of dominant is in fact useful.
 
-In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
-This points to an interesting open question.
+\iffalse
 
@@
 The results in this paper serve this purpose.
+\fi
+
+To study integrality gaps, we wish to find such a solution contructively:
+\begin{question}\label{question2}
+	Assume reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g_{\mathcal{I}}<\infty$, and $(x,y)\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq $C$ g_{\mathcal{I}}x$ in polynomial time?
+We wish to find the smallest slack factor $C$ as possible.
+\end{question}
 
 We give a general approximation framework for solving $\{0,1\}$-MILPs.  Consider the set of point described by a set 
+\cindy{I think this next definition ($S(I)$) should have integer variables.
+It looks the same as P(I).
+Also, are these significantly different from the $S(I)$ and $P(I)$ defined above?
+We will likely have some space issues.}
 \begin{equation}
@@
 
-The \textit{Fractional Decomposition Tree} algorithm (henceforth FDT) is a polynomial time algorithm that given a point $x\in P(I)$ produces a convex combination of feasible point in $S(I)$ that are dominates by a ``factor" of $x$.
-If this factor is $g_I$, it would settle Question \ref{question2}, however we can only guarantee a factor of $g_I^{|\spp(x)|}$.
+The \textit{Fractional Decomposition Tree} algorithm (henceforth FDT) is a polynomial time algorithm that given a point $x\in P(I)$ produces a convex combination of feasible point in $S(I)$ that are dominated by a ``factor" $C$ of $x$.
+If $C = g_I$, it would be optimal.
+However we can only guarantee a factor of $g_I^{|\spp(x)|}$.
 FDT relies on iteratively solving linear programs that are about the same size as the description of $P(I)$.
@@
 
-Notice, that the FDT algorithm needs to find feasible solutions to any MILP with finite gap. This can be of independent interest.
+FDT finds feasible solutions to any MILP with finite gap. This can be of independent interest, especially in proving that a model has unbounded gap.
 \begin{restatable}{theorem}{DomToIP}
@@
 
-Note that for general $I$ it is NP-hard to even decide if $S(I)$ is empty or not.
+For general $I$ it is NP-hard to even decide if $S(I)$ is empty or not.
 There are a number of heuristics for this purpose, such as the feasibility pump heuristic \cite{fp1,fp2}.
-These heuristics are often very effective and fast in practice, however, they can sometimes fail in finding a feasible solution.
-In addition these algorithms do not provide any bounds on the quality of the solution they find.
+These heuristics are often very effective and fast in practice, however, they can sometimes fail to find a feasible solution.
+These heuristics do not provide any bounds on the quality of the solution they find.
+
+We consider the following TSP-related problems.
+The {\em 2-edge-connected subgraph problem (2EC)} want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
+In the {\em tree-augmentation problem (TAP)} we wish to add a minimum-cost set of edges to a tree to make it 2-edge-connected.
+We formally define TAP in Section~\ref{experiment}.
 
@@
 In order to eradicate this factor, we need to treat the coordinate $i$ with $x_i=1$ differently.
-For  the 2-edge-connected subgraph problem we show how this can be done.
-In this problem we want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
-For this problem the natural linear programming relaxation is
+The 2EC problem has the natural linear programming relaxation is
 \begin{equation}\label{2ECpol}
@@
 
-Although the bound guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are very large for large problems, we show that in practice, the algorithm works very well providing approximation ratios that are far better than the theoretical bound in the theorem statements.
-We examine FDT for binary MILPs for problems such as the tree augmentation problem (TAP) and we apply FDT for 2EC on some interesting and ``hard to decompose" points in the linear relaxation.
+\paragraph{Experiments} Although the bound guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are very large for large problems, we show that in practice, the algorithm works very well for the TSP-like problems described above.
+We show how one might use FDT to investigate the integrality gap for such well-studied problems.
+
+Known polyhedral structure makes it easier to study integrality gaps for such problems. 
+\cindy{Is this right?  That citation is for Carr and Vempala.}
+Carr and Ravi \cite{CV} introduced the notion of fundamental extreme points.
+A point x in Held-Karp relaxation for TSP (or 2EC; they have the same relaxation) is a point whose support of $x$, namely $G_x$ satisfies the following: i)  $G_x$ is a cubic graph, ii) in $G_x$ there is exactly one edge with $x_e=1$ incident to each node iii) The fractional edges of $G_x$ form a Hamiltonian cycle.
+We say a fundamental extreme point (FEP) is {\em order $k$} if there are $k$ nodes on this Hamiltonian cycle.
+An FEP of order $k$ could represent an instance with many more than $k$ vertices.
+Carr and co-authors~\cite{CV,carr-ravi,Boyd-Carr-2011} proved that showing that $Cx$ is a convex combination of tours (resp.
+2-edge-connected subgraphs) for all fundamental extreme points is equivalent to proving that the integrality gap for TSP (resp.
+2EC) is bounded above by $C$.
+Thus we can create the ``hardest'' LP solutions to decompose.
+
+There are fairly good bounds known for the integrality gap for TSP or $\EC$.
+\cindy{Arash, please confirm this change is correct.}Benoit and Boyd \cite{TSPcompute} used a quadratic programming model to show that the integrality gap for TSP is at most $\frac{20}{17}$ for FEPs of order at most 10.
+Also,  Alexander et.
+al \cite{abe} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $\EC$ on FEPs of order at most 10.
+For $\EC$ we can show that the integrality gap of $\EC$ is at most $\frac{6}{5}$ for FEPs of order at most 12.
+%In fact, since FDT can be applied to different problem, we can use it to evaluate the integrality gap of other well-known problem.
+For TAP, we create random fractional extreme points and round them using FDT.
+For the instances that we create the blow-up factor is always below $\frac{3}{2}$ providing an upper bound for such instances.
+
+% providing approximation ratios that are far better than the theoretical bound in the theorem statements.
+%We examine FDT for binary MILPs for problems such as the tree augmentation problem (TAP) and we apply FDT for 2EC on some interesting and ``hard to decompose" points in the linear relaxation.
 Our computational results show that the FDT algorithm is a good tool to evaluate the integrality gap of integer programming formulations.
 
-Evaluating the integrality gap for instances of interesting problems such as TSP or $\EC$ have been done by others as well.
-For instance, Benoit and Boyd \cite{TSPcompute} used a quadratic programming model to show that the integrality gap for TSP is at most $\frac{20}{17}$ for instances with at most 10 vertices.
-Also,  Alexander et.
-al \cite{abe} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $\EC$ on instances with at most 10 vertices.
-For $\EC$ we can show that the integrality gap of $\EC$ is at most $\frac{6}{5}$ for fundamental vertices with 12 vertices.
-In fact, since FDT can be applied to different problem, we can use it to evaluate the integrality gap of other well-known problem.
-For example, for TAP, we create random fractional extreme points and round them using FDT.
-For the instances that we create the blow-up factor is always below $\frac{3}{2}$ providing an upper bound for such instances.
+\paragraph{Contributions}  The paper has the following contributions: 
+\begin{itemize}
+\item We give a simple algorithm, Dom2IP, that can prove a formulation’s integrality gap is unbounded.
+Someone formulating a first MILP for a new problem can test it with Dom2IP.
+If the algorithm ever fails, the MILP has an unbounded gap.
+\item We give an algorithm, Fractional Decomposition Tree (FDT), to construct the convex decomposition in the Carr-Vempala theorem, perhaps scaling by a factor larger than the integrality gap.
+Each step of this algorithm provides a {\em lower bound} on the instances integrality gap.
+This also provides a lower bound on the approximation factor of any LP-based approximation algorithm using this formulation.
+\item For a special set of problems related to TSP, where there is a notion of a fundamental extreme point and long-running attempts to exactly determine the integrality gap of classic formulations, experimental analysis with FDT can help give some intuition about which bound(s) is/are likely to be loose.
+Computing on fundamental extreme points is a way to experimentally characterize the gap upper bound.
+There is no guarantee.
+Still, this can help direct theoretical analysis in the most promising direction.
+Furthermore, for these kinds of problems, especially 2EC, FDT gives good approximate solutions, better than the best current competitor (Christofides).
+\end{itemize}
 

### 2018-11-21 IPCO format/FDT.tex
Abstract update

@@
 \begin{abstract}
-We present a new algorithm for finding a feasible solution for a mixed-integer linear program. The algorithm runs in polynomial time and is guaranteed to find a feasible integer solution provided the
-integrality gap is bounded. The algorithm is based on convex decomposition of scaled linear-
-programming relaxations, so in general it provides a suite of integer solutions. Because of the
-relationship between convex decomposition and integrality gaps, this algorithm can be seen as an approximation algorithm. We apply our algorithm our algorithm to a class of 
-fractional extreme points for two known problems in combinatorial optimization: the 2-edge-connected spanning subgraph problem and the tree augmentation problem.
-These computational experiments show that our algorithm can be used as a tool to evaluate the integrality gap of integer programs with their linear relaxation.
-Finally we provide a stronger characterization of integrality gap for a class of covering problems than that of \cite{goemans}.
+We present a new algorithm/tool for studying integrality gaps of mixed-integer linear programming formulations.
+The algorithm is based on convex decomposition of scaled linear-programming relaxations.
+The relationship between convex decomposition and integrality gaps provides both integrality-gap information and approximate solutions.
+% The algorithm finds a feasible solution for a mixed-integer linear program.
+Our algorithm runs in polynomial time and is guaranteed to find a feasible integer solution provided the
+integrality gap is bounded.  Thus when the algorithm fails, it proves an unbounded integrality gap.  The algorithm also provides a lower
+bound on the instance integrality gap at each step. 
+% so in general it provides a suite of integer solutions.
+%, this algorithm can be seen as an approximation algorithm. 
+We apply our algorithm to a class of 
+fractional extreme points for two traveling-salesman-like problems: 2-edge-connected spanning subgraph (2EC) and tree augmentation.
+These experiments provide insight into the current gap bounds.  Furthermore, for 2EC, the approximate solutions are consistently better than the best previous
+approximation algorithm due to Christofides.
+%These computational experiments show that our algorithm can be used as a tool to evaluate the integrality gap of integer programs with their linear relaxation.
+% Finally we provide a stronger characterization of integrality gap for a class of covering problems than that of \cite{goemans}.
 

### 2018-11-21 IPCO format/introduction.tex
comment applied in intro

@@
 It is  NP-hard even to determine if a MILP instance has a feasible solution~\cite{GJ79}.
-However, intelligent branch-and-bound strategies allow commercial and open-source MIP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.
+However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.
 
@@
 
-We give a general approximation framework for solving $\{0,1\}$-MILPs.  Consider the set of point described by a set 
-\cindy{I think this next definition ($S(I)$) should have integer variables.
-It looks the same as P(I).
-Also, are these significantly different from the $S(I)$ and $P(I)$ defined above?
-We will likely have some space issues.}
-\begin{equation}
-S(I)= \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'} 
-\end{equation}
-and a linear relaxation of set $S$
-\begin{equation}
-P(I) = \{(x,y)\in \bbbr^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
-\end{equation}
+We give a general approximation framework for solving $\{0,1\}$-MILPs.
+Consider the set of point described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively.
+Assume in addition that $S(I),P(I)\subseteq [0,1]^n\times \bbbr^p$.
 For a vector $x\in \bbbr^n$ such that $(x,y)\in P(I)$ for some $y\in \bbbr^p$, let $\spp(x)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.
@@
 
-One can trivially extend the FDT algorithm for binary MILPs into covering $\{0,1,2\}$-MILPs by losing a factor $2^{|\spp(x)|}$.
+One can extend the FDT algorithm for binary MILPs into covering $\{0,1,2\}$-MILPs by losing a factor $2^{|\spp(x)|}$.
 In order to eradicate this factor, we need to treat the coordinate $i$ with $x_i=1$ differently.
@@
 \cindy{Is this right?  That citation is for Carr and Vempala.}
-Carr and Ravi \cite{CV} introduced the notion of fundamental extreme points.
+Carr and Ravi \cite{carr-ravi} introduced the notion of fundamental extreme points.
 A point x in Held-Karp relaxation for TSP (or 2EC; they have the same relaxation) is a point whose support of $x$, namely $G_x$ satisfies the following: i)  $G_x$ is a cubic graph, ii) in $G_x$ there is exactly one edge with $x_e=1$ incident to each node iii) The fractional edges of $G_x$ form a Hamiltonian cycle.
@@
 There are fairly good bounds known for the integrality gap for TSP or $\EC$.
-\cindy{Arash, please confirm this change is correct.}Benoit and Boyd \cite{TSPcompute} used a quadratic programming model to show that the integrality gap for TSP is at most $\frac{20}{17}$ for FEPs of order at most 10.
+\cindy{Arash, please confirm this change is correct.}Benoit and Boyd \cite{TSPcompute} used a quadratic programming model to show that the integrality gap for TSP is at most $\frac{20}{17}$ for graphs with at most 10 vertices.
 Also,  Alexander et.
-al \cite{abe} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $\EC$ on FEPs of order at most 10.
+al \cite{abe} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $\EC$ on graphs with at most 10 vertices.
 For $\EC$ we can show that the integrality gap of $\EC$ is at most $\frac{6}{5}$ for FEPs of order at most 12.
@@
 \begin{itemize}
-\item We give a simple algorithm, Dom2IP, that can prove a formulation’s integrality gap is unbounded.
+\item We give a simple algorithm, Dom2IP, that can prove a formulation’s integrality gap is unbounded or if not provide a feasible integer solution.
 Someone formulating a first MILP for a new problem can test it with Dom2IP.
-If the algorithm ever fails, the MILP has an unbounded gap.
+If the algorithm ever fails in finding a feasible solution, the MILP has an unbounded gap.
 \item We give an algorithm, Fractional Decomposition Tree (FDT), to construct the convex decomposition in the Carr-Vempala theorem, perhaps scaling by a factor larger than the integrality gap.
@@
 This also provides a lower bound on the approximation factor of any LP-based approximation algorithm using this formulation.
+The overall approximation factor of the FDT algorithm is an upper bound on the integrality gap for that specific instance.
 \item For a special set of problems related to TSP, where there is a notion of a fundamental extreme point and long-running attempts to exactly determine the integrality gap of classic formulations, experimental analysis with FDT can help give some intuition about which bound(s) is/are likely to be loose.

### 2018-11-21 IPCO format/computational.tex
pass through this section

--- 2018-11-19 IPCO format/computational.tex
@@
 \section{Computational experiments with FDT}\label{experiment}
-We implement FDT to two covering problem.
-First, the tree argumentation problem (TAP) where given a tree $T=(V,E)$, and a set of link $L$ between the vertices in $V$ and costs $c\in \bbbr^{L}_{\geq 0}$ we with to find minimum cost subset $L'$ of $L$ such that $T+L'$ is 2-edge-connected.
+We ran FDT on two covering problem: TAP and 2EC.
+For the tree augmentation problem (TAP) we are given a tree $T=(V,E)$, and a set of non-edge links $L$ between the vertices in $V$ and costs $c\in \bbbr^{L}_{\geq 0}$.
+We wish to find the minimum-cost subset $L'$ of $L$ such that $T+L'$ is 2-edge-connected.
 For $\ell\in L$, let $P_\ell$ be the set of edges in the unique path between the endpoints of $\ell$ in $T$.
@@
 Relaxing the integrality constraint we get $P(\mbox{TAP})$.
-It is been shown that $\frac{3}{2}\leq g({\mbox{TAP}})\leq 2$ \cite{fj,32gap}.
+We know $\frac{3}{2}\leq g({\mbox{TAP}})\leq 2$~\cite{fj,32gap}.
 We applied the binary FDT algorithm on a set of 264 fractional extreme points of $P(\mbox{TAP})$.
-The result are summarized in Figure \ref{plotTAP}.
-
-Next we implemented the FDT for 2EC on a 900 fractional extreme points of $\EC(G)$.
-These points are obtained by considering all fundamental vertices with $12$ vertices (See \cite{CV} for the definition of fundamental vertices).
-The results are summarized in Figure \ref{plot2EC}.
-We also, implemented polyhedral version of Christofides' algorithm \cite{Wolsey1980} and compared its performance on fundamental extreme points with 10 vertices.
-The result are in Figure \ref{}.
+The result are summarized in Table \ref{tableTAP}.
+FDT found solutions better than the integrality-gap lower bound for most instances.
+\begin{table}[h]
+	\centering
+	  \begin{tabular}{c c c c c}
+	  \toprule
+	  	& $C\in [1.1,1.2]\;$ & $\;C\in (1.2,1.3]\;$ &
+               $\;C\in (1.3,1.4]$ &\; $C\in (1.4,1.5]\;$ \\ \midrule
+	  	TAP & $36$ & $66$ & $170$ & $10$\\  \bottomrule \\
+	  \end{tabular}\caption{The scale factor $C$ for FDT when run on 264 randomly generated tree-augmentation (TAP) instances with fractional extreme points: 138 of the 264 have $74$ variables.
+The rest have $250$ variables.}
+	  \label{tableTAP}
+\end{table}
+%\vspace*{-30pt}
+We ran FDT for 2EC on 963 fractional extreme points of $\EC(G)$.
+We enumerated all fundamental vertices of order $10$ and $12$.
+Table \ref{table2EC} shows that again FDT found solutions better than the integrality-gap lower bound for most instances.
+\begin{table}[h]
+	\centering
+	  \begin{tabular}{c c c c c}
+	  	\toprule
+	  	& $C\in [1.08,1.11]\;$ & $\;C\in (1.11,1.14]\;$ &
+               $\;C\in (1.14,1.17]$ &\; $C\in (1.17,1.2]\;$ \\ \midrule
+	  	2EC & $79$ & $201$ & $605$ & $78$ \\ \bottomrule\\
+	  \end{tabular}	\caption{FDT for $\EC$ implemented applied to all fundamental extreme points of order 10 or 12.
+A fundamental extreme point or order $k$ has $\frac{3k}{2}$ variables.
+The lower bound on $g(\EC)$ is $\frac{6}{5}$.}
+	  \label{table2EC}
+\end{table}
+We also implemented the polyhedral version of Christofides' algorithm \cite{Wolsey1980}.
+Figure \ref{fdtvschris} shows FDT's solutions on fundamental extreme points of order 10 are always better than those from Christofides' algorithm.
+%\vspace*{-.5in}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=9cm]{"fdt vs christofides".png}
+\caption{Christofides' algorithm vs FDT on all fundamental extreme points of order 10.}
+\label{fdtvschris}
+\end{figure}

### 2018-11-21 IPCO format/binaryFDT.tex
Dom2IP fixed

@@
 \begin{lemma}\label{domlemma}
-	Given $(x,y)\in \dom(P)$, there is an algorithm (the DomToIP algorithm) that finds $(x^{(t)},y^{(t)})\in S$ in polynomial time, such that $x^{t}\leq x$, where $t=|\spp(x)|$\end{lemma}
+	Given $(x,y)\in \dom(P)$, there is an algorithm (the Dom2IP algorithm) that finds $(x^{(t)},y^{(t)})\in S$ in polynomial time, such that $x^{t}\leq x$, where $t=|\spp(x)|$\end{lemma}
 
@@
 The above procedure suggests how to find $(x^{(\ell+1)},y^{(\ell+1)})$ from $(x^{(\ell)},y^{(\ell)})$.
-The DomToIP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$.
+The Dom2IP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$.
 \iffalse{
@@
 	\label{domtoIPalg}
-	\caption{The DomToIP algorithm}
+	\caption{The Dom2IP algorithm}
 \end{algorithm}
@@
 Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
-Consider iteration $j$ of the DomToIP algorithm.
+Consider iteration $j$ of the Dom2IP algorithm.
 Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.

### 2018-11-21 IPCO format/2ECFDT.tex
typo fixed

@@
 
-First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for 0,1,2 problems expect for one additional clause.
+First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for 0,1,2 problems except for one additional clause.
 
@@
 We can also show that $\gamma_0+\gamma_1+\gamma_2\geq \frac{1}{g_{\EC}}$, which means that (i) is also satisfied.
-The proof is similar to the proof of the claim in Lemma \ref{LPClemma}, but we need to replace each $f\in E$ with $x_f\geq 0$ with a suitably long path to ensure that Constraint (\ref{1edges2ec}) is also satisfied.	We skip the details.\iffalse{
+The proof is similar to the proof of the claim in Lemma \ref{LPClemma}, but we need to replace each $f\in E$ with $x_f\geq 1$ with a suitably long path to ensure that Constraint (\ref{1edges2ec}) is also satisfied.	We skip the details.\iffalse{
 	\begin{claim}\label{CVexists}
@@
 
-In contrast to FDT for binary MIPs where we round up the fractional variables that are already branched on at each level, in FDT for 2EC we keep all coordinates as they are and preform a rounding procedure at the end.
+In contrast to FDT for binary MIPs where we round up the fractional variables that are already branched on at each level, in FDT for 2EC we keep all coordinates as they are and perform a rounding procedure at the end.
 Formally, let $L_i$ for $i=1,\ldots,|\spp(x^*)|$ be collections of pairs of feasible points in $\EC(G)$ together with their multipliers.

### 2018-11-21 IPCO format/introduction.tex
little fix
lemma2 proof

@@
 An FEP of order $k$ could represent an instance with many more than $k$ vertices.
-Carr and co-authors~\cite{CV,carr-ravi,Boyd-Carr-2011} proved that showing that $Cx$ is a convex combination of tours (resp.
+Carr and co-authors~\cite{CV,carr-ravi, Boyd-Carr-2011} proved that showing that $Cx$ is a convex combination of tours (resp.
 2-edge-connected subgraphs) for all fundamental extreme points is equivalent to proving that the integrality gap for TSP (resp.
@@
 For $\EC$ we can show that the integrality gap of $\EC$ is at most $\frac{6}{5}$ for FEPs of order at most 12.
+Notice an FEP of order $k$ might correspond to an extreme point of a much bigger graph, since each edge in a FEP with value 1, actually corresponds to a path of edges with value 1.
 %In fact, since FDT can be applied to different problem, we can use it to evaluate the integrality gap of other well-known problem.

### 2018-11-21 IPCO format/introduction.tex
comments removed

@@
 Known polyhedral structure makes it easier to study integrality gaps for such problems.
-\cindy{Is this right?  That citation is for Carr and Vempala.}
 Carr and Ravi \cite{carr-ravi} introduced the notion of fundamental extreme points.
@@
 There are fairly good bounds known for the integrality gap for TSP or $\EC$.
-\cindy{Arash, please confirm this change is correct.}Benoit and Boyd \cite{TSPcompute} used a quadratic programming model to show that the integrality gap for TSP is at most $\frac{20}{17}$ for graphs with at most 10 vertices.
+Benoit and Boyd \cite{TSPcompute} used a quadratic programming model to show that the integrality gap for TSP is at most $\frac{20}{17}$ for graphs with at most 10 vertices.
 Also,  Alexander et.

### 2018-11-21 IPCO format/computational.tex
typo fixed
compress

@@
 \section{Computational experiments with FDT}\label{experiment}
-We ran FDT on two covering problem: TAP and 2EC.
-For the tree augmentation problem (TAP) we are given a tree $T=(V,E)$, and a set of non-edge links $L$ between the vertices in $V$ and costs $c\in \bbbr^{L}_{\geq 0}$.
-We wish to find the minimum-cost subset $L'$ of $L$ such that $T+L'$ is 2-edge-connected.
+We ran FDT on two covering problem: tree augmentation (TAP) and 2EC.
+For TAP we are given a tree $T=(V,E)$, and a set of non-edges $L$ between vertices in $V$ and costs $c\in \bbbr^{L}_{\geq 0}$.
+We wish to find the minimum-cost  $L'\subseteq L$ such that $T+L'$ is 2-edge-connected.
 For $\ell\in L$, let $P_\ell$ be the set of edges in the unique path between the endpoints of $\ell$ in $T$.
-For TAP, $S(\mbox{TAP})=\{x\in \bbbz^{L}_{\geq 0}: \sum_{\ell: e\in P_\ell}x_\ell \geq 1, \mbox{ for $e\in E$}\}$.
-Relaxing the integrality constraint we get $P(\mbox{TAP})$.
+For TAP, $S(\mbox{TAP})=\{x\in \bbbz^{L}_{\geq 0}: \sum_{\ell: e\in P_\ell}x_\ell \geq 1, \mbox{ for $e\in E$}\}$ and $P(\mbox{TAP})$ relaxes integrality.
 We know $\frac{3}{2}\leq g({\mbox{TAP}})\leq 2$~\cite{fj,32gap}.
-We applied the binary FDT algorithm on a set of 264 fractional extreme points of $P(\mbox{TAP})$.
-The result are summarized in Table \ref{tableTAP}.
-FDT found solutions better than the integrality-gap lower bound for most instances.
+We ran binary FDT on a set of 264 fractional extreme points of $P(\mbox{TAP})$.
+Table \ref{tableTAP} shows FDT found solutions better than the integrality-gap lower bound for most instances.
 \begin{table}[h]
@@
 	  \end{tabular}	\caption{FDT for $\EC$ implemented applied to all fundamental extreme points of order 10 or 12.
-A fundamental extreme point or order $k$ has $\frac{3k}{2}$ variables.
+A FEP of order $k$ has $\frac{3k}{2}$ variables.
 The lower bound on $g(\EC)$ is $\frac{6}{5}$.}

### 2018-11-21 IPCO format/introduction.tex
compress

@@
 \end{equation}
-For example, finding a  minimum-weight 2-edge-connected multigraph has a natural formulation: constraining every cut to be crossed at least twice.
+For example, finding a  minimum-weight 2-edge-connected multigraph has a natural formulation: every cut is crossed at least twice.
 The gap for this formulation is at most $\frac{3}{2}$ \cite{Wolsey1980} and at least $\frac{6}{5}$ \cite{carr-ravi}.
@@
 
-\paragraph{Decomposition} Our methods will take advantage of theory connecting integrality gaps to sets of feasible solutions.
-Instances $I$ with  $g_I=1$ has $P(I)=\conv(S(I))$ where $\conv(S(I))$ is the convex hull of the lattice of feasible points.
+\paragraph{Decomposition} Our methods apply theory connecting integrality gaps to sets of feasible solutions.
+Instances $I$ with  $g_I=1$ has $P(I)=\conv(S(I))$, the convex hull of the lattice of feasible points.
 In this case, $P(I)$ is an \textit{integral} polyhedron.

### 2018-11-21 IPCO format/FDT.tex
Fixed problem with a reference
typo fixed

@@
 % Shorter institutions
-\institute{University of New Mexico, \email{bobcarr@unm.}\\   \and
+\institute{University of New Mexico, \email{bobcarr@unm.edu}\\   \and
 Carnegie Mellon University, \email{ahaddada@cmu.edu}\and
@@
 
-	\bibitem[BC11]{Boyd-Carr-2011}
+	\bibitem{Boyd-Carr-2011}
 	Sylvia Boyd and Robert Carr.

### 2018-11-21 IPCO format/introduction.tex
compress

@@
 
-Carr and Vempala~\cite{CV} have a similar decomposition result for finite integrality gap $1<g(I)<\infty$.
+Carr and Vempala~\cite{CV} gave a decomposition result for integrality gap $1<g(I)<\infty$.
 %A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}, which
@@
 \end{theorem}
-In this theorem $\dom(P(I))$ is the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$, also known as the dominant of $P(I)$.
+Here $\dom(P(I))$ is the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$, also known as the dominant of $P(I)$.
 For covering problems the polyhedron is essentially the same as its dominant, but this is not true in general.
-In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
+While there is an exact algorithm for problems with gap $1$, Theorem~\ref{CV} is existenial, with no construction.
+%In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
 %This points to an interesting open question. 
 % We show later, for $I$ with $g(I)<\infty$, the notation of dominant is in fact useful.
-
 \iffalse
 
-\begin{question}\label{question1}
+\begin{question*}\label{question1}
 	Assume reasonable complexity assumptions (such as UGC or $\textrm{P}\neq \textrm{NP}$).
 Given instance $I$ with $1<g_I<\infty$ and $(x,y)\in P(I)$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(\conv(S(I)))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_Ix$ in polynomial time?
-\end{question}
+\end{question*}
 
@@
 \fi
-
 To study integrality gaps, we wish to find such a solution contructively:

### 2018-11-21 IPCO format/binaryFDT.tex
lemma2 proof
fix

@@
 Consider a formulation instance $I=(A,G,b)$.
-Define sets $S(I)$ and $P(I)$ as in (\ref{S'}) and (\ref{P'}), respectively.
+Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively.
+And assume $S(I),P(I)\in [0,1]^n\times \bbbr^p$.
 For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section.
@@
 	\end{proof}
-	This concludes the proof.	
+	This concludes the proof of Lemma \ref{LPClemma}.	
 \end{proof}
@@
 Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$.
-Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$.
+Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \t\label{key}heta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$.
 \end{proof}

### 2018-11-21 IPCO format/binaryFDT.tex
stuff

@@
 \paragraph{From leaves of FDT to feasible solutions}
-The leaves of the FDT tree,  $L_t$, have the property that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$.
+For the leaves of the FDT tree,  $L_t$, we have that every solution $(x,y)$ in $L_t$ has $x\in\{0,1\}^n$ and $(x,y)\in \dom(P)$.
 By applying Lemma \ref{domlemma} we can obtain a point $(x',y')\in S$ such that $x'\leq x$.

### 2018-11-21 IPCO format/introduction.tex
bibtex fix
stuff

@@
 
-The \textit{Fractional Decomposition Tree} algorithm (henceforth FDT) is a polynomial time algorithm that given a point $x\in P(I)$ produces a convex combination of feasible point in $S(I)$ that are dominated by a ``factor" $C$ of $x$.
+\textit{Fractional Decomposition Tree} (FDT) is a polynomial-time algorithm that given a point $x\in P(I)$ produces a convex combination of feasible points in $S(I)$ that are dominated by a ``factor" $C$ of $x$.
 If $C = g_I$, it would be optimal.
@@
 \EC(G)= \{x\in \bbbr_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
-We prove the following theorem.
+% We prove the following theorem.
 
@@
 Known polyhedral structure makes it easier to study integrality gaps for such problems.
-Carr and Ravi \cite{carr-ravi} introduced the notion of fundamental extreme points.
+Carr and Ravi \cite{carr-ravi} introduced fundamental extreme points.
 A point x in Held-Karp relaxation for TSP (or 2EC; they have the same relaxation) is a point whose support of $x$, namely $G_x$ satisfies the following: i)  $G_x$ is a cubic graph, ii) in $G_x$ there is exactly one edge with $x_e=1$ incident to each node iii) The fractional edges of $G_x$ form a Hamiltonian cycle.
@@
 
-There are fairly good bounds known for the integrality gap for TSP or $\EC$.
-Benoit and Boyd \cite{TSPcompute} used a quadratic programming model to show that the integrality gap for TSP is at most $\frac{20}{17}$ for graphs with at most 10 vertices.
-Also,  Alexander et.
+There are fairly good bounds for the integrality gap for TSP or $\EC$.
+Benoit and Boyd \cite{TSPcompute} used a quadratic program to show the integrality gap for TSP is at most $\frac{20}{17}$ for graphs with at most 10 vertices.
+Alexander et.
 al \cite{abe} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $\EC$ on graphs with at most 10 vertices.
-For $\EC$ we can show that the integrality gap of $\EC$ is at most $\frac{6}{5}$ for FEPs of order at most 12.
-Notice an FEP of order $k$ might correspond to an extreme point of a much bigger graph, since each edge in a FEP with value 1, actually corresponds to a path of edges with value 1.
+For $\EC$ we show that the integrality gap is at most $\frac{6}{5}$ for FEPs of order at most 12.
+An FEP of order $k$ might correspond to an extreme point of a much bigger graph, since each edge in a FEP with value 1 actually corresponds to a path of edges with value 1.
 %In fact, since FDT can be applied to different problem, we can use it to evaluate the integrality gap of other well-known problem.

### 2018-11-21 IPCO format/binaryFDT.tex
stuff

@@
 Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$.
-Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \t\label{key}heta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$.
+Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$.
 \end{proof}

### 2018-11-21 IPCO format/introduction.tex
foo

@@
 
-We consider the following TSP-related problems.
-The {\em 2-edge-connected subgraph problem (2EC)} want to find the minimum weight 2-edge-connected subgraph (which can multiple copies of each edge) in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
+We consider the following TSP-related problems.  The {\em 2-edge-connected subgraph problem (2EC)} is to find a minimum-weight 2-edge-connected (multigraph) subgraph
+% (which can multiple copies of each edge)
+in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
 In the {\em tree-augmentation problem (TAP)} we wish to add a minimum-cost set of edges to a tree to make it 2-edge-connected.
@@
 An FEP of order $k$ could represent an instance with many more than $k$ vertices.
-Carr and co-authors~\cite{CV,carr-ravi, Boyd-Carr-2011} proved that showing that $Cx$ is a convex combination of tours (resp.
+Carr and co-authors~\cite{CV,carr-ravi, BC11} proved that showing that $Cx$ is a convex combination of tours (resp.
 2-edge-connected subgraphs) for all fundamental extreme points is equivalent to proving that the integrality gap for TSP (resp.

### 2018-11-21 IPCO format/computational.tex
foo
Final version, I think.

@@
 \section{Computational experiments with FDT}\label{experiment}
+\begin{figure}[h!]
+\centering
+\includegraphics[width=6.5cm]{"fdt vs christofides".png}
+\caption{Christofides' algorithm vs FDT on all fundamental extreme points of order 10.}
+\label{fdtvschris}
+\end{figure}
+
 We ran FDT on two covering problem: tree augmentation (TAP) and 2EC.
@@
 Table \ref{tableTAP} shows FDT found solutions better than the integrality-gap lower bound for most instances.
-\begin{table}[h]
+
+We also implemented the polyhedral version of Christofides' algorithm \cite{Wolsey1980}.
+Figure \ref{fdtvschris} shows FDT's solutions on fundamental extreme points of order 10 are always better than those from Christofides' algorithm.
+\vspace*{-.2in}
+\begin{table}[h!]
+\begin{small}
 	\centering
@@
 	  	TAP & $36$ & $66$ & $170$ & $10$\\  \bottomrule \\
-	  \end{tabular}\caption{The scale factor $C$ for FDT when run on 264 randomly generated tree-augmentation (TAP) instances with fractional extreme points: 138 of the 264 have $74$ variables.
-The rest have $250$ variables.}
+	  \end{tabular}\caption{The scale factor $C$ for FDT run on 264 randomly generated TAP instances with fractional extreme points: 138 instances have $74$ variables. The rest have $250$.}
+\end{small}
 	  \label{tableTAP}
@@
 Table \ref{table2EC} shows that again FDT found solutions better than the integrality-gap lower bound for most instances.
-\begin{table}[h]
+\begin{table}[h!]
+\begin{small}
 	\centering
@@
 	  \label{table2EC}
+\end{small}
 \end{table}
-We also implemented the polyhedral version of Christofides' algorithm \cite{Wolsey1980}.
-Figure \ref{fdtvschris} shows FDT's solutions on fundamental extreme points of order 10 are always better than those from Christofides' algorithm.
-%\vspace*{-.5in}
-\begin{figure}[h!]
-\centering
-\includegraphics[width=9cm]{"fdt vs christofides".png}
-\caption{Christofides' algorithm vs FDT on all fundamental extreme points of order 10.}
-\label{fdtvschris}
-\end{figure}

### 2019-03-22 Journal Version/abstract.tex
journal

--- 2018-11-21 IPCO format/FDT.tex
@@
-% This is samplepaper.tex, a sample chapter demonstrating the
-% LLNCS macro package for Springer Computer Science proceedings;
-% Version 2.20 of 2017/10/04
-%
-
-\documentclass[runningheads]{llncs}
-%
-\usepackage{graphicx}
-\usepackage{amsthm}
-% Used for displaying a sample figure. If possible, figure files should
-% be included in EPS format.
-%
-% If you use the hyperref package, please uncomment the following line
-% to display URLs in blue roman font according to Springer's eBook style:
-% \renewcommand\UrlFont{\color{blue}\rmfamily}
-
-\begin{document}
-%
-\title{Fractional Decomposition Trees: A tool for studying mixed-integer-program integrality gaps}
-% \thanks{Supported by organization x.}}
-%
-%\titlerunning{Abbreviated paper title}
-% If the paper title is too long for the running head, you can set
-% an abbreviated paper title here
-%
-\author{Robert D. Carr\inst{1} \and
-Arash Haddadan\inst{2} \and
-Cynthia A. Phillips\inst{3}}
-
-%\author{Robert Carr\inst{1}\orcidID{} \and
-%Arash Haddadan\inst{2}\orcidID{} \and
-%Cynthia Phillips\inst{3}\orcidID{}}
-
-%
-\authorrunning{R. Carr, A. Haddadan, C. Phillips}
-% First names are abbreviated in the running head.
-% If there are more than two authors, 'et al.' is used.
-%
-% Shorter institutions
-\institute{University of New Mexico, \email{bobcarr@unm.edu}\\   \and
-Carnegie Mellon University, \email{ahaddada@cmu.edu}\and
-Sandia National Laboratories, \email{caphill@sandia.gov}}
-% Longer version
-%\institute{University of New Mexico, Albuquerque NM 87131, USA\\
-%\email{bobcarr@unm.}\\   \and
-%Carnegie Mellon University, Pittsburgh, PA 15213, USA\\
-%\email{ahaddada@cmu.edu}\and
-%Sandia National Laboratories, Albuquerque, NM 87185, USA\\
-%\email{caphill@sandia.gov}}
-%
-\maketitle              % typeset the header of the con	tribution
-%
-\begin{abstract}
 We present a new algorithm/tool for studying integrality gaps of mixed-integer linear programming formulations.
@@
 
-\keywords{Mixed-integer linear programming  \and  Integrality gap \and convex combinations.}
-\end{abstract}
-%
-%
-%
-\input{introduction.tex}
-\input{binaryFDT.tex}
-\input{computational}
-\iffalse{
-\input{strongerCV}
-}\fi
-
-%
-% ---- Bibliography ----
-%
-% BibTeX users should specify bibliography style 'splncs04'.
-% References will then be sorted and formatted in the correct style.
-%
-% \bibliographystyle{splncs04}
-% \bibliography{mybibliography}
-%
-\begin{thebibliography}{10}
-
-	\bibitem{Boyd-Carr-2011}
-	Sylvia Boyd and Robert Carr.
-	\newblock Finding low cost tsp and 2-matching solutions using certain
-	half-integer subtour vertices.
-	\newblock {\em Discrete Optimization}, 8(4):525--539, 2011.
-
-	\bibitem{carr-ravi}
-	Robert Carr and R.~Ravi.
-	\newblock A new bound for the 2-edge connected subgraph problem.
-	\newblock In {\em Proceedings of the 6th International IPCO Conference on
-		Integer Programming and Combinatorial Optimization}, pages 112--125, London,
-	UK, UK, 1998. Springer-Verlag.
-
-	\bibitem{CV}
-	Robert Carr and Santosh Vempala.
-	\newblock On the {H}eld-{K}arp relaxation for the asymmetric and symmetric
-	traveling salesman problems.
-	\newblock {\em Mathematical Programming}, 100(3):569--587, Jul 2004.
-
-		\bibitem{fj}
-	Greg N. Frederickson and Joseph Ja'Ja'.
-	\newblock Approximation algorithms for several graph
-	augmentation problems.
-	\newblock {\em SIAM Journal on Computing}, 10(2):270--283, 1981.
-
-		\bibitem{32gap}
-	Cheriyan, Joseph and Karloff, Howard and Khandekar, Rohit and K{\"o}nemann, Jochen.
-	\newblock On the integrality ratio for tree augmentation.
-	\newblock {\em Operations Research Letters}, 36(4):399--401, 2008.
-
-	\bibitem{abe}
-    Anthony Alexander, Sylvia Boyd, and Paul Elliott-Magwood.
-    \newblock {On the Integrality Gap of the 2-Edge Connected Subgraph Problem}.
-    \newblock Technical report, University of Ottawa, Ottawa, Canada, 04 2006.
-
-    \bibitem{TSPcompute}
-    Geneviève Benoit and Sylvia Boyd.
-    \newblock Finding the exact integrality gap for small traveling salesman
-      problems.
-    \newblock {\em Mathematics of Operations Research}, 33(4):921--931, 2008.
-
-	\bibitem{gerard}
-	G{\'e}rard Cornu{\'e}jols, Jean Fonlupt, and Denis Naddef.
-	\newblock The traveling salesman problem on a graph and some related integer
-	polyhedra.
-	\newblock {\em Mathematical Programming}, 33(1):1--27, Sep 1985.
-
-	\bibitem{fp1}
-	Matteo Fischetti, Fred Glover, and Andrea Lodi.
-	\newblock The feasibility pump.
-	\newblock {\em Mathematical Programming}, 104(1):91--104, Sep 2005.
-
-	\bibitem{fp2}
-	Matteo Fischetti and Domenico Salvagnin.
-	\newblock Feasibility pump 2.0.
-	\newblock {\em Mathematical Programming Computation}, 1(2):201--222, Oct 2009.
-
-	\bibitem{GJ79}
-	M.R. Garey and D.S. Johnson.
-	\newblock {\em Computers and Intractability -- A Guide to the Theory of
-		{NP}-Completeness}.
-	\newblock Freeman, San Francisco, CA, 1979.
-
-	\bibitem{goemans}
-	Michel~X. Goemans.
-	\newblock Worst-case comparison of valid inequalities for the {TSP}.
-	\newblock {\em Math. Program.}, 69(2):335--349, August 1995.
-
-	\bibitem{cons-cara}
-	Martin Gr{\"o}tschel, L{\'a}szl{\'o} Lov{\'a}sz, and Alexander Schrijver.
-	\newblock {\em Geometric Algorithms and Combinatorial Optimization}, volume~2.
-	\newblock Second corrected edition edition, 1993.
-
-	\bibitem{jain}
-	Kamal Jain.
-	\newblock A factor 2 approximation algorithm for the generalized steiner
-	network problem.
-	\newblock In {\em Proceedings of the 39th Annual Symposium on Foundations of
-		Computer Science}, FOCS '98, pages 448--, Washington, DC, USA, 1998. IEEE
-	Computer Society.
-
-	\bibitem{randomizedrounding}
-	Prabhakar Raghavan and Clark~D. Tompson.
-	\newblock Randomized rounding: A technique for provably good algorithms and
-	algorithmic proofs.
-	\newblock {\em Combinatorica}, 7(4):365--374, Dec 1987.
-
-	\bibitem{schrijver}
-	A.~Schrijver.
-	\newblock {\em Combinatorial Optimization - Polyhedra and Efficiency}.
-	\newblock Springer, 2003.
-
-	\bibitem{vazirani}
-	Vijay~V. Vazirani.
-	\newblock {\em Approximation Algorithms}.
-	\newblock Springer-Verlag, Berlin, Heidelberg, 2001.
-
-	\bibitem{sw}
-	David~P. Williamson and David~B. Shmoys.
-	\newblock {\em The Design of Approximation Algorithms}.
-	\newblock Cambridge University Press, New York, NY, USA, 1st edition, 2011.
-
-	\bibitem{Wolsey1980}
-	Laurence~A. Wolsey.
-	\newblock {\em Heuristic analysis, linear programming and branch and bound},
-	pages 121--134.
-	\newblock Springer Berlin Heidelberg, Berlin, Heidelberg, 1980.
-
-\end{thebibliography}
-\newpage
-\appendix
-
-\input{2ECFDT.tex}
-
-\end{document}
+\textbf{keywords:}{ Mixed-integer linear programming,  Integrality gap, convex combinations.}

### 2019-03-22 Journal Version/binaryFDT.tex
journal

--- 2018-11-21 IPCO format/binaryFDT.tex
@@
 Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively.
-And assume $S(I),P(I)\in [0,1]^n\times \bbbr^p$.
+Assume $S(I),P(I)\in [0,1]^n\times \mathbb{R}^p$.
 For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section.
@@
 \begin{lemma}\label{domlemma}
-	Given $(x,y)\in \dom(P)$, there is an algorithm (the Dom2IP algorithm) that finds $(x^{(t)},y^{(t)})\in S$ in polynomial time, such that $x^{t}\leq x$, where $t=|\spp(x)|$\end{lemma}
+	Given $(x,y)\in \dom(P)$, there is an algorithm (the DomToIP algorithm) that finds $(\bar{x},\bar{y})\in S$ in polynomial time, such that $\bar{x}\leq x$.\end{lemma}
 
@@
 Now consider the following linear program.
-The variables of this linear program are the $z\in \bbbr^n$ variables and $w\in \bbbr^p$.
+The variables of this linear program are the $z\in \mathbb{R}^n$ variables and $w\in \mathbb{R}^p$.
 \begin{align}
@@
 Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$.
-Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$.
+Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in \{1,\ldots,n\}\setminus \{\ell+1\}$ (See Algorithm \ref{domtoIPalg}).
 
@@
 The Dom2IP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$.
-\iffalse{
+
+\vspace*{10pt}
 \begin{algorithm}[H]
@@
 	}
+	\caption{The DomToIP algorithm}
 	\label{domtoIPalg}
-	\caption{The Dom2IP algorithm}
 \end{algorithm}
-}\fi
+\vspace*{10pt}
 We prove that indeed $(x^{(t)},y^{(t)})\in S$.
-
-	First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomtoIP the $\DOMtoS(x^{\ell})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
+First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomtoIP the $\DOMtoS(x^{\ell})$ is feasible.
+We show something stronger.
+For $\ell=0,\ldots,t-1$ let
 	\begin{align*}
@@
 By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ .
-We have
-	\begin{equation}
-	\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}
-	\end{equation}
+We have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}$
 	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$.
@@
 We show that $x^{(t)} = z'$.
-Observe that for $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
+For $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
 We just need to show that $z'_j = 1$.
@@
 
-\iffalse{
-\begin{algorithm}[H]\label{FDTFull}
-	\KwIn{$P= \{(x,y)\in \bbbr^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \bbbr^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
-	\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
-	$L^0\leftarrow [(x^*,y^*),1]$\\
-	\For{$i=1$ \textbf{to} $t$}{
-		$L'\leftarrow \emptyset$\\
-		\For{$[(x,y),\lambda] \in L^i$}{
-			Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
-			$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
-		}
-		Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
-	}
-	\For{$[(x,y),\lambda] \in L^t$}{
-		Apply Algorithm \ref{domtoIP} to $(x,y)$ to obtain $(z,w)\in S$\\
-		$F \leftarrow F \cup \{[(z,w),\lambda]\}$
-	}
-	\textbf{return} $F$
-	\caption{Fractional Decomposition Tree Algorithm}
-\end{algorithm}}\fi
-
-\section{FDT on binary MIPs}
+\section{FDT on binary MILPs}
 \label{binaryfdt}
@@
 In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm.
-\iffalse{We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution. }\fi
+We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.
 
@@
 Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$.
-We will later see how we can turn these into points in $S$.
+In Lemma  \ref{domlemma} we saw how to turn these into points in $S$.
 
@@
 Let $(\hat{x}^0,\hat{y}^0) = (\frac{x^0}{\gamma_0},\frac{y^0}{\gamma_0})$, $(\hat{x}^1,\hat{y}^1) = (\frac{x^1}{\gamma_1},\frac{y^1}{\gamma_1})$.
-Observe that  (ii), (iii), (iv) are satisfied with this choice.
-In order to show that (i) is also satisfied we prove the following claim.
+This choice satisfies  (ii), (iii), (iv).
+To show that (i) is also satisfied we prove the following claim.
 
@@
 We call the following linear program $\prun(L')$.
-Let $L' = \{[(x^1,y^1),\gamma_1],\ldots,[(x^{2k},y^{2k}),\gamma_{2k}]\}$.
-The variables of $\prun(L')$ is a scalar variable $\theta_j$ for each node $j$ in $L'$.
-	\begin{align}
-		\prun(L')\quad\quad& \max\quad \;\sum_{j=1}^{2k} \theta_j\\
-		&\;\text{s.t.} \quad \;\;\sum_{j=1}^{2k} \theta_j x^j_i\leq x^*_i &\mbox{ for $i=1,\ldots,t$} \label{packs}\\
-		&\;{\color{white}{\text{s.t.}} }\quad  \;\quad\quad\theta \geq 0\label{nonneg}
-	\end{align}
+Let $L' = \{[(x^1,y^1),\gamma_1],\ldots,[(x^{|L'|},y^{|L'|}),\gamma_{|L'|}]\}$.
+The variables of $\prun(L')$ are scalar variables $\theta_j$ for each node $j$ in $L'$.
+	\begin{equation}
+		\prun(L')=\{\max \sum_{j=1}^{|L'|} \theta_j\;:\; \sum_{j=1}^{|L'|} \theta_j x^j_i\leq x^*_i \mbox{ for $i=1,\ldots,t$},\; \theta\geq 0 \}
+	\end{equation}
 
@@
 Let $\theta^*$ be the optimal vertex point solution to this LP.
-Since the problem is in $\bbbr^{2k}$,  $\theta^*$ has to satisfy $2k$ linearly independent constraints at equality.
-However, there are only $t$ constraints of type (\ref{packs}).
+Since the problem is in $\mathbb{R}^{|L'|}$,  $\theta^*$ has to satisfy $|L'|$ linearly independent constraints at equality.
+However, there are only $t$ constraints of type $ \sum_{j=1}^{|L'|} \theta_j x^j_i\leq x^*_i$.
 Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero.
-We claim that $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,2k$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma.
+Set $L_{i+1}$ which consists of $(x^j,y^j)$ for $j=1,\ldots,|L'|$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma.
 Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$.
-Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{k} \theta^*_j \geq \sum_{j=1}^{2k}\gamma_j \geq \frac{1}{g^{i+1}}$.
+Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{|L'|} \theta^*_j \geq \sum_{j=1}^{|L'|}\gamma_j \geq \frac{1}{g^{i+1}}$.
 \end{proof}
+
 \paragraph{From leaves of FDT to feasible solutions}
@@
 This conclude the description of the FDT algorithm and proves Theorem \ref{binaryFDT}.
+See Algorithm \ref{FDTFull} for a summary of the FDT algorithm.
+
+	\vspace*{10pt}
+
+	\begin{algorithm}[H]\label{FDTFull}
+		\KwIn{$P= \{(x,y)\in \mathbb{R}^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \mathbb{R}^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
+		\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
+		$L^0\leftarrow [(x^*,y^*),1]$\\
+		\For{$i=1$ \textbf{to} $t$}{
+			$L'\leftarrow \emptyset$\\
+			\For{$[(x,y),\lambda] \in L^i$}{
+				Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
+				$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
+			}
+			Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
+		}
+		\For{$[(x,y),\lambda] \in L^t$}{
+			Apply Algorithm \ref{domtoIPalg} to $(x,y)$ to obtain $(z,w)\in S$\\
+			$F \leftarrow F \cup \{[(z,w),\lambda]\}$
+		}
+		\textbf{return} $F$
+		\caption{Fractional Decomposition Tree Algorithm}
+	\end{algorithm}

### 2019-03-22 IPCO format/binaryFDT.tex
journal

@@
 
+\vspace*{-.1in}
 \section{FDT on binary MIPs}
 \label{binaryfdt}
+\vspace*{-.1in}
 
@@
 \end{proof}
+\vspace*{-.2in}
 \paragraph{From leaves of FDT to feasible solutions}

### 2019-03-22 IPCO format/strongerCV.tex
journal

--- 2018-11-02 gap.tex
@@
-\section{Stronger version of Carr-Vempala for covering problems} \label{gap}
+\section{Stronger version of Theorem \ref{CV} for covering problems} \label{gap}
 
@@
 	\end{align*}
-			It is easy to show that  multipliers above are convex.
+	It is easy to show that  multipliers above are convex.}\fi
 \end{proof}

### 2019-03-22 Journal Version/2ECFDT.tex
journal

--- 2018-11-21 IPCO format/2ECFDT.tex
@@
 
-In Section \ref{binaryfdt} our focus was on binary MIPs.
-In this section, in an attempt to extend FDT to 0,1,2 problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem.
+In Section \ref{binaryfdt} our focus was on binary MILPs.
+In this section, in an attempt to extend FDT to \{0,1,2\} problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem.
 Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2.
@@
 We want to prove Theorem \ref{FDT2EC}.
+\FDTEC*
 We do not know the exact value for $g_{\EC}$, but we know $\frac{6}{5} \leq g_{\EC} \leq \frac{3}{2}$ \cite{carr-ravi,Wolsey1980}.
@@
 we already have an algorithm with $C\leq \frac{3}{2}$.
-However, we showed in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$ for fundamental extreme points with 10 vertices.
+However, we showed in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$ for FEPs of order 10.
 
@@
 
-First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for 0,1,2 problems except for one additional clause.
+First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for $\{0,1,2\}$ problems except for one additional clause.
 
@@
 		&\;{\color{white}{\text{s.t.}} }\quad x^j_e = j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
-		&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
+		&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq \lambda_j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
 		&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1+x^2 \leq x\label{packing2ec}\\
@@
 We can also show that $\gamma_0+\gamma_1+\gamma_2\geq \frac{1}{g_{\EC}}$, which means that (i) is also satisfied.
-The proof is similar to the proof of the claim in Lemma \ref{LPClemma}, but we need to replace each $f\in E$ with $x_f\geq 1$ with a suitably long path to ensure that Constraint (\ref{1edges2ec}) is also satisfied.	We skip the details.\iffalse{
+The proof is similar to the proof of the claim in Lemma \ref{LPClemma}, but we need to replace each $f\in E$ with $x_f\geq 1$ with a suitably long path to ensure that Constraint (\ref{1edges2ec}) is also satisfied.
 	\begin{claim}\label{CVexists}
@@
 		Suppose for contradiction $\sum_{j=0,1,2}\gamma_j = \frac{1}{g_{\EC}} - \epsilon$ for some $\epsilon >0$.
-
 Construct graph $G'$ by removing edge $f$ with $x_f\geq 1$ and replacing it with a path $P_f$ of length $\ceil{\frac{2}{\epsilon}}$.
@@
 add two copies of $f$ to $F_i$.
-If there is an edge $h\in P_f$ with $\chi^{F'_i}_h = 1$, let $\chi^{F_i}_f=1$, i.e.
+If there are at least two edges $h,h'\in P_f$ with $\chi^{F'_i}_h=\chi^{F'_i}_{h'} = 1$, let $\chi^{F_i}_f=1$, i.e.
 add one copy of $f$ to $F_i$.
@@
 	\end{proof}
-	This concludes the proof.}\fi \end{proof}
+	This concludes the proof. \end{proof}
 
@@
 \end{lemma}
-The proof is similar to Lemma \ref{prune}, but we need to use property (i) in Lemma \ref{LPC2EC} to prove that (a) also holds.
-\iffalse{
+The proof is similar to Lemma \ref{prune}, but we need to use property (v) in Lemma \ref{LPC2EC} to prove that (a) also holds.
 \begin{proof}
@@
 
-	If $|L'|\geq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
-\end{proof}	}\fi
+	Finally, if $|L'|\geq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
+\end{proof}
 

### 2019-03-22 Journal Version/computational.tex
journal

--- 2018-11-21 IPCO format/computational.tex
@@
 \section{Computational experiments with FDT}\label{experiment}
+We ran FDT on two covering problems: the tree augmentation problem (TAP) and 2EC.
+In TAP we are given a tree $T=(V,E)$, and a set of non-edges $L$ between vertices in $V$ and costs $c\in \mathbb{R}^{L}_{\geq 0}$.
+A feasible augmentation is $L'\subseteq L$ such that $T+L'$ is 2-edge-connected.
+In TAP we wish to find the minimum-cost feasible augmentation.
+
+For $\ell\in L$, let $P_\ell$ be the set of edges in the unique path between the endpoints of $\ell$ in $T$.
+Let $\TAP(T,L)=\{x\in [0,1]^{L}: \sum_{\ell: e\in P_\ell}x_\ell \geq 1, \mbox{ for $e\in E$}\}$.
+Then $\TAP(T,L)\cap \mathbb{Z}^{L}$ is set of feasible augmentations for the instance defined by $T$ and $L$.
+We know $\frac{3}{2}\leq g_{\TAP}\leq 2$~\cite{fj,32gap}.
+We ran binary FDT on a set of 264 fractional extreme points of randomly produces instances of $\TAP$.
+Table \ref{tableTAP} shows FDT found solutions better than the integrality-gap lower bound for most instances.
+
+\begin{table}[h!]
+	\begin{small}
+		\centering
+		\begin{tabular}{c c c c c}
+			\hline
+			& $C\in [1.1,1.2]\;$ & $\;C\in (1.2,1.3]\;$ &
+			$\;C\in (1.3,1.4]$ &\; $C\in (1.4,1.5]\;$ \\ \hline
+			TAP & $36$ & $66$ & $170$ & $10$\\  \hline \\
+		\end{tabular}\caption{The scale factor $C$ for FDT run on 264 randomly generated TAP instances with fractional extreme points: 138 instances have $74$ variables.
+The rest have $250$.} \label{tableTAP}
+	\end{small}
+
+\end{table}
+
+We also implemented the polyhedral version of Christofides' algorithm \cite{Wolsey1980}.
+In particular, we implemented the $T$-join augmentation in Christofides' algorithm, in a way that minimizes the average usage of every edge across the the convex combination of spanning trees.
+This allows the ``real'' approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$.
+Figure \ref{fdtvschris} shows FDT's solutions on all FEPs of order 10 are always better than those from Christofides' algorithm.
+
 \begin{figure}[h!]
@@
 
-We ran FDT on two covering problem: tree augmentation (TAP) and 2EC.
-For TAP we are given a tree $T=(V,E)$, and a set of non-edges $L$ between vertices in $V$ and costs $c\in \bbbr^{L}_{\geq 0}$.
-We wish to find the minimum-cost  $L'\subseteq L$ such that $T+L'$ is 2-edge-connected.
-For $\ell\in L$, let $P_\ell$ be the set of edges in the unique path between the endpoints of $\ell$ in $T$.
-For TAP, $S(\mbox{TAP})=\{x\in \bbbz^{L}_{\geq 0}: \sum_{\ell: e\in P_\ell}x_\ell \geq 1, \mbox{ for $e\in E$}\}$ and $P(\mbox{TAP})$ relaxes integrality.
-We know $\frac{3}{2}\leq g({\mbox{TAP}})\leq 2$~\cite{fj,32gap}.
-We ran binary FDT on a set of 264 fractional extreme points of $P(\mbox{TAP})$.
-Table \ref{tableTAP} shows FDT found solutions better than the integrality-gap lower bound for most instances.
-
-We also implemented the polyhedral version of Christofides' algorithm \cite{Wolsey1980}.
-Figure \ref{fdtvschris} shows FDT's solutions on fundamental extreme points of order 10 are always better than those from Christofides' algorithm.
-\vspace*{-.2in}
-\begin{table}[h!]
-\begin{small}
-	\centering
-	  \begin{tabular}{c c c c c}
-	  \toprule
-	  	& $C\in [1.1,1.2]\;$ & $\;C\in (1.2,1.3]\;$ &
-               $\;C\in (1.3,1.4]$ &\; $C\in (1.4,1.5]\;$ \\ \midrule
-	  	TAP & $36$ & $66$ & $170$ & $10$\\  \bottomrule \\
-	  \end{tabular}\caption{The scale factor $C$ for FDT run on 264 randomly generated TAP instances with fractional extreme points: 138 instances have $74$ variables. The rest have $250$.}
-\end{small}
-	  \label{tableTAP}
-\end{table}
-%\vspace*{-30pt}
 We ran FDT for 2EC on 963 fractional extreme points of $\EC(G)$.
@@
 	  \begin{tabular}{c c c c c}
-	  	\toprule
+	  	\hline
 	  	& $C\in [1.08,1.11]\;$ & $\;C\in (1.11,1.14]\;$ &
-               $\;C\in (1.14,1.17]$ &\; $C\in (1.17,1.2]\;$ \\ \midrule
-	  	2EC & $79$ & $201$ & $605$ & $78$ \\ \bottomrule\\
+               $\;C\in (1.14,1.17]$ &\; $C\in (1.17,1.2]\;$ \\ \hline
+	  	2EC & $79$ & $201$ & $605$ & $78$ \\ \hline\\
 	  \end{tabular}	\caption{FDT for $\EC$ implemented applied to all fundamental extreme points of order 10 or 12.
 A FEP of order $k$ has $\frac{3k}{2}$ variables.
-The lower bound on $g(\EC)$ is $\frac{6}{5}$.}
+The lower bound on $g_{\EC}$ is $\frac{6}{5}$.}
 	  \label{table2EC}

### 2019-03-22 Journal Version/gap.tex
journal

--- 2018-11-02 gap.tex
@@
-\section{Stronger version of Carr-Vempala for covering problems} \label{gap}
+\section{Strengthening Theorem \ref{CV} for bounded covering problems} \label{gap}
 
@@
 	Assume $\epsilon <1$. For $j\in \{1,\ldots,m\}$ such that $A_jz^i\leq Cb$, i.e. $t_j\leq 0$ (this includes $j$ such that $A_jv^i=b$, i.e. $s_j=0$) we have
-	\begin{equation}
+	\begin{equation*}
 	A_j u^i(\epsilon) = \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}\geq \frac{Cb-\epsilon Cb}{C(1-\epsilon)}=b
-	\end{equation}
+	\end{equation*}
 	Assume $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$.
@@
 We have
-	\begin{equation}
+	\begin{equation*}
 	Cv^1 \geq  \epsilon_1z^1 + C(1-\epsilon_1)x^1 \geq \epsilon_1z^1 + C(1-\epsilon_1) \sum_{\ell=1}^{r}\lambda^1_\ell v^\ell.
-	\end{equation}
+	\end{equation*}
 	Hence,
-	\begin{equation}
+	\begin{equation}\label{equation6}
 	Cv^1 \geq \frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}\cdot z^1 + (1-\epsilon_i)\sum_{\ell=2}^{r} \frac{\lambda^1_\ell}{1-(1-\epsilon_1)\lambda_1^1}\cdot Cv^\ell.
@@
 \end{proof}
+
+\begin{example}
+
+Consider  $\EC(G) = \{x\in [0,2]^E_{\geq 0}: \; x(\delta(U))\geq 2 \mbox{ for $\emptyset \subset U \subset V$}\},$ where $G=(V,E)$ is the graph in Figure \ref{example}. 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.2\linewidth]{example.pdf}
+	\caption{Graph $G=(V,E)$. Let $H$ be the Hamiltonian cycle of $G$ that contains edges $(1,2),(2,3),(3,4),(4,5),(5,6),(6,7),(7,8),(1,8)$. Let $M= E\setminus H$: $M=\{(1,5),(2,7),(3,6),(4,8)\}$.}
+	\label{example}
+\end{figure}
+
+Let $v^1$ be the following extreme point of $\EC(G)$: \begin{equation*}
+v^1_{e} = \left\{ \begin{array}{ll}
+1 & \mbox{if $e\in M$};\\
+1/2 & \mbox{if $e\in H$}.
+\end{array} \right. 
+\end{equation*}
+Define $z^1$ to be the following vector:
+\begin{equation*}
+z^1_{e} = \left\{ \begin{array}{ll}
+7/5 & \mbox{if $e= (1,5)$};\\
+1 & \mbox{if $e\in M\setminus \{(1,5)\}$};\\
+2/5 & \mbox{if $e \in \{(1,8),((4,5))\}$};\\
+3/5 & \mbox{if $e\in H\setminus\{(1,8),((4,5))\} $}.
+\end{array} \right. 
+\end{equation*}
+It is easy to check that $z^1$ satisfies the requirement of Theorem \ref{gap} when setting $C=\frac{6}{5}$.
+In particular, we have $ z^1(\delta(U))\leq \frac{6}{5}v^1(\delta(U))$ for all $\emptyset\subset U \subset V$.
+Also, is it easy to decompose $z^1$ into a convex combination of integer point in of $\EC(G)$.
+
+Now, we want to set the $\epsilon_i$ in the statement of Lemma \ref{epsilon} to be $2^{-k}$. By Lemma \ref{epsilon}
+\begin{equation*}
+x^1_{e} = \left\{ \begin{array}{ll}
+\frac{2^k-7/6}{2^k-1} & \mbox{if $e= (1,5)$};\\
+\frac{2^k-5/6}{2^k-1} & \mbox{if $e\in M\setminus \{(1,5)\}$};\\
+\frac{2^k- 2/3}{2\cdot (2^k-1)} & \mbox{if $e \in \{(1,8),((4,5))\}$};\\
+\frac{1}{2} & \mbox{if $e\in H\setminus\{(1,8),((4,5))\} $}.
+\end{array} \right. 
+\end{equation*}
+is in $\EC(G)$ for sufficiently large $k$. The vectors defined below $v^2,\ldots,v^7$ are also extreme points of $\EC(G)$.
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{ccccccccccccc}
+		\toprule
+		& (1,5) & (2,7)& (3,6)&(4,8)&(1,2)&(2,3)&(3,4)&(4,5)&(5,6)&(6,7)&(7,8)&(1,8)      \\ \midrule
+			$v^2=$ & (0&1&2&1&0&1&1&2&0&0&1&2)  \\
+			$v^3=$ & (0&2&2&1&0&0&0&1&1&1&1&2)\\
+			$v^4=$ & (1&2&2&2&1&1&1&1&0&0&0&0)\\
+			$v^5=$ & (0&2&1&1&1&1&0&1&1&0&0&1)\\
+			$v^6=$ & (1&1&1&2&0&1&0&0&1&0&1&1)\\
+			$v^7=$ & (1&1&1&2&1&0&1&1&0&1&0&0)\\
+				 \bottomrule
+	\end{tabular}
+\end{table}
+Moreover, we have 
+\begin{equation*}
+x^1 = (1-8\lambda)v^1+ \lambda v^2 + 2\lambda v^3+\lambda v^4+ \lambda v^5+ \lambda v^6 + 2\lambda v^7, \quad \lambda = \frac{1}{24\cdot (2^k-1)}
+\end{equation*}
+Now, this allows us to rewrite Inequality \ref{equation6} for this example.
+\begin{equation*} 
+\frac{6}{5}v^1 \geq \frac{3}{4} z^1 +\frac{1}{32}(\frac{6}{5}\cdot v^2) +\frac{1}{16}(\frac{6}{5}\cdot v^3) + \frac{1}{32}(\frac{6}{5}\cdot v^4)+\frac{1}{32}(\frac{6}{5}\cdot v^5) + \frac{1}{32}(\frac{6}{5}\cdot v^6)+ \frac{1}{16}(\frac{6}{5}\cdot v^7).
+\end{equation*}
+\end{example}

### 2019-03-22 Journal Version/introduction.tex
journal

--- 2018-11-21 IPCO format/introduction.tex
@@
 \begin{equation}
-S(A,G,b)= \{(x,y)\in \bbbz^{n}\times \bbbr^p\;:\; Ax+Gy\geq b\}  \label{S}.
+S(A,G,b)= \{(x,y)\in \mathbb{Z}^{n}\times \mathbb{R}^p\;:\; Ax+Gy\geq b\}  \label{S}.
 \end{equation}
@@
 \begin{equation}
-P(A,G,b) = \{(x,y)\in \bbbr^{n+ p}\;:\; Ax+Gy\geq b\}. \label{P}
+P(A,G,b) = \{(x,y)\in \mathbb{R}^{n+ p}\;:\; Ax+Gy\geq b\}. \label{P}
 \end{equation}
@@
 Then $S(I)$ and $P(I)$ denote $S(A,G,b)$ and $P(A,G,b)$, respectively.
-Given a linear objective function $c$, a MILP problem is $\min \;\{cx:\; (x,y) \in S(I)\}$.
-It is  NP-hard even to determine if a MILP instance has a feasible solution~\cite{GJ79}.
+Given a linear objective function $c$, a Mixed-Integer-Linear Program (MILP) is $\min \;\{cx:\; (x,y) \in S(I)\}$.
+It is  NP-hard even to determine if an MILP instance has a feasible solution~\cite{GJ79}.
 However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.
@@
 Many researchers (see \cite{vazirani,sw}) have developed polynomial-time LP-based algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$.
-The approximation factor $C$ can be a constant or depend a MILP parameter, e.g.
+The approximation factor $C$ can be a constant or depend a parameter of the MILP, e.g.
 $O(\log(n))$.
@@
 Consider the set of point described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively.
-Assume in addition that $S(I),P(I)\subseteq [0,1]^n\times \bbbr^p$.
-For a vector $x\in \bbbr^n$ such that $(x,y)\in P(I)$ for some $y\in \bbbr^p$, let $\spp(x)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.
+Assume in addition that $S(I),P(I)\subseteq [0,1]^n\times \mathbb{R}^p$.
+For a vector $x\in \mathbb{R}_{\geq 0}^n$ such that $(x,y)\in P(I)$ for some $y\in \mathbb{R}^p$, let $\spp(x)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.
 
-\textit{Fractional Decomposition Tree} (FDT) is a polynomial-time algorithm that given a point $x\in P(I)$ produces a convex combination of feasible points in $S(I)$ that are dominated by a ``factor" $C$ of $x$.
+\textit{Fractional Decomposition Tree} (FDT) is a polynomial-time algorithm that given a point $(x,y)\in P(I)$ produces a convex combination of feasible points in $S(I)$ that are dominated by a ``factor" $C$ of $x$ in the coordinates corresponding to $x$.
 If $C = g_I$, it would be optimal.
@@
 	Assume $1\leq g_I 	<\infty$. 	
-	The Fractional Decomposition Tree (FDT) algorithm , given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\spp(x^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
+	The Fractional Decomposition Tree (FDT) algorithm, given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\spp(x^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
 Moreover, $C\leq g_I^{|\spp(x^*)|}$.
@@
 
-We consider the following TSP-related problems.  The {\em 2-edge-connected subgraph problem (2EC)} is to find a minimum-weight 2-edge-connected (multigraph) subgraph
-% (which can multiple copies of each edge)
-in a graph $G=(V,E)$ with respect to weights $c\in \bbbr^E_{\geq 0}$.
+We consider the following TSP-related problems.
+The {\em 2-edge-connected subgraph problem (2EC)} is to find a minimum-weight 2-edge-connected multigraph (subgraph which can contain multiple copies of each edge)
+in a graph $G=(V,E)$ with respect to weights $c\in \mathbb{R}^E_{\geq 0}$.
 In the {\em tree-augmentation problem (TAP)} we wish to add a minimum-cost set of edges to a tree to make it 2-edge-connected.
@@
 
-One can extend the FDT algorithm for binary MILPs into covering $\{0,1,2\}$-MILPs by losing a factor $2^{|\spp(x)|}$.
-In order to eradicate this factor, we need to treat the coordinate $i$ with $x_i=1$ differently.
+One can extend the FDT algorithm for binary MILPs into covering $\{0,1,2\}$-MILPs by losing a factor $2^{|\spp(x)|}$ on top of the loss for FDT.
+In order to eradicate this extra factor, we need to treat the coordinate $i$ with $x_i=1$ differently.
+For 2EC we are able to achieve this.
 The 2EC problem has the natural linear programming relaxation is
 \begin{equation}\label{2ECpol}
-\EC(G)= \{x\in \bbbr_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
-% We prove the following theorem.
+\EC(G)= \{x\in [0,2]^{E}\;:\; x(\delta(U))\geq 2 \text{ for $\emptyset \subset U\subset V$})\}.
+\end{equation}
+ We prove the following theorem.
 
@@
 The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq 2|V|-1$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g({\EC})^{k}$, where $g({\EC})$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol})
+Moreover, $C\leq g_{\EC}^{k}$, where $g_{\EC}$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol})
 \end{restatable}
+
+We give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems.
+For this purpose assume $P= \{x\in \mathbb{R}^n_{\geq 0}: Ax\geq b\cdot \textbf{1}, x \leq b\cdot \textbf{1}\}$, where $A\in \mathbb{Z}^{m\times n}_{\geq 0}$ and $b\in \mathbb{Z}_{\geq 0}$.
+Let $S= P\cap \mathbb{Z}^n$ and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$.
+Examples of problems whose natural linear programming relaxation is $P$ (for some matrix $A$ and integer $b$) include the 2-edge-connected multigraph problem, Steiner tree problem, tree augmentation problem, and many others.
+
+\begin{restatable}{theorem}{tightcuts}
+	\label{tightcuts}
+	Let $x\in P$, there exists $\theta\in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i = 1$ and $\tilde{x}^i \in S$ for $i=1,\ldots,k$ such that \begin{itemize}
+		\item for $\ell\in \{1,\ldots,n\}$, if $x_\ell =0$, then $\tilde{x}^i_\ell=0$ for $i =1,\ldots,k$, i.e. $\tilde{x}^i$ is in the support of $x$,
+		\item we have $A_j (\sum_{i=1}^{k}\theta_i\tilde{x}^i)\leq C\cdot A_j x$, for $j$ such that $A_j x =b$,  
+	\end{itemize}
+	if and only if $C\geq g$.
+\end{restatable}
+
+This means in order to prove an upper bound on the integrality gap of a  bounded covering problem, we need to show there is a convex combination of integer feasible points that is ``cheap'' on all tight cuts.
+Notice that Theorem \ref{CV} requires the certificate convex combination to be ``cheap" on every single variable.
 
@@
 Carr and Ravi \cite{carr-ravi} introduced fundamental extreme points.
-A point x in Held-Karp relaxation for TSP (or 2EC; they have the same relaxation) is a point whose support of $x$, namely $G_x$ satisfies the following: i)  $G_x$ is a cubic graph, ii) in $G_x$ there is exactly one edge with $x_e=1$ incident to each node iii) The fractional edges of $G_x$ form a Hamiltonian cycle.
+A point $x$ in Held-Karp relaxation for TSP (or 2EC; they have the same relaxation) is a point whose support of $x$, namely $G_x$ satisfies the following: i)  $G_x$ is a cubic graph, ii) in $G_x$ there is exactly one edge with $x_e=1$ incident to each node iii) The fractional edges of $G_x$ form a Hamiltonian cycle.
 We say a fundamental extreme point (FEP) is {\em order $k$} if there are $k$ nodes on this Hamiltonian cycle.
 An FEP of order $k$ could represent an instance with many more than $k$ vertices.
-Carr and co-authors~\cite{CV,carr-ravi, BC11} proved that showing that $Cx$ is a convex combination of tours (resp.
-2-edge-connected subgraphs) for all fundamental extreme points is equivalent to proving that the integrality gap for TSP (resp.
+Carr and co-authors~\cite{CV,carr-ravi,BC11} proved that showing that $Cx$ is a convex combination of tours (resp.
+2-edge-connected multigraphs) for all fundamental extreme points is equivalent to proving that the integrality gap for TSP (resp.
 2EC) is bounded above by $C$.
-Thus we can create the ``hardest'' LP solutions to decompose.
+We use fundamental extreme point to create the ``hardest'' LP solutions to decompose.
 
@@
 \begin{itemize}
-\item We give a simple algorithm, Dom2IP, that can prove a formulation’s integrality gap is unbounded or if not provide a feasible integer solution.
-Someone formulating a first MILP for a new problem can test it with Dom2IP.
+\item We give a simple algorithm, DomToIP, that can prove a binary formulation’s integrality gap is unbounded or if not provide a feasible integer solution.
+Someone formulating a first MILP for a new problem can test it with DomToIP.
 If the algorithm ever fails in finding a feasible solution, the MILP has an unbounded gap.
@@
 Still, this can help direct theoretical analysis in the most promising direction.
-Furthermore, for these kinds of problems, especially 2EC, FDT gives good approximate solutions, better than the best current competitor (Christofides).
+For instance for 2EC, FDT gives good approximate solutions, better than the best current competitor (Christofides' algorithm).
+
+\item A stronger theoretical result on integrality gap that can be potentially employed to obtain improved upper bounds on the integrality gap of bounded covering problems.  
 \end{itemize}
@@
 Finally we give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems.
-For this purpose assume $P= \{x\in \bbbr^n_{\geq 0}: Ax\geq b\textbf{1}, x \leq b\textbf{1}\}$, $S= P\cap \bbbz^n$, and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$.
+For this purpose assume $P= \{x\in \mathbb{R}^n_{\geq 0}: Ax\geq b\textbf{1}, x \leq b\textbf{1}\}$, $S= P\cap \mathbb{Z}^n$, and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$.
 Examples of such problems include the 2-edge-connected multigraph problem, the tree augmentation problem, and many others.
@@
 \subsection{Notations}
-For vectors $x,y\in \bbbr_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$.
+For vectors $x,y\in \mathbb{R}_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$.
 For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$.
 Let $\textbf{1}$ be the vector of all ones of a suitable dimension.
-For a set $S$ of vectors in $\bbbr_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.
+For a set $S$ of vectors in $\mathbb{R}_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.
 }\fi

### 2019-03-29 Journal Version/2ECFDT.tex
updated

@@
 In this section, in an attempt to extend FDT to \{0,1,2\} problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem.
-Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2.
+Given a graph $G=(V,E)$, a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edges in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2.
 In the 2EC problem, we are given non-negative costs on the edge of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$.
-Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take an edge at most 2 times.
+Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take  each edge at most 2 times.
 The natural linear programming relaxation is $\EC(G) = \{x\in [0,2]^E: x(\delta(U))\geq 2 \mbox{ for } \emptyset \subset U \subset V\}$.
@@
 		&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq 2\lambda_j\; &\mbox{ for $j=0,1,2$}\label{bound2ec}\\
-		&\;{\color{white}{\text{s.t.}} }\quad x^j_e = j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
+		&\;{\color{white}{\text{s.t.}} }\quad x^j_e = j\cdot\lambda_j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
 		&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq \lambda_j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\

### 2019-03-29 Journal Version/binaryFDT.tex
updated

@@
 Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$.
+For polyhedron $L$ in $\mathbb{R}^{n\times p}$ let $\dom(L)= \{(x,y)\in \mathbb{R}^n\times \mathbb{R}^p: x\geq x' \text{ for some } (x',y')\in L\}$, and we call $\dom(L)$ the dominant of $L$.
 
@@
 \begin{lemma}\label{domlemma}
-	Given $(x,y)\in \dom(P)$, there is an algorithm (the DomToIP algorithm) that finds $(\bar{x},\bar{y})\in S$ in polynomial time, such that $\bar{x}\leq x$.\end{lemma}
+	Given $(x,y)\in \dom(P)$ where $x\in \mathbb{Z}^n$, there is an algorithm (the DomToIP algorithm) that finds $(\bar{x},\bar{y})\in S$ in polynomial time, such that $\bar{x}\leq x$.\end{lemma}
 
@@
 The above procedure suggests how to find $(x^{(\ell+1)},y^{(\ell+1)})$ from $(x^{(\ell)},y^{(\ell)})$.
-The Dom2IP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$.
+The DomToIP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$.
 
@@
 \begin{algorithm}[H]
-	\KwIn{$(x,y)\in \dom(S)$}
+	\KwIn{$(x,y)\in \dom(P)$, $x\in \mathbb{Z}^n$}
 	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
@@
 We prove that indeed $(x^{(t)},y^{(t)})\in S$.
-First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomtoIP the $\DOMtoS(x^{\ell})$ is feasible.
+First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomToIP, the feasible region of $\DOMtoS(x^{\ell})$ is non-empty.
 We show something stronger.
@@
 First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$.
-By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
-Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
+By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.	Thus we have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
 So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$.
-Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$.
+Also recall that $x^{(0)}\in \mathbb{Z}^n$.	Hence, $\tilde{z}^i\leq x^{(0)}$ for $i=1,\ldots,k$.
 Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.
@@
 Assume we are given a point $(x^*,y^*)\in P$.
-For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
+For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S} cx$.
 In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm.
-We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.
+We also remark that if $g=1$, then the algorithm will give an exact decomposition of any feasible solution.
 
@@
 			}
-			Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
+			Apply $\prun(L')$ to obtain $L^{i+1}$. 
 		}

### 2019-03-29 Journal Version/introduction.tex
updated

@@
 The solution can also provide some useful global structure, even though the fractional values are not directly meaningful.
-{\em LP-based approximation algorithms} for combinatorial problems involve modeling the problem as a MILP, solving the LP relaxation, finding a (problem-specific) integer-feasible solution from the LP solution, and proving an approximation bound by comparing the solution value to the LP lower bound.
+{\em LP-based approximation algorithms} for combinatorial problems involve modeling the problem as an MILP, solving the LP relaxation, finding a (problem-specific) integer-feasible solution from the LP solution, and proving an approximation bound by comparing the solution value to the LP lower bound.
 
 Many researchers (see \cite{vazirani,sw}) have developed polynomial-time LP-based algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$.
-The approximation factor $C$ can be a constant or depend a parameter of the MILP, e.g.
+The approximation factor $C$ can be a constant or depend on a parameter of the MILP, e.g.
 $O(\log(n))$.
@@
 \begin{theorem}[Carr, Vempala \cite{CV}] \label{CV}
-	Let $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(S(I))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ if and only if $g_I \leq C$.
+	Let $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ if and only if $g_I \leq C$.
 \end{theorem}
-Here $\dom(P(I))$ is the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$, also known as the dominant of $P(I)$.
-For covering problems the polyhedron is essentially the same as its dominant, but this is not true in general.
-While there is an exact algorithm for problems with gap $1$, Theorem~\ref{CV} is existenial, with no construction.
+While there is an exact algorithm for problems with gap $1$, Theorem~\ref{CV} is does not suggest an efficient construction.
 %In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
@@
 % We show later, for $I$ with $g(I)<\infty$, the notation of dominant is in fact useful.
-\iffalse
-
-\begin{question*}\label{question1}
+\iffalse \begin{question*}\label{question1}
 	Assume reasonable complexity assumptions (such as UGC or $\textrm{P}\neq \textrm{NP}$).
@@
 \fi
-To study integrality gaps, we wish to find such a solution contructively:
+To study integrality gaps, we wish to find such a solution efficiently.
 \begin{question}\label{question2}
@@
 
-We give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems.
+Our final result is a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems.
 For this purpose assume $P= \{x\in \mathbb{R}^n_{\geq 0}: Ax\geq b\cdot \textbf{1}, x \leq b\cdot \textbf{1}\}$, where $A\in \mathbb{Z}^{m\times n}_{\geq 0}$ and $b\in \mathbb{Z}_{\geq 0}$.
+Here, $\textbf{1}$ is the vector of all ones of suitable dimension.
 Let $S= P\cap \mathbb{Z}^n$ and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$.
@@
 		\item for $\ell\in \{1,\ldots,n\}$, if $x_\ell =0$, then $\tilde{x}^i_\ell=0$ for $i =1,\ldots,k$, i.e. $\tilde{x}^i$ is in the support of $x$,
-		\item we have $A_j (\sum_{i=1}^{k}\theta_i\tilde{x}^i)\leq C\cdot A_j x$, for $j$ such that $A_j x =b$,  
+		\item for $j\in \{1,\ldots,m\}$ with $A_jx = b$, we have $A_j (\sum_{i=1}^{k}\theta_i\tilde{x}^i)\leq C\cdot A_j x$,
 	\end{itemize}
@@
 
-This means in order to prove an upper bound on the integrality gap of a  bounded covering problem, we need to show there is a convex combination of integer feasible points that is ``cheap'' on all tight cuts.
+This means in order to prove an upper bound on the integrality gap of a  bounded covering problem, we only need to show there is a convex combination of integer feasible points in the support of the optimal fractional solution that is ``cheap'' on all of its tight cuts.
 Notice that Theorem \ref{CV} requires the certificate convex combination to be ``cheap" on every single variable.
@@
 2EC) is bounded above by $C$.
-We use fundamental extreme point to create the ``hardest'' LP solutions to decompose.
+We use fundamental extreme points to create the ``hardest'' LP solutions to decompose.
 
@@
 If the algorithm ever fails in finding a feasible solution, the MILP has an unbounded gap.
+A feasible solution can be used to obtain new valid cuts to be added to the MILP formulation.
 \item We give an algorithm, Fractional Decomposition Tree (FDT), to construct the convex decomposition in the Carr-Vempala theorem, perhaps scaling by a factor larger than the integrality gap.
-Each step of this algorithm provides a {\em lower bound} on the instances integrality gap.
+Each step of this algorithm provides a {\em lower bound} on the integrality gap of the instances.
 This also provides a lower bound on the approximation factor of any LP-based approximation algorithm using this formulation.
 The overall approximation factor of the FDT algorithm is an upper bound on the integrality gap for that specific instance.
+In computational pursuit of improved lower bounds for integrality gap, FDT can be used to massively prune the instances.
+
 \item For a special set of problems related to TSP, where there is a notion of a fundamental extreme point and long-running attempts to exactly determine the integrality gap of classic formulations, experimental analysis with FDT can help give some intuition about which bound(s) is/are likely to be loose.
@@
 
-\item A stronger theoretical result on integrality gap that can be potentially employed to obtain improved upper bounds on the integrality gap of bounded covering problems.  
+\item We give a stronger characterization of integrality gap for bounded covering problems.
+Many important combinatorial optimization problems are bounded covering problems, for which finding improved upper bounds on the integrality gap has been open for decades.
 \end{itemize}

### 2019-05-13 Journal Version/2ECFDT.tex
main body changes

@@
 We do not know the exact value for $g_{\EC}$, but we know $\frac{6}{5} \leq g_{\EC} \leq \frac{3}{2}$ \cite{carr-ravi,Wolsey1980}.
-Also, we need to remark that polyhedral version of Christofides' algorithm provides a $\frac{3}{2}$-approximation for 2EC, i.e.
-we already have an algorithm with $C\leq \frac{3}{2}$.
-However, we showed in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$ for FEPs of order 10.
+Also, we need to remark that the polyhedral analysis of Christofides' algorithm provides a $\frac{3}{2}$-approximation for 2EC, i.e.
+we already have an algorithm with $C\leq \frac{3}{2}$ \cite{Wolsey1980}.
+However, we will show in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$ for FEPs of order 10.
 
@@
 First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for $\{0,1,2\}$ problems except for one additional clause. 
-
+\arash{put $\hat{x}^1$}
 \begin{restatable}{lemma}{2ECLPC}
 	\label{LPC2EC}
-	Given $x\in \EC(G)$, and $e\in E$ we can find in polynomial time vectors $x^0,x^1$ and $x^2$ and scalars $\gamma_0,\gamma_1$, and $\gamma_2$ such that: (i) $\gamma_0 + \gamma_1 +\gamma_2 \geq \frac{ 1}{g_{\EC}}$, (ii) $x^0,x^1,$ and $x^2$ are in  $ \EC(G)$, (iii) $x^0_e=0$, $x^1_e=1$, and $x^2_e=2$, (iv) $\gamma_0 x^0 + \gamma_1{x}^1  + \gamma_2x^2\leq {x}$, (v) for $f\in E$ with ${x}_f\geq 1$, we have $x^j_f\geq 1$ for $j=0,1,2$.
+	Given $x\in \EC(G)$, and $e\in E$ we can find in polynomial time vectors $\hat{x}^0,\hat{x}^1$ and $\hat{x}^2$ and scalars $\gamma_0,\gamma_1$, and $\gamma_2$ such that: (i) $\gamma_0 + \gamma_1 +\gamma_2 \geq \frac{ 1}{g_{\EC}}$, (ii) $\hat{x}^0,\hat{x}^1,$ and $\hat{x}^2$ are in  $ \EC(G)$, (iii) $\hat{x}^0_e=0$, $\hat{x}^1_e=1$, and $\hat{x}^2_e=2$, (iv) $\gamma_0 \hat{x}^0 + \gamma_1{\hat{x}}^1  + \gamma_2\hat{x}^2\leq {x}$, (v) for $f\in E$ with ${x}_f\geq 1$, we have $\hat{x}^j_f\geq 1$ for $j=0,1,2$.
 \end{restatable}
@@
 add one copy of $f$ to $F_i$.
-If for all edge $h\in P_f$, we have $\chi^{F'_i}_h=2$, then let $\chi^{F_i}_f=2$.
+If for all edges $h\in P_f$, we have $\chi^{F'_i}_h=2$, then let $\chi^{F_i}_f=2$.
 For $f\in E$ with $x_f<1$ we have
@@
 			&\leq \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
-			&= \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
+			&= \frac{\sum_{h\in P_f} g_{\EC}x_f}{\ceil{\frac{2}{\epsilon}}-1}\\
 			&= \frac{\ceil{\frac{2}{\epsilon}}}{\ceil{\frac{2}{\epsilon}}-1}g_{\EC}x_f
@@
 		\begin{equation}
-		x' \geq \sum_{i\in [k]: \chi^{F_i}_e=1}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}+\sum_{i\in [k]: \chi^{F_i}_e=2}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}.
+		x_e \geq \sum_{i\in [k]: \chi^{F_i}_e=1}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi_e^{F_i}+\sum_{i\in [k]: \chi^{F_i}_e=2}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi_e^{F_i}.
 		\end{equation}
-		Let $x^j = \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}$ and $\theta_j =  \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$ for $j=0,1,2$.
+		Let $x^j$ be such that $x_e^j = \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}$ and $\theta_j =  \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$ for $j=0,1,2$.
 It is easy to check that $x^j$ , $\theta_j$ for $j=0,1,2$ is a feasible solution to the LP above.
@@
 \begin{proof}
-	We proceed by induction on the $i$.
+	We proceed by induction on $i$.
 Define $L_0=\{(x^*,1)\}$.
@@
 Consider a solution $x^\ell$ in $L_{i-1}$.
-For $e\in \{e_1,\ldots,e_{i-1}\}$ if $x^\ell_e =0$, then by property (iv) in Lemma \ref{LPC2EC} we have $x^{\ell j}=0$ for $j=0,1,2$.
+For $e\in \{e_1,\ldots,e_{i-1}\}$ if $x^\ell_e =0$, then by property (iv) in Lemma \ref{LPC2EC} we have $x^{\ell j}_e=0$ for $j=0,1,2$.
 Otherwise by induction we have $x^{\ell}_{e}\geq 1$ in which case property (v) in Lemma \ref{LPC2EC} ensures that $x^{\ell j}_e\geq 1$ for $j=0,1,2$.
@@
 
-	Finally, if $|L'|\geq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
+	Finally, if $|L'|\leq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$ with $|L_i|\leq t$	.
 \end{proof}

### 2019-05-13 Journal Version/binaryFDT.tex
main body changes

@@
 Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively.
-Assume $S(I),P(I)\in [0,1]^n\times \mathbb{R}^p$.
+Assume $S(I),P(I)\subseteq [0,1]^n\times \mathbb{R}^p$.
 For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section.
@@
 We prove Lemma \ref{domlemma} by introducing an algorithm that ``fixes" the variables iteratively, starting from $x_1$ and ending at $x_t$.
-Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$.
+Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,n$.
 Now consider the following linear program.
 The variables of this linear program are the $z\in \mathbb{R}^n$ variables and $w\in \mathbb{R}^p$.
+
 \begin{align}
@@
 We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
-First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$.
+First notice that $\LP^{(0)}$ is clearly non-empty since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$.
 By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.	Thus we have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
@@
 Also, $(z^*,w^*)\in P$.
-By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ .
+By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$.
 We have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}$
@@
 Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
-Consider iteration $j$ of the Dom2IP algorithm.
-Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.
+Consider iteration $j$ of the DomToIP algorithm.
+Notice that $z\leq x^{(\ell+1)}\leq x^{({j-1})}\leq x^{(j)}$.
 We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero.
@@
 
-	Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: rounding up any fractional point in $P$ gives us a point in $\dom(P)$.
+	Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: rounding up any fractional point in $P$ gives us an integral point in $\dom(P)$.
 
@@
 By applying Lemma \ref{domlemma} we can obtain a point $(x',y')\in S$ such that $x'\leq x$.
-This conclude the description of the FDT algorithm and proves Theorem \ref{binaryFDT}.
+This concludes the description of the FDT algorithm and proves Theorem \ref{binaryFDT}.
 See Algorithm \ref{FDTFull} for a summary of the FDT algorithm.
@@
 	\begin{algorithm}[H]\label{FDTFull}
-		\KwIn{$P= \{(x,y)\in \mathbb{R}^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \mathbb{R}^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
-		\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
+		\KwIn{$P= \{(x,y)\in \mathbb{R}^{n+ p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \mathbb{R}^n_+ }\frac{\min_{(x,y)\in S }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
+		\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^kx^*$  for a $k\leq t$}
 		$L^0\leftarrow [(x^*,y^*),1]$\\
@@
 				Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
-				$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
+				$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\lambda\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\lambda\gamma_1]\}$\\			
 			}

### 2019-05-13 Journal Version/gap.tex
main body changes

@@
 Observe that if $C\geq g$, by Theorem \ref{CV}, there is a convex combination of points in $S$ that is dominated by $Cx$, i.e.
-there exists $\theta\in [0,1]^{k}$, where $\sum_{i=1}^{k}\theta_i=1$, and $x^i\in S$, such that $\sum_{i=1}^{k}\theta_ix^i\leq gx$.
+there exists $\theta\in [0,1]^{k}$, where $\sum_{i=1}^{k}\theta_i=1$, and $x^i\in S$, such that $\sum_{i=1}^{k}\theta_ix^i\leq Cx$.
 The same convex combination also trivially satisfies both requirements in Theorem \ref{tightcuts}.
@@
 	For any  $i\in\{1,\ldots,r\}$, there exists $\epsilon_i >0$ and ${x^i}\in P$ where ${x^i}\leq \frac{Cv^i-\epsilon_i z^i}{C(1-\epsilon_i)}$.
-\end{lemma}
+\end{lemma}\bob{$u^1(\epsilon)$ maybe change to $x^i(\epsilon)$}
 \begin{proof}
 
-	Let $u^i(\epsilon) = \frac{Cv^i-\epsilon z^i}{C(1-\epsilon)}$. For $j\in \{1,\ldots,m\}$, let $t_j = A_jz^i-Cb$ and $s_j=A_jv^i-b$. 
+	Let $x^i(\epsilon) = \frac{Cv^i-\epsilon z^i}{C(1-\epsilon)}$. For $j\in \{1,\ldots,m\}$, let $t_j = A_jz^i-Cb$ and $s_j=A_jv^i-b$. 
 	Assume $\epsilon <1$. For $j\in \{1,\ldots,m\}$ such that $A_jz^i\leq Cb$, i.e. $t_j\leq 0$ (this includes $j$ such that $A_jv^i=b$, i.e. $s_j=0$) we have
 	\begin{equation*}
-	A_j u^i(\epsilon) = \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}\geq \frac{Cb-\epsilon Cb}{C(1-\epsilon)}=b
+	A_j x^i(\epsilon) = \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}\geq \frac{Cb-\epsilon Cb}{C(1-\epsilon)}=b
 	\end{equation*}
-	Assume $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$.
-Notice that $\max_{j: t_j >0} \frac{s_j}{t_j}>0$ since for $j$ such that $t_j>0$, we have $A_jz_i > Cb$ which implies that $A_jv^i>b$, so $s_j>0$.
+	Assume $0< \epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$.
+Notice that $\min_{j: t_j >0} \frac{s_j}{t_j}>0$ since for $j$ such that $t_j>0$, we have $A_jz^i > Cb$ which implies that $A_jv^i>b$, so $s_j>0$.
 For $j$ such that $t_j>0$ we have
 	\begin{align*}
-	A_ju^i(\epsilon) &= \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}& \\
+	A_jx^i(\epsilon) &= \frac{CA_jv^i-\epsilon A_jz^i}{C(1-\epsilon)}& \\
 	&= \frac{C(b+s_j)-\epsilon (Cb+t_j)}{C(1-\epsilon)}&\\
@@
 	\end{align*} 
-	Therefore if $\epsilon \leq 1$ and $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$ we have $Au^i(\epsilon)\geq \textbf{1}b$.
-Next, we show that we can choose $\epsilon$ so that $ u^i(\epsilon)\geq 0$.
+	Therefore if $\epsilon \leq 1$ and $\epsilon \leq C\cdot\min_{j: t_j >0} \frac{s_j}{t_j}$ we have $Ax^i(\epsilon)\geq \textbf{1}b$.
+Next, we show that we can choose $\epsilon$ so that $ x^i(\epsilon)\geq 0$.
 
-	For $\ell\in \{1,\ldots,n\}$, if $z^i_\ell=0$, then we have $u_\ell^i(\epsilon) = \frac{Cv_\ell^i}{C(1-\epsilon)}\geq 0$, since $v^i_\ell\geq 0$ and $\epsilon <1$.
+	For $\ell\in \{1,\ldots,n\}$, if $z^i_\ell=0$, then we have $x_\ell^i(\epsilon) = \frac{Cv_\ell^i}{C(1-\epsilon)}\geq 0$, since $v^i_\ell\geq 0$ and $\epsilon <1$.
 Otherwise we have $z^i_\ell>0$.
@@
 This means that $\min_{\ell:z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}>0$.
-Now, for $\ell$ such that $z^i_\ell>0$, we have $u^i_\ell(\epsilon) = \frac{Cv_\ell^i-\epsilon z_\ell^i}{C(1-\epsilon)}\geq 0$ by choice of $\epsilon$.
+Now, for $\ell$ such that $z^i_\ell>0$, we have $x^i_\ell(\epsilon) = \frac{Cv_\ell^i-\epsilon z_\ell^i}{C(1-\epsilon)}\geq 0$ by choice of $\epsilon$.
 
-	Define $\epsilon_i =\min\{1, C\cdot \min_{j: t_j >0}\frac{s_j}{t_j},C\cdot\min_{\ell: z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}\}$.
-By the arguments above $Au^i(\epsilon_i)\geq \textbf{1}b$ and $u^i(\epsilon_i)\geq 0$.
-Define $x^i$ as follows: For each $j\in \{1,\ldots,m\}$, if $u^i_j(\epsilon_i)\leq b$, then let $x^i_j=u^i_j(\epsilon_i)$, otherwise let $x^i_j=b$.
+	Define $\epsilon_i =\frac{1}{2}\cdot \min\{1, C\cdot \min_{j: t_j >0}\frac{s_j}{t_j},C\cdot\min_{\ell: z^i_\ell>0}\frac{v^i_\ell}{z^i_\ell}\}$.
+By the arguments above $Ax^i(\epsilon_i)\geq \textbf{1}b$ and $x^i(\epsilon_i)\geq 0$.
+Define $x^i$ as follows: For each $j\in \{1,\ldots,m\}$, if $x^i_j(\epsilon_i)\leq b$, then let $x^i_j=x^i_j(\epsilon_i)$, otherwise let $x^i_j=b$.
 We need to show that $x^i\in P$.
@@
 Suppose for contradiction there is $j\in \{1,\ldots,m\}$ such that $A_jx^i <b$.
-Since $u^i(\epsilon)\in P$, there must be $\ell^*\in\{1,\ldots,n\}$ such that $u^i_{\ell^*}(\epsilon)>b$, and $A_{j,\ell^*}>0$.
+Since $x^i(\epsilon)\in P$, there must be $\ell^*\in\{1,\ldots,n\}$ such that $x^i_{\ell^*}(\epsilon)>b$, and $A_{j,\ell^*}>0$.
 But this means that $A_{j,\ell^*}\geq 1$ and $x^i_{\ell^*}=b$.
@@
 	We proceed by induction on $i$.
-If $i=1$, we just need to show that $Cv^1$ is dominated by a convex combination of $z^1$ and $Cv^2,\ldots,Cv^r$.
+If $i=1$, we just need to show that $Cv^1$ dominates by a convex combination of $z^1$ and $Cv^2,\ldots,Cv^r$.
 By Lemma \ref{epsilon}, there exists $x^1\leq  \frac{Cv^1-\epsilon_1z^1}{C(1-\epsilon_1)}$.
@@
 We have
-	\begin{equation*}
+	\begin{equation}\label{equation5}
 	Cv^1 \geq  \epsilon_1z^1 + C(1-\epsilon_1)x^1 \geq \epsilon_1z^1 + C(1-\epsilon_1) \sum_{\ell=1}^{r}\lambda^1_\ell v^\ell.
-	\end{equation*}
+	\end{equation}
 	Hence,
@@
 	\end{equation}
+
+	A curious reader might notice that Inequality \ref{equation5} looks very strange: Based on Lemma \ref{epsilon} we can consider the limit of this inequality when $\epsilon_1$ goes to zero.
+However, assuming $\lim_{\epsilon\rightarrow 0}\frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}=0$, and
+	$\lim_{\epsilon\rightarrow 0}\frac{\lambda^1_\ell}{1-(1-\epsilon_1)\lambda_1^1}$ exists for $\ell=2,\ldots,r$, we would have $v^1\geq \sum_{\ell=2}^{r} \frac{\lambda^1_\ell}{1-\lambda_1^1}v^\ell$.
+This is a contradiction to the fact that $v^1$ is an extreme point.
+We will later illustrate with an example where $\lim_{\epsilon\rightarrow 0}\frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}$ exists and is not zero (See Example \ref{epslimit})
+
 	Observe that $\frac{\epsilon_1}{1-(1-\epsilon_1)\lambda^1_1}$ and $(1-\epsilon_1)\frac{\lambda^1_\ell}{1-(1-\epsilon_1)\lambda_1^1}$ for $\ell=2,\ldots,r$ form convex multipliers, so the base case holds.
@@
 	\begin{align*}
-	Cv^j& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\theta^{j}_{i+1}Cv^{i+1}+  \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell.& (\mbox{By } \ref{IHs})\\
-		& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\sum_{\ell=1}^{i+1}\theta^{j}_{i+1}\mu_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_{i+1}\mu_{\ell}Cv^\ell +   \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell.& (\mbox{By } \ref{claim})\\
-		&= \sum_{\ell=1}^{i} (\theta^j_\ell+\mu_{\ell}\theta^j_{i+1}) z^\ell + \mu_{j+1}\theta^j_{i+1}z^{i+1} + \sum_{\ell=i+2}^{r} (\theta^j_\ell+\mu_\ell\theta^j_{i+1})Cv^\ell.&
+	Cv^j& \geq \sum_{\ell=1}^{i} \theta^{j,i}_\ell z^\ell +\theta^{j,(i+1)}_{i+1}Cv^{i+1}+  \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell & (\mbox{By } \ref{IHs})\\
+		& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\sum_{\ell=1}^{i+1}\theta^{j}_{i+1}\mu_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_{i+1}\mu_{\ell}Cv^\ell +   \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell& (\mbox{By } \ref{claim})\\
+		&= \sum_{\ell=1}^{i} (\theta^j_\ell+\mu_{\ell}\theta^j_{i+1}) z^\ell + \mu_{i+1}\theta^j_{i+1}z^{i+1} + \sum_{\ell=i+2}^{r} (\theta^j_\ell+\mu_\ell\theta^j_{i+1})Cv^\ell.&
  			\end{align*} 
@@
 			\end{align*}
-			It is easy to show that  multipliers above are convex.
+			It is easy to show that  multipliers on the RHS above are convex after multiplying be the positive constant on the LHS.	
 \end{proof}
 
-\begin{example}
+\begin{example}\label{epslimit}
 
-Consider  $\EC(G) = \{x\in [0,2]^E_{\geq 0}: \; x(\delta(U))\geq 2 \mbox{ for $\emptyset \subset U \subset V$}\},$ where $G=(V,E)$ is the graph in Figure \ref{example}. 
+Consider  $\EC(G) = \{x\in [0,2]^E: \; x(\delta(U))\geq 2 \mbox{ for $\emptyset \subset U \subset V$}\},$ where $G=(V,E)$ is the graph in Figure \ref{example}. 
 \begin{figure}[h]
@@
 \end{equation*}
-is in $\EC(G)$ for sufficiently large $k$. The vectors defined below $v^2,\ldots,v^7$ are also extreme points of $\EC(G)$.
+is in $\EC(G)$ for sufficiently large $k$. The vectors defined below $v^2,\ldots,v^7$ are also integer extreme points of $\EC(G)$.
 
@@
 \end{equation*}
-Now, this allows us to rewrite Inequality \ref{equation6} for this example.
+Now, this allows us to rewrite Inequality (\ref{equation6}) for this example.
 \begin{equation*} 

### 2019-05-13 Journal Version/introduction.tex
main body changes

@@
 The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq 2|V|-1$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g_{\EC}^{k}$, where $g_{\EC}$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol})
+Moreover, $C\leq g_{\EC}^{k}$, where $g_{\EC}$ is the integrality gap of the 2-edge-connected multigraph problem with respect to the formulation in (\ref{2ECpol}).
 \end{restatable}
@@
 Our final result is a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems.
+Consider an instance $I$ where $p=0$ (pure integer program case).
+By Theorem \ref{CV}, integrality gap $g_I$ is the smallest number $C_1$ such that for each $x\in P(I)$, there is convex combination of points $z^1,\ldots,z^k$ in $S(I)$ that is dominated by $C_1x$, i.e.
+$\sum_{i=1}^{k}\lambda_i z^i \leq C_1x$.
+Note this clearly implies $\sum_{i=1}^{k}\lambda_i z^i_e \leq C_1x_e$.
+This allows us to introduce a lower bound on the integrality gap: let $C_2$ be the smallest number such  that for each $x\in P(I)$, there is convex combination of points in $S(I)$ such that for all $x\in P(I)$ there is a convex combination $\sum_{i=1}^{k}\lambda_iz^i$ of point in $S(I)$ such that $\sum_{i=1}^{k}\lambda_iz^i\leq C_2x$.
+As argued above $C_2\leq C_1$.
+Here, we can see that $\sum_{i=1}^{k}\lambda_i\langle y\cdot z^i\rangle\leq C_2\langle y\cdot x\rangle$.
+In particular we have $\sum_{i=1}^{k}\lambda_i\langle A_j\cdot z^i\rangle\leq C_2\langle A_j\cdot x\rangle$, where $A_j$ is the $j$-th row of $A$ for some $j=1,\ldots,m$.
+Even more particularly, $\sum_{i=1}^{k}\lambda_i\langle A_j\cdot z^i\rangle\leq C_2 b_j$ for $j\in \{1,\ldots,m\}$ such that $A_jx= b_j$, a tight constraints of $x$.
+This motivates us to define $C_3$ which is the smallest number such that for all $x\in P(I)$ there is convex combination of points $z_1,\ldots,z_k$ in $S(I)$ such that $\sum_{i=1}^{k}\theta_i\langle A_j,z^i\rangle\leq C_3 b_j$ for $j$ such that $A_jx = b_j$.
+We have $C_3\leq C_2\leq C_1$.
+We show for bounded covering problems $C_3=C_2=C_1=g_I$.
+
 For this purpose assume $P= \{x\in \mathbb{R}^n_{\geq 0}: Ax\geq b\cdot \textbf{1}, x \leq b\cdot \textbf{1}\}$, where $A\in \mathbb{Z}^{m\times n}_{\geq 0}$ and $b\in \mathbb{Z}_{\geq 0}$.
@@
 Examples of problems whose natural linear programming relaxation is $P$ (for some matrix $A$ and integer $b$) include the 2-edge-connected multigraph problem, Steiner tree problem, tree augmentation problem, and many others.
+We call this general problem a bounded covering problem.
 

### 2019-10-11 gap.tex
Add files via upload

@@
 Let $z^i = \sum_{\ell=1}^{k_i} \lambda^i_\ell w^i_\ell$.
+
+We can get the following lemma by tightness vs slackness arguments.
+
 \begin{lemma}\label{epsilon}
@@
 \begin{lemma}\label{tightcutcomb}
-	There exists a convex combination of point in $S$ that is dominated by $Cv^i$ for $i=1,\ldots,r$.
+	There exists a convex combination of points in $S$ that is dominated by $Cv^i$ for $i=1,\ldots,r$.
 \end{lemma}
@@
 		& \geq \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell +\sum_{\ell=1}^{i+1}\theta^{j}_{i+1}\mu_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_{i+1}\mu_{\ell}Cv^\ell +   \sum_{\ell=i+2}^{r}\theta^{j}_{\ell}Cv^\ell.& (\mbox{By } \ref{claim})\\
-		&= \sum_{\ell=1}^{i} (\theta^j_\ell+\mu_{\ell}\theta^j_{i+1}) z^\ell + \mu_{j+1}\theta^j_{i+1}z^{i+1} + \sum_{\ell=i+2}^{r} (\theta^j_\ell+\mu_\ell\theta^j_{i+1})Cv^\ell.&
+		&= \sum_{\ell=1}^{i} (\theta^j_\ell+\mu_{\ell}\theta^j_{i+1}) z^\ell + \mu_{i+1}\theta^j_{i+1}z^{i+1} + \sum_{\ell=i+2}^{r} (\theta^j_\ell+\mu_\ell\theta^j_{i+1})Cv^\ell.&
  			\end{align*} 
@@
 		Cv^{i+1}&\geq \epsilon_{i+1}z^{i+1}+ C(1-\epsilon_{i+1})x^{i+1}\\
-		&\geq \epsilon_{i+1}z^{i+1}+ (1-\epsilon_{i+1})\sum_{\ell=1}^{k}\lambda_{\ell}Cv^\ell
+		&\geq \epsilon_{i+1}z^{i+1}+ (1-\epsilon_{i+1})\sum_{\ell=1}^{r}\lambda_{\ell}Cv^\ell
 			\end{align*}
-			Applying induction we can replace $Cv^j$ by $ \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell + \sum_{\ell=i+1}^{r}\theta^{j}_{\ell}Cv^\ell$ for $j=1,\ldots,i$. 
+			Applying induction $Cv^j$ dominates $ \sum_{\ell=1}^{i} \theta^{j}_\ell z^\ell + \sum_{\ell=i+1}^{r}\theta^{j}_{\ell}Cv^\ell$ for $j=1,\ldots,i$. 
 			This means
@@
 			(1-(1-\epsilon_{i+1})(\lambda_{i+1}+\sum_{j=1}^{i}\lambda_j\theta^j_{i+1}))Cv^{i+1}&\geq \epsilon_{i+1}z^{i+1}+(1-\epsilon_{i+1})\sum_{j=1}^{i}\lambda_j (\sum_{\ell=1}^{i}\theta^j_\ell z^\ell+ \sum_{\ell=i+2}^{r}\theta^j_\ell Cv^\ell)\\
-			&+(1-\epsilon_{i+1})(\sum_{j=1}^{i}\lambda_j \lambda^j_{i+1}+\lambda^i_{i+1})C+ (1-\epsilon_{i+1})\sum_{j=i+2}^{r}\lambda_jCv^{j} 
+			&\;\;\;\;+(1-\epsilon_{i+1})\sum_{j=i+2}^{r}\lambda_jCv^{j} 
 			\end{align*}
+
 			It is easy to show that  multipliers above are convex.
 \end{proof}
+
+\begin{example}
+
+Consider  $\EC(G) = \{x\in [0,2]^E: \; x(\delta(U))\geq 2 \mbox{ for $\emptyset \subset U \subset V$}\},$ where $G=(V,E)$ is the graph in Figure \ref{example}. 
+\begin{figure}[h]
+	\centering
+	\includegraphics[width=0.2\linewidth]{example.pdf}
+	\caption{Graph $G=(V,E)$. Let $H$ be the Hamiltonian cycle of $G$ that contains edges $(1,2),(2,3),(3,4),(4,5),(5,6),(6,7),(7,8),(1,8)$. Let $M= E\setminus H$: $M=\{(1,5),(2,7),(3,6),(4,8)\}$.}
+	\label{example}
+\end{figure}
+
+Let $v^1$ be the following extreme point of $\EC(G)$: \begin{equation*}
+v^1_{e} = \left\{ \begin{array}{ll}
+1 & \mbox{if $e\in M$};\\
+1/2 & \mbox{if $e\in H$}.
+\end{array} \right. 
+\end{equation*}
+Define $z^1$ to be the following vector:
+\begin{equation*}
+z^1_{e} = \left\{ \begin{array}{ll}
+7/5 & \mbox{if $e= (1,5)$};\\
+1 & \mbox{if $e\in M\setminus \{(1,5)\}$};\\
+2/5 & \mbox{if $e \in \{(1,8),((4,5))\}$};\\
+3/5 & \mbox{if $e\in H\setminus\{(1,8),((4,5))\} $}.
+\end{array} \right. 
+\end{equation*}
+It is easy to check that $z^1$ satisfies the requirement of Theorem \ref{gap} when setting $C=\frac{6}{5}$.
+In particular, we have $ z^1(\delta(U))\leq \frac{6}{5}v^1(\delta(U))$ for all $\emptyset\subset U \subset V$.
+Also, is it easy to decompose $z^1$ into a convex combination of integer point in of $\EC(G)$.
+
+Now, we want to set the $\epsilon_i$ in the statement of Lemma \ref{epsilon} to be $2^{-k}$. By Lemma \ref{epsilon}
+\begin{equation*}
+x^1_{e} = \left\{ \begin{array}{ll}
+\frac{2^k-7/6}{2^k-1} & \mbox{if $e= (1,5)$};\\
+\frac{2^k-5/6}{2^k-1} & \mbox{if $e\in M\setminus \{(1,5)\}$};\\
+\frac{2^k- 2/3}{2\cdot (2^k-1)} & \mbox{if $e \in \{(1,8),((4,5))\}$};\\
+\frac{1}{2} & \mbox{if $e\in H\setminus\{(1,8),((4,5))\} $}.
+\end{array} \right. 
+\end{equation*}
+is in $\EC(G)$ for sufficiently large $k$. The vectors defined below $v^2,\ldots,v^7$ are also extreme points of $\EC(G)$.
+
+\begin{table}[h]
+	\centering
+	\begin{tabular}{ccccccccccccc}
+		\toprule
+		& (1,5) & (2,7)& (3,6)&(4,8)&(1,2)&(2,3)&(3,4)&(4,5)&(5,6)&(6,7)&(7,8)&(1,8)      \\ \midrule
+			$v^2=$ & (0&1&2&1&0&1&1&2&0&0&1&2)  \\
+			$v^3=$ & (0&2&2&1&0&0&0&1&1&1&1&2)\\
+			$v^4=$ & (1&2&2&2&1&1&1&1&0&0&0&0)\\
+			$v^5=$ & (0&2&1&1&1&1&0&1&1&0&0&1)\\
+			$v^6=$ & (1&1&1&2&0&1&0&0&1&0&1&1)\\
+			$v^7=$ & (1&1&1&2&1&0&1&1&0&1&0&0)\\
+				 \bottomrule
+	\end{tabular}
+\end{table}
+Moreover, we have 
+\begin{equation*}
+x^1 = (1-8\lambda)v^1+ \lambda v^2 + 2\lambda v^3+\lambda v^4+ \lambda v^5+ \lambda v^6 + 2\lambda v^7, \quad \lambda = \frac{1}{24\cdot (2^k-1)}
+\end{equation*}
+Now, this allows us to rewrite Inequality \ref{equation6} for this example.
+\begin{equation*} 
+\frac{6}{5}v^1 \geq \frac{3}{4} z^1 +\frac{1}{32}(\frac{6}{5}\cdot v^2) +\frac{1}{16}(\frac{6}{5}\cdot v^3) + \frac{1}{32}(\frac{6}{5}\cdot v^4)+\frac{1}{32}(\frac{6}{5}\cdot v^5) + \frac{1}{32}(\frac{6}{5}\cdot v^6)+ \frac{1}{16}(\frac{6}{5}\cdot v^7).
+\end{equation*}
+\end{example}

### 2019-10-11 introduction.tex
ipco format added
shorter version
Add files via upload

--- 2018-11-02 introduction.tex
@@
 
-Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, is a classic NP-hard problem \cite{GJ79}.
-In fact it is NP-hard in general to determine if there is a feasible solution to an MILP problem \cite{GJ79}.
-However, intelligent branch-and-bound strategies allow commercial and open-source MIP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.
-Modeling combinatorial optimization problems with MILPs also started the very popular area of LP-based approximation algorithms.
-
-Consider the set of point described by a set 
+Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, models many practical optimization problems including scheduling, logistics and resource allocation.
+The set of feasible points for a MILP is the set
 \begin{equation}
-S(A,G,b)= \{(x,y)\in \mathbb{Z}^{n}\times \mathbb{R}^p\;:\; Ax+Gy\geq b\}  \label{S}
+S(A,G,b)= \{(x,y)\in \mathbb{Z}^{n}\times \mathbb{R}^p\;:\; Ax+Gy\geq b\}  \label{S}.
 \end{equation}
-and the  linear relaxation of set $S(A,G,b)$,
+If we drop the integrality constraints, we have the linear relaxation of set $S(A,G,b)$,
 \begin{equation}
@@
 
-To make the notation simpler we use $I=(A,G,b)$, i.e.
-an instance of the formulation.
-Then we use $S(I)$ and $P(I)$ to denote $S(A,G,b)$ and $P(A,G,b)$, respectively.
-Notice that $\min \;\{cx:\; (x,y) \in S(I)\}$ is in fact an MILP problem and $\min \;\{cx:\;(x,y)\in P(I) \}$ is lower bound provided from the LP relaxation.
-Let $z_{IP}(I,c)$ and $z_{LP}(I,c)$ be the optimal solution to these problems, respectively.
+Let $I=(A,G,b)$ be the feasible set of a specific instance.
+Then $S(I)$ and $P(I)$ denote $S(A,G,b)$ and $P(A,G,b)$, respectively.
+Given a linear objective function $c$, a Mixed-Integer-Linear Program (MILP) is $\min \;\{cx:\; (x,y) \in S(I)\}$.
+It is  NP-hard even to determine if an MILP instance has a feasible solution~\cite{GJ79}.
+However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.
 
-Many researchers (see \cite{sw, vazirani}) have developed polynomial time algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$ for some $C$ which can be a constant number or dependent on some parameter of the MILP, e.g.
+Relaxing the integrality constraints gives the polynomial-time-solvable linear-programming relaxation: $\min \;\{cx:\;(x,y)\in P(I) \}$.
+The optimal value of this linear program (LP), denoted $z_{LP}(I,c)$, is a lower bound on the optimal value for the MILP, denoted $z_{IP}(I,c)$.
+The solution can also provide some useful global structure, even though the fractional values are not directly meaningful.
+{\em LP-based approximation algorithms} for combinatorial problems involve modeling the problem as a MILP, solving the LP relaxation, finding a (problem-specific) integer-feasible solution from the LP solution, and proving an approximation bound by comparing the solution value to the LP lower bound.
+
+Many researchers (see \cite{vazirani,sw}) have developed polynomial-time LP-based algorithms that find solutions for special classes of MILPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$.
+The approximation factor $C$ can be a constant or depend a parameter of the MILP, e.g.
 $O(\log(n))$.
 However, for many combinatorial optimization problems there is a limit to such techniques.
-Let $g_I= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$.
-Parameter $g_I$ depends on set $S(I)$ and the linear constraints in (\ref{S}) and is known as the \textit{integrality gap} of the formulation for instance $I$.
-It is easy to see, that we cannot hope to find solutions for the MILP with objective values better than $g_I\cdot z_{LP}(I,c)$.
-More generally we can define the integrality gap for a class of instances $\mathcal{I}$.
-In this case, the integrality gap for problem $\mathcal{I}$ is
+Define the \textit{integrality gap} of the MILP formulation for instance $I$ to be $g_I= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$.
+This value depends on the constraints in (\ref{S}).
+We cannot hope to find solutions for the MILP with objective values better than $g_I\cdot z_{LP}(I,c)$.
+
+More generally we can define the integrality gap for a class of instances $\mathcal{I}$:% In this case, the integrality gap for problem $\mathcal{I}$ is
 \begin{equation}
@@
 \end{equation}
+For example, finding a  minimum-weight 2-edge-connected multigraph has a natural formulation: every cut is crossed at least twice.
+The gap for this formulation is at most $\frac{3}{2}$ \cite{Wolsey1980} and at least $\frac{6}{5}$ \cite{carr-ravi}.
+Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation.
 
-For example, in the problem of finding a minimum weight 2-edge-connected multigraph, the gap of the the natural formulation, constraining every cut to be crossed at least twice, is at most $\frac{3}{2}$ \cite{Wolsey1980} and at least $\frac{6}{5}$ \cite{carr-ravi}.
-Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation.
-If we have $g_I=1$, $P(I)=\conv(S(I))$ and $P(I)$ is an \textit{integral} polyhedron.
-There are many interesting examples of such formulations such as spanning tree polytope and the perfect matching polytope \cite{schrijver}.
-For such problems we know how to write a vector $x\in P(I)$ as convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.
+\paragraph{The value of good MILP formulations:} There can be multiple correct MILP formulations for a problem with different integrality gaps.
+Finding MILP formulations with small integrality gap, e.g.
+by adding extra contraints, enables better provable approximation algorithms.
+Such formulations are also likely to work better in practice when using exact solvers because branch-and-bound algorithms for MILP use LP bounds to prove whole regions of the search space can be pruned.
+In this paper, we provide tools to help modelers develop MILP formulations with integrality gaps closer to the optimal.
 
-\begin{fact}\label{cara}
+\paragraph{Decomposition} Our methods apply theory connecting integrality gaps to sets of feasible solutions.
+Instances $I$ with  $g_I=1$ has $P(I)=\conv(S(I))$, the convex hull of the lattice of feasible points.
+In this case, $P(I)$ is an \textit{integral} polyhedron.
+The spanning-tree polytope and the perfect-matching polytope \cite{schrijver} have this property.
+For such problems there is an algorithm to express vector $x\in P(I)$ as a convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.
+\begin{proposition}\label{cara}
 	If $g_I=1$, then for $(x,y)\in P(I)$, there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$.
 Moreover, we can find such a convex combination in polynomial time.
-\end{fact}
+\end{proposition}
 
-	Now assume $1<g<\infty$. Denote by $\dom(P(I))$ be the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$.
-
-	A analogous result to Fact \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}.
+Carr and Vempala~\cite{CV} gave a decomposition result for integrality gap $1<g(I)<\infty$.
+%A analogous result to Proposition \ref{cara} is the following theorem due to Carr and Vempala \cite{CV}, which
+This is a generalization of Goemans' proof for blocking polyhedra \cite{goemans}.
 
@@
 \end{theorem}
+Here $\dom(P(I))$ is the set of points $(x',y')$ such that there exists a point $(x,y)\in P$ with $x'\geq x$, also known as the dominant of $P(I)$.
+For covering problems the polyhedron is essentially the same as its dominant, but this is not true in general.
+While there is an exact algorithm for problems with gap $1$, Theorem~\ref{CV} is existenial, with no construction.
+%In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
+%This points to an interesting open question. 
+% We show later, for $I$ with $g(I)<\infty$, the notation of dominant is in fact useful.
+\iffalse
 
-In contrast to Fact \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
-This points to an interesting open question.
-
-\begin{question}\label{question1}
-	Assume reasonable complexity assumptions (such as $\UGC$ or $\Pp\neq \NP$).
+\begin{question*}\label{question1}
+	Assume reasonable complexity assumptions (such as UGC or $\textrm{P}\neq \textrm{NP}$).
 Given instance $I$ with $1<g_I<\infty$ and $(x,y)\in P(I)$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(\conv(S(I)))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g_Ix$ in polynomial time?
-\end{question}
+\end{question*}
 
@@
 In fact, for set cover the approximation algorithm achieving the same factor as the integrality gap lower bound, is a \textit{randomized rounding} algorithm.
-Rhagavan and Thompson \cite{randomizedrounding} showed that this technique acheives provably good approximation for many combinatorial optimization problems.
+Raghavan and Thompson \cite{randomizedrounding} showed that this technique achieves provably good approximation for many combinatorial optimization problems.
 
-One key step, in answering Question \ref{question1} and \ref{question2} is being able to find a solution in $S(I)$.
-In fact, for general $I$ it is NP-hard to even decide if $S(I)$ is empty or not.
-There are a number of heuristics for this purpose, such as the feasibility pump heuristic \cite{fp1,fp2}.
-These heuristics are often very effective and fast in practice, however, they can sometimes fail in finding a feasible solution.
-In addition these algorithms do not provide any bounds on the quality of the solution they find.
+If we relax Question \ref{question1} (resp.
+Question \ref{question2}), but multiplying $g(I)$ (resp.
+$g(\mathcal{I})$) by a factor $C$, they are still very interesting, since they will provide upper bounds on the integraltiy gap the instance (resp.
+the problem).
+The results in this paper serve this purpose.
+\fi
+To study integrality gaps, we wish to find such a solution contructively:
+\begin{question}\label{question2}
+	Assume reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g_{\mathcal{I}}<\infty$, and $(x,y)\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq $C$ g_{\mathcal{I}}x$ in polynomial time?
+We wish to find the smallest slack factor $C$ as possible.
+\end{question}
 
-\subsection{Our results}
+We give a general approximation framework for solving $\{0,1\}$-MILPs.
+Consider the set of point described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively.
+Assume in addition that $S(I),P(I)\subseteq [0,1]^n\times \mathbb{R}^p$.
+For a vector $x\in \mathbb{R}_{\geq 0}^n$ such that $(x,y)\in P(I)$ for some $y\in \mathbb{R}^p$, let $\spp(x)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.
 
-In this paper we study Theorem \ref{CV} and the natural questions that follow from it (Questions \ref{question1} and \ref{question2}).
-
- We give a general approximation framework for solving $\{0,1\}$-MILPs.  Consider the set of point described by a set 
-\begin{equation}
-S(I)= \{(x,y)\in \mathbb{R}^{n\times p}\;:\; Ax+Gy\geq b,\; x\in \{0,1\}\},  \label{S'}
-\end{equation}
-and a linear relaxation of set $S$
-\begin{equation}
-P(I) = \{(x,y)\in \mathbb{R}^{n\times p}\;:\; Ax+Gy\geq b,\; 0 \leq x\leq 1\}. \label{P'}
-\end{equation}
-For a point $(x,y)\in P(I)$, let $\sup(x,y)= \{i \in \{1,\ldots,n\}: x_i \neq 0\}$.  We prove the following algorithm.
+\textit{Fractional Decomposition Tree} (FDT) is a polynomial-time algorithm that given a point $(x,y)\in P(I)$ produces a convex combination of feasible points in $S(I)$ that are dominated by a ``factor" $C$ of $x$ in the coordinates corresponding to $x$.
+If $C = g_I$, it would be optimal.
+However we can only guarantee a factor of $g_I^{|\spp(x)|}$.
+FDT relies on iteratively solving linear programs that are about the same size as the description of $P(I)$.
 
@@
 	\label{binaryFDT}
-	Assume $1\leq g_I<\infty$. 	
-The FDT algorithm (Algorithm \ref{FDTFull}), given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\sup(x^*,y^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g_I^{|\sup(x^*,y^*)|}$.
+	Assume $1\leq g_I 	<\infty$. 	
+	The Fractional Decomposition Tree (FDT) algorithm, given $(x^*,y^*)\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $(z^1,w^1),\ldots,(z^k,w^k) \in S(I)$ such that $k\leq |\spp(x^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
+Moreover, $C\leq g_I^{|\spp(x^*)|}$.
 \end{restatable}
 
-Notice, that the FDT algorithm needs to find feasible solutions to any MILP with finite gap. This can be of independent interest.
+FDT finds feasible solutions to any MILP with finite gap. This can be of independent interest, especially in proving that a model has unbounded gap.
 \begin{restatable}{theorem}{DomToIP}
-	\label{DomToIP}
-		Assume $1\leq g_I \leq \infty$. The DomToIP algorithm (Algorithm \ref{domtoIP}) finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
+	\label{domtoIP}
+	Assume $1\leq g_I < \infty$. The DomToIP algorithm finds $(\hat{x},\hat{y})\in S(I)$ in polynomial time.
 \end{restatable}
 
-In attempt to extend our results into $\{0,1,2\}$-MILPs we give an FDT algorithm for the 2-edge-connected multigraph problem.
-In this problem we want to find the minimum weight 2-edge-connected multigraph in a graph $G=(V,E)$ with respect to weights $c\in \mathbb{R}^E_{\geq 0}$.
-For this problem the natural linear programming relaxation is
+For general $I$ it is NP-hard to even decide if $S(I)$ is empty or not.
+There are a number of heuristics for this purpose, such as the feasibility pump heuristic \cite{fp1,fp2}.
+These heuristics are often very effective and fast in practice, however, they can sometimes fail to find a feasible solution.
+These heuristics do not provide any bounds on the quality of the solution they find.
+
+We consider the following TSP-related problems.
+The {\em 2-edge-connected subgraph problem (2EC)} is to find a minimum-weight 2-edge-connected multigraph (subgraph which can contain multiple copies of each edge)
+in a graph $G=(V,E)$ with respect to weights $c\in \mathbb{R}^E_{\geq 0}$.
+In the {\em tree-augmentation problem (TAP)} we wish to add a minimum-cost set of edges to a tree to make it 2-edge-connected.
+We formally define TAP in Section~\ref{experiment}.
+
+One can extend the FDT algorithm for binary MILPs into covering $\{0,1,2\}$-MILPs by losing a factor $2^{|\spp(x)|}$ on top of the loss for FDT.
+In order to eradicate this extra factor, we need to treat the coordinate $i$ with $x_i=1$ differently.
+For 2EC we are able to achieve this.
+The 2EC problem has the natural linear programming relaxation is
 \begin{equation}\label{2ECpol}
- \EC(G)= \{x\in \mathbb{R}_{\geq 0}^{E}\;:\; x(\delta(S))\geq 2 \text{ for $\emptyset \subset S\subset V$})\}.\end{equation}
+\EC(G)= \{x\in [0,2]^{E}\;:\; x(\delta(U))\geq 2 \text{ for $\emptyset \subset U\subset V$})\}.
+\end{equation}
  We prove the following theorem.
@@
 	Let $G=(V,E)$ and $x$ be an extreme point of  $\EC(G)$.
-The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq O(|V|)$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx^*$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g_{\EC}^{O(|V|)}$, where $g_{\EC}$ is the integrality gap of the 2-edge-connected multigraph problem with respect to formulation in (\ref{2ECpol})
+The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq 2|V|-1$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq Cx$, and $\sum_{i=1}^{k}\lambda_i = 1$.
+Moreover, $C\leq g_{\EC}^{k}$, where $g_{\EC}$ is the integrality gap of the 2-edge-connected multigraph problem with respect to the formulation in (\ref{2ECpol}).
 \end{restatable}
 
-Although the bound guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are very large for large problems, we show that in practice, the algorithm works very well providing approximation ratios that are far better than the theoretical bound in the theorem statements.
-We examine FDT for binary MILPs for problems such as the tree augmentation problem (TAP) and we apply FDT for 2EC on some interesting and ``hard to decompose" points in the linear relaxation.
+We give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems.
+For this purpose assume $P= \{x\in \mathbb{R}^n_{\geq 0}: Ax\geq b\cdot \textbf{1}, x \leq b\cdot \textbf{1}\}$, where $A\in \mathbb{Z}^{m\times n}_{\geq 0}$ and $b\in \mathbb{Z}_{\geq 0}$.
+Let $S= P\cap \mathbb{Z}^n$ and $g= \max_{c\geq 0} \frac{\min_{x\in S}cx}{\min_{x\in P}cx}$.
+Examples of problems whose natural linear programming relaxation is $P$ (for some matrix $A$ and integer $b$) include the 2-edge-connected multigraph problem, Steiner tree problem, tree augmentation problem, and many others.
 
+\begin{restatable}{theorem}{tightcuts}
+	\label{tightcuts}	
+	We have $g\leq C$ if and only if for each extreme point $x$ of $P$, there exists $\theta\in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i = 1$ and $\tilde{x}^i \in S$ for $i=1,\ldots,k$ such that \begin{itemize}
+		\item for $\ell\in \{1,\ldots,n\}$, if $x_\ell =0$, then $\tilde{x}^i_\ell=0$ for $i =1,\ldots,k$, i.e. $\tilde{x}^i$ is in the support of $x$,
+		\item we have $A_j (\sum_{i=1}^{k}\theta_i\tilde{x}^i)\leq C\cdot A_j x$, for $j$ such that $A_j x =b$.
+	\end{itemize}
+\end{restatable}
+
+This means in order to prove an upper bound on the integrality gap of a  bounded covering problem, we need to show there is a convex combination of integer feasible points that is ``cheap'' on all tight cuts.
+Notice that Theorem \ref{CV} requires the certificate convex combination to be ``cheap" on every single variable.
+
+\paragraph{Experiments} Although the bound guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are very large for large problems, we show that in practice, the algorithm works very well for the TSP-like problems described above.
+We show how one might use FDT to investigate the integrality gap for such well-studied problems.
+
+Known polyhedral structure makes it easier to study integrality gaps for such problems.
+Carr and Ravi \cite{carr-ravi} introduced fundamental extreme points.
+A point $x$ in Held-Karp relaxation for TSP (or 2EC; they have the same relaxation) is a point whose support of $x$, namely $G_x$ satisfies the following: i)  $G_x$ is a cubic graph, ii) in $G_x$ there is exactly one edge with $x_e=1$ incident to each node iii) The fractional edges of $G_x$ form a Hamiltonian cycle.
+We say a fundamental extreme point (FEP) is {\em order $k$} if there are $k$ nodes on this Hamiltonian cycle.
+An FEP of order $k$ could represent an instance with many more than $k$ vertices.
+Carr and co-authors~\cite{CV,carr-ravi,BC11} proved that showing that $Cx$ is a convex combination of tours (resp.
+2-edge-connected multigraphs) for all fundamental extreme points is equivalent to proving that the integrality gap for TSP (resp.
+2EC) is bounded above by $C$.
+We use fundamental extreme point to create the ``hardest'' LP solutions to decompose.
+
+There are fairly good bounds for the integrality gap for TSP or $\EC$.
+Benoit and Boyd \cite{TSPcompute} used a quadratic program to show the integrality gap for TSP is at most $\frac{20}{17}$ for graphs with at most 10 vertices.
+Alexander et.
+al \cite{abe} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $\EC$ on graphs with at most 10 vertices.
+For $\EC$ we show that the integrality gap is at most $\frac{6}{5}$ for FEPs of order at most 12.
+An FEP of order $k$ might correspond to an extreme point of a much bigger graph, since each edge in a FEP with value 1 actually corresponds to a path of edges with value 1.
+%In fact, since FDT can be applied to different problem, we can use it to evaluate the integrality gap of other well-known problem.
+For TAP, we create random fractional extreme points and round them using FDT.
+For the instances that we create the blow-up factor is always below $\frac{3}{2}$ providing an upper bound for such instances.
+
+% providing approximation ratios that are far better than the theoretical bound in the theorem statements.
+%We examine FDT for binary MILPs for problems such as the tree augmentation problem (TAP) and we apply FDT for 2EC on some interesting and ``hard to decompose" points in the linear relaxation.
+Our computational results show that the FDT algorithm is a good tool to evaluate the integrality gap of integer programming formulations.
+
+\paragraph{Contributions}  The paper has the following contributions: 
+\begin{itemize}
+\item We give a simple algorithm, DomToIP, that can prove a binary formulation’s integrality gap is unbounded or if not provide a feasible integer solution.
+Someone formulating a first MILP for a new problem can test it with DomToIP.
+If the algorithm ever fails in finding a feasible solution, the MILP has an unbounded gap.
+\item We give an algorithm, Fractional Decomposition Tree (FDT), to construct the convex decomposition in the Carr-Vempala theorem, perhaps scaling by a factor larger than the integrality gap.
+Each step of this algorithm provides a {\em lower bound} on the instances integrality gap.
+This also provides a lower bound on the approximation factor of any LP-based approximation algorithm using this formulation.
+The overall approximation factor of the FDT algorithm is an upper bound on the integrality gap for that specific instance.
+\item For a special set of problems related to TSP, where there is a notion of a fundamental extreme point and long-running attempts to exactly determine the integrality gap of classic formulations, experimental analysis with FDT can help give some intuition about which bound(s) is/are likely to be loose.
+Computing on fundamental extreme points is a way to experimentally characterize the gap upper bound.
+There is no guarantee.
+Still, this can help direct theoretical analysis in the most promising direction.
+For instance for 2EC, FDT gives good approximate solutions, better than the best current competitor (Christofides' algorithm).
+
+\item A stronger theoretical result on integrality gap that can be potentially employed to obtain improved upper bounds on the integrality gap of bounded covering problems.  
+\end{itemize}
+
+\iffalse{
 Finally we give a stronger characterization of integrality gap than that in Theorem \ref{CV} for bounded covering problems.
@@
 Notice that Theorem \ref{CV} requires the certificate convex combination to be ``cheap" on every single variable.
-
-\subsection{Notation and Preliminaries}
+\subsection{Notations}
+For vectors $x,y\in \mathbb{R}_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$.
+For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$.
+Let $\textbf{1}$ be the vector of all ones of a suitable dimension.
+For a set $S$ of vectors in $\mathbb{R}_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.
+}\fi

### 2019-10-11 2019 Journal/2ECFDT.tex
Add files via upload

--- 2018-11-21 IPCO format/2ECFDT.tex
@@
 
-In Section \ref{binaryfdt} our focus was on binary MIPs.
-In this section, in an attempt to extend FDT to 0,1,2 problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem.
+In Section \ref{binaryfdt} our focus was on binary MILPs.
+In this section, in an attempt to extend FDT to \{0,1,2\} problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem.
 Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2.
-In the 2EC problem, we are given non-negative costs on the edge of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$.
+In the 2EC problem, we are given non-negative costs on the edges of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$.
 Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take an edge at most 2 times.
@@
 We want to prove Theorem \ref{FDT2EC}.
+\FDTEC*
 We do not know the exact value for $g_{\EC}$, but we know $\frac{6}{5} \leq g_{\EC} \leq \frac{3}{2}$ \cite{carr-ravi,Wolsey1980}.
-Also, we need to remark that polyhedral version of Christofides' algorithm provides a $\frac{3}{2}$-approximation for 2EC, i.e.
+Also, we need to remark that the polyhedral version of Christofides' algorithm provides a $\frac{3}{2}$-approximation for 2EC, i.e.
 we already have an algorithm with $C\leq \frac{3}{2}$.
-However, we showed in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$ for fundamental extreme points with 10 vertices.
+However, we showed in Section \ref{experiment} that in practice the constant $C$ for the FDT algorithm for 2EC is much better than $\frac{3}{2}$ for FEPs of order 10.
 
@@
 		&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq 2\lambda_j\; &\mbox{ for $j=0,1,2$}\label{bound2ec}\\
-		&\;{\color{white}{\text{s.t.}} }\quad x^j_e = j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
-		&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
+		&\;{\color{white}{\text{s.t.}} }\quad x^j_e =j\cdot \lambda_j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
+		&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq \lambda_j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
 		&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1+x^2 \leq x\label{packing2ec}\\
@@
 add two copies of $f$ to $F_i$.
-If there is an edge $h\in P_f$ with $\chi^{F'_i}_h = 1$, let $\chi^{F_i}_f=1$, i.e.
+If there are at least one edge $h\in P_f$ with $\chi^{F'_i}_h= 1$, let $\chi^{F_i}_f=1$, i.e.
 add one copy of $f$ to $F_i$.
-If for all edge $h\in P_f$, we have $\chi^{F'_i}_h=2$, then let $\chi^{F_i}_f=2$.
+If for all edges $h\in P_f$, we have $\chi^{F'_i}_h=2$, then let $\chi^{F_i}_f=2$.
 For $f\in E$ with $x_f<1$ we have
@@
 			&\leq \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
-			&= \frac{\sum_{h\in P_f} g_{\EC}x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
-			&= \frac{\ceil{\frac{2}{\epsilon}}}{\ceil{\frac{2}{\epsilon}}-1}g_{\EC}x_f
+			&= \frac{\sum_{h\in P_f} g_{\EC}x_f}{\ceil{\frac{2}{\epsilon}}-1}\\
+			&= \frac{\ceil{\frac{2}{\epsilon}}}{\ceil{\frac{2}{\epsilon}}-1}g_{\EC}x_f.
 		\end{align*}
-		Therefore, we have 
+		Therefore, since $\frac{\ceil{\frac{2}{\epsilon}-1}}{\ceil{\frac{2}{\epsilon}}}\geq 1$, we have 
 		\begin{equation}
-		x' \geq \sum_{i\in [k]: \chi^{F_i}_e=1}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}+\sum_{i\in [k]: \chi^{F_i}_e=2}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}.
+		x \geq\sum_{i\in [k]: \chi^{F_i}_e=0}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}+ \sum_{i\in [k]: \chi^{F_i}_e=1}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}+\sum_{i\in [k]: \chi^{F_i}_e=2}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\chi^{F_i}.
 		\end{equation}
@@
 Notice that $\sum_{j=0,1,2}\theta_j = \frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}$.
-By assumption, we have $\frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\leq  \frac{1}{g_{\EC}}-\epsilon$.
-However, this means $2\leq 1$ which is a contradiction.
+By assumption, we have $\frac{\ceil{\frac{2}{\epsilon}}-1}{g_{\EC}\ceil{\frac{2}{\epsilon}}}\leq  \frac{1}{g_{\EC}}-\epsilon$, which is a contradiction.
 	\end{proof}
-	This concludes the proof.}\fi \end{proof}
-
+	This concludes the proof. \end{proof}
 In contrast to FDT for binary MIPs where we round up the fractional variables that are already branched on at each level, in FDT for 2EC we keep all coordinates as they are and perform a rounding procedure at the end.
@@
 \end{lemma}
-The proof is similar to Lemma \ref{prune}, but we need to use property (i) in Lemma \ref{LPC2EC} to prove that (a) also holds.
-\iffalse{
+The proof is similar to Lemma \ref{prune}, but we need to use property (v) in Lemma \ref{LPC2EC} to prove that (a) also holds.
 \begin{proof}
-	We proceed by induction on the $i$.
+	We proceed by induction on $i$.
 Define $L_0=\{(x^*,1)\}$.
@@
 
-	If $|L'|\geq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
-\end{proof}	}\fi
+	Finally, if $|L'|\leq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
+\end{proof}
 

### 2019-10-11 2019 Journal/binaryFDT.tex
Add files via upload

--- 2019-03-22 Journal Version/binaryFDT.tex
@@
 Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively.
-Assume $S(I),P(I)\in [0,1]^n\times \mathbb{R}^p$.
+Assume $S(I)\subseteq \{0,1\}^n\times \mathbb{R}^p$ and $P(I)\subseteq [0,1]^n\times \mathbb{R}^p$.
 For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section.
@@
 \begin{lemma}\label{domlemma}
-	Given $(x,y)\in \dom(P)$, there is an algorithm (the DomToIP algorithm) that finds $(\bar{x},\bar{y})\in S$ in polynomial time, such that $\bar{x}\leq x$.\end{lemma}
+	Given $(\tilde{x},\tilde{y})\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$, there is an algorithm (the DomToIP algorithm) that finds $(\bar{x},\bar{y})\in S$ in polynomial time, such that $\bar{x}\leq \tilde{x}$.\end{lemma}
 
@@
 The above procedure suggests how to find $(x^{(\ell+1)},y^{(\ell+1)})$ from $(x^{(\ell)},y^{(\ell)})$.
-The Dom2IP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$.
+The DomToIP algorithm initializes with $(x^{(0)},y^{(0)})=(\tilde{x},\tilde{y})$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$.
 
@@
 \begin{algorithm}[H]
-	\KwIn{$(x,y)\in \dom(S)$}
-	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
-	$x^{(0)}\leftarrow x$\\
+	\KwIn{$(\tilde{x},\tilde{y})\in \dom(P)$, $\tilde{x}\in \{0,1\}^n$ }
+	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq \tilde{x}$}
+	$x^{(0)}\leftarrow \tilde{x}$\\
 	\For{$\ell = 0$ \textbf{to} $t-1$}{
@@
 We prove that indeed $(x^{(t)},y^{(t)})\in S$.
-First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomtoIP the $\DOMtoS(x^{\ell})$ is feasible.
+First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomToIP the $\DOMtoS(x^{(\ell)})$ is feasible.
 We show something stronger.
@@
 So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$.
-Hence, $z^i\leq x^{(0)}$ for $i=1,\ldots,k$.
+Hence, $\tilde{z}^i\leq x^{(0)}$ for $i=1,\ldots,k$.
 Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.
@@
 Also, $(z^*,w^*)\in P$.
-By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$ .
-We have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}$
+By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$.
+We have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}$.
 	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$.
-Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$.
+This implies $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$.
 Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$.
@@
 Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
-Consider iteration $j$ of the Dom2IP algorithm.
+Consider iteration $j$ of the DomToIP algorithm.
 Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.
@@
 Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$.
-If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$.
-If $x^{(t)} =1$, it must be the case that $z_t > 0$.
+If $x^{(t)}_t = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$.
+If $x^{(t)}_t =1$, it must be the case that $z_t > 0$.
 By the argument above there is a point $(z',w')\in \IP^{(t-1)}$.
 We show that $x^{(t)} = z'$.
-For $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
-We just need to show that $z'_j = 1$.
-Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.
+For $j=1,\ldots,t-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$.
+We just need to show that $z'_t = 1$.
+Assume $z'_t	 = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution.
 This concludes the proof of Lemma \ref{domlemma}.
@@
 By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $(\tilde{x}^i,\tilde{y}^i)\in S$ for $i=1,\ldots,k$ such that
-		$\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$.
+		$\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$. So
 
@@
 		x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
-		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}
+		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}.
 		\end{equation}
@@
 For $i=0,1$, for $j=1,\ldots,\ell-1$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,t$ let $\hat{x}^i_j = \bar{x}^i_j$.
+
 	 We now show that $(\hat{x}^0,\bar{y}^0)$, $(\hat{x}^1,\bar{y}^1)$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions.
@@
 				Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
-				$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\gamma_1]\}$\\			
+				$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\lambda\cdot\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\lambda\cdot\gamma_1]\}$\\			
 			}

### 2019-10-11 2019 Journal/introduction.tex
Barely started with an edit and a few comments in the introduction.

--- 2019-10-11 introduction.tex
@@
 Mixed-integer linear programming (MILP), the optimization of a linear objective function subject to linear and integrality constraints, models many practical optimization problems including scheduling, logistics and resource allocation.
-The set of feasible points for a MILP is the set
+The set of feasible points for a MILP with $n$ integer variables and $p$ continuous variables is the set
 \begin{equation}
@@
 
-Let $I=(A,G,b)$ be the feasible set of a specific instance.
+Let $I=(A,G,b)$ be the feasible set \cindy{Should this be ``input?'' The feasible set is a set of ordered pairs $(x,y)$.} of a specific instance.
 Then $S(I)$ and $P(I)$ denote $S(A,G,b)$ and $P(A,G,b)$, respectively.
 Given a linear objective function $c$, a Mixed-Integer-Linear Program (MILP) is $\min \;\{cx:\; (x,y) \in S(I)\}$.
-It is  NP-hard even to determine if an MILP instance has a feasible solution~\cite{GJ79}.
+\cindy{Can't the objective function depend on the continuous variables too?
+Sometimes the continuous variables are helper variables for computing the objective.
+If you are only considering a restricted set of MIPs, then that has to be stated explicitly.
+This reads as though this is the general definition.} It is  NP-hard even to determine if an MILP instance has a feasible solution~\cite{GJ79}.
 However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or near-optimal with provable bound) to many specific instances of NP-hard combinatorial optimization problems.
@@
 Relaxing the integrality constraints gives the polynomial-time-solvable linear-programming relaxation: $\min \;\{cx:\;(x,y)\in P(I) \}$.
-The optimal value of this linear program (LP), denoted $z_{LP}(I,c)$, is a lower bound on the optimal value for the MILP, denoted $z_{IP}(I,c)$.
+\cindy{If we allow the orginal continuous variables to contribute to the objective function, this has to change too.} The optimal value of this linear program (LP), denoted $z_{LP}(I,c)$, is a lower bound on the optimal value for the MILP, denoted $z_{IP}(I,c)$.
 The solution can also provide some useful global structure, even though the fractional values are not directly meaningful.

### 2020-05-15 FDT2020/FDT.tex
2020 commit

\documentclass[11pt,notitlepage]{article}

\usepackage{thumbpdf, amssymb, amsmath, amsthm, microtype, array,
graphicx, verbatim, listings, color, fancybox}
\usepackage[pdftex]{hyperref}
\usepackage{mathtools}
\usepackage{amsmath, nccmath}
\usepackage{booktabs}
\usepackage{glossaries}

\usepackage{setspace}
\usepackage{acro}
\usepackage{url}
\usepackage[linesnumbered,ruled]{algorithm2e}
\usepackage{subcaption}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{thmtools}
\usepackage{bbm}
\usepackage{pgf,tikz}
\usetikzlibrary{arrows}
\pagestyle{plain}
\usepackage[margin=1.25in]{geometry}
\usepackage{multicol,multirow}

\usepackage{mathrsfs}

\usepackage{epigraph}
\usepackage{thm-restate}
\usepackage{cleveref}

\newcommand{\ee}{e'}

\newcommand{\oc}{\mathrm{oc}}
\newcommand{\mcc}{\mathcal{C}}
\newcommand{\NP}{\mathrm{NP}}
\newcommand{\Pp}{\mathrm{P}}
\newcommand{\UGC}{\mathrm{UGC}}
\newcommand{\W}{\mathrm{W}}	
\newcommand{\FPT}{\mathrm{FPT}}
\newcommand{\opt}{\mathrm{OPT}}
\newcommand\floor[1]{\lfloor#1\rfloor}
\newcommand\ceil[1]{\lceil#1\rceil}
\newcommand{\FF}{\mathbb{F}}
\newcommand{\AF}{\mathbb{A}}
\newcommand{\BF}{\mathbb{A}}
\newcommand{\CF}{\mathbb{C}}
\newcommand{\EC}{\mathrm{2EC}}
\newcommand{\HK}{\mathrm{LP}}
\newcommand{\con}{\mathrm{Connector}}
\newcommand{\cov}{\mathrm{cov}}
\newcommand{\point}{\mathrm{end}}

\newcommand{\gap}{\alpha^{\HK}_{\EC}}
\newcommand{\Lu}{\mathcal{L}_\ell} 
\newcommand{\Rv}{\mathcal{R}_\ell}

\newcommand{\Lup}{\mathcal{L}_{\ell'}} 
\newcommand{\Rvp}{\mathcal{R}_{\ell'}}

\newcommand{\Ex}{\mathop{\mathbb{E}}}

\setlength{\tabcolsep}{0.5em} % for the horizontal padding
{\renewcommand{\arraystretch}{1.3}% for the vertical padding

\declaretheorem[name=Theorem]{thm}
\declaretheoremstyle[style=claim,qed=$\Diamond$]{claim}
\declaretheoremstyle[style=plain,qed=$\square$]{theorem}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}[thm]{Corollary}
\newtheorem{lemma}[thm]{Lemma}
\newtheorem{conjecture}{Conjecture}
\newtheorem{problem}{Open Problem}
\newtheorem{fact}[thm]{Fact}
\newtheorem{observation}[thm]{Observation}
\newtheorem{proposition}[thm]{Proposition}
\newtheorem{definition}[thm]{Definition}
\newtheorem{claim}{Claim}
\newtheorem*{notation}{Notation}
\newtheorem*{remark}{Remark}
\newtheorem{example}[thm]{Example}%[section]

%%%%%%%%%%%%%

%%%%%%%%%%%%
\DeclareMathOperator{\chord}{chord}
\DeclareMathOperator{\spp}{supp}
\DeclareMathOperator{\CC}{CC}
\DeclareMathOperator{\degree}{deg}
\DeclareMathOperator{\join}{-\;JOIN}
\DeclareMathOperator{\oddcut}{ODD-CUT}
\DeclareMathOperator{\cover}{COVER}
\DeclareMathOperator{\lp}{LP}

\DeclareMathOperator{\st}{ST}
\DeclareMathOperator{\connector}{SS}
\DeclareMathOperator{\LP}{LP}
\DeclareMathOperator{\IP}{IP}
\DeclareMathOperator{\dom}{\mathcal{D}}
\DeclareMathOperator{\conv}{conv}
\DeclareMathOperator{\subt}{{SEP}}
\DeclareMathOperator{\subtour}{{Subtour}}
\DeclareMathOperator{\hamil}{{{Hamilton}}}
\DeclareMathOperator{\tsp}{{{TSP}}}
\DeclareMathOperator{\graphtsp}{{{Graph-TSP}}}
\DeclareMathOperator{\nwtsp}{{{NW-TSP}}}
\DeclareMathOperator{\2ec}{{{2EC}}}
\DeclareMathOperator{\ecs}{{{2ECS}}}
\DeclareMathOperator{\DOMtoS}{{{DomToIP}}}
\DeclareMathOperator{\LPC}{{{LPC}}}
\DeclareMathOperator{\prun}{{{Pruning}}}

\newcommand{\vtree}{\mathrm{\textsc{-tree}}}

\newcommand{\TT}{\mathcal{T}}
\newcommand{\JJ}{\mathcal{J}}
\DeclareMathOperator{\ecss}{{{S2ECS}}}

\DeclareMathOperator{\tap}{{{TAP}}}
\DeclareMathOperator{\cut}{{{CUT}}}
\DeclareMathOperator{\permat}{{{PM}}}
\DeclareMathOperator{\nwec}{{{NW-2ECM}}}
\DeclareMathOperator{\nwecs}{{{NW-2ECS}}}
\newenvironment{cproof}
{\begin{proof}
 [Proof.]
 \vspace{-1.5\parsep}%-3.2\parsep} %%%For use with US letter
}
{\renewcommand{\qed}{\hfill $\Diamond$} \end{proof}}

\onehalfspacing
\begin{document}{\bibliographystyle{alpha}}

\begin{abstract}

\end{abstract}
\clearpage

\input{Introduction}
\input{main section}

\addcontentsline{toc}{chapter}{Bibliography}
\bibliographystyle{abbrv}
\bibliography{haddadan-ref}

\end{document}

\input{Beyond4}

### 2020-05-15 FDT2020/Introduction.tex
2020 commit

\nocite{IPbook}
\section{Introduction}\label{chapter:intro}

In combinatorial optimization the aim is to find the optimal solution in a discrete and
usually finite yet large set of solutions. For many specific combinatorial optimization problems such a solution can be found efficiently. For many others, finding optimal or in many cases near optimal solutions is NP-hard. A common approach to deal with such problems is relaxing the discrete solution set into a continuous set, where the optimization problem becomes tractable. Obtaining feasible solutions by means of such a relaxation requires an additional step of rounding the potentially fractional solution of the continuous relaxation into integer solutions.

In this paper, our focus is on linear relaxation of combinatorial
optimization problems. Combinatorial optimization was pioneered by Edmonds even before efficient algorithms for solving linear programming problems where introduced by Khachiyan \cite{Khachiyan} and later by Karmarkar \cite{Karmarkar1984}. For problems such as the \textsc{Minimum Cost Spanning Tree Problem} there are linear programming relaxations whose basic feasible solutions coincide with  integral solutions, i.e. spanning trees. For other problems the value of the linear programming relaxation provides a bound (lower bound for a minimization problem and upper bound for a maximization problem) on the optimal solution. A common and successful approach is to round these (potentially) fractional solutions into integer solutions for the combinatorial optimization problem at hand. The Integrality gap of a linear relaxation of an integer programming problem is the worst case ratio between the objective values of the discrete problem and the continuous problem. Equivalently, the integrality gap of the linear programming relaxation is a limit to the rounding approach: rounding a fractional solution into an integer solution incurs
a multiplicative cost proportional to the integrality gap. In this dissertation we study integrality gaps for different combinatorial optimization problems and introduce new rounding algorithms that imply bounds on their respective integrality gaps.

\section{Integrality Gap}
\iffalse{

Let $S$ denote the set of feasible solutions to a combinatorial optimization problem. For instance, for many problems in network optimization, set $S$ is a subset of $ \{0,1\}^n$ where each coordinate of a point in $S$ indicates the absence or presence of the corresponding edge in a solution, and $n$ is the number of edges in the network. Suppose set $S$ can be described as $S=\{x\in \mathbb{Z}^n: Ax\geq b, x\geq 0 \}$ for some $A\in \mathbb{R}^{m\times n}$ and $b\in \mathbb{R}^m$. (Pure) Integer Programming (IP) asks for $\min_{x\in S}cx$ for some $c\in \mathbb{R}^n$. Integer programming is NP-hard and in fact, it is even NP-complete to decide whether set $S$ is empty or not \cite{GareyJohnson}. The convex hull of $S$ denoted by $\conv(S)$ is the minimal convex set containing $S$ and can be formulated as follows.
\begin{equation*}
\conv(S) =\{\sum_{i=1}^{k} \lambda_i x^i: x^i \in S \text{ for } i =1,\ldots,k,\; \lambda_i \geq 0 \text{ for } i = 1,\ldots,k \text{, and } \sum_{i=1}^{k}\lambda_i = 1\}.
\end{equation*}

A fundamental fact in polyhedral theory is that $\min_{c\in S} S = \min_{c\in S} \conv(S)$. Notice that $\conv(S)$ is a polyhedron and optimizing a linear function subject to the points lying in a polyhedron can be done in polynomial time in the number of variables and constraints in the description of $\conv(S)$. Such a description, however, might have exponential size in the description of set $S$.

A natural way to bound the solution to the integer program $\min_{x\in S} cx$ is to relax the integrality constraints. Let $L= \{x\in \mathbb{R}^n: Ax\geq b, x\geq 0\}$. Contrary to integer programming, the optimal solution to $\min_{x\in L}cx$ can be efficiently found. Set $L$ is called the linear programming relaxation of $S$. Since we relaxed the integrality requirement on $x$, we have	
\begin{equation}\label{lp-lower-bound}
\min_{x\in L} cx \leq \min_{x\in S}cx.
\end{equation}
For most relevant applications and for the entirety of this dissertation we assume $c$ is a non-negative vector and  $c\neq 0$, i.e. $c$ has a positive value in at least one coordinate. Following this assumption we can rewrite (\ref{lp-lower-bound}) as 
\begin{equation}
\frac{\min_{x\in S}cx}{\min_{x\in L} cx}\geq 1.
\end{equation}
Since we are concerned with the worst-case analysis, we consider

\vspace*{5pt}
\noindent\fbox{%
	\parbox{\textwidth}{%
		\vspace*{3pt}
		\begin{equation}\label{eq:IG}
		g=\max_{c\in \mathbb{R}^n_{\geq 0}}\frac{\min_{x\in S}cx}{\min_{x\in L} cx}.
		\end{equation}
	}%
}
\vspace*{3pt}

If $g=1$, we say that the linear programming formulation is a perfect formulation. Otherwise we have $g>1$. In this case, we cannot hope to achieve an integer solution with cost lower than $(g-\epsilon)\cdot (\min_{x\in L}cx)$, for any constant $\epsilon>0$. Thus, a lower bound on $g$ provide a certificate for impossibility of approximation via the linear relaxation for which the gap is $g$. On the other hand, an upper bound of $\alpha$ for $g$ is often accompanied with an $\alpha$-approximation algorithm. This is not always the case, as we will later discuss in details.

We refer to $g$ as the integrality gap of the linear relaxation. For a polyhedron $P\in \mathbb{R}^n$ let the \textit{dominant of $P$} be $\{x\in \mathbb{R}^n: \exists y \in P: x\geq y\}$ and denote it by $\dom(P)$. Goemans \cite{goemansblocking} gave a characterization of integrality gap based on convex combinations when $\conv(S)=\mathcal{D}(\conv(S))$. Carr and Vempala \cite{Carr2004} generalized this characterization.

\vspace*{5pt}
\noindent\fbox{%
	\parbox{\textwidth}{%
		\begin{thm}[\cite{Carr2004}]\label{CV}
			Let $S=\{x\in \mathbb{Z}^n: Ax\geq 0,x\geq 0\}$, and $L= \{x\in \mathbb{R}^n: Ax\geq 0, x\geq 0\}$ be the linear relaxation of $S$. Then
			\begin{equation*}
			\max_{c\in \mathbb{R}^n_{\geq 0}}\frac{\min_{x\in S}cx}{\min_{x\in L} cx}= \min \{\alpha: \alpha\cdot x \in \mathcal{D}(\conv(S)) \text{ for all $x\in L$}\}.
			\end{equation*}
		\end{thm}
	}%
}
\vspace*{5pt}

A polynomial time algorithm for proving an upper bound on integrality gap is called an LP-based approximation algorithm. For many well studied problems, we still do not know the exact integrality gap and the gap between the best known lower bound and the upper bound on the integrality gap are open. In some cases, there are known upper bounds, yet there is no known approximation algorithm, meaning that the proofs do not yield polynomial time algorithms.
}\fi

In this paper we focus on finding solutions to general Integer Linear Programs (IP). Integer Programming (and more generally Mixed Integer Linear Programming) can be used to model many practical optimization problems including scheduling, logistics and resource allocation. Recall that the set of feasible points for a pure IP (henceforth IP) is the set
\begin{equation}
S(A,b)= \{x\in \mathbb{Z}^{n}\;:\; Ax\geq b\}  \label{S}.
\end{equation}
If we drop the integrality constraints, we have the linear relaxation of set $S(A,b)$,
\begin{equation}
P(A,b) = \{x\in \mathbb{R}^{n}\;:\; Ax\geq b\}. \label{P}
\end{equation}

Let $I=(A,b)$ denote an instance. Then $S(I)$ and $P(I)$ denote $S(A,b)$ and $P(A,b)$, respectively. Given a linear objective function $c$, recall that an IP is $\min \;\{cx:\; x \in S(I)\}$. It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}. However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or near-optimal solution with provable bound) to many specific instances of NP-hard combinatorial optimization problems.

Relaxing the integrality constraints gives the polynomial-time-solvable linear-programming relaxation: $\min \;\{cx:\;x\in P(I) \}$.  The optimal value of this linear program (LP), denoted $z_{\lp}(I,c)$, is a lower bound on the optimal value for the IP, denoted $z_{\IP}(I,c)$. The solutions can also provide some useful global structure, even though the fractional values might not directly meaningful.

Many researchers (see \cite{davids,vazirani}) have developed polynomial-time LP-based approximation algorithms that find solutions for special classes of IPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$. The approximation factor $C$ can be a constant or depend on the input parameters of the IP, e.g. $O(\log(n))$ where $n$ is the number of variables in the formulation of the IP (the dimension of the problem). However, for many combinatorial optimization problems there is a limit to such techniques based on LP relaxations, represented  by the {integrality gap} of the IP formulation. Recall that integrality gap $g(I)$ for instance $I$ is defined to be $g(I)= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$. An example of instance specific integrality gap is the integrality gap of the subtour elimination relaxation for the 2-edge-connected spanning multigraph problem on $n$ vertices. The instance is the complete graph on $n$ vertices. Alexander et al. \cite{alexander2006integrality} showed the instance specific integrality gap of the subtour elimination relaxation for the 2-edge-connected multigraph problem for instances of the problem with $n= 10$ is at most $\frac{7}{6}$.

This value depends on the constraints in (\ref{S}).  We cannot hope to find solutions for the IP with objective values better than $g(I)\cdot z_{LP}(I,c)$.

More generally we can define the integrality gap for a class of instances $\mathcal{I}$ as follows.% In this case, the integrality gap for problem $\mathcal{I}$ is
\begin{equation}\label{gapproblem}
g(\mathcal{I}) = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}.
\end{equation}
For example, the aforementioned integrality gap of the subtour elimination relaxation for the 2-edge-connected multigraph problem is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}. Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation.

Our methods apply theory connecting integrality gaps to sets of feasible solutions. Instances $I$ with  $g(I)=1$ has $P(I)=\conv(S(I))$, the convex hull of the lattice of feasible points. In this case, $P(I)$ is an \textit{integral} polyhedron. The spanning tree polytope of graph $G$, $\st(G)$, and the perfect-matching polytope of graph $G$, $\permat(G)$, have this property (\cite{Edmonds2003,edmondsPM}). For such problems there is an algorithm to express vector $x\in P(I)$ as a convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.
\begin{proposition}\label{cara}
	If $g(I)=1$, then for $x\in P(I)$ there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in S(I)$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$. Moreover, we can find such a convex combination in polynomial time.
\end{proposition}

An equivalent way of describing Proposition \ref{cara} is the following Theorem of Carr and Vempala \cite{Carr2004}.

\begin{thm}[Carr, Vempala \cite{Carr2004}] \label{CV2}
	Let $x\in P(I)$. There exists $\theta \in [0,1]^k$ where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in \dom(S(I))$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ if and only if $g(I) \leq C$.
\end{thm}
Recall that $\dom(P(I))$ is the set of points $x'$ such that there exists a point $x\in P$ with $x'\geq x$, also known as the dominant of $P(I)$. For covering problems the polyhedron is essentially the same as its dominant, but this is not true in general. While there is an exact algorithm for problems with gap $1$ as stated in Proposition \ref{cara}, Theorem~\ref{CV2} is existential, with no construction.
%In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
%This points to an interesting open question. 
% We show later, for $I$ with $g(I)<\infty$, the notation of dominant is in fact useful.
\iffalse

\begin{question*}\label{question1}
	Assume reasonable complexity assumptions (such as UGC or $\textrm{P}\neq \textrm{NP}$). Given instance $I$ with $1<g(I)<\infty$ and $(x,y)\in P(I)$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in \dom(\conv(S(I)))$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g(I)x$ in polynomial time?
\end{question*}

This seems to be a very hard question. A more specific question is of more interest.

\begin{question}\label{question2}
	Assume reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g({\mathcal{I}})<\infty$, and $(x,y)\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $(\tilde{x}^i,\tilde{y}^i)\in S(I)$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq g(\mathcal{I})x$ in polynomial time?
\end{question}
Although Question \ref{question2} is wide open, for some problems there are polynomial time algorithms closing the gap. For example, for generalized Steiner forest problem \cite{jain} gave an LP-based 2-approximation algorithm. The gap for this problem is also lower bounded by 2. Same holds for the set covering problem \cite{randomizedrounding}. In fact, for set cover the approximation algorithm achieving the same factor as the integrality gap lower bound, is a \textit{randomized rounding} algorithm. Raghavan and Thompson \cite{randomizedrounding} showed that this technique achieves provably good approximation for many combinatorial optimization problems.

If we relax Question \ref{question1} (resp. Question \ref{question2}), but multiplying $g(I)$ (resp. $g(\mathcal{I})$) by a factor $C$, they are still very interesting, since they will provide upper bounds on the integrality gap of the instance (resp. the problem). The results in this paper serve this purpose.
\fi
To study integrality gaps, we wish to find such a solution constructively: assuming reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g(\mathcal{I})<\infty$, and $x\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in S(I)$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ in polynomial time? We wish to find the smallest factor $C$ as possible.

\section{Contributions of this paper}

We give a general approximation framework for solving binary IPs.  Consider the set of point described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume in addition that $S(I),P(I)\subseteq [0,1]^n$. For a vector $x\in \mathbb{R}_{\geq 0}^n$ such that $x\in P(I)$, let $\spp(x)= \{i \in [n]: x_i \neq 0\}$. For an integer $\beta$ let $\{\beta\}^n$ be the vector $y\in \mathbb{R}^n$ with $y_i=\beta$ for $i\in [n]$.

We introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which is a polynomial-time algorithm that given a point $x\in P(I)$ produces a convex combination of feasible points in $S(I)$ that are dominated by a ``factor" $C$ of $x$ in the coordinates corresponding to $x$. If $C = g(I)$, it would be optimal. However we can only guarantee a factor of $g(I)^{|\spp(x)|}$. FDT relies on iteratively solving linear programs that are about the same size as the description of $P(I)$.

\begin{restatable}{thm}{binaryFDT}
	\label{binaryFDT}
	Assume $1\leq g(I) 	<\infty$. 	
	The Fractional Decomposition Tree (FDT) algorithm, given $x^*\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $z^1,\ldots,z^k \in S(I)$ such that $k\leq |\spp(x^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq \min(Cx^*,\{1\}^{n})$, and $\sum_{i=1}^{k}\lambda_i = 1$. Moreover, $C\leq g(I)^{|\spp(x^*)|}$.
\end{restatable}

A subroutine of the FDT, called the DomToIP algorithm, finds feasible solutions to any IP with finite gap. This can be of independent interest, especially in proving that a model has unbounded gap.
\begin{restatable}{thm}{DomToIP}
	\label{domtoIP}
	Assume $1\leq g(I) < \infty$. The DomToIP algorithm finds $\hat{x}\in S(I)$ in polynomial time.
\end{restatable}

For a generic IP instance $I$ it is NP-hard to even decide if the set of feasible solutions $S(I)$ is empty or not. There are a number of heuristics for this purpose, such as the feasibility pump algorithm \cite{fp1,fp2}. These heuristics are often very effective and fast in practice, however, they can sometimes fail to find a feasible solution. Moreover, these heuristics do not provide any bounds on the quality of the solution they find.

Here is how the FDT algorithm works in a high level: in iteration $i$ the algorithm maintains a convex combination of  vectors in $\mathcal{D}(L(I))$ that have a 0 or 1 value for coordinates indexed $0,\ldots,i-1$. Let $y$ be a vector in the convex combination in iteration $i$ of the algorithm. We solve a linear programming problem that gives us $\theta\in [0,1]$ and $y^0,y^1\in \mathcal{D}(L(I))$ such that $g(I) y\geq \theta_1y^0 + (1-\theta) y^1$ and $y^0_i=0$ and $y^1_i=1$. We then replace $y$ in the convex combination with $\frac{\theta}{g(I)}y^0 +\frac{1-\theta}{g(I)}y^1$. Repeating this for every vector in the convex combination from previous iteration yields a convex combination  of points that is ``more'' integral. If in any iteration there are too many points in the convex combination we solve a linear programming problem that ``prunes'' the convex combination. At the end we find a convex combination of integer solutions $\mathcal{D}(L(I))$. For each such solution $z$ we invoke the DomToIP algorithm (see Section \ref{domTOIP}) to find $z'\in S(I)$ where $z'\leq z$.

One can extend the FDT algorithm for binary IPs into covering $\{0,1,2\}$ IPs by losing a factor $2^{|\spp(x)|}$ on top of the loss for FDT. In order to eradicate this extra factor, we need to treat the coordinate $i$ with $x_i=1$ differently. We focus on the \textsc{2-edge-connected multigraph graph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^{E}_{\geq 0}$ find a 2-edge-connected multi-subgraph (henceforth a multigraph) of $G$ with minimum cost. The natural linear programming relaxation for this problem is 
\begin{equation}
\min \{cx \; : \; x(\delta(U))\geq 2 \; \text{ for }\emptyset \subset U \subset V, \; x\in [0,2]^E\}
\end{equation}
We denote the feasible region of this LP by $\subtour(G)$. Let $\2ec(G)$ be the convex hull of incidence vectors of 2-edge-connected multigraphs of graph $G$. Following the definition in (\ref{gapproblem}) have
\begin{equation}
g(\2ec) = \max_{c\geq 0 , G}\frac{\min_{x\in \2ec(G)} cx}{\min_{x\in \subtour(G)} cx}.
\end{equation}

\begin{restatable}{thm}{FDTEC}
	\label{FDT2EC}
	Let $G=(V,E)$ and $x$ be an extreme point of  $\subtour(G)$. The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq 2|V|-1$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq \min(Cx,\{2\}^n)$, and $\sum_{i=1}^{k}\lambda_i = 1$. Moreover, $C\leq g(\2ec)^{|E_x|}$.
\end{restatable}

\subsection{Experiments.} Although the bound guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are very large, we show that in practice, the algorithm works very well for network design problems described above. We show how one might use FDT to investigate the integrality gap for such well-studied problems.

\subsubsection{Minimum vertex cover problem}

TODO

\subsubsection{Tree augmentation problem}
In the \textsc{Tree Augmentation Problem (TAP)} we are given a  graph $G=(V,E)$, a tree $T$. We also have a cost vector $c\in \mathbb{R}^{E\setminus T}_{\geq 0}$. A subset $F$ of $E\setminus T$ is called a \textit{feasible augmentation} if $(V,T\cup F)$ is a 2-edge-connected graph. In TAP we seek the minimum cost feasible augmentation. The natural linear programming relaxation for TAP is 
\begin{equation}
\min \{cx\; : \; \sum_{\ell \in \cov(e)} x_{\ell} \geq 1 \text{ for } e\in T, \; x\in [0,1]^{E\setminus T}\}.
\end{equation}
where $\cov(e)$ is set of edges $\ell \in E\setminus T$ such that $e$ is in the unique cycle of $T\cup \{\ell\}$. We call the LP above the cut-LP. The integrality gap of the cut-LP is known to be between $\frac{3}{2}$ \cite{32gaptap} and $2$ \cite{FJ81}. We create random fractional extreme points of the cut-LP and round them using FDT. For the instances that we create the blow-up factor is always below $\frac{3}{2}$ providing an upper bound for such instances.

\subsubsection{2-edge-connected multigraph problem}
Known polyhedral structure makes it easier to study integrality gaps for such problems. We use the idea of fundamental extreme point \cite{carrravi,boydcarr,Carr2004} to create the ``hardest'' LP solutions to decompose.

There are fairly good bounds for the integrality gap for TSP or 2EC. Benoit and Boyd \cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices. Alexander et al. \cite{alexander2006integrality} used the same ideas to provide an upper bound of $\frac{7}{6}$ for $g(\2ec)$ on graphs with at most 10 vertices.

A \textit{Carr-Vempala point} $x$ is a fractional point in the subtour elimination relaxation where the fractional edges of $x$, edges $e$ with $0<x_e<1$, form a Hamiltonian cycle. For $\2ec$ we show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the Hamiltonian cycle formed by the fractional edges. For Carr-Vempala points we assume that 1-edges are replaced by long paths of 1-edges making these points into potentially harder to round instances.

### 2020-05-15 FDT2020/main section.tex
2020 commit

	\subsection{Notations}
	For vectors $x,y\in \mathbb{R}_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$. For $m\times n$ matrix $A$, let $A_j$ be the $j$-th row of $A$ and $A^j$ be the $j$-th column of $A$. For a set $S$ of vectors in $\mathbb{R}_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.

\section{Finding a Feasible Solution}\label{domTOIP}
Consider an instance $I=(A,b)$ of the IP formulation. Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume $S(I)\subseteq \{0,1\}^n$ and $P(I)\subseteq [0,1]^n$. For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section. Also, for both sections we assume $t=|\spp(x)|$. Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$.

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given $\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time, such that $\bar{x}\leq \tilde{x}$.\end{lemma}
Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: rounding up any fractional point in $P$ gives us a point in $\dom(P)$.

\subsection{Proof of Lemma \ref{domlemma}: The DomToIP Algorithm}

We start by introducing an algorithm that ``fixes" the variables iteratively, starting from from the first coordinate and ending at the $t$-th coordinate. Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$. Notice that we can set $x^{(0)}=\tilde{x}$. Now consider the following linear program. The variables of this linear program are the $z\in \mathbb{R}^n$ variables.
\begin{align}
\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
&\;\text{s.t.} \quad \;\;Az\geq b \\
&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
\end{align}

If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$. Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$. Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in [n]\setminus \{\ell+1\}$ (See Algorithm \ref{domtoIPalg}).

The above procedure suggests how to find $x^{(\ell+1)}$ from $x^{(\ell)}$. The DomToIP algorithm initializes with $x^{(0)}=\tilde{x}$ and  iteratively calls this procedure in order to obtain $x^{(t)}$.

\vspace*{10pt}
\begin{algorithm}[h]
	\KwIn{$\tilde{x}\in \dom(P)$, $\tilde{x}\in \{0,1\}^n$ }
	\KwOut{$x^{(t)} \in S$, $x^{(t)}\leq \tilde{x}$}
	$x^{(0)}\leftarrow \tilde{x}$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\caption{The DomToIP algorithm}
	\label{domtoIPalg}
\end{algorithm}
\vspace*{10pt}

We prove that indeed $x^{(t)}\in S$. First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomToIP that $\DOMtoS(x^{(\ell)})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
\begin{align*}
\LP^{(\ell)}&= \{z\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j\in [\ell]\}, \text{ and}\\
\IP^{(\ell)}&= \{z\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
\end{align*}
Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$. First notice that $\LP^{(0)}$ is clearly feasible since by definition $x^{(0)}\in \dom(P)$, meaning there exists $z\in P$ such that $z\leq x^{(0)}$. By Theorem \ref{CV2}, there exists $\tilde{z}^i\in S$ and $\theta_i\geq 0$ for $i\in [k]$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$. Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$. So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i\in [k]$ and $j\in [n]$ where $x^{(0)}_j=0$. Hence, $\tilde{z}^i\leq x^{(0)}$ for $i\in [k]$. Therefore $\tilde{z}^i\in \IP^{(0)}$ for $i\in [k]$, which implies $\IP^{(0)}\neq \emptyset$.

Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in [t-2]$. Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $z^*$.

We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $z^*\in \LP^{(\ell+1)}$. Also, $z^*\in P$. By Theorem \ref{CV2} there exists $\tilde{z}^i\in S$ and $\theta_i\geq 0$ for $i\in [k]$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$. We have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}$.
So for $j\in [n]$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i\in [k]$. This implies $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $z\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $z\in \IP^{(\ell+1)}$. If $z\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of the DomToIP algorithm. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $z$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $z\in \IP^{(\ell+1)}$.

Now for the second case, assume $z^*_{\ell+1} > 0$. We have $x^{(\ell+1)}_{\ell+1}=1$. Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e. $z_{\ell+1}=1$. This means that $z\in \IP^{(\ell+1)}$, and $\IP^{(\ell+1)} \neq \emptyset$.

Now consider $x^{(t)}$. Let $z$ be the optimal solution to $\LP^{(t-1)}$. If $x^{(t)}_t = 0$, we have $x^{(t)} = z$, which implies that $x^{(t)}\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $x^{(t)}\in S$. If $x^{(t)}_t =1$, it must be the case that $z_t > 0$. By the argument above there is a point $z'\in \IP^{(t-1)}$. We show that $x^{(t)} = z'$. For $j\in [t-1]$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$. We just need to show that $z'_t = 1$. Assume $z'_t	 = 0$ for contradiction, then $z'\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $z$ being the optimal solution. This concludes the proof of Lemma \ref{domlemma}.

\section{FDT on Binary IPs}
\label{binaryfdt}

Assume we are given a point $x^*\in P$. For instance, $x^*$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.  In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm. We also remark that if $g(I)=1$, then the algorithm will give an exact decomposition of any feasible solution.

The FDT algorithm grows a tree similar to the classic branch-and-bound search tree for integer programs. Each node represents a partially integral vector $\bar{x}$ in $\dom(P)$ together with a multiplier $\bar{\lambda}$. The solutions contained in the nodes of the tree become progressively more integral at each level. In each level of the tree, the algorithm maintain a conic combination of points with the properties mentioned above. Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$. In Lemma  \ref{domlemma} we saw how to turn these into points in $S$.

\paragraph{Branching on a node.}
We begin with the following lemmas that show how the FDT algorithm branches on a variable.
\begin{lemma}\label{LPClemma}
	Given $x'\in \dom(P)$ and $\ell\in [n]$ where $x'_{\ell}<1$, we can find in polynomial time vectors $\hat{x}^0,\hat{x}^1$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\gamma_0 + \gamma_1  \geq 1/g$, (ii) $\hat{x}^0$ and $\hat{x}^1$ are in  $ P$
	,(iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
\end{lemma}

\begin{proof}	
	Consider the following linear program which we denote by $\LPC(\ell,x')$. The variables of $\LPC(\ell,x')$ are $\gamma_0,\gamma_1$ and $x^0$ and $x^1$. 
	\begin{align}
	\LPC(\ell,x')\quad\quad& \max\quad \;\lambda_0+\lambda_1\\
	&\;\text{s.t.} \quad Ax^j \geq b\lambda_j & \mbox{ for $j=0,1$} \label{feasibility}\\
	&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq \lambda_j &\mbox{ for $j=0,1$}\label{bound}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0_\ell = 0,\; x^1_\ell =\lambda_1\label{branchcoordinate}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1 \leq x'\label{packing}\\
	&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1 \geq 0
	\end{align}

	Let $x^0,x^1$, and $\gamma_0,\gamma_1$ be an optimal solution solution to the LP above. Let $\hat{x}^0 = x^0/\gamma_0$, $\hat{x}^1=x^1/\gamma_1$. This choice satisfies  (ii), (iii), (iv). To show that (i) is also satisfied we prove the following claim.

	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1\geq 1/g$.
	\end{claim}
	\begin{cproof}
		We show that there is a feasible solution that achieves the objective value of $\frac{1}{g}$. By Theorem \ref{CV2} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $\tilde{x}^i\in S$ for $i\in[k]$ such that 
		$\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$. So

		\begin{equation}\label{splitting}
		x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}.
		\end{equation}
		For $j=0,1$, let $x^j = \sum_{i\in [k]:\tilde{x}^i_\ell=j} \frac{\theta_i}{g}\tilde{x}^i$. Also let $\lambda_0=\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g}$ and $\lambda_1 = \sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g}$. Note that $\lambda_0+\lambda_1 =1/g$. Constraint (\ref{packing}) is satisfied by Inequality (\ref{splitting}). Also, for $j=0,1$ we have
		\begin{equation}
		Ax^j= \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} A\tilde{x}^i  \geq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
		\end{equation}
		Hence, Constraints (\ref{feasibility}) holds. Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$. The rest of the constraints trivially hold. 
	\end{cproof}
	This concludes the proof of Lemma \ref{LPClemma}.	
\end{proof}

We now show if $x'$ in the statement of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
\begin{lemma}\label{round-up}
	Given $x'\in \dom(P)$ where $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ and $x'_{\ell}<1$ for some $\ell\geq 1$ we can find in polynomial time vectors $\hat{x}^0,\hat{x}^1$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) ${ 1}/{g}\leq \gamma_0 + \gamma_1  \leq 1$, (ii) $\hat{x}^0$ and $\hat{x}^1$ are in  $\dom( P)$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
	x'$,(v) $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j\in[\ell-1]$.
\end{lemma} 
\begin{proof}
	By Lemma \ref{LPClemma} we can find $\bar{x}^0$, $\bar{x}^1$, $\gamma_0$ and $\gamma_1$ that satisfy (i), (ii), (iii), and (iv). We define $\hat{x}^0$ and $\hat{x}^1$ as follows. For $i=0,1$, for $j\in[\ell-1]$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,t$ let $\hat{x}^i_j = \bar{x}^i_j$.

	We now show that $\hat{x}^0$, $\hat{x}^1$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions. Note that conditions (i), (ii), (iii), and (v) are trivially satisfied. Thus we only need to show (iv) holds. We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$. If $j=\ell,\ldots,t$, then this clearly holds. Hence, assume $j\leq \ell-1$. By the property of $x'$ we have $x'_j\in \{0,1\}$. If $x'_j= 0$, then by Constraint (\ref{packing}) we have $\bar{x}^0_j = \bar{x}^1_j=0$. Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds. Otherwise if $x'_j = 1$, then we have
	$\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.$ 
	Therefore (v) holds.
\end{proof}

\paragraph{Growing and Pruning FDT tree.} The FDT algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm. The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree. The points in the leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.

\begin{lemma}\label{prune}
	There is a polynomial time algorithm that produces sets $L_0,\ldots,L_t$ of pairs of $x\in \dom(P)$ together with multipliers $\lambda$ with the following properties for $i=0,\ldots,t$:
	(a) If $x\in L_i$, then $x_j \in \{0,1\}$ for $j\in [i]$, i.e. the first $i$ coordinates of a solution in level $i$ are integral, (b) $\sum_{[x,\lambda]\in L_i} \lambda\geq\frac{1}{g^i}$, (c) $\sum_{[x,\lambda]\in L_i}\lambda x \leq x^*$, (d) $|L_i|\leq t$.
\end{lemma}
\begin{proof}
	We prove this lemma using induction but one can clearly see how to turn this proof into a polynomial time algorithm. Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $x^*$ and multiplier 1. It is easy to check all the requirements in the lemma are satisfied for this choice.

	Suppose by induction that we have constructed sets $L_0,\ldots,L_i$. Let the solutions in $L_i$ be $x^j$ for $j\in [k]$ and $\lambda_j$ be their multipliers, respectively. For each $j\in[k]$ if $x^j_{i+1}=1$ we add the pair $(x^j,\lambda_j)$ to $L'$. Otherwise,	applying Lemma \ref{round-up} (setting $x'= x^j$ and $\ell = i+1$) we can find $x^{j0}$, $x^{j1}$, $\lambda^0_j$ and $\lambda^1_j$ with the properties (i) to (v) in Lemma \ref{round-up}. Add the pairs  $(x^{j0} ,\lambda_j\lambda^0_j)$ and  $(x^{j1} ,\lambda_j\lambda^1_j)$ to $L'$. It is easy to check that set $L'$ is a suitable candidate for $L_{i+1}$, i.e. set $L'$ satisfies (a), (b) and (c). However we can only ensure that $|L'|\leq 2k\leq 2t$, and might have $|L'|>t$. We call the following linear program $\prun(L')$. Let $L' = \{[x^1,\gamma_1],\ldots,[x^{|L'|},\gamma_{|L'|}]\}$. The variables of $\prun(L')$ are scalar variables $\theta_j$ for each node $j$ in $L'$.  
		\begin{equation}
		\prun(L')\quad\quad\quad \{\max \sum_{j=1}^{|L'|} \theta_j\;:\; \sum_{j=1}^{|L'|} \theta_j x^j_i\leq x^*_i \mbox{ for $i\in [t]$},\; \theta\geq 0 \}
		\end{equation}

		Notice that $\theta = \gamma$ is in fact a feasible solution to $\prun(L')$. Let $\theta^*$ be the optimal vertex solution to this LP. Since the problem is in $\mathbb{R}^{|L'|}$,  $\theta^*$ has to satisfy $|L'|$ linearly independent constraints at equality. However, there are only $t$ constraints of type $ \sum_{j=1}^{|L'|} \theta_j x^j_i\leq x^*_i$. Therefore, there are at most $t$ coordinates of $\theta^*_j$ that are non-zero. Set $L_{i+1}$ which consists of $x^j$ for $j=1,\ldots,|L'|$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma. Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$. Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{|L'|} \theta^*_j \geq \sum_{j=1}^{|L'|}\gamma_j \geq \frac{1}{g^{i+1}}$.

	\end{proof}

	\paragraph{From leaves of FDT to feasible solutions.}
	For the leaves of the FDT tree,  $L_t$, we have that every solution $x$ in $L_t$ has $x\in\{0,1\}^n$ and $x\in \dom(P)$. By applying Lemma \ref{domlemma} we can obtain a point $x'\in S$ such that $x'\leq x$. This concludes the description of the FDT algorithm and proves Theorem \ref{binaryFDT}. See Algorithm \ref{FDTFull} for a summary of the FDT algorithm.

	\vspace*{10pt}

	\begin{algorithm}[H]\label{FDTFull}
		\KwIn{$P= \{x\in \mathbb{R}^{n}: Ax\geq b\}$ and $S=\{x\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \mathbb{R}^n_+ }\frac{\min_{x\in S}cx}{\min_{x\in P}cx}$ is finite, $x^*\in P$}
		\KwOut{$z^i\in S$ and $\lambda_i\geq 0$ for $i\in[k]$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
		$L^0\leftarrow [x^*,1]$\\
		\For{$i=1$ \textbf{to} $t$}{
			$L'\leftarrow \emptyset$\\
			\For{$[x,\lambda] \in L^i$}{
				Apply Lemma \ref{round-up} to obtain $[\hat{x}^0,\gamma_0]$ and $[\hat{x}^1,\gamma_1]$\\
				$L' \leftarrow L' \cup \{[\hat{x}^0,\lambda\cdot\gamma_0]\} \cup \{[\hat{x}^1,\lambda\cdot\gamma_1]\}$\\			
			}
			Apply Lemma \ref{prune} to prune $L'$ to obtain $L^{i+1}$. 
		}
		\For{$[x,\lambda] \in L^t$}{
			Apply Algorithm \ref{domtoIPalg} to $x$ to obtain $z\in S$\\
			$F \leftarrow F \cup \{[z,\lambda]\}$
		}
		\textbf{return} $F$
		\caption{Fractional Decomposition Tree Algorithm}
	\end{algorithm}

\section{FDT for 2EC}\label{2EC}

In Section \ref{binaryfdt} our focus was on binary IPs. In this section, in an attempt to extend FDT to \{0,1,2\} problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem. Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2. Recall that in the 2EC, we are given non-negative costs on the edges of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$. The natural linear programming relaxation is $\min \{cx \; : \; x\in \subtour(G)\}$ where $\subtour(G) = \{x\in [0,2]^E: x(\delta(U))\geq 2 \mbox{ for } \emptyset \subset U \subset V\}$. Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take an edge at most 2 times, hence in this chapter (unlike in the previous chapters) we work with a bounded version of $\subtour(G)$.  Notice that $\dom(\subtour(G))\cap [0,2]^{E} = \subtour(G)$. Thus, we also assume a multigraph can contain at most 2 copies of any edge in the graph. We want to prove Theorem \ref{FDT2EC}.
\FDTEC*
We do not know the exact value for $g(\2ec)$, but we know $\frac{6}{5} \leq g(\2ec) \leq \frac{3}{2}$ \cite{alexander2006integrality,wolsey}. The FDT algorithm for 2EC is very similar to the one for binary IPs, but there are some differences as well. A natural thing to do is to have three branches for each node of the FDT tree, however, the branches that are equivalent to setting a variable to $1$, might need further decomposition. That is the main difficulty when dealing with $\{0,1,2\}$-IPs.

First, we need a branching lemma. Observe that  the following branching lemma is essentially a translation of Lemma \ref{LPClemma} for $\{0,1,2\}$ problems except for one additional clause.

\begin{restatable}{lemma}{2ECLPC}
	\label{LPC2EC}
	Given $x\in \subtour(G)$, and $e\in E$ we can find in polynomial time vectors $x^0,x^1$ and $x^2$ and scalars $\gamma_0,\gamma_1$, and $\gamma_2$ such that: (i) $\gamma_0 + \gamma_1 +\gamma_2 \geq { 1}/{g(\2ec)}$, (ii) $x^0,x^1,$ and $x^2$ are in  $ \subtour(G)$, (iii) $x^0_e=0$, $x^1_e=1$, and $x^2_e=2$, (iv) $\gamma_0 x^0 + \gamma_1{x}^1  + \gamma_2x^2\leq {x}$, (v) for $f\in E$ with ${x}_f\geq 1$, we have $x^j_f\geq 1$ for $j=0,1,2$.
\end{restatable}

\begin{proof}
	Consider the following LP with variables $\lambda_j$ and $x^j$ for $j=0,1,2$. 
	\begin{align}
	\quad\quad& \max\quad \;\sum_{j=0,1,2}\lambda_j\\
	&\;\text{s.t.} \quad x^j(\delta(U))\geq 2\lambda_j \;& \mbox{ for $\emptyset \subset U \subset V$, and $j=0,1,2$} \label{feasibility2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad 0 \leq x^j \leq 2\lambda_j\; &\mbox{ for $j=0,1,2$}\label{bound2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^j_e =j\cdot \lambda_j\; &\mbox{ for $j=0,1,2$}\label{branchcoordinate2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^j_f \geq \lambda_j \; &\mbox{ for $f\in E$ where $x_f \geq 1$, and $j=0,1,2$}\label{1edges2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1+x^2 \leq x\label{packing2ec}\\
	&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1,\lambda_2 \geq 0
	\end{align}	Let $x^j$, $\gamma_j$ for $j=0,1,2$ be an optimal solution solution to the LP above. Let $\hat{x}^{j}={x^j}/{\gamma_j}$ for $j=0,1,2$ where $\gamma_j>0$. If $\gamma_j=0$, let $\hat{x}^{j}=0$. Observe that  (ii), (iii), (iv), and (v) are satisfied with this choice. We can also show that $\gamma_0+\gamma_1+\gamma_2\geq {1}/{g(\2ec)}$, which means that (i) is also satisfied. The proof is similar to the proof of the claim in Lemma \ref{LPClemma}, but we need to replace each $f\in E$ with $x_f\geq 1$ with a suitably long path to ensure that Constraint (\ref{1edges2ec}) is also satisfied.	
	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1+\gamma_2\geq \frac{1}{g(\2ec)}$.
	\end{claim}
	\begin{cproof}
		Suppose for contradiction $\sum_{j=0,1,2}\gamma_j = \frac{1}{g(\2ec)} - \epsilon$ for some $\epsilon >0$. Construct graph $G'$ by removing edge $f$ with $x_f\geq 1$ and replacing it with a path $P_f$ of length $\ceil{\frac{2}{\epsilon}}$. Define $x'_h = x_h$ for each edge $h$ such that $x_h<1$. For each $h\in P_f$ let $x'_h= x_f$ for all $f$ with $x_f\geq 1$. It is easy to check that $x'\in \subtour(G')$. By Theorem \ref{CV2} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and 2-edge-connected multigraphs $F'_i$ of $G'$ for $i=1,\ldots,k$ such that 
		$\sum_{i=1}^{k}\theta_i \chi^{F'_i}\leq g(\2ec)x'$.

		Note that each $F'_i$ contains at least one copy of every edge in any path $P_f$, except for at most one edge in the path. We will obtain 2-edge-connected multigraphs $F_1,\ldots,F_k$ of $G$ using $F'_1,\ldots,F'_k$, respectively. To obtain $F_i$ first remove all $P_f$ paths from $F'_i$. Suppose there is an edge $h$ in $P_f$ such that $\chi^{F'_i}_h=0$, this means that for any edge $p\in P_f$ such that $p\neq h$, $\chi^{F'_i}_p=2$. In this case, let $\chi^{F_i}_f=2$, i.e. add two copies of $f$ to $F_i$. If there are at least one edge $h\in P_f$ with $\chi^{F'_i}_h= 1$, let $\chi^{F_i}_f=1$, i.e. add one copy of $f$ to $F_i$. If for all edges $h\in P_f$, we have $\chi^{F'_i}_h=2$, then let $\chi^{F_i}_f=2$. For $f\in E$ with $x_f<1$ we have
		\begin{equation}
		\sum_{i=1}^{k}\theta_i \chi^{F_i}_f=\sum_{i=1}^{k}\theta_i \chi^{F'_i}_f\leq g(\2ec)x'_f= g(\2ec)x_f.
		\end{equation}
		In addition for $f\in E$ with $x_f\geq 1$ we have $\chi^{F_i}_f \leq \frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}$ by construction.
		\begin{align*}
		\sum_{i=1}^{k}\theta_i \chi^{F_i}_f&\leq \sum_{i=1}^{k}\theta_i\frac{\sum_{h\in P_f}\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
		&= \frac{\sum_{h\in P_f} \sum_{i=1}^{k}\theta_i\chi^{F'_i}_h}{\ceil{\frac{2}{\epsilon}}-1}\\
		&\leq \frac{\sum_{h\in P_f} g(\2ec)x'_h}{\ceil{\frac{2}{\epsilon}}-1}\\
		&= \frac{\sum_{h\in P_f} g(\2ec)x_f}{\ceil{\frac{2}{\epsilon}}-1}\\
		&= \frac{\ceil{\frac{2}{\epsilon}}}{\ceil{\frac{2}{\epsilon}}-1}g(\2ec)x_f.
		\end{align*}
		Therefore, since $\frac{\ceil{\frac{2}{\epsilon}}}{\ceil{\frac{2}{\epsilon}}-1}\geq 1$, we have 
		\begin{equation}
		x \geq\sum_{i\in [k]: \chi^{F_i}_e=0}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g(\2ec)\ceil{\frac{2}{\epsilon}}}\chi^{F_i}+ \sum_{i\in [k]: \chi^{F_i}_e=1}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g(\2ec)\ceil{\frac{2}{\epsilon}}}\chi^{F_i}+\sum_{i\in [k]: \chi^{F_i}_e=2}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g(\2ec)\ceil{\frac{2}{\epsilon}}}\chi^{F_i}.
		\end{equation}
		Let $x^j = \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g(\2ec)\ceil{\frac{2}{\epsilon}}}\chi^{F_i}$ and $\theta_j =  \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g(\2ec)\ceil{\frac{2}{\epsilon}}}$ for $j=0,1,2$. It is easy to check that $x^j$ , $\theta_j$ for $j=0,1,2$ is a feasible solution to the LP above. Notice that $\sum_{j=0,1,2}\theta_j = \frac{\ceil{\frac{2}{\epsilon}}-1}{g(\2ec)\ceil{\frac{2}{\epsilon}}}$. By assumption, we have $\frac{\ceil{\frac{2}{\epsilon}}-1}{g(\2ec)\ceil{\frac{2}{\epsilon}}}\leq  \frac{1}{g(\2ec)}-\epsilon$, which is a contradiction.
	\end{cproof}
	This concludes the proof. \end{proof}
In contrast to FDT for binary IPs where we round up the fractional variables that are already branched on at each level, in FDT for 2EC we keep all coordinates as they are and perform a rounding procedure at the end. Formally, let $L_i$ for $i=1,\ldots,|\spp(x^*)|$ be collections of pairs of feasible points in $\subtour(G)$ together with their multipliers. Let $t=|\spp(x^*)|$ and assume without loss of generality that $\spp(x^*)=\{e_1,\ldots,e_t\}$.

\begin{lemma}\label{2ecpruning}
	The FDT algorithm for 2EC in  polynomial time produces sets $L_0,\ldots,L_t$ of pairs $x\in \2ec(G)$ together with multipliers $\lambda$ with the following properties for $i\in [t]$:
	(a) If $x\in L_i$, then $x_{e_j}=0$ or $x_{e_j}\geq 1$ for $j=1,\ldots,i$, (b) $\sum_{(x,\lambda)\in L_i }\lambda \geq \frac{1}{g(\2ec)^i}$, (c) $\sum_{(x,\lambda)\in L_i }\lambda x \leq x^*$, (d) $|L_i|\leq t$.
\end{lemma}
The proof is similar to Lemma \ref{prune}, but we need to use property (v) in Lemma \ref{LPC2EC} to prove that (a) also holds.
\begin{proof}
	We proceed by induction on $i$. Define $L_0=\{(x^*,1)\}$. It is easy to check all the properties are satisfied. Now, suppose by induction we have $L_{i-1}$ for some $i=1,\ldots,t$ that satisfies all the properties. For each solution $x^\ell$ in $L_{i-1}$ apply Lemma \ref{LPC2EC} on $x^\ell$ and $e_{i}$ to obtain $x^{\ell j}$ and $\lambda_{\ell j}$ for $j=0,1,2$. Let $L'$ be the collection that contains $(x^{\ell j},\lambda_\ell \cdot \lambda_{\ell j})$ for $j=0,1,2$, when applied to all $(x^\ell,\lambda_\ell)$ in $L_{i-1}$. Similar to the proof in Lemma \ref{prune} one can check that $L_i$ satisfies properties (b), (c). We now verify property (a). Consider a solution $x^\ell$ in $L_{i-1}$. For $e\in \{e_1,\ldots,e_{i-1}\}$ if $x^\ell_e =0$, then by property (iv) in Lemma \ref{LPC2EC} we have $x^{\ell j}=0$ for $j=0,1,2$. Otherwise by induction we have $x^{\ell}_{e}\geq 1$ in which case property (v) in Lemma \ref{LPC2EC} ensures that $x^{\ell j}_e\geq 1$ for $j=0,1,2$. Also, $x^{\ell j}_{e_i}= j$, so $x^{\ell j}_{e_i}=0$ or $x^{\ell j}_{e_i}\geq 1$ for $j=0,1,2$.

	Finally, if $|L'|\leq t$ we let $L_i=L'$, otherwise apply $\prun(L')$ to obtain $L_{i}$.
\end{proof}

Consider the solutions $x$ in $L_t$. For each variable $e$ we have $x_e=0$ or $x_e\geq 1$. 
\begin{lemma}\label{rounddown}
	Let $x$ be a solution in $L_t$. Then $\floor{x} \in \subtour(G)$. 
\end{lemma}
\begin{proof}
	Suppose not. Then there is a set of vertices $\emptyset \subset U \subset V$ such that $\sum_{e\in \delta(U)}\floor{x_e}<2$. Since $x\in \subtour(G)$ we have $\sum_{e\in \delta(U)}x_e \geq 2$. Therefore, there is an edge $f\in \delta(U)$ such that $x_f$ is fractional. By property (a) in Lemma \ref{2ecpruning}, we have $1<  x_f < 2$. Therefore, there is another edge $h$ in $\delta(U)$ such that $x_h>0$, which implies that $x_h\geq 1$. But in this case $\sum_{e\in \delta(U)}\floor{x_e}\geq  \floor{x_f}+\floor{x_h}  \geq 2$. This is a contradiction.
\end{proof}

The FDT algorithm for 2EC iteratively applies Lemmas \ref{LPC2EC} and \ref{2ecpruning} to variables $x_1,\ldots,x_t$ to obtain leaf point solutions $L_t$. Finally, we just need to apply Lemma \ref{rounddown} to obtain the 2-edge-connected multigraphs from every solution in $L_t$. Notice that since $x$ is an extreme point we have $t\leq 2|V|-1$ \cite{boydpulley}. By Lemma \ref{2ecpruning} we have
\begin{align*}
\sum_{(x,\lambda)\in L_t} \frac{\lambda}{\sum_{(x,\lambda)\in L_t}\lambda} \floor{x} \leq \frac{1}{\sum_{(x,\lambda)\in L_t}\lambda} \sum_{(x,\lambda)\in L_t} \lambda {x} \leq g^t_{\2ec} x^*.
\end{align*}
\section{Computational Experiments with FDT}\label{experiment}
We ran FDT on two network design problems: TAP and 2EC.

\paragraph{FDT on randomly generated instances of TAP.}
Recall that in TAP we are given a tree $T=(V,E)$, and a set of links $L$ between vertices in $V$ and costs $c\in \mathbb{R}^{L}_{\geq 0}$. A feasible augmentation is $L'\subseteq L$ such that $T+L'$ is 2-edge-connected. In TAP we wish to find the minimum-cost feasible augmentation. The integrality gap of the cut-LP for TAP is defined as 
\begin{equation*}
g(\tap) = \max_{c\in \mathbb{R}^L_{\geq 0}} \frac{\min_{x\in\tap(T,L)} cx}{\min_{x\in\cut(T,L)} cx}.
\end{equation*}

We know $\frac{3}{2}\leq g(\tap)\leq 2$~\cite{FJ81,32gaptap}. Notice that $\min_{x\in \tap(T,L)}cx$ is a binary IP. We ran binary FDT on a set of 264 fractional extreme points of randomly generated instances of $\tap$. Table \ref{tableTAP} shows FDT found solutions better than the integrality-gap lower bound for most instances.

\begin{table}[h!]
	\begin{small}
		\centering
		\begin{tabular}{c c c c c}
			\hline
			& $C\in [1.1,1.2]\;$ & $\;C\in (1.2,1.3]\;$ &
			$\;C\in (1.3,1.4]$ &\; $C\in (1.4,1.5]\;$ \\ \hline
			TAP & $36$ & $66$ & $170$ & $10$\\  \hline \\
		\end{tabular}\caption{The scale factor $C$ for FDT run on 264 randomly generated TAP instances with fractional extreme points: 138 instances have $74$ variables. The rest have $250$.} \label{tableTAP}
	\end{small}

\end{table}

\paragraph{Computational comparison between Christofides' algorithm and FDT for 2EC on Carr-Vempala points.} We implemented the polyhedral version of Christofides' algorithm \cite{wolsey}. In particular, we implemented the $O$-join augmentation in Christofides' algorithm, in a way that minimizes the average usage of every edge in the $O$-join augmentation across the convex combination of spanning trees. In particular, let $x\in \subt(G_x)$. It is easy to check that $\frac{n-1}{n}x\in \st(G_x)$, hence we can write $x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G_x$, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$. Let $O_i$ be the set of odd degree vertices of $T_i$. We then solve the following LP that allows us to find parity corrections that are good for the whole convex combination.
\begin{align}\label{ojoinaverage}
\min \{ \alpha:\;&\sum_{i=1}^{k} \lambda_i	y^i = \alpha \cdot x,\;\\\nonumber &y^i(\delta(U)) \geq 1 \;\mbox{for $U\subseteq V(G_x), |V\cap O_i|$ odd},\;  y^i\in [0,1]^{E_x} \; \mbox{for $i\in [k]$}\}.
\end{align}
The variables in the above LP are $y^i\in \mathbb{R}^{E_x}_{
\geq 0}$ for $i\in [k]$. For each $i\in [k]$ we have $y^i\in \mathcal{D}(O_i\join(G_x))$. This formulation allows the instance specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$. Recall that a Carr-Vempala point consists of a Hamiltonian cycle of fractional edges.  Figure \ref{fdtvschris} shows FDT's solutions on all Carr-Vempala points with at most 10 vertices on the Hamiltonian cycle formed by the fractional edges are always better than those from the polyhedral version of Christofides' algorithm. In more details, in Figure \ref{fdtvschris} the horizontal axis of the plot is indexed with the 60 Carr-Vempala points that we considered. For each Carr-Vempala point $x$, there are two data points. The value of the first data point depicted by a circle on the vertical axis is $\frac{n-1}{n}+\alpha$ where $n$ is the number of vertices in the Hamiltonian cycle formed by fractional edges of $x$ and $\alpha$ is the optimal solution to (\ref{ojoinaverage}). 
The value of the second data point depicted by a cross on the vertical axis is $C$ where $C$ is obtained from applying Theorem \ref{FDT2EC} to $x$. In other words, Figure \ref{fdtvschris} is comparing the upper bounds on the instances specific integrality gap certified by Christofides' algorithm  and FDT algorithm for 2EC.

\begin{figure}[h!]
	\centering
	\includegraphics[width=9cm,scale=1.4]{"fdt vs christofides".png}
	\caption{Polyhedral version of Christofides' algorithm vs FDT on all Carr-Vempala points with 10 vertices on the Hamiltonian cycle of the fractional-edges.}
	\label{fdtvschris}
\end{figure}
\paragraph{FDT for 2EC on Carr-Vempala points.}
We ran FDT for 2EC on 963 fractional extreme points of $\subtour(G)$. We enumerated all (fractional) Carr-Vempala points with $10$ and $12$ vertices. Table \ref{table2EC} shows that again FDT found solutions better than the integrality-gap lower bound for most instances. 
\begin{table}[h!]
	\begin{small}
		\centering
		\begin{tabular}{c c c c c}
			\hline
			& $C\in [1.08,1.11]\;$ & $\;C\in (1.11,1.14]\;$ &
			$\;C\in (1.14,1.17]$ &\; $C\in (1.17,1.2]\;$ \\ \hline
			2EC & $79$ & $201$ & $605$ & $78$ \\ \hline\\
		\end{tabular}	\caption{FDT for $\2ec$ implemented applied to all Carr-Vempala with 10 or 12 vertices. A Carr-Vempala point with $k$ vertices has $\frac{3k}{2}$ edges. Thus, the upper bound provided by Theorem \ref{FDT2EC} is $g(\2ec)^{3k/2}$. The lower bound on $g(\2ec)$ is $\frac{6}{5}$.}
		\label{table2EC}
	\end{small}
\end{table}

### 2020-06-03 FDT2020/Introduction.tex
bob comment

@@
 It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}.
-However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or near-optimal solution with provable bound) to many specific instances of NP-hard combinatorial optimization problems.
+However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or nearoptimal solutions with a provable bound) to many specific instances of NP-hard combinatorial optimization problems.
 
-Relaxing the integrality constraints gives the polynomial-time-solvable linear-programming relaxation: $\min \;\{cx:\;x\in P(I) \}$.
+Relaxing the integrality constraints gives the polynomial time solvable linear programming relaxation: $\min \;\{cx:\;x\in P(I) \}$.
 The optimal value of this linear program (LP), denoted $z_{\lp}(I,c)$, is a lower bound on the optimal value for the IP, denoted $z_{\IP}(I,c)$.
-The solutions can also provide some useful global structure, even though the fractional values might not directly meaningful.
+The solutions can also provide some useful global structure, even though the fractional values might not be directly meaningful.
 
-Many researchers (see \cite{davids,vazirani}) have developed polynomial-time LP-based approximation algorithms that find solutions for special classes of IPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$.
+Many researchers (see \cite{davids,vazirani}) have developed polynomial time LP-based approximation algorithms that find solutions for special classes of IPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$.
 The approximation factor $C$ can be a constant or depend on the input parameters of the IP, e.g.
@@
 Recall that integrality gap $g(I)$ for instance $I$ is defined to be $g(I)= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$.
-An example of instance specific integrality gap is the integrality gap of the subtour elimination relaxation for the 2-edge-connected spanning multigraph problem on $n$ vertices.
+An example of an instance specific integrality gap is the integrality gap of the subtour elimination relaxation for the 2-edge-connected spanning multigraph problem on $n$ vertices.
 The instance is the complete graph on $n$ vertices.
@@
 \begin{thm}[Carr, Vempala \cite{Carr2004}] \label{CV2}
-	Let $x\in P(I)$.
-There exists $\theta \in [0,1]^k$ where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in \dom(S(I))$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ if and only if $g(I) \leq C$.
+	We have $g(I) \leq C$ if and only if for  $x\in P(I)$ there exists $\theta \in [0,1]^k$ where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in \dom(S(I))$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$.
 \end{thm}
@@
 To study integrality gaps, we wish to find such a solution constructively: assuming reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g(\mathcal{I})<\infty$, and $x\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in S(I)$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ in polynomial time?
-We wish to find the smallest factor $C$ as possible.
+We wish to find the smallest factor $C$ possible.
 
@@
 
-TODO
-
+In the \textsc{minimum vetex cover problem (VC)} we are given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$.
+A subset of $U$ of $V$ is a \textit{vertex cover} if for $e\in E$ at least one endpoint of $e$ is in $U$.
+The goal in VC is to find the minimum cost vertex cover.
+The linear programming relaxation for VC is
+\begin{equation}
+\min \{cx \; : \; x_u + x_v \geq	 1 \text{ for } e=uv \in E, \; x\in [0,1]^{V}\}.
+\end{equation}
+The integrality gap of this formulation is exactly 2.
+It is shown that it is NP-hard to approximte VC within any factor sctrictly better than 2 \cite{}.
+We run FDT on challenge test cases \cite{} and compare it with CPLEX IP solver and feasiblity pump.
 \subsubsection{Tree augmentation problem}

### 2020-06-03 FDT2020/main-section.tex
bob comment

--- 2020-05-15 FDT2020/main section.tex
@@
 
-We start by introducing an algorithm that ``fixes" the variables iteratively, starting from from the first coordinate and ending at the $t$-th coordinate.
+We start by introducing an algorithm that ``fixes" the variables iteratively, starting from the first coordinate and ending at the $t$-th coordinate.
 Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
@@
 
-	Let $x^0,x^1$, and $\gamma_0,\gamma_1$ be an optimal solution solution to the LP above.
+	Let $x^0,x^1$, and $\gamma_0,\gamma_1$ be an optimal solution to the LP above.
 Let $\hat{x}^0 = x^0/\gamma_0$, $\hat{x}^1=x^1/\gamma_1$.

### 2020-06-05 FDT2020/Introduction.tex
somefixes

@@
 The integrality gap of this formulation is exactly 2.
-It is shown that it is NP-hard to approximte VC within any factor sctrictly better than 2 \cite{}.
-We run FDT on challenge test cases \cite{} and compare it with CPLEX IP solver and feasiblity pump.
+It is shown that it is UG-hard to approximte VC within any factor sctrictly better than 2 \cite{UGhardVC}.
+We compare  FDT and the feasbility pump heuristic \cite{fp1} on the PACE 2019\footnote{ Parameterized Algorithms and Computational Experiments Challenge 2019: \url{https://pacechallenge.org/2019/}} challenge test cases \cite{PACE} and compare its performance with
 \subsubsection{Tree augmentation problem}
-In the \textsc{Tree Augmentation Problem (TAP)} we are given a  graph $G=(V,E)$, a tree $T$.
+In the \textsc{Tree Augmentation Problem (TAP)} we are given a  graph $G=(V,E)$, a a spanning tree $T$ of $G$.
 We also have a cost vector $c\in \mathbb{R}^{E\setminus T}_{\geq 0}$.
@@
 
-A \textit{Carr-Vempala point} $x$ is a fractional point in the subtour elimination relaxation where the fractional edges of $x$, edges $e$ with $0<x_e<1$, form a Hamiltonian cycle.
-For $\2ec$ we show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the Hamiltonian cycle formed by the fractional edges.
+Consider a graph $G=(V,E)$.
+A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a Hamiltonian cycle of $G$.
+Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point.
+We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the Hamiltonian cycle formed by the fractional edges.
 For Carr-Vempala points we assume that 1-edges are replaced by long paths of 1-edges making these points into potentially harder to round instances.

### 2020-06-05 FDT2020/main-section.tex
somefixes

@@
-	\subsection{Notations}
+\iffalse{
+	\subsection{Notation}
 	For vectors $x,y\in \mathbb{R}_{n}$ we say $x$ dominates $y$ if $x_i\geq y_i$ for $i= 1,\ldots,n$.
@@
 For a set $S$ of vectors in $\mathbb{R}_{n}$, $\conv(S)$ is the convex hull of all the points in $S$.
-
+}\fi
 \section{Finding a Feasible Solution}\label{domTOIP}
@@
 Recall that in the 2EC, we are given non-negative costs on the edges of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$.
-The natural linear programming relaxation is $\min \{cx \; : \; x\in \subtour(G)\}$ where $\subtour(G) = \{x\in [0,2]^E: x(\delta(U))\geq 2 \mbox{ for } \emptyset \subset U \subset V\}$.
-Notice that, no optimal solution ever takes 3 copies of an edge in 2EC, hence we assume that we can take an edge at most 2 times, hence in this chapter (unlike in the previous chapters) we work with a bounded version of $\subtour(G)$.
-Notice that $\dom(\subtour(G))\cap [0,2]^{E} = \subtour(G)$.
-Thus, we also assume a multigraph can contain at most 2 copies of any edge in the graph.
 We want to prove Theorem \ref{FDT2EC}.
@@
 \section{Computational Experiments with FDT}\label{experiment}
-We ran FDT on two network design problems: TAP and 2EC.
+We ran FDT on three network design problems: VC, TAP and 2EC. 
+\paragraph{FDT on VC instances from (PACE 2019) \cite{PACE}.}
 
@@
 
-\paragraph{Computational comparison between Christofides' algorithm and FDT for 2EC on Carr-Vempala points.} We implemented the polyhedral version of Christofides' algorithm \cite{wolsey}.
-In particular, we implemented the $O$-join augmentation in Christofides' algorithm, in a way that minimizes the average usage of every edge in the $O$-join augmentation across the convex combination of spanning trees.
-In particular, let $x\in \subt(G_x)$.
-It is easy to check that $\frac{n-1}{n}x\in \st(G_x)$, hence we can write $x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G_x$, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$.
+\paragraph{Computational comparison between Christofides' algorithm and FDT for 2EC on Carr-Vempala points.}
+
+First we need to describe the polyhedral version Christofides' algorithm.
+We do this specifically for the Carr-Vempala points.
+Let $x$ be a Carr-Vempala points defined on a graph $G=(V,E)$.
+It is well known that $\frac{|V|-1}{|V|}\cdot x$ is in the convex hull of incidence vectors of spanning trees of $G$.
+Hence, we can write $\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G$, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$.
 Let $O_i$ be the set of odd degree vertices of $T_i$.
+It is easy to see that $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, namely $O_i\join(G)$~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, and $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.}.
+
  We then solve the following LP that allows us to find parity corrections that are good for the whole convex combination.
-\begin{align}\label{ojoinaverage}
-\min \{ \alpha:\;&\sum_{i=1}^{k} \lambda_i	y^i = \alpha \cdot x,\;\\\nonumber &y^i(\delta(U)) \geq 1 \;\mbox{for $U\subseteq V(G_x), |V\cap O_i|$ odd},\;  y^i\in [0,1]^{E_x} \; \mbox{for $i\in [k]$}\}.
-\end{align}
+\begin{equation}\label{ojoinaverage}
+\min \{ \alpha:\;\sum_{i=1}^{k} \lambda_i y^i = \alpha \cdot x,\;  y^i \in O_i\join(G) \; \mbox{for $i\in [k]$}\}.
+\end{equation}
 The variables in the above LP are $y^i\in \mathbb{R}^{E_x}_{
 \geq 0}$ for $i\in [k]$.
-For each $i\in [k]$ we have $y^i\in \mathcal{D}(O_i\join(G_x))$.
+For each $i\in [k]$ we have $y^i\in O_i\join(G_x)$.
 This formulation allows the instance specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$.
 Recall that a Carr-Vempala point consists of a Hamiltonian cycle of fractional edges.
-Figure \ref{fdtvschris} shows FDT's solutions on all Carr-Vempala points with at most 10 vertices on the Hamiltonian cycle formed by the fractional edges are always better than those from the polyhedral version of Christofides' algorithm.
+Figure \ref{fdtvschris} shows FDT's solutions on all Carr-Vempala points defined on graphs with 10 vertices are always better than those from the polyhedral version of Christofides' algorithm.
 In more details, in Figure \ref{fdtvschris} the horizontal axis of the plot is indexed with the 60 Carr-Vempala points that we considered.
 For each Carr-Vempala point $x$, there are two data points.
-The value of the first data point depicted by a circle on the vertical axis is $\frac{n-1}{n}+\alpha$ where $n$ is the number of vertices in the Hamiltonian cycle formed by fractional edges of $x$ and $\alpha$ is the optimal solution to (\ref{ojoinaverage}).
+The value of the first data point depicted by a circle on the vertical axis is $\frac{|V|-1}{|V|}+\alpha$  and $\alpha$ is the optimal solution to (\ref{ojoinaverage}).
 The value of the second data point depicted by a cross on the vertical axis is $C$ where $C$ is obtained from applying Theorem \ref{FDT2EC} to $x$.
@@
 	\centering
-	\includegraphics[width=9cm,scale=1.4]{"fdt vs christofides".png}
-	\caption{Polyhedral version of Christofides' algorithm vs FDT on all Carr-Vempala points with 10 vertices on the Hamiltonian cycle of the fractional-edges.}
+	\includegraphics[width=9cm,scale=1.4]{"fdt-vs-christofides".png}
+	\caption{Polyhedral version of Christofides' algorithm vs FDT on all Carr-Vempala points defined on graphs with 10 vertices.}
 	\label{fdtvschris}

### 2020-06-10 FDT2020/FDT.tex
somefixes
Initial abstract and some comments

@@
 \documentclass[11pt,notitlepage]{article}
+
+\newcommand{\cindy}[1]{\textcolor{green!60!black}{(Cindy: #1)}}
+\newcommand{\arash}[1]{\textcolor{blue}{(Arash: #1)}}
+\newcommand{\bob}[1]{\textcolor{red}{(Bob: #1)}}
+% To drop all comments, just comment out \iffalse and \fi
+\iffalse
+\renewcommand{\cindy}[1]{}
+\renewcommand{\arash}[1]{}
+\renewcommand{\bob}[1]{}
+\fi
 
@@
 \usepackage{mathrsfs}
-
+\usepackage{hyperref}
 \usepackage{epigraph}
-\usepackage{thm-restate}
 \usepackage{cleveref}
@@
 \begin{abstract}
+We present a new algorithm, Fractional Decomposition Tree (FDT) for finding a feasible solution for an integer program (IP) where all variables are binary.
+FDT runs in polynomial time and is guaranteed to find a feasible integer solution provided the integrality gap is bounded.
+The algorithm gives a construction for Carr and Vempala's theorem that any feasible solution to the IP's linear-programming relaxation, when scaled by the instance integrality gap, dominates a convex combination of feasible solutions.
+FDT is also a tool for studying the integrality gap of IP formulations.
+We demonstrate that with experiments studying the integrality gap of two problems: optimally augmenting a tree to a 2-edge-connected graph and finding a minimum-cost 2-edge-connected multi-subgraph (2EC).
+We also give a simplified algorithm, Dom2IP, that more quickly determines if an instance has an unbounded integrality gap.
+We show that FDT's speed and approximation quality compare well to that of feasibility pump on moderate-sized instances of the vertex cover problem.
+For a particular set of hard-to-decompose fractional 2EC solutions, FDT always gave a better integer solution than the best previous approximation algorithm (Christofides).
 
@@
 \input{Introduction}
-\input{main section}
+\input{main-section}
 

### 2020-06-10 FDT2020/Introduction.tex
Initial abstract and some comments

@@
 
+\cindy{An original comment: There's material in this section (e.g.
+general discussion of combintatorial optimization) that's likely unnecessary for the journal paper.
+We probably want to start with what is now Section 2, but have some opening introduction giving the big picture.
+Remember when we first mention rounding to be clear this is not numerical rounding.
+TODO: Add English statement for things currently only given in math.
+Add definitions of problems so reviewers and readers don't have to look them up.}
 In combinatorial optimization the aim is to find the optimal solution in a discrete and
@@
 
+\cindy{TODO: remove ``recall that'' for anything we haven't already defined in this paper.
+Even though it's likely anyone reading this will care about IPs and integrality gaps, we should not assume they already know things we define the way we define them.}
 In this paper, our focus is on linear relaxation of combinatorial
@@
 \end{equation*}
+\cindy{Since most canonical formulations for IP/LP express variables bounds separately, we should mention here that they are rolled into matrix $A$.}
 
@@
 It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}.
-However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or nearoptimal solutions with a provable bound) to many specific instances of NP-hard combinatorial optimization problems.
+However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or near-optimal solutions with a provable bound) to many specific instances of NP-hard combinatorial optimization problems.
 
-Relaxing the integrality constraints gives the polynomial time solvable linear programming relaxation: $\min \;\{cx:\;x\in P(I) \}$.
+Relaxing the integrality constraints gives the polynomial-time-solvable linear programming relaxation: $\min \;\{cx:\;x\in P(I) \}$.
 The optimal value of this linear program (LP), denoted $z_{\lp}(I,c)$, is a lower bound on the optimal value for the IP, denoted $z_{\IP}(I,c)$.
@@
 Recall that integrality gap $g(I)$ for instance $I$ is defined to be $g(I)= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$.
-An example of an instance specific integrality gap is the integrality gap of the subtour elimination relaxation for the 2-edge-connected spanning multigraph problem on $n$ vertices.
-The instance is the complete graph on $n$ vertices.
+\cindy{Does the integrality gap always require positive objective coefficients?
+Or is that an extra restriction in our definition?
+Is there a reference that has that restriction?} An example of an instance-specific integrality gap is the integrality gap of the subtour-elimination relaxation for the 2-edge-connected spanning multigraph problem on $n$ vertices.
+\cindy{We might need to define the problem or have a forward pointer.} The instance is the complete graph on $n$ vertices.
 Alexander et al.
@@
 For such problems there is an algorithm to express vector $x\in P(I)$ as a convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.
+\cindy{Should this proposition just be a corollary of the Carr-Vempala theorem?  Are we going to describe how to do it?  If so, there should be a forward pointer to that discussion.}
 \begin{proposition}\label{cara}
@@
 Assume in addition that $S(I),P(I)\subseteq [0,1]^n$.
-For a vector $x\in \mathbb{R}_{\geq 0}^n$ such that $x\in P(I)$, let $\spp(x)= \{i \in [n]: x_i \neq 0\}$.
+\cindy{State somewhere that we can allow continuous variables as long as they are not in the objective function.
+(We will explain later how to extend to this case).} For a vector $x\in \mathbb{R}_{\geq 0}^n$ such that $x\in P(I)$, let $\spp(x)= \{i \in [n]: x_i \neq 0\}$.
 For an integer $\beta$ let $\{\beta\}^n$ be the vector $y\in \mathbb{R}^n$ with $y_i=\beta$ for $i\in [n]$.
@@
 We show how one might use FDT to investigate the integrality gap for such well-studied problems.
+\cindy{TODO: forward pointers to the sections with more details.}
 
@@
 The integrality gap of this formulation is exactly 2.
-It is shown that it is UG-hard to approximte VC within any factor sctrictly better than 2 \cite{UGhardVC}.
-We compare  FDT and the feasbility pump heuristic \cite{fp1} on the PACE 2019\footnote{ Parameterized Algorithms and Computational Experiments Challenge 2019: \url{https://pacechallenge.org/2019/}} challenge test cases \cite{PACE} and compare its performance with
+\cindy{Move to active voice once we have an actual reference for this.} It is shown that it is UG-hard to approximte VC within any factor sctrictly better than 2 \cite{UGhardVC}.
+\cindy{We compare to small instances} We compare  FDT and the feasbility pump heuristic \cite{fp1} on the PACE 2019\footnote{ Parameterized Algorithms and Computational Experiments Challenge 2019: \url{https://pacechallenge.org/2019/}} challenge test cases \cite{PACE} and compare its performance with
 \subsubsection{Tree augmentation problem}
-In the \textsc{Tree Augmentation Problem (TAP)} we are given a  graph $G=(V,E)$, a a spanning tree $T$ of $G$.
+In the \textsc{Tree Augmentation Problem (TAP)} we are given a  graph $G=(V,E)$, a spanning tree $T$ of $G$.
 We also have a cost vector $c\in \mathbb{R}^{E\setminus T}_{\geq 0}$.
@@
 A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a Hamiltonian cycle of $G$.
-Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point.
+\cindy{I am having a hard time parsing the next sentence.
+Is there supposed to be a value for $g(\2ec)$ for this case?} Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point.
 We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the Hamiltonian cycle formed by the fractional edges.
-For Carr-Vempala points we assume that 1-edges are replaced by long paths of 1-edges making these points into potentially harder to round instances.
+For Carr-Vempala points we assume that 1-edges are replaced by long paths of 1-edges making these points into potentially harder-to-round instances.

### 2020-06-10 FDT2020/Introduction.tex
some replies to cindy questions

@@
 Or is that an extra restriction in our definition?
-Is there a reference that has that restriction?} An example of an instance-specific integrality gap is the integrality gap of the subtour-elimination relaxation for the 2-edge-connected spanning multigraph problem on $n$ vertices.
-\cindy{We might need to define the problem or have a forward pointer.} The instance is the complete graph on $n$ vertices.
+Is there a reference that has that restriction?} For example consider the minimum cost 2-edge-connected multi-subgraph problem (2EC): Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected multi-subgraph of $G$.
+A linear programming relaxation for this problem known as the subtour elimination relaxation  is
+ \begin{equation}\min \{cx: \sum_{e\in \delta(U)}x_e \geq 2 \mbox{ for } \emptyset \subsetneq U \subsetneq V,\; x\in [0,2]^{E}\}. 
+ \end{equation}
+ In this case the instance-specific integrality gap is the integrality gap of the subtour-elimination relaxation for the 2EC on graph with $n$ vertices.
+\cindy{We might need to define the problem or have a forward pointer.} \arash{See above}.
 Alexander et al.
-\cite{alexander2006integrality} showed the instance specific integrality gap of the subtour elimination relaxation for the 2-edge-connected multigraph problem for instances of the problem with $n= 10$ is at most $\frac{7}{6}$.
+\cite{alexander2006integrality} showed the instance-specific integrality gap of the subtour elimination relaxation for the 2EC for instances of the problem with $n= 10$ is at most $\frac{7}{6}$.
 
@@
 \end{equation}
-For example, the aforementioned integrality gap of the subtour elimination relaxation for the 2-edge-connected multigraph problem is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}.
+For example, the aforementioned integrality gap of the subtour elimination relaxation for the 2EC is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}.
 Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation.
@@
 \cindy{Should this proposition just be a corollary of the Carr-Vempala theorem?  Are we going to describe how to do it?  If so, there should be a forward pointer to that discussion.}
+
+\arash{not exactly: Carr-Vempala don't give a construction.
+The proposition below is a result of constructive version of Carathedory's theorem which I think is implied by the Ellipsoid algorithm, but there are even faster versions of it.
+In some way the difference between prop 1 and theorem 2 is our initial motivation for thinking of polynomial construction.}
 \begin{proposition}\label{cara}
@@
 Recall that $\dom(P(I))$ is the set of points $x'$ such that there exists a point $x\in P$ with $x'\geq x$, also known as the dominant of $P(I)$.
-For covering problems the polyhedron is essentially the same as its dominant, but this is not true in general.
+A polyhedron is of \textit{blocking type} if it is equal to its dominant.
+Theorem \ref{CV2} was first introduced by Goemans \cite{goemansblocking} for blocking type polyhedra.
 While there is an exact algorithm for problems with gap $1$ as stated in Proposition \ref{cara}, Theorem~\ref{CV2} is existential, with no construction.
@@
 Consider a graph $G=(V,E)$.
-A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a Hamiltonian cycle of $G$.
+A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$.
 \cindy{I am having a hard time parsing the next sentence.
-Is there supposed to be a value for $g(\2ec)$ for this case?} Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point.
-We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the Hamiltonian cycle formed by the fractional edges.
-For Carr-Vempala points we assume that 1-edges are replaced by long paths of 1-edges making these points into potentially harder-to-round instances.
+Is there supposed to be a value for $g(\2ec)$ for this case?}\arash{There was a missing word.
+How about now?} Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point.
+We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges.
+Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.

### 2020-06-11 FDT2020/Introduction.tex
comments asnwered

@@
 \nocite{IPbook}
-\section{Introduction}\label{chapter:intro}
 
@@
 Add definitions of problems so reviewers and readers don't have to look them up.}
+\iffalse{
+\section{Introduction}\label{chapter:intro}
+
 In combinatorial optimization the aim is to find the optimal solution in a discrete and
@@
 Obtaining feasible solutions by means of such a relaxation requires an additional step of rounding the potentially fractional solution of the continuous relaxation into integer solutions.
-
+}\fi
 \cindy{TODO: remove ``recall that'' for anything we haven't already defined in this paper.
 Even though it's likely anyone reading this will care about IPs and integrality gaps, we should not assume they already know things we define the way we define them.}
-In this paper, our focus is on linear relaxation of combinatorial
-optimization problems.
-Combinatorial optimization was pioneered by Edmonds even before efficient algorithms for solving linear programming problems where introduced by Khachiyan \cite{Khachiyan} and later by Karmarkar \cite{Karmarkar1984}.
+
+\section{Introduction}
+In this paper we focus on finding solutions to general Integer Linear Programs (IP).
+Integer Programming (and more generally Mixed Integer Linear Programming) can be used to model many practical optimization problems including scheduling, logistics and resource allocation.
+
+A common approach to Integer programming is considering their linear relaxation.
 For problems such as the \textsc{Minimum Cost Spanning Tree Problem} there are linear programming relaxations whose basic feasible solutions coincide with  integral solutions, i.e.
@@
 For other problems the value of the linear programming relaxation provides a bound (lower bound for a minimization problem and upper bound for a maximization problem) on the optimal solution.
-A common and successful approach is to round these (potentially) fractional solutions into integer solutions for the combinatorial optimization problem at hand.
+A common and successful approach is to round these (potentially) fractional solutions into integer solutions for the optimization problem at hand.
 The Integrality gap of a linear relaxation of an integer programming problem is the worst case ratio between the objective values of the discrete problem and the continuous problem.
@@
 
-\section{Integrality Gap}
 \iffalse{
@@
 }\fi 
-
-In this paper we focus on finding solutions to general Integer Linear Programs (IP).
-Integer Programming (and more generally Mixed Integer Linear Programming) can be used to model many practical optimization problems including scheduling, logistics and resource allocation.
-Recall that the set of feasible points for a pure IP (henceforth IP) is the set
+The set of feasible points for a pure IP (henceforth IP) is the set
 \begin{equation}
@@
 \end{equation}
-
 Let $I=(A,b)$ denote an instance.
 Then $S(I)$ and $P(I)$ denote $S(A,b)$ and $P(A,b)$, respectively.
-Given a linear objective function $c$, recall that an IP is $\min \;\{cx:\; x \in S(I)\}$.
+Given a linear objective function $c$, an IP is $\min \;\{cx:\; x \in S(I)\}$.
 It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}.
@@
 However, for many combinatorial optimization problems there is a limit to such techniques based on LP relaxations, represented  by the {integrality gap} of the IP formulation.
-Recall that integrality gap $g(I)$ for instance $I$ is defined to be $g(I)= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$.
+The integrality gap $g(I)$ for instance $I$ is defined to be $g(I)= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$.
 \cindy{Does the integrality gap always require positive objective coefficients?
@@
 \end{thm}
-Recall that $\dom(P(I))$ is the set of points $x'$ such that there exists a point $x\in P$ with $x'\geq x$, also known as the dominant of $P(I)$.
+We denote by $\dom(P(I))$ the set of points $x'$ such that there exists a point $x\in P$ with $x'\geq x$, also known as the dominant of $P(I)$.
 A polyhedron is of \textit{blocking type} if it is equal to its dominant.
@@
 \end{equation}
-The integrality gap of this formulation is exactly 2.
-\cindy{Move to active voice once we have an actual reference for this.} It is shown that it is UG-hard to approximte VC within any factor sctrictly better than 2 \cite{UGhardVC}.
-\cindy{We compare to small instances} We compare  FDT and the feasbility pump heuristic \cite{fp1} on the PACE 2019\footnote{ Parameterized Algorithms and Computational Experiments Challenge 2019: \url{https://pacechallenge.org/2019/}} challenge test cases \cite{PACE} and compare its performance with
+The integrality gap of this formulation is exactly 2 \cite{davids}.
+\cindy{Move to active voice once we have an actual reference for this.} \arash{I guess we can site a general approx book,} It is shown that it is UG-hard to approximte VC within any factor sctrictly better than 2 \cite{UGhardVC}.
+\cindy{We compare to small instances} We compare  FDT and the feasbility pump heuristic \cite{fp1} on the the small instances of PACE 2019\footnote{ Parameterized Algorithms and Computational Experiments Challenge 2019: \url{https://pacechallenge.org/2019/}} challenge test cases \cite{PACE}.
 \subsubsection{Tree augmentation problem}

### 2020-06-11 FDT2020/FDT.tex
comments asnwered
more changes

@@
 \onehalfspacing
+
+\title{Fractional Decomposition Tree Algorithm: A tool for studying the integrality gap of Integer Programs}
+
+\author{\textsc{Robert Carr}\thanks{University of New Mexico  {\tt{bobcarr@unm.edu}}. This material is based upon research supported in part by
+the U.S. Office of Naval Research under award number N00014-18-1-2099.}
+\and \textsc{Arash Haddadan}\thanks{Carnegie Mellon University  {\tt{ahaddada@andrew.cmu.edu}}.}
+\and \textsc{Cynthia A. Phillips}\thanks{Sandia National Laboratories  {\tt{caphill@sandia.gov}}.}}
+
 \begin{document}{\bibliographystyle{alpha}}
+
+\maketitle
 
@@
 For a particular set of hard-to-decompose fractional 2EC solutions, FDT always gave a better integer solution than the best previous approximation algorithm (Christofides).
-
 \end{abstract}
-\clearpage
 
@@
 
-\addcontentsline{toc}{chapter}{Bibliography}
 \bibliographystyle{abbrv}
-\bibliography{haddadan-ref}
+\bibliography{FDT}
 

### 2020-06-11 FDT2020/Introduction.tex
more changes

@@
 
-This value depends on the constraints in (\ref{S}).  We cannot hope to find solutions for the IP with objective values better than $g(I)\cdot z_{LP}(I,c)$.
-
+The value of $g(I)$ depends on the constraints in (\ref{S}).
+We cannot hope to find solutions for the IP with objective values better than $g(I)\cdot z_{LP}(I,c)$.
 More generally we can define the integrality gap for a class of instances $\mathcal{I}$ as follows.% In this case, the integrality gap for problem $\mathcal{I}$ is
@@
 In order to eradicate this extra factor, we need to treat the coordinate $i$ with $x_i=1$ differently.
-We focus on the \textsc{2-edge-connected multigraph graph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^{E}_{\geq 0}$ find a 2-edge-connected multi-subgraph (henceforth a multigraph) of $G$ with minimum cost.
+We focus on the \textsc{2-edge-connected multi-subgraph graph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^{E}_{\geq 0}$ find a 2-edge-connected multi-subgraph of $G$ with minimum cost.
 The natural linear programming relaxation for this problem is
@@
 We denote the feasible region of this LP by $\subtour(G)$.
-Let $\2ec(G)$ be the convex hull of incidence vectors of 2-edge-connected multigraphs of graph $G$.
+Let $\2ec(G)$ be the convex hull of incidence vectors of 2-edge-connected multi-subgraphs of graph $G$.
 Following the definition in (\ref{gapproblem}) have
@@
 	Let $G=(V,E)$ and $x$ be an extreme point of  $\subtour(G)$.
-The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multigraphs $F_1,\ldots,F_k$ such that $k\leq 2|V|-1$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq \min(Cx,\{2\}^n)$, and $\sum_{i=1}^{k}\lambda_i = 1$.
+The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multi-subgraphs $F_1,\ldots,F_k$ such that $k\leq 2|V|-1$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq \min(Cx,\{2\}^n)$, and $\sum_{i=1}^{k}\lambda_i = 1$.
 Moreover, $C\leq g(\2ec)^{|E_x|}$.
@@
 
-\subsubsection{2-edge-connected multigraph problem}
+\subsubsection{2-edge-connected multi-subgraph problem}
 Known polyhedral structure makes it easier to study integrality gaps for such problems.

### 2020-06-11 FDT2020/main-section.tex
Initial abstract and some comments
more changes

@@
 Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{|L'|} \theta^*_j \geq \sum_{j=1}^{|L'|}\gamma_j \geq \frac{1}{g^{i+1}}$.
-
 \end{proof}
@@
 
-	\vspace*{10pt}
+	\vspace*{8pt}
 
@@
 
+\vspace{8pt}
+It is not difficut to see that the number of nodes in the FDT tree is $O(n^2)$.
+A faster way to achieve feasible solutions with good quality for an IP with bounded integrality gap is an algorithm that takes a random dive into the FDT tree, hence only visiting $O(n)$ nodes.
+
+	\vspace*{8pt}
+
+	\begin{algorithm}[H]\label{FDT-dive}
+		\KwIn{$P= \{x\in \mathbb{R}^{n}: Ax\geq b\}$ and $S=\{x\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \mathbb{R}^n_+ }\frac{\min_{x\in S}cx}{\min_{x\in P}cx}$ is finite, $x^*\in P$}
+		\KwOut{$z \in S$}
+		$y = x^*$\\
+		\For{$i=1$ \textbf{to} $t$}{
+
+			Apply Lemma \ref{round-up} to obtain $[\hat{x}^0,\gamma_0]$ and $[\hat{x}^1,\gamma_1]$\\
+			$i \sim\text{Bernoulli}(\frac{\gamma_0}{\gamma_0+\gamma_1})$\\
+			$y\rightarrow \hat{x}^i$
+
+		}
+		Apply Algorithm \ref{domtoIPalg} to $y$ to obtain $z\in S$\\
+		\textbf{return} $z$
+		\caption{Dive FDT Algorithm}
+	\end{algorithm}
+
 \section{FDT for 2EC}\label{2EC}
@@
 In Section \ref{binaryfdt} our focus was on binary IPs.
-In this section, in an attempt to extend FDT to \{0,1,2\} problems we introduce an FDT algorithm for a 2-edge-connected multigraph problem.
-Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multigraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2.
-Recall that in the 2EC, we are given non-negative costs on the edges of $G$ and the goal is to find the minimum cost 2-edge-connected multigraph of $G$.
+In this section, in an attempt to extend FDT to \{0,1,2\} problems we introduce an FDT algorithm for a 2-edge-connected multi-subgraph problem.
+Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multi-subgraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2.
+Recall that in the 2EC, we are given non-negative costs on the edges of $G$ and the goal is to find the minimum cost 2-edge-connected multi-subgraph of $G$.
 We want to prove Theorem \ref{FDT2EC}.
@@
 It is easy to check that $x'\in \subtour(G')$.
-By Theorem \ref{CV2} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and 2-edge-connected multigraphs $F'_i$ of $G'$ for $i=1,\ldots,k$ such that
+By Theorem \ref{CV2} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and 2-edge-connected multi-subgraphs $F'_i$ of $G'$ for $i=1,\ldots,k$ such that
 		$\sum_{i=1}^{k}\theta_i \chi^{F'_i}\leq g(\2ec)x'$.
@@
 		Note that each $F'_i$ contains at least one copy of every edge in any path $P_f$, except for at most one edge in the path.
-We will obtain 2-edge-connected multigraphs $F_1,\ldots,F_k$ of $G$ using $F'_1,\ldots,F'_k$, respectively.
+We will obtain 2-edge-connected multi-subgraphs $F_1,\ldots,F_k$ of $G$ using $F'_1,\ldots,F'_k$, respectively.
 To obtain $F_i$ first remove all $P_f$ paths from $F'_i$.
@@
 The FDT algorithm for 2EC iteratively applies Lemmas \ref{LPC2EC} and \ref{2ecpruning} to variables $x_1,\ldots,x_t$ to obtain leaf point solutions $L_t$.
-Finally, we just need to apply Lemma \ref{rounddown} to obtain the 2-edge-connected multigraphs from every solution in $L_t$.
+Finally, we just need to apply Lemma \ref{rounddown} to obtain the 2-edge-connected multi-subgraphs from every solution in $L_t$.
 Notice that since $x$ is an extreme point we have $t\leq 2|V|-1$ \cite{boydpulley}.
@@
 We ran FDT on three network design problems: VC, TAP and 2EC.
+
+We implemented the experiments for VC and TAP in Python running on a linux workstation (Ubuntu 18.04.3) with 8 cores of Intel(R) Core(TM) i7-8565U CPU  1.80GHz processors and 1Mb of cache.
+We used the CPLEX 12.9.0.0 solver to solve the pyomo LP models.
+The experiments on 2EC are done on a Windows machine and coded in AMPL with CPLEX as the solver.
 \paragraph{FDT on VC instances from (PACE 2019) \cite{PACE}.}
@@
 We ran binary FDT on a set of 264 fractional extreme points of randomly generated instances of $\tap$.
-Table \ref{tableTAP} shows FDT found solutions better than the integrality-gap lower bound for most instances.
+\cindy{How big were the trees?
+And how many candidate links?} Table \ref{tableTAP} shows FDT found solutions better than the integrality-gap lower bound for most instances.
 
@@
 This formulation allows the instance specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$.
-Recall that a Carr-Vempala point consists of a Hamiltonian cycle of fractional edges.
-Figure \ref{fdtvschris} shows FDT's solutions on all Carr-Vempala points defined on graphs with 10 vertices are always better than those from the polyhedral version of Christofides' algorithm.
+Recall that a Carr-Vempala point consists of a signle cycle of fractional edges.
+Figure \ref{fdtvschris} shows FDT's solutions on all Carr-Vempala points that have 10 vertices on the cycle formed by fractional edges.
+We show for these points the apporoximation factor provided by FDT is always better than those from the polyhedral version of Christofides' algorithm.
 In more details, in Figure \ref{fdtvschris} the horizontal axis of the plot is indexed with the 60 Carr-Vempala points that we considered.
@@
 	\includegraphics[width=9cm,scale=1.4]{"fdt-vs-christofides".png}
-	\caption{Polyhedral version of Christofides' algorithm vs FDT on all Carr-Vempala points defined on graphs with 10 vertices.}
+	\caption{Polyhedral version of Christofides' algorithm vs FDT on all Carr-Vempala points that have 10 vertices on the single cycle formed by fractional edges.}
 	\label{fdtvschris}

### 2020-06-12 FDT2020/FDT.tex
Adding required Sandia line (necessary to pass internal review), making a section a subsection, etc

@@
 \and \textsc{Arash Haddadan}\thanks{Carnegie Mellon University  {\tt{ahaddada@andrew.cmu.edu}}.}
-\and \textsc{Cynthia A. Phillips}\thanks{Sandia National Laboratories  {\tt{caphill@sandia.gov}}.}}
+\and \textsc{Cynthia A.
+Phillips}\thanks{Sandia National Laboratories  {\tt{caphill@sandia.gov}}.
+Sandia National Laboratories is a multi-mission laboratory managed and operated by National Technology and Engineering Solutions of Sandia, LLC., a wholly owned subsidiary of Honeywell International, Inc., for the U.S.
+Department of Energy’s National Nuclear Security Administration under contract DE-NA0003525.}}
 

### 2020-06-12 FDT2020/Introduction.tex
Adding required Sandia line (necessary to pass internal review), making a section a subsection, etc
Work on introduction

@@
 }\fi
-\cindy{TODO: remove ``recall that'' for anything we haven't already defined in this paper.
-Even though it's likely anyone reading this will care about IPs and integrality gaps, we should not assume they already know things we define the way we define them.}
 
 \section{Introduction}
-In this paper we focus on finding solutions to general Integer Linear Programs (IP).
-Integer Programming (and more generally Mixed Integer Linear Programming) can be used to model many practical optimization problems including scheduling, logistics and resource allocation.
+In this paper we focus on finding feasible solutions to binary Integer Linear Programs (IP).
+Informally, an integer program is the optimization of a linear objective function subject to linear constraints, where the variables must take integer values.
+Binary variables represent yes/no decisions.
+Integer Programming (and more generally Mixed Integer Linear Programming (MILP)) can model many practical optimization problems including scheduling, logistics and resource allocation.
+It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}.
+However, there is substantial research into finding a feasible, provably-good approximate, and even (computationally) provably optimal solutions to specific IP instances.
+\cindy{TODO: probably need to informally distinguish between a IP for a general problem, and a specific instance when the parameters are set.}
 
-A common approach to Integer programming is considering their linear relaxation.
-For problems such as the \textsc{Minimum Cost Spanning Tree Problem} there are linear programming relaxations whose basic feasible solutions coincide with  integral solutions, i.e.
+A major tool for finding feasible solutions is the {\em linear-programming (LP) relaxation} for the instance.
+This is a new problem created by relaxing the integrality constraints for an IP instance, allowing the variables to take continuous (rational) values.
+Linear programs can be solved in polynomial time.
+The objective value of the linear programming relaxation provides a bound (lower bound for a minimization problem and upper bound for a maximization problem) on the optimal solution to the IP instance.
+The solutions can also provide some useful global structure, even though the fractional values might not be directly meaningful.
+
+{\em LP-based approximation algorithms} use LP relaxations to find provably good approximate feasible solutions to IP problems in polynomial time.
+At the highest level, they involve solving the LP relaxation, using special structure from the problem to find a feasible solution, and proving that the objective value of the solution is no more than $C$ times worse than the bound from the LP relaxation.
+The approximation factor $C$ can be a constant or depend on the input parameters of the IP, e.g.
+$O(\log(n))$ where $n$ is the number of variables in the formulation of the IP (the dimension of the problem).
+
+There is an inherent limit to how small $C$ can be for a given IP.
+The integrality gap for an IP instance is the ratio of the best integer solution to the best solution of the LP relaxation.
+Any LP-based approximation cannot have an approximation factor $C$ smaller than the integrality gap because there is no feasible solution with an objective value better than a factor of $C$ worse than the optimal solution of the LP relaxation.
+
+If the integrality gap for an IP formulation is large, it is sometimes possible to add families of constraints to the formulation to reduce the integrality gap.
+These constraints are redundant for the integer problem, but can make some fractional solutions no longer feasible for the LP.
+These families of constraints (cuts) can have exponential size as long as we can provide a polynomial-time separation algorithm.
+\cindy{To be self contained, we can add a few sentences about separation, but under the current time pressure, I won't for now.}
+
+Reducing the integrality gap of an IP formulation has two advantages.
+It can lead to better LP-based approximation algorithm bounds as described above.
+It can also help exact solvers run faster or solve instances it could not before.
+Exact IP solvers are based on intelligent branch-and-bound strategies.
+Commercial and open-source MILP solvers can find exact solutions (or near-optimal solutions with a provable bound) to many specific instances of NP-hard combinatorial optimization problems.
+These solvers use the LP relaxation to get lower bounds (for minimization problems).
+The worst-case exponential search is practically feasible when the solver can prune large amounts of the search space.
+This happens when the lower bound for a problem is worse than the value of a known feasible solution.
+This requires a way to find good heuristic solution and it requires good lower bounds that are as close to the actual optimal value of an IP subproblem as possible.
+
+In this paper, we give a method to find feasible solutions for IPs if the integrality gap is bounded.
+The method is also a tool for evaluating the integrality gap for a formulation.
+Researcher can use it to determine whether they should expend effort to find new classes of cuts.
+They can also use it to help guide theory for finding tighter bounds on the integrality gap for classic problems like the traveling salesman problem.
+
+% A common approach to Integer programming is considering their linear relaxation.
+For some problems such as the \textsc{Minimum Cost Spanning Tree Problem} there are linear programming relaxations whose basic feasible solutions coincide with  integral solutions, i.e.
 spanning trees.
-For other problems the value of the linear programming relaxation provides a bound (lower bound for a minimization problem and upper bound for a maximization problem) on the optimal solution.
-A common and successful approach is to round these (potentially) fractional solutions into integer solutions for the optimization problem at hand.
+
+%A common and successful approach is to round these (potentially) fractional solutions into integer solutions for the optimization problem at hand.
 The Integrality gap of a linear relaxation of an integer programming problem is the worst case ratio between the objective values of the discrete problem and the continuous problem.
-Equivalently, the integrality gap of the linear programming relaxation is a limit to the rounding approach: rounding a fractional solution into an integer solution incurs
-a multiplicative cost proportional to the integrality gap.
-In this dissertation we study integrality gaps for different combinatorial optimization problems and introduce new rounding algorithms that imply bounds on their respective integrality gaps.
+Equivalently, the integrality gap of the linear programming relaxation is a limit to the rounding approach: rounding a fractional solution into an integer solution incurs a multiplicative cost proportional to the integrality gap.
+In this paper we study integrality gaps for different combinatorial optimization problems and introduce new rounding algorithms that imply bounds on their respective integrality gaps.
 
@@
 \end{equation}
-Let $I=(A,b)$ denote an instance.
-Then $S(I)$ and $P(I)$ denote $S(A,b)$ and $P(A,b)$, respectively.
-Given a linear objective function $c$, an IP is $\min \;\{cx:\; x \in S(I)\}$.
-It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}.
-However, intelligent branch-and-bound strategies allow commercial and open-source MILP solvers to give exact solutions (or near-optimal solutions with a provable bound) to many specific instances of NP-hard combinatorial optimization problems.
+Let $I=(A,b)$ denote an instance. Then $S(I)$ and $P(I)$ denote $S(A,b)$ and $P(A,b)$, respectively. Given a linear objective function $c$, an IP is $\min \;\{cx:\; x \in S(I)\}$.
 
@@
 The optimal value of this linear program (LP), denoted $z_{\lp}(I,c)$, is a lower bound on the optimal value for the IP, denoted $z_{\IP}(I,c)$.
-The solutions can also provide some useful global structure, even though the fractional values might not be directly meaningful.
 
 Many researchers (see \cite{davids,vazirani}) have developed polynomial time LP-based approximation algorithms that find solutions for special classes of IPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$.
-The approximation factor $C$ can be a constant or depend on the input parameters of the IP, e.g.
-$O(\log(n))$ where $n$ is the number of variables in the formulation of the IP (the dimension of the problem).
 However, for many combinatorial optimization problems there is a limit to such techniques based on LP relaxations, represented  by the {integrality gap} of the IP formulation.
@@
 
-\section{Contributions of this paper}
+\subsection{Algorithms and Theory Contributions}
 

### 2020-06-12 FDT2020/Introduction.tex
quick edit

@@
 % A common approach to Integer programming is considering their linear relaxation.
+\cindy{TODO: this has to move to a logical place, problem in the more formal treatment below.}
 For some problems such as the \textsc{Minimum Cost Spanning Tree Problem} there are linear programming relaxations whose basic feasible solutions coincide with  integral solutions, i.e.
@@
 }\fi 
-The set of feasible points for a pure IP (henceforth IP) is the set
+We now describe IPs and our methods more formally. The set of feasible points for a pure IP (henceforth IP) is the set
 \begin{equation}

### 2020-06-12 FDT2020/main-section.tex
arxiv version

@@
 
+We compared Dive FDT (Algorithm \ref{FDT-dive}) with feasbility pump \cite{fp1} in the terms of time spent solving LP relaxations and the quality of solution provided by each algorithm.
+The results are presented in Figure \ref{fpvsfdt}.
+
+\begin{figure}[h!]
+\begin{subfigure}{.5\textwidth}
+\centering
+	\includegraphics[width=8cm,scale=1]{"fpvsfdt".png}
+	\caption{Dive FDT vs feasbility pump on the instances of PACE 2019 \cite{PACE} with 200 vertices.}
+	\label{fpvsfdt}
+	\end{subfigure}
+	$\quad\;$
+	\begin{subfigure}{.5\textwidth}
+	\centering
+	\includegraphics[width=8cm,scale=1]{"fjvsfdt".png}
+	\caption{FDT vs the 2-approximation for TAP\cite{FJ81} on randomly generated extreme points of the cut-LP.}
+	\label{fjvsfdt}
+	\end{subfigure}
+	\caption{Computational experiments with the FDT algorithm}
+	\label{fdtcomp}
+\end{figure}
 \paragraph{FDT on randomly generated instances of TAP.}
@@
 
-We know $\frac{3}{2}\leq g(\tap)\leq 2$~\cite{FJ81,32gaptap}.
-Notice that $\min_{x\in \tap(T,L)}cx$ is a binary IP.
-We ran binary FDT on a set of 264 fractional extreme points of randomly generated instances of $\tap$.
-\cindy{How big were the trees?
-And how many candidate links?} Table \ref{tableTAP} shows FDT found solutions better than the integrality-gap lower bound for most instances.
+We know $\frac{3}{2}\leq g(\tap)\leq 2$~\cite{FJ81,32gaptap}. Notice that $\min_{x\in \tap(T,L)}cx$ is a binary IP. 
+We considered full binary trees with 3 to 7 levels.
+We assume the set of links to be the set of all pairs of leaves of the trees and we choose the costs of the links uniformly at random.
+We then ran binary FDT and chose the solution that is gives the minimum cost.
+We then compared it with the circulation-based 2-approximation algorithm of Frederickson and Ja'Ja' \cite{FJ81} in Figure \ref{fjvsfdt}.
 
@@
 		\centering
-		\begin{tabular}{c c c c c}
+		\begin{tabular}{c c c c}
 			\hline
-			& $C\in [1.1,1.2]\;$ & $\;C\in (1.2,1.3]\;$ &
-			$\;C\in (1.3,1.4]$ &\; $C\in (1.4,1.5]\;$ \\ \hline
-			TAP & $36$ & $66$ & $170$ & $10$\\  \hline \\
-		\end{tabular}\caption{The scale factor $C$ for FDT run on 264 randomly generated TAP instances with fractional extreme points: 138 instances have $74$ variables.
-The rest have $250$.} \label{tableTAP}
+			& number of edges in $T$ & number of links in $L$ & number of instances $(T,L)$\\ \hline
+			 & $6$ & $6$ & $100$ \\ 
+			 & $14$ & $28$ & $100$ \\ 
+			 & $30$ & $120$ & $100$ \\
+			 & $62$ & $496$ & $100$ \\ 
+			  & $126$ & $2016$ & $50$ \\  \hline \\
+		\end{tabular}\caption{Summary of the randomly generated instances of TAP.} \label{tableTAP}
 	\end{small}
-
 \end{table}
-
+For all these 450 fractional extreme points of the cut-LP our experiments showed that the integrality gap $g(\tap)$ is at most $\frac{3}{2}$ when restricted to the instances considered.
+In fact, only for one instance the upper bound we provided by our experiment is at $\frac{3}{2}$.
+For 425 instances, the upper bound is $\frac{4}{3}$, for 22 instances it is $\frac{6}{5}$, for 2 instances it is $\frac{8}{7}$.
 \paragraph{Computational comparison between Christofides' algorithm and FDT for 2EC on Carr-Vempala points.}
@@
 	\centering
-	\includegraphics[width=9cm,scale=1.4]{"fdt-vs-christofides".png}
+	\includegraphics[width=9cm,scale=1.4]{christofides-vs-fdt.png}
 	\caption{Polyhedral version of Christofides' algorithm vs FDT on all Carr-Vempala points that have 10 vertices on the single cycle formed by fractional edges.}

### 2020-06-18 FDT2020/main-section.tex
Couple of minor edits

@@
 In this section, in an attempt to extend FDT to \{0,1,2\} problems we introduce an FDT algorithm for a 2-edge-connected multi-subgraph problem.
-Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multi-subgraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edge in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2.
-Recall that in the 2EC, we are given non-negative costs on the edges of $G$ and the goal is to find the minimum cost 2-edge-connected multi-subgraph of $G$.
+Given a graph $G=(V,E)$ a multi-subset of edges $F$ of $G$ is a 2-edge-connected multi-subgraph of $G$ if for each set $\emptyset\subset U \subset V$, the number of edges in $F$ that have one endpoint in $U$ and one not in $U$ is at least 2.
+In 2EC, we are given non-negative costs on the edges of $G$ and the goal is to find the minimum cost 2-edge-connected multi-subgraph of $G$.
 We want to prove Theorem \ref{FDT2EC}.

### 2020-08-02 FDT2020/Introduction.tex
Mostly updates to the introduction, removal of comments, suggestion for a conclusion

@@
 
-\cindy{An original comment: There's material in this section (e.g.
+%\cindy{An original comment:
+%There's material in this section (e.g.
 general discussion of combintatorial optimization) that's likely unnecessary for the journal paper.
 We probably want to start with what is now Section 2, but have some opening introduction giving the big picture.
-Remember when we first mention rounding to be clear this is not numerical rounding.
+%Remember when we first mention rounding to be clear this is not numerical rounding.
 TODO: Add English statement for things currently only given in math.
@@
 It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}.
+Given its practical importance, however, there are many commercial (e.g.
+CPLEX, GUROBI, XPRESS) and free (e.g.
+CBC) solvers that for specific IP instances can often find solutions that are optimal within a given tolerance.
+Still we have formulated moderate-sized IP instances that no commercial solver can currently solve.
+Thus there is value in heuristics to find feasible solutions for general IP instances (see e.g.~\cite{HanafiT2017}).
+
+\iffalse
 However, there is substantial research into finding a feasible, provably-good approximate, and even (computationally) provably optimal solutions to specific IP instances. 
+There is substantial research into finding a feasible, provably-good approximate solution for TODO, and even (computationally) provably optimal solutions to specific IP instances.
 \cindy{TODO: probably need to informally distinguish between a IP for a general problem, and a specific instance when the parameters are set.}
+\fi
 
-A major tool for finding feasible solutions is the {\em linear-programming (LP) relaxation} for the instance.
+A major tool for finding feasible solutions for discrete optimization problems expressed as IPs is the {\em linear-programming (LP) relaxation} for the IP formulation.
 This is a new problem created by relaxing the integrality constraints for an IP instance, allowing the variables to take continuous (rational) values.
@@
 These constraints are redundant for the integer problem, but can make some fractional solutions no longer feasible for the LP.
-These families of constraints (cuts) can have exponential size as long as we can provide a polynomial-time separation algorithm.
-\cindy{To be self contained, we can add a few sentences about separation, but under the current time pressure, I won't for now.}
+These families of constraints (cuts) can have exponential size (number of constraints) as long as we can provide a polynomial-time separation algorithm.
+A separation algorithm for a family of constraints takes an optimal solution to an LP instance that explicitly enforces only a (potentially empty) subset of the family.
+It either confirms that all constraints are satisfied or returns a most violated constraint.
+Thus one can add this constraint and repeat at most a polynomial number of times until all are satisfied.
 
@@
 Exact IP solvers are based on intelligent branch-and-bound strategies.
-Commercial and open-source MILP solvers can find exact solutions (or near-optimal solutions with a provable bound) to many specific instances of NP-hard combinatorial optimization problems.
+As mentioned above, commercial and open-source MILP solvers can find exact solutions (or near-optimal solutions with a provable bound) to many specific instances of NP-hard combinatorial optimization problems.
 These solvers use the LP relaxation to get lower bounds (for minimization problems).
-The worst-case exponential search is practically feasible when the solver can prune large amounts of the search space.
-This happens when the lower bound for a problem is worse than the value of a known feasible solution.
-This requires a way to find good heuristic solution and it requires good lower bounds that are as close to the actual optimal value of an IP subproblem as possible.
+The search requires exponential time in the worst case.
+But this search is practically feasible when the solver can prune large amounts of the search space.
+This happens when the lower bound for a region of the search space (subproblem) is worse than the value of a known feasible solution.
+This requires a way to find a good heuristic solution and it requires good lower bounds that are as close to the actual optimal value of an IP subproblem as possible.
 
@@
 % A common approach to Integer programming is considering their linear relaxation.
-\cindy{TODO: this has to move to a logical place, problem in the more formal treatment below.}
-For some problems such as the \textsc{Minimum Cost Spanning Tree Problem} there are linear programming relaxations whose basic feasible solutions coincide with  integral solutions, i.e.
-spanning trees.
+% \cindy{TODO: this has to move to a logical place in the more formal treatment below:
+%For some problems such as the \textsc{Minimum Cost Spanning Tree Problem} there are linear programming relaxations whose basic feasible solutions coincide with  integral solutions, i.e.
+spanning trees.}
 
@@
 \begin{equation}
-S(A,b)= \{x\in \mathbb{Z}^{n}\;:\; Ax\geq b\}  \label{S}.
+S(A,b)= \{x\in \mathbb{Z}^{n}\;:\; Ax\geq b\}  \label{S},
 \end{equation}
+where matrix $A$ of rationals has $m$ constraints on $n$ variables and $b \in \mathbb{R}^{m}$.
 If we drop the integrality constraints, we have the linear relaxation of set $S(A,b)$,
@@
 Many researchers (see \cite{davids,vazirani}) have developed polynomial time LP-based approximation algorithms that find solutions for special classes of IPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$.
-However, for many combinatorial optimization problems there is a limit to such techniques based on LP relaxations, represented  by the {integrality gap} of the IP formulation.
-The integrality gap $g(I)$ for instance $I$ is defined to be $g(I)= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}$.
-\cindy{Does the integrality gap always require positive objective coefficients?
+If the analysis uses the LP bound to prove the approximation quality, then $C$ is at least the integrality gap.
+%However, for many combinatorial optimization problems there is a limit to such techniques based on LP relaxations, represented  by the {integrality gap} of the IP formulation.
+\begin{definition}
+The integrality gap $g(I)$ for instance $I$ is: $$g(I)= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)},$$
+where $z_{IP}(I,c)$ is the optimal solution to the integer program and $z_{LP}(I,c)$ is the solution to the linear-programming relaxation.
+\end{definition}
+\cindy{I'm not sure I got an answer for this, so I'll just make it clear this is the definition we use: Does the integrality gap always require positive objective coefficients?
 Or is that an extra restriction in our definition?
-Is there a reference that has that restriction?}  For example consider the minimum cost 2-edge-connected multi-subgraph problem (2EC): Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected multi-subgraph of $G$.
+Is there a reference that has that restriction?}
+For example consider the minimum cost 2-edge-connected multi-subgraph problem (2EC): Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected subgraph of $G$, with multiedges allowed.
+A graph is 2-edge-connected if there are at least two edge-disjoint paths between every pair of vertices.
 A linear programming relaxation for this problem known as the subtour elimination relaxation  is
- \begin{equation}\min \{cx: \sum_{e\in \delta(U)}x_e \geq 2 \mbox{ for } \emptyset \subsetneq U \subsetneq V,\; x\in [0,2]^{E}\}. 
+ \begin{equation}\min \{cx: \sum_{e\in \delta(U)}x_e \geq 2 \mbox{ for } \emptyset \subsetneq U \subsetneq V,\; x\in [0,2]^{E}\}, 
  \end{equation}
+where $\delta(U)$ for vertex subset $U$ is the set of edges that cross the cut defined by $U$.  That is, each $e \in \delta(U)$ has one endpoint in $U$ and the other endpoint in $V-U$.
  In this case the instance-specific integrality gap is the integrality gap of the subtour-elimination relaxation for the 2EC on graph with $n$ vertices.
-\cindy{We might need to define the problem or have a forward pointer.} \arash{See above}.
 Alexander et al.
-\cite{alexander2006integrality} showed the instance-specific integrality gap of the subtour elimination relaxation for the 2EC for instances of the problem with $n= 10$ is at most $\frac{7}{6}$.
+\cite{alexander2006integrality} showed this instance-specific integrality gap
+%of the subtour elimination relaxation for the 2EC
+is at most $\frac{7}{6}$ for instances with $n= 10$ .
 
@@
 \end{equation}
-For example, the aforementioned integrality gap of the subtour elimination relaxation for the 2EC is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}.
-Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation.
+For example, the integrality gap of the subtour elimination relaxation for the 2EC is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}.
+Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation to bound the quality of a feasible solution.
 
 Our methods apply theory connecting integrality gaps to sets of feasible solutions.
-Instances $I$ with  $g(I)=1$ has $P(I)=\conv(S(I))$, the convex hull of the lattice of feasible points.
+Instances $I$ with $g(I)=1$ have $P(I)=\conv(S(I))$, the convex hull of the lattice of feasible points.
 In this case, $P(I)$ is an \textit{integral} polyhedron.
 The spanning tree polytope of graph $G$, $\st(G)$, and the perfect-matching polytope of graph $G$, $\permat(G)$, have this property (\cite{Edmonds2003,edmondsPM}).
-For such problems there is an algorithm to express vector $x\in P(I)$ as a convex combination of points in $S(I)$ in polynomial time \cite{cons-cara}.
-\cindy{Should this proposition just be a corollary of the Carr-Vempala theorem?  Are we going to describe how to do it?  If so, there should be a forward pointer to that discussion.}
+Thus the linear-programming relaxation for minimum-cost spanning tree has basic feasible solutions (vertices) that are integral solutions, i.e.
+spanning trees.
+For such problems there is an algorithm to express vector $x\in P(I)$ (a feasible LP solution) as a convex combination of points in $S(I)$ (feasible IP solutions) in polynomial time \cite{cons-cara}.
+% The number of feasible solutions ($k$) in the convex combination can vary by instance.
+%\cindy{Should this proposition just be a corollary of the Carr-Vempala theorem?  Are we going to describe how to do it?  If so, there should be a forward pointer to that discussion.}
 
-\arash{not exactly: Carr-Vempala don't give a construction.
+%\arash{not exactly: Carr-Vempala don't give a construction.
 The proposition below is a result of constructive version of Carathedory's theorem which I think is implied by the Ellipsoid algorithm, but there are even faster versions of it.
@@
 \begin{proposition}\label{cara}
-	If $g(I)=1$, then for $x\in P(I)$ there exists $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in S(I)$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$.
+	If $g(I)=1$, then for $x\in P(I)$ there exists a positive integer $k$ and $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in S(I)$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$.
 Moreover, we can find such a convex combination in polynomial time.
@@
 An equivalent way of describing Proposition \ref{cara} is the following Theorem of Carr and Vempala \cite{Carr2004}.
+The {\em dominant} of $P(I)$, which we denote by $\dom(P(I))$, is the set of points $x'$ such that there exists a point $x\in P$ with $x'\geq x$ in every component.
+A polyhedron is of \textit{blocking type} if it is equal to its dominant.
 
@@
 \end{thm}
-We denote by $\dom(P(I))$ the set of points $x'$ such that there exists a point $x\in P$ with $x'\geq x$, also known as the dominant of $P(I)$.
-A polyhedron is of \textit{blocking type} if it is equal to its dominant.
-Theorem \ref{CV2} was first introduced by Goemans \cite{goemansblocking} for blocking type polyhedra.
-While there is an exact algorithm for problems with gap $1$ as stated in Proposition \ref{cara}, Theorem~\ref{CV2} is existential, with no construction.
+Goemans \cite{goemansblocking} first introduced Theorem \ref{CV2} for blocking-type polyhedra.
+While there is an exact algorithm for problems with gap $1$, as stated in Proposition \ref{cara}, Theorem~\ref{CV2} is existential, with no construction.
 %In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
@@
 \fi
-To study integrality gaps, we wish to find such a solution constructively: assuming reasonable complexity assumptions, a specific problem $\mathcal{I}$ with  $1<g(\mathcal{I})<\infty$, and $x\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in S(I)$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ in polynomial time?
+To study integrality gaps, we wish to decompose a suitably scaled linear-programming solution into a convex combination of feasible integer solutions {\bf constructively}.
+That is, we ask: assuming reasonable complexity assumptions, given a specific problem $\mathcal{I}$ with  $1<g(\mathcal{I})<\infty$, and $x\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in S(I)$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ in polynomial time?
 We wish to find the smallest factor $C$ possible.
@@
 We give a general approximation framework for solving binary IPs.
-Consider the set of point described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively.
-Assume in addition that $S(I),P(I)\subseteq [0,1]^n$.
-\cindy{State somewhere that we can allow continuous variables as long as they are not in the objective function.
-(We will explain later how to extend to this case).} For a vector $x\in \mathbb{R}_{\geq 0}^n$ such that $x\in P(I)$, let $\spp(x)= \{i \in [n]: x_i \neq 0\}$.
+Consider the set of points described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume in addition that $S(I),P(I)\subseteq [0,1]^n$.
+\cindy{Is it $S(I) \subseteq \{0,1\}^n$}
+For a vector $x\in \mathbb{R}_{\geq 0}^n$ such that $x\in P(I)$, let the {\em support} of $x$ be $\spp(x)= \{i \in [n]: x_i \neq 0\}$.
 For an integer $\beta$ let $\{\beta\}^n$ be the vector $y\in \mathbb{R}^n$ with $y_i=\beta$ for $i\in [n]$.
 
-We introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which is a polynomial-time algorithm that given a point $x\in P(I)$ produces a convex combination of feasible points in $S(I)$ that are dominated by a ``factor" $C$ of $x$ in the coordinates corresponding to $x$.
+We introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which runs in polynomial time algorithm.
+Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated by a ``factor" $C$ of $x$ in the coordinates corresponding to $x$.
 If $C = g(I)$, it would be optimal.
@@
 The integrality gap of this formulation is exactly 2 \cite{davids}.
-\cindy{Move to active voice once we have an actual reference for this.} \arash{I guess we can site a general approx book,} It is shown that it is UG-hard to approximte VC within any factor sctrictly better than 2 \cite{UGhardVC}.
-\cindy{We compare to small instances} We compare  FDT and the feasbility pump heuristic \cite{fp1} on the the small instances of PACE 2019\footnote{ Parameterized Algorithms and Computational Experiments Challenge 2019: \url{https://pacechallenge.org/2019/}} challenge test cases \cite{PACE}.
+Austrin, Khot and Safra~\cite{UGhardVC} show that it is UG-hard to approximte VC within any factor sctrictly better than 2.
+We compare  FDT and the feasbility pump heuristic \cite{fp1} on the small instances of PACE\footnote{ Parameterized Algorithms and Computational Experiments: \url{https://pacechallenge.org/2019/}} 2019 challenge test cases \cite{PACE}.
 \subsubsection{Tree augmentation problem}
@@
 The integrality gap of the cut-LP is known to be between $\frac{3}{2}$ \cite{32gaptap} and $2$ \cite{FJ81}.
-We create random fractional extreme points of the cut-LP and round them using FDT.
-For the instances that we create the blow-up factor is always below $\frac{3}{2}$ providing an upper bound for such instances.
+We create random fractional extreme points of the cut-LP and apply FDT to find integral solutions.
+For the instances that we create, the blow-up factor is always below $\frac{3}{2}$ providing an upper bound for such instances.
 
@@
 A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$.
-\cindy{I am having a hard time parsing the next sentence.
-Is there supposed to be a value for $g(\2ec)$ for this case?}\arash{There was a missing word.
-How about now?} Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point.
+Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point.
 We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges.

### 2020-08-02 FDT2020/main-section.tex
Mostly updates to the introduction, removal of comments, suggestion for a conclusion

@@
 The value of the second data point depicted by a cross on the vertical axis is $C$ where $C$ is obtained from applying Theorem \ref{FDT2EC} to $x$.
-In other words, Figure \ref{fdtvschris} is comparing the upper bounds on the instances specific integrality gap certified by Christofides' algorithm  and FDT algorithm for 2EC.
+In other words, Figure \ref{fdtvschris} is comparing the instance-specific upper bound on integrality gap certified by Christofides' algorithm to the approximation factor of the FDT algorithm for 2EC.
 
@@
 \end{table}
+
+\cindy{
+Most papers have a ``discussion and conclusions'' section.
+It doesn't have to be long and it doesn't have to repeat the paper contributions said before.
+It can include extensions or thoughts/discussions that don't easily fit into the main body.
+It can include new insights into the value of work now that the reader understands it better.
+Here are some thoughts about what could go there:
+1) Bob was quite insistent at one point that we describe how to extend to continuous variables as long as they are not in the objective function.
+Can we state that in a conclusion and very briefly summarize what would change for this case?
+2) Open questions/future research.
+Any thoughts on open theory questions?
+Experimental questions would include doing a more high-performance version (e.g.
+in C or C++) to run on larger instances, and a more comprehensive set of experiments to determine on what kind of problems FDT is likely to outperform other general heuristics.
+3) TODO: more after I have gone all the way through.
+}

### 2020-08-02 FDT2020/Introduction.tex
More addition of careful definitions, removal of redundancy, etc.

@@
 Integer Programming (and more generally Mixed Integer Linear Programming (MILP)) can model many practical optimization problems including scheduling, logistics and resource allocation.
+
 It is  NP-hard even to determine if an IP instance has a feasible solution~\cite{GareyJohnson}.
@@
 Thus there is value in heuristics to find feasible solutions for general IP instances (see e.g.~\cite{HanafiT2017}).
+%For a generic IP instance $I$ it is NP-hard to even decide if the set of feasible solutions $S(I)$ is empty or not.
+%There are a number of heuristics for this purpose, such as the
+These heuristics, such as the popular Feasibility pump algorithm \cite{fp1,fp2}, are often effective and fast in practice.
+However, the heuristics can sometimes fail to find a feasible solution.
+Moreover, these heuristics do not provide any bounds on the quality of the solution they find.
 
@@
 %However, for many combinatorial optimization problems there is a limit to such techniques based on LP relaxations, represented  by the {integrality gap} of the IP formulation.
+\cindy{Arash: Just read and comment it out if you're OK with this.
+I'm not sure I got an answer for the following questions, so I'll just make it clear this is the definition we use: Does the integrality gap always require positive objective coefficients?
+Or is that an extra restriction in our definition?
+Is there a reference that has that restriction?}
 \begin{definition}
@@
 \end{definition}
-\cindy{I'm not sure I got an answer for this, so I'll just make it clear this is the definition we use: Does the integrality gap always require positive objective coefficients?
-Or is that an extra restriction in our definition?
-Is there a reference that has that restriction?}
-For example consider the minimum cost 2-edge-connected multi-subgraph problem (2EC): Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected subgraph of $G$, with multiedges allowed.
+
+For example consider the minimum cost \textsc{2-edge-connected multi-subgraph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected subgraph of $G$, with multiedges allowed.
 A graph is 2-edge-connected if there are at least two edge-disjoint paths between every pair of vertices.
-A linear programming relaxation for this problem known as the subtour elimination relaxation  is
+A linear programming relaxation for this problem, known as the {\em subtour-elimination} relaxation, is
  \begin{equation}\min \{cx: \sum_{e\in \delta(U)}x_e \geq 2 \mbox{ for } \emptyset \subsetneq U \subsetneq V,\; x\in [0,2]^{E}\}, 
+ \label{eq:subtour}
  \end{equation}
@@
 Consider the set of points described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume in addition that $S(I),P(I)\subseteq [0,1]^n$.
-\cindy{Is it $S(I) \subseteq \{0,1\}^n$}
+\cindy{Is it $S(I) \subseteq \{0,1\}^n$?}
 For a vector $x\in \mathbb{R}_{\geq 0}^n$ such that $x\in P(I)$, let the {\em support} of $x$ be $\spp(x)= \{i \in [n]: x_i \neq 0\}$.
@@
 We introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which runs in polynomial time algorithm.
-Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated by a ``factor" $C$ of $x$ in the coordinates corresponding to $x$.
-If $C = g(I)$, it would be optimal.
-However we can only guarantee a factor of $g(I)^{|\spp(x)|}$.
-FDT relies on iteratively solving linear programs that are about the same size as the description of $P(I)$.
+Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated coordinatewise by a ``factor" $C$ times $x$.
+% in the coordinates corresponding to $x$.
+If $C = g(I)$, it would be optimal. However we can only guarantee a factor of $g(I)^{|\spp(x)|}$. FDT iteratively solves linear programs that are about the same size as the description of $P(I)$.
 
@@
 
-For a generic IP instance $I$ it is NP-hard to even decide if the set of feasible solutions $S(I)$ is empty or not.
-There are a number of heuristics for this purpose, such as the feasibility pump algorithm \cite{fp1,fp2}.
-These heuristics are often very effective and fast in practice, however, they can sometimes fail to find a feasible solution.
-Moreover, these heuristics do not provide any bounds on the quality of the solution they find.
-
-Here is how the FDT algorithm works in a high level: in iteration $i$ the algorithm maintains a convex combination of  vectors in $\mathcal{D}(L(I))$ that have a 0 or 1 value for coordinates indexed $0,\ldots,i-1$.
-Let $y$ be a vector in the convex combination in iteration $i$ of the algorithm.
-We solve a linear programming problem that gives us $\theta\in [0,1]$ and $y^0,y^1\in \mathcal{D}(L(I))$ such that $g(I) y\geq \theta_1y^0 + (1-\theta) y^1$ and $y^0_i=0$ and $y^1_i=1$.
+\cindy{Arash, please check how I defined $L(I)$.  It was not defined before.}
+\cindy{TODO: This implies we know $g(I)$, which is not true in general.
+We should add how we bound/estimate it.
+I'll return to this after putting that detail back in core if you (Arash) haven't added it by then.}
+Here is how the FDT algorithm works at a high level for an instance $I$ with LP feasible region $L(I)$: in iteration $i$ the algorithm maintains a convex combination of  vectors in $\mathcal{D}(L(I))$ that have a 0 or 1 value for coordinates indexed $0,\ldots,i-1$.
+Let $y$ be a vector in the convex combination from iteration $i-1$.
+We solve a linear programming problem that gives us $\theta\in [0,1]$ and $y^0,y^1\in \mathcal{D}(L(I))$ such that $g(I) y\geq \theta y^0 + (1-\theta) y^1$ and $y^0_i=0$ and $y^1_i=1$.
 We then replace $y$ in the convex combination with $\frac{\theta}{g(I)}y^0 +\frac{1-\theta}{g(I)}y^1$.
-Repeating this for every vector in the convex combination from previous iteration yields a convex combination  of points that is ``more'' integral.
-If in any iteration there are too many points in the convex combination we solve a linear programming problem that ``prunes'' the convex combination.
-At the end we find a convex combination of integer solutions $\mathcal{D}(L(I))$.
+Repeating this for every vector in the convex combination from the previous iteration yields a new convex combination of points.
+It is ``more'' integral because now all vectors in the convex combination are integral in their first $i+1$ elements.
+If in any iteration there are too many points in the convex combination,  we solve a linear programming problem that ``prunes'' the convex combination.
+At the end we have a convex combination of integer solutions $\mathcal{D}(L(I))$.
 For each such solution $z$ we invoke the DomToIP algorithm (see Section \ref{domTOIP}) to find $z'\in S(I)$ where $z'\leq z$.
 
-One can extend the FDT algorithm for binary IPs into covering $\{0,1,2\}$ IPs by losing a factor $2^{|\spp(x)|}$ on top of the loss for FDT.
-In order to eradicate this extra factor, we need to treat the coordinate $i$ with $x_i=1$ differently.
-We focus on the \textsc{2-edge-connected multi-subgraph graph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^{E}_{\geq 0}$ find a 2-edge-connected multi-subgraph of $G$ with minimum cost.
-The natural linear programming relaxation for this problem is
-\begin{equation}
-\min \{cx \; : \; x(\delta(U))\geq 2 \; \text{ for }\emptyset \subset U \subset V, \; x\in [0,2]^E\}
-\end{equation}
-We denote the feasible region of this LP by $\subtour(G)$.
-Let $\2ec(G)$ be the convex hull of incidence vectors of 2-edge-connected multi-subgraphs of graph $G$.
+One can extend the FDT algorithm for binary IPs into covering\footnote{A covering IP has nonnegative constraint matrix, objective coefficients and right-hand side ($A,b,c$).} $\{0,1,2\}$ IPs by losing a factor $2^{|\spp(x)|}$ on top of the loss for FDT.
+To eradicate this extra factor, we must treat the coordinate $i$ with $x_i=1$ differently.
+We focus on the 2-edge-connected multi-subgraph graph problem (2EC) defined above.
+It's subtour-elimination LP relaxation is given in (\ref{eq:subtour}).
+%}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^{E}_{\geq 0}$ find a 2-edge-connected multi-subgraph of $G$ with minimum cost. The natural linear programming relaxation for this problem is 
+%\begin{equation}
+%\min \{cx \; : \; x(\delta(U))\geq 2 \; \text{ for }\emptyset \subset U \subset V, \; x\in [0,2]^E\}
+%\end{equation}
+For input graph $G$, let $\subtour(G)$ denote the feasible region of this LP.
+Let $\2ec(G)$ be the convex hull of incidence vectors\footnote{The incidence vector $x$ of a 2-edge-connected multigraph has an element for each edge $e$, with $x_e \in \{0,1,2\}$ indicating the number of times edge $e$ appears in the solution.} of 2-edge-connected multi-subgraphs of graph $G$.
 Following the definition in (\ref{gapproblem}) have
@@
 
-\subsection{Experiments.} Although the bound guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are very large, we show that in practice, the algorithm works very well for network design problems described above.
-We show how one might use FDT to investigate the integrality gap for such well-studied problems.
-\cindy{TODO: forward pointers to the sections with more details.}
+\subsection{Experiments.} Although the bounds guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are large, in Section~\ref{sec:experiment} we show that in practice, the algorithm works well for network design problems like those described above.
+We also show how one might use FDT to investigate the integrality gap for such well-studied problems.
+%\cindy{TODO: forward pointers to the sections with more details.}
 
@@
 
-In the \textsc{minimum vetex cover problem (VC)} we are given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$.
-A subset of $U$ of $V$ is a \textit{vertex cover} if for $e\in E$ at least one endpoint of $e$ is in $U$.
-The goal in VC is to find the minimum cost vertex cover.
+In the \textsc{minimum vertex cover problem (VC)} we are given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$.
+A subset of $U$ of $V$ is a \textit{vertex cover} if for all $e\in E$ at least one endpoint of $e$ is in $U$.
+The goal in VC is to find the minimum-cost vertex cover.
 The linear programming relaxation for VC is
 \begin{equation}
-\min \{cx \; : \; x_u + x_v \geq	 1 \text{ for } e=uv \in E, \; x\in [0,1]^{V}\}.
+\min \{cx \; : \; x_u + x_v \geq	 1 \text{ for all } e=uv \in E, \; x\in [0,1]^{V}\}.
 \end{equation}
 The integrality gap of this formulation is exactly 2 \cite{davids}.
-Austrin, Khot and Safra~\cite{UGhardVC} show that it is UG-hard to approximte VC within any factor sctrictly better than 2.
+Austrin, Khot and Safra~\cite{UGhardVC} show that it is UG-hard to approximate VC within any factor strictly better than 2.
 We compare  FDT and the feasbility pump heuristic \cite{fp1} on the small instances of PACE\footnote{ Parameterized Algorithms and Computational Experiments: \url{https://pacechallenge.org/2019/}} 2019 challenge test cases \cite{PACE}.
+\cindy{TODO: summary of results.
+Something like FDT was 3-5x slower, but still not too long, and almost always had a much lower gap.}
 \subsubsection{Tree augmentation problem}

### 2020-08-02 FDT2020/Introduction.tex
Cindys Intro comments replied

@@
 Is there a reference that has that restriction?}
+\arash{I looked for a formal definition of integrality gap in the literature this is the most descriptive I've found from \cite{davids} as follows: \textit{the integrality gap of an integer program is the worst-case ratio over all instances of the problem of value of an optimal solution to the integer programming formulalation to value of an optimal solution to its linear programming relaxation.}.
+Based on this definition I think we are not adding a restriction but we are looking at specific type of IPs arising form problems whose instances have non-negative cost vectors which is not a huge stretch as most combinatorial optimization problems are of this forms.}
 \begin{definition}
@@
 We give a general approximation framework for solving binary IPs.
-Consider the set of points described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume in addition that $S(I),P(I)\subseteq [0,1]^n$.
-\cindy{Is it $S(I) \subseteq \{0,1\}^n$?}
+Consider the set of points described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume in addition that $S(I)\in \{0,1\}^n$ and $P(I)\subseteq [0,1]^n$.
+%\cindy{Is it $S(I) \subseteq \{0,1\}^n$?}
 For a vector $x\in \mathbb{R}_{\geq 0}^n$ such that $x\in P(I)$, let the {\em support} of $x$ be $\spp(x)= \{i \in [n]: x_i \neq 0\}$.
@@
 I'll return to this after putting that detail back in core if you (Arash) haven't added it by then.}
+\arash{Isn't $P(I)$ the feasible region defined above.
+I keep $L(I)$ for now but we can replace it later if needed.} \arash{I fixed below so that I don't imply we know $g(I)$, we also might to clearly state that somewhere?}
+
 Here is how the FDT algorithm works at a high level for an instance $I$ with LP feasible region $L(I)$: in iteration $i$ the algorithm maintains a convex combination of  vectors in $\mathcal{D}(L(I))$ that have a 0 or 1 value for coordinates indexed $0,\ldots,i-1$.
 Let $y$ be a vector in the convex combination from iteration $i-1$.
-We solve a linear programming problem that gives us $\theta\in [0,1]$ and $y^0,y^1\in \mathcal{D}(L(I))$ such that $g(I) y\geq \theta y^0 + (1-\theta) y^1$ and $y^0_i=0$ and $y^1_i=1$.
-We then replace $y$ in the convex combination with $\frac{\theta}{g(I)}y^0 +\frac{1-\theta}{g(I)}y^1$.
+We solve a linear programming problem that gives us $\theta_0,\theta_1\in [0,1]$ and $y^0,y^1\in \mathcal{D}(L(I))$ such that $y\geq \theta_0 y^0 + \theta^1 y^1$, $\theta_0+\theta_1\leq g(I)$, $y^0_i=0$ and $y^1_i=1$.
+We then replace $y$ in the convex combination with $\frac{\theta_0}{\theta_0+\theta_1}y^0 +\frac{\theta_1}{\theta_0+\theta_1}y^1$.
 Repeating this for every vector in the convex combination from the previous iteration yields a new convex combination of points.

### 2020-08-02 FDT2020/conclusion.tex
conclusion first try and a small change in biblio

\section{Concluding Remarks}

The results in Sections \ref{binaryfdt}, \ref{domTOIP} and \ref{2EC} hold if the intial integer program has soem auxilliary continious variables\footnote{Here by auxilliary variables we mean a variable that does not participate in the objective function}, i.e. when we have 
\begin{equation*}
S(A,b) = \{x\in \mathbb{Z}^n\times \mathbb{R}^p: Ax\geq b\},
\end{equation*}
where the last $p$ variables are continous, $P(A,b) = \{x\in \mathbb{R}^n: Ax\geq b\}$ and define
\begin{equation*}
g(I) = \max_{c\in \mathbb{R}^n_+}\frac{\min_{x\in S(A,b)} \sum_{i=1}^{n}c_ix_i}{\min_{x\in P(A,b)} \sum_{i=1}^{n}c_ix_i},
\end{equation*}
our main results work. In fact out implementation of the subtour elimination formulation is based on an extended formulation with auxiliary variables (see \cite{subtour-extended}). We removed this extension in order to make the presentation simpler.

Fractional Decomposition Tree is a tool to experminetally evaluate the known bounds (and conjectured bounds) on integrality gap of combinatorial optimization problems. We hope that applying this tool to a wide range of problems can be successful in refuting conjectures on the upper bounds of integrality gap or at least narrow down the instances for which a closer look is required for the study of integrality gap.

### 2020-08-02 FDT2020/Introduction.tex
Finished first full careful pass of the introduction.

--- 2020-08-02 FDT2020/Introduction.tex
@@
 
-Many researchers (see \cite{davids,vazirani}) have developed polynomial time LP-based approximation algorithms that find solutions for special classes of IPs whose cost are provably smaller than $C\cdot z_{LP}(I,c)$.
+Many researchers (see \cite{davids,vazirani}) have developed polynomial time LP-based approximation algorithms that find solutions for special classes of IPs whose cost are provably at most $C\cdot z_{LP}(I,c)$ for some (possibly constant) function $C$.
 If the analysis uses the LP bound to prove the approximation quality, then $C$ is at least the integrality gap.
 %However, for many combinatorial optimization problems there is a limit to such techniques based on LP relaxations, represented  by the {integrality gap} of the IP formulation.
-\cindy{Arash: Just read and comment it out if you're OK with this.
+%\cindy{Arash: Just read and comment it out if you're OK with this.
 I'm not sure I got an answer for the following questions, so I'll just make it clear this is the definition we use: Does the integrality gap always require positive objective coefficients?
@@
 Is there a reference that has that restriction?}
+%\arash{I looked for a formal definition of integrality gap in the literature this is the most descriptive I've found from \cite{davids} as follows: \textit{the integrality gap of an integer program is the worst-case ratio over all instances of the problem of value of an optimal solution to the integer programming formulalation to value of an optimal solution to its linear programming relaxation.}.
+Based on this definition I think we are not adding a restriction but we are looking at specific type of IPs arising form problems whose instances have non-negative cost vectors which is not a huge stretch as most combinatorial optimization problems are of this forms.}
 \begin{definition}
@@
 
+In general the integrality gap is defined similarly for any objective function, but we wish to be explicit about the class of problems we assume in this paper.
 For example consider the minimum cost \textsc{2-edge-connected multi-subgraph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected subgraph of $G$, with multiedges allowed.
@@
 where $\delta(U)$ for vertex subset $U$ is the set of edges that cross the cut defined by $U$.  That is, each $e \in \delta(U)$ has one endpoint in $U$ and the other endpoint in $V-U$.
- In this case the instance-specific integrality gap is the integrality gap of the subtour-elimination relaxation for the 2EC on graph with $n$ vertices.
+ In this case the instance-specific integrality gap is the integrality gap of the subtour-elimination relaxation for the 2EC on a graph with $n$ vertices.
 Alexander et al.
@@
 
-The value of $g(I)$ depends on the constraints in (\ref{S}).
+The value of $g(I)$ depends on the constraints in~(\ref{S}).
 We cannot hope to find solutions for the IP with objective values better than $g(I)\cdot z_{LP}(I,c)$.
@@
 
-\cindy{Arash, please check how I defined $L(I)$.  It was not defined before.}
-\cindy{TODO: This implies we know $g(I)$, which is not true in general.
+%\cindy{Arash, please check how I defined $L(I)$.  It was not defined before.}
+%\cindy{TODO: This implies we know $g(I)$, which is not true in general.
 We should add how we bound/estimate it.
 I'll return to this after putting that detail back in core if you (Arash) haven't added it by then.}
-Here is how the FDT algorithm works at a high level for an instance $I$ with LP feasible region $L(I)$: in iteration $i$ the algorithm maintains a convex combination of  vectors in $\mathcal{D}(L(I))$ that have a 0 or 1 value for coordinates indexed $0,\ldots,i-1$.
+%\arash{Isn't $P(I)$ the feasible region defined above.
+I keep $L(I)$ for now but we can replace it later if needed.} \arash{I fixed below so that I don't imply we know $g(I)$, we also might to clearly state that somewhere?}
+
+Here is how the FDT algorithm works at a high level for an instance $I$ with LP feasible region $P(I)$: in iteration $i$ the algorithm maintains a convex combination of  vectors in $\mathcal{D}(P(I))$ that have a 0 or 1 value for coordinates indexed $0,\ldots,i-1$.
 Let $y$ be a vector in the convex combination from iteration $i-1$.
-We solve a linear programming problem that gives us $\theta\in [0,1]$ and $y^0,y^1\in \mathcal{D}(L(I))$ such that $g(I) y\geq \theta y^0 + (1-\theta) y^1$ and $y^0_i=0$ and $y^1_i=1$.
-We then replace $y$ in the convex combination with $\frac{\theta}{g(I)}y^0 +\frac{1-\theta}{g(I)}y^1$.
+We solve a linear programming problem that gives us $\theta_0,\theta_1\in [0,1]$ and $y^0,y^1\in \mathcal{D}(P(I))$ such that $y\geq \theta_0 y^0 + \theta_1 y^1$, $\theta_0+\theta_1\leq g(I)$, $y^0_i=0$ and $y^1_i=1$.
+We then replace $y$ in the convex combination with $\frac{\theta_0}{\theta_0+\theta_1}y^0 +\frac{\theta_1}{\theta_0+\theta_1}y^1$.
 Repeating this for every vector in the convex combination from the previous iteration yields a new convex combination of points.
@@
 If in any iteration there are too many points in the convex combination,  we solve a linear programming problem that ``prunes'' the convex combination.
-At the end we have a convex combination of integer solutions $\mathcal{D}(L(I))$.
+At the end we have a convex combination of integer solutions $\mathcal{D}(P(I))$.
 For each such solution $z$ we invoke the DomToIP algorithm (see Section \ref{domTOIP}) to find $z'\in S(I)$ where $z'\leq z$.
@@
 
-\subsection{Experiments.} Although the bounds guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are large, in Section~\ref{sec:experiment} we show that in practice, the algorithm works well for network design problems like those described above.
+\subsection{Experiments.} Although the bounds guaranteed in both Theorems \ref{binaryFDT} and \ref{FDT2EC} are large, in Section~\ref{sec:experiment} we show that in practice, the algorithm can work well for network design problems like those described above.
 We also show how one might use FDT to investigate the integrality gap for such well-studied problems.
@@
 Austrin, Khot and Safra~\cite{UGhardVC} show that it is UG-hard to approximate VC within any factor strictly better than 2.
-We compare  FDT and the feasbility pump heuristic \cite{fp1} on the small instances of PACE\footnote{ Parameterized Algorithms and Computational Experiments: \url{https://pacechallenge.org/2019/}} 2019 challenge test cases \cite{PACE}.
-\cindy{TODO: summary of results.
-Something like FDT was 3-5x slower, but still not too long, and almost always had a much lower gap.}
+We compare  FDT and the feasbility pump heuristic \cite{fp1} on the small instances of the PACE\footnote{ Parameterized Algorithms and Computational Experiments: \url{https://pacechallenge.org/2019/}} 2019 challenge test cases \cite{PACE}.
+FDT was 3-5x slower, but still ran in seconds.
+It always gave a better vertex cover.
+For some instances the FDT solution's relative gap with respect to the optimal was half that of feasibility pump.
 \subsubsection{Tree augmentation problem}
-In the \textsc{Tree Augmentation Problem (TAP)} we are given a  graph $G=(V,E)$, a spanning tree $T$ of $G$.
-We also have a cost vector $c\in \mathbb{R}^{E\setminus T}_{\geq 0}$.
+In the \textsc{Tree Augmentation Problem (TAP)} we are given a  graph $G=(V,E)$, a spanning tree $T$ of $G$ and a cost vector $c\in \mathbb{R}^{E\setminus T}_{\geq 0}$.
 A subset $F$ of $E\setminus T$ is called a \textit{feasible augmentation} if $(V,T\cup F)$ is a 2-edge-connected graph.
@@
 \end{equation}
-where $\cov(e)$ is set of edges $\ell \in E\setminus T$ such that $e$ is in the unique cycle of $T\cup \{\ell\}$.
-We call the LP above the cut-LP.
-The integrality gap of the cut-LP is known to be between $\frac{3}{2}$ \cite{32gaptap} and $2$ \cite{FJ81}.
-We create random fractional extreme points of the cut-LP and apply FDT to find integral solutions.
-For the instances that we create, the blow-up factor is always below $\frac{3}{2}$ providing an upper bound for such instances.
+where $\cov(e)$ for $e \in T$ is the set of edges $\ell \in E\setminus T$ such that $e$ is in the unique cycle of $T\cup \{\ell\}$.
+Another way to think of $\cov(e)$ is that if we remove edge $e$ from tree $T$, this partitions the vertices into two connected sets $U$ and $V-U$.
+Then $\cov(e) = \delta(U)$ is the set of edges $\ell \neq e$ that cross the cut between $U$ and $V-U$, and whose addition would reconnect the tree.
+We call the LP above the cut LP.
+The integrality gap of the cut LP is known to be between $\frac{3}{2}$ \cite{32gaptap} and $2$ \cite{FJ81}.
+We create random fractional extreme points of the cut LP and apply FDT to find integral solutions.
+For our instances, the ratio of the value of the feasible solution to the LP lower bound is always below $\frac{3}{2}$.
+This provides evidence that the integrality gap for such instances may be less than $\frac{3}{2}$.
 
@@
 
-There are fairly good bounds for the integrality gap for TSP or 2EC.
-Benoit and Boyd \cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices.
+There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP) or 2EC.
+\cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
+Benoit and Boyd~\cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices.
 Alexander et al.
@@
 A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$.
+\cindy{Every pair of vertices on the cycle is connected this way?
+It sounds like that, though I don't recall that being necessary.
+We probably have a figure from an old version we could include if it's not too much trouble.
+This will help reviewers and future readers understand much more easily, especially that there could be far more than 12 vertices in the overall solution.}
 Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point.
 We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges.
+\cindy{This sounds like a contribution of the paper.}
 Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.
+
+\cindy{We probably need an explicit list of contributions.  It could be another subsection of the introduction.  This will help the reviewer and eventually, if published, the reader.}

### 2020-08-03 FDT2020/Introduction.tex
Carr-Vempala point figure added, TSP book reference added, Comments replied

@@
 
-There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP) or 2EC.
+There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP) or 2EC (see \cite{tspbook})
 \cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
@@
 Consider a graph $G=(V,E)$.
-A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$.
+A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$ (see Figure \ref{fig:CVpoint})
 \cindy{Every pair of vertices on the cycle is connected this way?
@@
 This will help reviewers and future readers understand much more easily, especially that there could be far more than 12 vertices in the overall solution.}
+
+\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?}
+
+\begin{figure}
+\centering
+\begin{tikzpicture}[scale=0.4]
+
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (0,-4)};
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(2.83,2.83) (-4,0)};
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (-2.83,-2.83)};
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-2.83,2.83) (2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (2.83,2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (-2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (-2.83,2.83)};
+
+\draw[black,fill=white] (0,4) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (4,0) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (0,-4) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (-4,0) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (-2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (-2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
+
+\node (1) at (0,4) {{1}};
+\node (2) at (2.83,2.83) {{2}};
+\node (3) at (4,0) {{3}};
+\node (4) at (2.83,-2.83) {{4}};
+\node (5) at (0,-4) {{5}};
+\node (6) at (-2.83,-2.83) {{6}};
+\node (7) at (-4,0) {{7}};
+\node (8) at (-2.83,2.83) {{8}};
+\end{tikzpicture}
+\caption{A Carr-Vempala point with 8 vertices on its cycle. Dashed edges represent paths where each edge on the path have $x_e =1$.}
+\label{fig:CVpoint}
+\end{figure}
+
 Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point.
 We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges.
-\cindy{This sounds like a contribution of the paper.}
+\cindy{This sounds like a contribution of the paper.} \arash{Yes, particlarly since a similar research question have been studied by \cite{alexander2006integrality} and \cite{TSPcompute}}
 Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.

### 2020-08-03 FDT2020/Introduction.tex
A few small changes

@@
 
-There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP) or 2EC (see \cite{tspbook})
-\cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
+There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP, see \cite{tspbook}) or 2EC 
+%\cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
 Benoit and Boyd~\cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices.
@@
 A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$ (see Figure \ref{fig:CVpoint})
-\cindy{Every pair of vertices on the cycle is connected this way?
+%\cindy{Every pair of vertices on the cycle is connected this way?
 It sounds like that, though I don't recall that being necessary.
@@
 
-\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?}
+\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?} \cindy{Yes that would be fine, if the reader could also use that figure then.
+They could page forward to see the figure when reading the introduction.}
 
@@
 \end{tikzpicture}
-\caption{A Carr-Vempala point with 8 vertices on its cycle. Dashed edges represent paths where each edge on the path have $x_e =1$.}
+\caption{A Carr-Vempala point with 8 vertices on its cycle.
+Solid lines are edges with value strictly between $0$ and $1$.
+Dashed edges represent paths where each edge on the path has $x_e =1$.
+There can be an arbitrary number of degree-$2$ vertices on the dashed paths.}
 \label{fig:CVpoint}

### 2020-08-03 FDT2020/main-section.tex
More addition of careful definitions, removal of redundancy, etc.
A few small changes

@@
 \section{Finding a Feasible Solution}\label{domTOIP}
+In this section we give the algorithm for DomToIP and prove its performance (Theorem~\ref{DomtoIP}).
+
 Consider an instance $I=(A,b)$ of the IP formulation.
@@
 Assume $S(I)\subseteq \{0,1\}^n$ and $P(I)\subseteq [0,1]^n$.
-For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section.
+For simplicity in the notation we assume and instance $I$ and denote $P(I),S(I),$ and $g(I)$ by $P$, $S$, and $g$ for this section and the next section.
 Also, for both sections we assume $t=|\spp(x)|$.
 Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$.
+\cindy{TODO: Is this something that should be clear to the reader with what they know at this point? Does it need an explanation? Does it need an explanation at the end of this section or the next?}
 
@@
 	Given $\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time, such that $\bar{x}\leq \tilde{x}$.\end{lemma}
-Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: rounding up any fractional point in $P$ gives us a point in $\dom(P)$.
+Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up any fractional point in $P$ gives us a point in $\dom(P)$.
 
@@
 \end{align*}
-\section{Computational Experiments with FDT}\label{experiment}
+\section{Computational Experiments with FDT}\label{sec:experiment}
 We ran FDT on three network design problems: VC, TAP and 2EC.

### 2020-08-03 FDT2020/Introduction.tex
Adding section pointers for FDT and DomToIP

@@
 
-We introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which runs in polynomial time algorithm.
+In Section~\ref{binaryfdt} we introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which runs in polynomial time algorithm.
 Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated coordinatewise by a ``factor" $C$ times $x$.
@@
 
-A subroutine of the FDT, called the DomToIP algorithm, finds feasible solutions to any IP with finite gap. This can be of independent interest, especially in proving that a model has unbounded gap.
+In Section~\ref{domTOIP} we describe a subroutine of the FDT, called the DomToIP algorithm, which finds feasible solutions to any IP with finite gap.
+This can be of independent interest, especially in proving that a model has unbounded gap.
 \begin{restatable}{thm}{DomToIP}

### 2020-08-03 FDT2020/Introduction.tex
Pass for typos, etc, in the conclusion. Fixing undefined references.

--- 2020-08-03 FDT2020/Introduction.tex
@@
 
-We introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which runs in polynomial time algorithm.
+In Section~\ref{sec:binaryfdt} we introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which runs in polynomial time algorithm.
 Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated coordinatewise by a ``factor" $C$ times $x$.
@@
 
-A subroutine of the FDT, called the DomToIP algorithm, finds feasible solutions to any IP with finite gap. This can be of independent interest, especially in proving that a model has unbounded gap.
+In Section~\ref{sec:domTOIP} we describe a subroutine of the FDT, called the DomToIP algorithm, which finds feasible solutions to any IP with finite gap.
+This can be of independent interest, especially in proving that a model has unbounded gap.
 \begin{restatable}{thm}{DomToIP}
@@
 At the end we have a convex combination of integer solutions $\mathcal{D}(P(I))$.
-For each such solution $z$ we invoke the DomToIP algorithm (see Section \ref{domTOIP}) to find $z'\in S(I)$ where $z'\leq z$.
+For each such solution $z$ we invoke the DomToIP algorithm
+% CAP: forward pointer earlier now
+% (see Section~\ref{sec:domTOIP})
+to find $z'\in S(I)$ where $z'\leq z$.
 
@@
 To eradicate this extra factor, we must treat the coordinate $i$ with $x_i=1$ differently.
-We focus on the 2-edge-connected multi-subgraph graph problem (2EC) defined above.
+In Section~\ref{sec:2EC} we focus on the 2-edge-connected multi-subgraph graph problem (2EC) defined above.
 It's subtour-elimination LP relaxation is given in (\ref{eq:subtour}).

### 2020-08-03 FDT2020/conclusion.tex
Pass for typos, etc, in the conclusion. Fixing undefined references.

@@
 
-The results in Sections \ref{binaryfdt}, \ref{domTOIP} and \ref{2EC} hold if the intial integer program has soem auxilliary continious variables\footnote{Here by auxilliary variables we mean a variable that does not participate in the objective function}, i.e.
+The results in Sections \ref{sec:binaryfdt}, \ref{sec:domTOIP} and \ref{sec:2EC} hold if the intial integer program has some auxilliary continuous variables\footnote{Here by auxilliary variables we mean a variable that does not participate in the objective function}, i.e.
 when we have
@@
 our main results work.
-In fact out implementation of the subtour elimination formulation is based on an extended formulation with auxiliary variables (see \cite{subtour-extended}).
-We removed this extension in order to make the presentation simpler.
+In fact our implementation of the subtour elimination formulation is based on an extended formulation with auxiliary variables (see \cite{subtour-extended}).
+We removed this extension to make the presentation simpler.
 
-Fractional Decomposition Tree is a tool to experminetally evaluate the known bounds (and conjectured bounds) on integrality gap of combinatorial optimization problems.
-We hope that applying this tool to a wide range of problems can be successful in refuting conjectures on the upper bounds of integrality gap or at least narrow down the instances for which a closer look is required for the study of integrality gap.
+Fractional Decomposition Tree is a tool to experminetally evaluate the known bounds (and conjectured bounds) on the integrality gap of combinatorial optimization IP formulations.
+We hope that applying this tool to a wide range of problems can be a tool to guide conjectures on the upper bounds of integrality gap or at least narrow down the instances for which a closer look is required for the study of integrality gap.

### 2020-08-03 FDT2020/main-section.tex
Pass for typos, etc, in the conclusion. Fixing undefined references.

@@
 }\fi
-\section{Finding a Feasible Solution}\label{domTOIP}
-In this section we give the algorithm for DomToIP and prove its performance (Theorem~\ref{DomtoIP}).
+\section{Finding a Feasible Solution}\label{sec:domTOIP}
+In this section we give the algorithm for DomToIP and prove its performance (Theorem~\ref{domtoIP}).
 
@@
 \section{FDT on Binary IPs}
-\label{binaryfdt}
+\label{sec:binaryfdt}
 
@@
 
-\section{FDT for 2EC}\label{2EC}
+\section{FDT for 2EC}\label{sec:2EC}
 
-In Section \ref{binaryfdt} our focus was on binary IPs.
+In Section~\ref{sec:binaryfdt} our focus was on binary IPs.
 In this section, in an attempt to extend FDT to \{0,1,2\} problems we introduce an FDT algorithm for a 2-edge-connected multi-subgraph problem.

### 2020-08-03 FDT2020/conclusion.tex
Mostly a pass through the conclusion section. Moved the relevant comment from the main section to the conclusion file.

@@
 
-The results in Sections \ref{sec:binaryfdt}, \ref{sec:domTOIP} and \ref{sec:2EC} hold if the intial integer program has some auxilliary continuous variables\footnote{Here by auxilliary variables we mean a variable that does not participate in the objective function}, i.e.
-when we have
+The results in Sections \ref{sec:domTOIP}, \ref{sec:binaryfdt}  and \ref{sec:2EC} hold if the intial integer program has some auxilliary continuous variables\footnote{Here by auxilliary variables we mean a variable that does not participate in the objective function}.
+That is, when we have
 \begin{equation*}
@@
 \end{equation*}
-where the last $p$ variables are continous, $P(A,b) = \{x\in \mathbb{R}^n: Ax\geq b\}$ and define
+where the last $p$ variables are continous, $P(A,b) = \{x\in \mathbb{R}^n: Ax\geq b\}$
+\cindy{should this be $P(A,b) = \{x\in \mathbb{R}^{n+p}: Ax\geq b\}$?}
+and define
 \begin{equation*}
@@
 
-Fractional Decomposition Tree is a tool to experminetally evaluate the known bounds (and conjectured bounds) on the integrality gap of combinatorial optimization IP formulations.
+Our experiments in Section~\ref{sec:experiment} give a proof of concept.
+They show that its plausible FDT will have practical benefit as an IP heuristic for problems with appropriate structure.
+FDT performance will likely improve in a future more high-performance version coded in C or C++, perhaps able to take advantage of the low-level parallelism available on all modern platforms (even laptops).
+This will allow tests on larger instances.
+We leave as future work a more comprehensive set of experiments to determine on which kinds of problems FDT is likely to outperform other general heuristics.
+Any consistent structure of such instances could lead to proofs of better approximation bounds.
+
+Fractional Decomposition Tree is a tool to experimentally evaluate the known bounds (and conjectured bounds) on the integrality gap of combinatorial optimization IP formulations.
 We hope that applying this tool to a wide range of problems can be a tool to guide conjectures on the upper bounds of integrality gap or at least narrow down the instances for which a closer look is required for the study of integrality gap.
+
+\cindy{
+Here's my original comment on a conclusion section with updated list.
+Most papers have a ``discussion and conclusions'' section.
+It doesn't have to be long and it doesn't have to repeat the paper contributions said before.
+It can include extensions or thoughts/discussions that don't easily fit into the main body.
+It can include new insights into the value of work now that the reader understands it better.
+Here are some thoughts about what could go there:
+1)DONE: Bob was quite insistent at one point that we describe how to extend to continuous variables as long as they are not in the objective function.
+Can we state that in a conclusion and very briefly summarize what would change for this case?
+2) Open questions/future research.  Any thoughts on open theory questions?
+3) DONE: Experimental questions would include doing a more high-performance version (e.g.
+in C or C++) to run on larger instances, and a more comprehensive set of experiments to determine on what kind of problems FDT is likely to outperform other general heuristics.
+4) TODO: more after I have gone all the way through.
+}

### 2020-08-03 FDT2020/main-section.tex
Mostly a pass through the conclusion section. Moved the relevant comment from the main section to the conclusion file.

@@
 We used the CPLEX 12.9.0.0 solver to solve the pyomo LP models.
-The experiments on 2EC are done on a Windows machine and coded in AMPL with CPLEX as the solver.
+We ran the experiments for 2EC on a Windows machine, coded in AMPL with CPLEX as the solver.
 \paragraph{FDT on VC instances from (PACE 2019) \cite{PACE}.}
@@
 \end{table}
-
-\cindy{
-Most papers have a ``discussion and conclusions'' section.
-It doesn't have to be long and it doesn't have to repeat the paper contributions said before.
-It can include extensions or thoughts/discussions that don't easily fit into the main body.
-It can include new insights into the value of work now that the reader understands it better.
-Here are some thoughts about what could go there:
-1) Bob was quite insistent at one point that we describe how to extend to continuous variables as long as they are not in the objective function.
-Can we state that in a conclusion and very briefly summarize what would change for this case?
-2) Open questions/future research.
-Any thoughts on open theory questions?
-Experimental questions would include doing a more high-performance version (e.g.
-in C or C++) to run on larger instances, and a more comprehensive set of experiments to determine on what kind of problems FDT is likely to outperform other general heuristics.
-3) TODO: more after I have gone all the way through.
-}

### 2020-08-03 FDT2020/main-section.tex
fixing a typo

@@
 Assume $S(I)\subseteq \{0,1\}^n$ and $P(I)\subseteq [0,1]^n$.
-For simplicity in the notation we assume and instance $I$ and denote $P(I),S(I),$ and $g(I)$ by $P$, $S$, and $g$ for this section and the next section.
+For simplicity in the notation we assume an instance $I$ and denote $P(I),S(I),$ and $g(I)$ by $P$, $S$, and $g$ for this section and the next section.
 Also, for both sections we assume $t=|\spp(x)|$.

### 2020-08-03 FDT2020/main-section.tex
Edits in the experimental section through the TAP part. Fixing accents in JaJa's name.

@@
 
-We compared Dive FDT (Algorithm \ref{FDT-dive}) with feasbility pump \cite{fp1} in the terms of time spent solving LP relaxations and the quality of solution provided by each algorithm.
-The results are presented in Figure \ref{fpvsfdt}.
+We compared Dive FDT (Algorithm \ref{FDT-dive}) with feasbility pump \cite{fp1} in terms of running time
+% spent solving LP relaxations
+and the quality of solution provided by each algorithm. We used the small (200 vertex) test cases from the PACE 2019 vertex-cover challenge. The results are presented in Figure \ref{fpvsfdt}.
 
@@
 	\includegraphics[width=8cm,scale=1]{"fjvsfdt".png}
-	\caption{FDT vs the 2-approximation for TAP\cite{FJ81} on randomly generated extreme points of the cut-LP.}
+%	\caption{FDT vs the 2-approximation for TAP\cite{FJ81} on randomly generated extreme points of the cut-LP.}
+	\caption{TAP on our random instances: FDT run on LP optimal vs the 2-approximation for TAP\cite{FJ81}.}
 	\label{fjvsfdt}
@@
 \paragraph{FDT on randomly generated instances of TAP.}
-Recall that in TAP we are given a tree $T=(V,E)$, and a set of links $L$ between vertices in $V$ and costs $c\in \mathbb{R}^{L}_{\geq 0}$.
+Recall that in the tree-augmentation problem (TAP) we are given a tree $T=(V,E)$, a set of non-tree links $L$ between vertices in $V$ and costs $c\in \mathbb{R}^{L}_{\geq 0}$.
 A feasible augmentation is $L'\subseteq L$ such that $T+L'$ is 2-edge-connected.
 In TAP we wish to find the minimum-cost feasible augmentation.
-The integrality gap of the cut-LP for TAP is defined as
+The integrality gap of the cut LP for TAP (given in (\ref{eq:cutLP})) is
 \begin{equation*}
-g(\tap) = \max_{c\in \mathbb{R}^L_{\geq 0}} \frac{\min_{x\in\tap(T,L)} cx}{\min_{x\in\cut(T,L)} cx}.
+g(\tap) = \max_{c\in \mathbb{R}^L_{\geq 0}} \frac{\min_{x\in\tap(T,L)} cx}{\min_{x\in\cut(T,L)} cx},
 \end{equation*}  
+where $TAP(T,L)$ is the feasible set for the IP and $CUT(T,L)$ is the feasible set for the cut LP (relaxation).
+We know $\frac{3}{2}\leq g(\tap)\leq 2$~\cite{FJ81,32gaptap}.
+Notice that $\min_{x\in \tap(T,L)}cx$ is a binary IP.
 
-We know $\frac{3}{2}\leq g(\tap)\leq 2$~\cite{FJ81,32gaptap}. Notice that $\min_{x\in \tap(T,L)}cx$ is a binary IP. 
-We considered full binary trees with 3 to 7 levels.
-We assume the set of links to be the set of all pairs of leaves of the trees and we choose the costs of the links uniformly at random.
-We then ran binary FDT and chose the solution that is gives the minimum cost.
-We then compared it with the circulation-based 2-approximation algorithm of Frederickson and Ja'Ja' \cite{FJ81} in Figure \ref{fjvsfdt}.
+As input for our experiments, we considered full binary trees with 3 to 7 levels with a link for each pairs of leaves.
+We set the link costs uniformly at random.
+We summarize these test instances in Table~\ref{tableTAP}.
+We ran binary FDT on each test instance and chose the solution with minimum cost.
+We compare the FDT solutions to those from the circulation-based 2-approximation algorithm of Frederickson and J\'{a}J\'{a}~\cite{FJ81} in Figure \ref{fjvsfdt}.
+\cindy{We should say something about running time.
+Since we showed running time in part a, the reader will just assume otherwise that our running time is terrible compared to the Fredrickson and J\'{a}J\'{a} algorithm.}
+\cindy{It may be too late now, but it might be easier to understand the results if there is another figure that shows instance number vs the ratio  FDT gap/FJ gap.
+It's hard to pair corresponding points with the current figure.
+I would suggest replacing the current figure with that, but then we'd lose the absolute gap values.}
+\cindy{Please check my new caption for Figure 2b.  The old one is just commented out.}
 
@@
 \end{table}
-For all these 450 fractional extreme points of the cut-LP our experiments showed that the integrality gap $g(\tap)$ is at most $\frac{3}{2}$ when restricted to the instances considered.
-In fact, only for one instance the upper bound we provided by our experiment is at $\frac{3}{2}$.
-For 425 instances, the upper bound is $\frac{4}{3}$, for 22 instances it is $\frac{6}{5}$, for 2 instances it is $\frac{8}{7}$.
+\cindy{Please check the edits to the next paragraph carefully to ensure I captured what you were trying to say.}
+For all 450 instances in our experiments, running FDT on the LP optimal (fractional extreme point) of the cut LP gave a feasible solution with value at most a factor $\frac{3}{2}$ larger than the LP lower bound.
+Such a feasible solution gives an upper bound on the integrality gap $g(\tap)$ of that specific instance of at most $\frac{3}{2}$.
+\cindy{There are 450 instances, so you tested one extreme point (the LP optimal) per instance?  I'm assuming that was the LP optimal.}
+%when restricted to the instances considered.
+In fact, the integrality gap upper bound derived this way was equal to $\frac{3}{2}$ for only one instance.
+%the upper bound we provided by our experiment is at $\frac{3}{2}$.
+For 425 instances, the integrality gap upper bound was $\frac{4}{3}$, for 22 instances it was $\frac{6}{5}$, for 2 instances it was $\frac{8}{7}$.
 \paragraph{Computational comparison between Christofides' algorithm and FDT for 2EC on Carr-Vempala points.}

### 2020-08-03 FDT2020/main-section.tex
Questions on the Christofides part of the experiments

@@
 
-First we need to describe the polyhedral version Christofides' algorithm.
-We do this specifically for the Carr-Vempala points.
-Let $x$ be a Carr-Vempala points defined on a graph $G=(V,E)$.
-It is well known that $\frac{|V|-1}{|V|}\cdot x$ is in the convex hull of incidence vectors of spanning trees of $G$.
-Hence, we can write $\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G$, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$.
-Let $O_i$ be the set of odd degree vertices of $T_i$.
-It is easy to see that $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, namely $O_i\join(G)$~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, and $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.}.
+We first describe the polyhedral version of Christofides' algorithm specifically for Carr-Vempala points.
+\cindy{I think it would be very helpful for the reader for you to remind them of the classic (graph-based, not polyhedral) metric (triangle-inequality) Christofides algorithm here and argue that it applies to 2EC.
+Most people will remember Christofides' TSP approximation algorithm because it's so classic.
+But it's easy to remind people.
+Then it would be helpful to explain that when you give the LP in (\ref{ojoinaverage}) how that relates to Christofides.
+If this paper is accepted, all kinds of CS/OR researchers may want to read it, so we should make their job as easy as possible.
+It would be nice for others to use FDT and to build off it.}
+Let $x$ be a Carr-Vempala point defined on a graph $G=(V,E)$. It is well known that $\frac{|V|-1}{|V|}\cdot x$ is in the convex hull of incidence vectors of spanning trees of $G$.
+\cindy{The statement before this depends very much on the audience.
+For those who study polyhedral combinatorics especially for TSP and who know what a Carr-Vempala point is off the top of their heads, it may be well known.
+For people who generally do combinatorial optimization, I would not expect them to know this.
+So this kind of phrasing might annoy a reader.
+General rule: either a statement is really obvious (so just state it), or it is not (so give a reference or justification).
+Otherwise (and I know you don't intend this), you are implying the reader is stupid if they don't see the argument right away.
+Of course, it's the authors' job to teach and convince the reader.
+Thus one should avoid phrases like ``It's obvious/trivial that...'' and similar phrases.
+I would change the sentence before this comment to ``The vector $\frac{|V|-1}{|V|}\cdot x$ is in the convex hull...'' and give a short justification or reference.
+Or ``Foo and Barr (cite Foo and Bar's paper) argue that ...
+is in the convex hull...'' I'm sure I could figure this out if a had a little time to think, but I don't have that time now.}
+Hence, we can write $\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G$, $\chi^{T_i}$ is its incidence vector, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$.
+Let $O_i$ be the set of odd-degree vertices of $T_i$.
+It is easy to see that $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, namely $O_i\join(G)$~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.}.
+\cindy{Here is another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.'' Also, do you mean that $x/2$ is in the convex hull of the incident vectors of all $O_i$-joins for any spanning tree $T_i$?
+If so, it would be good to make that clear.
+Since I will not make it through every word of Sections 2-4 if you submit today, I recommend looking for similar places in those sections.}
 
- We then solve the following LP that allows us to find parity corrections that are good for the whole convex combination.
+\cindy{Do you have to precompute the joins?
+Does that mean generating spanning trees before setting up the LP?
+Or generating them on the fly?
+Only minimum-weight spanning trees?
+I haven't had a lot of time to think about this.}
+ We solve the following LP that allows us to find parity corrections that are good for the whole convex combination.
 \begin{equation}\label{ojoinaverage}

### 2020-08-03 FDT2020/main-section.tex
chris vs FDT plot updated (leneged out of the plot now)

--- 2020-08-03 FDT2020/main-section.tex
@@
 Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$.
-\cindy{TODO: Is this something that should be clear to the reader with what they know at this point? Does it need an explanation? Does it need an explanation at the end of this section or the next?}
+\cindy{TODO: Is this something that should be clear to the reader with what they know at this point?
+Does it need an explanation?
+Does it need an explanation at the end of this section or the next?}\arash{this is just a relabeling of the indices.}
 
@@
 where $TAP(T,L)$ is the feasible set for the IP and $CUT(T,L)$ is the feasible set for the cut LP (relaxation).
-We know $\frac{3}{2}\leq g(\tap)\leq 2$~\cite{FJ81,32gaptap}.
+\arash{Did you intentionally change the TAP and CUT module?
+They print as italic now as opposed to how they look in $\tap(T,L)$ and $\cut(T,L)$} We know $\frac{3}{2}\leq g(\tap)\leq 2$~\cite{FJ81,32gaptap}.
 Notice that $\min_{x\in \tap(T,L)}cx$ is a binary IP.
@@
 For 425 instances, the integrality gap upper bound was $\frac{4}{3}$, for 22 instances it was $\frac{6}{5}$, for 2 instances it was $\frac{8}{7}$.
+\arash{it's all correct, I'm running the experiments again to get the running time so these numbers might change.}
 \paragraph{Computational comparison between Christofides' algorithm and FDT for 2EC on Carr-Vempala points.}

### 2020-08-03 FDT2020/main-section.tex
TAP experiments updated

@@
 			 & $62$ & $496$ & $100$ \\ 
-			  & $126$ & $2016$ & $50$ \\  \hline \\
+			  & $126$ & $2016$ & $100$ \\  \hline \\
 		\end{tabular}\caption{Summary of the randomly generated instances of TAP.} \label{tableTAP}
@@
 \cindy{Please check the edits to the next paragraph carefully to ensure I captured what you were trying to say.}
-For all 450 instances in our experiments, running FDT on the LP optimal (fractional extreme point) of the cut LP gave a feasible solution with value at most a factor $\frac{3}{2}$ larger than the LP lower bound.
+For all 500 instances in our experiments, running FDT on the LP optimal (fractional extreme point) of the cut LP gave a feasible solution with value at most a factor $\frac{3}{2}$ larger than the LP lower bound.
 Such a feasible solution gives an upper bound on the integrality gap $g(\tap)$ of that specific instance of at most $\frac{3}{2}$.
@@
 %the upper bound we provided by our experiment is at $\frac{3}{2}$.
-For 425 instances, the integrality gap upper bound was $\frac{4}{3}$, for 22 instances it was $\frac{6}{5}$, for 2 instances it was $\frac{8}{7}$.
+For 480 instances, the integrality gap upper bound was $\frac{4}{3}$, for 16 instances it was $\frac{6}{5}$, for 2 instances it was $\frac{8}{7}$, for 1 instance it was $\frac{10}{9}$. 
 \arash{it's all correct, I'm running the experiments again to get the running time so these numbers might change.}

### 2020-08-05 FDT2020/main-section.tex

--- 2020-08-03 FDT2020/main-section.tex
@@
 %the upper bound we provided by our experiment is at $\frac{3}{2}$.
-For 425 instances, the integrality gap upper bound was $\frac{4}{3}$, for 22 instances it was $\frac{6}{5}$, for 2 instances it was $\frac{8}{7}$.
+For 480 instances, the integrality gap upper bound was $\frac{4}{3}$, for 16 instances it was $\frac{6}{5}$, for 2 instances it was $\frac{8}{7}$, for 1 instance it was $\frac{10}{9}$. 
+\arash{it's all correct, I'm running the experiments again to get the running time so these numbers might change.}
 \paragraph{Computational comparison between Christofides' algorithm and FDT for 2EC on Carr-Vempala points.}

### 2020-08-05 FDT2020/main-section.tex
Updating comments, using macro, etc (minor)

@@
 Does it need an explanation?
-Does it need an explanation at the end of this section or the next?}\arash{this is just a relabeling of the indices.}
+Does it need an explanation at the end of this section or the next?}\arash{this is just a relabeling of the indices.} \cindy{Sorry.
+I didn't understand that you meant the solution has that property.
+Right?
+The vector $x$ isn't defined in this paragraph and it's not in the next lemma either.
+If $x$ is the output of DomToIP, then we should say that.
+``Without loss of generality the solution $x$ returned by DomToIP has ...''}
 
@@
 \end{equation*}  
-where $TAP(T,L)$ is the feasible set for the IP and $CUT(T,L)$ is the feasible set for the cut LP (relaxation).
-\arash{Did you intentionally change the TAP and CUT module?
-They print as italic now as opposed to how they look in $\tap(T,L)$ and $\cut(T,L)$} We know $\frac{3}{2}\leq g(\tap)\leq 2$~\cite{FJ81,32gaptap}.
-Notice that $\min_{x\in \tap(T,L)}cx$ is a binary IP.
+where $\tap(T,L)$ is the feasible set for the IP and $\cut(T,L)$ is the feasible set for the cut LP (relaxation).
+\arash{Did you intentionally change the TAP and CUT module? They print as italic now as opposed to how they look in $\tap(T,L)$ and $\cut(T,L)$}
+\cindy{Did you mean macro?
+No, I didn't intentionally change it.
+I just hadn't noticed you had a macro for those two and was in a rush.
+At least for the previous section, I changed to the macros.
+I don't immediately see other places where it's used in math mode, and therefore needs the macro.}
+We know $\frac{3}{2}\leq g(\tap)\leq 2$~\cite{FJ81,32gaptap}. Notice that $\min_{x\in \tap(T,L)}cx$ is a binary IP.
 
@@
 Since we showed running time in part a, the reader will just assume otherwise that our running time is terrible compared to the Fredrickson and J\'{a}J\'{a} algorithm.}
-\cindy{It may be too late now, but it might be easier to understand the results if there is another figure that shows instance number vs the ratio  FDT gap/FJ gap.
+%\cindy{It may be too late now, but it might be easier to understand the results if there is another figure that shows instance number vs the ratio  FDT gap/FJ gap.
 It's hard to pair corresponding points with the current figure.
 I would suggest replacing the current figure with that, but then we'd lose the absolute gap values.}
-\cindy{Please check my new caption for Figure 2b.  The old one is just commented out.}
+%\cindy{Please check my new caption for Figure 2b.  The old one is just commented out.}
 
@@
 \end{table}
-\cindy{Please check the edits to the next paragraph carefully to ensure I captured what you were trying to say.}
+%\cindy{Please check the edits to the next paragraph carefully to ensure I captured what you were trying to say.}
 For all 500 instances in our experiments, running FDT on the LP optimal (fractional extreme point) of the cut LP gave a feasible solution with value at most a factor $\frac{3}{2}$ larger than the LP lower bound.
 Such a feasible solution gives an upper bound on the integrality gap $g(\tap)$ of that specific instance of at most $\frac{3}{2}$.
-\cindy{There are 450 instances, so you tested one extreme point (the LP optimal) per instance?  I'm assuming that was the LP optimal.}
+%\cindy{There are 450 instances, so you tested one extreme point (the LP optimal) per instance?  I'm assuming that was the LP optimal.}
 %when restricted to the instances considered.

### 2020-08-07 FDT2020/Introduction.tex
Edits in the experimental section through the TAP part. Fixing accents in JaJa's name.
Moved the Carr-Vempala figure to the experimental section, typo fixes, questions

@@
 The natural linear programming relaxation for TAP is
-\begin{equation}
+\begin{equation}\label{eq:cutLP}
 \min \{cx\; : \; \sum_{\ell \in \cov(e)} x_{\ell} \geq 1 \text{ for } e\in T, \; x\in [0,1]^{E\setminus T}\}.
@@
 
-There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP, see \cite{tspbook}) or 2EC 
+There are fairly good bounds for the integrality gap for the Traveling Salesman Problem (TSP, see \cite{tspbook}) or 2EC.
 %\cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
@@
 Consider a graph $G=(V,E)$.
-A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$ (see Figure \ref{fig:CVpoint})
+A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$ (see Figure \ref{fig:CVpoint}).
 %\cindy{Every pair of vertices on the cycle is connected this way?
@@
 
-\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?} \cindy{Yes that would be fine, if the reader could also use that figure then.
+%\arash{I added this figure \ref{fig:CVpoint} but maybe we can put it later in the experiments section to make the introduction shorter?} \cindy{Yes that would be fine, if the reader could also use that figure then.
 They could page forward to see the figure when reading the introduction.}
-
-\begin{figure}
-\centering
-\begin{tikzpicture}[scale=0.4]
-
-\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (0,-4)};
-\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(2.83,2.83) (-4,0)};
-\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (-2.83,-2.83)};
-\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-2.83,2.83) (2.83,-2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (2.83,2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,-2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (2.83,-2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (-2.83,-2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,-2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (-2.83,2.83)};
-
-\draw[black,fill=white] (0,4) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (4,0) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (0,-4) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (-4,0) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (-2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (-2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
-
-\node (1) at (0,4) {{1}};
-\node (2) at (2.83,2.83) {{2}};
-\node (3) at (4,0) {{3}};
-\node (4) at (2.83,-2.83) {{4}};
-\node (5) at (0,-4) {{5}};
-\node (6) at (-2.83,-2.83) {{6}};
-\node (7) at (-4,0) {{7}};
-\node (8) at (-2.83,2.83) {{8}};
-\end{tikzpicture}
-\caption{A Carr-Vempala point with 8 vertices on its cycle.
-Solid lines are edges with value strictly between $0$ and $1$.
-Dashed edges represent paths where each edge on the path has $x_e =1$.
-There can be an arbitrary number of degree-$2$ vertices on the dashed paths.}
-\label{fig:CVpoint}
-\end{figure}
 

### 2020-08-07 FDT2020/main-section.tex
Moved the Carr-Vempala figure to the experimental section, typo fixes, questions

@@
 Let $x$ be a Carr-Vempala point defined on a graph $G=(V,E)$. It is well known that $\frac{|V|-1}{|V|}\cdot x$ is in the convex hull of incidence vectors of spanning trees of $G$.
+\cindy{Is this for any feasible solution, or extreme point of the subtour LP or just Carr-Vempala points?
+It seems that it's for any feasible point since you don't remind the reader about Carr-Vempala points until later.}
 \cindy{The statement before this depends very much on the audience.
@@
 is in the convex hull...'' I'm sure I could figure this out if a had a little time to think, but I don't have that time now.}
+\cindy{I'm going to remove things like ``It's easy to see that,'' where I can. But we may need to add a justification or reference.}
 Hence, we can write $\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G$, $\chi^{T_i}$ is its incidence vector, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$.
 Let $O_i$ be the set of odd-degree vertices of $T_i$.
-It is easy to see that $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, namely $O_i\join(G)$~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.}.
-\cindy{Here is another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.'' Also, do you mean that $x/2$ is in the convex hull of the incident vectors of all $O_i$-joins for any spanning tree $T_i$?
-If so, it would be good to make that clear.
-Since I will not make it through every word of Sections 2-4 if you submit today, I recommend looking for similar places in those sections.}
+We have $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, denoted $O_i\join(G)$~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.}.
+\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}
 
-\cindy{Do you have to precompute the joins?
+\cindy{Do you have to precompute the joins (If they are more than the spanning trees themselves)?
 Does that mean generating spanning trees before setting up the LP?
@@
 Only minimum-weight spanning trees?
-I haven't had a lot of time to think about this.}
+It seems that with a little more explanation, a reader who has not been immersed in 2EC and TSP could follow this.}
+
  We solve the following LP that allows us to find parity corrections that are good for the whole convex combination.
@@
 The variables in the above LP are $y^i\in \mathbb{R}^{E_x}_{
-\geq 0}$ for $i\in [k]$.
-For each $i\in [k]$ we have $y^i\in O_i\join(G_x)$.
-This formulation allows the instance specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$.
-Recall that a Carr-Vempala point consists of a signle cycle of fractional edges.
+\geq 0}$ for $i\in [k]$. For each $i\in [k]$ we have $y^i\in O_i\join(G_x)$.
+\cindy{You say the $y^i$ are LP variables, not integers.
+It even looks like they can even be more than $1$.
+What does it mean for a non-binary vector to be in a set of binary variables?
+I would have expected the lambdas to be the variables, given their use as the convex combination multipliers in most of the paper.}
+This formulation allows the instance-specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$.
+Recall that a Carr-Vempala point consists of a single cycle of fractional edges.
 Figure \ref{fdtvschris} shows FDT's solutions on all Carr-Vempala points that have 10 vertices on the cycle formed by fractional edges.
 We show for these points the apporoximation factor provided by FDT is always better than those from the polyhedral version of Christofides' algorithm.
-In more details, in Figure \ref{fdtvschris} the horizontal axis of the plot is indexed with the 60 Carr-Vempala points that we considered.
+In Figure \ref{fdtvschris} the horizontal axis of the plot is indexed with the 60 Carr-Vempala points that we considered.
 For each Carr-Vempala point $x$, there are two data points.
 The value of the first data point depicted by a circle on the vertical axis is $\frac{|V|-1}{|V|}+\alpha$  and $\alpha$ is the optimal solution to (\ref{ojoinaverage}).
+\cindy{TODO: say when giving the LP~(\ref{ojoinaverage}) how that gives a solution to TAP with this value.}
 The value of the second data point depicted by a cross on the vertical axis is $C$ where $C$ is obtained from applying Theorem \ref{FDT2EC} to $x$.
 In other words, Figure \ref{fdtvschris} is comparing the instance-specific upper bound on integrality gap certified by Christofides' algorithm to the approximation factor of the FDT algorithm for 2EC.
+
+\begin{figure}
+\centering
+\begin{tikzpicture}[scale=0.4]
+
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (0,-4)};
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(2.83,2.83) (-4,0)};
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (-2.83,-2.83)};
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-2.83,2.83) (2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (2.83,2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (-2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (-2.83,2.83)};
+
+\draw[black,fill=white] (0,4) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (4,0) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (0,-4) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (-4,0) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (-2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (-2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
+
+\node (1) at (0,4) {{1}};
+\node (2) at (2.83,2.83) {{2}};
+\node (3) at (4,0) {{3}};
+\node (4) at (2.83,-2.83) {{4}};
+\node (5) at (0,-4) {{5}};
+\node (6) at (-2.83,-2.83) {{6}};
+\node (7) at (-4,0) {{7}};
+\node (8) at (-2.83,2.83) {{8}};
+\end{tikzpicture}
+\caption{A Carr-Vempala point with 8 vertices on its cycle.
+Solid lines are edges with value strictly between $0$ and $1$.
+Dashed edges represent paths where each edge on the path has $x_e =1$.
+There can be an arbitrary number of degree-$2$ vertices on the dashed paths.}
+\label{fig:CVpoint}
+\end{figure}
 

### 2020-08-07 FDT2020/Introduction.tex
comments replied

@@
 They could page forward to see the figure when reading the introduction.}
-
+\arash{I changed the paragraph below a little bit, can you check?}
 Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point.
-We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges.
+It has be conjectured that $g(\2ec)\leq \frac{6}{5}$ (see \cite{alexander2006integrality,boydlegault,hn19}, but the only known upper bound on $g(\2ec)$ stands at $\frac{3}{2}$ \cite{wolsey}.
+We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges, thereby confirming the conjecture for these instances.
 \cindy{This sounds like a contribution of the paper.} \arash{Yes, particlarly since a similar research question have been studied by \cite{alexander2006integrality} and \cite{TSPcompute}}

### 2020-08-07 FDT2020/main-section.tex
comments replied

@@
 For simplicity in the notation we assume an instance $I$ and denote $P(I),S(I),$ and $g(I)$ by $P$, $S$, and $g$ for this section and the next section.
-Also, for both sections we assume $t=|\spp(x)|$.
-Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$.
+Also, for both sections let $x^*$ be the optimal solution to the LP formulation and assume $t=|\spp(x^*)|$.
+Without loss of generality we can assume $x^*_i = 0$ for $i=t+1,\ldots,n$.
 \cindy{TODO: Is this something that should be clear to the reader with what they know at this point?
@@
 If $x$ is the output of DomToIP, then we should say that.
-``Without loss of generality the solution $x$ returned by DomToIP has ...''}
+``Without loss of generality the solution $x$ returned by DomToIP has ...''}\arash{I see your point, please see if the change made it better}
 
@@
 	Given $\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time, such that $\bar{x}\leq \tilde{x}$.\end{lemma}
-Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up any fractional point in $P$ gives us a point in $\dom(P)$.
-
+Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up $x^*$ (or any fractional point in $P$) gives us a point in $\dom(P)$.
+Hence, we can assume in the proof below that $\tilde{x}_i= 0$ for $i=t+1,\ldots,n$.
+\arash{I also made a change based on the change above}
 \subsection{Proof of Lemma \ref{domlemma}: The DomToIP Algorithm}
@@
 \label{sec:binaryfdt}
-
-Assume we are given a point $x^*\in P$.
-For instance, $x^*$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
+\arash{I made a small change here based on our discussion in the bottom of page 8}
+Recall that $x^*$ was the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
 In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm.

### 2020-08-07 FDT2020/Introduction.tex
Just responding to the latest comments

@@
 They could page forward to see the figure when reading the introduction.}
-\arash{I changed the paragraph below a little bit, can you check?}
+\arash{I changed the paragraph below a little bit, can you check?} \cindy{Looks good.
+I just changed one sentence to the active voice.
+If you're OK with that, you can delete these 2 comments.
+Thanks!}
 Carr and Vempala \cite{Carr2004} showed that $g(\2ec)$ is achieved for instances where the optimal solution to $\min_{x\in \subtour(G)}cx$ is a Carr-Vempala point.
-It has be conjectured that $g(\2ec)\leq \frac{6}{5}$ (see \cite{alexander2006integrality,boydlegault,hn19}, but the only known upper bound on $g(\2ec)$ stands at $\frac{3}{2}$ \cite{wolsey}.
+Multiple groups of researchers have conjectured that $g(\2ec)\leq \frac{6}{5}$ (see \cite{alexander2006integrality,boydlegault,hn19}, but the only known upper bound on $g(\2ec)$ stands at $\frac{3}{2}$ \cite{wolsey}.
 We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges, thereby confirming the conjecture for these instances.

### 2020-08-07 FDT2020/main-section.tex
Just responding to the latest comments

@@
 If $x$ is the output of DomToIP, then we should say that.
-``Without loss of generality the solution $x$ returned by DomToIP has ...''}\arash{I see your point, please see if the change made it better}
+``Without loss of generality the solution $x$ returned by DomToIP has ...''}\arash{I see your point, please see if the change made it better} \cindy{Yes, thanks.
+We can delete this conversation after you see this response.}
 
@@
 Hence, we can assume in the proof below that $\tilde{x}_i= 0$ for $i=t+1,\ldots,n$.
-\arash{I also made a change based on the change above}
+\arash{I also made a change based on the change above}\cindy{Thanks!}
 \subsection{Proof of Lemma \ref{domlemma}: The DomToIP Algorithm}
@@
 \label{sec:binaryfdt}
-\arash{I made a small change here based on our discussion in the bottom of page 8}
+\arash{I made a small change here based on our discussion in the bottom of page 8}\cindy{Thanks!}
 Recall that $x^*$ was the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
@@
 where $\tap(T,L)$ is the feasible set for the IP and $\cut(T,L)$ is the feasible set for the cut LP (relaxation).
-\arash{Did you intentionally change the TAP and CUT module? They print as italic now as opposed to how they look in $\tap(T,L)$ and $\cut(T,L)$}
-\cindy{Did you mean macro?
+%\arash{Did you intentionally change the TAP and CUT module? They print as italic now as opposed to how they look in $\tap(T,L)$ and $\cut(T,L)$}
+%\cindy{Did you mean macro?
 No, I didn't intentionally change it.

### 2020-08-08 FDT2020/Introduction.tex
some comment exchanges removed

@@
 They could page forward to see the figure when reading the introduction.}
-\arash{I changed the paragraph below a little bit, can you check?} \cindy{Looks good.
+%\arash{I changed the paragraph below a little bit, can you check?} \cindy{Looks good.
 I just changed one sentence to the active voice.

### 2020-08-08 FDT2020/main-section.tex
some comment exchanges removed

@@
 Without loss of generality we can assume $x^*_i = 0$ for $i=t+1,\ldots,n$.
-\cindy{TODO: Is this something that should be clear to the reader with what they know at this point?
+%\cindy{TODO: Is this something that should be clear to the reader with what they know at this point?
 Does it need an explanation?
@@
 Hence, we can assume in the proof below that $\tilde{x}_i= 0$ for $i=t+1,\ldots,n$.
-\arash{I also made a change based on the change above}\cindy{Thanks!}
+%\arash{I also made a change based on the change above}\cindy{Thanks!}
 \subsection{Proof of Lemma \ref{domlemma}: The DomToIP Algorithm}
@@
 \label{sec:binaryfdt}
-\arash{I made a small change here based on our discussion in the bottom of page 8}\cindy{Thanks!}
+%\arash{I made a small change here based on our discussion in the bottom of page 8}\cindy{Thanks!}
 Recall that $x^*$ was the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
@@
 For 480 instances, the integrality gap upper bound was $\frac{4}{3}$, for 16 instances it was $\frac{6}{5}$, for 2 instances it was $\frac{8}{7}$, for 1 instance it was $\frac{10}{9}$. 
-\arash{it's all correct, I'm running the experiments again to get the running time so these numbers might change.}
+%\arash{it's all correct, I'm running the experiments again to get the running time so these numbers might change.}
 \paragraph{Computational comparison between Christofides' algorithm and FDT for 2EC on Carr-Vempala points.}

### 2020-08-08 FDT2020/main-section.tex
Start at revision of the Christofides section

@@
 
-We first describe the polyhedral version of Christofides' algorithm specifically for Carr-Vempala points.
-\cindy{I think it would be very helpful for the reader for you to remind them of the classic (graph-based, not polyhedral) metric (triangle-inequality) Christofides algorithm here and argue that it applies to 2EC.
+As described in Section~\ref{sec:2EC-intro}), when the LP optimum for the subtour-elimination relaxation is a Carr-Vempala point (see Figure~\ref{fig:CVpoint}), the integrality gap of that instance is equal to that of 2EC.
+So in that sense, these are the hardest fractional points to round to a feasible solution.
+We now compare the quality of FDT's solution from a Carr-Vempala point to that of Christofides, the best known approximation algorithm.
+In the classic graph-based Christofides algorithm, find a minimum spanning tree of the graph.
+Then, for a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)graph 2-connected.
+If the graph is not complete we can instead add an $O$-join, where $O$ is the set of odd-degree vertices in the spanning tree~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.
+Graphs always have an even number of odd vertices since every edge has two endpoints, giving an even number of endpoints.}.
+In practice, the best-of-many Christofides (BOMC) algorithm~\cite{AKS15,GW17} works better than the classic Christofides algorithm.
+The BOMC algorithm samples many spanning trees from the LP relaxation (with edges chosen proportionally to the LP value), augments each spanning tree with the matching, and taking the best overall solution.
+
+We now describe the polyhedral version of Christofides' algorithm specifically for Carr-Vempala points.
+Consider the subtour-elimination LP~(\ref{eq:subtour}) and any feasible point $x$.
+Consider any partitioning of the vertices of the graph into $b$ pieces and let $E_c$ be the set of edges that connect any two of the $b$ pieces.
+Then we have $\sum_{E_c} x_e \ge b$.
+That is because there are (fractionally) at least $2$ edge endpoints in each piece, for a total of at least $2b$ endpoints, and at least $b$ edges.
+An LP relaxation for the spanning-tree polytope will guarantee $b-1$ edges connecting any $b$ groups of vertices.
+Thus we can scale any LP solution for the subtour-elimination polytope for an $n$-node graph by $(n-1)/n$ and it will still be feasible for the spanning tree polytope.
+
+%\cindy{I think it would be very helpful for the reader for you to remind them of the classic (graph-based, not polyhedral) metric (triangle-inequality) Christofides algorithm here and argue that it applies to 2EC.
 Most people will remember Christofides' TSP approximation algorithm because it's so classic.
@@
 It would be nice for others to use FDT and to build off it.}
-Let $x$ be a Carr-Vempala point defined on a graph $G=(V,E)$. It is well known that $\frac{|V|-1}{|V|}\cdot x$ is in the convex hull of incidence vectors of spanning trees of $G$.
-\cindy{Is this for any feasible solution, or extreme point of the subtour LP or just Carr-Vempala points?
+%It is well known that $\frac{|V|-1}{|V|}\cdot x$ is in the convex hull of incidence vectors of spanning trees of $G$.
+%\cindy{Is this for any feasible solution, or extreme point of the subtour LP or just Carr-Vempala points?
 It seems that it's for any feasible point since you don't remind the reader about Carr-Vempala points until later.}
-\cindy{The statement before this depends very much on the audience.
+%\cindy{The statement before this depends very much on the audience.
 For those who study polyhedral combinatorics especially for TSP and who know what a Carr-Vempala point is off the top of their heads, it may be well known.
@@
 is in the convex hull...'' I'm sure I could figure this out if a had a little time to think, but I don't have that time now.}
-\cindy{I'm going to remove things like ``It's easy to see that,'' where I can. But we may need to add a justification or reference.}
-Hence, we can write $\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G$, $\chi^{T_i}$ is its incidence vector, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$.
-Let $O_i$ be the set of odd-degree vertices of $T_i$.
-We have $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, denoted $O_i\join(G)$~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.}.
-\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}
+%\cindy{I'm going to remove things like ``It's easy to see that,'' where I can. But we may need to add a justification or reference.}
 
-\cindy{Do you have to precompute the joins (If they are more than the spanning trees themselves)?
+Let $x$ be a Carr-Vempala point defined on a graph $G=(V,E)$.
+From the above discussion, we can write $\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G$, $\chi^{T_i}$ is its incidence vector, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$.
+The spanning-tree polytope is integral so there are polynomial-time algorithms to construct this decomposition (See Proposition~\ref{cara} and surrounding discussion).
+
+Let $O_i$ be the set of odd-degree vertices of spanning tree $T_i$.
+Now consider the incidence vectors of feasible $O_i$-joins.
+Consider any subset of vertices $S$ with an even number of odd-degree vertices.
+Then the $O_i$-join LP requires at least one edge joining $S$ to the rest of the vertices.
+The subtour-elimination LP requires every subset of vertices have two edges connecting it to the rest of the graph.
+Therefore, since $x$ is a feasible solution to the subtour-elimination LP, then $x/2$ is feasible for the $O_i$-join associated with spanning tree $T_i$.
+Thus we have $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, denoted $O_i\join(G)$.
+%\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}
+
+%\cindy{Do you have to precompute the joins (If they are more than the spanning trees themselves)?
 Does that mean generating spanning trees before setting up the LP?

### 2020-08-08 FDT2020/main-section.tex
Few small edits

@@
 Let $O_i$ be the set of odd-degree vertices of spanning tree $T_i$.
-Now consider the incidence vectors of feasible $O_i$-joins.
-Consider any subset of vertices $S$ with an even number of odd-degree vertices.
-Then the $O_i$-join LP requires at least one edge joining $S$ to the rest of the vertices.
-The subtour-elimination LP requires every subset of vertices have two edges connecting it to the rest of the graph.
-Therefore, since $x$ is a feasible solution to the subtour-elimination LP, then $x/2$ is feasible for the $O_i$-join associated with spanning tree $T_i$.
-Thus we have $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, denoted $O_i\join(G)$.
+Consider the incidence vectors of feasible $O_i$-joins.
+Let $S$ be any subset of vertices with an even number of odd-degree vertices.
+The $O_i$-join LP requires at least one edge joining $S$ to the rest of the vertices.
+The subtour-elimination LP requires every subset of vertices have two edges connecting it to the rest of the vertices.
+Therefore, since $x$ is a feasible solution to the subtour-elimination LP, $x/2$ is feasible for the $O_i$-join LP associated with spanning tree $T_i$.
+That is, $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, denoted $O_i\join(G)$.
 %\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}
@@
 This formulation allows the instance-specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$.
-Recall that a Carr-Vempala point consists of a single cycle of fractional edges.
+
+%Recall that a Carr-Vempala point consists of a single cycle of fractional edges.
 Figure \ref{fdtvschris} shows FDT's solutions on all Carr-Vempala points that have 10 vertices on the cycle formed by fractional edges.

### 2020-08-08 FDT2020/main-section.tex
A few edits

@@
 
-Let $x$ be a Carr-Vempala point defined on a graph $G=(V,E)$.
-From the above discussion, we can write $\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i}$ where $T_i$ is spanning tree of $G$, $\chi^{T_i}$ is its incidence vector, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$.
+Let $x$ be a Carr-Vempala point defined on a graph $G=(V,E)$.  From the above discussion, we can write
+\begin{equation}
+\label{eq:tree-decomp}
+\frac{|V|-1}{|V|}\cdot x= \sum_{i=1}^{k}\lambda_i\chi^{T_i},
+\end{equation}
+where $T_i$ is spanning tree of $G$, $\chi^{T_i}$ is its incidence vector, $\sum_{i=1}^{k}\lambda_i=1$, and $\lambda_i\geq 0$ for $i\in [k]$.
 The spanning-tree polytope is integral so there are polynomial-time algorithms to construct this decomposition (See Proposition~\ref{cara} and surrounding discussion).
@@
 Let $O_i$ be the set of odd-degree vertices of spanning tree $T_i$.
-Consider the incidence vectors of feasible $O_i$-joins.
+%Consider the incidence vectors of feasible $O_i$-joins.
 Let $S$ be any subset of vertices with an even number of odd-degree vertices.

### 2020-08-08 FDT2020/main-section.tex
Rest of the revision to Christofides discussion

@@
 
-As described in Section~\ref{sec:2EC-intro}), when the LP optimum for the subtour-elimination relaxation is a Carr-Vempala point (see Figure~\ref{fig:CVpoint}), the integrality gap of that instance is equal to that of 2EC.
+As described in Section~\ref{sec:2EC-intro}), when the LP optimum for (\ref{eq:subtour}) is a Carr-Vempala point (see Figure~\ref{fig:CVpoint}), the integrality gap of that instance is equal to that of 2EC.
 So in that sense, these are the hardest fractional points to round to a feasible solution.
 We now compare the quality of FDT's solution from a Carr-Vempala point to that of Christofides, the best known approximation algorithm.
-In the classic graph-based Christofides algorithm, find a minimum spanning tree of the graph.
-Then, for a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)graph 2-connected.
-If the graph is not complete we can instead add an $O$-join, where $O$ is the set of odd-degree vertices in the spanning tree~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.
+In the classic graph-based Christofides algorithm for TSP, find a minimum spanning tree of the graph.
+Then, since TSP runs on a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)graph 2-connected.
+If we stop that algorithm without shortcutting, we have a feasible solution for TSP.
+For 2EC, however, the graph is not usually complete.
+We can instead add an $O$-join, where $O$ is the set of odd-degree vertices in the spanning tree~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.
 Graphs always have an even number of odd vertices since every edge has two endpoints, giving an even number of endpoints.}.
-In practice, the best-of-many Christofides (BOMC) algorithm~\cite{AKS15,GW17} works better than the classic Christofides algorithm.
+The best-of-many Christofides (BOMC) algorithm~\cite{AKS15} works better than the classic Christofides algorithm in practice~\cite{GW17}.
 The BOMC algorithm samples many spanning trees from the LP relaxation (with edges chosen proportionally to the LP value), augments each spanning tree with the matching, and taking the best overall solution.
 
-We now describe the polyhedral version of Christofides' algorithm specifically for Carr-Vempala points.
-Consider the subtour-elimination LP~(\ref{eq:subtour}) and any feasible point $x$.
-Consider any partitioning of the vertices of the graph into $b$ pieces and let $E_c$ be the set of edges that connect any two of the $b$ pieces.
+We now describe the polyhedral version of Christofides' algorithm~\cite{Wolsey} specifically for Carr-Vempala points.
+% Consider the LP~(\ref{eq:subtour}) in~(\ref{eq:subtour}) and any feasible point $x$. 
+%Consider any partitioning of the vertices of the graph into $b$ pieces and let $E_c$ be the set of edges that connect any two of the $b$ pieces.
 Then we have $\sum_{E_c} x_e \ge b$.
@@
 Thus we can scale any LP solution for the subtour-elimination polytope for an $n$-node graph by $(n-1)/n$ and it will still be feasible for the spanning tree polytope.
-
 %\cindy{I think it would be very helpful for the reader for you to remind them of the classic (graph-based, not polyhedral) metric (triangle-inequality) Christofides algorithm here and argue that it applies to 2EC.
@@
 %\cindy{I'm going to remove things like ``It's easy to see that,'' where I can. But we may need to add a justification or reference.}
-
-Let $x$ be a Carr-Vempala point defined on a graph $G=(V,E)$.  From the above discussion, we can write
+Let $x$ be a Carr-Vempala point (from~(\ref{eq:subtour})) defined on a graph $G=(V,E)$.  From~\cite{Vygen12}, we can decompose a slightly-scaled-down $x$ into a convex combination of spanning trees:
 \begin{equation}
@@
 %Consider the incidence vectors of feasible $O_i$-joins.
-Let $S$ be any subset of vertices with an even number of odd-degree vertices.
+% \cindy{Arash, do you also want to replace this longer discussion with a reference?}
+Adding an $O_i$-join to tree $T_i$ gives a solution to 2EC.
+% CAP: TODO, use later?
+%Let $S$ be any subset of vertices with an even number of odd-degree vertices.
 The $O_i$-join LP requires at least one edge joining $S$ to the rest of the vertices.
@@
 Therefore, since $x$ is a feasible solution to the subtour-elimination LP, $x/2$ is feasible for the $O_i$-join LP associated with spanning tree $T_i$.
-That is, $\frac{x}{2}$ is in the convex hull of incidence vectors of $O_i$-join of $G$, denoted $O_i\join(G)$.
+We will use Wolsey's observation~\cite{wolsey} that $\frac{x}{2}$ is in the convex hull of incidence vectors of the $O_i$-join of $G$ (denoted $O_i\join(G)$).
 %\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}
-
 %\cindy{Do you have to precompute the joins (If they are more than the spanning trees themselves)?
@@
 It seems that with a little more explanation, a reader who has not been immersed in 2EC and TSP could follow this.}
-
- We solve the following LP that allows us to find parity corrections that are good for the whole convex combination.
+We solve the following LP that allows us to find edges that simultaneously augment all the spanning trees to solutions to 2EC.
+%$O$-join-based parity corrections that are good for the whole convex combination.
 \begin{equation}\label{ojoinaverage}
@@
 \end{equation}
-The variables in the above LP are $y^i\in \mathbb{R}^{E_x}_{
-\geq 0}$ for $i\in [k]$. For each $i\in [k]$ we have $y^i\in O_i\join(G_x)$.
-\cindy{You say the $y^i$ are LP variables, not integers.
+The variables in the above LP are $y^i\in \mathbb{R}^{E}_{\geq 0}$ for $i\in [k]$, where $E$ is the number of edges in the graph.
+The parameters $\lambda_i$ are those we computed in~(\ref{eq:tree-decomp}).
+For each $i\in [k]$, we require $y^i$ to be in the dominant of $O_i\join(G_x)$.
+We enforce this by adding a set of constraints for each $i$ from~\cite[p.
+490]{schrijverbook}.
+These constraints force the inclusion of at least one edge from the cut associated with each set of vertices that have an even number of elements from $O_i$.
+The $O_i$ joins are selected fractionally, but because the $O_i$-join polytope is integral, we can find integral solutions (proposition~\ref{cara}).
+This method gives a ($\frac{|V|-1}{|V|}+\alpha$)-approximation for the specific instance $x$.
+In general this can be less than the classic $\frac{3}{2}$.
+%\cindy{You say the $y^i$ are LP variables, not integers.
 It even looks like they can even be more than $1$.
@@
 I would have expected the lambdas to be the variables, given their use as the convex combination multipliers in most of the paper.}
-This formulation allows the instance-specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$.
+%This formulation allows the instance-specific approximation ratio of Christofides' algorithm to be below $\frac{3}{2}$.
+\cindy{Arash, I liked your explanation about how a single edge will need to contribute 3/2 in the classic method.  You can add that if you'd like, but that might not be necessary given the time.}
 
@@
 We show for these points the apporoximation factor provided by FDT is always better than those from the polyhedral version of Christofides' algorithm.
-In Figure \ref{fdtvschris} the horizontal axis of the plot is indexed with the 60 Carr-Vempala points that we considered.
+In Figure~\ref{fdtvschris} the horizontal axis of the plot is indexed with the 60 Carr-Vempala points that we considered.
 For each Carr-Vempala point $x$, there are two data points.
-The value of the first data point depicted by a circle on the vertical axis is $\frac{|V|-1}{|V|}+\alpha$  and $\alpha$ is the optimal solution to (\ref{ojoinaverage}).
-\cindy{TODO: say when giving the LP~(\ref{ojoinaverage}) how that gives a solution to TAP with this value.}
+The value of the first data point depicted by a circle on the vertical axis is $\frac{|V|-1}{|V|}+\alpha$  where $\alpha$ is the optimal solution to (\ref{ojoinaverage}).
+%\cindy{TODO: say when giving the LP~(\ref{ojoinaverage}) how that gives a solution to TAP with this value.}
 The value of the second data point depicted by a cross on the vertical axis is $C$ where $C$ is obtained from applying Theorem \ref{FDT2EC} to $x$.

### 2020-08-08 FDT2020/main-section.tex
TAP runtime comments. A comment on Lemma 7

@@
 
-Consider an instance $I=(A,b)$ of the IP formulation.
+Consider an IP instance $I=(A,b)$.
 Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively.
@@
 	Given $\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time, such that $\bar{x}\leq \tilde{x}$.\end{lemma}
-Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up $x^*$ (or any fractional point in $P$) gives us a point in $\dom(P)$.
+Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up $x^*$ (or any fractional point in $P$) gives us a point in $\dom(P)$.
+\cindy{Does this Lemma need the caveat that the instance has a finite integrality gap?}
 Hence, we can assume in the proof below that $\tilde{x}_i= 0$ for $i=t+1,\ldots,n$. 
@@
 We compare the FDT solutions to those from the circulation-based 2-approximation algorithm of Frederickson and J\'{a}J\'{a}~\cite{FJ81} in Figure \ref{fjvsfdt}.
-\cindy{We should say something about running time.
+The simple FJ heuristic was faster than FDT, from about 8x to about 60x on our examples.
+However, FDT still ran in less than a minute on the bigger problems and less than 10 seconds on the others.
+FDT (in the worst case) solves $\Omega(m^2)$ LPs, where $m$ is the number of edges, and FJ solves one LP.
+So the difference in running time, which depends on instance size, is not surprising.
+FDT runs in polynomial time and usually gives much better solutions than FJ.
+%\cindy{We should say something about running time.
 Since we showed running time in part a, the reader will just assume otherwise that our running time is terrible compared to the Fredrickson and J\'{a}J\'{a} algorithm.}

### 2020-08-08 FDT2020/main-section.tex
arash comments in page 20

@@
 
-As described in Section~\ref{sec:2EC-intro}), when the LP optimum for (\ref{eq:subtour}) is a Carr-Vempala point (see Figure~\ref{fig:CVpoint}), the integrality gap of that instance is equal to that of 2EC.
+As described in Section~\ref{sec:2EC-intro}, when the LP optimum for (\ref{eq:subtour}) is a Carr-Vempala point (see Figure~\ref{fig:CVpoint}), the integrality gap of that instance is equal to that of 2EC.
 So in that sense, these are the hardest fractional points to round to a feasible solution.
@@
 In the classic graph-based Christofides algorithm for TSP, find a minimum spanning tree of the graph.
-Then, since TSP runs on a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)graph 2-connected.
+Then, since TSP runs on a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)graph 2-edge-connected.
 If we stop that algorithm without shortcutting, we have a feasible solution for TSP.
+\arash{The following sentence is not accurate, Metric-TSP is the same as TSP on a non-complete graph where we can take multiple copies of the edges, Metric-2EC (given complete graph with metric costs find the minimum cost 2-edge-connected SUBgraph -no doubling of edges-) is the same as 2EC on a non-complete graph where we can take multiple copies of edges.}
 For 2EC, however, the graph is not usually complete.
@@
 The BOMC algorithm samples many spanning trees from the LP relaxation (with edges chosen proportionally to the LP value), augments each spanning tree with the matching, and taking the best overall solution.
+
+\arash{I think here we should say that something like this: the polyhedral analaysis of Christofides shows that if $x\in \subtour(G)$, then $\frac{3}{2}x$ dominates a convex combination of connected Eulerian (hence 2-edge-connected) multigraph of $G$ \cite{wolsey,shmoyswilliamson}.
+This bound holds for any point $x\in \subtour(G)$ for any graph $G$, including any Carr-Vempala point.
+Below we ask if this bound can be improved for specific instances by doing a slightly improved analysis of the algorithm}\arash{Then we explain the LP in (32)}
 
@@
 %\cindy{I'm going to remove things like ``It's easy to see that,'' where I can. But we may need to add a justification or reference.}
-Let $x$ be a Carr-Vempala point (from~(\ref{eq:subtour})) defined on a graph $G=(V,E)$.  From~\cite{Vygen12}, we can decompose a slightly-scaled-down $x$ into a convex combination of spanning trees:
+Let $x$ be a Carr-Vempala point (from~(\ref{eq:subtour})) defined on a graph $G=(V,E)$.
+\arash{I think it's better to say that: It is a well-known fact that if $x\in \subtour(G)$, then $\frac{|V|-1}{|V|}x$ can be written as a convex combination of spanning trees of $G$ (See Proposition 2 in \cite{Vygen12} for instance), the reason is that this is because Vygen didn't come up with this.} From~\cite{Vygen12}, we can decompose a slightly-scaled-down $x$ into a convex combination of spanning trees:
 \begin{equation}
@@
 Therefore, since $x$ is a feasible solution to the subtour-elimination LP, $x/2$ is feasible for the $O_i$-join LP associated with spanning tree $T_i$.
+\arash{I still think this following sentence is confusing: we are not using the observation of Wolsey.
+Actually I don't think Wolsey spefically talks about writing 3/2x as a convex combination of solutions...
+I think it's would be better if we just explain how $(\frac{|V|-1}{|V|} + \alpha) x$ as convex combination of solutions and cite Wolsey as a general thing.
+How about deleting the next sentence, and after describing the LP below saying that $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ is a feasible solution to this LP yielding the integarlity gap of $\frac{3}{2}$ of the subtour elimination relaxation for the TSP \cite{wolsey}.}
 We will use Wolsey's observation~\cite{wolsey} that $\frac{x}{2}$ is in the convex hull of incidence vectors of the $O_i$-join of $G$ (denoted $O_i\join(G)$).
@@
 \begin{equation}\label{ojoinaverage}
-\min \{ \alpha:\;\sum_{i=1}^{k} \lambda_i y^i = \alpha \cdot x,\;  y^i \in O_i\join(G) \; \mbox{for $i\in [k]$}\}.
+\min \{ \alpha:\;\sum_{i=1}^{k} \lambda_i y^i = \alpha \cdot x,\;  y^i \in \dom(O_i\join(G)) \; \mbox{for $i\in [k]$}\}.
 \end{equation}
@@
 The parameters $\lambda_i$ are those we computed in~(\ref{eq:tree-decomp}).
-For each $i\in [k]$, we require $y^i$ to be in the dominant of $O_i\join(G_x)$.
+For each $i\in [k]$, we require $y^i$ to be in the dominant of $O_i\join(G)$.
 We enforce this by adding a set of constraints for each $i$ from~\cite[p.
@@
 These constraints force the inclusion of at least one edge from the cut associated with each set of vertices that have an even number of elements from $O_i$.
-The $O_i$ joins are selected fractionally, but because the $O_i$-join polytope is integral, we can find integral solutions (proposition~\ref{cara}).
+The $O_i$ joins are selected fractionally \arash{(specifically $y^i$ need not be integer vectors)}, but because the $O_i$-join polytope is integral, we can \arash{replace $y^i$ with a convex combination of} find $O_i$-joins of $G$ (proposition~\ref{cara}).
 This method gives a ($\frac{|V|-1}{|V|}+\alpha$)-approximation for the specific instance $x$.

### 2020-08-08 FDT2020/main-section.tex
Addressing Arash's comments

@@
 Then, since TSP runs on a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)graph 2-edge-connected.
-If we stop that algorithm without shortcutting, we have a feasible solution for TSP.
+If we stop that algorithm without shortcutting, we have a feasible solution for Metric-2EC (given a complete graph, find the minimum-cost 2-edge-connected subgraph, with no multiedges).
 \arash{The following sentence is not accurate, Metric-TSP is the same as TSP on a non-complete graph where we can take multiple copies of the edges, Metric-2EC (given complete graph with metric costs find the minimum cost 2-edge-connected SUBgraph -no doubling of edges-) is the same as 2EC on a non-complete graph where we can take multiple copies of edges.}
-For 2EC, however, the graph is not usually complete.
-We can instead add an $O$-join, where $O$ is the set of odd-degree vertices in the spanning tree~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.
+\cindy{It sounded like 2EC doesn't assume a complete graph.  But I removed the sentence.  Is the following OK?}
+For 2EC, instead of a matching, we add an $O$-join, where $O$ is the set of odd-degree vertices in the spanning tree~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.
 Graphs always have an even number of odd vertices since every edge has two endpoints, giving an even number of endpoints.}.
 The best-of-many Christofides (BOMC) algorithm~\cite{AKS15} works better than the classic Christofides algorithm in practice~\cite{GW17}.
-The BOMC algorithm samples many spanning trees from the LP relaxation (with edges chosen proportionally to the LP value), augments each spanning tree with the matching, and taking the best overall solution.
+The BOMC algorithm samples many spanning trees from the LP relaxation (with edges chosen proportionally to the LP value), augments each spanning tree with the matching, and takes the best solution.
 
@@
 Below we ask if this bound can be improved for specific instances by doing a slightly improved analysis of the algorithm}\arash{Then we explain the LP in (32)}
+\cindy{I like that and have added it, but I don't think it is too much detail to walk the reader through the decompositions.}
 
-We now describe the polyhedral version of Christofides' algorithm~\cite{Wolsey} specifically for Carr-Vempala points.
+The polyhedral analysis of Christofides shows that if $x\in \subtour(G)$, then $\frac{3}{2}x$ dominates a convex combination of connected Eulerian (hence 2-edge-connected) multigraphs of $G$~\cite{wolsey,shmoyswilliamson}.
+This bound holds for any point $x\in \subtour(G)$ for any graph $G$, including any Carr-Vempala point.
+We show how this bound can be improved for specific instances by doing a slightly improved analysis of the algorithm.
+
+%We now describe the polyhedral version of Christofides' algorithm~\cite{Wolsey} specifically for Carr-Vempala points.
 % Consider the LP~(\ref{eq:subtour}) in~(\ref{eq:subtour}) and any feasible point $x$. 
@@
 Let $x$ be a Carr-Vempala point (from~(\ref{eq:subtour})) defined on a graph $G=(V,E)$.
-\arash{I think it's better to say that: It is a well-known fact that if $x\in \subtour(G)$, then $\frac{|V|-1}{|V|}x$ can be written as a convex combination of spanning trees of $G$ (See Proposition 2 in \cite{Vygen12} for instance), the reason is that this is because Vygen didn't come up with this.} From~\cite{Vygen12}, we can decompose a slightly-scaled-down $x$ into a convex combination of spanning trees:
+\arash{I think it's better to say that: It is a well-known fact that if $x\in \subtour(G)$, then $\frac{|V|-1}{|V|}x$ can be written as a convex combination of spanning trees of $G$ (See Proposition 2 in \cite{Vygen12} for instance), the reason is that this is because Vygen didn't come up with this.}
+%From~\cite{Vygen12}, we can decompose a slightly-scaled-down $x$ into a convex combination of spanning trees:
+If $x\in \subtour(G)$, then $\frac{|V|-1}{|V|}x$ can be written as a convex combination of spanning trees of $G$ (See Proposition 2 in~\cite{Vygen12} for instance).  More explicitly,
 \begin{equation}
@@
 How about deleting the next sentence, and after describing the LP below saying that $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ is a feasible solution to this LP yielding the integarlity gap of $\frac{3}{2}$ of the subtour elimination relaxation for the TSP \cite{wolsey}.}
-We will use Wolsey's observation~\cite{wolsey} that $\frac{x}{2}$ is in the convex hull of incidence vectors of the $O_i$-join of $G$ (denoted $O_i\join(G)$).
+%We will use Wolsey's observation~\cite{wolsey} that $\frac{x}{2}$ is in the convex hull of incidence vectors of the $O_i$-join of $G$ (denoted $O_i\join(G)$).
 %\cindy{There was another instance of ``It's easy to see that...'' Given that (quite reasonably) you do not expect the reader to know what an O-join is, you should probably just give the short justification for this statement and remove ``It's easy to see that.''}
@@
 These constraints force the inclusion of at least one edge from the cut associated with each set of vertices that have an even number of elements from $O_i$.
-The $O_i$ joins are selected fractionally \arash{(specifically $y^i$ need not be integer vectors)}, but because the $O_i$-join polytope is integral, we can \arash{replace $y^i$ with a convex combination of} find $O_i$-joins of $G$ (proposition~\ref{cara}).
-This method gives a ($\frac{|V|-1}{|V|}+\alpha$)-approximation for the specific instance $x$.
-In general this can be less than the classic $\frac{3}{2}$.
+The  $y^i$ need not be integer vectors.
+Because the $O_i$-join polytope is integral, we can replace $y^i$ with a convex combination of $O_i$-joins of $G$ (proposition~\ref{cara}).
+Setting $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ gives a feasible solution to this LP, yielding the integarlity gap of $\frac{3}{2}$ of the subtour elimination relaxation for the TSP \cite{wolsey}.
+More generally, this method gives a ($\frac{|V|-1}{|V|}+\alpha$)-approximation for the specific instance $x$.
+% In general this can be less than the classic $\frac{3}{2}$.
+
 %\cindy{You say the $y^i$ are LP variables, not integers.

### 2020-08-09 FDT2020/main-section.tex
Changing the name of the helper LP for DomToIP and minor edits.

@@
 Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
-Notice that we can set $x^{(0)}=\tilde{x}$.
+We can set $x^{(0)}=\tilde{x}$.
 Now consider the following linear program.
@@
 \begin{align}
-\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
+\HelperLP(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
 &\;\text{s.t.} \quad \;\;Az\geq b \\
@@
 
-If the optimal value to $\DOMtoS(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$.
+If the optimal value to $\HelperLP(x^{(\ell)})$ is 0, then let $x^{(\ell+1)}_{\ell+1} = 0$.
 Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$.
@@
 		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
-		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
+		$\eta \leftarrow$ optimal value of $ \HelperLP(x^{(\ell)})$\\
 		\eIf{$\eta = 0$}{
@@
 We prove that indeed $x^{(t)}\in S$.
-First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomToIP that $\DOMtoS(x^{(\ell)})$ is feasible.
+First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomToIP that $\HelperLP(x^{(\ell)})$ is feasible.
 We show something stronger.
@@
 \end{align*}
-Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible.
+If $\LP^{(\ell)}$ is a non-empty set then $\HelperLP(x^{(\ell)})$ is feasible.
 We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
@@
 Now assume $\IP^{(\ell)}$ is non-empty for some $\ell \in [t-2]$.
-Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\DOMtoS(x^{(\ell)})$ has an optimal solution $z^*$.
+Since $\IP^{(\ell)}\subseteq\LP^{(\ell)}$ we have $\LP^{(\ell)}\neq \emptyset$ and hence the $\HelperLP(x^{(\ell)})$ has an optimal solution $z^*$.
 
@@
 Consider iteration $j$ of the DomToIP algorithm.
-Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$.
-We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero.
-However, $z$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0.
+We have $z\leq x^{(\ell+1)}\leq x^{(j)}$.
+We also have $x^{(j)}_j=1$ which implies when we solved $\HelperLP(x^{(j-1)})$ the optimal value was strictly larger than zero.
+However, $z$ is a feasible solution to $\HelperLP(x^{(j-1)})$ and gives an objective value of 0.
 This is a contradiction, so $z\in \IP^{(\ell+1)}$.
@@
 We have $x^{(\ell+1)}_{\ell+1}=1$.
-Notice that for each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e.
+For each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e.
 $z_{\ell+1}=1$.
@@
 We just need to show that $z'_t = 1$.
-Assume $z'_t	 = 0$ for contradiction, then $z'\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $z$ being the optimal solution.
+Assume $z'_t	 = 0$ for contradiction, then $z'\in \LP^{(t-1)}$ has objective value of $0$ for $\HelperLP(x^{(t-1)})$, this is a contradiction to $z$ being the optimal solution.
 This concludes the proof of Lemma \ref{domlemma}.
@@
 
-		Notice that $\theta = \gamma$ is in fact a feasible solution to $\prun(L')$.
+		Setting $\theta = \gamma$ gives a feasible solution to $\prun(L')$.
 Let $\theta^*$ be the optimal vertex solution to this LP.
@@
 Set $L_{i+1}$ which consists of $x^j$ for $j=1,\ldots,|L'|$ and their corresponding multipliers $\theta^*_j$ satisfy the properties in the statement of the lemma.
-Notice that, we can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$.
+We can discard the nodes in $L_{i+1}$ that have $\theta^*_j=0$, so $|L_{i+1}| \leq t$.
 Also, since $\theta^*$ is optimal and $\gamma$ is feasible for $\prun(L')$, we have $\sum_{j=1}^{|L'|} \theta^*_j \geq \sum_{j=1}^{|L'|}\gamma_j \geq \frac{1}{g^{i+1}}$.
@@
 
-		Note that each $F'_i$ contains at least one copy of every edge in any path $P_f$, except for at most one edge in the path.
+		Each $F'_i$ contains at least one copy of every edge in any path $P_f$, except for at most one edge in the path.
 We will obtain 2-edge-connected multi-subgraphs $F_1,\ldots,F_k$ of $G$ using $F'_1,\ldots,F'_k$, respectively.
@@
 It is easy to check that $x^j$ , $\theta_j$ for $j=0,1,2$ is a feasible solution to the LP above.
-Notice that $\sum_{j=0,1,2}\theta_j = \frac{\ceil{\frac{2}{\epsilon}}-1}{g(\2ec)\ceil{\frac{2}{\epsilon}}}$.
+We have $\sum_{j=0,1,2}\theta_j = \frac{\ceil{\frac{2}{\epsilon}}-1}{g(\2ec)\ceil{\frac{2}{\epsilon}}}$.
 By assumption, we have $\frac{\ceil{\frac{2}{\epsilon}}-1}{g(\2ec)\ceil{\frac{2}{\epsilon}}}\leq  \frac{1}{g(\2ec)}-\epsilon$, which is a contradiction.
@@
 Finally, we just need to apply Lemma \ref{rounddown} to obtain the 2-edge-connected multi-subgraphs from every solution in $L_t$.
-Notice that since $x$ is an extreme point we have $t\leq 2|V|-1$ \cite{boydpulley}.
+Since $x$ is an extreme point we have $t\leq 2|V|-1$ \cite{boydpulley}.
 By Lemma \ref{2ecpruning} we have
@@
 I don't immediately see other places where it's used in math mode, and therefore needs the macro.}
-We know $\frac{3}{2}\leq g(\tap)\leq 2$~\cite{FJ81,32gaptap}. Notice that $\min_{x\in \tap(T,L)}cx$ is a binary IP.
+We know $\frac{3}{2}\leq g(\tap)\leq 2$~\cite{FJ81,32gaptap}. The IP $\min_{x\in \tap(T,L)}cx$ is binary.
 
@@
 I think it's would be better if we just explain how $(\frac{|V|-1}{|V|} + \alpha) x$ as convex combination of solutions and cite Wolsey as a general thing.
-How about deleting the next sentence, and after describing the LP below saying that $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ is a feasible solution to this LP yielding the integarlity gap of $\frac{3}{2}$ of the subtour elimination relaxation for the TSP \cite{wolsey}.}
+How about deleting the next sentence, and after describing the LP below saying that $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ is a feasible solution to this LP yielding an integrality gap of $\frac{3}{2}$ for the subtour-elimination relaxation for the TSP \cite{wolsey}.}
 %We will use Wolsey's observation~\cite{wolsey} that $\frac{x}{2}$ is in the convex hull of incidence vectors of the $O_i$-join of $G$ (denoted $O_i\join(G)$).

### 2020-08-09 FDT2020/Introduction.tex
Adding a section label
unified Subtour elimination and multi-graph notation

@@
 In general the integrality gap is defined similarly for any objective function, but we wish to be explicit about the class of problems we assume in this paper.
-For example consider the minimum cost \textsc{2-edge-connected multi-subgraph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected subgraph of $G$, with multiedges allowed.
+For example consider the minimum cost \textsc{2-edge-connected multi-subgraph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected subgraph of $G$, with multi-edges allowed.
 A graph is 2-edge-connected if there are at least two edge-disjoint paths between every pair of vertices.
@@
 \end{equation}
-For example, the integrality gap of the subtour elimination relaxation for the 2EC is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}.
+For example, the integrality gap of the subtour-elimination relaxation for the 2EC is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}.
 Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation to bound the quality of a feasible solution.
@@
 For input graph $G$, let $\subtour(G)$ denote the feasible region of this LP.
-Let $\2ec(G)$ be the convex hull of incidence vectors\footnote{The incidence vector $x$ of a 2-edge-connected multigraph has an element for each edge $e$, with $x_e \in \{0,1,2\}$ indicating the number of times edge $e$ appears in the solution.} of 2-edge-connected multi-subgraphs of graph $G$.
+Let $\2ec(G)$ be the convex hull of incidence vectors\footnote{The incidence vector $x$ of a 2-edge-connected multi-subgraph has an element for each edge $e$, with $x_e \in \{0,1,2\}$ indicating the number of times edge $e$ appears in the solution.} of 2-edge-connected multi-subgraphs of graph $G$.
 Following the definition in (\ref{gapproblem}) have
@@
 \subsubsection{2-edge-connected multi-subgraph problem}
+\label{sec:2EC-intro}
 Known polyhedral structure makes it easier to study integrality gaps for such problems.
@@
 %\cindy{We don't define the TSP, though probably don't need to since that really is so classical, and we don't mention it again.  We could consider citing the TSP book.}
-Benoit and Boyd~\cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices.
+Benoit and Boyd~\cite{TSPcompute} used a quadratic program to show the integrality gap of the subtour-elimination relaxation for the TSP, $g(\tsp)$, is at most $\frac{20}{17}$ for graphs with at most 10 vertices.
 Alexander et al.

### 2020-08-09 FDT2020/conclusion.tex
unified Subtour elimination and multi-graph notation

@@
 \end{equation*}
-where the last $p$ variables are continous, $P(A,b) = \{x\in \mathbb{R}^n: Ax\geq b\}$
-\cindy{should this be $P(A,b) = \{x\in \mathbb{R}^{n+p}: Ax\geq b\}$?}
+where the last $p$ variables are continous, $P(A,b) = \{x\in \mathbb{R}^{n+p}: Ax\geq b\}$
+%\cindy{should this be $P(A,b) = \{x\in \mathbb{R}^{n+p}: Ax\geq b\}$?}
 and define
@@
 our main results work.
-In fact our implementation of the subtour elimination formulation is based on an extended formulation with auxiliary variables (see \cite{subtour-extended}).
+In fact our implementation of the subtour-elimination relaxation is based on an extended formulation with auxiliary variables (see \cite{subtour-extended}).
 We removed this extension to make the presentation simpler.

### 2020-08-09 FDT2020/main-section.tex
unified Subtour elimination and multi-graph notation

@@
 In the classic graph-based Christofides algorithm for TSP, find a minimum spanning tree of the graph.
-Then, since TSP runs on a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)graph 2-edge-connected.
+Then, since TSP runs on a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)-subgraph 2-edge-connected.
 If we stop that algorithm without shortcutting, we have a feasible solution for Metric-2EC (given a complete graph, find the minimum-cost 2-edge-connected subgraph, with no multiedges).
@@
 \cindy{It sounded like 2EC doesn't assume a complete graph.  But I removed the sentence.  Is the following OK?}
+\arash{Still not quite accurate.
+The sentence gives the impression that changing matching with $T$-join is the difference between TSP and 2EC, but its the difference between working with complete graph with metric costs and a non-complete graph where doubling edges is allowed.}
 For 2EC, instead of a matching, we add an $O$-join, where $O$ is the set of odd-degree vertices in the spanning tree~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.
@@
 
-\arash{I think here we should say that something like this: the polyhedral analaysis of Christofides shows that if $x\in \subtour(G)$, then $\frac{3}{2}x$ dominates a convex combination of connected Eulerian (hence 2-edge-connected) multigraph of $G$ \cite{wolsey,shmoyswilliamson}.
+%\arash{I think here we should say that something like this: the polyhedral analaysis of Christofides shows that if $x\in \subtour(G)$, then $\frac{3}{2}x$ dominates a convex combination of connected Eulerian (hence 2-edge-connected) multigraph of $G$ \cite{wolsey,shmoyswilliamson}.
 This bound holds for any point $x\in \subtour(G)$ for any graph $G$, including any Carr-Vempala point.
 Below we ask if this bound can be improved for specific instances by doing a slightly improved analysis of the algorithm}\arash{Then we explain the LP in (32)}
-\cindy{I like that and have added it, but I don't think it is too much detail to walk the reader through the decompositions.}
+%\cindy{I like that and have added it, but I don't think it is too much detail to walk the reader through the decompositions.}
 
-The polyhedral analysis of Christofides shows that if $x\in \subtour(G)$, then $\frac{3}{2}x$ dominates a convex combination of connected Eulerian (hence 2-edge-connected) multigraphs of $G$~\cite{wolsey,shmoyswilliamson}.
+The polyhedral analysis of Christofides shows that if $x\in \subtour(G)$, then $\frac{3}{2}x$ dominates a convex combination of connected Eulerian (hence 2-edge-connected) multi-subgraphs of $G$~\cite{wolsey,shmoyswilliamson}.
 This bound holds for any point $x\in \subtour(G)$ for any graph $G$, including any Carr-Vempala point.
@@
 Let $x$ be a Carr-Vempala point (from~(\ref{eq:subtour})) defined on a graph $G=(V,E)$.
-\arash{I think it's better to say that: It is a well-known fact that if $x\in \subtour(G)$, then $\frac{|V|-1}{|V|}x$ can be written as a convex combination of spanning trees of $G$ (See Proposition 2 in \cite{Vygen12} for instance), the reason is that this is because Vygen didn't come up with this.}
+%\arash{I think it's better to say that: It is a well-known fact that if $x\in \subtour(G)$, then $\frac{|V|-1}{|V|}x$ can be written as a convex combination of spanning trees of $G$ (See Proposition 2 in \cite{Vygen12} for instance), the reason is that this is because Vygen didn't come up with this.}
 %From~\cite{Vygen12}, we can decompose a slightly-scaled-down $x$ into a convex combination of spanning trees:
@@
 Therefore, since $x$ is a feasible solution to the subtour-elimination LP, $x/2$ is feasible for the $O_i$-join LP associated with spanning tree $T_i$.
-\arash{I still think this following sentence is confusing: we are not using the observation of Wolsey.
+%\arash{I still think this following sentence is confusing: we are not using the observation of Wolsey.
 Actually I don't think Wolsey spefically talks about writing 3/2x as a convex combination of solutions...
@@
 Because the $O_i$-join polytope is integral, we can replace $y^i$ with a convex combination of $O_i$-joins of $G$ (proposition~\ref{cara}).
-Setting $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ gives a feasible solution to this LP, yielding the integarlity gap of $\frac{3}{2}$ of the subtour elimination relaxation for the TSP \cite{wolsey}.
+Setting $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ gives a feasible solution to this LP, yielding the integarlity gap of $\frac{3}{2}$ of the subtour-elimination relaxation for the TSP \cite{wolsey}.
 More generally, this method gives a ($\frac{|V|-1}{|V|}+\alpha$)-approximation for the specific instance $x$.

### 2020-08-09 FDT2020/main-section.tex
Adding a comment in Dom2IP section.

@@
 
-The above procedure suggests how to find $x^{(\ell+1)}$ from $x^{(\ell)}$.
-The DomToIP algorithm initializes with $x^{(0)}=\tilde{x}$ and  iteratively calls this procedure in order to obtain $x^{(t)}$.
+The above procedure shows how to find $x^{(\ell+1)}$ from $x^{(\ell)}$. The DomToIP algorithm initializes with $x^{(0)}=\tilde{x}$ and  iteratively calls this procedure in order to obtain $x^{(t)}$.
 
@@
 We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
-First notice that $\LP^{(0)}$ is clearly feasible since by definition $x^{(0)}\in \dom(P)$, meaning there exists $z\in P$ such that $z\leq x^{(0)}$.
+First, $\LP^{(0)}$ is feasible since by definition $x^{(0)}\in \dom(P)$, meaning there exists $z\in P$ such that $z\leq x^{(0)}$.
 By Theorem \ref{CV2}, there exists $\tilde{z}^i\in S$ and $\theta_i\geq 0$ for $i\in [k]$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
+\cindy{Is this the place (and others like it) where we require $g$ to be finite?}
 Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
@@
 In the first case, we have $z^*_{\ell+1}=0$.
-In this case we have $x^{(\ell+1)}_{\ell+1}=0$.
+In this case we set $x^{(\ell+1)}_{\ell+1}=0$.
 Since $z^*\leq x^{(\ell+1)}$, we have $z^*\in \LP^{(\ell+1)}$.
@@
 If $z\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$.
-Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
+Without loss of generality assume $j$ is the minimum index (between $1$ and $\ell$) satisfying $z_j < x^{(\ell+1)}_{j}$.
 Consider iteration $j$ of the DomToIP algorithm.
 We have $z\leq x^{(\ell+1)}\leq x^{(j)}$.
+\cindy{I certainly believe you and Bob on correctness, and I was convinced of the correctness of (and wrote a bunch of the proofs for) the earlier version.
+But while I have a little time, I'll point out places where I was confused (and hence a reader might be).
+This last statement I don't see right away.
+It doesn't seem that $x^{(\ell+1)}\leq x^{(j)}$ in general when $j < \ell + 1$.
+It seems that in general, for a fractional element $x_q$, DomToIP can round the $q$th element either up or down depending on whether it's OK to round down (future feasibility assured).
+So it seems that $x^j$, which is more fractional, could have some elements smaller and some elements larger than the more integral $x^{(\ell+1)}$.
+This confusion carries forward to the assertion that $z$ is a feasible solution to $\HelperLP(x^{(j-1)})$.
+Suppose that $x_q = .2$ for some $q < \ell$ and Dom2IP rounded the $q$th element up to $1$.
+$\HelperLP(x^{q})$ has a constraint $z_q \le 0.2$, but subsequent LPs, such as $\HelperLP(x^{(\ell)})$ have a constraint $x_j = 1$.
+So the later LP solutions may not be feasible for the earlier ones.}
 We also have $x^{(j)}_j=1$ which implies when we solved $\HelperLP(x^{(j-1)})$ the optimal value was strictly larger than zero.
@@
 Now for the second case, assume $z^*_{\ell+1} > 0$.
-We have $x^{(\ell+1)}_{\ell+1}=1$.
+We set $x^{(\ell+1)}_{\ell+1}=1$.
 For each point $z\in \LP^{(\ell)}$ we have $z_{\ell+1} >0$, so for each $z\in \IP^{(\ell)}$ we have $z_{\ell+1}>0$, i.e.
@@
 Because the $O_i$-join polytope is integral, we can replace $y^i$ with a convex combination of $O_i$-joins of $G$ (proposition~\ref{cara}).
-Setting $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ gives a feasible solution to this LP, yielding the integarlity gap of $\frac{3}{2}$ of the subtour-elimination relaxation for the TSP \cite{wolsey}.
+Setting $y^i = \frac{x}{2}$ and $\alpha = \frac{1}{2}$ gives a feasible solution to this LP, yielding an integrality gap of at most $\frac{3}{2}$ for the subtour-elimination relaxation for the TSP \cite{wolsey}.
 More generally, this method gives a ($\frac{|V|-1}{|V|}+\alpha$)-approximation for the specific instance $x$.

### 2020-08-09 FDT2020/main-section.tex
typo in comment
Removing the big comment.  Fixes related to my earlier comments/confusion.

--- 2020-08-09 FDT2020/main-section.tex
@@
 Also, for both sections let $x^*$ be the optimal solution to the LP formulation and assume $t=|\spp(x^*)|$.
-Without loss of generality we can assume $x^*_i = 0$ for $i=t+1,\ldots,n$.
+Reorder variables as necessary to put all the nonzero variables into the first $t$ indices.
+So we can assume $x^*_i = 0$ for $i=t+1,\ldots,n$.
 %\cindy{TODO: Is this something that should be clear to the reader with what they know at this point?
@@
 \begin{lemma}\label{domlemma}
-	Given $\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time, such that $\bar{x}\leq \tilde{x}$.\end{lemma}
+	Given an integral vector in the dominant of an LP relaxation ($\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$) for an IP instance that has integrality gap $g < \infty$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time such that $\bar{x}\leq \tilde{x}$.\end{lemma}
 Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up $x^*$ (or any fractional point in $P$) gives us a point in $\dom(P)$.
-\cindy{Does this Lemma need the caveat that the instance has a finite integrality gap?}
+\cindy{I added the caveat that the instance has a finite integrality gap and made it a little more self-contained.  Is it OK?}
 Hence, we can assume in the proof below that $\tilde{x}_i= 0$ for $i=t+1,\ldots,n$. 
@@
 
-We start by introducing an algorithm that ``fixes" the variables iteratively, starting from the first coordinate and ending at the $t$-th coordinate.
-Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
-We can set $x^{(0)}=\tilde{x}$.
-Now consider the following linear program.
-The variables of this linear program are the $z\in \mathbb{R}^n$ variables.
+We introduce an algorithm that considers each of the variables iteratively, starting from the first coordinate and ending at the $t$-th coordinate.
+If the initial (integral) point $\tilde{x}$ has the variable set to $1$, the algorithm tries to reduce the variable to $0$ if possible.
+We run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
+\cindy{I think the previous sentence also added to my confusion before (along with the term ``fix'' which I have replaced).
+After $\ell$ iterations the first $\ell$ components are integer, but they were integer before.
+Did you intend to say that we finalize a 0-1 value for the first $\ell$ coordinates?}
+We can set $x^{(0)}=\tilde{x}$. Now consider the following linear program. The variables of this linear program are the $z\in \mathbb{R}^n$.
 \begin{align}
@@
 We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
-First notice that $\LP^{(0)}$ is clearly feasible since by definition $x^{(0)}\in \dom(P)$, meaning there exists $z\in P$ such that $z\leq x^{(0)}$.
+First, $\LP^{(0)}$ is feasible since by definition $x^{(0)}\in \dom(P)$, meaning there exists $z\in P$ such that $z\leq x^{(0)}$.
 By Theorem \ref{CV2}, there exists $\tilde{z}^i\in S$ and $\theta_i\geq 0$ for $i\in [k]$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
+(This assumes a finite integrality gap $g$).
+%\cindy{Is this the place (and others like it) where we require $g$ to be finite?}
 Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
@@
 If $z\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$.
-Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$.
+Without loss of generality assume $j$ is the minimum index (between $1$ and $\ell$) satisfying $z_j < x^{(\ell+1)}_{j}$.
 Consider iteration $j$ of the DomToIP algorithm.
 We have $z\leq x^{(\ell+1)}\leq x^{(j)}$.
+%\cindy{I certainly believe you and Bob on correctness, and I was convinced of the correctness of (and wrote a bunch of the proofs for) the earlier version.
+But while I have a little time, I'll point out places where I was confused (and hence a reader might be).
+This last statement I don't see right away.
+It doesn't seem that $x^{(\ell+1)}\leq x^{(j)}$ in general when $j < \ell + 1$.
+It seems that in general, for a fractional element $x_q$, DomToIP can round the $q$th element either up or down depending on whether it's OK to round down (future feasibility assured).
+So it seems that $x^j$, which is more fractional, could have some elements smaller and some elements larger than the more integral $x^{(\ell+1)}$.
+This confusion carries forward to the assertion that $z$ is a feasible solution to $\HelperLP(x^{(j-1)})$.
+Suppose that $x_q = .2$ for some $q < \ell$ and Dom2IP rounded the $q$th element up to $1$.
+$\HelperLP(x^{q})$ has a constraint $z_q \le 0.2$, but subsequent LPs, such as $\HelperLP(x^{(\ell)})$ have a constraint $x_q = 1$.
+So the later LP solutions may not be feasible for the earlier ones.}
 We also have $x^{(j)}_j=1$ which implies when we solved $\HelperLP(x^{(j-1)})$ the optimal value was strictly larger than zero.

### 2020-08-09 FDT2020/main-section.tex
A few fixes, and a question for Arash.

@@
 We just need to show that $z'_t = 1$.
-Assume $z'_t	 = 0$ for contradiction, then $z'\in \LP^{(t-1)}$ has objective value of $0$ for $\HelperLP(x^{(t-1)})$, this is a contradiction to $z$ being the optimal solution.
+Assume $z'_t	 = 0$ for contradiction.
+Then $z'\in \LP^{(t-1)}$ has objective value $0$ for $\HelperLP(x^{(t-1)})$.
+This is a contradiction to $z$ being the optimal solution to $\LP^{(t-1)}$.
 This concludes the proof of Lemma \ref{domlemma}.
@@
 %\arash{I made a small change here based on our discussion in the bottom of page 8}\cindy{Thanks!}
-Recall that $x^*$ was the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
+Recall that $x^*$ was the optimal solution to minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.
 In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm.
-We also remark that if $g(I)=1$, then the algorithm will give an exact decomposition of any feasible solution.
+We also remark that if $g(I)=1$, then the algorithm gives an exact decomposition of any feasible solution.
 
@@
 In each level of the tree, the algorithm maintain a conic combination of points with the properties mentioned above.
-Leaves of the FDT tree contain solutions with integer values for all the $x$ variables that dominate a point in $P$.
-In Lemma  \ref{domlemma} we saw how to turn these into points in $S$.
+Leaves of the FDT tree contain integral solutions
+%with integer values for all the $x$ variables
+that dominate a point in $P$. In Lemma~\ref{domlemma} we saw how to turn these into points in $S$.
 
@@
 \begin{lemma}\label{LPClemma}
-	Given $x'\in \dom(P)$ and $\ell\in [n]$ where $x'_{\ell}<1$, we can find in polynomial time vectors $\hat{x}^0,\hat{x}^1$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\gamma_0 + \gamma_1  \geq 1/g$, (ii) $\hat{x}^0$ and $\hat{x}^1$ are in  $ P$
-	,(iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
+	Given $x'\in \dom(P)$ and $\ell\in [n]$ where $x'_{\ell}<1$, in polynomial time we can find vectors $\hat{x}^0,\hat{x}^1$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\gamma_0 + \gamma_1  \geq 1/g$, (ii) $\hat{x}^0$ and $\hat{x}^1$ are in  $ P$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, and (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
 \end{lemma}
@@
 	Consider the following linear program which we denote by $\LPC(\ell,x')$. The variables of $\LPC(\ell,x')$ are $\gamma_0,\gamma_1$ and $x^0$ and $x^1$.
+\cindy{I think you mean that the $\lambda$s are variables, not $\gamma$s.
+However the above lemma uses $\gamma$ and then there is a mix of $\lambda$ and $\gamma$ below the LP.
+Can you please check that you intend to have both types and they are used properly?}
 	\begin{align}

### 2020-08-10 FDT2020/main-section.tex
linking lambda and gamma

@@
 \begin{proof}	
-	Consider the following linear program which we denote by $\LPC(\ell,x')$. The variables of $\LPC(\ell,x')$ are $\gamma_0,\gamma_1$ and $x^0$ and $x^1$.
-\cindy{I think you mean that the $\lambda$s are variables, not $\gamma$s.
+	Consider the following linear program which we denote by $\LPC(\ell,x')$. The variables of $\LPC(\ell,x')$ are $\lambda_0$, $\lambda_1$, $x^0$ and $x^1$.
+% \cindy{I think you mean that the $\lambda$s are variables, not $\gamma$s.
 However the above lemma uses $\gamma$ and then there is a mix of $\lambda$ and $\gamma$ below the LP.
@@
 
-	Let $x^0,x^1$, and $\gamma_0,\gamma_1$ be an optimal solution to the LP above.
-Let $\hat{x}^0 = x^0/\gamma_0$, $\hat{x}^1=x^1/\gamma_1$.
-This choice satisfies  (ii), (iii), (iv).
-To show that (i) is also satisfied we prove the following claim.
+	Let $x^0$, $x^1$, $\lambda_0$, and $\lambda_1$ be an optimal solution to the LP above. Set $\gamma_0=\lambda_0$ and $\gamma_1 = lambda_1$.
+\cindy{The sentence right before this is how I think you link the $\lambda$ in the LP to the $\gamma$ constants in the Lemma statement and the claim below, etc.}
+Let $\hat{x}^0 = x^0/\gamma_0$, $\hat{x}^1=x^1/\gamma_1$. This choice satisfies  (ii), (iii), (iv). To show that (i) is also satisfied we prove the following claim.
 
@@
 Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $x^*$ and multiplier 1.
-It is easy to check all the requirements in the lemma are satisfied for this choice.
+All the requirements in the lemma are satisfied for this choice.
 

### 2020-08-10 FDT2020/main-section.tex
fixing typo
added comments in 2.1 and lemma 8

@@
 If the initial (integral) point $\tilde{x}$ has the variable set to $1$, the algorithm tries to reduce the variable to $0$ if possible.
+\arash{A caution here: the phrase if possible a bit vague here.
+We round down to zero, if there is feasible solution to LP (so a point in $P(I)$, such that the first $\ell$ coordinates of it are all equal to the point $x^{(\ell)}$ that we have in iteration $\ell$ and its $\ell+1$-th coordinate is 0}.
 We run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
@@
 
-	Let $x^0$, $x^1$, $\lambda_0$, and $\lambda_1$ be an optimal solution to the LP above. Set $\gamma_0=\lambda_0$ and $\gamma_1 = lambda_1$.
+	Let $x^0$, $x^1$, $\lambda_0$, and $\lambda_1$ be an optimal solution to the LP above. Set $\gamma_0=\lambda_0$ and $\gamma_1 = \lambda_1$.
 \cindy{The sentence right before this is how I think you link the $\lambda$ in the LP to the $\gamma$ constants in the Lemma statement and the claim below, etc.}
 Let $\hat{x}^0 = x^0/\gamma_0$, $\hat{x}^1=x^1/\gamma_1$. This choice satisfies  (ii), (iii), (iv). To show that (i) is also satisfied we prove the following claim.
-
+	\arash{Now that I notice, we use $\lambda_0,\lambda_1,x^0,x^1}$ to represnt a feasible solution to the system 13-18.
+Since the optimal solution is use only for the duration of one sentence above maybe we can change the notation for the optimal solution.
+For instance use $y^0,y^1, \lambda^*_0,\lambda^*_1$}
 	\begin{claim}\label{CVexists}

### 2020-08-10 FDT2020/main-section.tex
Responding to Arash's comments.

@@
 Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up $x^*$ (or any fractional point in $P$) gives us a point in $\dom(P)$.
-\cindy{I added the caveat that the instance has a finite integrality gap and made it a little more self-contained.  Is it OK?}
+%\cindy{I added the caveat that the instance has a finite integrality gap and made it a little more self-contained.  Is it OK?}
 Hence, we can assume in the proof below that $\tilde{x}_i= 0$ for $i=t+1,\ldots,n$. 
@@
 
-We introduce an algorithm that considers each of the variables iteratively, starting from the first coordinate and ending at the $t$-th coordinate.
-If the initial (integral) point $\tilde{x}$ has the variable set to $1$, the algorithm tries to reduce the variable to $0$ if possible.
+We introduce an algorithm that builds a solution from the input integral point $\tilde{x}$.
+It finalizes a binary value for each variable iteratively, starting from the first coordinate and ending at the $t$-th coordinate.
+%Any coordinate that is $0$ in $\tilde{x}$ remains $0$ in the solution.
+In iteration $\ell\in \{0,\ldots,t-1\}$, if $\tilde{x}_{\ell+1}=1$, the algorithm reduces the $\ell + 1$st coordinate of the solution to $0$ if there is an LP-feasible point $x'$ that respects the decisions made so far, and has $x'_{\ell}=0$.
+Intuitively, we can fix this coordinate to $0$ in the partial solution and still set the remaining coordinates to find the solution promised in Lemma~\ref{domlemma}.
 \arash{A caution here: the phrase if possible a bit vague here.
 We round down to zero, if there is feasible solution to LP (so a point in $P(I)$, such that the first $\ell$ coordinates of it are all equal to the point $x^{(\ell)}$ that we have in iteration $\ell$ and its $\ell+1$-th coordinate is 0}.
-We run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
-\cindy{I think the previous sentence also added to my confusion before (along with the term ``fix'' which I have replaced).
+\cindy{Yes.
+I was just trying to give intuition.
+In particular, I was trying to distinguish Dom2IP that starts with an integral vector, where we push $1$s down, from FDT, where we start with a fractional vector and progressively set components to binary values.
+Do you think the above version is OK?}
+More specifically, in iteration $\ell\in \{0,\ldots,t-1\}$ we produce $x^{(\ell)}\in \dom(P)$ such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
+These $\ell$ components will not change for the remainder of the algorithm.
+%We run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and in each iteration we find $x^{(\ell)}\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
+%\cindy{I think the previous sentence also added to my confusion before (along with the term ``fix'' which I have replaced).
 After $\ell$ iterations the first $\ell$ components are integer, but they were integer before.
 Did you intend to say that we finalize a 0-1 value for the first $\ell$ coordinates?}
-We can set $x^{(0)}=\tilde{x}$. Now consider the following linear program. The variables of this linear program are the $z\in \mathbb{R}^n$.
+
+We can set $x^{(0)}=\tilde{x}$. We now show how to find $x^{(\ell+1)}$ from $x^{(\ell)}$. Consider the following linear program. The variables of this linear program are the $z\in \mathbb{R}^n$.
 \begin{align}
@@
 Otherwise if the optimal value is strictly positive let $x^{(\ell+1)}_{\ell+1} = 1$.
-Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in [n]\setminus \{\ell+1\}$ (See Algorithm \ref{domtoIPalg}).
-
-The above procedure shows how to find $x^{(\ell+1)}$ from $x^{(\ell)}$. The DomToIP algorithm initializes with $x^{(0)}=\tilde{x}$ and  iteratively calls this procedure in order to obtain $x^{(t)}$.
+Let $x^{(\ell+1)}_j = x^{(\ell)}_j$ for $j\in [n]\setminus \{\ell+1\}$.
+The DomToIP algorithm initializes with $x^{(0)}=\tilde{x}$ and iteratively calls this procedure in order to obtain $x^{(t)}$ (See Algorithm \ref{domtoIPalg}).
+\cindy{I rearranged the above paragraph a bit without changing the content.  Please see if you think it's OK.}
 
@@
 
-	Let $x^0$, $x^1$, $\lambda_0$, and $\lambda_1$ be an optimal solution to the LP above. Set $\gamma_0=\lambda_0$ and $\gamma_1 = \lambda_1$.
+	Let $y^0$, $y^1$, $\lambda^*_0$, and $\lambda^*_1$ be an optimal solution to the LP above. Set $\gamma_0=\lambda^*_0$ and $\gamma_1 = \lambda^*_1$.
+%Let $x^0$, $x^1$, $\lambda_0$, and $\lambda_1$ be an optimal solution to the LP above. Set $\gamma_0=\lambda_0$ and $\gamma_1 = \lambda_1$.
 \cindy{The sentence right before this is how I think you link the $\lambda$ in the LP to the $\gamma$ constants in the Lemma statement and the claim below, etc.}
-Let $\hat{x}^0 = x^0/\gamma_0$, $\hat{x}^1=x^1/\gamma_1$. This choice satisfies  (ii), (iii), (iv). To show that (i) is also satisfied we prove the following claim.
-	\arash{Now that I notice, we use $\lambda_0,\lambda_1,x^0,x^1}$ to represnt a feasible solution to the system 13-18.
+Let $\hat{x}^0 = y^0/\lambda^*_0$, $\hat{x}^1=y^1/\lambda^*_1$. This choice satisfies  (ii), (iii), (iv). To show that (i) is also satisfied we prove the following claim.
+	\arash{Now that I notice, we use $\lambda_0,\lambda_1,x^0,x^1$ to represnt a feasible solution to the system 13-18.
 Since the optimal solution is use only for the duration of one sentence above maybe we can change the notation for the optimal solution.
 For instance use $y^0,y^1, \lambda^*_0,\lambda^*_1$}
+\cindy{I think I made the changes you suggested.  I also used the LP optima to set the $\hat{x}$.  Please check.}
 	\begin{claim}\label{CVexists}

### 2020-08-10 FDT2020/Introduction.tex
A contribution summary list

@@
 \cindy{We probably need an explicit list of contributions.  It could be another subsection of the introduction.  This will help the reviewer and eventually, if published, the reader.}
+\subsection{Contribution summary}
+In summary, this papers's contributions are:
+\begin{itemize}
+\item We give an algorithm to express any feasible point for the LP relaxation of a binary IP (or a \{0,1,2\} IP) as a convex combination of feasible solutions, provided the IP integrality gap is bounded.
+This is the Fractional Decomposition Tree (FDT) algorithm.
+\item We give a simpler, faster algorithm algorithm to give one feasible solution for any IP with bounded integrality gap. If this algorithm fails, then the integrality gap is infinite.
+\item We experimentally show that FDT can give good approximate solutions to small instances of vertex-cover and tree-augmentation problems.
+\item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for integrality gap for 2EC for these instances.
+\item We demonstrate (with tree augmentation and 2EC) how FDT exeriments can support theoretical work on integrality gaps for specific problems.
+\end{itemize}

### 2020-08-10 FDT2020/Introduction.tex
draft before submission

@@
 Linear programs can be solved in polynomial time.
-The objective value of the linear programming relaxation provides a bound (lower bound for a minimization problem and upper bound for a maximization problem) on the optimal solution to the IP instance.
+The objective value of the linear-programming relaxation provides a bound (lower bound for a minimization problem and upper bound for a maximization problem) on the optimal solution to the IP instance.
 The solutions can also provide some useful global structure, even though the fractional values might not be directly meaningful.
@@
 Contrary to integer programming, the optimal solution to $\min_{x\in L}cx$ can be efficiently found.
-Set $L$ is called the linear programming relaxation of $S$.
+Set $L$ is called the linear-programming relaxation of $S$.
 Since we relaxed the integrality requirement on $x$, we have
@@
 
-If $g=1$, we say that the linear programming formulation is a perfect formulation.
+If $g=1$, we say that the linear-programming formulation is a perfect formulation.
 Otherwise we have $g>1$.
@@
 
-Relaxing the integrality constraints gives the polynomial-time-solvable linear programming relaxation: $\min \;\{cx:\;x\in P(I) \}$.
+Relaxing the integrality constraints gives the polynomial-time-solvable linear-programming relaxation: $\min \;\{cx:\;x\in P(I) \}$.
 The optimal value of this linear program (LP), denoted $z_{\lp}(I,c)$, is a lower bound on the optimal value for the IP, denoted $z_{\IP}(I,c)$.
@@
 A graph is 2-edge-connected if there are at least two edge-disjoint paths between every pair of vertices.
-A linear programming relaxation for this problem, known as the {\em subtour-elimination} relaxation, is
+A linear-programming relaxation for this problem, known as the {\em subtour-elimination} relaxation, is
  \begin{equation}\min \{cx: \sum_{e\in \delta(U)}x_e \geq 2 \mbox{ for } \emptyset \subsetneq U \subsetneq V,\; x\in [0,2]^{E}\}, 
@@
 Let $y$ be a vector in the convex combination from iteration $i-1$.
-We solve a linear programming problem that gives us $\theta_0,\theta_1\in [0,1]$ and $y^0,y^1\in \mathcal{D}(P(I))$ such that $y\geq \theta_0 y^0 + \theta_1 y^1$, $\theta_0+\theta_1\leq g(I)$, $y^0_i=0$ and $y^1_i=1$.
+We solve a linear-programming problem that gives us $\theta_0,\theta_1\in [0,1]$ and $y^0,y^1\in \mathcal{D}(P(I))$ such that $y\geq \theta_0 y^0 + \theta_1 y^1$, $\theta_0+\theta_1\leq g(I)$, $y^0_i=0$ and $y^1_i=1$.
 We then replace $y$ in the convex combination with $\frac{\theta_0}{\theta_0+\theta_1}y^0 +\frac{\theta_1}{\theta_0+\theta_1}y^1$.
@@
 It is ``more'' integral because now all vectors in the convex combination are integral in their first $i+1$ elements.
-If in any iteration there are too many points in the convex combination,  we solve a linear programming problem that ``prunes'' the convex combination.
+If in any iteration there are too many points in the convex combination,  we solve a linear-programming problem that ``prunes'' the convex combination.
 At the end we have a convex combination of integer solutions $\mathcal{D}(P(I))$.
@@
 The goal in VC is to find the minimum-cost vertex cover.
-The linear programming relaxation for VC is
+The linear-programming relaxation for VC is
 \begin{equation}
@@
 In TAP we seek the minimum cost feasible augmentation.
-The natural linear programming relaxation for TAP is
+The natural linear-programming relaxation for TAP is
 \begin{equation}\label{eq:cutLP}
@@
 \begin{itemize}
-\item We give an algorithm to express any feasible point for the LP relaxation of a binary IP (or a \{0,1,2\} IP) as a convex combination of feasible solutions, provided the IP integrality gap is bounded.
-This is the Fractional Decomposition Tree (FDT) algorithm.
-\item We give a simpler, faster algorithm algorithm to give one feasible solution for any IP with bounded integrality gap. If this algorithm fails, then the integrality gap is infinite.
-\item We experimentally show that FDT can give good approximate solutions to small instances of vertex-cover and tree-augmentation problems.
+\item We give an algorithm to express any feasible point for the LP relaxation of a binary IP
+%(or a \{0,1,2\} IP) 
+as a convex combination of feasible solutions, provided the IP integrality gap is bounded.  This is the Fractional Decomposition Tree (FDT) algorithm.
+\item We give a simple  algorithm to give a feasible solution for any binary IP with bounded integrality gap. If this algorithm fails, then the integrality gap is infinite.
+\item We experimentally show that FDT can give good approximate solutions to small instances of vertex-cover and tree augmentation problems.
 \item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for integrality gap for 2EC for these instances.

### 2020-08-10 FDT2020/main-section.tex
small change
draft before submission

@@
 \vspace{8pt}
-It is not difficut to see that the number of nodes in the FDT tree is $O(n^2)$.
+There are $O(n^2)$ nodes in the FDT tree.
 A faster way to achieve feasible solutions with good quality for an IP with bounded integrality gap is an algorithm that takes a random dive into the FDT tree, hence only visiting $O(n)$ nodes.
@@
 \paragraph{FDT on randomly generated instances of TAP.}
-Recall that in the tree-augmentation problem (TAP) we are given a tree $T=(V,E)$, a set of non-tree links $L$ between vertices in $V$ and costs $c\in \mathbb{R}^{L}_{\geq 0}$.
+Recall that in the tree augmentation problem (TAP) we are given a tree $T=(V,E)$, a set of non-tree links $L$ between vertices in $V$ and costs $c\in \mathbb{R}^{L}_{\geq 0}$.
 A feasible augmentation is $L'\subseteq L$ such that $T+L'$ is 2-edge-connected.

### 2022-01-15 FDT2020/response/response.tex
started a respones file with all reviewers comments

\documentclass[11pt,epsf]{article}
%\documentstyle[12pt,psfig,draft]{article}

%% These ``comments'' only appear with [draft] option
\long\def\comment#1{\ifdim\overfullrule>0pt{\sf[{#1}]}\fi}
\def\mn{\medskip}

\usepackage{amsmath}
\usepackage{comment,amsthm,graphicx}
\usepackage{latexsym}
\usepackage{epsfig}
\usepackage{bbm}
\usepackage[usenames]{color}
\usepackage{colordvi, xcolor}
\usepackage{pdfsync}
\usepackage{amsfonts}

\usepackage{color}
\usepackage{appendix}

\setlength{\topmargin}{-0.0in}
\setlength{\textheight}{8.2in}
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{-0.0in}
\setlength{\textwidth}{6.5in}
\addtolength{\parskip}{2pt}
\addtolength{\itemsep}{0.1in}

\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{proposition}{Proposition}
\newtheorem{claim}{Claim} \newtheorem{lemma}{Lemma}
\newtheorem{fact}{Fact}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{observation}{Observation}
\newtheorem{exercise}{Exercise}
\newtheorem{hypothesis}{Hypothesis}

\newcommand{{\Ex}}{\mathbb{E}}
\newcommand{{\TM}}{T^C}

\newcommand{{\C}}{\mathcal{C}}
\newcommand{{\Ob}}{\Omega}

\newcommand{{\bchords}}{Black$-$Chords}
\newcommand{{\wchords}}{White$-$Chords}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\ifx\pdftexversion\undefined
\usepackage[colorlinks,linkcolor=black,filecolor=black,citecolor=black,urlco
lor=black,pdfstartview=FitH]{hyperref}
\else
\usepackage[colorlinks,linkcolor=blue,filecolor=blue,citecolor=blue,urlcolor
=blue,pdfstartview=FitH]{hyperref}
\fi
\newcommand{\supp}{{\rm supp}}
\newcommand{\opt}{{\rm OPT}}
\newcommand{\disc}{{\rm disc}}
%\newcommand{\choos}[2] {\left( \begin{array}{c} #1\\#2

%\end{array} \right)}
\newcommand{\namedref}[2]{\hyperref[#2]{#1~\ref*{#2}}}
\newcommand{\sectionref}[1]{\namedref{Section}{#1}}
\newcommand{\factref}[1]{\namedref{Fact}{#1}}
\newcommand{\appendixref}[1]{\namedref{Appendix}{#1}}
\newcommand{\subsectionref}[1]{\namedref{Subsection}{#1}}
\newcommand{\theoremref}[1]{\namedref{Theorem}{#1}}
\newcommand{\defref}[1]{\namedref{Definition}{#1}}
\newcommand{\figureref}[1]{\namedref{Figure}{#1}}
\newcommand{\claimref}[1]{\namedref{Claim}{#1}}
\newcommand{\lemmaref}[1]{\namedref{Lemma}{#1}}
\newcommand{\tableref}[1]{\namedref{Table}{#1}}
\newcommand{\propref}[1]{\namedref{Proposition}{#1}}
\newcommand{\obref}[1]{\namedref{Observation}{#1}}
\newcommand{\eqnref}[1]{\namedref{Equation}{#1}}
\newcommand{\remarkref}[1]{\namedref{Remark}{#1}}
\newcommand{\corollaryref}[1]{\namedref{Corollary}{#1}}
\newcommand{\propertyref}[1]{\namedref{Property}{#1}}
%\input{psfig}

\newcommand{\alert}[1]{\textbf{\color{red}
[[[#1]]]}\marginpar{\textbf{\color{red}**}}\typeout{ALERT:
\the\inputlineno: #1}}

\newenvironment{cproof}
{\begin{proof}
 [Proof.]
 \vspace{-1.5\parsep}%-3.2\parsep} %%%For use with US letter
}
{\renewcommand{\qed}{\hfill $\Diamond$} \end{proof}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\newcommand{\qed}{\hspace*{\fill}\mbox{$\Box$}}
\newcommand{\choos}[2] {\left( \begin{array}{c} #1\\#2
\end{array} \right)}

%\input{psfig}

\begin{document} \bibliographystyle{alpha}
\def\proofend{\hfill$\Box$\medskip}
\def\Proof{\noindent{\bf Proof:\ \ }}
\def\Sketch{\noindent{\bf Sketch:\ \ }}
\def\eps{\epsilon}
\newcommand{\arash}[1]{\noindent{\bf {\color{blue!60!black}{\sc Arash:}  #1}}}
\newcommand{\cindy}[1]{\noindent{\bf {\color{magenta!80!black}{\sc Cindy:}  #1}}}
\newcommand{\response}[1]{\noindent{{\color{blue!80!black}  #1}}}
\iffalse
\renewcommand{\arash}[1]{}
\renewcommand{\cindy}[1]{}
\fi
\title{Responses to reviewers comments}
\maketitle

\section{General Response}
\response{We thank the editor and reviewers for their insighful and constructive comments. 
}

\section{Detailed Responses}

\subsection{Reviewer \#1}
\begin{itemize}
\item Introduction: Introduction jumps between describing methods and problems the methods are applied to. The there is a subsection 1.2 Experiments with more problem descriptions. Please restructure the introduction so
that the flow is more logical.

\item p. 2, last paragraph: “Integrality gap” is defined with respect to an IP instance, instead of a family of IP instances (IP formulation) for a problem. This makes the paragraph rather awkward to read, because the statements are not correct as stated.

\item p. 3, below equation (1): Why is $A$ defined as a matrix of rational numbers but $b$ a vector or real numbers?
\item p. 3: Is there a reason why you choose to not include the coefficients of the objective function in an instance?
\item p. 4, Definition 1: Now the integrality gap is defined with respect to a matrix $A$ and vector $b$, taking the supremum (not maximum, please correct) over all coefficients $c$, that are nonnegative. This is inconsistent
with the previous statement, and also nonstandard as far as I know. Please add some remarks for the reader about this choice. Also, the importance of considering $c \geq 0$ only should be emphasized more in the text (it is of
vital importance when using Carr-Vempala).
\item p. 4, equation (4): supremum instead of maximum
\item p. 5, Proposition 2: Please specify where this is stated in [GLS93].
\item p. 5, below Proposition 2: I don’t see that Proposition 2 and Theorem 3 are equivalent as stated. (Also in light of the remark about one result having an algorithm, and the other not.)
\item p. 6, Theorem 4: “Moreover, [. . .]” — $C$ is not specified otherwise; replace “Moreover” by “where”.
\item p. 6, Theorem 5: Why “$1\leq$”? Is that not automatic?
\item p. 6, below Theorem 5: “in iteration i the algorithm maintains a convex combination of vecotrs” — please phrase this more precisely 
\item p. 6, near bottom: “It’s subtour-elimination...” — Its
\item p. 7, equation (5): sup instead of max
\item p. 7, Theorem 6: “Moreover, [. . .]” — $C$ is not specified otherwise; replace “Moreover” by “where”.
\item p. 9, last bullet point of Contribution summary: “can support theoretical work” — be more specific about what you did, and what it showed. 
\item p. 9, Lemma 7: add $\tilde{x}$ right after “Given an integral vector”
\item p. 9, bottom: Isn’t it even easier? Is $\{1\}^n$ not a point in $\mathcal{D}(P)$ (provided
$P\neq \emptyset$)?
\item p. 11, 3rd line below definitions of $LP^{(\ell)}$ and $IP^{(\ell)}$ : “By Theorem 3, there
exist [not exists] $\tilde{z}_i\in S$". In the statement of Theorem 3 this is $\mathcal{D}(S)$. Is
$S$ the same as $\mathcal{D}(S)$ here? If so explain.
(`)
If not, can you still draw the conclusion that $IP^{(\ell)}\neq \emptyset$?
\item p. 11, third paragraph: Same problem as previous bullet point.
\item p. 13, top of page: Same problem.
\item p. 24 and following, references: missing capitalization in a few entries

\end{itemize}

\subsection{Reviewer 2}

\subsubsection{Major Comments}
The computational results seem quite weak to me. The classic Feasibility Pump heuristic is known to produce solutions of fairly poor quality; it is designed primarily to produce feasible solutions to potentially difficult MIPs
quickly. On TAP and 2EC, the authors compare to problem-specific approximation algorithms that are not particularly designed to produce high quality solutions either.
\begin{enumerate}

\item The abstract is misleading in multiple ways. First, it says that the paper will give a constructive version of the Carr-Vempala theorem but does not mention the rather large loss in quality of g to (potentially) g n . Secondly,
it says that “[Dom2IP] more quickly determines if an instance has an unbounded integrality gap” but really this algorithm will only sometimes provide proof that the integrality gap is unbounded; it is not guaranteed
to certify this. Lastly, it is claimed that Christofides’ algorithm is the “best previous approximation algorithm”. But Christofides is only best wrt. its theoretical approximation guarantee not its practical performance
which is what is compared in the paper. 
\item The paper should mention the randomized metarounding algorithm by Carr and Vempala and compare it to the FDT algorithm. 
\item In the proofs of Lemma 8 and Lemma 11, I do not see why it can be assumed that $\lambda_0,\lambda_1,\lambda_2>0$. I think one has to allow the case in which
the branching step returns just 1 or (in the case of 2EC) just 2 vectors.
4. As noted before, I find the comparisons against the FP heuristic on VC
and the 2-approximation for TAP rather dubious. To show that the FDT
algorithm performs much better than the theoretical $g^{|supp(x)|}$ bound, just comparing to the initial fractional solution is all that is needed. On the other hand, if the goal is to show that the FDT algorithm works well as a
general purpose feasibility heuristic, then comparing to a FDT to a more modern variant of FP (e.g. as in the Feasibility Pump 2.0 paper) would be more reasonable.

\end{enumerate}

\subsubsection{Minor Comments}
\begin{enumerate}

\item  The abstract says “Dom2IP” but the paper mostly uses “DomToIP”. 
\item In Theorem 3, I think $\mathcal{D}(S(I))$ should just be $S(I)$.
\item On page 6, “which runs in polynomial time algorithm” should be “which runs in polynomial time”.
\item On page 6, the use of $\theta_0$ and $\theta_1$ is not consistent with how $\gamma_0$ and $\gamma_1$ are
defined in Lemma 8.
\item In Theorem 6, is $E_x=\mbox{supp}(x)$?
\item On page 8, the wording “We use the idea of fundamental extreme point to create the hardest LP solutions to decompose.” seems to suggest that this is something that will be done in this paper.
\item On page 8, you refer to Figure 2 but this figure only shows up on page 23.
\item You mention that the Dom2IP algorithm can be used to prove that an IPs integrality gap is unbounded. How effective is this?
\item Lemma 9 requires $\gamma_0 + \gamma_1 \leq 1$. Perhaps this should already be included
in Lemma 8.
\item In the proof of Lemma 9, “We need to show that $\gamma_0\hat{x}^0_j + \gamma\hat{x}^1_j \leq gx'_j.$" has
an extra g in it.
\item On page 13, “nodes in level $L_i$” should be “nodes in level $i$” and “points
in the leaves” should be just “leaves.”
\item On page 24, “applying this tool . . . can be a tool” is redundant. 
\end{enumerate}

\subsection{Reviewer \#3}

\subsubsection{Main Comments}

\subsubsection{Detailed Comments}
\begin{itemize}
\item I’m attaching a file with line numbers. I strongly recommend for any future submission
using the lineno package, because it makes my job as a reviewer much easier. I will refer to
pairs (page number, line number) below.

\item (2,10) “we have formulated” – better to say “instances … are known” and give a reference, e.g. to MIPLIB; or if you have some particularly hard instances in mind that YOU have formulated, you can refer to them, but this should be a fairly widely known
fact. 
\item (2,14) “the” -> “these”?
\item (2,26) “from the problem” – what problem? Maybe “using special problem structure together with the result of an LP relaxation to obtain an integer feasible solution
whose value is at most C times the value of the LP optimum” or something like that.
\item (3,7) you say that a separation oracle should return a most violated constraint, but I don’t think this is the standard definition of e.g. Grötschel-Lovász-Schrijver – any violated constraint suffices to get polynomial convergence. 
\item (3,11) “it could not before” -> “they could not before”
\item (3,23) “ResearcherS”
\item (4,26) “We cannot hope to find…” – you’ve said this already.
\item (5,8) “express A vector”
\item (5,10) Please define $[0,1]$ which appears in $[0,1]^k$ . It seems you mean the closed interval between 0 and 1, but it is very commonly also used to be the set $\{0,1\}$, so clarification is in order.
\item (5,16) “of A blocking type”
\item (5,23) “assuming” –> “under”
\item (5,30) ”$S(I)\in \{0,1\}^n$ should be $\subseteq$ instead of $\in$
\item (6,1) delete “algorithm”
\item (6,3) “it would be optimal” - what is “it”?
\item (6,3) “we can only guarantee a factor of” I think it would be clearer to say “we can
only guarantee $C\leq g(I)$ ... ”
\item (6,7) how does the $\min$ in $\min(Cx^*, {0,1}^n )$ work? Coordinate-wise, or?
\item (6,27) “It’s” –> “Its”
\item (7,5) what is $\chi^{F_i}$ ? I suppose it is the characteristic vector of $F_i$ but you should state
this clearly. Also, what is $E_x$ ? is it the number of edges of $x$, that is, $\mbox{supp}(x)|$? Again
please state clearly.
\item (7,13) “A subset of $U$ of $V$ ” – delete first “of”
\item (7,18) define or comment on UG-hard
\item (7,19) “feasbility” –> “feasibility”
\item (7,20) “3-5x slower” use “$\times$” (\\times) instead of “x”
\item (7,29) Large space before “Note” - something fishy is going on here.
\item (9,14) add your experimental results about VC here also
\item (10,7) again, large space
\item (10,14) it seems to me that the definition of the coordinates of $x^{(\ell+1)}$ other than $\ell+1$
should appear in the algorithm too, not just here.
\item (11,14-25) I’m getting tripped up at line 17. I understand the case for coordinates which have $x_j=0$. But where do you deal with those that do not? I suppose I’m just
missing something obvious, but so could any other reader. Please clarify your proof here.
\item (12,10) “maintainS” 
\item (13,28) “Growing and Pruning THE FDT tree”
\item (14,12) “It is easy to check” <– you do this quite a bit. Please go through your paper and
pay attention to all the “easy to check”, “obvious”, “clearly” etc. If these things really are easy, then just state them and don’t waste space. However, if some observation is necessary, think about the clearest and most concise way to impart this observation to the reader, and then do that instead of telling the reader that it should be “easy”. 
\item (14,12) “THE set $L'$”
\item (14,25) “From THE leaves”
\item (16,11-17) You should discuss why the intuitive approach of binarizing an LP (just split each variable into two binary variables and copy the respective column of the
constraint matrix) does not lead to the same or better result. Or maybe it does?
\item (19,14) “1Mb cache” – I looked up this CPU and it has 1MB of L2 cache. Note that
1Mb $\neq$ 1MB, and “cache” is quite an ambiguous term (there are several types of CPU
cache). Moreover, the amount of cache is a property of the CPU and is usually not
stated, so I would just not comment on it. If you must, give a correct capacity and
indicate the level of the cache.
\item (19,22-26) Is there no good benchmark set for TAP? If not, please mention that as
the reason why you study random instances. (It is not good practise in experimental
algorithmics to study random instances unless necessary.)
\item (20,22) One idea to consider and comment on: did you warm-start each computation of FDT? It seems to me that you could reuse the model that FDT solves in each
iteration – basically, you only change the objective and fix the variables which corresponds to changing lower/upper bounds, so you should be able to save time on
building / destroying the model. I’m not sure how much the pruning model can be reused. Either way, please comment on this idea. The idea was successful elsewhere,
e.g. https://arxiv.org/abs/1911.08636 
\item (21,10) Christofides’ algorithm is no longer the fastest https://arxiv.org/abs/2007.01409
\item (21,10-11) “In the classic graph-based…” <– this is a weird sentence; you should say
that you will re-cap the algorithm and then you can describe it. Right now it comes
out of nowhere.

\end{itemize}

\end{document}

### 2022-01-17 FDT2020/response/response.tex
first run through reviewer 1 comments

@@
 %\documentstyle[12pt,psfig,draft]{article}
-
 %% These ``comments'' only appear with [draft] option
@@
 \item p. 3, below equation (1): Why is $A$ defined as a matrix of rational numbers but $b$ a vector or real numbers?
+
+\response{Fixed. Both $A$ and $b$ are comprised of rational numbers.}
 \item p. 3: Is there a reason why you choose to not include the coefficients of the objective function in an instance?
+\response{Not final! We choose this definition because it allows us to talk about instance specific integrality gaps (or integrality gap in the special cases).}
+
 \item p.
@@
 \item p. 4, equation (4): supremum instead of maximum
+\response{Fixed.}
 \item p. 5, Proposition 2: Please specify where this is stated in [GLS93].
 \item p. 5, below Proposition 2: I don’t see that Proposition 2 and Theorem 3 are equivalent as stated. (Also in light of the remark about one result having an algorithm, and the other not.)
+\response{Fixed. Now we say they are similar statement. We also tried to word the statements in a way to draw the similarity between the two.}
+
 \item p. 6, Theorem 4: “Moreover, [. . .]” — $C$ is not specified otherwise; replace “Moreover” by “where”.
+\response{Fixed.}
 \item p. 6, Theorem 5: Why “$1\leq$”? Is that not automatic?
+\response{We added the lower bound as a reminder to the reader, but we removed since we agree that it is redundant.}
 \item p. 6, below Theorem 5: “in iteration i the algorithm maintains a convex combination of vecotrs” — please phrase this more precisely 
+\response{Done. The algorithm computes a convex combination from the one constructed in the last iteration that is progressively more integral.}
 \item p. 6, near bottom: “It’s subtour-elimination...” — Its
+\response{Fixed.}
 \item p. 7, equation (5): sup instead of max
+\response{Fixed.}
 \item p. 7, Theorem 6: “Moreover, [. . .]” — $C$ is not specified otherwise; replace “Moreover” by “where”.
+\response{Fixed.}
 \item p. 9, last bullet point of Contribution summary: “can support theoretical work” — be more specific about what you did, and what it showed. 
+\response{This sentence is now added to this bullet: In particular, we computationally prove an upper bound on small instances of 2EC with a specific structure.}
 \item p. 9, Lemma 7: add $\tilde{x}$ right after “Given an integral vector”
+\response{Fixed.}
 \item p. 9, bottom: Isn’t it even easier? Is $\{1\}^n$ not a point in $\mathcal{D}(P)$ (provided
-$P\neq \emptyset$)?
+$P\neq \emptyset$)? \response{Correct, however, the proof would be simpler if restrict the solution to the support of $x$. That's why we use the round-up (i.e. the support of solution).}
 \item p. 11, 3rd line below definitions of $LP^{(\ell)}$ and $IP^{(\ell)}$ : “By Theorem 3, there
@@
 $S$ the same as $\mathcal{D}(S)$ here? If so explain.
-(`)
-If not, can you still draw the conclusion that $IP^{(\ell)}\neq \emptyset$?
+(`) If not, can you still draw the conclusion that
+$IP^{(\ell)}\neq \emptyset$?
+
+\response{Thank you for pointing this out.
+We corrected to say $\tilde{z}^i\in \mathcal{D}(S)$.
+We also added this observation at the beginning of section 2 that is cross-reference in the proofs: Any point $x\in [0,1]^n$ that is a convex combination of points in $\mathcal{D}(S)$, is also a convex combination of points in $\mathcal{D}(S) \cap [0,1]^n$}
 \item p. 11, third paragraph: Same problem as previous bullet point.
+\response{Fixed with referencing the Observation above.}
 \item p. 13, top of page: Same problem.
+\response{Fixed with referencing the Observation above.}
 \item p. 24 and following, references: missing capitalization in a few entries

### 2022-01-17 FDT2020/Introduction.tex
first run through reviewer 1 comments

@@
 \end{equation}
-where matrix $A$ of rationals has $m$ constraints on $n$ variables and $b \in \mathbb{R}^{m}$.
+where matrix $A\in \mathbb{Q}^{m\times n}$ and $b \in \mathbb{Q}^{m}$, where $\mathbb{Q}$ denotes the set of rational numbers.
 If we drop the integrality constraints, we have the linear relaxation of set $S(A,b)$,
@@
 \begin{definition}
-The integrality gap $g(I)$ for instance $I$ is: $$g(I)= \max_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)},$$
+The integrality gap $g(I)$ for instance $I$ is: $$g(I)= \sup_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)},$$
 where $z_{IP}(I,c)$ is the optimal solution to the integer program and $z_{LP}(I,c)$ is the solution to the linear-programming relaxation.
@@
 In some way the difference between prop 1 and theorem 2 is our initial motivation for thinking of polynomial construction.}
+
+Formally, for some positive integer $k$, given a set of points $S\subseteq \mathbb{R}^k$ and a vector $x\in \mathbb{R}^k$, we say \textit{$x$ \underline{is} as a convex combination of points in $S$} if there exists a positive integer $\ell$ and $\theta \in [0,1]^\ell$, where $\sum_{i=1}^{\ell}\theta_i =1$ and $\tilde{x}^i\in S$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$.
+If a such a convex combination in polynomial time in the encoding size of the definition of $S$ and $x$, we say  \textit{$x$ \underline{can be written} as a convex combination of points in $S$}
+
 \begin{proposition}\label{cara}
-	If $g(I)=1$, then for $x\in P(I)$ there exists a positive integer $k$ and $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in S(I)$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$.
-Moreover, we can find such a convex combination in polynomial time.
+	We have $g(I)=1$ if and only if $x\in P(I)$ can be written as a convex combination of points in $S(I)$.
 \end{proposition}
 
-An equivalent way of describing Proposition \ref{cara} is the following Theorem of Carr and Vempala \cite{Carr2004}.
+For the case when $g(I)>1$ a similar statement is as follows.
 The {\em dominant} of $P(I)$, which we denote by $\dom(P(I))$, is the set of points $x'$ such that there exists a point $x\in P$ with $x'\geq x$ in every component.
@@
 \begin{thm}[Carr, Vempala \cite{Carr2004}] \label{CV2}
-	We have $g(I) \leq C$ if and only if for  $x\in P(I)$ there exists $\theta \in [0,1]^k$ where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in \dom(S(I))$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$.
+	We have $g(I) \leq C$ if and only if for $x\in P(I)$ the vector $Cx$ can be is as a convex combination of points in $\dom(S(I))$. 
 \end{thm}
@@
 To study integrality gaps, we wish to decompose a suitably scaled linear-programming solution into a convex combination of feasible integer solutions {\bf constructively}.
-That is, we ask: assuming reasonable complexity assumptions, given a specific problem $\mathcal{I}$ with  $1<g(\mathcal{I})<\infty$, and $x\in P(I)$ for some $I\in \mathcal{I}$, can we find $\theta \in [0,1]^k$, where $\sum_{i=1}^{k}\theta_i =1$ and $\tilde{x}^i\in S(I)$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq Cx$ in polynomial time?
+That is, we ask: assuming reasonable complexity assumptions, given a specific problem $\mathcal{I}$ with  $1<g(\mathcal{I})<\infty$, and $x\in P(I)$ for some $I\in \mathcal{I}$, \textbf{can we write} $Cx$ as a convex combination of points in $\dom(S(I))$?
 We wish to find the smallest factor $C$ possible.
@@
 	\label{binaryFDT}
-	Assume $1\leq g(I) 	<\infty$. 	
-	The Fractional Decomposition Tree (FDT) algorithm, given $x^*\in P(I)$, produces in polynomial time $\lambda\in [0,1]^k$ and $z^1,\ldots,z^k \in S(I)$ such that $k\leq |\spp(x^*)|$, $\sum_{i=1}^{k}\lambda_i z^i\leq \min(Cx^*,\{1\}^{n})$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g(I)^{|\spp(x^*)|}$.
+	Assume $g(I) 	<\infty$. For $x^*\in P(I)$, using 	the Fractional Decomposition Tree (FDT) algorithm we can write $x$ as a convex combination of points in $S(I)$, where $C\leq g(I)^{|\spp(x^*)|}$.
 \end{restatable}
@@
 	\label{domtoIP}
-	Assume $1\leq g(I) < \infty$. The DomToIP algorithm finds $\hat{x}\in S(I)$ in polynomial time.
+	Assume $g(I) < \infty$. The DomToIP algorithm finds $\hat{x}\in S(I)$ in polynomial time.
 \end{restatable}
@@
 
-Here is how the FDT algorithm works at a high level for an instance $I$ with LP feasible region $P(I)$: in iteration $i$ the algorithm maintains a convex combination of  vectors in $\mathcal{D}(P(I))$ that have a 0 or 1 value for coordinates indexed $0,\ldots,i-1$.
-Let $y$ be a vector in the convex combination from iteration $i-1$.
-We solve a linear-programming problem that gives us $\theta_0,\theta_1\in [0,1]$ and $y^0,y^1\in \mathcal{D}(P(I))$ such that $y\geq \theta_0 y^0 + \theta_1 y^1$, $\theta_0+\theta_1\leq g(I)$, $y^0_i=0$ and $y^1_i=1$.
+Here is how the FDT algorithm works at a high level for an instance $I$ with LP feasible region $P(I)$: in iteration $i-1$ the algorithm computes a convex combination of vectors in $\mathcal{D}(P(I))$ that have a 0 or 1 value for coordinates indexed $1,\ldots,i-1$.
+Let $y$ be a vector in this convex combination from iteration $i-1$.
+In iteration $i$, we solve a linear-programming problem that gives us $\theta_0,\theta_1\in [0,1]$ and $y^0,y^1\in \mathcal{D}(P(I))$ such that $y\geq \theta_0 y^0 + \theta_1 y^1$, $\theta_0+\theta_1\leq g(I)$, $y^0_i=0$ and $y^1_i=1$.
 We then replace $y$ in the convex combination with $\frac{\theta_0}{\theta_0+\theta_1}y^0 +\frac{\theta_1}{\theta_0+\theta_1}y^1$.
-Repeating this for every vector in the convex combination from the previous iteration yields a new convex combination of points.
-It is ``more'' integral because now all vectors in the convex combination are integral in their first $i+1$ elements.
+Repeating this for every vector in the convex combination from the previous iteration yields a new convex combination of points in $\dom(P(I))$.
+It is ``more'' integral because now all vectors in the convex combination are integral in their first $i$ coordinates.
 If in any iteration there are too many points in the convex combination,  we solve a linear-programming problem that ``prunes'' the convex combination.
@@
 In Section~\ref{sec:2EC} we focus on the 2-edge-connected multi-subgraph graph problem (2EC) defined above.
-It's subtour-elimination LP relaxation is given in (\ref{eq:subtour}).
+Its subtour-elimination LP relaxation is given in (\ref{eq:subtour}).
 %}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^{E}_{\geq 0}$ find a 2-edge-connected multi-subgraph of $G$ with minimum cost. The natural linear programming relaxation for this problem is 
@@
 \begin{equation}
-g(\2ec) = \max_{c\geq 0 , G}\frac{\min_{x\in \2ec(G)} cx}{\min_{x\in \subtour(G)} cx}.
+g(\2ec) = \sup_{c\geq 0 , G}\frac{\min_{x\in \2ec(G)} cx}{\min_{x\in \subtour(G)} cx}.
 \end{equation}
+
+For a multi-subset of edges $F$ of $E$, we use $\chi^F$ to denote the characteristic vector of $F$ which is a vector in $\mathbb{R}^E$ where $\chi^F_e$ is equal to the multiplicity of edge $e$ in $F$.
+We denote $E_x$ to denote $\spp(x)$ as a subset of edges of $E$.
 
@@
 	Let $G=(V,E)$ and $x$ be an extreme point of  $\subtour(G)$.
-The FDT algorithm for 2EC produces $\lambda\in [0,1]^k$ and 2-edge-connected multi-subgraphs $F_1,\ldots,F_k$ such that $k\leq 2|V|-1$, $\sum_{i=1}^{k}\lambda_i \chi^{F_i}\leq \min(Cx,\{2\}^n)$, and $\sum_{i=1}^{k}\lambda_i = 1$.
-Moreover, $C\leq g(\2ec)^{|E_x|}$.
+By FDT algorithm for 2EC, we can write $y= \min(Cx,\{2\}^n)$ as a convex combination of characteristic vector of 2-edge-connected multi-subgraphs of $G$, where $C\leq g(\2ec)^{|E_x|}$.
 \end{restatable}
@@
 \item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for integrality gap for 2EC for these instances.
-\item We demonstrate (with tree augmentation and 2EC) how FDT exeriments can support theoretical work on integrality gaps for specific problems.
+\item We demonstrate (with 2EC) how FDT exeriments can support theoretical work on integrality gaps for specific problems.
+In particular, we computationally prove an upper bound on small instances of 2EC with a specific structure.
 \end{itemize}

### 2022-01-17 FDT2020/main-section.tex
first run through reviewer 1 comments

@@
 So we can assume $x^*_i = 0$ for $i=t+1,\ldots,n$.
+
+Before diving into the main results, we state the following simple observation that we will use several times in the proofs of this section and the next section.
+\begin{observation}\label{dom01}
+Any point $x\in [0,1]^n$ that is a convex combination of points in $\dom(S)$, is also a convex combination of points in $\dom(S) \cap [0,1]^n$
+\end{observation}
+\begin{proof}
+This is because if there exists ${z}^i\in \dom(S)$ and $\theta_i\geq 0$ for $i\in [k]$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i {z}^i \leq gz$, then 
+we let ${y}^i$ be the coordiante-wise minimum of vector ${z}^i$ and $\{1\}^n$ for $i\in [k]$ and we have ${y}^i\in \dom(S)$ and $\sum_{i=1}^{k}\theta_i{y}^i \leq gz$.
+\end{proof}
 %\cindy{TODO: Is this something that should be clear to the reader with what they know at this point?
@@
 \begin{lemma}\label{domlemma}
-	Given an integral vector in the dominant of an LP relaxation ($\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$) for an IP instance that has integrality gap $g < \infty$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time such that $\bar{x}\leq \tilde{x}$.\end{lemma}
+	Given an integral vector $\tilde{x}$ in the dominant of an LP relaxation ($\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$) for an IP instance that has integrality gap $g < \infty$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time such that $\bar{x}\leq \tilde{x}$.\end{lemma}
 Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up $x^*$ (or any fractional point in $P$) gives us a point in $\dom(P)$.
@@
 \end{align*}
-If $\LP^{(\ell)}$ is a non-empty set then $\HelperLP(x^{(\ell)})$ is feasible.
-We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
+
+If $\LP^{(\ell)}$ is a non-empty set then $\HelperLP(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$.
+
 First, $\LP^{(0)}$ is feasible since by definition $x^{(0)}\in \dom(P)$, meaning there exists $z\in P$ such that $z\leq x^{(0)}$.
-By Theorem \ref{CV2}, there exists $\tilde{z}^i\in S$ and $\theta_i\geq 0$ for $i\in [k]$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
+By Theorem \ref{CV2} and Observation \ref{dom01}, there exists $\tilde{z}^i\leq 1$ in $\dom(S)$ and $\theta_i\geq 0$ for $i\in [k]$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.
 (This assumes a finite integrality gap $g$).
 %\cindy{Is this the place (and others like it) where we require $g$ to be finite?}
+
  Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$.
@@
 Also, $z^*\in P$.
-By Theorem \ref{CV2} there exists $\tilde{z}^i\in S$ and $\theta_i\geq 0$ for $i\in [k]$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$.
+By Theorem \ref{CV2} and Observation \ref{dom01}, there exists $\tilde{z}^i\leq 1$ in $\dom(S)$ and $\theta_i\geq 0$ for $i\in [k]$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$.
 We have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}$.
@@
 		We show that there is a feasible solution that achieves the objective value of $\frac{1}{g}$.
-By Theorem \ref{CV2} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $\tilde{x}^i\in S$ for $i\in[k]$ such that
+By Theorem \ref{CV2} and Observation \ref{dom01} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $\tilde{x}^i\leq 1$ in $\dom(S)$ for $i\in[k]$ such that
 		$\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$. So

### 2022-01-17 FDT2020/response/response.tex
first run through reviewer 2 minor comments

@@
 \item  The abstract says “Dom2IP” but the paper mostly uses “DomToIP”. 
+\response{Fixed.}
 \item In Theorem 3, I think $\mathcal{D}(S(I))$ should just be $S(I)$.
+\response{NOT FINAL: The proof of this theorem only shows it for the dominant of $S(I)$ and not $S(I)$ itself, although for many problems of interest we have $S(I)=\mathcal{D}(S(I))$. }
+
 \item On page 6, “which runs in polynomial time algorithm” should be “which runs in polynomial time”. 
+\response{Fixed.}
 \item On page 6, the use of $\theta_0$ and $\theta_1$ is not consistent with how $\gamma_0$ and $\gamma_1$ are
 defined in Lemma 8. 
-\item In Theorem 6, is $E_x=\mbox{supp}(x)$?
+\response{Fixed and switched to $\gamma_0$ and $\gamma_1$ in the overview to be consistent with Lemma 8.}
+\item In Theorem 6, is $E_x=\mbox{supp}(x)$? \response{Fixed. We added the definition of $E_x$ right before Theorem 6.}
+
 \item On page 8, the wording “We use the idea of fundamental extreme point to create the hardest LP solutions to decompose.” seems to suggest that this is something that will be done in this paper.
+\response{We changed the wording as follows: Known polyhedral structure makes it easier to study integrality gaps for such problems.
+In particular, for the subtour-elimination relaxation [CR98, BC11, CV04] introduced fundamental extreme points that create the ``hardest'' LP solutions to decompose.}.
 \item On page 8, you refer to Figure 2 but this figure only shows up on page 23.
-\item You mention that the Dom2IP algorithm can be used to prove that an IPs integrality gap is unbounded. How effective is this?
+
+\response{The figure is moved to page 3.}
+\item You mention that the Dom2IP algorithm can be used to prove that an IPs integrality gap is unbounded. How effective is this? \arash{need to think about this.}
 \item Lemma 9 requires $\gamma_0 + \gamma_1 \leq 1$. Perhaps this should already be included
 in Lemma 8.
+\response{Fixed. Also added a constraint into the formulation of LPC that ensures $\lambda_0 + \lambda_1\leq 1$ and corresponding changes in the proof of the Claim.}
 \item In the proof of Lemma 9, “We need to show that $\gamma_0\hat{x}^0_j + \gamma\hat{x}^1_j \leq gx'_j.$" has
-an extra g in it.
+an extra $g$ in it.
+\response{Fixed.}
 \item On page 13, “nodes in level $L_i$” should be “nodes in level $i$” and “points
-in the leaves” should be just “leaves.”
-\item On page 24, “applying this tool . . . can be a tool” is redundant. 
+in the leaves” should be just “leaves.” \response{Fixed.}
+\item On page 24, “applying this tool . . . can be a tool” is redundant. \response{Fixed.}
 \end{enumerate}

### 2022-01-17 FDT2020/Introduction.tex
first run through reviewer 2 minor comments

@@
 
-In Section~\ref{sec:binaryfdt} we introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which runs in polynomial time algorithm.
+In Section~\ref{sec:binaryfdt} we introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which is polynomial time algorithm.
 Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated coordinatewise by a ``factor" $C$ times $x$.
@@
 Let $y$ be a vector in this convex combination from iteration $i-1$.
-In iteration $i$, we solve a linear-programming problem that gives us $\theta_0,\theta_1\in [0,1]$ and $y^0,y^1\in \mathcal{D}(P(I))$ such that $y\geq \theta_0 y^0 + \theta_1 y^1$, $\theta_0+\theta_1\leq g(I)$, $y^0_i=0$ and $y^1_i=1$.
-We then replace $y$ in the convex combination with $\frac{\theta_0}{\theta_0+\theta_1}y^0 +\frac{\theta_1}{\theta_0+\theta_1}y^1$.
+In iteration $i$, we solve a linear-programming problem that gives us $\gamma_0,\gamma_1\in [0,1]$ and $y^0,y^1\in \mathcal{D}(P(I))$ such that $y\geq \gamma_0 y^0 + \gamma_1 y^1$, $\gamma_0+\\gamma_1\leq g(I)$, $y^0_i=0$ and $y^1_i=1$.
+We then replace $y$ in the convex combination with $\frac{\gamma_0}{\gamma_0+\gamma_1}y^0 +\frac{\gamma_1}{\gamma_0+\gamma_1}y^1$.
 Repeating this for every vector in the convex combination from the previous iteration yields a new convex combination of points in $\dom(P(I))$.
@@
 Known polyhedral structure makes it easier to study integrality gaps for such problems.
-We use the idea of fundamental extreme point \cite{carrravi,boydcarr,Carr2004} to create the ``hardest'' LP solutions to decompose.
+In particular, for the subtour-elimination relaxation \cite{carrravi,boydcarr,Carr2004} introduced fundamental extreme points that create the ``hardest'' LP solutions to decompose.
 
@@
 A \textit{Carr-Vempala point} $x\in \mathbb{R}^E$ is a fractional point in $\subtour(G)$ where the edges $e$ with $0<x_e<1$ form a single cycle in $G$ and the vertices on the cycle are connected via vertex-disjoint paths of edges $e$ with $x_e =1$ (see Figure \ref{fig:CVpoint}).
+
+\begin{figure}
+\centering
+\begin{tikzpicture}[scale=0.4]
+
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (0,-4)};
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(2.83,2.83) (-4,0)};
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (-2.83,-2.83)};
+\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-2.83,2.83) (2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (2.83,2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (-2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,-2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,2.83)};
+
+\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (-2.83,2.83)};
+
+\draw[black,fill=white] (0,4) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (4,0) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (0,-4) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (-4,0) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (-2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
+\draw[black,fill=white] (-2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
+
+\node (1) at (0,4) {{1}};
+\node (2) at (2.83,2.83) {{2}};
+\node (3) at (4,0) {{3}};
+\node (4) at (2.83,-2.83) {{4}};
+\node (5) at (0,-4) {{5}};
+\node (6) at (-2.83,-2.83) {{6}};
+\node (7) at (-4,0) {{7}};
+\node (8) at (-2.83,2.83) {{8}};
+\end{tikzpicture}
+\caption{A Carr-Vempala point with 8 vertices on its cycle.
+Solid lines are edges with value strictly between $0$ and $1$.
+Dashed edges represent paths where each edge on the path has $x_e =1$.
+There can be an arbitrary number of degree-$2$ vertices on the dashed paths.}
+\label{fig:CVpoint}
+\end{figure}
 %\cindy{Every pair of vertices on the cycle is connected this way?
@@
 Multiple groups of researchers have conjectured that $g(\2ec)\leq \frac{6}{5}$ (see \cite{alexander2006integrality,boydlegault,hn19}, but the only known upper bound on $g(\2ec)$ stands at $\frac{3}{2}$ \cite{wolsey}.
-We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges, thereby confirming the conjecture for these instances.
-\cindy{This sounds like a contribution of the paper.} \arash{Yes, particlarly since a similar research question have been studied by \cite{alexander2006integrality} and \cite{TSPcompute}}
-Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.
+We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges, thereby confirming the conjecture for these instances.\cindy{This sounds like a contribution of the paper.} \arash{Yes, particlarly since a similar research question have been studied by \cite{alexander2006integrality} and \cite{TSPcompute}}Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.
 

### 2022-01-17 FDT2020/conclusion.tex
first run through reviewer 2 minor comments

@@
 Fractional Decomposition Tree is a tool to experimentally evaluate the known bounds (and conjectured bounds) on the integrality gap of combinatorial optimization IP formulations.
-We hope that applying this tool to a wide range of problems can be a tool to guide conjectures on the upper bounds of integrality gap or at least narrow down the instances for which a closer look is required for the study of integrality gap.
+We hope that applying this tool to a wide range of problems can guide conjectures on the upper bounds of integrality gap or at least narrow down the instances for which a closer look is required for the study of integrality gap.
 

### 2022-01-17 FDT2020/main-section.tex
first run through reviewer 2 minor comments

@@
 \begin{lemma}\label{LPClemma}
-	Given $x'\in \dom(P)$ and $\ell\in [n]$ where $x'_{\ell}<1$, in polynomial time we can find vectors $\hat{x}^0,\hat{x}^1$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\gamma_0 + \gamma_1  \geq 1/g$, (ii) $\hat{x}^0$ and $\hat{x}^1$ are in  $ P$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, and (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
+	Given $x'\in \dom(P)$ and $\ell\in [n]$ where $x'_{\ell}<1$, in polynomial time we can find vectors $\hat{x}^0,\hat{x}^1$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $1/g \leq \gamma_0 + \gamma_1  \leq 1$, (ii) $\hat{x}^0$ and $\hat{x}^1$ are in  $ P$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, and (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
 \end{lemma}
@@
 	&\;{\color{white}{\text{s.t.}} }\quad x^0 + x^1 \leq x'\label{packing}\\
+		&\;{\color{white}{\text{s.t.}} }\quad \lambda_0 + \lambda_1  \leq 1\label{mulitplier-packing}\\
 	&\;{\color{white}{\text{s.t.}} }\quad \lambda_0,\lambda_1 \geq 0
@@
 Note that $\lambda_0+\lambda_1 =1/g$.
+Since $g\leq 1$, Constraint (\ref{mulitplier-packing}) is satisfied.
 Constraint (\ref{packing}) is satisfied by Inequality (\ref{splitting}).
@@
 Thus we only need to show (iv) holds.
-We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$.
+We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq x'_j$.
 If $j=\ell,\ldots,t$, then this clearly holds.
@@
 \paragraph{Growing and Pruning FDT tree.} The FDT algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm.
-The nodes in $L_i$ correspond to the nodes in level $L_i$ of the FDT tree.
-The points in the leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.
+The nodes in $L_i$ correspond to the nodes in level $i$ of the FDT tree.
+The leaves of the FDT tree, $L_t$, are points in $\dom(P)$ and are integral for all integer variables.
 
@@
 In other words, Figure \ref{fdtvschris} is comparing the instance-specific upper bound on integrality gap certified by Christofides' algorithm to the approximation factor of the FDT algorithm for 2EC.
-
-\begin{figure}
-\centering
-\begin{tikzpicture}[scale=0.4]
-
-\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (0,-4)};
-\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(2.83,2.83) (-4,0)};
-\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (-2.83,-2.83)};
-\draw [dashed] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-2.83,2.83) (2.83,-2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (2.83,2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(4,0) (2.83,-2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (2.83,-2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,-4) (-2.83,-2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,-2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(-4,0) (-2.83,2.83)};
-
-\draw [-] [black, line width=0.2mm] plot [smooth, tension=0] coordinates {(0,4) (-2.83,2.83)};
-
-\draw[black,fill=white] (0,4) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (4,0) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (0,-4) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (-4,0) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (-2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (2.83,-2.83) ellipse (0.5 cm  and 0.5 cm);
-\draw[black,fill=white] (-2.83,2.83) ellipse (0.5 cm  and 0.5 cm);
-
-\node (1) at (0,4) {{1}};
-\node (2) at (2.83,2.83) {{2}};
-\node (3) at (4,0) {{3}};
-\node (4) at (2.83,-2.83) {{4}};
-\node (5) at (0,-4) {{5}};
-\node (6) at (-2.83,-2.83) {{6}};
-\node (7) at (-4,0) {{7}};
-\node (8) at (-2.83,2.83) {{8}};
-\end{tikzpicture}
-\caption{A Carr-Vempala point with 8 vertices on its cycle.
-Solid lines are edges with value strictly between $0$ and $1$.
-Dashed edges represent paths where each edge on the path has $x_e =1$.
-There can be an arbitrary number of degree-$2$ vertices on the dashed paths.}
-\label{fig:CVpoint}
-\end{figure}
-
 \begin{figure}[h!]

### 2022-01-19 FDT2020/response/response.tex
went through half of reviewer 3 minor comments

@@
 pairs (page number, line number) below.
-
+\response{Thank you for the recommendation. We added line numbers to the document.}
 \item (2,10) “we have formulated” – better to say “instances … are known” and give a reference, e.g.
@@
 fact. 
+\response{MIPLIB citation added and the wording is changed as suggested.}
+
 \item (2,14) “the” -> “these”?
@@
 whose value is at most C times the value of the LP optimum” or something like that.
+\response{Paragraph reworded as follows: Many combinatorial optimization problems can be formulated as IPs.
+An {\em LP-based approximation algorithm} uses the LP relaxations to the IP formulation to find provably good approximate feasible integer solutions in polynomial time.
+At the highest level, this involves solving the LP relaxation, using special  problem structure to find a feasible integer solution, and proving that the objective value of the solution is no more than $C$ times worse than the bound from the LP relaxation.
+The approximation factor $C$ can be a constant or depend on the input parameters of the IP, e.g.
+$O(\log(n))$ where $n$ is the number of variables in the formulation of the IP (the dimension of the problem).}
 \item (3,7) you say that a separation oracle should return a most violated constraint, but I don’t think this is the standard definition of e.g.
 Grötschel-Lovász-Schrijver – any violated constraint suffices to get polynomial convergence.
+\response{Fixed.}
 \item (3,11) “it could not before” -> “they could not before”
+\response{Fixed.}
 \item (3,23) “ResearcherS”
-\item (4,26) “We cannot hope to find…” – you’ve said this already.
-\item (5,8) “express A vector”
+\response{Fixed.}
+\item (4,26) “We cannot hope to find…” – you’ve said this already. \response{The sentence was removed.}
+\item (5,8) “express A vector” \response{Fixed.}
 \item (5,10) Please define $[0,1]$ which appears in $[0,1]^k$ .
 It seems you mean the closed interval between 0 and 1, but it is very commonly also used to be the set $\{0,1\}$, so clarification is in order.
-\item (5,16) “of A blocking type”
-\item (5,23) “assuming” –> “under”
-\item (5,30) ”$S(I)\in \{0,1\}^n$ should be $\subseteq$ instead of $\in$
-\item (6,1) delete “algorithm”
-\item (6,3) “it would be optimal” - what is “it”?
+\response{Added: , where $[0,1]^n = \{x\in \mathbb{R}^n, 0\leq x_i\leq 1 \mbox{ for } i\in[n]\}$ and $\{0,1\}^n = [0,1]^n \cap \mathbb{Z}^n$.}
+\item (5,16) “of A blocking type” \response{Fixed.}
+\item (5,23) “assuming” –> “under” \response{Fixed as suggested.}
+\item (5,30) ”$S(I)\in \{0,1\}^n$ should be $\subseteq$ instead of $\in$ \response{Fixed.}
+\item (6,1) delete “algorithm” \cite{Fixed.}
+\item (6,3) “it would be optimal” - what is “it”? \response{Rephrased as follows: If $C = g(I)$, FDT would have been optimal.}
 \item (6,3) “we can only guarantee a factor of” I think it would be clearer to say “we can
-only guarantee $C\leq g(I)$ ... ”
+only guarantee $C\leq g(I)$ ... ” \response{Fixed as suggested.}
 \item (6,7) how does the $\min$ in $\min(Cx^*, {0,1}^n )$ work? Coordinate-wise, or?
+\response{ Yes. But we removed this point-wise minimizing from the statement to make it simpler to state.}
 \item (6,27) “It’s” –> “Its” 
+\response{Fixed.}
 \item (7,5) what is $\chi^{F_i}$ ? I suppose it is the characteristic vector of $F_i$ but you should state
 this clearly. Also, what is $E_x$ ? is it the number of edges of $x$, that is, $\mbox{supp}(x)|$? Again
-please state clearly.
+please state clearly.  \response{We added definition of $E_x$ right before Theorem 6 and $\chi$ in the footnote of this page.}
 \item (7,13) “A subset of $U$ of $V$ ” – delete first “of”  
-\item (7,18) define or comment on UG-hard
+\response{Fixed.}
+\item (7,18) define or comment on UG-hard \response{Added this in the footnote: UGC is short for Unique Game Conjecture and conjectured to be NP-hard [Khot2002]}
 \item (7,19) “feasbility” –> “feasibility”
-\item (7,20) “3-5x slower” use “$\times$” (\\times) instead of “x”
-\item (7,29) Large space before “Note” - something fishy is going on here.
+\response{Fixed.}
+\item (7,20) “3-5x slower” use “$\times$” (\\times) instead of “x”\response{Fixed.}
+\item (7,29) Large space before “Note” - something fishy is going on here. \response{Fixed.}
 \item (9,14) add your experimental results about VC here also

### 2022-01-19 FDT2020/Introduction.tex
went through half of reviewer 3 minor comments

@@
 CBC) solvers that for specific IP instances can often find solutions that are optimal within a given tolerance.
-Still we have formulated moderate-sized IP instances that no commercial solver can currently solve.
+Still there are known moderate-sized IP instances that no commercial solver can currently solve \cite{MIPLIB}.
 Thus there is value in heuristics to find feasible solutions for general IP instances (see e.g.~\cite{HanafiT2017}).
@@
 
-{\em LP-based approximation algorithms} use LP relaxations to find provably good approximate feasible solutions to IP problems in polynomial time.
-At the highest level, they involve solving the LP relaxation, using special structure from the problem to find a feasible solution, and proving that the objective value of the solution is no more than $C$ times worse than the bound from the LP relaxation.
+Many combinatorial optimization problems can be formulated as IPs.
+An {\em LP-based approximation algorithm} uses the LP relaxations to the IP formulation to find provably good approximate feasible integer solutions in polynomial time.
+At the highest level, this involves solving the LP relaxation, using special  problem structure to find a feasible integer solution, and proving that the objective value of the solution is no more than $C$ times worse than the bound from the LP relaxation.
 The approximation factor $C$ can be a constant or depend on the input parameters of the IP, e.g.
@@
 A separation algorithm for a family of constraints takes an optimal solution to an LP instance that explicitly enforces only a (potentially empty) subset of the family.
-It either confirms that all constraints are satisfied or returns a most violated constraint.
+It either confirms that all constraints are satisfied or returns a violated constraint.
 Thus one can add this constraint and repeat at most a polynomial number of times until all are satisfied.
@@
 It can lead to better LP-based approximation algorithm bounds as described above.
-It can also help exact solvers run faster or solve instances it could not before.
+It can also help exact solvers run faster or solve instances they could not before.
 Exact IP solvers are based on intelligent branch-and-bound strategies.
@@
 The method is also a tool for evaluating the integrality gap for a formulation.
-Researcher can use it to determine whether they should expend effort to find new classes of cuts.
+Researchers can use it to determine whether they should expend effort to find new classes of cuts.
 They can also use it to help guide theory for finding tighter bounds on the integrality gap for classic problems like the traveling salesman problem.
@@
 The value of $g(I)$ depends on the constraints in~(\ref{S}).
-We cannot hope to find solutions for the IP with objective values better than $g(I)\cdot z_{LP}(I,c)$.
 More generally we can define the integrality gap for a class of instances $\mathcal{I}$ as follows.% In this case, the integrality gap for problem $\mathcal{I}$ is
@@
 spanning trees.
-For such problems there is an algorithm to express vector $x\in P(I)$ (a feasible LP solution) as a convex combination of points in $S(I)$ (feasible IP solutions) in polynomial time \cite{cons-cara}.
+For such problems there is an algorithm to express a vector $x\in P(I)$ (a feasible LP solution) as a convex combination of points in $S(I)$ (feasible IP solutions) in polynomial time \cite{cons-cara}.
 % The number of feasible solutions ($k$) in the convex combination can vary by instance.
@@
 The {\em dominant} of $P(I)$, which we denote by $\dom(P(I))$, is the set of points $x'$ such that there exists a point $x\in P$ with $x'\geq x$ in every component.
-A polyhedron is of \textit{blocking type} if it is equal to its dominant.
+A polyhedron is of \textit{a blocking type} if it is equal to its dominant.
 
@@
 To study integrality gaps, we wish to decompose a suitably scaled linear-programming solution into a convex combination of feasible integer solutions {\bf constructively}.
-That is, we ask: assuming reasonable complexity assumptions, given a specific problem $\mathcal{I}$ with  $1<g(\mathcal{I})<\infty$, and $x\in P(I)$ for some $I\in \mathcal{I}$, \textbf{can we write} $Cx$ as a convex combination of points in $\dom(S(I))$?
+That is, we ask: under reasonable complexity assumptions, given a specific problem $\mathcal{I}$ with  $1<g(\mathcal{I})<\infty$, and $x\in P(I)$ for some $I\in \mathcal{I}$, \textbf{can we write} $Cx$ as a convex combination of points in $\dom(S(I))$?
 We wish to find the smallest factor $C$ possible.
@@
 We give a general approximation framework for solving binary IPs.
-Consider the set of points described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume in addition that $S(I)\in \{0,1\}^n$ and $P(I)\subseteq [0,1]^n$.
+Consider the set of points described by sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively.
+Assume in addition that $S(I)\subseteq  \{0,1\}^n$ and $P(I)\subseteq [0,1]^n$, where $[0,1]^n = \{x\in \mathbb{R}^n, 0\leq x_i\leq 1 \mbox{ for } i\in[n]\}$ and $\{0,1\}^n = [0,1]^n \cap \mathbb{Z}^n$.
 %\cindy{Is it $S(I) \subseteq \{0,1\}^n$?}
@@
 
-In Section~\ref{sec:binaryfdt} we introduce the \textit{Fractional Decomposition Tree Algorithm} (FDT) which is polynomial time algorithm.
+In Section~\ref{sec:binaryfdt} we introduce the \textit{Fractional Decomposition Tree} (FDT) which is polynomial time algorithm.
 Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated coordinatewise by a ``factor" $C$ times $x$.
 % in the coordinates corresponding to $x$.
-If $C = g(I)$, it would be optimal. However we can only guarantee a factor of $g(I)^{|\spp(x)|}$. FDT iteratively solves linear programs that are about the same size as the description of $P(I)$.
+If $C = g(I)$, FDT would have been optimal. However we can only guarantee $C\leq g(I)^{|\spp(x)|}$. FDT iteratively solves linear programs that are about the same size as the description of $P(I)$.
 
@@
 For input graph $G$, let $\subtour(G)$ denote the feasible region of this LP.
-Let $\2ec(G)$ be the convex hull of incidence vectors\footnote{The incidence vector $x$ of a 2-edge-connected multi-subgraph has an element for each edge $e$, with $x_e \in \{0,1,2\}$ indicating the number of times edge $e$ appears in the solution.} of 2-edge-connected multi-subgraphs of graph $G$.
+Let $\2ec(G)$ be the convex hull of incidence vectors\footnote{The incidence vector of a 2-edge-connected multi-subgraph $F$, denoted by $\chi^F$ has an element for each edge $e$, with $x_e \in \{0,1,2\}$ indicating the number of times edge $e$ appears in the solution.} of 2-edge-connected multi-subgraphs of graph $G$.
 Following the definition in (\ref{gapproblem}) have
@@
 
-For a multi-subset of edges $F$ of $E$, we use $\chi^F$ to denote the characteristic vector of $F$ which is a vector in $\mathbb{R}^E$ where $\chi^F_e$ is equal to the multiplicity of edge $e$ in $F$.
-We denote $E_x$ to denote $\spp(x)$ as a subset of edges of $E$.
+We denote $E_x$ when regarding to $\spp(x)$ as a subset of edges of $E$.
 
@@
 In the \textsc{minimum vertex cover problem (VC)} we are given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$.
-A subset of $U$ of $V$ is a \textit{vertex cover} if for all $e\in E$ at least one endpoint of $e$ is in $U$.
+A subset $U$ of $V$ is a \textit{vertex cover} if for all $e\in E$ at least one endpoint of $e$ is in $U$.
 The goal in VC is to find the minimum-cost vertex cover.
@@
 The integrality gap of this formulation is exactly 2 \cite{davids}.
-Austrin, Khot and Safra~\cite{UGhardVC} show that it is UG-hard to approximate VC within any factor strictly better than 2.
-We compare  FDT and the feasbility pump heuristic \cite{fp1} on the small instances of the PACE\footnote{ Parameterized Algorithms and Computational Experiments: \url{https://pacechallenge.org/2019/}} 2019 challenge test cases \cite{PACE}.
-FDT was 3-5x slower, but still ran in seconds.
+Austrin, Khot and Safra~\cite{UGhardVC} show that it is UGC-hard to approximate VC within any factor strictly better than 2\footnote{UGC is short for Unique Game Conjecture and conjectured to be NP-hard \cite{Khot2002OnTP}}.
+We compare  FDT and the feasibility pump heuristic \cite{fp1} on the small instances of the PACE\footnote{ Parameterized Algorithms and Computational Experiments: \url{https://pacechallenge.org/2019/}} 2019 challenge test cases \cite{PACE}.
+FDT was $3$-$5\times$ slower, but still ran in seconds.
 It always gave a better vertex cover.
@@
 Multiple groups of researchers have conjectured that $g(\2ec)\leq \frac{6}{5}$ (see \cite{alexander2006integrality,boydlegault,hn19}, but the only known upper bound on $g(\2ec)$ stands at $\frac{3}{2}$ \cite{wolsey}.
-We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges, thereby confirming the conjecture for these instances.\cindy{This sounds like a contribution of the paper.} \arash{Yes, particlarly since a similar research question have been studied by \cite{alexander2006integrality} and \cite{TSPcompute}}Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.
-
+We show that the integrality gap is at most $\frac{6}{5}$ for Carr-Vempala points with at most 12 vertices on the cycle formed by the fractional edges, thereby confirming the conjecture for these instances.
+Note that the number of vertices in these instances can be arbitrarily high since the paths of edges with $x$-value 1 can be arbitrarily long.
+\cindy{This sounds like a contribution of the paper.} \arash{Yes, particlarly since a similar research question have been studied by \cite{alexander2006integrality} and \cite{TSPcompute}}
 \cindy{We probably need an explicit list of contributions.  It could be another subsection of the introduction.  This will help the reviewer and eventually, if published, the reader.}

### 2022-01-22 FDT2020/response/response.tex
finished minor comments - mostly

@@
 \item (9,14) add your experimental results about VC here also 
+\response{Added.}
 \item (10,7) again, large space
+\response{Fixed.}
 \item (10,14) it seems to me that the definition of the coordinates of $x^{(\ell+1)}$ other than $\ell+1$
 should appear in the algorithm too, not just here.
+\response{Line 3 in Algorithm 1 takes care of the other coordinates.}
 \item (11,14-25) I’m getting tripped up at line 17. I understand the case for coordinates which have $x_j=0$. But where do you deal with those that do not? I suppose I’m just
 missing something obvious, but so could any other reader. Please clarify your proof here.
-\item (12,10) “maintainS” 
+\response{Here the goal is to establish that there is a $z\leq x^{(\ell+1)}$.
+For the coordinates of $x^{(\ell+1)}$ that are zero we show the proof.
+The other coordinates of $x^{(\ell+1)}$ are 1.
+So we just need to emphasize that all the $\tilde{z}_i \leq 1$.
+This is added now, an a reference to an observation we added (Observation 7)}.
+
+\item (12,10) “maintainS”  \response{Fixed.}
 \item (13,28) “Growing and Pruning THE FDT tree”
+\response{Fixed.}
 \item (14,12) “It is easy to check” <– you do this quite a bit. Please go through your paper and
@@
 However, if some observation is necessary, think about the clearest and most concise way to impart this observation to the reader, and then do that instead of telling the reader that it should be “easy”.
-\item (14,12) “THE set $L'$”
+
+\response{Thank you for the reminder. We find several occurrences of trivially, obviously, easy to check and clearly.}
+
+\item (14,12) “THE set $L'$” \response{Fixed.}
 \item (14,25) “From THE leaves” 
+\response{Fixed.}
 \item (16,11-17) You should discuss why the intuitive approach of binarizing an LP (just split each variable into two binary variables and copy the respective column of the
@@
 stated, so I would just not comment on it. If you must, give a correct capacity and
-indicate the level of the cache.
+indicate the level of the cache. \response{We removed the cache amount. Thanks.}
 \item (19,22-26) Is there no good benchmark set for TAP? If not, please mention that as
@@
 \item (21,10) Christofides’ algorithm is no longer the fastest https://arxiv.org/abs/2007.01409
+
+\response{We added a reference to the KKO paper in the footnote.}
 \item (21,10-11) “In the classic graph-based…” <– this is a weird sentence; you should say
@@
 out of nowhere.
+\response{Rewrote this part: Let us remind our reader the Christofides algorithm for TSP: given a graph with edge costs find a minimum spanning tree of the graph. 
+Next, we add an $O$-join, where $O$ is the set of odd-degree vertices in the spanning tree.
+Note that the solutions to the TSP are also 2-edge-connected, which means that Christofides algorithm also provides solutions to the 2EC.
+The best-of-many Christofides (BOMC) algorithm~[AKS15] works better than the classic Christofides algorithm in practice[GW17].}
 

### 2022-01-22 FDT2020/Introduction.tex
finished minor comments - mostly

@@
 Formally, for some positive integer $k$, given a set of points $S\subseteq \mathbb{R}^k$ and a vector $x\in \mathbb{R}^k$, we say \textit{$x$ \underline{is} as a convex combination of points in $S$} if there exists a positive integer $\ell$ and $\theta \in [0,1]^\ell$, where $\sum_{i=1}^{\ell}\theta_i =1$ and $\tilde{x}^i\in S$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$.
-If a such a convex combination in polynomial time in the encoding size of the definition of $S$ and $x$, we say  \textit{$x$ \underline{can be written} as a convex combination of points in $S$}
+If such a convex combination can be found in time polynomial in the encoding size of the definition of $S$ and $x$, then we say  \textit{$x$ \underline{can be written} as a convex combination of points in $S$}
 
@@
 In particular, we computationally prove an upper bound on small instances of 2EC with a specific structure.
+\item We demonstrate (with VC) how FDT can be used to find feasible solutions of improved quality compared to those from the feasiblity pump \cite{fp1}.
 \end{itemize}

### 2022-01-22 FDT2020/main-section.tex
finished minor comments - mostly

@@
 	Given an integral vector $\tilde{x}$ in the dominant of an LP relaxation ($\tilde{x}\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$) for an IP instance that has integrality gap $g < \infty$, there is an algorithm (the DomToIP algorithm) that finds $\bar{x}\in S$ in polynomial time such that $\bar{x}\leq \tilde{x}$.\end{lemma}
-Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: numerically rounding up $x^*$ (or any fractional point in $P$) gives us a point in $\dom(P)$.
+Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since one can obtain an integer point in $\dom(P)$ by numerically rounding up $x^*$ (or any fractional point in $P$) gives us a point in $\dom(P)$.
 %\cindy{I added the caveat that the instance has a finite integrality gap and made it a little more self-contained.  Is it OK?}
@@
 In iteration $\ell\in \{0,\ldots,t-1\}$, if $\tilde{x}_{\ell+1}=1$, the algorithm reduces the $\ell + 1$st coordinate of the solution to $0$ if there is an LP-feasible point $x'$ that respects the decisions made so far, and has $x'_{\ell}=0$.
-Intuitively, we can fix this coordinate to $0$ in the partial solution and still set the remaining coordinates to find the solution promised in Lemma~\ref{domlemma}.
-\arash{A caution here: the phrase if possible a bit vague here.
-We round down to zero, if there is feasible solution to LP (so a point in $P(I)$, such that the first $\ell$ coordinates of it are all equal to the point $x^{(\ell)}$ that we have in iteration $\ell$ and its $\ell+1$-th coordinate is 0}.
-\cindy{Yes.
+Intuitively, we can fix this coordinate to $0$ in the partial solution and still set the remaining coordinates to find the solution promised in Lemma~\ref{domlemma}.\arash{A caution here: the phrase if possible a bit vague here.
+We round down to zero, if there is feasible solution to LP (so a point in $P(I)$, such that the first $\ell$ coordinates of it are all equal to the point $x^{(\ell)}$ that we have in iteration $\ell$ and its $\ell+1$-th coordinate is 0}\cindy{Yes.
 I was just trying to give intuition.
 In particular, I was trying to distinguish Dom2IP that starts with an integral vector, where we push $1$s down, from FDT, where we start with a fractional vector and progressively set components to binary values.
-Do you think the above version is OK?}
-More specifically, in iteration $\ell\in \{0,\ldots,t-1\}$ we produce $x^{(\ell)}\in \dom(P)$ such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
+Do you think the above version is OK?} More specifically, in iteration $\ell\in \{0,\ldots,t-1\}$ we produce $x^{(\ell)}\in \dom(P)$ such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,\ell$.
 These $\ell$ components will not change for the remainder of the algorithm.
@@
 So for $j\in [n]$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i\in [k]$.
-This implies $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$.
+This implies $\tilde{z}^i\leq x^{(\ell+1)}$ for $i\in [k]$.
 Hence, there exists $z\in S$ such that $z\leq x^{(\ell+1)}$.
@@
 The solutions contained in the nodes of the tree become progressively more integral at each level.
-In each level of the tree, the algorithm maintain a conic combination of points with the properties mentioned above.
+In each level of the tree, the algorithm maintains a conic combination of points with the properties mentioned above.
 Leaves of the FDT tree contain integral solutions
@@
 		Hence, Constraints (\ref{feasibility}) holds.
-Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$.
-The rest of the constraints trivially hold.
+Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is  $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$.
+Finally, we have $x^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g}\tilde{x}^i \leq \sum_{i\in[k], \tilde{x}^i_\ell = j}\theta_i\tilde{x}\leq \sum_{i\in[k], \tilde{x}^i_\ell = j}\theta_i = \lambda^j$.
+So all the constraints hold.
 	\end{cproof}
@@
 	We now show that $\hat{x}^0$, $\hat{x}^1$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions.
-Note that conditions (i), (ii), (iii), and (v) are trivially satisfied.
+Note that conditions (i), (ii), (iii), and (v) are satisfied directly from the  fact that $\bar{x}^0,\bar{x}^1,\gamma_0$ and $\gamma_1$ satisfy these conditions.
 Thus we only need to show (iv) holds.
 We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq x'_j$.
-If $j=\ell,\ldots,t$, then this clearly holds.
+If $j=\ell,\ldots,t$, the inequality is satisfied since $\hat{x}^i_j = \bar{x}^i_j$ for $i=0,1$ and property (iv) holds for $\bar{x}^0$ and $\bar{x}^1$.
 Hence, assume $j\leq \ell-1$.
@@
 
-\paragraph{Growing and Pruning FDT tree.} The FDT algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm.
+\paragraph{Growing and Pruning the FDT tree.} The FDT algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm.
 The nodes in $L_i$ correspond to the nodes in level $i$ of the FDT tree.
@@
 \begin{proof}
-	We prove this lemma using induction but one can clearly see how to turn this proof into a polynomial time algorithm.
+	We prove this lemma using induction but one can see how to turn this proof into a polynomial time algorithm.
 Let $L_0$ be the set that contains a single node (\textit{root of the FDT tree}) with $x^*$ and multiplier 1.
@@
 Add the pairs  $(x^{j0} ,\lambda_j\lambda^0_j)$ and  $(x^{j1} ,\lambda_j\lambda^1_j)$ to $L'$.
-It is easy to check that set $L'$ is a suitable candidate for $L_{i+1}$, i.e.
+The set $L'$ is a suitable candidate for $L_{i+1}$, i.e.
 set $L'$ satisfies (a), (b) and (c).
@@
 
-	\paragraph{From leaves of FDT to feasible solutions.}
+	\paragraph{From the leaves of FDT to feasible solutions.}
 	For the leaves of the FDT tree,  $L_t$, we have that every solution $x$ in $L_t$ has $x\in\{0,1\}^n$ and $x\in \dom(P)$.
@@
 For each $h\in P_f$ let $x'_h= x_f$ for all $f$ with $x_f\geq 1$.
-It is easy to check that $x'\in \subtour(G')$.
+We have $x'\in \subtour(G')$.
 By Theorem \ref{CV2} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and 2-edge-connected multi-subgraphs $F'_i$ of $G'$ for $i=1,\ldots,k$ such that
@@
 		Let $x^j = \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g(\2ec)\ceil{\frac{2}{\epsilon}}}\chi^{F_i}$ and $\theta_j =  \sum_{i\in [k]: \chi^{F_i}_e=j}\frac{\theta_i(\ceil{\frac{2}{\epsilon}}-1)}{g(\2ec)\ceil{\frac{2}{\epsilon}}}$ for $j=0,1,2$.
-It is easy to check that $x^j$ , $\theta_j$ for $j=0,1,2$ is a feasible solution to the LP above.
+Notice that  $x^j$ , $\theta_j$ for $j=0,1,2$ is a feasible solution to the LP above.
 We have $\sum_{j=0,1,2}\theta_j = \frac{\ceil{\frac{2}{\epsilon}}-1}{g(\2ec)\ceil{\frac{2}{\epsilon}}}$.
@@
 	We proceed by induction on $i$.
-Define $L_0=\{(x^*,1)\}$.
-It is easy to check all the properties are satisfied.
+Define $L_0=\{(x^*,1)\}$, which satisfies properties (a) to (d).
 Now, suppose by induction we have $L_{i-1}$ for some $i=1,\ldots,t$ that satisfies all the properties.
@@
 
-We implemented the experiments for VC and TAP in Python running on a linux workstation (Ubuntu 18.04.3) with 8 cores of Intel(R) Core(TM) i7-8565U CPU  1.80GHz processors and 1Mb of cache.
+We implemented the experiments for VC and TAP in Python running on a linux workstation (Ubuntu 18.04.3) with 8 cores of Intel(R) Core(TM) i7-8565U CPU  1.80GHz processors.
 We used the CPLEX 12.9.0.0 solver to solve the pyomo LP models.
@@
 %	\caption{FDT vs the 2-approximation for TAP\cite{FJ81} on randomly generated extreme points of the cut-LP.}
-	\caption{TAP on our random instances: FDT run on LP optimal vs the 2-approximation for TAP\cite{FJ81}.}
+	\caption{TAP on our random instances: FDT run on LP optimal vs the 2-approximation for TAP \cite{FJ81}.}
 	\label{fjvsfdt}
@@
 So in that sense, these are the hardest fractional points to round to a feasible solution.
-We now compare the quality of FDT's solution from a Carr-Vempala point to that of Christofides, the best known approximation algorithm.
-In the classic graph-based Christofides algorithm for TSP, find a minimum spanning tree of the graph.
-Then, since TSP runs on a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)-subgraph 2-edge-connected.
-If we stop that algorithm without shortcutting, we have a feasible solution for Metric-2EC (given a complete graph, find the minimum-cost 2-edge-connected subgraph, with no multiedges).
-\arash{The following sentence is not accurate, Metric-TSP is the same as TSP on a non-complete graph where we can take multiple copies of the edges, Metric-2EC (given complete graph with metric costs find the minimum cost 2-edge-connected SUBgraph -no doubling of edges-) is the same as 2EC on a non-complete graph where we can take multiple copies of edges.}
-\cindy{It sounded like 2EC doesn't assume a complete graph.  But I removed the sentence.  Is the following OK?}
-\arash{Still not quite accurate.
+We now compare the quality of FDT's solution from a Carr-Vempala point to that of Christofides, the best known approximation algorithm\footnote{Recently, \cite{KKO} improved over Christofides algorithm by a small factor.}.
+Let us remind our reader the Christofides algorithm for TSP: given a graph with edge costs find a minimum spanning tree of the graph.
+%Then, since TSP runs on a complete graph, add a perfect matching on the vertices that have odd degree in the spanning tree to make the (multi)-subgraph 2-edge-connected.
+If we stop that algorithm without shortcutting, we have a feasible solution for Metric-2EC (given a complete graph, find the minimum-cost 2-edge-connected subgraph, with no multiedges).\arash{The following sentence is not accurate, Metric-TSP is the same as TSP on a non-complete graph where we can take multiple copies of the edges, Metric-2EC (given complete graph with metric costs find the minimum cost 2-edge-connected SUBgraph -no doubling of edges-) is the same as 2EC on a non-complete graph where we can take multiple copies of edges.}\cindy{It sounded like 2EC doesn't assume a complete graph.
+But I removed the sentence.
+Is the following OK?}\arash{Still not quite accurate.
 The sentence gives the impression that changing matching with $T$-join is the difference between TSP and 2EC, but its the difference between working with complete graph with metric costs and a non-complete graph where doubling edges is allowed.}
-For 2EC, instead of a matching, we add an $O$-join, where $O$ is the set of odd-degree vertices in the spanning tree~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.
+Next, we add an $O$-join, where $O$ is the set of odd-degree vertices in the spanning tree~\footnote{For graph $G=(V,E)$ and $O\subseteq V$ with $|O|$ even, an $O$-join of $G$ is a subgraph of $G$ that has odd degree on the vertices in $O$ and even degree on vertices in $V\setminus O$.
 Graphs always have an even number of odd vertices since every edge has two endpoints, giving an even number of endpoints.}.
+Note that the solutions to the TSP are also 2-edge-connected, which means that Christofides algorithm also provides solutions to the 2EC.
 The best-of-many Christofides (BOMC) algorithm~\cite{AKS15} works better than the classic Christofides algorithm in practice~\cite{GW17}.
-The BOMC algorithm samples many spanning trees from the LP relaxation (with edges chosen proportionally to the LP value), augments each spanning tree with the matching, and takes the best solution.
+The BOMC algorithm samples many spanning trees from the LP relaxation (with edges chosen proportionally to the LP value), augments each spanning tree with minimum cost join on the odd degree vertices of the spanning tree, and takes the best solution.
 

### 2022-01-22 FDT2020/response/response.tex
one major comment responsed with disagreement

@@
 quickly. On TAP and 2EC, the authors compare to problem-specific approximation algorithms that are not particularly designed to produce high quality solutions either.
+\response{Our comparison of FDT to feasibility pump is to main showcase a use case of the algorithm and a direction that could be possibly explored.
+We are not offering FDT as a replacement for FP.
+We will add remarks that make this clear to the reader.
+
+We respectfully disagree about the comment for 2EC since we use BOMC and turn it into an instance specific rounding algorithm for subtour elimination points.
+As presented in Figure 3, we don't settle for the worst-case upper bound of 3/2.
+Similarly, for TAP, FJ81 is the only rounding algorithm known for the solution of the CUT-LP.
+Again, we don't use the worst-case upper bound of 2 and use the instance specific gap provided by the algorithm.
+Also we remark that FDT is a generic algorithm that applies to any type of IP formulation, while BOMC and FJ81 only work for a certain type of formulation.}
+
 \begin{enumerate}

### 2022-01-22 FDT2020/FDT_revised.tex
main file - fdt revised added

--- 2020-06-12 FDT2020/FDT.tex
@@
 % To drop all comments, just comment out \iffalse and \fi
-\iffalse
+
 \renewcommand{\cindy}[1]{}
@@
 \renewcommand{\bob}[1]{}
-\fi
 
@@
 \usepackage{glossaries}
+\usepackage{subcaption}
 
@@
 \DeclareMathOperator{\prun}{{{Pruning}}}
+\DeclareMathOperator{\HelperLP}{{{FixNextVarLP}}}
 
@@
 \DeclareMathOperator{\ecss}{{{S2ECS}}}
+
+\usepackage{lineno}
+\linenumbers
 
@@
 the U.S. Office of Naval Research under award number N00014-18-1-2099.}
-\and \textsc{Arash Haddadan}\thanks{Carnegie Mellon University  {\tt{ahaddada@andrew.cmu.edu}}.}
+\and \textsc{Arash Haddadan}\thanks{University of Virginia  {\tt{ahaddada@virginia.edu}}.  This work was mainly done when this author was a graduate student at Carnegie Mellon University.}
 \and \textsc{Cynthia A.
@@
 
-\begin{document}{\bibliographystyle{alpha}}
+\begin{document}
 
@@
 We demonstrate that with experiments studying the integrality gap of two problems: optimally augmenting a tree to a 2-edge-connected graph and finding a minimum-cost 2-edge-connected multi-subgraph (2EC).
-We also give a simplified algorithm, Dom2IP, that more quickly determines if an instance has an unbounded integrality gap.
+We also give a simplified algorithm, DomToIP, that more quickly determines if an instance has an unbounded integrality gap.
 We show that FDT's speed and approximation quality compare well to that of feasibility pump on moderate-sized instances of the vertex cover problem.
@@
 
+\clearpage
 \input{Introduction}
 \input{main-section}
-
-\bibliographystyle{abbrv}
+\input{conclusion}
+\bibliographystyle{alpha}
+%\bibliographystyle{abbrv}
 \bibliography{FDT}
@@
 \end{document}
-
-\input{Beyond4}

### 2022-01-23 FDT2020/response/response.tex
addressed the comment on binrazing the 0,1,2 programs

@@
 constraint matrix) does not lead to the same or better result. Or maybe it does?
+\response{We added this paragraph in the discussion of why $\{0,1,2\}$ problems are different from binary problems: Another approach to a $\{0,1,2\}$ problem could be to ``binarize'' the variables, but splitting each variable into two binary copies and solving the binary problem via FDT for binary IPs (Theorem \ref{FDTFull}).
+One potential issue that can arise by doing this is that the binary version of a problem might have a larger integrality gap compared to the one that allows larger multiplicity.
+One example of this is the 2EC problem considered in this section.
+As mentioned above, we have $g(\mbox{2EC})\leq \frac{3}{2}$, while $g(\mbox{2ECSS})\geq \frac{3}{2}$, where 2ECSS is a problem equivalent to 2EC but without any doubled edges allowed {CKKK08}.}
+
 \item (19,14) “1Mb cache” – I looked up this CPU and it has 1MB of L2 cache. Note that

### 2022-01-23 FDT2020/main-section.tex
addressed the comment on binrazing the 0,1,2 programs

@@
 \FDTEC*
-We do not know the exact value for $g(\2ec)$, but we know $\frac{6}{5} \leq g(\2ec) \leq \frac{3}{2}$ \cite{alexander2006integrality,wolsey}.
+We do not know the exact value for $g(\2ec)$, but we know $\frac{6}{5} \leq g(\2ec) \leq \frac{3}{2}$ \cite{alexander2006integrality,wolsey}\footnote{The recent result of \cite{KKO}  shows that $g(\2ec) \leq \frac{3}{2}-\epsilon$ for a tiny but constant $\epsilon >0$.}.
 The FDT algorithm for 2EC is very similar to the one for binary IPs, but there are some differences as well.
@@
 That is the main difficulty when dealing with $\{0,1,2\}$-IPs.
+
+Another approach to a $\{0,1,2\}$ problem could be to ``binarize'' the variables, but splitting each variable into two binary copies and solving the binary problem via FDT for binary IPs (Theorem \ref{binaryFDT}).
+One potential issue that can arise by doing this is that the binary version of a problem might have a larger integrality gap compared to the one that allows larger multiplicity.
+For instance, as mentioned above we have $g(\2ec)\leq \frac{3}{2}$ and  $g(\mbox{2ECSS})\geq \frac{3}{2}$, where 2ECSS is a problem equivalent to $\2ec$ but without any doubled edges allowed \cite{32gaptap}\footnote{In light of the recent paper of \cite{KKO} we now know that $g(\2ec)< g(\mbox{2ECSS})$.}
 

### 2022-01-24 FDT2020/response/response.tex
addressed the major comment on null branches

@@
 the branching step returns just 1 or (in the case of 2EC) just 2 vectors.
-4. As noted before, I find the comparisons against the FP heuristic on VC
+\response{Yes. We corrected this in the statement of Lemma 9, 10, 12. Also in the description of the Algorithm 2.}
+\item As noted before, I find the comparisons against the FP heuristic on VC
 and the 2-approximation for TAP rather dubious. To show that the FDT
@@
 \item (5,30) ”$S(I)\in \{0,1\}^n$ should be $\subseteq$ instead of $\in$ \response{Fixed.}
-\item (6,1) delete “algorithm” \cite{Fixed.}
+\item (6,1) delete “algorithm” \response{Fixed.}
 \item (6,3) “it would be optimal” - what is “it”? \response{Rephrased as follows: If $C = g(I)$, FDT would have been optimal.}

### 2022-01-24 FDT2020/main-section.tex
addressed the major comment on null branches

@@
 
+We also make the following assumption that make the presentation of the results simpler: for $\ell \in [n]$ the set $\{x\in P: x_\ell = 0\}$ is empty, we assume that every point in $P$ has 1 in the $\ell$-th coordinate, i.e.
+constraints matrix $A$ contains the valid constraint that $x_\ell \geq 1$.
+We make this assumption to enusre that we always have a two branches when branching on a fractional coordinate of a point.
+
 \paragraph{Branching on a node.}
@@
 \begin{lemma}\label{LPClemma}
-	Given $x'\in \dom(P)$ and $\ell\in [n]$ where $x'_{\ell}<1$, in polynomial time we can find vectors $\hat{x}^0,\hat{x}^1$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $1/g \leq \gamma_0 + \gamma_1  \leq 1$, (ii) $\hat{x}^0$ and $\hat{x}^1$ are in  $ P$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, and (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
+	Given $x'\in \dom(P)$ and $\ell\in [n]$ where $0 \leq x'_{\ell}<1$, in polynomial time we can find vectors $\hat{x}^0,\hat{x}^1$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $1/g \leq \gamma_0 + \gamma_1  \leq 1$, (ii) if $\gamma_i > 0$, then $\hat{x}^i \in P$ for $i=0,1$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, and (iv) $\gamma_0 \hat{x}^0 + \gamma_1\hat{x}^1 \leq x'$.
 \end{lemma}
@@
 
-	Let $y^0$, $y^1$, $\lambda^*_0$, and $\lambda^*_1$ be an optimal solution to the LP above. Set $\gamma_0=\lambda^*_0$ and $\gamma_1 = \lambda^*_1$.
-%Let $x^0$, $x^1$, $\lambda_0$, and $\lambda_1$ be an optimal solution to the LP above. Set $\gamma_0=\lambda_0$ and $\gamma_1 = \lambda_1$.
-\cindy{The sentence right before this is how I think you link the $\lambda$ in the LP to the $\gamma$ constants in the Lemma statement and the claim below, etc.}
-Let $\hat{x}^0 = y^0/\lambda^*_0$, $\hat{x}^1=y^1/\lambda^*_1$. This choice satisfies  (ii), (iii), (iv). To show that (i) is also satisfied we prove the following claim.
+	Let $y^0$, $y^1$, $\lambda^*_0$, and $\lambda^*_1$ be an optimal solution to the LP above.
+For $i = 0,1$, if $\lambda^*_i = 0$, then let $\gamma_i=0$ and $\hat{x}^i = \{i\}^n$, otherwise let $\gamma_i = \lambda_i$ and $\hat{x}^i=y^i/\lambda_i$.\cindy{The sentence right before this is how I think you link the $\lambda$ in the LP to the $\gamma$ constants in the Lemma statement and the claim below, etc.} This choice satisfies  (ii), (iii), (iv).
+To show that (i) is also satisfied we prove the following claim.
 	\arash{Now that I notice, we use $\lambda_0,\lambda_1,x^0,x^1$ to represnt a feasible solution to the system 13-18.
@@
 \begin{lemma}\label{round-up}
-	Given $x'\in \dom(P)$ where $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ and $x'_{\ell}<1$ for some $\ell\geq 1$ we can find in polynomial time vectors $\hat{x}^0,\hat{x}^1$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) ${ 1}/{g}\leq \gamma_0 + \gamma_1  \leq 1$, (ii) $\hat{x}^0$ and $\hat{x}^1$ are in  $\dom( P)$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
+	Given $x'\in \dom(P)$ where $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ and $x'_{\ell}<1$ for some $\ell\geq 1$ we can find in polynomial time vectors $\hat{x}^0,\hat{x}^1$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) ${ 1}/{g}\leq \gamma_0 + \gamma_1  \leq 1$, (ii) if $\gamma_i>0$, then $\hat{x}^i\in \dom(P)$ for $i=0,1$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
 	x'$,(v) $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j\in[\ell-1]$.
@@
 
-\paragraph{Growing and Pruning the FDT tree.} The FDT algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm.
+\paragraph{Growing and Pruning the FDT tree.} The FDT algorithm maintains nodes $L_i$ in iteration $i$ of the algorithm with multiplier strictly larger than 0.
 The nodes in $L_i$ correspond to the nodes in level $i$ of the FDT tree.
@@
 				Apply Lemma \ref{round-up} to obtain $[\hat{x}^0,\gamma_0]$ and $[\hat{x}^1,\gamma_1]$\\
-				$L' \leftarrow L' \cup \{[\hat{x}^0,\lambda\cdot\gamma_0]\} \cup \{[\hat{x}^1,\lambda\cdot\gamma_1]\}$\\			
+				\For{$j=0,1$}{
+				\If {$\gamma_j > 0$}{
+				$L' \leftarrow L' \cup \{[\hat{x}^j,\lambda\cdot\gamma_j]\}$
+				}		
+			}	
 			}
@@
 
-Another approach to a $\{0,1,2\}$ problem could be to ``binarize'' the variables, but splitting each variable into two binary copies and solving the binary problem via FDT for binary IPs (Theorem \ref{binaryFDT}).
+Another approach to a $\{0,1,2\}$ problem could be to split each variable into two binary copies and solving the binary problem via FDT for binary IPs (Theorem \ref{binaryFDT}).
 One potential issue that can arise by doing this is that the binary version of a problem might have a larger integrality gap compared to the one that allows larger multiplicity.
-For instance, as mentioned above we have $g(\2ec)\leq \frac{3}{2}$ and  $g(\mbox{2ECSS})\geq \frac{3}{2}$, where 2ECSS is a problem equivalent to $\2ec$ but without any doubled edges allowed \cite{32gaptap}\footnote{In light of the recent paper of \cite{KKO} we now know that $g(\2ec)< g(\mbox{2ECSS})$.}
+For instance, as mentioned above we have $g(\2ec)\leq \frac{3}{2}$ and  $g(\mbox{2ECSS})\geq \frac{3}{2}$, where 2ECSS is a problem equivalent to $\2ec$ but without any doubled edges allowed \cite{32gaptap}\footnote{In light of the recent paper of \cite{KKO} we now know that $g(\2ec)< g(\mbox{2ECSS})$.}.
 
@@
 	\label{LPC2EC}
-	Given $x\in \subtour(G)$, and $e\in E$ we can find in polynomial time vectors $x^0,x^1$ and $x^2$ and scalars $\gamma_0,\gamma_1$, and $\gamma_2$ such that: (i) $\gamma_0 + \gamma_1 +\gamma_2 \geq { 1}/{g(\2ec)}$, (ii) $x^0,x^1,$ and $x^2$ are in  $ \subtour(G)$, (iii) $x^0_e=0$, $x^1_e=1$, and $x^2_e=2$, (iv) $\gamma_0 x^0 + \gamma_1{x}^1  + \gamma_2x^2\leq {x}$, (v) for $f\in E$ with ${x}_f\geq 1$, we have $x^j_f\geq 1$ for $j=0,1,2$.
+	Given $x\in \subtour(G)$, and $e\in E$ we can find in polynomial time vectors $x^0,x^1$ and $x^2$ and scalars $\gamma_0,\gamma_1$, and $\gamma_2$ such that: (i) $\gamma_0 + \gamma_1 +\gamma_2 \geq { 1}/{g(\2ec)}$, (ii) if $\gamma_i > 0$, then $x^i \in \subtour(G)$ for $i=0,1,2$, (iii) $x^0_e=0$, $x^1_e=1$, and $x^2_e=2$, (iv) $\gamma_0 x^0 + \gamma_1{x}^1  + \gamma_2x^2\leq {x}$, (v) for $f\in E$ with ${x}_f\geq 1$, we have $x^j_f\geq 1$ for $j=0,1,2$ with $\gamma_j > 0$.
 \end{restatable}
@@
 	\end{align}	Let $x^j$, $\gamma_j$ for $j=0,1,2$ be an optimal solution solution to the LP above.
-Let $\hat{x}^{j}={x^j}/{\gamma_j}$ for $j=0,1,2$ where $\gamma_j>0$.
-If $\gamma_j=0$, let $\hat{x}^{j}=0$.
+For $j=0,1,2$, if $\gamma_j = 0$, then let $\hat{x}^j=\{j\}^E$, otherwise let $\hat{x}^{j}={x^j}/{\gamma_j}$ for $j=0,1,2$ where $\gamma_j>0$.
 Observe that  (ii), (iii), (iv), and (v) are satisfied with this choice.

### 2022-01-24 FDT2020/main-section.tex
small fixed - removed the unneccary assumption

@@
 that dominate a point in $P$. In Lemma~\ref{domlemma} we saw how to turn these into points in $S$.
-
-We also make the following assumption that make the presentation of the results simpler: for $\ell \in [n]$ the set $\{x\in P: x_\ell = 0\}$ is empty, we assume that every point in $P$ has 1 in the $\ell$-th coordinate, i.e.
-constraints matrix $A$ contains the valid constraint that $x_\ell \geq 1$.
-We make this assumption to enusre that we always have a two branches when branching on a fractional coordinate of a point.
 

### 2022-01-29 FDT2020/Introduction.tex
small changes in intro
fixed bug
IG discussion

@@
 In this paper, we give a method to find feasible solutions for IPs if the integrality gap is bounded.
-The method is also a tool for evaluating the integrality gap for a formulation.
+The method is also a tool for evaluating the integrality gap for a polyhedron.
 Researchers can use it to determine whether they should expend effort to find new classes of cuts.
@@
 \end{equation}
-Let $I=(A,b)$ denote an instance. Then $S(I)$ and $P(I)$ denote $S(A,b)$ and $P(A,b)$, respectively. Given a linear objective function $c$, an IP is $\min \;\{cx:\; x \in S(I)\}$.
+Let $I=(A,b)$ denote an instance of a polyhedron (henceforth an instance).
+Then $S(I)$ and $P(I)$ denote $S(A,b)$ and $P(A,b)$, respectively.
+Given a linear objective function $c$, an IP is $\min \;\{cx:\; x \in S(I)\}$.
 
@@
 
-Many researchers (see \cite{davids,vazirani}) have developed polynomial time LP-based approximation algorithms that find solutions for special classes of IPs whose cost are provably at most $C\cdot z_{LP}(I,c)$ for some (possibly constant) function $C$.
-If the analysis uses the LP bound to prove the approximation quality, then $C$ is at least the integrality gap.
 %However, for many combinatorial optimization problems there is a limit to such techniques based on LP relaxations, represented  by the {integrality gap} of the IP formulation.
@@
 Based on this definition I think we are not adding a restriction but we are looking at specific type of IPs arising form problems whose instances have non-negative cost vectors which is not a huge stretch as most combinatorial optimization problems are of this forms.}
-\begin{definition}
+\begin{definition}\label{IGofPoly}
 The integrality gap $g(I)$ for instance $I$ is: $$g(I)= \sup_{c\geq 0}\frac{z_{IP}(I,c)}{z_{LP}(I,c)},$$
@@
 
-In general the integrality gap is defined similarly for any objective function, but we wish to be explicit about the class of problems we assume in this paper.
+Consider an instance of a combinatorial optimization problem $\mathcal{P}$.
+We can characetrize $\mathcal{P}$ by a set of feasible solutions in $S\in \mathbb{Z}_{\geq 0}^n$ and a cost function $c\in \mathbb{R}_{\geq 0}^n$.
+In many cases (see \cite{vazirani,shmoyswilliamson}) the set $S$ can decribed as a set of integer points within a polyhedron $P$ (in fact the choice of $P$ need not be unique.) In this case, the integrality gap of $\mathcal{P}$ with respect to $P$ is $\min\{cx:x\in S\}/{\min\{cx:x\in P\}}$.
+Hence $g(I)$ in Defintion \ref{IGofPoly} is equivalent to the worst-case integrality gap of all instances of a problem with respect to $P(I)$.
+
+A combinatorial optimization problem consists of a family of instances that potentially have different sets of feasible solutions (e.g.
+due to different sizes).
+In this case, the integraltiy gap of combinatorial optimization problem with respect to a IP formulation, is the worst case integrality gap of over all instances of the combinatorial optmization problem with the linear relaxation of the respective instance of the IP formulation, or the worst case integrality gap of $I$ for all instances $\mathcal{I}$ in the IP formulation.
+Therefore, we define,
+
+\begin{equation}\label{gapproblem}
+g(\mathcal{I}) = \sup_{I\in\mathcal{I}}g(I).
+\end{equation}
+
 For example consider the minimum cost \textsc{2-edge-connected multi-subgraph problem (2EC)}: Given a graph $G=(V,E)$ and $c\in \mathbb{R}^E_{\geq 0}$, 2EC asks for the minimum cost 2-edge-connected subgraph of $G$, with multi-edges allowed.
 A graph is 2-edge-connected if there are at least two edge-disjoint paths between every pair of vertices.
-A linear-programming relaxation for this problem, known as the {\em subtour-elimination} relaxation, is
- \begin{equation}\min \{cx: \sum_{e\in \delta(U)}x_e \geq 2 \mbox{ for } \emptyset \subsetneq U \subsetneq V,\; x\in [0,2]^{E}\}, 
+An IP formulation for this problem, known as the {\em subtour-elimination}, is
+ \begin{equation}\min \{cx: \sum_{e\in \delta(U)}x_e \geq 2 \mbox{ for } \emptyset \subsetneq U \subsetneq V,\; x\in \{0,1,2\}^{E}\}, 
  \label{eq:subtour}
  \end{equation}
-where $\delta(U)$ for vertex subset $U$ is the set of edges that cross the cut defined by $U$.  That is, each $e \in \delta(U)$ has one endpoint in $U$ and the other endpoint in $V-U$.
- In this case the instance-specific integrality gap is the integrality gap of the subtour-elimination relaxation for the 2EC on a graph with $n$ vertices.
+where $\delta(U)$ for vertex subset $U$ is the set of edges that cross the cut defined by $U$.
+That is, each $e \in \delta(U)$ has one endpoint in $U$ and the other endpoint in $V-U$.
+We denote the linear relaxation of this IP as $\subtour(G)$.
+Notice that in this case, $G$ defines the polyhedron, while the pair of $G$ and $c$ defines the instance of 2EC.
+Let $I_G$ be the polyhedron instance defined by $\subtour(G)$.
+Then $g(I_G)$ is the worst-case integrality gap 2EC on $G$ over all non-negative cost functions and integrality gap of 2EC is $\max_{G} g(I_G))$.
+
+% In this case the instance-specific integrality gap is the integrality gap of the subtour-elimination relaxation for the 2EC on a graph with $n$ vertices.
 Alexander et al.
 \cite{alexander2006integrality} showed this instance-specific integrality gap
-%of the subtour elimination relaxation for the 2EC
-is at most $\frac{7}{6}$ for instances with $n= 10$ .
+%of the subtour elimination relaxation for the 2EC is at most $\frac{7}{6}$ for instances with $n= 10$ .
 
-The value of $g(I)$ depends on the constraints in~(\ref{S}).
+% The value of $g(I)$ depends on the constraints in~(\ref{S}).
 More generally we can define the integrality gap for a class of instances $\mathcal{I}$ as follows.% In this case, the integrality gap for problem $\mathcal{I}$ is
-\begin{equation}\label{gapproblem}
-g(\mathcal{I}) = \max_{c\geq 0 , I\in\mathcal{I}}\frac{z_{IP}(I,c)}{z_{LP}(I,c)}.
-\end{equation}
-For example, the integrality gap of the subtour-elimination relaxation for the 2EC is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}.
+
+%Many researchers (see \cite{davids,vazirani}) have developed polynomial time LP-based approximation algorithms that find solutions for special classes of IPs whose cost are provably at most $C\cdot z_{LP}(I,c)$ for some (possibly constant) function $C$.
+If the analysis uses the LP bound to prove the approximation quality, then $C$ is at least the integrality gap.
+
+%For example, the integrality gap of the subtour-elimination relaxation for the 2EC is at most $\frac{3}{2}$ \cite{wolsey} and at least $\frac{6}{5}$ \cite{alexander2006integrality}.
 Therefore, we cannot hope to obtain an LP-based $(\frac{6}{5}-\epsilon)$-approximation algorithm for this problem using this LP relaxation to bound the quality of a feasible solution.
@@
 While there is an exact algorithm for problems with gap $1$, as stated in Proposition \ref{cara}, Theorem~\ref{CV2} is existential, with no construction.
+We remark that Proposition \label{CV2} would not work if we drop the non-negatvitiy constraints on the cost function $c$ in the definition of integrality gap (Defitinon \ref{IGofPoly}).
 %In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
@@
 \fi
+
 To study integrality gaps, we wish to decompose a suitably scaled linear-programming solution into a convex combination of feasible integer solutions {\bf constructively}.
@@
 We wish to find the smallest factor $C$ possible.
+
+Carr and Vempala \cite{metarounding} showed if there an algorithm $\mathcal{A}$ that for $I\in \mathcal{I}$ and $c\geq 0$ finds $z\in S(I)$ with $cz\leq g'cx$ for any $x\in P(I)$, then $g'x$ can be \textbf{write} as a convex combination of points in $S(I)$.
+However, for many known problems there is a gap between the best known $g'$ and $g(\mathcal{I})$.
 

### 2022-01-29 FDT2020/Introduction.tex
adrresed the choice

@@
 
+The reason that we define integrality gap for a polyhedron as opposed to an instance of a problem is that our algorithms are independent of the cost function $c$.
+
 A combinatorial optimization problem consists of a family of instances that potentially have different sets of feasible solutions (e.g.
@@
 Let $I_G$ be the polyhedron instance defined by $\subtour(G)$.
-Then $g(I_G)$ is the worst-case integrality gap 2EC on $G$ over all non-negative cost functions and integrality gap of 2EC is $\max_{G} g(I_G))$.
+Then $g(I_G)$ is the worst-case integrality gap 2EC on $G$ over all non-negative cost functions and integrality gap of 2EC is $\sup_{G} g(I_G)$.
 

### 2022-01-30 FDT2020/conclusion.tex
p 25 footnote fix

@@
 
-The results in Sections \ref{sec:domTOIP}, \ref{sec:binaryfdt}  and \ref{sec:2EC} hold if the intial integer program has some auxilliary continuous variables\footnote{Here by auxilliary variables we mean a variable that does not participate in the objective function}.
+The results in Sections \ref{sec:domTOIP}, \ref{sec:binaryfdt}  and \ref{sec:2EC} hold if the intial integer program has some auxilliary continuous variables\footnote{Here by auxilliary variables we mean a variable that does not participate in the objective function.}.
 That is, when we have

### 2022-01-31 FDT2020/Introduction.tex
addressed the issue w. adding constraints

@@
 These heuristics, such as the popular Feasibility pump algorithm \cite{fp1,fp2}, are often effective and fast in practice.
-However, the heuristics can sometimes fail to find a feasible solution.
+However, these heuristics can sometimes fail to find a feasible solution.
 Moreover, these heuristics do not provide any bounds on the quality of the solution they find.
@@
 
+A keen reader might ask why Theorem \ref{domtoIP} does not imply that P = NP, as one iteratively find a feasible solution $x^*\in S(I)$, and add the constraint $x\leq cx^*-\epsilon$ for some small enough $\epsilon>0$ to $I$ until DomToIP fails to find a feasible solution.
+However, note that adding constraints to $I$ might result in $g(I)$ becoming infinite, in which case DomToIP would fail to find a feasible solution to the IP.
+
 %\cindy{Arash, please check how I defined $L(I)$.  It was not defined before.}

### 2022-05-05 FDT2020/FDT_revised.tex
comments almost all done

@@
 \begin{abstract}
+
 We present a new algorithm, Fractional Decomposition Tree (FDT) for finding a feasible solution for an integer program (IP) where all variables are binary.
@@
 FDT is also a tool for studying the integrality gap of IP formulations.
-We demonstrate that with experiments studying the integrality gap of two problems: optimally augmenting a tree to a 2-edge-connected graph and finding a minimum-cost 2-edge-connected multi-subgraph (2EC).
-We also give a simplified algorithm, DomToIP, that more quickly determines if an instance has an unbounded integrality gap.
+The upper bound on the integrality gap provided by FDT can be exponentially large.
+However our experiments demonstrate that FDT can be effective in practice.
+We study the integrality gap of two problems: optimally augmenting a tree to a 2-edge-connected graph and finding a minimum-cost 2-edge-connected multi-subgraph (2EC).
+We also give a simplified algorithm, DomToIP, that finds a feasible solution to an IP or concludes that it has unbounded integrality gap.
 We show that FDT's speed and approximation quality compare well to that of feasibility pump on moderate-sized instances of the vertex cover problem.
-For a particular set of hard-to-decompose fractional 2EC solutions, FDT always gave a better integer solution than the best previous approximation algorithm (Christofides).
+For a particular set of hard-to-decompose fractional 2EC solutions, FDT always gave a better integer solution than the Best of Many Christofides Algorithm (BOMC).
 \end{abstract}

### 2022-05-05 FDT2020/Introduction.tex
comments almost all done

@@
 The integrality gap for an IP instance is the ratio of the best integer solution to the best solution of the LP relaxation.
-Any LP-based approximation cannot have an approximation factor $C$ smaller than the integrality gap because there is no feasible solution with an objective value better than a factor of $C$ worse than the optimal solution of the LP relaxation.
+No LP-based approximation algorithm can have an approximation factor $C$ smaller than the integrality gap because there is not always a feasible solution to the IP with an objective value better than a factor of $C$ times the optimal solution of the LP relaxation.
 
@@
 Consider an instance of a combinatorial optimization problem $\mathcal{P}$.
-We can characetrize $\mathcal{P}$ by a set of feasible solutions in $S\in \mathbb{Z}_{\geq 0}^n$ and a cost function $c\in \mathbb{R}_{\geq 0}^n$.
-In many cases (see \cite{vazirani,shmoyswilliamson}) the set $S$ can decribed as a set of integer points within a polyhedron $P$ (in fact the choice of $P$ need not be unique.) In this case, the integrality gap of $\mathcal{P}$ with respect to $P$ is $\min\{cx:x\in S\}/{\min\{cx:x\in P\}}$.
-Hence $g(I)$ in Defintion \ref{IGofPoly} is equivalent to the worst-case integrality gap of all instances of a problem with respect to $P(I)$.
+We can characterize $\mathcal{P}$ by a set of feasible solutions in $S\in \mathbb{Z}_{\geq 0}^n$ and a cost function $c\in \mathbb{R}_{\geq 0}^n$.
+In many cases (see \cite{vazirani,shmoyswilliamson}) the set $S$ can described as a set of integer points within a polyhedron $P$ (in fact the choice of $P$ need not be unique.) In this case, the integrality gap of $\mathcal{P}$ with respect to $P$ is $\min\{cx:x\in S\}/{\min\{cx:x\in P\}}$.
+Hence $g(I)$ in Definition \ref{IGofPoly} is equivalent to the worst-case integrality gap of all instances of a problem with respect to $P(I)$.
 
@@
 
+Relatedly, Eisenbrand and Shmonin \cite{eisenbrand} introduced an algorithm that finds the maximum gap between the optimal values of an IP and its LP relaxation over all realizations of vector $b$ (for which the IP is feasible).
+Their algorithm runs in polynomial-time given $n$ is fixed.
+In contrast, FDT always runs in time polynomial in $n$, but obtains an upper bound on the integrality gap as opposed to an exact value.
+
 \subsection{Algorithms and Theory Contributions}
@@
 
-One can extend the FDT algorithm for binary IPs into covering\footnote{A covering IP has nonnegative constraint matrix, objective coefficients and right-hand side ($A,b,c$).} $\{0,1,2\}$ IPs by losing a factor $2^{|\spp(x)|}$ on top of the loss for FDT.
+One can extend the FDT algorithm for binary IPs into covering\footnote{A covering IP has nonnegative constraint matrix, objective coefficients and right-hand side ($A,b,c$).} $\{0,1,2\}$ IPs by losing a factor $2$ on top of the loss for FDT.
 To eradicate this extra factor, we must treat the coordinate $i$ with $x_i=1$ differently.

### 2022-05-05 FDT2020/main-section.tex
comments almost all done

@@
 \begin{proof}	
-	Consider the following linear program which we denote by $\LPC(\ell,x')$. The variables of $\LPC(\ell,x')$ are $\lambda_0$, $\lambda_1$, $x^0$ and $x^1$.
+	Consider the following linear program which we denote by $\LPC(\ell,x')$. The variables of $\LPC(\ell,x')$ are scalars $\lambda_0$, $\lambda_1$, and vectors $x^0$ and $x^1$.
 % \cindy{I think you mean that the $\lambda$s are variables, not $\gamma$s.
@@
 	$\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.$ 
-	Therefore (v) holds.
+	Therefore (iv) holds.
 \end{proof}
@@
 \begin{proof}
-	Consider the following LP with variables $\lambda_j$ and $x^j$ for $j=0,1,2$. 
+	Consider the following LP with $\lambda_j$ and $x^j\in \mathbb{R}^E$ for $j=0,1,2$. 
 	\begin{align}
@@
 %\arash{it's all correct, I'm running the experiments again to get the running time so these numbers might change.}
-\paragraph{Computational comparison between Christofides' algorithm and FDT for 2EC on Carr-Vempala points.}
+\paragraph{Computational comparison between BOMC and FDT for 2EC on Carr-Vempala points.}
 
@@
 So in that sense, these are the hardest fractional points to round to a feasible solution.
-We now compare the quality of FDT's solution from a Carr-Vempala point to that of Christofides, the best known approximation algorithm\footnote{Recently, \cite{KKO} improved over Christofides algorithm by a small factor.}.
+We now compare the quality of FDT's solution from a Carr-Vempala point to BOMC.
+BOMC (and simply Christofides) provide the best known upper bound on $g(\2ec)$\footnote{Recently, \cite{KKO} improved over Christofides algorithm by a small factor.}.
 Let us remind our reader the Christofides algorithm for TSP: given a graph with edge costs find a minimum spanning tree of the graph.

### 2022-05-05 FDT2020/response/response.tex
responses updated

@@
 \documentclass[11pt,epsf]{article}
+
 %\documentstyle[12pt,psfig,draft]{article}
@@
 \section{General Response}
-\response{We thank the editor and reviewers for their insighful and constructive comments. 
-}
+\response{We thank the editor and reviewers for their insightful and constructive comments. }
 
+\arash{TODO: Thank the reviewers at length. Apologies for the delay in submission for the revisions, thanks the editor for the extensions.}
 \section{Detailed Responses}
 
-\subsection{Reviewer \#1}
+\subsection{Reviewer 1}
+\subsubsection{Major Comments}
+\response{We have addressed the issue in the proof of Theorem 3 as detailed below.
+We also made several major revision in our presentation specially with regards to the more technical parts of the paper.}
+\subsubsection{Minor Comments}
 \begin{itemize}
@@
 that the flow is more logical.
+\response{We agree that the introduction is a little bit lengthy and not direct.
+However, we wanted to make sure that the reader is familiar with our terminology before diving into the results presentation.
+
+That being said, we have made some changes in the introduction. We hope the new state of the introduction is satisfactory.}
 
@@
 This makes the paragraph rather awkward to read, because the statements are not correct as stated.
+\response{We made various changes starting from the paragraph before Definition 1 and the discussion that follows, drawing the comparison between different objects that a gap can be defined on and where Definition 1 stands.
+Our definition is integrality gap of a polyhedron.}
 
@@
 \item p. 3: Is there a reason why you choose to not include the coefficients of the objective function in an instance?
-\response{Not final! We choose this definition because it allows us to talk about instance specific integrality gaps (or integrality gap in the special cases).}
+\response{Added this sentence: The reason that we define integrality gap for a polyhedron as opposed to an instance of a problem is that our algorithms are independent of the cost function $c$. }
 
@@
 vital importance when using Carr-Vempala).
+
+\response{As stated above, the discussion following Definition 1. We added a remark that $c$ need to be non-negative for Carr-Vempala to works.}
+
 \item p. 4, equation (4): supremum instead of maximum
@@
 \item p. 24 and following, references: missing capitalization in a few entries
+\response{We fixed many instances of missing capitalization.}
 
@@
 
-We respectfully disagree about the comment for 2EC since we use BOMC and turn it into an instance specific rounding algorithm for subtour elimination points.
+With respect to Christofides, we mistakenly mentioned comparing FDT with Christofides but we in fact compare FDT with BOMC (Best of Many Christofides) - this has been fixed in the abstract and the paper.
 As presented in Figure 3, we don't settle for the worst-case upper bound of 3/2.
@@
 \item The abstract is misleading in multiple ways.
-First, it says that the paper will give a constructive version of the Carr-Vempala theorem but does not mention the rather large loss in quality of g to (potentially) g n .
+First, it says that the paper will give a constructive version of the Carr-Vempala theorem but does not mention the rather large loss in quality of $g$ to (potentially) $g^n$ .
 Secondly,
@@
 which is what is compared in the paper.
+
+\response{We made several fixed in the abstract that addressed all the points mentioned above.}
 \item The paper should mention the randomized metarounding algorithm by Carr and Vempala and compare it to the FDT algorithm. 
+\response{Added this paragraph right before section 1.1: 
+Carr and Vempala [CV00] showed if there an algorithm $\mathcal{A}$ that for $I\in \mathcal{I}$ and $c\geq 0$ finds $z\in S(I)$ with $cz\leq g'cx$ for any $x\in P(I)$, then $g'x$ can be \textbf{write} as a convex combination of points in $S(I)$.
+However, for many known problems there is a gap between the best known $g'$ and $g(\mathcal{I})$.
+}
 \item In the proofs of Lemma 8 and Lemma 11, I do not see why it can be assumed that $\lambda_0,\lambda_1,\lambda_2>0$. I think one has to allow the case in which
@@
 general purpose feasibility heuristic, then comparing to a FDT to a more modern variant of FP (e.g. as in the Feasibility Pump 2.0 paper) would be more reasonable.
+
+\response{The comparisons with FP are not presented to claim that FDT to provide direct comparisons between the two algorithms, but to provide a baseline on the IG upper bounds provided by another LP-based algorithm.
+We want to emphasize that the scope of this work in mostly on the theoretical contributions, rather than experimental results.}
 
@@
 \subsubsection{Main Comments}
+\begin{itemize}
+\item
+Is your definition of integrality gap used elsewhere?
+If not, try to use a different word - maybe something like “objective-oblivious integrality gap”?
+The point is to make it clear that yes, this is something like integrality gap, but it does NOT match anything the reader has seen before.
+\response{We agree that using a different term will provide much better clarity for future readers.
+We now call our version the ``integrality gap of a polyhedron'' (IGP)} \cindy{TODO: update this if we change it.}
+
+\arash{I actually don't agree with the reviewer here.
+They are saying that in their opinion for integrality gap you keep $c$ constant and take $\max$ over instances.
+This does not make sense to me.
+Because $c$ itself is dependent on the instance.
+}
+
+\arash{Let's look at Definition 5.13 in SW book: The integrality gap of an integer program is the worst-case ratio over all instances of the problem of value of an optimal solution to the integer programming formulation to value of an optimal solution to its linear programming relaxation.
+So this is $\max_c \frac{cx:Ax\leq b, x\in \mathbb{Z}^n}{cx:Ax\leq b, x\in \mathbb{R}^n}$, which is inline with Definition 1.}
+\cindy{Does the SW book actually give that math-based definition, where the max is only over c?
+I don't have a copy and I don't see a SW book in our reference list right now.
+Or is that math your interpretation?
+As I said to Bob in a phone call, for a given combinatorial optimization problem, A,b, and c can change from instance to instance.
+For some problems, c is fixed (e.g.
+all 1).
+But any problem that allows weighting of the combinatorial objects could have changes anywhere (perhaps we could add examples of that, because this reviewer is really concerned about this).
+If the SW book has this definition, then we should include a citation to that book when we define what we mean by integrality gap.
+We should probably also include the papers that this reviewer gave us.
+We (and SW if the math is as above) are still considering the integrality gap when the polyhedron is fixed, which is not over all instances of a problem in general.
+If the papers this reviewer cited consider everything fixed but b, that is also a restriction.
+That is ours and theirs are still a subset of the ``normal'' definition.
+I still think it will help reduce confusion if we call ours something more restrictive.
+Is that OK?}
+\arash{The definition in SW is just in words. There are two ways to read SW: 1. the instances of an IP over $A,b,c$, 2. the instances of an IP over all $c$.}
+\arash{To me the second one makes so much more sense: since integrality gap can only be defined with respect to a formulation - so if you change the formulation you expect the integraltiy gap to change.
+Reviewer \#3's definition is not like that: consider matching: the formulation with only degree constraints has gap infinity, but formulation with degree constraints and odd set constraints has gap $1$.
+While in definition of integrality gap of reviewer \#3 you can say that the gap is changing.}
+\arash{I do agree we should cite what the reviewer suggested, but not sure where it fits.}
+\cindy{I agree that the integrality gap depends on the formulation.
+I think of a formulation the way they appear in technical papers.
+There are parameters and variables, an objective function and then families of constraints.
+The form of the objective and constraints is the formulation.
+But the values of a particular set of parameters, which includes things like graph topology for graph-based problems, identifies a specific instance.
+This supports what you call definition 1 from WS.
+This is why I suggested we spend a little time somewhere in the paper discussing problem formulations that fix c or fix A or fix b, or fix none of them, etc.
+Given the (definition 1) form, which comes from a mathematical formulation, researchers can prove an upper bound (for min problems) of $alpha$ (a constant or a function of the input size) by finding an algorithm that ``rounds'' an optimal LP solution to a feasible integer solution and proves the objective of that solution is no more than $\alpha$ times the optimal LP value.
+One can prove a lower bound of $\beta$ on the integrality gap for that formulation by finding an instance, or a family of instances, where the integrality gap is at least $\beta$.
+It's useful to prove large lower bounds, because it shows one has to add more constraints to get a good LP-based approximation algorithm for that problem.
+This paper gives a computational/experimental way to prove a lower bound on the integrality gap for a problem.
+It's reasonable to fix some parts of the formulation for experiments.
+For this paper, the polyhedron is fixed for a given test.
+It's convenient that WS include the same restriction.
+I pulled a copy of the book.
+I will try to look at the context of that definition and see why they give it that way.
+Wherever we have this discussion is where we should include the references that Reviewer 3 gave to us.
+I thought we had included a lot of the logic I just added, but perhaps not, or not clearly.}
+
+\response{
+We added this explanation after Definition 1:
+
+Consider an instance of a combinatorial optimization problem $\mathcal{P}$.
+We can characterize $\mathcal{P}$ by a set of feasible solutions in $S\in \mathbb{Z}_{\geq 0}^n$ and a cost function $c\in \mathbb{R}_{\geq 0}^n$.
+In many cases (see [VZ,SW]) the set $S$ can described as a set of integer points within a polyhedron $P$ (in fact the choice of $P$ need not be unique.) In this case, the integrality gap of $\mathcal{P}$ with respect to $P$ is $\min\{cx:x\in S\}/{\min\{cx:x\in P\}}$.
+Hence $g(I)$ in Definition 1 is equivalent to the worst-case integrality gap of all instances of a problem with respect to $P(I)$.
+
+The reason that we define integrality gap for a polyhedron as opposed to an instance of a problem is that our algorithms are independent of the cost function $c$.
+
+}
+Relatedly, Eisenbrand and Shmonin \cite{eisenbrand} introduced an algorithm that finds the maximum gap between the optimal values of an IP and its LP relaxation over all realizations of vector $b$ (for which the IP is feasible).
+Their algorithm runs in polynomial-time given $n$ is fixed.
+In contrast, FDT always runs in time polynomial in $n$, but obtains an upper bound on the integrality gap as opposed to an exact value.
+\item
+Mention the existing work on integrality gaps and compare your results to it.
+\response{Added a pointer to Carr Vemapala Meta-rounding and  Eisenbrand and Shmonin Fixed Dimension work right before section 1.1.
+and motioned how it isn related to our work.
+Thank you for this pointer.}
+\item
+Mention known work on obtaining integer feasible solutions.
+Is FDT the first algorithm which constructs a feasible solution if the instance has finite integrality gap?
+For which definitions of integrality gap can this be done in polynomial time, and with what quality of the resulting solution (wrt the integrality gap)?
+\response{See above.}
+\item
+Explain why FDT cannot be used to obtain a feasible solution attaining g(I, c) – is it because despite g(I, c) being finite, g(I) is infinite?
+or would FDT find some solution, but of worse value because g(I) is much larger than g(I,c), or can both scenarios happen?
+
+\response{Thank you for pointing this out.
+We added a short discussion right after Theorem 5 to discuss the issue in a (slightly) different way:  A keen reader might ask why Theorem 5 does not imply that P = NP, as one iteratively find a feasible solution $x^*\in S(I)$, and add the constraint $x\leq cx^*-\epsilon$ for some small enough $\epsilon>0$ to $I$ until DomToIP fails to find a feasible solution.
+However, note that adding constraints to $I$ might result in $g(I)$ becoming infinite, in which case DomToIP would fail to find a feasible solution to the IP.
+}
+\end{itemize}
 
@@
 fact. 
-\response{MIPLIB citation added and the wording is changed as suggested.}
+\response{MIPLIB citation added and the wording is changed as suggested.}\cindy{I actually did mean that we, researchers at Sandia National Laboratories, have formulated problems that these solvers cannot solve.
+This is because our problems are from national security, and don't always look like the kinds of problem that industry or academia solve.
+These problems are not published.
+One doesn't generally publish MIP formulations that don't solve (negative results are not interesting unless accompanied by positive results, or for famous open problems).
+We can add that to the response, but stick to MIPLIB in the paper if you like.
+However, {\bf Question}: Did you check the status of MIPLIB?
+How many moderate-size problems are not solvable by commercial solvers?
+Do you have to go to more recent updates of MIPLIB, like MIPLIB 2010 and probably even more recent to find unsolved problems and are they still moderate-sized?}
 
-\item (2,14) “the” -> “these”?
+\item (2,14) “the” $\rightarrow$ “these”?
+\response{Fixed.}
 \item (2,26) “from the problem” – what problem? Maybe “using special problem structure together with the result of an LP relaxation to obtain an integer feasible solution
@@
 constraint matrix) does not lead to the same or better result. Or maybe it does?
-\response{We added this paragraph in the discussion of why $\{0,1,2\}$ problems are different from binary problems: Another approach to a $\{0,1,2\}$ problem could be to ``binarize'' the variables, but splitting each variable into two binary copies and solving the binary problem via FDT for binary IPs (Theorem \ref{FDTFull}).
+\response{We added this paragraph in the discussion of why $\{0,1,2\}$ problems are different from binary problems: Another approach to a $\{0,1,2\}$ problem could be to ``binarize'' the variables, but splitting each variable into two binary copies and solving the binary problem via FDT for binary IPs (Theorem 4).
 One potential issue that can arise by doing this is that the binary version of a problem might have a larger integrality gap compared to the one that allows larger multiplicity.
@@
 the reason why you study random instances. (It is not good practise in experimental
-algorithmics to study random instances unless necessary.)
+algorithmics to study random instances unless necessary.) \response{Unfortunately we couldn't find any benchmark database of instances for TAP.
+We can remove this experiment for the paper (or move it to an appendix).}
 \item (20,22) One idea to consider and comment on: did you warm-start each computation of FDT? It seems to me that you could reuse the model that FDT solves in each
@@
 e.g. https://arxiv.org/abs/1911.08636
+
+\response{Thank you for the great suggestion.
+We added a comment related to this in the conclusion.
+Even-though this seems like a great suggestion we think trying this in our experiments would fall beyond the mostly theoretical scope of this work.}
+
 \item (21,10) Christofides’ algorithm is no longer the fastest https://arxiv.org/abs/2007.01409

### 2022-05-05 FDT2020/Introduction.tex
Minor edits

@@
 We can characterize $\mathcal{P}$ by a set of feasible solutions in $S\in \mathbb{Z}_{\geq 0}^n$ and a cost function $c\in \mathbb{R}_{\geq 0}^n$.
-In many cases (see \cite{vazirani,shmoyswilliamson}) the set $S$ can described as a set of integer points within a polyhedron $P$ (in fact the choice of $P$ need not be unique.) In this case, the integrality gap of $\mathcal{P}$ with respect to $P$ is $\min\{cx:x\in S\}/{\min\{cx:x\in P\}}$.
+In many cases (see \cite{vazirani,shmoyswilliamson}) the set $S$ is a set of integer points within a polyhedron $P$ (in fact the choice of $P$ need not be unique.) In this case, the integrality gap of problem $\mathcal{P}$ with respect to polyhedron $P$ is $\min\{cx:x\in S\}/{\min\{cx:x\in P\}}$.
 Hence $g(I)$ in Definition \ref{IGofPoly} is equivalent to the worst-case integrality gap of all instances of a problem with respect to $P(I)$.

### 2022-05-05 FDT2020/FDT.tex
arxiv version
Mostly updates to the introduction, removal of comments, suggestion for a conclusion
added conclusion section
chris vs FDT plot updated (leneged out of the plot now)
affiliation fixed
unified Subtour elimination and multi-graph notation
draft before submission
Edits

@@
 \onehalfspacing
+% CAP: adding this for R&A (no date)
+\date{}
 
@@
 We present a new algorithm, Fractional Decomposition Tree (FDT) for finding a feasible solution for an integer program (IP) where all variables are binary.
-FDT runs in polynomial time and is guaranteed to find a feasible integer solution provided the integrality gap is bounded.
+FDT runs in polynomial time and is guaranteed to find a feasible integer solution provided the integrality gap of an instance's polyhedron, independent of objective function, is bounded.
 The algorithm gives a construction for Carr and Vempala's theorem that any feasible solution to the IP's linear-programming relaxation, when scaled by the instance integrality gap, dominates a convex combination of feasible solutions.
 FDT is also a tool for studying the integrality gap of IP formulations.
-We demonstrate that with experiments studying the integrality gap of two problems: optimally augmenting a tree to a 2-edge-connected graph and finding a minimum-cost 2-edge-connected multi-subgraph (2EC).
+We demonstrate this with experiments studying the integrality gap of two problems: optimally augmenting a tree to a 2-edge-connected graph and finding a minimum-cost 2-edge-connected multi-subgraph (2EC).
 We also give a simplified algorithm, Dom2IP, that more quickly determines if an instance has an unbounded integrality gap.

### 2022-05-05 FDT2020/Introduction.tex
Edits

--- 2022-05-05 FDT2020/Introduction.tex
@@
 
-Consider an instance of a combinatorial optimization problem $\mathcal{P}$.
-We can characterize $\mathcal{P}$ by a set of feasible solutions in $S\in \mathbb{Z}_{\geq 0}^n$ and a cost function $c\in \mathbb{R}_{\geq 0}^n$.
-In many cases (see \cite{vazirani,shmoyswilliamson}) the set $S$ can described as a set of integer points within a polyhedron $P$ (in fact the choice of $P$ need not be unique.) In this case, the integrality gap of $\mathcal{P}$ with respect to $P$ is $\min\{cx:x\in S\}/{\min\{cx:x\in P\}}$.
+Consider an instance of a combinatorial optimization problem $\mathcal{P}$ given by a set of feasible solutions in $S\in \mathbb{Z}_{\geq 0}^n$ and a cost function $c\in \mathbb{R}_{\geq 0}^n$.
+In many cases (see \cite{vazirani,shmoyswilliamson}), $S$ is a set of integer points within a polyhedron $P$, where the choice of $P$ need not be unique.
+In this case, the integrality gap of problem $\mathcal{P}$ with respect to polyhedron $P$ is $\min\{cx:x\in S\}/{\min\{cx:x\in P\}}$.
 Hence $g(I)$ in Definition \ref{IGofPoly} is equivalent to the worst-case integrality gap of all instances of a problem with respect to $P(I)$.

### 2022-05-05 FDT2020/FDT.tex
Changing Christofides to Best-of-Many Christofides in the abstract

@@
 We show that FDT's speed and approximation quality compare well to that of feasibility pump on moderate-sized instances of the vertex cover problem.
-For a particular set of hard-to-decompose fractional 2EC solutions, FDT always gave a better integer solution than the best previous approximation algorithm (Christofides).
+For a particular set of hard-to-decompose fractional 2EC solutions, FDT always gave a better integer solution than the best previous approximation algorithm (Best-of-Many Christofides).
 \end{abstract}

### 2022-05-05 FDT2020/FDT_revised.tex
Revisions to the abstract

@@
 
-We present a new algorithm, Fractional Decomposition Tree (FDT) for finding a feasible solution for an integer program (IP) where all variables are binary.
-FDT runs in polynomial time and is guaranteed to find a feasible integer solution provided the integrality gap is bounded.
+We present a new algorithm, Fractional Decomposition Tree (FDT), for finding a feasible solution for an integer program (IP) where all variables are binary.
+FDT runs in polynomial time and is guaranteed to find a feasible integer solution provided the integrality gap of an instance's polyhedron, independent of objective function, is bounded.
 The algorithm gives a construction for Carr and Vempala's theorem that any feasible solution to the IP's linear-programming relaxation, when scaled by the instance integrality gap, dominates a convex combination of feasible solutions.
 FDT is also a tool for studying the integrality gap of IP formulations.
-The upper bound on the integrality gap provided by FDT can be exponentially large.
+The upper bound on the integrality gap of an FDT solution can be exponentially large.
 However our experiments demonstrate that FDT can be effective in practice.
@@
 We also give a simplified algorithm, DomToIP, that finds a feasible solution to an IP or concludes that it has unbounded integrality gap.
-We show that FDT's speed and approximation quality compare well to that of feasibility pump on moderate-sized instances of the vertex cover problem.
-For a particular set of hard-to-decompose fractional 2EC solutions, FDT always gave a better integer solution than the Best of Many Christofides Algorithm (BOMC).
+We show that FDT's speed and approximation quality compare well to that of the original feasibility pump heuristic on moderate-sized instances of the vertex cover problem.
+For a particular set of hard-to-decompose fractional 2EC solutions, FDT always gave a better integer solution than the Best-of-Many Christofides Algorithm (BOMC).
 \end{abstract}

### 2022-05-05 FDT2020/Introduction.tex
Some edits around non-negativity of c, typo fixes, etc.

@@
 The reason that we define integrality gap for a polyhedron as opposed to an instance of a problem is that our algorithms are independent of the cost function $c$.
+We do, however, require the cost function $c$ to be non-negative since that is required to use the Carr-Vempala theorem, as described below.
 
@@
 \begin{thm}[Carr, Vempala \cite{Carr2004}] \label{CV2}
-	We have $g(I) \leq C$ if and only if for $x\in P(I)$ the vector $Cx$ can be is as a convex combination of points in $\dom(S(I))$. 
+	We have $g(I) \leq C$ if and only if for $x\in P(I)$ the vector $Cx$ can be expressed as a convex combination of points in $\dom(S(I))$. 
 \end{thm}
 Goemans \cite{goemansblocking} first introduced Theorem \ref{CV2} for blocking-type polyhedra.
-While there is an exact algorithm for problems with gap $1$, as stated in Proposition \ref{cara}, Theorem~\ref{CV2} is existential, with no construction.
-We remark that Proposition \label{CV2} would not work if we drop the non-negatvitiy constraints on the cost function $c$ in the definition of integrality gap (Defitinon \ref{IGofPoly}).
+While there is an exact algorithm for problems with gap $1$, as stated in Proposition~\ref{cara}, Theorem~\ref{CV2} is existential, with no construction.
+Proposition~\label{cara} would not work if we drop the non-negativity constraints on the cost function $c$ in the definition of integrality gap (Definition~\ref{IGofPoly}).
 %In contrast to Proposition \ref{cara} which implies exact algorithms for problems with a gap of 1, Theorem \ref{CV} does not imply an approximation algorithm, since it does not suggest how to find such a convex combination in polynomial time.
@@
 
-Carr and Vempala \cite{metarounding} showed if there an algorithm $\mathcal{A}$ that for $I\in \mathcal{I}$ and $c\geq 0$ finds $z\in S(I)$ with $cz\leq g'cx$ for any $x\in P(I)$, then $g'x$ can be \textbf{write} as a convex combination of points in $S(I)$.
+Carr and Vempala \cite{metarounding} showed if there an algorithm $\mathcal{A}$ that for $I\in \mathcal{I}$ and $c\geq 0$ finds $z\in S(I)$ with $cz\leq g'cx$ for any $x\in P(I)$, then $g'x$ can be written as a convex combination of points in $S(I)$.
 However, for many known problems there is a gap between the best known $g'$ and $g(\mathcal{I})$.

### 2022-05-05 FDT2020/conclusion.tex
comments almost all done
Added some disclaimers, etc, to the first paragraph of the experimental section

@@
 Our experiments in Section~\ref{sec:experiment} give a proof of concept.
-They show that its plausible FDT will have practical benefit as an IP heuristic for problems with appropriate structure.
+They show that it's plausible FDT will have practical benefit as an IP heuristic for problems with appropriate structure.
 FDT performance will likely improve in a future more high-performance version coded in C or C++, perhaps able to take advantage of the low-level parallelism available on all modern platforms (even laptops).
@@
 Any consistent structure of such instances could lead to proofs of better approximation bounds.
+Furthermore, in FDT we solve somewhat similar LPs iteratively.
+Hence, the running time of the algorithm can benefit from warm-starting the solver for the LPC problem (see \cite{warmstart} for a successful application of this approach.)
 

### 2022-05-05 FDT2020/main-section.tex
Added some disclaimers, etc, to the first paragraph of the experimental section

@@
 We ran FDT on three network design problems: VC, TAP and 2EC.
+These experiments, especially those for 2EC, illustrate possible uses of FDT to study the integrality gap of a problem.
+We also compare FDT the original feasibility pump algorithm~\cite{fp1}\footnote{We coud not find code for feasibility pump 2.0~\cite{fp2}.} or problem-specific approximation algorithms.
+Our intent is to show that FDT's performance in practice is far better than the provable bound on integrality gap and the run time is reasonable.
+We are not recommending FDT as a replacement for other general heuristics, but it may have a place in a suite of heuristics for some problems.
 
@@
 We now compare the quality of FDT's solution from a Carr-Vempala point to BOMC.
-BOMC (and simply Christofides) provide the best known upper bound on $g(\2ec)$\footnote{Recently, \cite{KKO} improved over Christofides algorithm by a small factor.}.
+BOMC (and simply Christofides) provide the best known upper bound on $g(\2ec)$\footnote{Recently, \cite{KKO} gave an approximation algorithm that improves upon Christofides' bound by a small factor.}.
 Let us remind our reader the Christofides algorithm for TSP: given a graph with edge costs find a minimum spanning tree of the graph.

### 2022-05-05 FDT2020/Introduction.tex
small edits

@@
 
-Carr and Vempala \cite{metarounding} showed if there an algorithm $\mathcal{A}$ that for $I\in \mathcal{I}$ and $c\geq 0$ finds $z\in S(I)$ with $cz\leq g'cx$ for any $x\in P(I)$, then $g'x$ can be written as a convex combination of points in $S(I)$.
+Carr and Vempala \cite{metarounding} showed if there is an algorithm $\mathcal{A}$ that for $I\in \mathcal{I}$ and $c\geq 0$ finds $z\in S(I)$ with $cz\leq g'cx$ for any $x\in P(I)$, then $g'x$ can be written as a convex combination of points in $S(I)$.
 However, for many known problems there is a gap between the best known $g'$ and $g(\mathcal{I})$.

### 2022-05-05 FDT2020/main-section.tex
small edits

@@
 We ran FDT on three network design problems: VC, TAP and 2EC.
-These experiments, especially those for 2EC, illustrate possible uses of FDT to study the integrality gap of a problem.
-We also compare FDT the original feasibility pump algorithm~\cite{fp1}\footnote{We coud not find code for feasibility pump 2.0~\cite{fp2}.} or problem-specific approximation algorithms.
+These experiments, especially those for 2EC, demonstrate using FDT to study the integrality gap of a problem.
+We also compare FDT to the original feasibility pump algorithm~\cite{fp1}\footnote{We could not find code for feasibility pump 2.0~\cite{fp2}.} or problem-specific approximation algorithms.
 Our intent is to show that FDT's performance in practice is far better than the provable bound on integrality gap and the run time is reasonable.
-We are not recommending FDT as a replacement for other general heuristics, but it may have a place in a suite of heuristics for some problems.
+We are not recommending FDT as a replacement for other general heuristics, but for some problems, it may have a place in a suite of heuristics.
 

### 2022-05-05 FDT2020/Introduction.tex
typo fix

@@
 Known polyhedral structure makes it easier to study integrality gaps for such problems.
-In particular, for the subtour-elimination relaxation \cite{carrravi,boydcarr,Carr2004} introduced fundamental extreme points that create the ``hardest'' LP solutions to decompose.
+In particular, for the subtour-elimination relaxation, \cite{carrravi,boydcarr,Carr2004} introduced fundamental extreme points that create the ``hardest'' LP solutions to decompose.
 

### 2022-05-05 FDT2020/Introduction.tex
Comments from Bob

@@
 Let $I_G$ be the polyhedron instance defined by $\subtour(G)$.
-Then $g(I_G)$ is the worst-case integrality gap 2EC on $G$ over all non-negative cost functions and integrality gap of 2EC is $\sup_{G} g(I_G)$.
+Then $g(I_G)$ is the worst-case integrality gap of 2EC on $G$ over all non-negative cost functions and the integrality gap of 2EC is $\sup_{G} g(I_G)$.
 
@@
 
-Formally, for some positive integer $k$, given a set of points $S\subseteq \mathbb{R}^k$ and a vector $x\in \mathbb{R}^k$, we say \textit{$x$ \underline{is} as a convex combination of points in $S$} if there exists a positive integer $\ell$ and $\theta \in [0,1]^\ell$, where $\sum_{i=1}^{\ell}\theta_i =1$ and $\tilde{x}^i\in S$ for $i\in [k]$ such that $\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq x$.
+Formally, for some positive integer $k$, given a set of points $S\subseteq \mathbb{R}^k$ and a vector $x\in \mathbb{R}^k$, we say \textit{$x$ \underline{is/dominates} a convex combination of points in $S$} if there exists a positive integer $\ell$ and $\theta \in [0,1]^\ell$, where $\sum_{i=1}^{\ell}\theta_i =1$ and $\tilde{x}^i\in S$ for $i\in [\ell]$ such that $\sum_{i=1}^{\ell}\theta_i \tilde{x}^i\leq x$.
 If such a convex combination can be found in time polynomial in the encoding size of the definition of $S$ and $x$, then we say  \textit{$x$ \underline{can be written} as a convex combination of points in $S$}
@@
 \begin{thm}[Carr, Vempala \cite{Carr2004}] \label{CV2}
-	We have $g(I) \leq C$ if and only if for $x\in P(I)$ the vector $Cx$ can be expressed as a convex combination of points in $\dom(S(I))$. 
+	We have $g(I) \leq C$ if and only if for $x\in P(I)$ the vector $Cx$ dominates a convex combination of points in $\dom(S(I))$. 
 \end{thm}
 Goemans \cite{goemansblocking} first introduced Theorem \ref{CV2} for blocking-type polyhedra.
-While there is an exact algorithm for problems with gap $1$, as stated in Proposition~\ref{cara}, Theorem~\ref{CV2} is existential, with no construction.
+While there is an exact algorithm for problems with gap $1$, as stated in Theorem~\ref{CV2} is existential, with no construction.
 Proposition~\label{cara} would not work if we drop the non-negativity constraints on the cost function $c$ in the definition of integrality gap (Definition~\ref{IGofPoly}).
@@
 
-In Section~\ref{sec:binaryfdt} we introduce the \textit{Fractional Decomposition Tree} (FDT) which is polynomial time algorithm.
+In Section~\ref{sec:binaryfdt} we introduce the \textit{Fractional Decomposition Tree} (FDT) which is a polynomial time algorithm.
 Given a point $x\in P(I)$ FDT produces a convex combination of feasible points in $S(I)$ that are dominated coordinatewise by a ``factor" $C$ times $x$.
@@
 	\label{binaryFDT}
-	Assume $g(I) 	<\infty$. For $x^*\in P(I)$, using 	the Fractional Decomposition Tree (FDT) algorithm we can write $x$ as a convex combination of points in $S(I)$, where $C\leq g(I)^{|\spp(x^*)|}$.
+	Assume $g(I) 	<\infty$. For $x^*\in P(I)$, using 	the Fractional Decomposition Tree (FDT) algorithm we can write $Cx^*$ as a convex combination of points in $S(I)$, where $C\leq g(I)^{|\spp(x^*)|}$.
 \end{restatable}
@@
 
-A keen reader might ask why Theorem \ref{domtoIP} does not imply that P = NP, as one iteratively find a feasible solution $x^*\in S(I)$, and add the constraint $x\leq cx^*-\epsilon$ for some small enough $\epsilon>0$ to $I$ until DomToIP fails to find a feasible solution.
+A keen reader might ask why Theorem \ref{domtoIP} does not imply that P = NP, as one iteratively find a feasible solution $x^*\in S(I)$, and add the constraint $cx\leq cx^*-\epsilon$ for some small enough $\epsilon>0$ to $I$ until DomToIP fails to find a feasible solution.
 However, note that adding constraints to $I$ might result in $g(I)$ becoming infinite, in which case DomToIP would fail to find a feasible solution to the IP.
@@
 Let $y$ be a vector in this convex combination from iteration $i-1$.
-In iteration $i$, we solve a linear-programming problem that gives us $\gamma_0,\gamma_1\in [0,1]$ and $y^0,y^1\in \mathcal{D}(P(I))$ such that $y\geq \gamma_0 y^0 + \gamma_1 y^1$, $\gamma_0+\\gamma_1\leq g(I)$, $y^0_i=0$ and $y^1_i=1$.
+In iteration $i$, we solve a linear-programming problem that gives us $\gamma_0,\gamma_1\in [0,1]$ and $y^0,y^1\in \mathcal{D}(P(I))$ such that $y\geq \gamma_0 y^0 + \gamma_1 y^1$, $\gamma_0+\gamma_1\leq g(I)$, $y^0_i=0$ and $y^1_i=1$.
 We then replace $y$ in the convex combination with $\frac{\gamma_0}{\gamma_0+\gamma_1}y^0 +\frac{\gamma_1}{\gamma_0+\gamma_1}y^1$.
@@
 
-One can extend the FDT algorithm for binary IPs into covering\footnote{A covering IP has nonnegative constraint matrix, objective coefficients and right-hand side ($A,b,c$).} $\{0,1,2\}$ IPs by losing a factor $2$ on top of the loss for FDT.
+One can extend the FDT algorithm for binary IPs into covering\footnote{A covering IP has nonnegative constraint matrix, right-hand side and objective coefficients ($A,b,c$).} $\{0,1,2\}$ IPs by losing a factor $2$ on top of the loss for FDT.
 To eradicate this extra factor, we must treat the coordinate $i$ with $x_i=1$ differently.
@@
 %(or a \{0,1,2\} IP) 
-as a convex combination of feasible solutions, provided the IP integrality gap is bounded.  This is the Fractional Decomposition Tree (FDT) algorithm.
+as a convex combination of feasible solutions, provided the IP integrality gap is bounded, when scaled by a factor depending on the integrality gap of the IP formulation.
+This is the Fractional Decomposition Tree (FDT) algorithm.
 \item We give a simple  algorithm to give a feasible solution for any binary IP with bounded integrality gap. If this algorithm fails, then the integrality gap is infinite.
@@
 \item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for integrality gap for 2EC for these instances.
-\item We demonstrate (with 2EC) how FDT exeriments can support theoretical work on integrality gaps for specific problems.
+\item We demonstrate (with 2EC) how FDT experiments can support theoretical work on integrality gaps for specific problems.
 In particular, we computationally prove an upper bound on small instances of 2EC with a specific structure.

### 2022-05-05 FDT2020/main-section.tex
Comments from Bob

@@
 For simplicity in the notation we assume an instance $I$ and denote $P(I),S(I),$ and $g(I)$ by $P$, $S$, and $g$ for this section and the next section.
-Also, for both sections let $x^*$ be the optimal solution to the LP formulation and assume $t=|\spp(x^*)|$.
+Also, for both sections let $x^*$ be the optimal solution to the LP relaxation and assume $t=|\spp(x^*)|$.
 Reorder variables as necessary to put all the nonzero variables into the first $t$ indices.
@@
 \begin{observation}\label{dom01}
-Any point $x\in [0,1]^n$ that is a convex combination of points in $\dom(S)$, is also a convex combination of points in $\dom(S) \cap [0,1]^n$
+Any point $z\in [0,1]^n$ that is a convex combination of points in $\dom(S)$, is also a convex combination of points in $\dom(S) \cap [0,1]^n$
 \end{observation}

### 2022-05-05 FDT2020/Introduction.tex
Rearragement of first contribution

@@
 \begin{itemize}
-\item We give an algorithm to express any feasible point for the LP relaxation of a binary IP
+\item We give an algorithm to express any feasible point for the LP relaxation of a binary IP, when scaled by a factor depending on the integrality gap of the IP formulation, 
 %(or a \{0,1,2\} IP) 
-as a convex combination of feasible solutions, provided the IP integrality gap is bounded, when scaled by a factor depending on the integrality gap of the IP formulation.
-This is the Fractional Decomposition Tree (FDT) algorithm.
+as a convex combination of feasible solutions, provided the IP integrality gap is bounded.  This is the Fractional Decomposition Tree (FDT) algorithm.
 \item We give a simple  algorithm to give a feasible solution for any binary IP with bounded integrality gap. If this algorithm fails, then the integrality gap is infinite.

### 2022-05-05 FDT2020/Introduction.tex
typo

@@
 \item We experimentally show that FDT can give good approximate solutions to small instances of vertex-cover and tree augmentation problems.
-\item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for integrality gap for 2EC for these instances.
+\item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for the integrality gap for 2EC for these instances.
 \item We demonstrate (with 2EC) how FDT experiments can support theoretical work on integrality gaps for specific problems.

### 2022-05-05 FDT2020/Introduction.tex
added a word

--- 2022-05-05 FDT2020/Introduction.tex
@@
 \item We experimentally show that FDT can give good approximate solutions to small instances of vertex-cover and tree augmentation problems.
-\item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for integrality gap for 2EC for these instances.
+\item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for the integrality gap for 2EC for these challenging instances.
 \item We demonstrate (with 2EC) how FDT experiments can support theoretical work on integrality gaps for specific problems.

### 2022-05-06 FDT2020/response/response.tex
final commit for revisions

@@
 \newcommand{\cindy}[1]{\noindent{\bf {\color{magenta!80!black}{\sc Cindy:}  #1}}}
+
 \newcommand{\response}[1]{\noindent{{\color{blue!80!black}  #1}}}
-\iffalse
 \renewcommand{\arash}[1]{}
 \renewcommand{\cindy}[1]{}
-\fi
 \title{Responses to reviewers comments}
@@
 \section{General Response}
-\response{We thank the editor and reviewers for their insightful and constructive comments. }
-
-\arash{TODO: Thank the reviewers at length. Apologies for the delay in submission for the revisions, thanks the editor for the extensions.}
+\response{We thank the reviewers for their insightful and constructive comments.
+We sincerely apologize for the long delay in submitting our revision.
+We thank our editor very much for the extension.
+Our junior author finished his training and took a job in industry.
+The more senior co-author at a national lab accepts her considerable share of responsibility for the delay as well.
+}
+%\arash{TODO: Thank the reviewers at length. Apologies for the delay in submission for the revisions, thanks the editor for the extensions.}
 \section{Detailed Responses}
@@
 \response{We have addressed the issue in the proof of Theorem 3 as detailed below.
-We also made several major revision in our presentation specially with regards to the more technical parts of the paper.}
+We also made several major revision in our presentation especially with regards to the more technical parts of the paper.}
 \subsubsection{Minor Comments}
@@
 \item Introduction: Introduction jumps between describing methods and problems the methods are applied to.
-The there is a subsection 1.2 Experiments with more problem descriptions.
+There is a subsection 1.2 Experiments with more problem descriptions.
 Please restructure the introduction so
@@
 This makes the paragraph rather awkward to read, because the statements are not correct as stated.
-\response{We made various changes starting from the paragraph before Definition 1 and the discussion that follows, drawing the comparison between different objects that a gap can be defined on and where Definition 1 stands.
-Our definition is integrality gap of a polyhedron.}
+\response{We made various changes starting with the paragraph before Definition 1 through the discussion that follows.
+We compare our Definition 1 to other definitions of the integrality gap.
+Our definition is the integrality gap of a polyhedron.
+We explain why we use this definition.
+We also added more context about our definition of integrality gap to the abstract, so the reader is aware immediately that we are using a polyhedron-based definition.}
 
@@
 
-\response{As stated above, the discussion following Definition 1. We added a remark that $c$ need to be non-negative for Carr-Vempala to works.}
+\response{As stated above, the discussion following Definition 1. We added a remark that $c$ must be non-negative for Carr-Vempala to work.}
 
@@
 \response{Fixed.}
-\item p. 5, Proposition 2: Please specify where this is stated in [GLS93].
+
 \item p. 5, below Proposition 2: I don’t see that Proposition 2 and Theorem 3 are equivalent as stated. (Also in light of the remark about one result having an algorithm, and the other not.)
@@
 quickly. On TAP and 2EC, the authors compare to problem-specific approximation algorithms that are not particularly designed to produce high quality solutions either.
-\response{Our comparison of FDT to feasibility pump is to main showcase a use case of the algorithm and a direction that could be possibly explored.
-We are not offering FDT as a replacement for FP.
+\response{We respect and understand this reviewer's point of view.
+We have added some caveats to the start of the experimental section.
+Our experiments are intended to demonstrate using FDT for experimentally studying integrality gaps.
+We have explicitly stated the we are not recommending FDT as a replacement heuristic.
+We hope it will complement other general heuristics.
+%Our comparison of FDT to feasibility pump is mainly to showcase a use case of the algorithm and a direction that could be possibly explored.
+We are not suggesting FDT as a replacement for FP.
 We will add remarks that make this clear to the reader.
 
-With respect to Christofides, we mistakenly mentioned comparing FDT with Christofides but we in fact compare FDT with BOMC (Best of Many Christofides) - this has been fixed in the abstract and the paper.
+With respect to Christofides, we mistakenly wrote that we compared FDT to Christofides.
+In fact, we compare FDT with BOMC (Best of Many Christofides) - this has been fixed in the abstract and the paper.
 As presented in Figure 3, we don't settle for the worst-case upper bound of 3/2.
 Similarly, for TAP, FJ81 is the only rounding algorithm known for the solution of the CUT-LP.
-Again, we don't use the worst-case upper bound of 2 and use the instance specific gap provided by the algorithm.
-Also we remark that FDT is a generic algorithm that applies to any type of IP formulation, while BOMC and FJ81 only work for a certain type of formulation.}
+Again, we don't use the worst-case upper bound of 2.
+Instead we use the instance-specific gap provided by the algorithm.
+Also, FDT is a generic algorithm that applies to any formulation with a suitablly bounded integrality gap, while BOMC and FJ81 problem-specific.}
 
@@
 
-\response{We made several fixed in the abstract that addressed all the points mentioned above.}
+\response{We made several edits to the abstract. We believe they address all the points mentioned above.}
 \item The paper should mention the randomized metarounding algorithm by Carr and Vempala and compare it to the FDT algorithm. 
-\response{Added this paragraph right before section 1.1: 
-Carr and Vempala [CV00] showed if there an algorithm $\mathcal{A}$ that for $I\in \mathcal{I}$ and $c\geq 0$ finds $z\in S(I)$ with $cz\leq g'cx$ for any $x\in P(I)$, then $g'x$ can be \textbf{write} as a convex combination of points in $S(I)$.
+\response{We added this paragraph right before section 1.1: 
+Carr and Vempala [CV00] showed if there is an algorithm $\mathcal{A}$ that for $I\in \mathcal{I}$ and $c\geq 0$ finds $z\in S(I)$ with $cz\leq g'cx$ for any $x\in P(I)$, then $g'x$ can be written as a convex combination of points in $S(I)$.
 However, for many known problems there is a gap between the best known $g'$ and $g(\mathcal{I})$.
@@
 
-\response{The comparisons with FP are not presented to claim that FDT to provide direct comparisons between the two algorithms, but to provide a baseline on the IG upper bounds provided by another LP-based algorithm.
-We want to emphasize that the scope of this work in mostly on the theoretical contributions, rather than experimental results.}
+\response{We felt that readers might be curious about how FDT compares to another general incumbent heuristic.
+We were not able to find any code for feasibility pump 2.0.
+In the FP 2.0 paper, the authors wrote that the “overhead of constraint propagation can be quite large … Hence we need a very efficient implementation of the whole constraint propagation system, including both the single propagators and the overall propagation engine.”  FP 2.0 is much more complex than simple FP.
+To be fair to FP 2.0 in a comparison, we would need to program the authors’ optimizations to achieve their performance.
+Since our goal was to show that the performance can be reasonable, we felt that implementing the full, optimized FP 2.0 was out of scope.}
+%The comparisons with FP are not presented to claim that FDT to provide direct comparisons between the two algorithms, but to provide a baseline on the IG upper bounds provided by another LP-based algorithm.
+We want to emphasize that the scope of this work in mostly on the theoretical contributions, rather than experimental results.
 
@@
 \item In Theorem 3, I think $\mathcal{D}(S(I))$ should just be $S(I)$.
-\response{NOT FINAL: The proof of this theorem only shows it for the dominant of $S(I)$ and not $S(I)$ itself, although for many problems of interest we have $S(I)=\mathcal{D}(S(I))$. }
+\response{The proof of this theorem only holds for the dominant of $S(I)$ and not $S(I)$ itself, although for many problems of interest we have $S(I)=\mathcal{D}(S(I))$. }
 
@@
 \response{The figure is moved to page 3.}
-\item You mention that the Dom2IP algorithm can be used to prove that an IPs integrality gap is unbounded. How effective is this? \arash{need to think about this.}
+\item You mention that the Dom2IP algorithm can be used to prove that an IPs integrality gap is unbounded. How effective is this?
+
+\response{
+DomToIP starts from a feasible solution to the LP relaxation and tries to find an integer feasible solution in the support of the fractional solution.
+If Dom2IP fails to do this for any instance, we can conclude the integrality gap is infinite.
+We could perform a broad search over possible (useful/interesting) feasible points to the LP relaxation to find such a certificate for the unboundedness of the integrality gap.}
 \item Lemma 9 requires $\gamma_0 + \gamma_1 \leq 1$. Perhaps this should already be included
@@
 }
-Relatedly, Eisenbrand and Shmonin \cite{eisenbrand} introduced an algorithm that finds the maximum gap between the optimal values of an IP and its LP relaxation over all realizations of vector $b$ (for which the IP is feasible).
-Their algorithm runs in polynomial-time given $n$ is fixed.
-In contrast, FDT always runs in time polynomial in $n$, but obtains an upper bound on the integrality gap as opposed to an exact value.
+
 \item
@@
 constraint matrix) does not lead to the same or better result. Or maybe it does?
-\response{We added this paragraph in the discussion of why $\{0,1,2\}$ problems are different from binary problems: Another approach to a $\{0,1,2\}$ problem could be to ``binarize'' the variables, but splitting each variable into two binary copies and solving the binary problem via FDT for binary IPs (Theorem 4).
+\response{We added this paragraph in the discussion of why $\{0,1,2\}$ problems are different from binary problems: Another approach to a $\{0,1,2\}$ problem could be to ``binarize'' the variables, but splitting each variable into two binary copies and solving the binary problem via FDT for binary IPs (Theorem \ref{FDTFull}).
 One potential issue that can arise by doing this is that the binary version of a problem might have a larger integrality gap compared to the one that allows larger multiplicity.

### 2022-05-06 FDT2020/Introduction.tex
added a word
final commit for revisions

@@
 \item We give a simple  algorithm to give a feasible solution for any binary IP with bounded integrality gap. If this algorithm fails, then the integrality gap is infinite.
-\item We experimentally show that FDT can give good approximate solutions to small instances of vertex-cover and tree augmentation problems.
+\item We experimentally show that FDT can give good approximate solutions to small instances of vertex-cover (VC) and tree augmentation problems.
 \item We show that the integrality gap for 2EC (minimum 2-edge-connected sub-multigraph) is at most $\frac{6}{5}$ for Carr-Vempala points with at most $12$ vertices on the cycle formed by the fractional edges, matching the lower bound for the integrality gap for 2EC for these challenging instances.
@@
 In particular, we computationally prove an upper bound on small instances of 2EC with a specific structure.
-\item We demonstrate (with VC) how FDT can be used to find feasible solutions of improved quality compared to those from the feasiblity pump \cite{fp1}.
+\item We give proof-of-concept experimental results that demonstrate that FDT might be a reasonable heuristic in practice for some problems.
+For VC, FDT gives better solutions than the original feasibility pump \cite{fp1}, though requiring more time.
+Similarly, for TAP, FDT usually gives much better solutions than the known 2-approximation \cite{FJ81}, but runs more slowly.
+
 \end{itemize}
